### 2019-09-10 paper/abstract.Rmd
fst abstract

---
title: The problem and promise of scale in multilayer networks
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
---

Scale remains a seminal concept in ecology. Spatial scale has become a central consideration in the way we understand landscape ecology and animal space use. Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogenous landscapes. Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of how an animals perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics. Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animals perception of scale. We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales. Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data. Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data. Effective integration of spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network. Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.

### 2019-09-10 paper/guidelines.Rmd
split to guidelines

---
output: 
  github_document:
    toc: true
author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
date: "-- `r Sys.Date()`"
bibliography: multilayer-networks.bib
---

## Info
[Special Column info](https://academic.oup.com/CZ/pages/animal_social_system)

### Deadlines
* ~~Abstract submission: 30 August 2019~~
* Manuscript submission: 31 January 2020
* Printing: June 2020

### Guidelines
[General Instructions page](https://academic.oup.com/cz/pages/General_Instructions)

#### From issue organisers

* Appreciate ambition to link LE and SNA.
* Like the idea of reviewing different kinds of spatial data relevant to ML framework
* Hope simulations will be as relevant to movement and SNA data typically collected
* Manuscript will be relevant to both theoreticians and empiricists

## Keywords

1. spatial scale
1. social systems
1. multilayer networks
1. landscape ecology
1. network theory

## Boxes / paper layout

* Abstract
* Intro
* Box 1: Mathematical + language definitions of multilayer networks
* Box 2: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
* Spatial variables - example of GPS data, sampling landcover and networks across landcover classes?
* Temporal variables - example of GoG data, chunked seasonally maybe?
* Relevant multilayer metrics with above two? 
* Conclusion/fin

# References

### 2019-09-10 paper/introduction.Rmd
fst intro

--- 2019-09-10 paper/abstract.Rmd
@@
 date: "-- `r Sys.Date()`"
+bibliography: multilayer-networks.bib
 ---
-
-Scale remains a seminal concept in ecology.
-Spatial scale has become a central consideration in the way we understand landscape ecology and animal space use.
-Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogenous landscapes.
-Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of how an animals perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics.
-Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animals perception of scale.
-We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
-Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data.
-Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.
-Effective integration of spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network.
-Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.

### 2019-09-10 paper/unstructured.Rmd
fst intro

--- 2019-09-10 paper/guidelines.Rmd
@@
 date: "-- `r Sys.Date()`"
-bibliography: multilayer-networks.bib
 ---
-
-## Info
-[Special Column info](https://academic.oup.com/CZ/pages/animal_social_system)
-
-### Deadlines
-* ~~Abstract submission: 30 August 2019~~
-* Manuscript submission: 31 January 2020
-* Printing: June 2020
-
-### Guidelines
-[General Instructions page](https://academic.oup.com/cz/pages/General_Instructions)
 
@@
 * Conclusion/fin
-
-# References

### 2019-09-11 paper/unstructured.Rmd
rm temp variables
fin skeleton

@@
 
+**Conservation implications**
+
 ## Keywords
@@
 
-## Boxes / paper layout
+## Skeleton
+* Abstract
+* Brief introduction
+  * Networks, social networks, animal social systems 
+  * Landscape ecology, scale
+* Multilayer Networks
+  * What is a ML network
+  * What kinds of ML nets exist
+  * Which are relevant to spatial variables
+* Scale 
+  * What is scale
+  * In LE lit, how has scale been investigated
+  * Elements of scale relevant to animal social systems, animal movement data, landcover data
+* Box 1: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
+* Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data
+* Simulations
+* Discussion/results
+* Brief conclusion
+
+---
+
+From a sample of CZ papers:
 
 * Abstract
-* Intro
-* Box 1: Mathematical + language definitions of multilayer networks
-* Box 2: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
-* Spatial variables - example of GPS data, sampling landcover and networks across landcover classes?
-* Temporal variables - example of GoG data, chunked seasonally maybe?
-* Relevant multilayer metrics with above two? 
-* Conclusion/fin
+* Materials and Methods
+* Results
+* Discussion
+
+and sometimes
+* Conservation implications
+* Conclusion

### 2019-09-11 paper/introduction.Rmd
new refs.bib
fin skeleton
start intro

@@
 date: "-- `r Sys.Date()`"
-bibliography: multilayer-networks.bib
+bibliography: ../references/refs.bib
 ---
+
+# Introduction
+
+Animal social systems are complex and multifaceted
+
+traditionally, animal social systems are measured using direct observation, telemetry or pit tags
+interactions, e.g. grooming, aggression, etc,  between individuals are quantified by simplified measures 
+and often lacking any indication of the spatial context of the interaction
+
+recently the multilayer has been used to
+
+along with spatial variables, comes a large history of landscape ecology exploring and evaluating sensitivity to scale
+
+here we'll use simulations to evaluate the impact of scale on social and spatial variables 
+to better understand it's impact, implications in ML networks
+
+# Multilayer Networks
+
+Multilayer networks combine multiple networks layers with interlayer edges
+
+Layers in multilayer networks can be
+Animal social systems are
+
+What is a network
+
+How does a ML network build on that
+
+What kinds of ML nets exist
+
+Which can include spatial variables
+
+Multifaceted nature of animal social systems 
+many variables having a spatial component
+including landcover and habitat type
+fix rate and
+
+spatial variables defined by
+
+# Scale
+Scale
+
+in grain and extent
+
+grain is this
+
+extent is this

### 2019-09-11 paper/introduction.Rmd
more intro

@@
 # Multilayer Networks
+Multilayer networks combine network layers with interlayer edges
 
-Multilayer networks combine multiple networks layers with interlayer edges
+Two main types of multilayer networks exist: multiplex networks and interconnected networks.
+Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks).
+Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks).
+
+Of these, we have identified multirelational networks, networks of networks, intercontextual networks and spatial networks as likely to have spatial and scale considerations
 
@@
 How does a ML network build on that
-
-What kinds of ML nets exist
 
@@
 # Scale
-Scale
+What is scale
 
-in grain and extent
+in LE lit, how has scale been investigated
 
-grain is this
+Elements of scale relevant to animal social systems, animal movement data, landcover data
 
-extent is this
+Grain is this, extent is this
+
+How might scale influence results
+
+What kinds of spatial scale are there

### 2019-09-11 paper/unstructured.Rmd
rm temporal

@@
   * Elements of scale relevant to animal social systems, animal movement data, landcover data
-* Box 1: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
+* Box 1: Types of spatially explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
 * Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data

### 2019-09-11 paper/introduction.Rmd
start box1

@@
 Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks).
-Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks).
+Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks) [@finn2019].
 
@@
 What kinds of spatial scale are there
+
+# Box 1: Types of spatiotemporally explicit data
+
+Spatial data can be
+
+how associations are measured: e.g. spatsoc
+how relocations are categorized: e.g. landcover
+
+Multilayer networks incoroprate spatial variables in two ways:
+1. for determining association between individuals in a social system
+1. for characterizing the spatial context of social systems
+
+For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices.
+Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].
+
+# References

### 2019-09-11 scripts/pseudocode.R
fst pseudocode

@@ -1,0 +1,18 @@
+# Social association by landcover type
+
+
+library(spatsoc)
+
+DT <- fread('')
+
+group_times(DT, 'datetime', '5 minutes')
+
+group_pts(
+  DT,
+  ....
+  
+  splitBy = 'landcover'
+        )
+
+
+# make graphs by landcover

### 2019-09-11 paper/introduction.Rmd
more box1

@@
 
-Spatial data can be
+Spatial data can be:
 
-how associations are measured: e.g. spatsoc
-how relocations are categorized: e.g. landcover
+* how associations are measured: e.g. spatsoc
+* how relocations are categorized: e.g. landcover
 
 Multilayer networks incoroprate spatial variables in two ways:
+
 1. for determining association between individuals in a social system
@@
 
+## Measuring association
 For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices.
+
 Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].
 
+Biologging with GPS allows for simultaneous spatiotemporal sampling of multiple individuals in a group or population
+
+## Spatial context
+The spatial context of social systems can be defined as all
+
+what is the spatial context of an animal social system
+
+explicit spatial locations
+habitat patches
+landscape/habitat connectivity
+social variable + home range overlap = opportunity to interact
+
 # References

### 2019-09-12 paper/introduction.Rmd
more box 1

@@
 # Introduction
-
 Animal social systems are complex and multifaceted
@@
 
-# Box 1: Types of spatiotemporally explicit data
+# Box 1: Types of spatial variables 
+Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers.
+Edges connect different entities in the same layer or across layers as well as to the same entities across layers.
+The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within.
+Depending on the type, a multilayer network may include one or both of these types of spatial variables to better understand the complex connections between social systems and the landscapes they
 
-Spatial data can be:
+The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and *landscape scale data.
+* Georeferenced biologging data, including radio-frequency identification tags, radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to time and labour intensive direct observations of individuals and their interactions [@krause2011]
+
+Land cover, land use
+
+Edges between nodes can define individual's associations, preda
 

### 2019-09-12 paper/introduction.Rmd
it's complicated

@@
 
-The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and *landscape scale data.
-* Georeferenced biologging data, including radio-frequency identification tags, radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to time and labour intensive direct observations of individuals and their interactions [@krause2011]
+The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data.
+Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
+integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions.
+In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide an inside look.
+Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches.
+Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.
 
-Land cover, land use
+Given the variety of multilayer networks and types of spatial data that can be included, there are a large number of ways to combine them.
+Multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling'), including spatial variables such as land cover, land use, and explicit habitat patches.
+Multiplex networks, where each layer represents a different type of interaction, may be composed of a layer defined by an association index and another one by home range overlap.
+A network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.
 
-Edges between nodes can define individual's associations, preda
+<!-- it's complicated -->
+
+Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network
+
+All biologging sensors have some spatial error
+
+In addition, biologging sensors vary in terms of fix rate or data collection rate. GPS collars can be programmed but will inevitably vary
+Temporal grouping
+
+All remotely sensed imagery is an average of area on land, reported by the
+
+Matching scale of imagery to resolution of fix rate
+
+PIT tags have <1m reading distance [@krause2013]
+GPS collars have challenges due to dense vegetation 
+Telemetry >10m location error
 

### 2019-09-12 paper/introduction.Rmd
fin draft box1

--- 2019-09-11 paper/introduction.Rmd
@@
 
-# Box 1: Types of spatiotemporally explicit data
+# Box 1: Types of spatial variables 
+Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers.
+Edges connect different entities in the same layer or across layers, or the same entities across layers.
+The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within.
+A multilayer network may include one or both of these types of spatial variables to better understand the complex connections between individuals and the landscapes they occupy.
 
-Spatial data can be:
+The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data.
+Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
+integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions.
+In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide *an inside look*.
+Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches.
+Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.
+
+Given the variety of multilayer networks and types of spatial data that can be included, there are many ways to combine them.
+For example, multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling') defined by spatial variables such as land cover, land use, and explicit habitat patches.
+Multiplex networks, where each layer represents a different type of interaction, may be composed of layers defined by association indices and by home range overlap.
+Finally, a network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.
+
+<!-- it's complicated -->
+
+Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network.
+All biologging sensors have some limiting spatial resolution: PIT tags have <1m reading distance [@krause2013], radio telemetry can have >10m location error, and GPS devices are accurate within 3-30m, largely influenced by habitat and vegetation cover.
+In addition, biologging sensors vary in terms of data collection rate with GPS devices recording spatial locations on fixed measurement rates, PIT tags only recording spatial locations when individuals are within the reading distance of a fixed recording device and radio telemetry requiring either active users with handheld receivers or fixed receivers at specific locations.
+All landscape level measures derived from remotely sensed imagery are defined by their spatial resolution.
+Typically ranging from 1-1000m, the spatial resolution of an image is the length of one side of a pixel, usually square, that corresponds to its relative size on the ground.
+Lastly, combining the scale of the imagery and the fix rate of the biologging device in a biologically meaningful way remains a challenge.
+
+---
 

### 2019-09-20 paper/unstructured.Rmd
touch on which networks we will focus on

@@
 **Conservation implications**
+
+## To add
+
+### Introduction?
+We determined three types of multilayer networks most relevant to spatial variables
+Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
+Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here
 

### 2019-09-20 paper/unstructured.Rmd
add table 1 draft

@@
 ### Introduction?
-We determined three types of multilayer networks most relevant to spatial variables
+We determined three types of multilayer networks most relevant to spatial variables.
 Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure.
 Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here
+
+### Table 1
+
+|               | Spatial                                                           | Net of nets                                      | Interspecific                                              |
+|---------------|-------------------------------------------------------------------|--------------------------------------------------|------------------------------------------------------------|
+| layer         | spatially explicit                                                | subpops, fuzzy patches                           | dif species                                                |
+| node          | individuals                                                       | ind + nets                                       | ind + species nets                                         |
+| inter edges   | to self                                                           | to nets                                          | to species                                                 |
+| intra edges   | association to other                                              | association                                      | association                                                |
+| social grain  | type of interaction, chain rule, spatsoc threshold, hyena session | for intra, see left. for inter: define community |  for intra, see left. for inter: similarity, vulnerability |
+| spatial grain | resolution                                                        | patches, k=                                      | connectivity, clusters                                     |
 

### 2019-09-25 paper/table1.Rmd
mv table 1 to separate rmd

--- 2019-09-20 paper/unstructured.Rmd
@@
 
-#### From issue organisers
-
-* Appreciate ambition to link LE and SNA.
-* Like the idea of reviewing different kinds of spatial data relevant to ML framework
-* Hope simulations will be as relevant to movement and SNA data typically collected
-* Manuscript will be relevant to both theoreticians and empiricists
-
-**Conservation implications**
-
-## To add
-
-### Introduction?
 We determined three types of multilayer networks most relevant to spatial variables.
@@
 ### Table 1
+
+In table 1, we define three types of multilayer networks that incorporate spatial variables. 
+How are layers defined, nodes defined, inter layer edges
+
+We list variables affected by spatial and social scale
+
+We use a definition of spatial scale from LE,
+
+social scale is
+
+TODO: find pictures of ML nets to include
 
@@
 | spatial grain | resolution                                                        | patches, k=                                      | connectivity, clusters                                     |
-
-## Keywords
-
-1. spatial scale
-1. social systems
-1. multilayer networks
-1. landscape ecology
-1. network theory
-
-## Skeleton
-* Abstract
-* Brief introduction
-  * Networks, social networks, animal social systems 
-  * Landscape ecology, scale
-* Multilayer Networks
-  * What is a ML network
-  * What kinds of ML nets exist
-  * Which are relevant to spatial variables
-* Scale 
-  * What is scale
-  * In LE lit, how has scale been investigated
-  * Elements of scale relevant to animal social systems, animal movement data, landcover data
-* Box 1: Types of spatially explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
-* Box 2: Mathematical + language definitions of multilayer networks, metrics and measures of ML networks that are relevant to spatial data
-* Simulations
-* Discussion/results
-* Brief conclusion
-
----
-
-From a sample of CZ papers:
-
-* Abstract
-* Materials and Methods
-* Results
-* Discussion
-
-and sometimes
-* Conservation implications
-* Conclusion

### 2019-09-25 paper/unstructured.Rmd
start table 1 cap
mv table 1 to separate rmd

--- 2019-09-20 paper/unstructured.Rmd
@@
 ### Introduction?
-We determined three types of multilayer networks most relevant to spatial variables
+We determined three types of multilayer networks most relevant to spatial variables.
 Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure.

### 2019-09-26 paper/table1.Rmd
drop toc

@@
 ---
-output: 
-  github_document:
-    toc: true
+output: github_document
 author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
@@
 ---
+
+### Table 1
 
@@
 
-### Table 1
+In table 1, we define three types of multilayer networks that *can* incorporate spatial variables.
 
-In table 1, we define three types of multilayer networks that incorporate spatial variables. 
+Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers are
+
 How are layers defined, nodes defined, inter layer edges

### 2019-09-26 paper/table1.Rmd
use csv to build table 1

@@
 
-|               | Spatial                                                           | Net of nets                                      | Interspecific                                              |
-|---------------|-------------------------------------------------------------------|--------------------------------------------------|------------------------------------------------------------|
-| layer         | spatially explicit                                                | subpops, fuzzy patches                           | dif species                                                |
-| node          | individuals                                                       | ind + nets                                       | ind + species nets                                         |
-| inter edges   | to self                                                           | to nets                                          | to species                                                 |
-| intra edges   | association to other                                              | association                                      | association                                                |
-| social grain  | type of interaction, chain rule, spatsoc threshold, hyena session | for intra, see left. for inter: define community |  for intra, see left. for inter: similarity, vulnerability |
-| spatial grain | resolution                                                        | patches, k=                                      | connectivity, clusters                                     |
+```{r, echo = FALSE}
+library(data.table)
+tab1 <- fread('table1.csv')
+knitr::kable(tab1)
+```

### 2019-09-26 paper/table1.Rmd
gh doc is nice
start intro paragraph

@@
 ---
-output: github_document
+output: 
+#   pdf_document
+# classoption: landscape
+  # word_document:
+  #   reference_docx: template.docx
+  github_document
 author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
@@
 ### Table 1
+In Table 1, we define three types of multilayer networks that incorporate spatial variables.
+Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges.
+Layers represent the different types of relationships, individuals or contexts of the social system.
+Nodes represent individual entities in the network, connected by some association or relationship with edges.
+Interlayer edges connect layers to other layers or individuals across layers.
+Intralayer edges connect individuals to other individuals within a network layer.
 
-We determined three types of multilayer networks most relevant to spatial variables.
-Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure.
+Depending on the type of network, interlayer edges connect individuals to themselves across different contexts or to different individuals
+
+multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
 Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here
 
-In table 1, we define three types of multilayer networks that *can* incorporate spatial variables.
-
-Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges. Layers are
+An animal's social network is multifaceted and complex, though this system is often examined
 
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, warning = FALSE}
+# library(pander)
+# panderOptions('table.alignment.default', function(df)
+#     ifelse(sapply(df, is.numeric), 'right', 'left'))
+# panderOptions('table.split.table', Inf)
+# panderOptions('big.mark', ",")
+# panderOptions('keep.trailing.zeros', TRUE)
+
 library(data.table)
+library(magrittr)
+library(kableExtra)
+
 tab1 <- fread('table1.csv')
-knitr::kable(tab1)
+
+options(knitr.table.format = "markdown")
+
+knitr::kable(tab1[c(1:7, 9)])
 ```

### 2019-09-27 paper/table1.Rmd
use table format md, works in pdf, word, gh doc

@@
 # classoption: landscape
-  # word_document:
-  #   reference_docx: template.docx
-  github_document
+  word_document:
+    reference_docx: template.docx
+  # github_document
 author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
-date: "-- `r Sys.Date()`"
+date: "`r Sys.Date()`"
 ---
@@
 
-knitr::kable(tab1[c(1:7, 9)])
+knitr::kable(tab1)
 ```

### 2019-09-27 paper/table1.Rmd
rm old pander

@@
 output: 
-  # pdf_document
-# classoption: landscape
-  word_document:
-    reference_docx: template.docx
-  # github_document
+  # word_document:
+  #   reference_docx: template.docx
+  github_document
 author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
 date: "`r Sys.Date()`"
+bibliography: ../references/refs.bib
+
 ---
@@
 ### Table 1
-In Table 1, we define three types of multilayer networks that incorporate spatial variables.
-Multilayer networks are composed of layers, nodes, interlayer edges and intralayer edges.
+In Table 1, we describe three types of multilayer networks that incorporate spatial variables.
+Multilayer networks are composed of layers, nodes and edges.
+Layers represent different types of relationships
+
+The edges are often abstracted because they no longer in the sense that they represent a specific spatial and temporal context, which
+
+[@dale2017applying]
+
 Layers represent the different types of relationships, individuals or contexts of the social system.
@@
 Intralayer edges connect individuals to other individuals within a network layer.
+
+Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)
+
+Layers represent a type of edge (e.g.: grooming and association), entity (e.g.: male and female, or different species), or spatial context (e.g.: landcover type, patch).
 
@@
 
-TODO: find pictures of ML nets to include
-
 ```{r, echo = FALSE, warning = FALSE}
-# library(pander)
-# panderOptions('table.alignment.default', function(df)
-#     ifelse(sapply(df, is.numeric), 'right', 'left'))
-# panderOptions('table.split.table', Inf)
-# panderOptions('big.mark', ",")
-# panderOptions('keep.trailing.zeros', TRUE)
-
 library(data.table)
-library(magrittr)
-library(kableExtra)
 

### 2019-09-27 paper/introduction.Rmd
add notes from meeting
integrate wg revisions on box 1

@@
 # Scale
+perception of scale
+
 What is scale
@@
 # Box 1: Types of spatial variables 
+<!-- try:
+
+I think you could organize this in the analytical steps you will follow and then have the effect of scale at the end of each? Then you can demonstrate the additive effects scale decisions can have
+
+ Biologging data and landscape data
+- table
+Multilayer networks: Edges
+- images
+ Combining networks and spatial data
+- information about your results
+-->
+
 Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers.
@@
 The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within.
-A multilayer network may include one or both of these types of spatial variables to better understand the complex connections between individuals and the landscapes they occupy.
+A multilayer network may include one or both types of spatial variables to better understand the complex connections between individuals and the landscapes they occupy.
 
-The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data.
+The main types of spatial data that are included in multilayer networks are georeferenced biologging data and landscape level data.
 Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
 integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions.
-In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide *an inside look*.
-Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches.
-Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.
+Also, many animals are small or cryptic, e.g.: marine mammals and birds, thus remotely sensed data are used to infer behavioural processes.
+Many derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches.
+Landscape scale data include relatively static measures of a lanscape such as land cover, land use, and elevation, and more dynamic measures such as temperature, precipitation and snow cover.
 
-Given the variety of multilayer networks and types of spatial data that can be included, there are many ways to combine them.
+Given the variety of multilayer networks and types of spatial data that can be included, there are many ways to integrate spatial data within multilayer networks.
 For example, multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling') defined by spatial variables such as land cover, land use, and explicit habitat patches.
 Multiplex networks, where each layer represents a different type of interaction, may be composed of layers defined by association indices and by home range overlap.
-Finally, a network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.
+Finally, a network of networks may be used to represent *communities* as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.
 
@@
 
-Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network.
+<!-- the list of accuracies could be a table -->
+Spatial scale influences the inferences derived from spatial data when combining them in a multilayer network.
 All biologging sensors have some limiting spatial resolution: PIT tags have <1m reading distance [@krause2013], radio telemetry can have >10m location error, and GPS devices are accurate within 3-30m, largely influenced by habitat and vegetation cover.
-In addition, biologging sensors vary in terms of data collection rate with GPS devices recording spatial locations on fixed measurement rates, PIT tags only recording spatial locations when individuals are within the reading distance of a fixed recording device and radio telemetry requiring either active users with handheld receivers or fixed receivers at specific locations.
+Also, biologging sensors vary in terms of data collection rate with GPS devices recording spatial locations on fixed measurement rates, PIT tags only recording spatial locations when individuals are within the reading distance of a fixed recording device and radio telemetry requiring either active users with handheld receivers or fixed receivers at specific locations.
 All landscape level measures derived from remotely sensed imagery are defined by their spatial resolution.
 Typically ranging from 1-1000m, the spatial resolution of an image is the length of one side of a pixel, usually square, that corresponds to its relative size on the ground.
-Lastly, combining the scale of the imagery and the fix rate of the biologging device in a biologically meaningful way remains a challenge.
+In conclusion, combining the scale of the imagery and the fix rate of biologging devices *can be resolved using <reccomendation>*.
 

### 2019-09-27 paper/table1.Rmd
submit table1 wg

@@
 output: 
-  # word_document:
-  #   reference_docx: template.docx
-  github_document
+  word_document:
+    reference_docx: template.docx
+  # github_document
 author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
@@
 bibliography: ../references/refs.bib
-
+csl: vancouver.csl
 ---
 
+<!--
+*network of networks is just an intraspecific network* *interspecific networks are networks of networks*
+-->
+
 ### Table 1
-In Table 1, we describe three types of multilayer networks that incorporate spatial variables.
 Multilayer networks are composed of layers, nodes and edges.
-Layers represent different types of relationships
+Layers represent different types of relationships (e.g.: grooming or association), types of entities (e.g.: male and female, or different species), and spatial locations (e.g.: landcover type, patch) [@pilosof2017].
+Nodes represent individual entities in the network, connected by some association or relationship with edges.
+Interlayer edges connect layers to other layers or individuals across layers.
+Intralayer edges connect individuals to other individuals within a layer.
+In Table 1, we describe three types of multilayer networks that incorporate spatial variables: spatially explicit networks, networks of networks and interspecific networks.
+Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and relevant considerations will be detailed here.
+
+<!-- 
+Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)
+
+An animal's social network is multifaceted and complex, though this system is often examined
 
@@
 
-[@dale2017applying]
-
-Layers represent the different types of relationships, individuals or contexts of the social system.
-Nodes represent individual entities in the network, connected by some association or relationship with edges.
-Interlayer edges connect layers to other layers or individuals across layers.
-Intralayer edges connect individuals to other individuals within a network layer.
-
-Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)
-
-Layers represent a type of edge (e.g.: grooming and association), entity (e.g.: male and female, or different species), or spatial context (e.g.: landcover type, patch).
-
-Depending on the type of network, interlayer edges connect individuals to themselves across different contexts or to different individuals
-
-multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
-Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here
-
-An animal's social network is multifaceted and complex, though this system is often examined
-
-How are layers defined, nodes defined, inter layer edges
-
-We list variables affected by spatial and social scale
-
-We use a definition of spatial scale from LE,
-
-social scale is
+what about intralayer social grain -->
 
@@
 ```
+
+# References

### 2019-09-30 paper/table1.Rmd
add wg notes

@@
 In Table 1, we describe three types of multilayer networks that incorporate spatial variables: spatially explicit networks, networks of networks and interspecific networks.
-Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and relevant considerations will be detailed here.
+<!-- not clear --> Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and relevant considerations will be detailed here.
 
 <!-- 
+highlight examples at the beginning? in the text?
+
 Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)
@@
 The edges are often abstracted because they no longer in the sense that they represent a specific spatial and temporal context, which
+
+mv type of network across the top
 

### 2019-12-08 paper/box1.Rmd
split box1 off

--- 2019-09-27 paper/introduction.Rmd
@@
 ---
-title: The problem and promise of scale in multilayer networks
 output: 
@@
 ---
-
-# Introduction
-Animal social systems are complex and multifaceted
-
-traditionally, animal social systems are measured using direct observation, telemetry or pit tags
-interactions, e.g. grooming, aggression, etc,  between individuals are quantified by simplified measures 
-and often lacking any indication of the spatial context of the interaction
-
-recently the multilayer has been used to
-
-along with spatial variables, comes a large history of landscape ecology exploring and evaluating sensitivity to scale
-
-here we'll use simulations to evaluate the impact of scale on social and spatial variables 
-to better understand it's impact, implications in ML networks
-
-# Multilayer Networks
-Multilayer networks combine network layers with interlayer edges
-
-Two main types of multilayer networks exist: multiplex networks and interconnected networks.
-Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks).
-Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks) [@finn2019].
-
-Of these, we have identified multirelational networks, networks of networks, intercontextual networks and spatial networks as likely to have spatial and scale considerations
-
-Layers in multilayer networks can be
-Animal social systems are
-
-What is a network
-
-How does a ML network build on that
-
-Which can include spatial variables
-
-Multifaceted nature of animal social systems 
-many variables having a spatial component
-including landcover and habitat type
-fix rate and
-
-spatial variables defined by
-
-# Scale
-perception of scale
-
-What is scale
-
-in LE lit, how has scale been investigated
-
-Elements of scale relevant to animal social systems, animal movement data, landcover data
-
-Grain is this, extent is this
-
-How might scale influence results
-
-What kinds of spatial scale are there
 

### 2019-12-08 paper/introduction.Rmd
tidy intro

--- 2019-09-12 paper/introduction.Rmd
@@
 ---
-title: The problem and promise of scale in multilayer networks
-output: 
-  github_document:
-    toc: true
-author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
-date: "-- `r Sys.Date()`"
+output: github_document
 bibliography: ../references/refs.bib
@@
 
-# Box 1: Types of spatial variables 
-Multilayer networks can incorporate spatial variables to define edges between nodes and to characterize the spatial context of network layers.
-Edges connect different entities in the same layer or across layers as well as to the same entities across layers.
-The spatial context of a network layer is defined here as the landscape elements, generally abiotic, that an animal social system exists within.
-Depending on the type, a multilayer network may include one or both of these types of spatial variables to better understand the complex connections between social systems and the landscapes they
-
-The main types of spatial data that can be included in multilayer networks are georeferenced biologging data and landscape level data.
-Georeferenced biologging data, including radio-frequency identification tags (RFID), passive
-integrated transponder (PIT), radiotelemetry, and Global Positioning System (GPS) devices, provide an alternative to intensive direct observations of individuals and their interactions.
-In addition, some animals are not easily observed, e.g.: marine mammals and birds, and these data provide an inside look.
-Some derived products can be generated from these data as well, including home ranges, utilization distributions and habitat patches.
-Landscape level data include relatively stable measures of a lanscape such as land cover, land use and elevation, and more variable measures such as temperature, precipitation and snow cover.
-
-Given the variety of multilayer networks and types of spatial data that can be included, there are a large number of ways to combine them.
-Multilayer networks may be composed of categorical and unordered layers (termed 'categorical coupling'), including spatial variables such as land cover, land use, and explicit habitat patches.
-Multiplex networks, where each layer represents a different type of interaction, may be composed of a layer defined by an association index and another one by home range overlap.
-A network of networks may be used to represent communities as layers with interlayer edges defined by their spatial connectivity and intralayer edges defined by a spatially derived association index.
-
-<!-- it's complicated -->
-
-Spatial scale influences all of these types of spatial data and the inferences derived when combining them in a multilayer network
-
-All biologging sensors have some spatial error
-
-In addition, biologging sensors vary in terms of fix rate or data collection rate. GPS collars can be programmed but will inevitably vary
-Temporal grouping
-
-All remotely sensed imagery is an average of area on land, reported by the
-
-Matching scale of imagery to resolution of fix rate
-
-PIT tags have <1m reading distance [@krause2013]
-GPS collars have challenges due to dense vegetation 
-Telemetry >10m location error
-
-* how associations are measured: e.g. spatsoc
-* how relocations are categorized: e.g. landcover
-
-Multilayer networks incoroprate spatial variables in two ways:
-
-1. for determining association between individuals in a social system
-1. for characterizing the spatial context of social systems
-
-## Measuring association
-For example, association between individuals can be determined using georeferenced biologging devices such as radio‐frequency identification tags, radiotelemetry, and global positioning system (GPS) devices.
-
-Proximity based social networks (PBSNs) are association networks based on close proximity between individuals [@spiegel2016].
-
-Biologging with GPS allows for simultaneous spatiotemporal sampling of multiple individuals in a group or population
-
-## Spatial context
-The spatial context of social systems can be defined as all
-
-what is the spatial context of an animal social system
-
-explicit spatial locations
-habitat patches
-landscape/habitat connectivity
-social variable + home range overlap = opportunity to interact
-
 # References

### 2019-12-08 paper/introduction.Rmd
skeleton

@@
 # Introduction
+
+<!-- Landscape spatial scale -->
+<!-- Social proximity scale -->
+<!-- Regular networks -->
+<!-- Multilayer networks -->
+<!-- Case study -->
+
+---
+
+Spatial scale is a central consideration in the way we understand landscape ecology and animal space use.
+
+Despite the interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of how an animals perception of spatial scale, e.g., grain and extent,
+
+We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
+Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data.
+Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.
+Effective integration of spatial processes, including biologically meaningful scales, into animal social networks is an emerging area of research.
+Our contribution will incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network.
+Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.
+
+---
+
+potential for interconnectedness among individual animals and the landscapes they occupy.
+
 Animal social systems are complex and multifaceted

### 2019-12-08 paper/introduction.Rmd
more skeleton

@@
 <!-- Landscape spatial scale -->
+
 <!-- Social proximity scale -->
-<!-- Regular networks -->
-<!-- Multilayer networks -->
-<!-- Case study -->
+
+<!-- Regular networks
+* SNA significant outcomes
+-->
+
+<!-- Multilayer networks
+used across disciplines
+-->
+Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a].
+They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a].
+Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].
+
+<!-- Case study 
+deer
+fogo caribou
+-->
 

### 2019-12-08 paper/introduction.Rmd
first paragraph

@@
 <!-- Landscape spatial scale -->
+Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992].
 
-<!-- Social proximity scale -->
+heteroneity of landscapes
+within seemingly homogeneous patches, exist lower level processes including species interactions, resource availability, disease transfer [@legendre1993]
+
+Animals may be influenced by processes at multiple scales
+
+<!-- observational scales of landscapes do not necessarily correspond to the "scale of effect" of species-landscape relationships, or the scale at which there is the strongest relationship [@jackson2015]-->
+
+the scales that influence animals and the patterns of their landscapes may be disjoint [@chave2013].
+The effects of scale have been explicitly investigated across many ecological studies including habitat selection [@mayor2007], evaluating satellite imagery [@benson1995] and    of ecology including landscape ecology, movement ecology, earth observation [@benson1995], habitat selection[@mayor2007]
+
+<!-- observers bias their perspective when selecting a scale,often unknowingly or without considering the implications [@allen2015].  -->
+
+Scale can be considered for all measured quantities [@schneider2009] including spatial and temporal variables as well as domain specific <!--lead into social-->
+
+<!-- Social proximity scale 
+sociality exists 
+-->
+Social scale is the type of social relationship measured and how this relationship is defined [@farine2015].
+If the greater range of a social relationship is the entire social system for an organism, a particular social scale may focus on only a limited type of relationship like grooming or aggression.
 
@@
 They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a].
-Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].
+<!--GENERALLY INTERESTING Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].-->
+
+For multilayer social networks, three types of scale are relevant: spatial, temporal and social scale.
 
@@
 -->
+
+integrating networks across scales
+explore sensitivity of network measures to scale
 

### 2019-12-08 paper/introduction.Rmd
start second

@@
 -->
+Sociality is important because conspecifics have positive and negative benefits
+
+Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007].
+Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007].
+Negative effects include increased competition, risk of disease transfer and infection [@silk2007].
+
 Social scale is the type of social relationship measured and how this relationship is defined [@farine2015].

### 2019-12-08 paper/introduction.Rmd
clarify skeleton

@@
 
-<!-- Landscape spatial scale -->
-Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992].
+<!-- ### Landscape spatial scale -->
+Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992problem].
 

### 2019-12-08 paper/introduction.Rmd
more spatial

@@
 
-<!-- Social proximity scale 
+Spatial scale is a central consideration in the way we understand landscape ecology and animal space use.
+
+<!-- ### Social proximity scale 
 sociality exists 
@@
 
-<!-- Regular networks
+<!-- ### Regular networks
 * SNA significant outcomes
 -->
+Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009]
 
-<!-- Multilayer networks
+infer process from large scale pattern [@krause2009]
+
+Structure of social networks affects evolutionary processes, population dynamics, [@kurvers2014]
+
+<!-- ### Multilayer networks
 used across disciplines
@@
 
-<!-- Case study 
+<!-- ### Case study 
 deer
@@
 ---
-
-Spatial scale is a central consideration in the way we understand landscape ecology and animal space use.
 

### 2019-12-09 paper/introduction.Rmd
fin first

@@
 <!-- ### Landscape spatial scale -->
-Our understanding of ecological patterns and processes are directly linked to the scale at which they are observed [@levin1992problem].
-
-heteroneity of landscapes
-within seemingly homogeneous patches, exist lower level processes including species interactions, resource availability, disease transfer [@legendre1993]
-
-Animals may be influenced by processes at multiple scales
+Our understandings of ecological pattern and process are directly linked to the scale at which they are observed [@levin1992problem].
+Animals and landscapes are influenced across scales by higher level processes, e.g.
+climate and productivity [@field2009], and lower level processes, e.g.
+species interactions and resource availability [@legendre1993; @chave2013].
+The effect of scale has been explicity considered in ecology including in species distribution [@elith2009], habitat selection [@mayor2007] and food webs [@sugihara1989b].
+Scale can be considered for all measured quantities [@schneider2009] including spatial and temporal variables as well as domain specific variables such as sociality.
 
@@
 
-the scales that influence animals and the patterns of their landscapes may be disjoint [@chave2013].
-The effects of scale have been explicitly investigated across many ecological studies including habitat selection [@mayor2007], evaluating satellite imagery [@benson1995] and    of ecology including landscape ecology, movement ecology, earth observation [@benson1995], habitat selection[@mayor2007]
+<!-- the scales that influence animals and the patterns of their landscapes may be disjoint [@chave2013].  -->
 
@@
 
-Scale can be considered for all measured quantities [@schneider2009] including spatial and temporal variables as well as domain specific <!--lead into social-->
-
-Spatial scale is a central consideration in the way we understand landscape ecology and animal space use.
+<!-- Spatial scale is a central consideration in the way we understand landscape ecology and animal space use.  -->
 
@@
 
----
-
 Despite the interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of how an animals perception of spatial scale, e.g., grain and extent,
@@
 We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
+
+---
+
 Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data.

### 2019-12-09 paper/introduction.Rmd
a bit of case study
fin pour la nuit

@@
 -->
-Sociality is important because conspecifics have positive and negative benefits
 
-Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007].
+<!-- Sociality exists across scales -->
+
+<!-- How do consider shared space use -->
+
+<!-- Spatial proximity as a proxy for interactions  -->
+
+<!-- Social association -->
+
+<!-- Home range overlap  -->
+
+<!-- Connection of individuals within a social structure can be formalized/analyzed as a social network -->
+
+co-occurrence is used in social network studies as a synonym for social association (Farine and Whitehead 2015).
+
+Sociality, defined simply as some degree of shared space use among conspecifics [@tinbergen1951], exists across scales.
+Social scale is the type of social relationship observed and how this relationship is defined [@farine2015].
+For example, grooming and mating relationships require immediate proximity between conspecifics whereas home range overlap occurs over much larger spatial and temporal scales.
+
+Shared space is a requirement for social interaction, however, it remains unclear whether spatial proximity scales predictably with social interactions (Castles et al. 2014; Farine 2015).
+
+<!-- Sociality is defined here as by @tinbergen1951: "an animal is called social when it strives to be in the neighbourhood of fellow members of its species when performing some, or all, of its instinctive activities".
+-->
+
+<!-- Sociality is important because conspecifics have positive and negative benefits -->
+
+<!-- Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007].
 Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007].
 Negative effects include increased competition, risk of disease transfer and infection [@silk2007].
+-->
 
@@
 -->
+We will use two case studies to explore the sensitivity of multilayer network measures across scales. One, using an island population of caribou (*Rangifer tarandus*)
 

### 2019-12-09 paper/introduction.Rmd
start sna

--- 2019-12-09 paper/introduction.Rmd
@@
 bibliography: ../references/refs.bib
+csl: cite.csl
 ---
@@
 <!-- ### Landscape spatial scale -->
-Our understandings of ecological pattern and process are directly linked to the scale at which they are observed [@levin1992problem].
-Animals and landscapes are influenced across scales by higher level processes, e.g.
-climate and productivity [@field2009], and lower level processes, e.g.
-species interactions and resource availability [@legendre1993; @chave2013].
+Our understandings of ecological pattern and process are directly linked to the scale at which they are observed [@levin1992problem; @allen2015].
+Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity [@field2009], and lower level processes, such as species interactions and resource availability [@legendre1993; @chave2013].
 The effect of scale has been explicity considered in ecology including in species distribution [@elith2009], habitat selection [@mayor2007] and food webs [@sugihara1989b].
@@
 
-<!-- ### Social proximity scale 
-sociality exists 
--->
-Sociality is important because conspecifics have positive and negative benefits
-
-Sociality is accompanied by positive and negative effects, and evolves when the net benefit is greater than the cost [@silk2007].
-Positive effects include protection from predators, mating opportunities, and resource location and access [@silk2007].
-Negative effects include increased competition, risk of disease transfer and infection [@silk2007].
-
-Social scale is the type of social relationship measured and how this relationship is defined [@farine2015].
-If the greater range of a social relationship is the entire social system for an organism, a particular social scale may focus on only a limited type of relationship like grooming or aggression.
+<!-- ### Social proximity scale  -->
+Sociality, defined simply as the degree of shared space use among conspecifics [@tinbergen1951], exists across scales.
+For example, grooming and mating relationships requires close proximity between conspecifics and occurs over brief time periods whereas home range overlap occurs over larger spatial and temporal scales.
+Shared space is a requirement for social interaction, however, it remains unclear whether spatial proximity scales predictably with social interactions [@castles2014a; @farine2015a].
+Social scale can be defined as the type of relationship observed [@farine2015a] and these relationships can be explicitly defined and measured in social network analyses [@farine2015b].
 
@@
 -->
+
+Rooted in mathematical graph theory, animal social networks measures the relationships of individuals and organization of animal social systems [@krause2009; @Wey2008; @croft2008].
+Social network analyses provide insight into mating behaviours, species interactions, and community structures.
+
 Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009]

### 2019-12-09 paper/introduction.Rmd
fin sna

@@
 
-Rooted in mathematical graph theory, animal social networks measures the relationships of individuals and organization of animal social systems [@krause2009; @Wey2008; @croft2008].
-Social network analyses provide insight into mating behaviours, species interactions, and community structures.
+Rooted in mathematical graph theory, animal social networks measure the relationships of individuals and organization of social systems [@krause2009; @wey2008a; @croft2008].
+Social network analyses provide insight into mating behaviours, interspecific interactions, and community structures [@pinter-wollman2014].
+The structure of social networks influences population dynamics and evolutionary processes [@kurvers2014].
+Nevertheless, social network analyses usually only consider a single measure of sociality, drastically simplifying the complexity of animal social systems [@finn2019].
 
-Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009]
+<!-- Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009] -->
 
-infer process from large scale pattern [@krause2009]
-
-Structure of social networks affects evolutionary processes, population dynamics, [@kurvers2014]
+<!-- infer process from large scale pattern [@krause2009] -->
 

### 2019-12-09 paper/introduction.Rmd
start ml

@@
 -->
-Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a].
-They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a].
-<!--GENERALLY INTERESTING Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].-->
+Multilayer networks explicitly consider social systems across contexts [@pilosof2017a].
+They are made up of multiple layers, each representing types of relationships or individuals, spatial areas and temporal windows [@kivela2014; @porter2018a].
+Multilayer networks have been used to described multidimensional human social systems, complex transportation networks and the complete neural network of an organism [@boccaletti2014].
+Recently, multilayer networks have been highlighted as a way to better characterize complex social systems in animal behaviour studies [@silk2018a; @finn2019].
 
-For multilayer social networks, three types of scale are relevant: spatial, temporal and social scale.
+<!-- For multilayer social networks, three types of scale are relevant: spatial, temporal and social scale. -->
 
@@
 -->
-We will use two case studies to explore the sensitivity of multilayer network measures across scales. One, using an island population of caribou (*Rangifer tarandus*)
+We will use two case studies to explore the sensitivity of multilayer network measures across scales.
+One, using a population of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland, Canada with seasonal differences in resource availability and social association [@peignier2019].
+The second using a small group of white-tailed deer (*Odocoileus virginianus*)
 

### 2019-12-09 paper/introduction.Rmd
tidy + fin ml (for now)

@@
 One, using a population of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland, Canada with seasonal differences in resource availability and social association [@peignier2019].
-The second using a small group of white-tailed deer (*Odocoileus virginianus*)
-
-integrating networks across scales
-explore sensitivity of network measures to scale
-
-Despite the interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of how an animals perception of spatial scale, e.g., grain and extent,
-
-We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
-
----
-
-Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data.
-Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.
-Effective integration of spatial processes, including biologically meaningful scales, into animal social networks is an emerging area of research.
-Our contribution will incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network.
-Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.
-
----
-
-potential for interconnectedness among individual animals and the landscapes they occupy.
-
-Animal social systems are complex and multifaceted
-
-traditionally, animal social systems are measured using direct observation, telemetry or pit tags
-interactions, e.g. grooming, aggression, etc,  between individuals are quantified by simplified measures 
-and often lacking any indication of the spatial context of the interaction
-
-recently the multilayer has been used to
-
-along with spatial variables, comes a large history of landscape ecology exploring and evaluating sensitivity to scale
-
-here we'll use simulations to evaluate the impact of scale on social and spatial variables 
-to better understand it's impact, implications in ML networks
-
-# Multilayer Networks
-Multilayer networks combine network layers with interlayer edges
-
-Two main types of multilayer networks exist: multiplex networks and interconnected networks.
-Layers in multiplex networks consist of the same entities with each layer representing either a different type of interaction (as in multirelational networks) or a different time point or window (as in temporal networks).
-Layers in interconnected networks consist of the same or different entities with layers representing different subsystems (as in networks of networks), different types of entities (as in intercontextual networks), or different spatial locations (as in spatial networks) [@finn2019].
-
-Of these, we have identified multirelational networks, networks of networks, intercontextual networks and spatial networks as likely to have spatial and scale considerations
-
-Layers in multilayer networks can be
-Animal social systems are
-
-What is a network
-
-How does a ML network build on that
-
-Which can include spatial variables
-
-Multifaceted nature of animal social systems 
-many variables having a spatial component
-including landcover and habitat type
-fix rate and
-
-spatial variables defined by
-
-# Scale
-perception of scale
-
-What is scale
-
-in LE lit, how has scale been investigated
-
-Elements of scale relevant to animal social systems, animal movement data, landcover data
-
-Grain is this, extent is this
-
-How might scale influence results
-
-What kinds of spatial scale are there
+The second using a small group of white-tailed deer (*Odocoileus virginianus*) in an urban environment **WHERE XYZ**.
+We will manipulate the spatial scale of landscapes, temporal windows of analysis and social scale of relationships, highlighting the importance of considering scale in multilayer networks.
 

### 2019-12-11 scripts/explore-networkx.Rmd
from_pandas_dataframe -> from_pandas_edgelist

---
title: "explore networkx"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source('../scripts/1-single-scale.R')
```

Expectation is an edge list

```{python}
import pandas as pd
import networkx as nx

edges = pd.read_csv('../data/edgels.csv')
edges
G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')
```

### 2019-12-11 scripts/explore-networkx.py

@@ -1,2 +1,5 @@
+
+
+
 import networkx as nx
 G = nx.Graph()

### 2019-12-11 scripts/1-single-scale.R
output edges from 1-single-scale.R

@@ -132,12 +132,18 @@ add_layers_ml(ml, ulc, directed = FALSE)
 
 add_vertices_ml(ml, unique(na.omit(sub[, .(get(idcol), relc)])))
 
-edges <- rbindlist(lapply(gLs, function(g) data.table(get.edgelist(g))),
-                   idcol = 'relc')
+edges <- rbindlist(
+  lapply(gLs, function(g) {
+    data.table(get.edgelist(g), w = E(g)$weight)}),
+  idcol = 'relc')
 
 add_edges_ml(ml, edges[, .(V1, relc, V2, relc)])
 
 plot(ml)
+
+
+### Output ----
+fwrite(edges, 'data/edgels.csv')
 
 ### Plots ----
 ggplot(multideg) +

### 2019-12-16 paper/manuscript.Rmd
fst manuscript

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
output: github_document
---

## Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use. Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogenous landscapes. Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animals perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics. Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animals perception of scale. We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales. Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data. *Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.* Effective integration of spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network. Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al 2015). Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al 2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distributions (Elith et al 2009) habitat selection (Mayor et al 2007) and food webs (Sugihara et al 1989). Scale can be considered for all types of measured quantities9 including spatial and temporal variables, as well as behavioural variables including sociality.

Sociality exists across scales (Whitehead 2008). For example, grooming and mating relationships requires close proximity between conspecifics and occur over brief time periods (e.g. Carter et al. 2015), whereas social association represents shared space use by members of the same social group (Franks et al. 2010). Further, home range overlap among individuals is a coarse scale of sociality, where individuals share space over larger spatial and temporal scales (e.g. Piza-Roca et al. 2018). Shared space is a requirement for most types of social interactions, however, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al. 2014; Farine 2015). Social scale can be defined as the type of relationship observed (Farine 2015) and these relationships can be explicitly defined and measured in social network analyses (Farine et al. 2015).

Animal social network analysis are a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al 2009; Wey et al. 2008; Croft et al. 2008). Social network analyses provide insight into interspecific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al. 2014; Kurvers et al. 2014). Nevertheless, despite the power of traditional social network analysis, it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al. 2019).

Unlike traditional social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g. male or female), types of behaviours (e.g. grooming or mating), spatial areas (e.g. local or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al 2014; Porter 2018). Multilayer networks are relatively novel to describing animal behaviour studies (Finn et al. 2019; Silk et al. 2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and the complete neural network of an organism (Silk et al. 2018). The role of scale within a multilayer social network context remains unexplored, but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework. We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework seasonally variable social system case study of caribou (Rangifer tarandus) in Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two principal questions associated with scale-dependent multilayer networks. First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems? Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association. We conclude with perspectives for further development and application of scale in multilayer networks by discussing the problem and promise of scale from the perspective of social systems (Castles et al. 2014; Farine 2015) and landscape ecology (Schneider 2009).

## Scale in multilayer networks: a case study

### Caribou socioecology
Here, we use caribou (Rangifer tarandus) as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception). Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier et al. 2019) and spatial (Webber et al. unpublished data) variation in social networks. In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters once they are established. The average area of craters dug by caribou in Newfoundland was 0.41 m2 (SD = 0.48; Mayor et al. 2009) and crater density, which varies based on snow condition, depth, and local caribou density, can range from 366–1980 craters/ha (Bergerud 1974). There is therefore considerably less access to forage than when the landscape is snow-free. Importantly, craters exist on the landscape at multiple scales: the carter scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al. 2009). The distribution of craters on the landscape is therefore heterogeneous and access to vegetation in winter is highly variable among individual caribou.

### Caribou location data
We used GPS location data collected from Fogo Island caribou in winter 2018 (1 January – 16 March). Adult female caribou were immobilized and fitted with global positioning system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al. (2010). We did not collar all female caribou in the herd, however, we assumed that our sample of collared animals was random. Although associations between collared and uncollared animals were unrecorded, we assumed that our networks (see below) were unbiased representations of the relative degree of social association among all caribou.

### Landscape data and habitat classification

### Social network analysis
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social networks (PBSN) from GPS telemetry data. We generated social networks for each herd in each season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

We applied the ‘chain rule’, where each discrete spatiotemporal GPS fix was buffered by 50 m and we considered individuals in the same group if 50 m buffers for two or more individuals were contiguous, even if some individuals within the buffer were not within 50 m of one another. Group assignment based on the chain rule has commonly been applied to gregarious mammals, including caribou (Peignier et al. 2019; Lesmerises et al. 2018). We weighted edges of social networks by the strength of association between dyads of caribou using the simple ratio index (SRI, Cairns and Schwager 1987):

$$ SRI = \frac{x}{x + y_{AB} + y_{A} + y_{B}} $$

where x is the number of fixes where individuals A and B were within 50 m of each other, yA is the number of fixes from individual A when individual B did not have a simultaneous fix, yB is the number of fixes from individual B when individual A did not have a simultaneous fix, and yAB is the number of simultaneous fixes from individuals A and B that were separated by >50 m (Farine & Whitehead 2015). Social groups were designated if two or more individuals occurred within 50 m of one another at any given time point. We generated social networks with the igraph package in R, version 1.2.2 (Csárdi & Nepusz 2006). For each network, we calculated graph strength, defined as the sum of the edge weights for each individual in each network. We considered graph strength generated from PBSNs as an index of sociality (i.e., social strength).

## Scale in multilayer networks in practice: case study results

### 2019-12-16 scripts/explore-networkx.Rmd
fst multiNetX

@@
 import networkx as nx
+import multiNetX as ml
 
@@
 G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')
+
 ```

### 2019-12-17 scripts/explore-networkx.Rmd
separate graphs by lc

--- 2019-12-11 scripts/explore-networkx.Rmd
@@
 import networkx as nx
+import multinetx as ml
 
 edges = pd.read_csv('../data/edgels.csv')
-edges
-G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')
+
+print(edges['relc'].unique())
+
+G1 = nx.from_pandas_edgelist(edges[edges['relc'] == 1], 'V1', 'V2', edge_attr='w')
+G2 = nx.from_pandas_edgelist(edges[edges['relc'] == 2], 'V1', 'V2', edge_attr='w')
+G3 = nx.from_pandas_edgelist(edges[edges['relc'] == 3], 'V1', 'V2', edge_attr='w')
+
 ```

### 2020-01-09 paper/manuscript.Rmd
Small edits to MS

@@
 Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use.
-Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogenous landscapes.
-Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animals perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics.
-Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animals perception of scale.
+Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogeneous landscapes.
+Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics.
+Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animal’s perception of scale.
 We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
@@
 The effect of scale in ecology has been explored through species distributions (Elith et al 2009) habitat selection (Mayor et al 2007) and food webs (Sugihara et al 1989).
-Scale can be considered for all types of measured quantities9 including spatial and temporal variables, as well as behavioural variables including sociality.
+Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.
 
 Sociality exists across scales (Whitehead 2008).
-For example, grooming and mating relationships requires close proximity between conspecifics and occur over brief time periods (e.g.
+For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g.
 Carter et al.
@@
 2018).
-Shared space is a requirement for most types of social interactions, however, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al.
+Shared space is a requirement for most types of social interactions.
+However, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al.
 2014; Farine 2015).
@@
 
-Animal social network analysis are a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al 2009; Wey et al.
+Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al 2009; Wey et al.
 2008; Croft et al.
@@
 2018).
-The role of scale within a multilayer social network context remains unexplored, but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
+The role of scale within a multilayer social network context remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
+
 Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework.
-We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework seasonally variable social system case study of caribou (Rangifer tarandus) in Newfoundland, Canada (Peignier et al.
+We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework seasonally variable social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
 2019).
@@
 First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems?
-Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association.
+Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association?
 We conclude with perspectives for further development and application of scale in multilayer networks by discussing the problem and promise of scale from the perspective of social systems (Castles et al.
@@
 ### Caribou socioecology
-Here, we use caribou (Rangifer tarandus) as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception).
+Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception).
 Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al.
@@
 There is therefore considerably less access to forage than when the landscape is snow-free.
-Importantly, craters exist on the landscape at multiple scales: the carter scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al.
+Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al.
 2009).
@@
 (2010).
-We did not collar all female caribou in the herd, however, we assumed that our sample of collared animals was random.
+We did not collar all female caribou in the herd.
+However, we assumed that our sample of collared animals was random.
 Although associations between collared and uncollared animals were unrecorded, we assumed that our networks (see below) were unbiased representations of the relative degree of social association among all caribou.

### 2020-01-14 scripts/4-just-spatial.R
rm 4-just-spatial.R

@@ -1,160 +1,0 @@
-### Scale in multilayer networks - sensitivity of thresholds JUST SPATIAL
-# Alec Robitaille
-
-### Packages ----
-pkgs <- c('data.table',
-					'ggplot2',
-					'spatsoc',
-					'rgdal',
-					'asnipe',
-					'igraph')
-p <- lapply(pkgs, library, character.only = TRUE)
-
-
-### Data ----
-DT <- fread('input/FogoCaribou.csv')
-
-
-### Date and time columns ----
-DT[, c('idate', 'itime') := .(as.IDate(idate), as.ITime(itime))]
-
-## Seasons - Winter: 1-75, Summer: 215-290
-DT[between(JDate, 1, 75), season := 'winter']
-DT[between(JDate, 215, 290), season := 'summer']
-
-splitBy <- 'season'
-
-### Sub data ----
-idcol <- 'ANIMAL_ID'
-
-# dropid <- c('FO2016011', 'FO2017001', 'FO2017013', 'FO2016006')
-# & !(ANIMAL_ID %in% dropid)
-sub <- DT[Year == 2018  & !is.na(season)]
-
-keepids <- sub[, .N, .(ANIMAL_ID, season)][, .N, ANIMAL_ID][N == 2, ANIMAL_ID]
-sub <- sub[ANIMAL_ID %chin% keepids]
-
-### Project relocations ----
-# UTM zone 21N
-projCols <- c('EASTING', 'NORTHING')
-utm21N <- '+proj=utm +zone=21 ellps=WGS84'
-
-sub[, (projCols) := as.data.table(project(cbind(X_COORD, Y_COORD), utm21N))]
-
-### Spatiotemporal grouping with spatsoc ----
-# list spatial thresholds
-# spatThresholds <- seq(20, 2000, by = 20)
-spatThresholds <- seq(20, 200000, by = 200)
-
-thresholds <- data.table(spat = spatThresholds)
-
-lapply(seq_len(nrow(thresholds)), function(i) {
-	group_times(
-		sub,
-		datetime =  c('idate', 'itime'),
-		threshold = '10 minutes'
-	)
-	group_pts(
-		sub,
-		threshold = thresholds[i, spat],
-		id = idcol,
-		coords = projCols,
-		timegroup = 'timegroup',
-		splitBy = splitBy
-	)
-	setnames(sub, 'group',
[…]

### 2020-01-14 scripts/4-time-window.R
fst time window

@@ -1,0 +1,35 @@
+### Scale in multilayer networks - time window
+# Alec Robitaille
+
+### Packages ----
+pkgs <- c('data.table',
+					'ggplot2',
+					'spatsoc',
+					'rgdal',
+					'asnipe',
+					'igraph')
+p <- lapply(pkgs, library, character.only = TRUE)
+
+
+### Data ----
+DT <- fread('data/FogoCaribou.csv')
+
+### Sub data ----
+# TODO: add season? 
+sub <- DT[Year == 2018]
+
+idcol <- 'ANIMAL_ID'
+# keepids <- sub[, .N, c(idcol, 'season')][, .N, idcol][N == 2][[idcol]]
+# sub <- sub[get(idcol) %chin% keepids]
+
+### Cast columns ----
+sub[, idate := as.IDate(idate)]
+sub[, itime := as.ITime(itime)]
+
+### Project relocations ----
+# UTM zone 21N
+projCols <- c('EASTING', 'NORTHING')
+utm21N <- '+proj=utm +zone=21 ellps=WGS84'
+
+sub[, (projCols) := as.data.table(project(cbind(X_COORD, Y_COORD), utm21N))]
+

### 2020-01-14 scripts/1-data-prep.R
fst 1-data-prep.R

@@ -1,0 +1,44 @@
+### Scale in multilayer networks - data prep
+# Alec Robitaille
+
+### Packages ----
+pkgs <- c('data.table',
+					'ggplot2',
+					'spatsoc',
+					'multinet',
+					'rgdal',
+					'asnipe',
+					'raster',
+					'igraph',
+					'grainchanger')
+p <- lapply(pkgs, library, character.only = TRUE)
+
+### Data ----
+DT <- fread('data/FogoCaribou.csv')
+
+
+### Date and time columns ----
+DT[, c('idate', 'itime') := .(as.IDate(idate), as.ITime(itime))]
+
+## Seasons - Winter: 1-75, Summer: 215-290
+DT[between(JDate, 1, 75), season := 'winter']
+DT[between(JDate, 215, 290), season := 'summer']
+
+splitBy <- 'season'
+
+### Sub data ----
+sub <- DT[Year == 2018  & !is.na(season)]
+
+idcol <- 'ANIMAL_ID'
+keepids <- sub[, .N, c(idcol, 'season')][, .N, idcol][N == 2][[idcol]]
+sub <- sub[get(idcol) %chin% keepids]
+
+### Project relocations ----
+# UTM zone 21N
+projCols <- c('EASTING', 'NORTHING')
+utm21N <- '+proj=utm +zone=21 ellps=WGS84'
+
+sub[, (projCols) := as.data.table(project(cbind(X_COORD, Y_COORD), utm21N))]
+
+
+### Output ----

### 2020-01-14 scripts/1-single-scale.R

@@ -1,174 +1,0 @@
-### Scale in multilayer networks - landcover networks
-# Alec Robitaille
-
-### Packages ----
-pkgs <- c('data.table',
-					'ggplot2',
-					'spatsoc',
-					'multinet',
-					'rgdal',
-					'asnipe',
-					'raster',
-					'igraph',
-					'grainchanger')
-p <- lapply(pkgs, library, character.only = TRUE)
-
-### Data ----
-DT <- fread('data/FogoCaribou.csv')
-
-lc <- raster('data/Landcover/FogoSDSS_RS.tif')
-
-
-### Reclassify raster ----
-open <- c(1, 6, 7, 9)
-forest <- c(2, 3, 4, 5)
-lichen <- 8
-
-rcl <- matrix(c(
-	open,
-	forest,
-	lichen,
-	rep(1, length(open)),
-	rep(2, length(forest)),
-	rep(3, length(lichen))
-),
-ncol = 2)
-rclnms <- list(open = 1, forest = 2, lichen = 3)
-
-reclass <- reclassify(lc, rcl)
-
-### Sub data ----
-idcol <- 'ANIMAL_ID'
-
-dropid <- c('FO2016011', 'FO2017001', 'FO2017013', 'FO2016006')
-sub <- DT[Year == 2018 & JDate < 75][!(ANIMAL_ID %in% dropid)]
-sub[, c('idate', 'itime') := .(as.IDate(idate), as.ITime(itime))]
-
-
-### Project relocations ----
-# UTM zone 21N
-projCols <- c('EASTING', 'NORTHING')
-utm21N <- '+proj=utm +zone=21 ellps=WGS84'
-
-sub[, (projCols) := as.data.table(project(cbind(X_COORD, Y_COORD), utm21N))]
-
-### Sample landcover ----
-# landcover
-sub[, landcov := extract(lc,
-												 matrix(c(EASTING, NORTHING),
-												 			 ncol = 2))]
-
-sub[, relc := extract(reclass,
-												 matrix(c(EASTING, NORTHING),
-												 			 ncol = 2))]
-
-splitBy <- 'relc'
-
-
-### Spatiotemporal grouping with spatsoc ----
-group_times(
-	sub,
-	datetime =  c('idate', 'itime'),
-	threshold = '10 minutes'
-)
-
-group_pts(
-	sub,
-	threshold = 50,
-	id = idcol,
-	coords = projCols,
-	timegroup = 'timegroup',
[…]

### 2020-01-14 scripts/1-data-prep.R
data prep todos

@@ -17,6 +17,16 @@ p <- lapply(pkgs, library, character.only = TRUE)
 DT <- fread('data/FogoCaribou.csv')
 
 
+# TODO: add seasons
+# TODO: output to rds
+# TODO: read in as rds everywhere else
+# TODO: rm old prep from all
+# TODO: confirm seasons
+# TODO: dont drop if na season here
+# TODO: only 2018
+# TODO: which individuals are dropped
+
+
 ### Date and time columns ----
 DT[, c('idate', 'itime') := .(as.IDate(idate), as.ITime(itime))]
 

### 2020-01-21 R/metrics.R
filling roxygen doc

@@ -42,17 +42,45 @@ neigh <- function(DT, id, splitBy = NULL) {
 
 
 
-redundancy <- function(DT, id, var) {
+#' Connective Redundancy
+#'
+#' When connective redundancy is 0, all edges on all layers 
+#' are necessary to preserve the social ties
+#' 
+#' DT must be result of `neigh()` function, having columns "splitNeighborhood" 
+#' and "neighborhood"
+#' 
+#' @param DT 
+#' @param id 
+#' @param splitBy
+#'
+#' @return
+#' @export
+#'
+#' @examples
+redundancy <- function(DT, id, splitBy) {
   # Check cols
   DT[, connredund := 1 - (splitNeighborhood / neighborhood), 
-     by = nobs]
+     by = splitBy]
 }
 
 
 
-multidegree <- function(DT, degreeCol, id, var) {
-  DT[, multdeg := sum(splitNeighborhood - 1), 
-     by = c(idcol, 'nobs')]
+#' Multidegree
+#'
+#' @param DT 
+#' @param degreeCol 
+#' @param id 
+#' @param var 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+multidegree <- function(DT, degree, id, splitBy) {
+  DT[, multdeg := sum(.SD),
+     .SDcol = degree,
+     by = c(id, splitBy)]
 }
 
 relevance <- function(DT, id, var, splitBy) {

### 2020-01-21 paper/glossary.rmd
add glossary rmd

--- 2019-09-27 paper/table1.Rmd
@@
 
-<!--
-*network of networks is just an intraspecific network* *interspecific networks are networks of networks*
--->
-
-### Table 1
-Multilayer networks are composed of layers, nodes and edges.
-Layers represent different types of relationships (e.g.: grooming or association), types of entities (e.g.: male and female, or different species), and spatial locations (e.g.: landcover type, patch) [@pilosof2017].
-Nodes represent individual entities in the network, connected by some association or relationship with edges.
-Interlayer edges connect layers to other layers or individuals across layers.
-Intralayer edges connect individuals to other individuals within a layer.
-In Table 1, we describe three types of multilayer networks that incorporate spatial variables: spatially explicit networks, networks of networks and interspecific networks.
-Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and relevant considerations will be detailed here.
-
-<!-- 
-Relationships between individuals can be differentiated by their physical distance: communication or other high distance, grooming (physical contact), association (threshold distance)
-
-An animal's social network is multifaceted and complex, though this system is often examined
-
-The edges are often abstracted because they no longer in the sense that they represent a specific spatial and temporal context, which
-
-what about intralayer social grain -->
-
-```{r, echo = FALSE, warning = FALSE}
-library(data.table)
-
-tab1 <- fread('table1.csv')
-
-options(knitr.table.format = "markdown")
-
-knitr::kable(tab1)
-```
+## Glossary
 

### 2020-01-21 paper/manuscript.Rmd
update rmd
add perspective subheaders
Merge branch 'master' of https://gitlab.com/robit.a/scale-in-multilayer-networks.git
Conflicts:
	paper/manuscript.Rmd
	paper/manuscript.md
collective move

@@
 ## Scale in multilayer networks in practice: case study results
+
+## Perspectives  to advance multilayer networks
+
+### Landscape ecology
+
+### Individual fitness and phenotypes
+
+### Movement ecology and collective movement
+
+Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al.
+2015) and multilayer networks are no exception (Mourier et al.
+2019).
+Movement is a dynamic process and is related to an individual’s space use as well as the resources consumed within their home range (Van Moorter et al.
+2016).
+Collective movement can reduce group-level predation via detection-dilution trade-offs, while it can also improve information transfer about the quality or location of resources (Jolles et al.
+2019).
+Social processes, movement decisions, and space use are therefore inextricably linked.
+
+Although multilayer animal social networks are relatively novel (Silk et al.
+2018), integrating movement behaviour within multilayer networks has not yet been widely applied.
+In gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al.
+2019).
+In addition, *spatial networks* are networks of locations, which are connected in a network when individuals move between locations.
+For example, spatial networks were applied to monitor movement of sharks between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
+2019).
+While both studies integrate movement in some capacity, neither generate networks based on continuous measures of collective, or dyadic, movement (Long et al.
+2014).
+
+	Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make movement decisions in the context of their local environment (Strandburg-Peshkin et al.
+2015, 2017) and across scales.
+A collective movement layer could constitute similarity in movement for dyads (Long et al.
+2014) or groups (Bode et al.
+2011) as well as at a fine (i.e.
+minute-to-minute: Cleasby et al.
+2019) or coarse (global migration: Flack et al.
+2018) scales.
+Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al.
+2018).

### 2020-01-21 paper/manuscript.Rmd
update md
ms

@@
 Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association?
-We conclude with perspectives for further development and application of scale in multilayer networks by discussing the problem and promise of scale from the perspective of social systems (Castles et al.
-2014; Farine 2015) and landscape ecology (Schneider 2009).
+We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Ref), and movement ecology and collective movement (Jolles et al.
+2019).
 

### 2020-01-21 paper/manuscript.Rmd
update to ms

@@
 2018) scales.
+In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
 Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al.
 2018).
+
+Given the existing framework for constructing multilayer networks from behavioural layers (e.g.
+Smith-Aguilar et al.
+2019), movement layers could be integrated with interaction or association layers.
+Integrating movement layers with habitat-specific association layers could further shed light on the role of movement as a driver of the social and spatial environments an individual experiences (Webber and Vander Wal 2018).
+In our case study, we generated multilayer networks based on habitat-specific monolayers.
+Dyadic movement could XXX [not done here yet].
+The approach we outline could be used to explore mechanisms linking the social and spatial environments.
+For example, social processes may be an emergent property of the landscape because animals aggregate at resources, such as waterholes (Chamaillé-Jammes et al.
+2008).
+For example, XXXX.

### 2020-01-22 README.Rmd
fst Rmd README

--- 2019-09-10 paper/guidelines.Rmd
@@
 ---
-output: 
-  github_document:
-    toc: true
-author: Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
-date: "-- `r Sys.Date()`"
-bibliography: multilayer-networks.bib
+output: github_document
 ---
+
+<!-- README.md is generated from README.Rmd. Please edit that file -->
+
+```{r, include = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  fig.path = "man/figures/README-",
+  out.width = "100%"
+)
+```
+
+<!-- badges: start -->
+<!-- badges: end -->
+
+# The problem and promise of scale in multilayer networks
+Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
 
@@
 [General Instructions page](https://academic.oup.com/cz/pages/General_Instructions)
-
-#### From issue organisers
-
-* Appreciate ambition to link LE and SNA.
-* Like the idea of reviewing different kinds of spatial data relevant to ML framework
-* Hope simulations will be as relevant to movement and SNA data typically collected
-* Manuscript will be relevant to both theoreticians and empiricists
-
-## Keywords
-
-1. spatial scale
-1. social systems
-1. multilayer networks
-1. landscape ecology
-1. network theory
-
-## Boxes / paper layout
-
-* Abstract
-* Intro
-* Box 1: Mathematical + language definitions of multilayer networks
-* Box 2: Types of spatiotemporally explicit data and considerations relevant to these e.g. fix rate/grouping with GPS and gambit of the group, etc (table)
-* Spatial variables - example of GPS data, sampling landcover and networks across landcover classes?
-* Temporal variables - example of GoG data, chunked seasonally maybe?
-* Relevant multilayer metrics with above two? 
-* Conclusion/fin
-
-# References

### 2020-01-22 scripts/2-landcover-scale.R
fst grep TODOs

@@ -21,6 +21,7 @@ lc <- raster('data/Landcover/FogoSDSS_RS.tif')
 water <- readOGR('data/Landcover/FogoPoly.shp')
 
 ### Sub data ----
+# TODO: move this prep
 # TODO: add season? 
 sub <- DT[Year == 2018]
 

### 2020-01-22 scripts/0-variables.R
fst 0-variables.R

@@ -1,0 +1,1 @@
+idcol <- 'ANIMAL_ID'

### 2020-01-22 scripts/1-data-prep.R
split data to raw/derived

@@ -14,16 +14,13 @@ pkgs <- c('data.table',
 p <- lapply(pkgs, library, character.only = TRUE)
 
 ### Data ----
-DT <- fread('data/FogoCaribou.csv')
+DT <- fread('data/raw-data/FogoCaribou.csv')
 
-
-# TODO: add seasons
-# TODO: output to rds
+idcol <- 'ANIMAL_ID'
 # TODO: read in as rds everywhere else
 # TODO: rm old prep from all
 # TODO: confirm seasons
 # TODO: dont drop if na season here
-# TODO: only 2018
 # TODO: which individuals are dropped
 
 
@@ -41,7 +38,7 @@ sub <- DT[Year == 2018  & !is.na(season)]
 
 idcol <- 'ANIMAL_ID'
 keepids <- sub[, .N, c(idcol, 'season')][, .N, idcol][N == 2][[idcol]]
-sub <- sub[get(idcol) %chin% keepids]
+# sub <- sub[get(idcol) %chin% keepids]
 
 ### Project relocations ----
 # UTM zone 21N
@@ -52,3 +49,4 @@ sub[, (projCols) := as.data.table(project(cbind(X_COORD, Y_COORD), utm21N))]
 
 
 ### Output ----
+saveRDS('data/derived-data/prep-fogo-caribou.Rds')

### 2020-01-22 scripts/2-landcover-scale.R

@@ -30,6 +30,7 @@ idcol <- 'ANIMAL_ID'
 # sub <- sub[get(idcol) %chin% keepids]
 
 ### Cast columns ----
+# TODO: move this prep
 sub[, idate := as.IDate(idate)]
 sub[, itime := as.ITime(itime)]
 

### 2020-01-22 paper/manuscript.Rmd
update ms

--- 2020-01-21 paper/manuscript.Rmd
@@
 author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
-output: github_document
+output: 
+    word_document
+    #github_document
 ---
@@
 2018) scales.
+Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including moving, interacting, or foraging (e.g.
+Muller et al.
+2018; Finn et al.
+2019) and construct a multilayer networks based on behaviour-specific monolayer networks (e.g.
+Smith-Aguilar et al.
+2019) In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
 Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al.
 2018).
+
+Given the existing framework for constructing multilayer networks from behavioural layers (e.g.
+Smith-Aguilar et al.
+2019), movement layers could be integrated with interaction or association layers.
+Integrating movement layers with habitat-specific social association layers could further shed light on the role of movement as a driver of the social and spatial environments an individual experiences (Webber and Vander Wal 2018).
+In our case study, we generated multilayer networks based on habitat-specific monolayers.
+Coordinated movement of dyads, or groups, could vary based on habitat and the approach we outline could be used to explore mechanisms linking the social and spatial environments.
+For example, social processes may be an emergent property of the landscape because animals aggregate at resources, such as waterholes (Chamaillé-Jammes et al.
+2008), while movement to, from, or within habitat patches can also contribute to the formation of the social environment (Spiegel et al.
+2016).
+Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.
+In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insight into the

### 2020-01-22 paper/manuscript.Rmd
format

@@
 ## Introduction
-Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al 2015).
-Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al 2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013).
-The effect of scale in ecology has been explored through species distributions (Elith et al 2009) habitat selection (Mayor et al 2007) and food webs (Sugihara et al 1989).
+Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al.
+2015).
+Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al.
+2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013).
+The effect of scale in ecology has been explored through species distributions (Elith et al.
+2009) habitat selection (Mayor et al.
+2007) and food webs (Sugihara et al.
+1989).
 Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.
@@
 
-Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al 2009; Wey et al.
+Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al.
+2009; Wey et al.
 2008; Croft et al.
@@
 local or regional), or temporal windows (e.g.
-daily or seasonal) (Kivela et al 2014; Porter 2018).
+daily or seasonal) (Kivela et al.
+2014; Porter 2018).
 Multilayer networks are relatively novel to describing animal behaviour studies (Finn et al.

### 2020-01-22 paper/manuscript.Rmd
edit P1 intro

@@
 2015).
-Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al.
-2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013).
-The effect of scale in ecology has been explored through species distributions (Elith et al.
-2009) habitat selection (Mayor et al.
-2007) and food webs (Sugihara et al.
+Animals and landscapes are influenced across scales processes as global as climate and productivity (Field et al.
+2009), and species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013).
+The effect of scale in ecology has been explored through species distribution modelling (Elith et al.
+2009), habitat selection (Mayor et al.
+2007), and food webs (Sugihara et al.
 1989).
-Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.
+Scale can be considered throughout ecology, including animal behaviour and the social environment that animals experience.
 

### 2020-01-22 paper/glossary.rmd
Update glossary.rmd
update to glossary
define social scale

@@
 
+**Interlayer edge**:
+
+**Intralayer edge**:
+
+**Monolayer**:
+
+**Social environment**: Social life of an individual (or group of individuals) described by social interactions (Saltz et al. 2016).
+
+**Social scale**: The type of social relationship observed that can be explicitly defined and measured in social network analyses (Farine 2015).
+For example, social interactions where animals come in direct contact (e.g.
+grooming) constitute the finest social scale, while co-occurrence or social association constitute an intermediate social scale, and home range overlap constitutes a coarse social scale.
+
+**Spatial network**: Networks of locations, which be linked with social networks of animals that move between the locations (Silk et al. 2018.
+
 # References

### 2020-01-22 paper/manuscript.Rmd
edit P2 intro

@@
 2010).
-Further, home range overlap among individuals is a coarse scale of sociality, where individuals share space over larger spatial and temporal scales (e.g.
+Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges.
+In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g.
 Piza-Roca et al.
 2018).
-Shared space is a requirement for most types of social interactions.
-However, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al.
+Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al.
 2014; Farine 2015).
-Social scale can be defined as the type of relationship observed (Farine 2015) and these relationships can be explicitly defined and measured in social network analyses (Farine et al.
+Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (Farine et al.
 2015).

### 2020-01-22 paper/manuscript.Rmd
edit P3 intro

@@
 2008).
-Social network analyses provide insight into interspecific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al.
+Social network analysis provides insight into intra-specific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al.
 2014; Kurvers et al.
 2014).
-Nevertheless, despite the power of traditional social network analysis, it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al.
+Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al.
 2019).

### 2020-01-22 paper/manuscript.Rmd
edit P4 intro

@@
 male or female), types of behaviours (e.g.
-grooming or mating), spatial areas (e.g.
+grooming, travelling, or foraging), spatial areas (e.g.
 local or regional), or temporal windows (e.g.
@@
 2014; Porter 2018).
-Multilayer networks are relatively novel to describing animal behaviour studies (Finn et al.
+Multilayer networks are relatively novel to studies of animal behaviour (Finn et al.
 2019; Silk et al.
-2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and the complete neural network of an organism (Silk et al.
+2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and organismal neural networks (Silk et al.
 2018).
-The role of scale within a multilayer social network context remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
+The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
 

### 2020-01-22 paper/manuscript.Rmd
edit P5 intro

@@
 Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework.
-We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework seasonally variable social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
+We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
 2019).

### 2020-01-22 paper/manuscript.Rmd
edit P1 methods

@@
 In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974).
-As a result, caribou tend to occupy and re-use craters once they are established.
-The average area of craters dug by caribou in Newfoundland was 0.41 m2 (SD = 0.48; Mayor et al.
-2009) and crater density, which varies based on snow condition, depth, and local caribou density, can range from 366–1980 craters/ha (Bergerud 1974).
-There is therefore considerably less access to forage than when the landscape is snow-free.
+As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free.
 Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al.
 2009).
-The distribution of craters on the landscape is therefore heterogeneous and access to vegetation in winter is highly variable among individual caribou.
+The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
 

### 2020-01-22 paper/manuscript.Rmd
ms edits

@@
 Although multilayer animal social networks are relatively novel (Silk et al.
-2018), integrating movement behaviour within multilayer networks has not yet been widely applied.
+2018), movement behaviour within multilayer networks has already been considered in a handful of studies.
 In gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al.
@@
 In addition, *spatial networks* are networks of locations, which are connected in a network when individuals move between locations.
-For example, spatial networks were applied to monitor movement of sharks between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
+For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
 2019).
@@
 Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.
-In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insight into the
+In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insight into the effects of habitat configuration on the formation of the social environment (He et al.
+2019).

### 2020-01-22 paper/manuscript.Rmd
knit rmd
quick describe landcover scale

@@
 output: 
-    word_document
-    #github_document
+    #word_document
+    github_document
 ---
@@
 
+### Variables/sensitivity
+
+1. landcover scale
+
+Sample same landcover product at different scales.
+Landcover is the Fogo landcover product.
+Resampled using `grainchanger` from regular resolution (believe it's 30m), to 100m, 250m, 500m, 1000m, 2500m (tentative numbers).
+Resampling method was modal moving window.
+Water areas were masked before resampling.
+Landcover reclassified to open, forest and lichen.
+
+```
+open <- c(1, 6, 7, 9)
+forest <- c(2, 3, 4, 5)
+lichen <- 8
+```
+
+1. spatial threshold
+1. number of observations
+1. time window length
+1. time window position
+
+### Metrics
+
 ## Scale in multilayer networks in practice: case study results

### 2020-01-22 paper/manuscript.Rmd
quick describe spatial buffer
quick describe default thresholds
quick describe metrics

@@
 
+Unless otherwise mentioned, the spatial threshold is 50 and the temporal threshold is 5 minutes.
+
 1. landcover scale
@@
 
+Each modal landcover, and the original are sampled and separate network layers constructed for each.
+
 1. spatial threshold
+
+Social networks constructed using spatsoc. Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.
+
 1. number of observations
+
+Randomly select max number of observations - timegroups -  (right now 750).
+For each iteration, include n observations for each season for all individuals.
+Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
+Parallels with observation data.
+
 1. time window length
+
+Varying length of time window (used to define seasons).
+From 75 to 150 right now.
+Fixed start julian day for winter is day 1 and for summer is 215.
+Network layers for winter and summer are calculated for each window length.
+
 1. time window position
+Varying position of time window (used to define seasons).
+Fixed length at 75.
+Window positions starting at 1, to + 75.
+So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
+Same for summer, starting at 215.
+Network layers for each season are constructed.
 
 ### Metrics
+
+Right now, we calculate mostly degree/neighborhood based metrics.
+
+* Degree centrality
+* Multidegree
+* Degree deviation: standard deviation of degree across layers
+
+* Neighbors/neighborhood (number of unique actors directly connected to each focal)
+
+Neighbors = degree within a network layer
+But across a multilayer network with multiple layers, some neighbors are repeated.
+
+So the difference between neighbors and degree is the basis for
+
+* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties
+
+* Relevance: neighborhood of specific layer  / neighbourhood of full ml net.
+This is the proportion of neighbors present on the layer of focus.
+Comparing across, it tells you which layers are most important for each individual.
+
+Then there will be some layer similarity. Right now it's just a correlation of each season's asnipe SRI matrix
+
+Finally, some weighted variable.
 

### 2020-01-22 paper/manuscript.Rmd
add lc details

@@
 ### Landscape data and habitat classification
+Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division.
+Available landcover classification included nine habitat types, which we distilled into two broad categories: open and closed habitat types.
+Open habitat consisted of lichen, wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
 

### 2020-01-22 paper/manuscript.Rmd
tweak methods

@@
 The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
+We therefore partitioned data into two discrete seasons: summer (DATES) and winter (DATES) based on caribou socioecology (Peignier et al.
+2019).
 
@@
 (2010).
-We did not collar all female caribou in the herd.
-However, we assumed that our sample of collared animals was random.
-Although associations between collared and uncollared animals were unrecorded, we assumed that our networks (see below) were unbiased representations of the relative degree of social association among all caribou.
+We did not collar all female caribou in the herd; however, we assumed that our sample of collared animals was random.
 
@@
 
-### Social network analysis
+### Generating multilayer social networks
 We used R package spatsoc (Robitaille et al.
-2019) in *R version* (R CITATION) to generate proximity-based social networks (PBSN) from GPS telemetry data.
-We generated social networks for each herd in each season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
+2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above).
+We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
 2018).
@@
 
-### Variables/sensitivity
+Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer)
 
-Unless otherwise mentioned, the spatial threshold is 50 and the temporal threshold is 5 minutes.
+#### Generating multilayer social networks
 

### 2020-01-22 paper/manuscript.Rmd
describe habitat types

@@
 Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division.
-Available landcover classification included nine habitat types, which we distilled into two broad categories: open and closed habitat types.
-Open habitat consisted of lichen, wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
+Available landcover classification included nine habitat types at 30x30m resolution.
+We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat.
+Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
 
@@
 
-Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer)
+Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer).
 
-#### Generating multilayer social networks
-
-1. landcover scale
+#### Landcover scale
 

### 2020-01-22 paper/manuscript.Rmd
scale methods

@@
 Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division.
-Available landcover classification included nine habitat types at 30x30m resolution.
+Available landcover classification included nine habitat types at 30 x 30m resolution.
 We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat.
@@
 
-#### Landcover scale
+#### Altering landcover scale
 
-Sample same landcover product at different scales.
-Landcover is the Fogo landcover product.
-Resampled using `grainchanger` from regular resolution (believe it's 30m), to 100m, 250m, 500m, 1000m, 2500m (tentative numbers).
-Resampling method was modal moving window.
+To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
+Specifically, we selected scales relevant to caribou ecology.
+We re-sampled landcover using the **`grainchanger` package[???]** at five scales: 100m, 250m, 500m, 1000m, 2500m.
+Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
+2017).
+represents the local foraging Resampling method was modal moving window.
 Water areas were masked before resampling.

### 2020-01-22 paper/manuscript.Rmd
Update manuscript.Rmd

@@
 We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat.
-Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
+Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
+Water habitat was excluded from all subsequent analyses.
 
+```
+open <- c(1, 6, 7, 9)
+forest <- c(2, 3, 4, 5)
+lichen <- 8
+```
 ### Generating multilayer social networks
@@
 Specifically, we selected scales relevant to caribou ecology.
-We re-sampled landcover using the **`grainchanger` package[???]** at five scales: 100m, 250m, 500m, 1000m, 2500m.
+We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m.
 Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
 2017).
-represents the local foraging Resampling method was modal moving window.
-Water areas were masked before resampling.
-Landcover reclassified to open, forest and lichen.
+Resampling occurred based on a modal moving window method, where XXXXX.
 
-```
-open <- c(1, 6, 7, 9)
-forest <- c(2, 3, 4, 5)
-lichen <- 8
-```
+**Each modal landcover, and the original are sampled and separate network layers constructed for each. [QW: NOT SURE WHAT THIS MEANS]**
 
-Each modal landcover, and the original are sampled and separate network layers constructed for each.
+#### Altering social scale
 
-1. spatial threshold
+Social networks constructed using spatsoc (Robitaille et al. 2019). Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.
 
-Social networks constructed using spatsoc. Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.
-
-1. number of observations
+#### Altering the number of observations
 

### 2020-01-23 paper/manuscript.Rmd
update network methods

@@
 ```
-### Generating multilayer social networks
-We used R package spatsoc (Robitaille et al.
-2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above).
+### Caribou multilayer social networks
+
+#### Network types and construction (defining layers for the multilayer network)
+
+We generated seasonal multilayer social networks consisting of habitat-specific monolayers.
+Each layer was the social association network generated in one of three habitat types (lichen, open, and closed).
+Briefly, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al.
+2019) in *R version* (R CITATION).
+
 We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
@@
 
-Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer).
-
 #### Altering landcover scale
@@
 
-Social networks constructed using spatsoc (Robitaille et al. 2019). Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.
+As above, we generated social association networks in three habitat types and two seasons.
+We generated separate multilayer networks consisting of  for each season.
+Variable modified is the spatial buffer.
+Series from 5 to 500.
 

### 2020-01-23 paper/manuscript.Rmd
methods

@@
 As above, we generated social association networks in three habitat types and two seasons.
-We generated separate multilayer networks consisting of  for each season.
-Variable modified is the spatial buffer.
-Series from 5 to 500.
+For our baseline networks, we assumed individuals were in the same group if they were within a 50m spatial buffer of one another (see above).
+Based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?), we modified the spatial buffer and re-assigned groups at incremental distance between 5 and 500.
+Thus, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
+Modifying social scale enabled us to assess the
 
@@
 
+Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al.
+2018; Webber and Vander Wal 2019).
 Randomly select max number of observations - timegroups -  (right now 750).

### 2020-01-23 paper/glossary.rmd
add terms to gloss
Update glossary.rmd

@@
 
+**Connective redundancy**: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties.[QW: FROM ALEC'S WRITING IN THE MS]
+
+**Degree centrality**:
+
+**Degree deviation**:
+
 **Interlayer edge**:
@@
 **Monolayer**:
+
+**Multidegree**:
+
+**Neighbours**: degree within a network layer.[QW: FROM ALEC'S WRITING IN THE MS]
+
+**Relevance**: neighborhood of specific layer  / neighbourhood of full ml net.
+This is the proportion of neighbors present on the layer of focus.
+Comparing across, it tells you which layers are most important for each individual.
+[QW: FROM ALEC'S WRITING IN THE MS]
 

### 2020-01-23 paper/manuscript.Rmd
methods
Update manuscript.Rmd

@@
 
-#### Altering landcover scale
+#### Altering spatial scale
 
@@
 Resampling occurred based on a modal moving window method, where XXXXX.
+[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]
 
@@
 
-### Metrics
+### Network metrics
 
+We used Muxviz blah blag whatever to generate XX number of multilayer network metrics.
+These include four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions).
+GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE)
+
+We generated all networks 
 Right now, we calculate mostly degree/neighborhood based metrics. 
-
 * Degree centrality

### 2020-01-23 paper/manuscript.Rmd
updates to ms

@@
 The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
-We therefore partitioned data into two discrete seasons: summer (DATES) and winter (DATES) based on caribou socioecology (Peignier et al.
+We therefore partitioned data into two discrete seasons: summer (DATES) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al.
 2019).
@@
 ### Caribou location data
-We used GPS location data collected from Fogo Island caribou in winter 2018 (1 January – 16 March).
+We used GPS location data collected from Fogo Island caribou in 2018.
 Adult female caribou were immobilized and fitted with global positioning system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g) as described by Schaefer and Mahoney (2013).
@@
 
-```
-open <- c(1, 6, 7, 9)
-forest <- c(2, 3, 4, 5)
-lichen <- 8
-```
 ### Caribou multilayer social networks
@@
 
-We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
+We generated monolayer association networks for caribou for each habitat-by-season combination based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
 2018).
-We represented individuals in our networks by nodes and associations between individuals were represented by edges.
+In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.
 
@@
 
-where x is the number of fixes where individuals A and B were within 50 m of each other, yA is the number of fixes from individual A when individual B did not have a simultaneous fix, yB is the number of fixes from individual B when individual A did not have a simultaneous fix, and yAB is the number of simultaneous fixes from individuals A and B that were separated by >50 m (Farine & Whitehead 2015).
+where x is the number of fixes where individuals A and B were within 50 m of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by >50 m (Farine & Whitehead 2015).
 Social groups were designated if two or more individuals occurred within 50 m of one another at any given time point.
 We generated social networks with the igraph package in R, version 1.2.2 (Csárdi & Nepusz 2006).
-For each network, we calculated graph strength, defined as the sum of the edge weights for each individual in each network.
-We considered graph strength generated from PBSNs as an index of sociality (i.e., social strength).
+For each multilayer network, we calculated XXX metrics (see below).
 

### 2020-01-23 paper/manuscript.Rmd
Update manuscript.Rmd

@@
 Each layer was the social association network generated in one of three habitat types (lichen, open, and closed).
-Briefly, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al.
+For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al.
 2019) in *R version* (R CITATION).
 
-We generated monolayer association networks for caribou for each habitat-by-season combination based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al.
+Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another.
+Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment.
+For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al.
+2019).
+Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al.
+2019; Lesmerises et al.
 2018).
+To assess the role of social scale in multilayer networks, we varied the threshold distance for group assignment between 5-500m (see *Social scale* section below).
 In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.
 
-We applied the ‘chain rule’, where each discrete spatiotemporal GPS fix was buffered by 50 m and we considered individuals in the same group if 50 m buffers for two or more individuals were contiguous, even if some individuals within the buffer were not within 50 m of one another.
-Group assignment based on the chain rule has commonly been applied to gregarious mammals, including caribou (Peignier et al.
-2019; Lesmerises et al.
-2018).
-We weighted edges of social networks by the strength of association between dyads of caribou using the simple ratio index (SRI, Cairns and Schwager 1987):
+We weighted edges of social networks by the strength of association between caribou using the simple ratio index (SRI, Cairns and Schwager 1987):
 
@@
 
-where x is the number of fixes where individuals A and B were within 50 m of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by >50 m (Farine & Whitehead 2015).
-Social groups were designated if two or more individuals occurred within 50 m of one another at any given time point.
-We generated social networks with the igraph package in R, version 1.2.2 (Csárdi & Nepusz 2006).
+where x is the number of fixes where individuals A and B were within a given distance of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by more than the given distance (Farine & Whitehead 2015).
+Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point.
 For each multilayer network, we calculated XXX metrics (see below).
@@
 
-As above, we generated social association networks in three habitat types and two seasons.
-For our baseline networks, we assumed individuals were in the same group if they were within a 50m spatial buffer of one another (see above).
-Based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?), we modified the spatial buffer and re-assigned groups at incremental distance between 5 and 500.
-Thus, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
-Modifying social scale enabled us to assess the
+We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
+Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
+For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
 
@@
 
-Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al.
-2018; Webber and Vander Wal 2019).
+Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).
+
 Randomly select max number of observations - timegroups -  (right now 750).

### 2020-01-23 paper/manuscript.Rmd
network metrics

@@
 Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point.
-For each multilayer network, we calculated XXX metrics (see below).
 
-#### Altering spatial scale
-
-To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
-Specifically, we selected scales relevant to caribou ecology.
-We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m.
-Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
-2017).
-Resampling occurred based on a modal moving window method, where XXXXX.
-[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]
-
-**Each modal landcover, and the original are sampled and separate network layers constructed for each. [QW: NOT SURE WHAT THIS MEANS]**
-
-#### Altering social scale
-
-We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
-Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
-For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
-
-#### Altering the number of observations
-
-Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).
-
-Randomly select max number of observations - timegroups -  (right now 750).
-For each iteration, include n observations for each season for all individuals.
-Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
-Parallels with observation data.
-
-1. time window length
-
-Varying length of time window (used to define seasons).
-From 75 to 150 right now.
-Fixed start julian day for winter is day 1 and for summer is 215.
-Network layers for winter and summer are calculated for each window length.
-
-1. time window position
-Varying position of time window (used to define seasons).
-Fixed length at 75.
-Window positions starting at 1, to + 75.
-So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
-Same for summer, starting at 215.
-Network layers for each season are constructed.
-
-### Network metrics
-
-We used Muxviz blah blag whatever to generate XX number of multilayer network metrics.
-These include four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions).
-GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE)
+For each multilayer network, we calculated XXX metrics.These included four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions).
+GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).
 
@@
 Finally, some weighted variable.
+
+### Scale in multilayer networks
+
+#### Temporal scale
+
+#### Spatial scale
+
+To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
+Specifically, we selected scales relevant to caribou ecology.
+We re-sampled landcover using the `grainchanger` **package/function[???]** (REF) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
+Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
+2017).
+Resampling occurred based on a modal moving window method, where **XXXXX.
+[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
+
+Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]**
+
+#### Altering social scale
+
+We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
+Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
+For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
+
+#### Altering observational scale
+
+Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).
+
+Randomly select max number of observations - timegroups -  (right now 750).
+For each iteration, include n observations for each season for all individuals.
+Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
+Parallels with observation data.
+
+1. time window length
+
+Varying length of time window (used to define seasons).
+From 75 to 150 right now.
+Fixed start julian day for winter is day 1 and for summer is 215.
+Network layers for winter and summer are calculated for each window length.
+
+1. time window position
+Varying position of time window (used to define seasons).
+Fixed length at 75.
+Window positions starting at 1, to + 75.
+So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
+Same for summer, starting at 215.
+Network layers for each season are constructed.
 

### 2020-01-23 paper/manuscript.Rmd
Update manuscript.Rmd

@@
 The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
-We therefore partitioned data into two discrete seasons: summer (DATES) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al.
+We therefore partitioned data into two discrete seasons: summer (3 August - 17 October) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al.
 2019).
@@
 
+We altered the temporal scale of mutlilayer networks using a moving time-window approach to define seasons.
+
+1. time window length
+
+Varying length of time window (used to define seasons).
+From 75 to 150 right now.
+Fixed start julian day for winter is day 1 and for summer is 215.
+Network layers for winter and summer are calculated for each window length.
+
+1. time window position
+Varying position of time window (used to define seasons).
+Fixed length at 75.
+Window positions starting at 1, to + 75.
+So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
+Same for summer, starting at 215.
+Network layers for each season are constructed.
+
 #### Spatial scale
 
-To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
+To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
 Specifically, we selected scales relevant to caribou ecology.
@@
 Parallels with observation data.
-
-1. time window length
-
-Varying length of time window (used to define seasons).
-From 75 to 150 right now.
-Fixed start julian day for winter is day 1 and for summer is 215.
-Network layers for winter and summer are calculated for each window length.
-
-1. time window position
-Varying position of time window (used to define seasons).
-Fixed length at 75.
-Window positions starting at 1, to + 75.
-So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
-Same for summer, starting at 215.
-Network layers for each season are constructed.
 

### 2020-01-23 paper/manuscript.Rmd
clarify original+modal lc

@@
 
-Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]**
+For each landcover (the original resolution and modal resampled resolutions), seasonal network layers are combined in a multilayer network
+<!-- Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
 

### 2020-01-23 paper/manuscript.Rmd
add grainchanger ref
affiliations

@@
 title: The problem and promise of scale in multilayer networks
-author: Alec L. Robitaille, Quinn M.R. Webber, Julie W. Turner, Eric Vander Wal
+author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
+header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
+
 output: 
@@
 Specifically, we selected scales relevant to caribou ecology.
-We re-sampled landcover using the `grainchanger` **package/function[???]** (REF) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
+We re-sampled landcover using the `grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
 Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.

### 2020-01-23 paper/manuscript.Rmd
add ref for some metrics
add ref for ml eig centrality

@@
 Right now, we calculate mostly degree/neighborhood based metrics.
+
+Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."
+
 * Degree centrality
@@
 
-Finally, some weighted variable.
+Finally, some weighted variables:
+
+* eigenvector centrality, summed across layers as described in Boccaletti, Stefano, et al. "The structure and dynamics of multilayer networks." Physics Reports 544.1 (2014): 1-122.
 

### 2020-01-23 scripts/4-time-window-length.R
bring back igraph, asnipe, gbiLs for eig cent

@@ -62,34 +62,40 @@ nets <- lapply(winlengths[1:2], function(len) {
     splitBy = col
   )
   
-  # usplit <- unique(na.omit(DT, cols = col)[[col]])
-  # 
-  # # GBI for each season
-  # gbiLs <- lapply(usplit, function(u) {
-  #   gbi <- get_gbi(
-  #     DT = DT[get(col) == u],
-  #     group = 'group',
-  #     id = idcol
-  #   )
-  # })
-  # 
-  # # Generate networks for each season
-  # netLs <- lapply(
-  #   gbiLs,
-  #   get_network,
-  #   data_format = 'GBI',
-  #   association_index = 'SRI'
-  # )
-  # 
-  # gLs <- lapply(
-  #   netLs,
-  #   graph.adjacency,
-  #   mode = 'undirected',
-  #   diag = FALSE,
-  #   weighted = TRUE
-  # )
-  # names(gLs) <- paste0(col, '-', usplit)
-  # gLs
+  usplit <- unique(na.omit(sub, cols = col)[[col]])
+
+  # GBI for each season
+  gbiLs <- lapply(usplit, function(u) {
+    gbi <- get_gbi(
+      DT = sub[get(col) == u],
+      group = 'group',
+      id = idcol
+    )
+  })
+
+  # Generate networks for each season
+  netLs <- lapply(
+    gbiLs,
+    get_network,
+    data_format = 'GBI',
+    association_index = 'SRI'
+  )
+
+  gLs <- lapply(
+    netLs,
+    graph.adjacency,
+    mode = 'undirected',
+    diag = FALSE,
+    weighted = TRUE
+  )
+  names(gLs) <- paste0(col, '-', usplit)
+
+  eig <- rbindlist(
+    lapply(lapply(gLs, function(g) eigen_centrality(g)$vector), stack),
+    idcol = 'lenseason')
+  eig[, c('winlength', 'season') := tstrsplit(lenseason, '-')]
+  eig[, winlength := as.integer(gsub('season', '', winlength))]
+  setnames(eig, c('ind', 'values'), c(idcol, 'eigcent'))
   
   neigh(sub, idcol, col)
   
@@ -97,6 +103,8 @@ nets <- lapply(winlengths[1:2], function(len) {
   out <- unique(sub[, .SD, .SDcols = outcols])
   setnames(out, col, 'season')
   set(out, j = 'winlength', value = len)
+  
+  out[eig, on = c(idcol, 'season', 'winlength')]
 })
[…]

### 2020-01-23 scripts/4-time-window-length.R
TODOs for simplifying metric calculations

@@ -97,6 +97,10 @@ nets <- lapply(winlengths[1:2], function(len) {
   eig[, winlength := as.integer(gsub('season', '', winlength))]
   setnames(eig, c('ind', 'values'), c(idcol, 'eigcent'))
   
+  # TODO: modify neigh so it's working on a by
+  # TODO: remove it from this lapply and merge afterwards
+  # TODO: just return eig centrality and network correlation etc
+  # TODO: then merge onto neigh output from above
   neigh(sub, idcol, col)
   
   outcols <- c('neighborhood', 'splitNeighborhood', idcol, col)

### 2020-01-23 paper/manuscript.Rmd
add perspective

@@
 
+Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype, and they are increasingly linked to important fitness outcomes for individuals among species ranging from primates (e.g.
+Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019) to dolphins (e.g.
+Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011) to birds (e.g.
+McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012).
+But there are many ways that scale comes into play in determining how characteristics of an individual’s social network position are related to fitness that depend on the hypotheses being tested and logistical constraints.
+The two scales that repeatedly come across as important for understanding fitness consequences are temporal and social scale (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
+
+Social network structures depend on the time frame used to create them, which can make different networks difficult to compare (Castles et al., 2014).
+Furthermore, social network structures can vary by season and indicate social environments that an individual experiences (e.g.
+Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018).
+Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).
+
+Additionally, in long-lived species especially, social network metrics of individuals can change over their lifetimes in ways that can have impacts on their reproductive success and longevity (Berger et al., 2015; Brent et al., 2017).
+These findings highlight the necessity to think carefully about the temporal scale that is meaningful for the proposed hypotheses, especially for understanding individual social phenotypes or environments and how they relate to that individual’s fitness.
+Further complicating the issue, social network metrics can change over stages of ontogeny, but individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018).
+This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social network position over different stages of ontogeny even more difficult.
+However, thinking about temporal scales at such a fine level can provide insights for important stages of development that may have otherwise been missed (CITE-myself??).
+However, multilayer networks provide a framework to test hypotheses about how social dynamics over time relate to fitness.
+Because of the non-independent nature of social interactions, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017).
+Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.
+
+Social scale is another major consideration for social network analysis, especially when thinking about different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
+It is a common trope that individuals need to be associating in order to interact and an assumption that proximity is proxy for interacting (Farine, 2015).
+For instance, baboons need to be in proximity in order to groom each other, but this trope is only thinking about interactions that humans are most prone to seeing and valuing with our bias toward visual perception.
+Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015).
+With improved and more affordable technology, we can now start to understand some of these interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
+The multilayer network framework further enables researchers to look at these different social scales and test how good a proxy proximity is for various forms of interacting in a holistic way.
+
+These different social scales can have different fitness repercussions for individuals.
+Rhesus macaques (*Macaca mulatta*) that had stronger, more stable associates and grooming partners but not more partners in general had greater survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019).
+This finding highlights the need to look at social network positions at both multiple temporal and social scales to understand the social positions and fitness repercussions of individuals, and multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.
+
+Multilayer networks further provide unique challenges and opportunities for understanding the social phenotypes and environments of individuals and their fitness outcomes.
+Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should be made for the same time period, and the period needs to be long enough for each layer to have enough data for robust networks (Farine, 2017).
+These considerations may be limiting factors when answering questions that require timeframes that are relevant to different individuals.
+On the other hand, multilayer network metrics provide an opportunity to help simplify statistical models.
+Interactions that happen mere meters apart, proximity associations, and long-distance interactions can be encapsulated in one network to gain a single metric to describe the various social scales of an individual’s network position.
+This multilevel network metric would be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).
+This method could be an alternative to using PCA to simplify many social network metrics into one social phenotype (e.g.
+Foster et al., 2012; Oldham et al., 2019).
+Future analyses should explore the differences in how well each of these methods describe and predict fitness outcomes of the complex social network positions of individuals.
+
 ### Movement ecology and collective movement

### 2020-01-23 paper/manuscript.Rmd
edit fitness Paragraph1

@@
 
-Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype, and they are increasingly linked to important fitness outcomes for individuals among species ranging from primates (e.g.
-Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019) to dolphins (e.g.
-Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011) to birds (e.g.
+Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype.
+Social phenotypes are increasingly linked to important fitness for individuals of various species, including primates (e.g.
+Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019), dolphins (e.g.
+Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds (e.g.
 McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012).
-But there are many ways that scale comes into play in determining how characteristics of an individual’s social network position are related to fitness that depend on the hypotheses being tested and logistical constraints.
-The two scales that repeatedly come across as important for understanding fitness consequences are temporal and social scale (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
+The effect of scale on the relationship between an individual’s social network position and fitness may depend on the hypotheses being tested and logistical constraints.
+Two scales that are important for understanding fitness consequences in the context of social network positions are temporal and social scales (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
 

### 2020-01-23 paper/manuscript.Rmd
edit fitness P2

@@
 
-Social network structures depend on the time frame used to create them, which can make different networks difficult to compare (Castles et al., 2014).
-Furthermore, social network structures can vary by season and indicate social environments that an individual experiences (e.g.
+Social network structure depends on the timeframe of observation, which can make networks difficult to compare (Castles et al., 2014).
+Furthermore, social network structure can vary seasonally and indicate social environments that an individual experiences (e.g.
 Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018).

### 2020-01-23 paper/manuscript.Rmd
edit fitness P3

@@
 Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).
+**[QW: I'm not sure what this paragraph adds - I think if we need to save space we could cut it]**
 
-Additionally, in long-lived species especially, social network metrics of individuals can change over their lifetimes in ways that can have impacts on their reproductive success and longevity (Berger et al., 2015; Brent et al., 2017).
-These findings highlight the necessity to think carefully about the temporal scale that is meaningful for the proposed hypotheses, especially for understanding individual social phenotypes or environments and how they relate to that individual’s fitness.
-Further complicating the issue, social network metrics can change over stages of ontogeny, but individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018).
-This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social network position over different stages of ontogeny even more difficult.
-However, thinking about temporal scales at such a fine level can provide insights for important stages of development that may have otherwise been missed (CITE-myself??).
-However, multilayer networks provide a framework to test hypotheses about how social dynamics over time relate to fitness.
-Because of the non-independent nature of social interactions, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017).
+In long-lived species, social phenotypes can change over their lifetimes in ways that can have affect fitness (Berger et al., 2015; Brent et al., 2017).
+These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness.
+Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018).
+This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social phenotype over different stages of ontogeny even more difficult.
+However, considering fine temporal scales may provide insight across development stages that may otherwise be missed (CITE-myself??).
+Multilayer networks provide a framework to test hypotheses linking social phenotypes and fitness across temporal scales.
+Because of the non-independent nature of social interactions and associations, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017).
 Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.

### 2020-01-23 paper/manuscript.Rmd
edit fitness P4

@@
 
-Social scale is another major consideration for social network analysis, especially when thinking about different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
-It is a common trope that individuals need to be associating in order to interact and an assumption that proximity is proxy for interacting (Farine, 2015).
-For instance, baboons need to be in proximity in order to groom each other, but this trope is only thinking about interactions that humans are most prone to seeing and valuing with our bias toward visual perception.
+Social scale is another major consideration for social network analysis, especially in the context of different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
+It is a common trope that individuals must be associating to interact and most studies therefore assume that proximity is proxy for interacting (Farine, 2015).
+For instance, baboons need to be in proximity in order to groom each other, but this trope highlights human bias toward interactions that can be readily observed in the field.
 Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015).
-With improved and more affordable technology, we can now start to understand some of these interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
-The multilayer network framework further enables researchers to look at these different social scales and test how good a proxy proximity is for various forms of interacting in a holistic way.
+With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
+The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity is for various forms of interacting in a holistic way.
 

### 2020-01-23 paper/manuscript.Rmd
edit fitness P5

@@
 With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
-The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity is for various forms of interacting in a holistic way.
+The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity as a proxy for social interactions in a holistic way.
 
 These different social scales can have different fitness repercussions for individuals.
-Rhesus macaques (*Macaca mulatta*) that had stronger, more stable associates and grooming partners but not more partners in general had greater survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019).
-This finding highlights the need to look at social network positions at both multiple temporal and social scales to understand the social positions and fitness repercussions of individuals, and multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.
+Rhesus macaques (*Macaca mulatta*) that had stronger, more stable social associates and grooming partners, but not more social partners, had higher survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019).
+This finding highlights the need to investigate the effect of temporal and social scales on the relationship between social network positions and fitness.
+Multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.
 

### 2020-01-23 R/metrics.R
next TODO steps reorg/restructure functions

@@ -3,6 +3,7 @@
 #' Number of neighbors adjacent to each actor. Calculated excluding self from set of neighbors.
 #'
 #' @param DT a data.table with column "group" generated by spatsoc::group_pts
+#' @param var if there are subgroups within the DT, eg if the DT is the result of some kind of sensitivity analysis on spatsoc spatial buffers, include that field here
 #' @param splitBy this is not the splitBy (eg season)
 #' @param id 
 #'
@@ -33,6 +34,7 @@
 #' neigh(DT, 'id', var, splitBy = 'season')
 layer_neighbors <- function(DT, id, var = NULL, splitBy = NULL) {
   cols <- c(id, 'group', var, splitBy)
+  
   if (any(!(cols %in% colnames(DT)))) {
     stop(paste0(
       as.character(paste(setdiff(
@@ -48,20 +50,20 @@ layer_neighbors <- function(DT, id, var = NULL, splitBy = NULL) {
         g <- group
         DT[group %in% g, data.table::uniqueN(get(id)) - 1]
       },
-      by = id][]
+      by = c(id, var)][]
   } else {
     DT[, neighborhood := {
       g <- group
       DT[group %in% g, data.table::uniqueN(get(id)) - 1]
     },
-    by = id]
+    by = c(id, var)]
     
     
     DT[, splitNeighborhood := {
       g <- group
       DT[group %in% g, data.table::uniqueN(get(id)) - 1]
     },
-    by = c(splitBy, id)][]
+    by = c(splitBy, var, id)][]
   }
 }
 

### 2020-01-23 scripts/4-time-window-length.R

@@ -79,10 +79,16 @@ graphLs <- lapply(winlengths[1:2], function(len) {
 
 
 ### Multilayer network metrics ----
+# TODO: run neigh in lapply, combine with corr with eigen
+# TODO: 
+
+
 var <- 'winlength'
 
-vapply(graphLs, layer_correlation, FUN.VALUE = 42.0)
-
+corrs <- data.table(
+  winlength = winlengths,
+  layercorr = vapply(graphLs, layer_correlation, FUN.VALUE = 42.0)
+)
 
 gLs <- unlist(graphLs, recursive = FALSE)
 eig <- layer_eigen(gLs, idcol)
@@ -90,11 +96,11 @@ eig <- layer_eigen(gLs, idcol)
 eig[, c(var, splitBy) := tstrsplit(layer, '-', type.convert = TRUE)]
 
 
+layer_neighbors(sub, idcol, var, col)
+
+
 # TODO: modify neigh so it's working on a by
-# TODO: remove it from this lapply and merge afterwards
-# TODO: just return eig centrality and network correlation etc
 # TODO: then merge onto neigh output from above
-# neigh(sub, idcol, col)
 # 
 # outcols <- c('neighborhood', 'splitNeighborhood', idcol, col)
 # out <- unique(sub[, .SD, .SDcols = outcols])

### 2020-01-23 paper/manuscript.Rmd
edit fitness P6

@@
 Multilayer networks further provide unique challenges and opportunities for understanding the social phenotypes and environments of individuals and their fitness outcomes.
-Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should be made for the same time period, and the period needs to be long enough for each layer to have enough data for robust networks (Farine, 2017).
+Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should reflect the same time period, and the period should be long enough for each layer to have enough data for robust networks (Farine, 2017).
 These considerations may be limiting factors when answering questions that require timeframes that are relevant to different individuals.
-On the other hand, multilayer network metrics provide an opportunity to help simplify statistical models.
-Interactions that happen mere meters apart, proximity associations, and long-distance interactions can be encapsulated in one network to gain a single metric to describe the various social scales of an individual’s network position.
-This multilevel network metric would be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).
-This method could be an alternative to using PCA to simplify many social network metrics into one social phenotype (e.g.
-Foster et al., 2012; Oldham et al., 2019).
-Future analyses should explore the differences in how well each of these methods describe and predict fitness outcomes of the complex social network positions of individuals.
+On the other hand, multilayer network metrics provide an opportunity to simplify statistical models.
+Interactions that happen meters apart, proximity associations, and long-distance interactions can be encapsulated in a single multilayer network and a single metric can be used to describe the various social scales of an individual’s network position.
+This multilevel network metric could be used to assess the relationship between an individuals social phenotype and fitness.
+It would also be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).
 

### 2020-01-23 paper/manuscript.Rmd
conclusion
add questions

@@
 2019).
+
+## Conclusions
+
+something something blah blah.
+
+Silk et al.
+(2018) presented some key multilayer questions in animal behaviour research.
+While these questions represent an importanting starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:
+
+  1) How do social phenotypes across scales differently influence fitness? Are some social scales better predictors for different fitness metrics?
+
+  2) Why do individuals associate more strongly with certain conspecifics in some habitats? What, if any, is the role of movement in the context of habitat networks?
+
+  3)

### 2020-01-24 paper/manuscript.Rmd
edit movement ecol p1

@@
 
-In long-lived species, social phenotypes can change over their lifetimes in ways that can have affect fitness (Berger et al., 2015; Brent et al., 2017).
+In long-lived species, social phenotypes can change over their lifetimes in ways that can affect fitness (Berger et al., 2015; Brent et al., 2017).
 These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness.
@@
 Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al.
-2015) and multilayer networks are no exception (Mourier et al.
+2015), and multilayer networks are no exception (Mourier et al.
 2019).
-Movement is a dynamic process and is related to an individual’s space use as well as the resources consumed within their home range (Van Moorter et al.
+Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al.
 2016).
-Collective movement can reduce group-level predation via detection-dilution trade-offs, while it can also improve information transfer about the quality or location of resources (Jolles et al.
+Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al.
 2019).

### 2020-01-24 paper/manuscript.Rmd
edit movement ecol p2

@@
 Although multilayer animal social networks are relatively novel (Silk et al.
-2018), movement behaviour within multilayer networks has already been considered in a handful of studies.
-In gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al.
+2018), movement behaviour within multilayer networks has already been considered in a couple studies.
+In vulturine gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al.
 2019).
-In addition, *spatial networks* are networks of locations, which are connected in a network when individuals move between locations.
-For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
+In addition, *spatial networks* are physical locations (nodes) which are connected in a network when individuals move between said locations (ties).
+For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
 2019).
-While both studies integrate movement in some capacity, neither generate networks based on continuous measures of collective, or dyadic, movement (Long et al.
+While both studies integrate movement in some capacity, neither generate networks based on continuous measures of dyadic or collective movement (Long et al.
 2014).

### 2020-01-24 paper/manuscript.Rmd
edit movement ecol p3

@@
 2014) or groups (Bode et al.
-2011) as well as at a fine (i.e.
+2011).
+This movement layer could be made at a fine (i.e.
 minute-to-minute: Cleasby et al.
 2019) or coarse (global migration: Flack et al.
-2018) scales.
-Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including moving, interacting, or foraging (e.g.
+2018) scale.
+In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
+Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging **[JWT: these are not mutually exclusive behaviors, which may not matter here]** (e.g.
 Muller et al.
 2018; Finn et al.
-2019) and construct a multilayer networks based on behaviour-specific monolayer networks (e.g.
+2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g.
 Smith-Aguilar et al.
-2019) In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
+2019).
 Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al.

### 2020-01-24 paper/manuscript.Rmd
edit movement ecol p4

@@
 In our case study, we generated multilayer networks based on habitat-specific monolayers.
-Coordinated movement of dyads, or groups, could vary based on habitat and the approach we outline could be used to explore mechanisms linking the social and spatial environments.
+Coordinated movement of dyads, or groups, could vary based on habitat, and the approach we outline could be used to explore mechanisms linking the social and spatial environments.
 For example, social processes may be an emergent property of the landscape because animals aggregate at resources, such as waterholes (Chamaillé-Jammes et al.
-2008), while movement to, from, or within habitat patches can also contribute to the formation of the social environment (Spiegel et al.
+2008).
+Movement to, from, or within habitat patches can also contribute to the formation of the social environment **[JWT: how?
+I think it would help to clarify the example]**(Spiegel et al.
 2016).
 Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.
-In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insight into the effects of habitat configuration on the formation of the social environment (He et al.
+In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insights into the effects of habitat configuration on the formation of the social environment (He et al.
 2019).

### 2020-01-24 paper/manuscript.Rmd
small grammar fixes

@@
 In long-lived species, social phenotypes can change over their lifetimes in ways that can affect fitness (Berger et al., 2015; Brent et al., 2017).
-These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness.
+These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotype and fitness.
 Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018).
@@
 Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015).
-With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
-The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity as a proxy for social interactions in a holistic way.
+With the advancement of bio-logging technology, we have the ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
+The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good social proximity is as a proxy for social interactions in a holistic way.
 
@@
 On the other hand, multilayer network metrics provide an opportunity to simplify statistical models.
-Interactions that happen meters apart, proximity associations, and long-distance interactions can be encapsulated in a single multilayer network and a single metric can be used to describe the various social scales of an individual’s network position.
-This multilevel network metric could be used to assess the relationship between an individuals social phenotype and fitness.
+Interactions that happen meters apart, proximity associations, and long-distance interactions can be encapsulated in a single multilayer network, and a single metric can be used to describe the various social scales of an individual’s network position.
+This multilevel network metric could be used to assess the relationship between an individual's social phenotype and fitness.
 It would also be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).

### 2020-01-24 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md
Update manuscript.Rmd

@@
 2014; Farine 2015).
-Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (Farine et al.
+Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al.
 2015).
@@
 
-  1) How do social phenotypes across scales differently influence fitness? Are some social scales better predictors for different fitness metrics?
+  1) How do social phenotypes across scales differently influence fitness? Are some temporal or social scales better predictors for different fitness metrics?
 

### 2020-01-24 paper/manuscript.Rmd
intro edit

@@
 2008).
-Social network analysis provides insight into intra-specific interactions and the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al.
+Social network analysis provides insight into the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al.
 2014; Kurvers et al.

### 2020-01-24 paper/manuscript.Rmd
monolayr

@@
 
-Unlike traditional social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al.
+Unlike traditional *monolayer* social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al.
 2017).

### 2020-01-24 paper/manuscript.Rmd
intro edits

@@
 2019; Silk et al.
-2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and organismal neural networks (Silk et al.
+2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and neural networks (Silk et al.
 2018).
@@
 Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association?
-We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Ref), and movement ecology and collective movement (Jolles et al.
+We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
 2019).

### 2020-01-24 paper/manuscript.Rmd
Update manuscript.Rmd
soc scale
scale section

@@
 For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al.
-2019) in *R version* (R CITATION).
+2019) in *R version* (R Core Team 2020).
 
@@
 2018).
-To assess the role of social scale in multilayer networks, we varied the threshold distance for group assignment between 5-500m (see *Social scale* section below).
 In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.
@@
 
-### Scale in multilayer networks
+### Varying scale in multilayer networks
 
@@
 
-#### Altering social scale
+#### Social scale
 
@@
 
-#### Altering observational scale
+#### Observational scale
 
@@
 
-## Scale in multilayer networks in practice: case study results
+## Scale in multilayer networks in practice: case study results and discussion
+
+Results and interpretation of temporal scale - balh
+
+Results and interpretation of spatial scale - blah blah
+
+Results and interpretation of social scale - blah blah blah
 

### 2020-01-24 paper/manuscript.Rmd
move obs scale up

@@
 
+**Observational scale** (temorary header): Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al.
+2018; Webber and Vander Wal 2019).
+
+Randomly select max number of observations - timegroups -  (right now 750).
+For each iteration, include n observations for each season for all individuals.
+Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
+Parallels with observation data.
+
 #### Spatial scale
@@
 For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
-
-#### Observational scale
-
-Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).
-
-Randomly select max number of observations - timegroups -  (right now 750).
-For each iteration, include n observations for each season for all individuals.
-Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
-Parallels with observation data.
 

### 2020-01-24 paper/manuscript.Rmd
methods

@@
 2018).
-In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.
+In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented connections between the same individuals across contexts.
 

### 2020-01-24 scripts/4-time-window-length.R
smaller window length range

@@ -24,8 +24,7 @@ alloc.col(DT)
 # Remove season column from 1-data-prep.R
 DT[, season := NULL]
 
-# TODO: should this be a smaller min window size?
-winlengths <- seq(75, 150, 5)
+winlengths <- seq(40, 100, 5)
   
 l <- lapply(winlengths, function(l) {
   col <- paste0('season', l)

### 2020-01-24 paper/manuscript.Rmd
temp scale
temp scale2

@@
 Varying length of time window (used to define seasons).
-From 75 to 150 right now.
+Starting with a window of day 1-40 and using a moving window to go to day 1-100.
 Fixed start julian day for winter is day 1 and for summer is 215.
@@
 Varying position of time window (used to define seasons).
-Fixed length at 75.
-Window positions starting at 1, to + 75.
-So 1-75 is first iteration for winter and 75-150 is second iteration for "winter".
+Fixed length at 48 Window positions starting at 1, to + 48 So 1-48 is first iteration for winter and 48-96 is second iteration for "winter".
 Same for summer, starting at 215.

### 2020-01-24 scripts/6-time-window-position.R
smaller window position movement and fixed length

@@ -24,8 +24,8 @@ alloc.col(DT)
 # Remove season column from 1-prep
 DT[, season := NULL]
 
-winlength <- 75
-winpositions <- seq(1, 75, by = 1)
+winlength <- 48
+winpositions <- seq(1, 48, by = 1)
   
 l <- lapply(winpositions, function(pos) {
   col <- paste0('season', pos)

### 2020-01-24 paper/manuscript.Rmd
address JWT edits

@@
 In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
-Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging **[JWT: these are not mutually exclusive behaviors, which may not matter here]** (e.g.
+Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g.
 Muller et al.
@@
 2008).
-Movement to, from, or within habitat patches can also contribute to the formation of the social environment **[JWT: how?
-I think it would help to clarify the example]**(Spiegel et al.
+Movement to, from, or within habitat patches can also contribute to the formation of the social environment (Spiegel et al.
 2016).
+For example, XXX **[JWT: how?
+I think it would help to clarify the example]**.
 Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.

### 2020-01-24 scripts/1-data-prep.R
fin read in as rds

@@ -5,7 +5,6 @@
 pkgs <- c('data.table', 'rgdal')
 p <- lapply(pkgs, library, character.only = TRUE)
 
-# TODO: read in as rds everywhere else
 # TODO: timezones
 # TODO: rm old prep from all
 # TODO: confirm seasons

### 2020-01-24 scripts/1-data-prep.R
rm old prep todos

@@ -6,8 +6,6 @@ pkgs <- c('data.table', 'rgdal')
 p <- lapply(pkgs, library, character.only = TRUE)
 
 # TODO: timezones
-# TODO: rm old prep from all
-# TODO: confirm seasons
 # TODO: which individuals are dropped
 
 ### Data ----

### 2020-01-24 paper/manuscript.Rmd
todo update dates in manuscript

@@
 The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
-We therefore partitioned data into two discrete seasons: summer (3 August - 17 October) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al.
+We therefore partitioned data into two discrete seasons: <!-- TODO update these --> *summer (3 August - 17 October) and winter (1 January – 16 March)* based on caribou socioecology (Peignier et al.
 2019).
@@
 
-### Landscape ecology
+### Habitat selection and space use
+
+Mayor et al. 2009 paper
+
+MRSF Laforge paper
+
+van Beest et al. 2014 scale paper
+
+1st/2nd/3rd order selection blah blah
+
+Paper: Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
 

### 2020-01-24 scripts/1-data-prep.R
Update 1-data-prep.R

@@ -23,7 +23,6 @@ DT[, c(datecol, timecol) := .(as.IDate(get(datecol)), as.ITime(get(timecol)))]
 ## Seasons
 DT[between(JDate, winterlow, winterhigh), season := 'winter']
 DT[between(JDate, summerlow, summerhigh), season := 'summer']
-DT[!is.na(season)]
 ### Project relocations ----
 DT[, (projCols) := as.data.table(project(cbind(get(xcol), get(ycol)), utm21N))]
 
@@ -33,9 +32,9 @@ sub <- DT[Year >= 2017 & JDate > summerlow | Year == 2018]
 
 # Sub only individuals with data in both seasons
 keepids <- sub[, .N, c(idcol, 'season')][!is.na(season), .N, idcol][N == 2][[idcol]]
-subSeasons <- sub2018[!is.na(season)][get(idcol) %chin% keepids]
+subSeasons <- sub[!is.na(season)][get(idcol) %chin% keepids]
 
 
 ### Output ----
-saveRDS(sub2018, 'data/derived-data/sub-2018-fogo-caribou.Rds')
+saveRDS(sub, 'data/derived-data/sub-fogo-caribou.Rds')
 saveRDS(subSeasons, 'data/derived-data/sub-seasons-fogo-caribou.Rds')

### 2020-01-24 paper/manuscript.Rmd
habitat selection

@@
 The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
-We therefore partitioned data into two discrete seasons: <!-- TODO update these --> *summer (3 August - 17 October) and winter (1 January – 16 March)* based on caribou socioecology (Peignier et al.
+We therefore partitioned data into two discrete seasons: summer (3 August - 17 October) and winter (1 January – 16 March) based on caribou socioecology (Peignier et al.
 2019).

### 2020-01-28 paper/manuscript.Rmd
add paper title to hab selection section
add acknowledge notes
edit abstract + intro

--- 2020-01-24 paper/manuscript.Rmd
@@
 Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use.
+Meanwhile, social processes can also scale from fine-scale interactions to co-occurrence and overlapping home ranges.
 Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogeneous landscapes.
 Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics.
-Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animal’s perception of scale.
-We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales.
-Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data.
-*Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.* Effective integration of spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network.
-Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.
+Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social, spatial, temporal scale on multilayer processes.
+We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement (Jolles et al.
+2019).Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
+Based on social network and behavioural ecology theory as well as our case study, we demonstrate potential for interconnectedness among individual animals, their social environment, and the landscapes they occupy.
 
@@
 First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems?
-Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association?
-We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
+Second, can variation in social, spatial, and temporal scale improve predictions associated with seasonal differences in resource availability and social association?
+We conclude with perspectives for future development and application of scale in multilayer networks with respect to habitat selection and space use (Van Moorter et al.
+2016), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
 2019).
@@
 
+Multi-scale habitat selection modeling: a review and outlook
+
 ### Individual fitness and phenotypes
@@
   3)
+
+## Acknowledgements
+* DCS
+* check WG

### 2020-01-28 paper/manuscript.Rmd
add fig1

@@
 Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social, spatial, temporal scale on multilayer processes.
-We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement (Jolles et al.
-2019).Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
+We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement.Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
 Based on social network and behavioural ecology theory as well as our case study, we demonstrate potential for interconnectedness among individual animals, their social environment, and the landscapes they occupy.
@@
 
-Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework.
+Here, we discuss and integrate variation in social, spatial, and temporal scales within a multilayer network framework (Figure 1).
 We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
@@
 2019).
+
+\captionsetup[figure]{labelformat=empty}
+
+![**Figure 1**](../graphics/figure1.png) 
+**Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
+\clearpage
 

### 2020-01-28 paper/manuscript.Rmd
blah

@@
 ![**Figure 1**](../graphics/figure1.png)
+
 **Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.

### 2020-01-28 paper/manuscript.Rmd
metric section

@@
 
-For each multilayer network, we calculated XXX metrics.These included four neighborhood-based metrics: degree centrality, multidegree, degree deviation, and neighbours as well as two multilayer [need better term here?] metrics: connective redundancy and relevance (see Glossary for definitions).
+#### Network metrics
+
+For each multilayer network, we calculated four metrics.These included: multidegree, graph strength, redundancy/relevance, and  layer similarity.
 GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).
 
-We generated all networks 
-Right now, we calculate mostly degree/neighborhood based metrics.
+ALR: Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."
 
-Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."
+##### Multidegree
 
@@
 * Neighbors/neighborhood (number of unique actors directly connected to each focal)
-
 Neighbors = degree within a network layer
@@
 
-So the difference between neighbors and degree is the basis for
+##### Graph strength
+
+Finally, some weighted variables:
+
+* eigenvector centrality, summed across layers as described in Boccaletti, Stefano, et al. "The structure and dynamics of multilayer networks." Physics Reports 544.1 (2014): 1-122.
+
+##### Redundancy/relevance
 
@@
 
+##### Layer similarity
+
 Then there will be some layer similarity. Right now it's just a correlation of each season's asnipe SRI matrix
-
-Finally, some weighted variables:
-
-* eigenvector centrality, summed across layers as described in Boccaletti, Stefano, et al. "The structure and dynamics of multilayer networks." Physics Reports 544.1 (2014): 1-122.
 

### 2020-01-28 paper/manuscript.Rmd
acknowledgements

@@
 ## Acknowledgements
-* DCS
-* check WG
+
+We thank all members of the Wildlife Evolutionary Ecology Lab, including XXXXX **check WG reviewers** for their comments on previous versions of this manuscript as well as D.
+Schneider for inspiration and helpful discussions about scale.
+Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.

### 2020-01-28 paper/manuscript.Rmd
acknowledgements - add WG reviewers for ALR submissions

@@
 
-We thank all members of the Wildlife Evolutionary Ecology Lab, including XXXXX **check WG reviewers** for their comments on previous versions of this manuscript as well as D.
+We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
+Kingdon, S.
+Boyle,  C.
+Prokopenko, I.
+Richmond, and L.
+Newediuk for their comments on previous versions of this manuscript as well as D.
 Schneider for inspiration and helpful discussions about scale.

### 2020-01-28 paper/manuscript.Rmd
conclusions

@@
 (2018) presented some key multilayer questions in animal behaviour research.
-While these questions represent an importanting starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:
+While these questions represent an important starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:
 
@@
 
-  3)
+  3) How, and why, does the spatial scale of perception influence, e.g.
+auditory, visual, or chemotaxis, influence the  social environment across scales?
+What is the role of memory, and by extension social and spatial cognition, as animals navigate their environment and make decisions about where to move next?
 

### 2020-01-28 paper/manuscript.Rmd
abstract edits

@@
 Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use.
-Meanwhile, social processes can also scale from fine-scale interactions to co-occurrence and overlapping home ranges.
-Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogeneous landscapes.
-Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics.
-Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social, spatial, temporal scale on multilayer processes.
-We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement.Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
+Meanwhile, social processes can also scale from fine-scale interactions to co-occurrence to overlapping home ranges.
+Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal space use and movement in heterogeneous landscapes.
+Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of scale, e.g., grain and extent.
+But scale can affect multilayer network dynamics and how we build and interpret them.
+Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of temporal, spatial, and social scale **[JWT: I made this follow the order Alec has below, but should the order maybe be spatial, temproal, social, since spatial is the most novel?
+Maybe that's not a good flow of the story though?]** on multilayer processes.
+We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement.Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution uniquely incorporates perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
 Based on social network and behavioural ecology theory as well as our case study, we demonstrate potential for interconnectedness among individual animals, their social environment, and the landscapes they occupy.

### 2020-01-28 R/metrics.R
rm layer_correlation function

@@ -185,16 +185,20 @@ layer_strength <- function(graphLs) {
 #' @export
 #'
 #' @examples
-layer_correlation <- function(gLs, attr = 'weight') {
-  if (length(gLs) != 2) {
-    stop('gLs must be length 2')
-  }
-  cor(c(igraph::as_adj(
-    gLs[[1]], attr = attr, sparse = FALSE
-  )), c(igraph::as_adj(
-    gLs[[2]], attr = attr, sparse = FALSE
-  )))
-}
+# layer_correlation <- function(DT,gLs, attr = 'weight') {
+#   matrices <- DT[, property_matrix(.SD, idcol, 'layer', 'splitNeigh'), var]
+#   layersim <- matrices[, .(layersd = sd(unlist(.SD))), winlength, .SDcols = patterns('FO')]
+#   DT[layersim, layersd := layersd, on = var]
+#   
+#   if (length(gLs) != 2) {
+#     stop('gLs must be length 2')
+#   }
+#   cor(c(igraph::as_adj(
+#     gLs[[1]], attr = attr, sparse = FALSE
+#   )), c(igraph::as_adj(
+#     gLs[[2]], attr = attr, sparse = FALSE
+#   )))
+# }
 
 
 

### 2020-01-28 scripts/8-plots.R
simpler patchwork

@@ -71,18 +71,7 @@ g8 <- g + geom_line(aes(y = mngraphstrength))
 
 
 # Patchwork
-1, 2, 5, 7, 8, 
-
-(g1 + g2 + g5) / (g7 + g8)
-
-g1 / 
-  g2
-  g3 /
-  g4 / # neigh
-  g5 /
-  g6 /
-  g7 /
-  g8
+(g1 + g5) / (g7 + g8)
 
 
 ## Supplemental figures

### 2020-01-28 paper/manuscript.Rmd
fst metric interpretation summary

@@
 
+### Each metric's interpretation
+* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
+* Degree deviation: deviation of degree across layers.
+High degree deviation = large difference between degree for an individual across layers.
+Low degree deviation = individuals are similarly connected across layers.
+*
+
+###
+
 Results and interpretation of temporal scale - balh

### 2020-01-28 paper/manuscript.Rmd
interpret strength, neighbors

@@
 Low degree deviation = individuals are similarly connected across layers.
-*
+* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
+* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
+* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
+* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor.
+High relevance means that the layer is highly relevant to the individuals connections.
+A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood.
+* Connective redundancy: the total multilayer neighborhood divided by the multidegree.
+High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours.
+Low connective redundancy is
 

### 2020-01-31 paper/manuscript.Rmd
interpret conn redund
interpret layer similarity
refs

@@
     github_document
+
+references: ../references/franks.bib
 ---
@@
 Carter et al.
-2015), whereas social association represents shared space use by members of the same social group (Franks et al.
-2010).
+2015), whereas social association represents shared space use by members of the same social group [@Franks2010].
 Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges.
@@
 High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours.
-Low connective redundancy is
+Low connective redundancy indicates that each layer is important for preserving all social ties.
+* Layer similarily/correlation: how similar each layer is (Brodka 2018). right now - standard deviation of the vectors.. so decrease deviation = increased similarity
 
@@
 
-Animal movement undoubtedly affects the social environment (Strandburg-Peshkin et al.
+Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al.
 2015), and multilayer networks are no exception (Mourier et al.

### 2020-01-31 paper/manuscript.Rmd
refs
movement edits from WG

@@
 Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al.
-2015), and multilayer networks are no exception (Mourier et al.
-2019).
+2015).
 Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al.
@@
 2019).
-Social processes, movement decisions, and space use are therefore inextricably linked.
+Social processes, movement decisions, and space use are therefore inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g.
+Mourier et al.
+2019).
 
@@
 2019).
-In addition, *spatial networks* are physical locations (nodes) which are connected in a network when individuals move between said locations (ties).
-For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between fixed location autonomous arrays, where nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
+In addition, *spatial networks* are physical locations (nodes) which are connected in a network when individuals move between said locations (edges).
+For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between fixed location autonomous arrays.
+In this example, nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
 2019).
@@
 
-Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make movement decisions in the context of their local environment (Strandburg-Peshkin et al.
+In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
+Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al.
 2015, 2017) and across scales.
@@
 minute-to-minute: Cleasby et al.
-2019) or coarse (global migration: Flack et al.
-2018) scale.
-In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
+2019) or coarse scale (global migration: Flack et al.
+2018).
 Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g.
@@
 2008).
-Movement to, from, or within habitat patches can also contribute to the formation of the social environment (Spiegel et al.
+Movement to, from, or within habitat patches  or territories can also contribute to the formation of the social environment (Spiegel et al.
 2016).
-For example, XXX **[JWT: how?
-I think it would help to clarify the example]**.
+For example, in sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range edges, presumably driving territorial behaviour (Spiegel et al.
+2018).
 Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.
@@
 Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.
+
+## References

### 2020-01-31 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md
move

@@
 
-references: ../references/franks.bib
+references: ../references/refs.bib
 ---
@@
 2015).
-Movement is a dynamic process that is related to the resources an individual consumes within their home range and their general space use (Van Moorter et al.
+Movement is a dynamic process that is related to the resources an individual consumes within their home range and the space that they use (Van Moorter et al.
 2016).
@@
 2019).
-Social processes, movement decisions, and space use are therefore inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g.
+Social processes, movement decisions, and space use are inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g.
 Mourier et al.
@@
 
-In contrast to spatial networks, movement networks could assimilate dyadic movement metrics into a network representing the continuous and simultaneous movement trajectories of animals.
+In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks represent continuous and simultaneous movement trajectories of animals.
 Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al.

### 2020-01-31 paper/manuscript.Rmd
Update manuscript.Rmd

@@
 
-In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks represent continuous and simultaneous movement trajectories of animals.
+In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks can represent continuous and simultaneous movement trajectories of multiple animals.
 Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al.
@@
 Prokopenko, I.
-Richmond, and L.
+Richmond, J.
+Hogg, and L.
 Newediuk for their comments on previous versions of this manuscript as well as D.

### 2020-01-31 paper/manuscript.Rmd
abstract

@@
 But scale can affect multilayer network dynamics and how we build and interpret them.
-Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of temporal, spatial, and social scale **[JWT: I made this follow the order Alec has below, but should the order maybe be spatial, temproal, social, since spatial is the most novel?
-Maybe that's not a good flow of the story though?]** on multilayer processes.
+Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social,spatial, and temporal scale on multilayer processes.
 We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement.Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution uniquely incorporates perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.

### 2020-01-31 scripts/8-plots.R
use patchwork & to spread theme

@@ -101,20 +101,13 @@ linesize <- 1.3
 
 # Plot by landcover
 base1 <- ggplot(unique(DT[, .SD, .SDcols = c(var, 'lcname', 'layersim')]), 
-            aes(x = get(var), linetype = lcname)) +
-  # guides(color = FALSE) +
-  labs(x = varnames[var == var, varname]) + 
-  p# +
-  # scale_color_grey()
+            aes(x = get(var), linetype = lcname))
 
 g1 <- base1 + geom_line(aes(y = (layersim)), size = linesize) + ylab('Layer Similarity')
 
 # Plot full, across
 base2 <- ggplot(DT[, .SD[1], by = var], 
-            aes(x = get(var)), color = 'black') +
-  guides(color = FALSE) +
-  labs(x = varnames[var == var, varname]) + 
-  p
+            aes(x = get(var)), color = 'black')
 
 g2 <- base2 + geom_line(aes(y = mnmultideg), size = linesize) + ylab('Multidegree')
 g3 <- base2 + geom_line(aes(y = mndegdev), size = linesize) + ylab('Degree Deviation')
@@ -123,27 +116,27 @@ g5 <- base2 + geom_line(aes(y = mnconnredund), size = linesize) + ylab('Connecti
 
 
 # Plot within
-base3 <- ggplot(DT, aes(x = get(var), color = season, linetype = lcname)) + 
-  labs(x = varnames[var == var, varname]) + 
-  p + 
+base3 <- ggplot(DT, aes(x = get(var), color = season, linetype = lcname)) +
   scale_color_manual(values = c(cols$hex[1], cols$hex[5]))
-
-  
 
 g6 <- base3 + geom_line(aes(y = mnsplitNeigh), size = linesize) + ylab('Degree')
 g7 <- base3 + geom_line(aes(y = mnrelev), size = linesize) + ylab('Relevance') +
   theme(legend.position = pos2) + guides(linetype = FALSE)
 g8 <- base3 + geom_line(aes(y = mngraphstrength), size = linesize) + ylab('Graph Strength') +
-  theme(legend.position = 'none') 
+  guides(color = FALSE, linetype = FALSE)
 
 
 # Patchwork
-(fig2 <- (g1 + g5) / (g7 + g8) )
+(fig2 <- (g1 + g5) / (g7 + g8) +
+    plot_annotation(tag_levels = 'A') & 
[…]

### 2020-01-31 scripts/8-plots.R
fix var with vars

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'lcres'
+var <- 'nobs'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -40,7 +40,7 @@ DT[get(lccol) == 3, c('lcname', 'layernm') := .('lichen', paste0(season, '-liche
 
 # Var x lab names
 varnames <- data.table(
-  var = c('lcres', 'spatialthreshold', 'winlength', 'nobs', 'winpos'),
+  vars = c('lcres', 'spatialthreshold', 'winlength', 'nobs', 'winpos'),
   varname = c('Landcover Resolution', 'Social Threshold', 'Time Window Length',
               'Number of Observations', 'Time Window Position')
 )

### 2020-01-31 paper/manuscript.Rmd
adjust scale order methods
clarify layer similarity interpretation
include bookdown::word_doc2 for text references

@@
 output: 
-    #word_document
-    github_document
+    bookdown::word_document2
+    # github_document
 
@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(
+    echo = FALSE,
+    # warning = FALSE,
+    # message = FALSE,
+    eval = TRUE
+)
+```
 
@@
 
+#### Social scale
+
+We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
+Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
+For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
+
+#### Spatial scale
+
+To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
+Specifically, we selected scales relevant to caribou ecology.
+We re-sampled landcover using the `grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
+Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
+2017).
+Resampling occurred based on a modal moving window method, where **XXXXX.
+[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
+
+For each landcover (the original resolution and modal resampled resolutions), seasonal network layers are combined in a multilayer network
+<!-- Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
+
 #### Temporal scale
@@
 
-#### Spatial scale
-
-To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
-Specifically, we selected scales relevant to caribou ecology.
-We re-sampled landcover using the `grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
-Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
-2017).
-Resampling occurred based on a modal moving window method, where **XXXXX.
-[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
-
-For each landcover (the original resolution and modal resampled resolutions), seasonal network layers are combined in a multilayer network
-<!-- Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
-
-#### Social scale
-
-We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
-Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
-For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
-
 ## Scale in multilayer networks in practice: case study results and discussion
@@
 Low connective redundancy indicates that each layer is important for preserving all social ties.
-* Layer similarily/correlation: how similar each layer is (Brodka 2018). right now - standard deviation of the vectors.. so decrease deviation = increased similarity
+* Layer similarily: how similar each layer is (Brodka 2018). Pearson's correlation coefficient of degree vectors for each layer, comparing each landcover across seasons.
 

### 2020-01-31 paper/manuscript.Rmd
switch fig 1 to include_graphics

@@
 
-\captionsetup[figure]{labelformat=empty}
+<!-- \captionsetup[figure]{labelformat=empty} -->
 
-![**Figure 1**](../graphics/figure1.png)
+(ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
 
-**Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
-\clearpage
+```{r spacetime, fig.cap='(ref:spacetime)'}
+knitr::include_graphics('../graphics/figure1.png')
+```
 

### 2020-01-31 scripts/8-plots.R
add Layer to Relevance ylab

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'nobs'
+var <- 'lcres'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -120,7 +120,7 @@ base3 <- ggplot(DT, aes(x = get(var), color = season, linetype = lcname)) +
   scale_color_manual(values = c(cols$hex[1], cols$hex[5]))
 
 g6 <- base3 + geom_line(aes(y = mnsplitNeigh), size = linesize) + ylab('Degree')
-g7 <- base3 + geom_line(aes(y = mnrelev), size = linesize) + ylab('Relevance') +
+g7 <- base3 + geom_line(aes(y = mnrelev), size = linesize) + ylab('Layer Relevance') +
   theme(legend.position = pos2) + guides(linetype = FALSE)
 g8 <- base3 + geom_line(aes(y = mngraphstrength), size = linesize) + ylab('Graph Strength') +
   guides(color = FALSE, linetype = FALSE)

### 2020-01-31 paper/manuscript.Rmd
fst lcres cap and interpret

@@
 
-<!-- \captionsetup[figure]{labelformat=empty} -->
-
 (ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
 
-```{r spacetime, fig.cap='(ref:spacetime)'}
+```{r, fig.cap='(ref:spacetime)'}
 knitr::include_graphics('../graphics/figure1.png')
@@
 
+### Figure captions and brief interpretations
+
+#### Interpretations:
+
+(ref:lcres) : varying scale in landcover resolution.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+
+```{r, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
+Figure 2: point based spatial grouping with `group_pts`.
+A) Three relocations for four individuals in three time groups (example data described in Table 1).
+The relocation in the second timegroup for all individuals is buffered, to depict the distance threshold (in this case 50m) to generate spatial groups.
+The temporal threshold used is five minutes (see Figure 1 B).
+B) A distance matrix of relocations for all four individuals at timegroup 2 where highlighted rows are pairwise distances that meet the user defined criteria for spatial grouping, i.e.
+are less than the spatial threshold.
+C) The connected components showing the chain rule implementation of point based distance grouping with `group_pts`.
+The connected components show individuals E, F and G grouped (group 2 coloured blue), despite individual F and G being further apart than the spatial threshold, since they were both within the threshold distance from E.
+Individual H is assigned a group on their own, since they are not within the spatial threshold of any other individuals (group 9 coloured pink).
+D) Output spatiotemporal groups from `group_pts` showing individuals ("ID"), timegroups ("timegroup") and spatiotemporal groups ("group").
+
+* landcover resolution
+
 ###
-
 Results and interpretation of temporal scale - balh

### 2020-01-31 paper/manuscript.Rmd
rm example fig cap

@@
 
-Figure 2: point based spatial grouping with `group_pts`.
-A) Three relocations for four individuals in three time groups (example data described in Table 1).
-The relocation in the second timegroup for all individuals is buffered, to depict the distance threshold (in this case 50m) to generate spatial groups.
-The temporal threshold used is five minutes (see Figure 1 B).
-B) A distance matrix of relocations for all four individuals at timegroup 2 where highlighted rows are pairwise distances that meet the user defined criteria for spatial grouping, i.e.
-are less than the spatial threshold.
-C) The connected components showing the chain rule implementation of point based distance grouping with `group_pts`.
-The connected components show individuals E, F and G grouped (group 2 coloured blue), despite individual F and G being further apart than the spatial threshold, since they were both within the threshold distance from E.
-Individual H is assigned a group on their own, since they are not within the spatial threshold of any other individuals (group 9 coloured pink).
-D) Output spatiotemporal groups from `group_pts` showing individuals ("ID"), timegroups ("timegroup") and spatiotemporal groups ("group").
-
-* landcover resolution
-
 ###

### 2020-01-31 paper/manuscript.Rmd
fst spatial threshold interpretation

@@
 output: 
-    bookdown::word_document2
-    # github_document
+    # bookdown::word_document2
+    github_document
 
@@
 
-#### Interpretations:
-
 (ref:lcres) : varying scale in landcover resolution.
@@
 knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
+(ref:socres) : varying scale in social threshold.
+For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
+B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m.
+C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
+D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.
+
+```{r, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-spatialthreshold.png')
 ```

### 2020-01-31 paper/manuscript.Rmd
lcres proper interpret points

@@
 
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+
 (ref:socres) : varying scale in social threshold.

### 2020-01-31 paper/manuscript.Rmd
spat thresh proper interpret points

@@
 
+* increasing layer relevance as more individuals are connected with increasing buffer size
+* decrease in connective redundancy due an increase in summer forest degree at the last (500m) social threshold
+* increasing graph strength consistent with increasing strength in winter
+
+(ref:winlen) : varying scale in time window length.
+For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
+B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m.
+C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
+D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.
+
+* increasing window length = increasingly similar
+*
+
+```{r, fig.cap='(ref:winlen)'}
+knitr::include_graphics('../graphics/figure-winlength.png')
+```
+
 ###

### 2020-01-31 paper/manuscript.Rmd
win len proper interpret points

@@
 
-* increasing window length = increasingly similar
-*
+* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
+* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
+* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
+* layers are more similarly relevant at high window length
 

### 2020-01-31 scripts/8-plots.R

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'lcres'
+var <- 'winlength'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]

### 2020-01-31 paper/manuscript.Rmd
nobs proper interpret and cap

@@
 
+<!-- RO first sentence... -->
+
+(ref:nobs) : varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations.
+C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.
+
+* common, though at different points - more observations until stabilizing
+* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming..
+* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
+
+```{r, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
+```
+
 ###

### 2020-01-31 scripts/8-plots.R

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'winlength'
+var <- 'nobs'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]

### 2020-01-31 paper/manuscript.Rmd
winpos points and cap

@@
 
+(ref:winpos) : varying scale in time window position.
+For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
+B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions.
+D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+
+* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
+* same theme shown in the connective redundancy
+* quite variable layer similarity, not sure what to pull out of that one
+* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
+
+```{r, fig.cap='(ref:winpos)'}
+knitr::include_graphics('../graphics/figure-winpos.png')
+```
+
 ###

### 2020-01-31 scripts/8-plots.R

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'nobs'
+var <- 'winpos'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]

### 2020-01-31 paper/manuscript.Rmd
use template docx
fix text refs space :

@@
 output: 
-    # bookdown::word_document2
-    github_document
+    bookdown::word_document2:
+      reference_docx: template.docx
+    # github_document
 
@@
 
-(ref:lcres) : varying scale in landcover resolution.
+(ref:lcres): varying scale in landcover resolution.
 For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:socres) : varying scale in social threshold.
+(ref:socres): varying scale in social threshold.
 For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:winlen) : varying scale in time window length.
+(ref:winlen): varying scale in time window length.
 For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:nobs) : varying scale in number of observations.
+(ref:nobs): varying scale in number of observations.
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:winpos) : varying scale in time window position.
+(ref:winpos): varying scale in time window position.
 For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.

### 2020-01-31 paper/manuscript.Rmd
integrate edits intro

@@
 ## Introduction
-Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al.
+Our inference regarding the ecological processes underlying ecological patterns are directly linked to the scale at which they are observed (Levin 1992; Allen et al.
 2015).
-Animals and landscapes are influenced across scales processes as global as climate and productivity (Field et al.
-2009), and species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013).
-The effect of scale in ecology has been explored through species distribution modelling (Elith et al.
+Animals are influenced across scales, through processes such as species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013) and global climate and productivity (Field et al.
+2009).
+Multiscale ecology has been integrated into species distribution modelling (Elith et al.
 2009), habitat selection (Mayor et al.
@@
 1989).
-Scale can be considered throughout ecology, including animal behaviour and the social environment that animals experience.
-
-Sociality exists across scales (Whitehead 2008).
-For example, grooming and mating relationships require close proximity between conspecifics and occur over brief time periods (e.g.
+Meanwhile, in the context of animal behaviour, certain behaviours are scale dependent, for example, acoustic communication in birds occurs over variable spatial scales (Luther 2009).
+We posit that animal behaviour and, more specifically, the social environment that animals experience must also be scale-dependent.
+Sociality exists across both temporal and spatial scales (Whitehead 2008).
+For example, grooming requires close spatial proximity between conspecifics and occurs over brief time periods (e.g.
 Carter et al.
-2015), whereas social association represents shared space use by members of the same social group [@Franks2010].
+2015), whereas social association represents shared space use by members of the same social group (Figure 1, Franks et al.
+2010).
 Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges.
-In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over larger spatial and temporal scales (e.g.
+In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over coarser spatial and temporal scales (e.g.
 Piza-Roca et al.
@@
 2014; Farine 2015).
-Here, we define *social scale* as the type of social relationship observed that can be explicitly defined and measured in social network analyses (see Glossary; Farine et al.
+Thus, we define social scale as the type of social relationship observed that can be explicitly defined and measured (Farine et al.
 2015).
-
 Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al.
@@
 2008).
-Social network analysis provides insight into the structure of social communities and social network properties can influences population dynamics and evolutionary processes (Pinter-Wollman et al.
+Social network analysis provides insight into the structure of social communities and social network properties, which can influence population dynamics and evolutionary processes (Pinter-Wollman et al.
 2014; Kurvers et al.
 2014).
-Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network, drastically simplifying the complexity of animal social systems (Finn et al.
+Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network (monolayer), drastically simplifying the potential complexity of animal social systems (Finn et al.
 2019).
-
-Unlike traditional *monolayer* social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al.
+Unlike traditional monolayer social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al.
 2017).
@@
 The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
-
-Here, we discuss and integrate variation in social, spatial, and temporal scales within a multilayer network framework (Figure 1).
-We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
+Our study is motivated by behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
 2019).
 We use this case study to address two principal questions associated with scale-dependent multilayer networks.
-First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems?
-Second, can variation in social, spatial, and temporal scale improve predictions associated with seasonal differences in resource availability and social association?
-We conclude with perspectives for future development and application of scale in multilayer networks with respect to habitat selection and space use (Van Moorter et al.
-2016), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
+First, to what degree does the social scale of relationships, spatial scale of landscapes, and temporal scale of analysis influence our ability to interpret complex social systems?
+Second, can variation in social, spatial, and temporal improve predictions associated with biological differences in seasonal resource availability and social association?
+We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
 2019).

### 2020-01-31 paper/manuscript.Rmd
fix text refs end paragraph space

@@
 
-(ref:lcres): varying scale in landcover resolution.
+(ref:lcres) varying scale in landcover resolution.
 For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:socres): varying scale in social threshold.
+(ref:socres) varying scale in social threshold.
 For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:winlen): varying scale in time window length.
+(ref:winlen) varying scale in time window length.
 For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:nobs): varying scale in number of observations.
+(ref:nobs) varying scale in number of observations.
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
@@
 
-(ref:winpos): varying scale in time window position.
+(ref:winpos) varying scale in time window position.
 For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.

### 2020-01-31 paper/manuscript.Rmd
try reflow paragraph

@@
 ## Abstract
-Scale remains a seminal concept in ecology.
-Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use.
-Meanwhile, social processes can also scale from fine-scale interactions to co-occurrence to overlapping home ranges.
-Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal space use and movement in heterogeneous landscapes.
-Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of scale, e.g., grain and extent.
-But scale can affect multilayer network dynamics and how we build and interpret them.
-Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social,spatial, and temporal scale on multilayer processes.
-We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement.Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution uniquely incorporates perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework.
-Based on social network and behavioural ecology theory as well as our case study, we demonstrate potential for interconnectedness among individual animals, their social environment, and the landscapes they occupy.
+Scale remains a seminal concept in ecology. Spatial scale, for instance, has
+become a central consideration in the way we understand landscape ecology and
+animal space use. Meanwhile, social processes can also scale from fine-scale
+interactions to co-occurrence to overlapping home ranges. Multilayer networks
+promise the integration of monolayer animal social networks with the complexity
+and importance of animal space use and movement in heterogeneous landscapes.
+Despite the complex interplay between social networks and how animals use space,
+there remains an important biological and methodological gap in our
+understanding of an animal’s perception of scale, e.g., grain and extent. But
+scale can affect multilayer network dynamics and how we build and interpret
+them. Here, we discuss the role of scale in the context of multilayer networks
+and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role
+of social,spatial, and temporal scale on multilayer processes. We also present
+perspectives on future development and application of scale in multilayer
+networks with respect to habitat selection and space use, individual fitness and
+phenotypes, and movement ecology and collective movement.Effective integration
+of social and spatial processes, including biologically meaningful scales,
+within the context of animal social networks is an emerging area of research;
+our contribution uniquely incorporates perspectives on how the social
+environment and spatial processes are linked across scales in a multilayer
+framework. Based on social network and behavioural ecology theory as well as our
+case study, we demonstrate potential for interconnectedness among individual
+animals, their social environment, and the landscapes they occupy.
 
@@
 We posit that animal behaviour and, more specifically, the social environment that animals experience must also be scale-dependent.
+
 Sociality exists across both temporal and spatial scales (Whitehead 2008).
@@
 2015).
+
 Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al.
@@
 The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
+
 Our study is motivated by behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.

### 2020-01-31 paper/manuscript.Rmd
reflow intro

@@
 ## Introduction
-Our inference regarding the ecological processes underlying ecological patterns are directly linked to the scale at which they are observed (Levin 1992; Allen et al.
-2015).
-Animals are influenced across scales, through processes such as species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013) and global climate and productivity (Field et al.
-2009).
-Multiscale ecology has been integrated into species distribution modelling (Elith et al.
-2009), habitat selection (Mayor et al.
-2007), and food webs (Sugihara et al.
-1989).
-Meanwhile, in the context of animal behaviour, certain behaviours are scale dependent, for example, acoustic communication in birds occurs over variable spatial scales (Luther 2009).
-We posit that animal behaviour and, more specifically, the social environment that animals experience must also be scale-dependent.
+Our inference regarding the ecological processes underlying ecological patterns
+are directly linked to the scale at which they are observed (Levin 1992; Allen
+et al. 2015). Animals are influenced across scales, through processes such as
+species-specific as trophic interactions and resource availability (Legendre
+1993; Chave 2013) and global climate and productivity (Field et al. 2009).
+Multiscale ecology has been integrated into species distribution modelling
+(Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs
+(Sugihara et al. 1989). Meanwhile, in the context of animal behaviour, certain
+behaviours are scale dependent, for example, acoustic communication in birds
+occurs over variable spatial scales (Luther 2009). We posit that animal
+behaviour and, more specifically, the social environment that animals experience
+must also be scale-dependent.
 
-Sociality exists across both temporal and spatial scales (Whitehead 2008).
-For example, grooming requires close spatial proximity between conspecifics and occurs over brief time periods (e.g.
-Carter et al.
-2015), whereas social association represents shared space use by members of the same social group (Figure 1, Franks et al.
-2010).
-Further, for social interactions or associations to occur individuals must share space, and thus have overlapping home ranges.
-In the context of the social environment, home range overlap is a relatively coarse scale of sociality across which individuals share space over coarser spatial and temporal scales (e.g.
-Piza-Roca et al.
-2018).
-Although the social environment clearly scales spatially and temporally, it remains unclear whether coarser scales of sociality, including social association and home range overlap, vary predictably with social interaction (Castles et al.
-2014; Farine 2015).
-Thus, we define social scale as the type of social relationship observed that can be explicitly defined and measured (Farine et al.
-2015).
+Sociality exists across both temporal and spatial scales (Whitehead 2008). For
+example, grooming requires close spatial proximity between conspecifics and
+occurs over brief time periods (e.g. Carter et al. 2015), whereas social
+association represents shared space use by members of the same social group
+(Figure 1, Franks et al. 2010). Further, for social interactions or associations
+to occur individuals must share space, and thus have overlapping home ranges. In
+the context of the social environment, home range overlap is a relatively coarse
+scale of sociality across which individuals share space over coarser spatial and
+temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
+clearly scales spatially and temporally, it remains unclear whether coarser
+scales of sociality, including social association and home range overlap, vary
+predictably with social interaction (Castles et al. 2014; Farine 2015). Thus, we
+define social scale as the type of social relationship observed that can be
+explicitly defined and measured (Farine et al. 2015).
 
-Animal social network analysis is a well-developed tool used to measure the relationships of individuals and organization of social systems (Krause et al.
-2009; Wey et al.
-2008; Croft et al.
-2008).
-Social network analysis provides insight into the structure of social communities and social network properties, which can influence population dynamics and evolutionary processes (Pinter-Wollman et al.
-2014; Kurvers et al.
-2014).
-Despite the widespread use and innovation of traditional social network analysis (Webber & Vander Wal 2019), it typically considers a single scale of sociality in a given network (monolayer), drastically simplifying the potential complexity of animal social systems (Finn et al.
-2019).
-Unlike traditional monolayer social networks, multilayer networks explicitly consider social systems across contexts, including scale-dependent contexts (Pilosof et al.
-2017).
-Multilayer networks are made up of multiple layers, each representing different classes of individuals (e.g.
-male or female), types of behaviours (e.g.
-grooming, travelling, or foraging), spatial areas (e.g.
-local or regional), or temporal windows (e.g.
-daily or seasonal) (Kivela et al.
-2014; Porter 2018).
-Multilayer networks are relatively novel to studies of animal behaviour (Finn et al.
-2019; Silk et al.
-2018), although they have been used to describe multidimensional human social systems, complex transportation networks, and neural networks (Silk et al.
-2018).
-The role of scale within multilayer social networks remains unexplored but provides a unique opportunity to develop novel understanding of variation in the temporal or spatial scales associated with social systems.
+Animal social network analysis is a well-developed tool used to measure the
+relationships of individuals and organization of social systems (Krause et al.
+2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides
+insight into the structure of social communities and social network properties,
+which can influence population dynamics and evolutionary processes
+(Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use
+and innovation of traditional social network analysis (Webber & Vander Wal
+2019), it typically considers a single scale of sociality in a given network
+(monolayer), drastically simplifying the potential complexity of animal social
+systems (Finn et al. 2019). Unlike traditional monolayer social networks,
+multilayer networks explicitly consider social systems across contexts,
+including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks
+are made up of multiple layers, each representing different classes of
+individuals (e.g. male or female), types of behaviours (e.g. grooming,
+travelling, or foraging), spatial areas (e.g. local or regional), or temporal
+windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer
+networks are relatively novel to studies of animal behaviour (Finn et al. 2019;
+Silk et al. 2018), although they have been used to describe multidimensional
+human social systems, complex transportation networks, and neural networks (Silk
+et al. 2018). The role of scale within multilayer social networks remains
+unexplored but provides a unique opportunity to develop novel understanding of
+variation in the temporal or spatial scales associated with social systems.
 
-Our study is motivated by behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al.
-2019).
-We use this case study to address two principal questions associated with scale-dependent multilayer networks.
-First, to what degree does the social scale of relationships, spatial scale of landscapes, and temporal scale of analysis influence our ability to interpret complex social systems?
-Second, can variation in social, spatial, and temporal improve predictions associated with biological differences in seasonal resource availability and social association?
-We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
+Our study is motivated by behavioural, landscape, and spatial ecology to build a
+conceptual and analytical framework for scale-dependent multilayer networks and
+we apply this framework to a case study of caribou (*Rangifer tarandus*) in
+Newfoundland, Canada (Peignier et al. 2019). We use this case study to address
+two principal questions associated with scale-dependent multilayer networks.
+First, to what degree does the social scale of relationships, spatial scale of
+landscapes, and temporal scale of analysis influence our ability to interpret
+complex social systems? Second, can variation in social, spatial, and temporal
+improve predictions associated with biological differences in seasonal resource
+availability and social association? We conclude with perspectives for further
+development and application of scale in multilayer networks with respect to
+landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber &
+Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
 2019).
@@
 ###
-Results and interpretation of temporal scale - balh
+Results and interpretation of temporal scale
 
-Results and interpretation of spatial scale - blah blah
+Results and interpretation of spatial scale
 
-Results and interpretation of social scale - blah blah blah
+Results and interpretation of social scale
 
 ## Perspectives  to advance multilayer networks 
-
 ### Habitat selection and space use
 
-Mayor et al. 2009 paper
-
-MRSF Laforge paper
-
-van Beest et al. 2014 scale paper
-
-1st/2nd/3rd order selection blah blah
-
-Paper: Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
-
-Multi-scale habitat selection modeling: a review and outlook
+* Mayor et al. 2009 paper 
+* MRSF Laforge paper 
+* van Beest et al. 2014 scale paper 
+* 1st/2nd/3rd order selection
+* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
+* Multi-scale habitat selection modeling: a review and outlook
 

### 2020-01-31 paper/manuscript.Rmd
plenty of reflowing

@@
 (monolayer), drastically simplifying the potential complexity of animal social
-systems (Finn et al. 2019). Unlike traditional monolayer social networks,
+systems (Finn et al. 2019).
+
+Unlike traditional monolayer social networks,
 multilayer networks explicitly consider social systems across contexts,
@@
 ### Caribou socioecology
-Here, we use caribou as a case study to develop scale-dependent multilayer networks based on temporal (seasonal), spatial (habitat type), and social (visual and auditory perception).
-Caribou are gregarious ungulates with fission-fusion dynamics (Lesmerises et al.
-2018) that display temporal (Peignier et al.
-2019) and spatial (Webber et al.
-unpublished data) variation in social networks.
-In winter, caribou dig holes in the snow, termed craters to access forage (Bergerud 1974).
-As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to forage than when the landscape is snow-free.
-Importantly, craters exist on the landscape at multiple scales: the crater scale (a single crater), the feeding area scale (multiple craters in close proximity), and the winter range scale (all craters within an individual’s range) (Mayor et al.
-2009).
-The distribution of forage for caribou is therefore seasonally heterogeneous, with greater access in snow-free seasons compared to winter as well as spatially heterogeneous in winter because the distribution of craters on the landscape varies meaning that access to vegetation in winter is highly variable for caribou.
-We therefore partitioned data into two discrete seasons: <!-- TODO update these --> *summer (3 August - 17 October) and winter (1 January – 16 March)* based on caribou socioecology (Peignier et al.
-2019).
+Here, we use caribou as a case study to develop scale-dependent multilayer
+networks based on temporal (seasonal), spatial (habitat type), and social
+(visual and auditory perception). Caribou are gregarious ungulates with
+fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier
+et al. 2019) and spatial (Webber et al. unpublished data) variation in social
+networks. In winter, caribou dig holes in the snow, termed craters to access
+forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters
+once they are established and there is considerably less access to forage than
+when the landscape is snow-free. Importantly, craters exist on the landscape at
+multiple scales: the crater scale (a single crater), the feeding area scale
+(multiple craters in close proximity), and the winter range scale (all craters
+within an individual’s range) (Mayor et al. 2009). The distribution of forage
+for caribou is therefore seasonally heterogeneous, with greater access in
+snow-free seasons compared to winter as well as spatially heterogeneous in
+winter because the distribution of craters on the landscape varies meaning that
+access to vegetation in winter is highly variable for caribou. We therefore
+partitioned data into two discrete seasons: <!-- TODO update these --> *summer
+(3 August - 17 October) and winter (1 January – 16 March)* based on caribou
+socioecology (Peignier et al. 2019).
 
 ### Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2018.
-Adult female caribou were immobilized and fitted with global positioning system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g) as described by Schaefer and Mahoney (2013).
-Collars were programmed to collect location fixes every 2 hours.
-Prior to analyses, we subset GPS fixes into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al.
-(2010).
-We did not collar all female caribou in the herd; however, we assumed that our sample of collared animals was random.
+We used GPS location data collected from Fogo Island caribou in 2018. Adult
+female caribou were immobilized and fitted with global positioning system (GPS)
+collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g)
+as described by Schaefer and Mahoney (2013). Collars were programmed to collect
+location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
+discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al.
+(2010). We did not collar all female caribou in the herd; however, we assumed
+that our sample of collared animals was random.
 
 ### Landscape data and habitat classification
-Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division.
-Available landcover classification included nine habitat types at 30 x 30m resolution.
-We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat.
-Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
+Landscape classification data were provided by the Newfoundland and Labrador
+Wildlife Division. Available landcover classification included nine habitat
+types at 30 x 30m resolution. We distilled the landcover types into three broad
+categories: foraging habitat, open habitat, and closed habitat. Foraging habitat
+consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
+and anthropogenic habitat types, while closed habitat consisted of coniferous
+forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
 Water habitat was excluded from all subsequent analyses.
@@
 
-We generated seasonal multilayer social networks consisting of habitat-specific monolayers.
-Each layer was the social association network generated in one of three habitat types (lichen, open, and closed).
-For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al.
-2019) in *R version* (R Core Team 2020).
+We generated seasonal multilayer social networks consisting of habitat-specific
+monolayers. Each layer was the social association network generated in one of
+three habitat types (lichen, open, and closed). For habitat-specific networks,
+all GPS relocations were assigned to the corresponding habitat type and
+proximity-based social network layers were generated using the R package spatsoc
+(Robitaille et al. 2019) in *R version* (R Core Team 2020).
 
-Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another.
-Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment.
-For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al.
-2019).
-Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al.
-2019; Lesmerises et al.
-2018).
-In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented connections between the same individuals across contexts.
+Within each habitat-specific monolayer network, we assumed individuals were
+associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
+other) were within a given distance of one another. Typically for ungulates and
+other gregarious mammals, the ‘chain rule’ is applied for group assignment. For
+GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes
+buffered by a given distance formed a contiguous buffer for two or more
+individuals, even if some individuals within the buffer were not within the
+given distance of one another (Robitaille et al. 2019). Group assignment based
+on the chain rule has previously been applied to caribou at a distance of 50m
+(Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes
+represented individuals, intralayer edges represented associations between
+individuals in a given habitat type, and interlayer edges represented
+connections between the same individuals across contexts.
 
-We weighted edges of social networks by the strength of association between caribou using the simple ratio index (SRI, Cairns and Schwager 1987):
+We weighted edges of social networks by the strength of association between
+caribou using the simple ratio index (SRI, Cairns and Schwager 1987):
 
@@
 
-where x is the number of fixes where individuals A and B were within a given distance of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by more than the given distance (Farine & Whitehead 2015).
-Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point.
+where x is the number of fixes where individuals A and B were within a given
+distance of each other, y<sub>A</sub> is the number of fixes from individual A
+when individual B did not have a simultaneous fix, y<sub>B</sub> is the number
+of fixes from individual B when individual A did not have a simultaneous fix,
+and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B
+that were separated by more than the given distance (Farine & Whitehead 2015).
+Social groups were designated if two or more individuals occurred within a given
+distance of one another at any given time point.
 
@@
 
-For each multilayer network, we calculated four metrics.These included: multidegree, graph strength, redundancy/relevance, and  layer similarity.
-GOING TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON EXPLAINING THESE).
+For each multilayer network, we calculated four metrics.These included:
+multidegree, graph strength, redundancy/relevance, and  layer similarity.  GOING
+TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
+EXPLAINING THESE).
 
-ALR: Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."
+ALR: Reference for extending degree centrality to multilayer, neighbors,
+connective redundancy and relevance: Berlingerio 2011 "Foundations of
+multidimensional..."
 
@@
 * Neighbors/neighborhood (number of unique actors directly connected to each focal)
+
 Neighbors = degree within a network layer
@@
 
-* eigenvector centrality, summed across layers as described in Boccaletti, Stefano, et al. "The structure and dynamics of multilayer networks." Physics Reports 544.1 (2014): 1-122.
+* eigenvector centrality, summed across layers as described in Boccaletti,
+Stefano, et al. "The structure and dynamics of multilayer networks." Physics
+Reports 544.1 (2014): 1-122.
 
@@
 
-We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?).
-Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m.
-For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.
+We altered social scale based on visual (short distance) and auditory (long
+distnace) sensory modalities of caribou (REF?). Specifically, we modified the
+distance threshold required for group assignment (see above) and re-assigned
+groups at incremental distance between 5-500m. For example, at the finest social
+scale, only individuals within 5m of one another were considered in the same
+group, whereas at the coarset social scale, only individuals within 500m of one
+another were considered in the same group.
 
@@
 
-To assess the influence of spatial scale on multilayer networks, we re-sampled our landcover classification map at varying scales.
-Specifically, we selected scales relevant to caribou ecology.
-We re-sampled landcover using the `grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m, 1000m, 2500m.
-Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
-2017).
-Resampling occurred based on a modal moving window method, where **XXXXX.
-[ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
+To assess the influence of spatial scale on multilayer networks, we re-sampled
+our landcover classification map at varying scales. Specifically, we selected
+scales relevant to caribou ecology. We re-sampled landcover using the
+`grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m,
+1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
+caribou during foraging (REF), while re-sampling at 1000m and 2500m represents
+the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
+et al. 2017). Resampling occurred based on a modal moving window method, where
+**XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
 
-For each landcover (the original resolution and modal resampled resolutions), seasonal network layers are combined in a multilayer network
-<!-- Each modal landcover, and the original are sampled and separate network layers constructed for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
+For each landcover (the original resolution and modal resampled resolutions),
+seasonal network layers are combined in a multilayer network <!-- Each modal
+landcover, and the original are sampled and separate network layers constructed
+for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
 
@@
 
-We altered the temporal scale of mutlilayer networks using a moving time-window approach to define seasons.
+We altered the temporal scale of mutlilayer networks using a moving time-window
+approach to define seasons.
 
@@
 
-Varying length of time window (used to define seasons).
-Starting with a window of day 1-40 and using a moving window to go to day 1-100.
-Fixed start julian day for winter is day 1 and for summer is 215.
-Network layers for winter and summer are calculated for each window length.
+Varying length of time window (used to define seasons). Starting with a window
+of day 1-40 and using a moving window to go to day 1-100. Fixed start julian day
+for winter is day 1 and for summer is 215. Network layers for winter and summer
+are calculated for each window length.
 
 1. time window position
-Varying position of time window (used to define seasons).
-Fixed length at 48 Window positions starting at 1, to + 48 So 1-48 is first iteration for winter and 48-96 is second iteration for "winter".
-Same for summer, starting at 215.
+Varying position of time window (used to define seasons). Fixed length at 48
+Window positions starting at 1, to + 48 So 1-48 is first iteration for winter
+and 48-96 is second iteration for "winter". Same for summer, starting at 215.
 Network layers for each season are constructed.
 
-**Observational scale** (temorary header): Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al.
-2018; Webber and Vander Wal 2019).
+**Observational scale** (temorary header): Studies of social network analysis
+vary in the number and frequency of observations as well as the data collection
+technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
+2019).
 
-Randomly select max number of observations - timegroups -  (right now 750).
-For each iteration, include n observations for each season for all individuals.
-Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity.
-Parallels with observation data.
+Randomly select max number of observations - timegroups -  (right now 750). For
+each iteration, include n observations for each season for all individuals.
+Subsequent iterations include nstep more (right now 25), along with previously
+included to remove stochasticity. Parallels with observation data.
 
@@
 ### Each metric's interpretation
-* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
-* Degree deviation: deviation of degree across layers.
-High degree deviation = large difference between degree for an individual across layers.
-Low degree deviation = individuals are similarly connected across layers.
-* Graph strength: weighted version of degree. High graph strength = highly connected. Not summed in this case across layers. 
-* Neighbors: number of unique individuals adjacent to each actor. Considered in a single layer, this is equal to the degree. 
-* Neighborhood: number of unique individuals across all layers. High neighborhood = a high number of unique individuals connected to an actor. 
-* Relevance: layer centric metric, corresponding to the number of neighbors on a layer divided by the total neighborhood for each actor.
-High relevance means that the layer is highly relevant to the individuals connections.
-A low relevance means this layer does not contribute many neighbors to an individuals overall neighborhood.
-* Connective redundancy: the total multilayer neighborhood divided by the multidegree.
-High connective redundancy indicates a multilayer network that has many repeated edges across layers between an actor and its neighbours.
-Low connective redundancy indicates that each layer is important for preserving all social ties.
-* Layer similarily: how similar each layer is (Brodka 2018). Pearson's correlation coefficient of degree vectors for each layer, comparing each landcover across seasons.
+* Multidegree: sum of degree across layers. High multidegree = connected to many
+individuals across layers. Low multidegree = not connected to many individuals
+across layers.
+
+* Degree deviation: deviation of degree across layers. High degree deviation =
+large difference between degree for an individual across layers. Low degree
+deviation = individuals are similarly connected across layers.
+
+* Graph strength: weighted version of degree. High graph strength = highly
+connected. Not summed in this case across layers.
+
+* Neighbors: number of unique individuals adjacent to each actor. Considered in
+a single layer, this is equal to the degree.
+
+* Neighborhood: number of unique individuals across all layers. High
+neighborhood = a high number of unique individuals connected to an actor.
+
+* Relevance: layer centric metric, corresponding to the number of neighbors on a
+layer divided by the total neighborhood for each actor. High relevance means
+that the layer is highly relevant to the individuals connections. A low
+relevance means this layer does not contribute many neighbors to an individuals
+overall neighborhood.
+
+* Connective redundancy: the total multilayer neighborhood divided by the
+multidegree. High connective redundancy indicates a multilayer network that has
+many repeated edges across layers between an actor and its neighbours. Low
+connective redundancy indicates that each layer is important for preserving all
+social ties.
+
+* Layer similarily: how similar each layer is (Brodka 2018). Pearson's
+correlation coefficient of degree vectors for each layer, comparing each
+landcover across seasons.
 
@@
 
-Social network positions are frequently used to represent the social environment that an individual experiences or their social phenotype.
-Social phenotypes are increasingly linked to important fitness for individuals of various species, including primates (e.g.
-Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019), dolphins (e.g.
-Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds (e.g.
-McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012).
-The effect of scale on the relationship between an individual’s social network position and fitness may depend on the hypotheses being tested and logistical constraints.
-Two scales that are important for understanding fitness consequences in the context of social network positions are temporal and social scales (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
+Social network positions are frequently used to represent the social environment
+that an individual experiences or their social phenotype. Social phenotypes are
+increasingly linked to important fitness for individuals of various species,
+including primates (e.g. Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019),
+dolphins (e.g. Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds
+(e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). The effect
+of scale on the relationship between an individual’s social network position and
+fitness may depend on the hypotheses being tested and logistical constraints.
+Two scales that are important for understanding fitness consequences in the
+context of social network positions are temporal and social scales (Almeling,
+Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître,
+Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
 
-Social network structure depends on the timeframe of observation, which can make networks difficult to compare (Castles et al., 2014).
-Furthermore, social network structure can vary seasonally and indicate social environments that an individual experiences (e.g.
-Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018).
-Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).
-**[QW: I'm not sure what this paragraph adds - I think if we need to save space we could cut it]**
+Social network structure depends on the timeframe of observation, which can make
+networks difficult to compare (Castles et al., 2014). Furthermore, social
+network structure can vary seasonally and indicate social environments that an
+individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede,
+Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, &
+Watts, 2012), or they can be consistent across time, which can be used to
+reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, &
+Shultz, 2018). Seasonal fluctuations have the potential to have disease
+transmission and fitness effects for individuals (Balasubramaniam et al., 2019;
+Chen et al., 2014). **[QW: I'm not sure what this paragraph adds - I think if we
+need to save space we could cut it]**
 
-In long-lived species, social phenotypes can change over their lifetimes in ways that can affect fitness (Berger et al., 2015; Brent et al., 2017).
-These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotype and fitness.
-Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018).
-This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social phenotype over different stages of ontogeny even more difficult.
-However, considering fine temporal scales may provide insight across development stages that may otherwise be missed (CITE-myself??).
-Multilayer networks provide a framework to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017).
-Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.
+In long-lived species, social phenotypes can change over their lifetimes in ways
+that can affect fitness (Berger et al., 2015; Brent et al., 2017). These
+findings highlight the necessity to carefully consider the temporal scale that
+is meaningful for the proposed hypotheses, especially for understanding the
+relationship between an individuals social phenotype and fitness. Further
+complicating the issue, social phenotypes can change over stages of ontogeny,
+although it is important to note that individuals progress through development
+at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This
+variation can make defining appropriate temporal scales for testing the fitness
+implications of an individual’s social phenotype over different stages of
+ontogeny even more difficult. However, considering fine temporal scales may
+provide insight across development stages that may otherwise be missed
+(CITE-myself??). Multilayer networks provide a framework to test hypotheses
+linking social phenotypes and fitness across temporal scales. Because of the
+non-independent nature of social interactions and associations, especially over
+time, it is hard to test hypotheses about social dynamics with a suitable null
+control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of
+multilayer networks, making layers of different temporal periods provides a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods.
 
-Social scale is another major consideration for social network analysis, especially in the context of different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
-It is a common trope that individuals must be associating to interact and most studies therefore assume that proximity is proxy for interacting (Farine, 2015).
-For instance, baboons need to be in proximity in order to groom each other, but this trope highlights human bias toward interactions that can be readily observed in the field.
-Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015).
-With the advancement of bio-logging technology, we have the ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017).
-The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good social proximity is as a proxy for social interactions in a holistic way.
+Social scale is another major consideration for social network analysis,
+especially in the context of different types of interactions and associations in
+the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine,
+2015). It is a common trope that individuals must be associating to interact and
+most studies therefore assume that proximity is proxy for interacting (Farine,
+2015). For instance, baboons need to be in proximity in order to groom each
+other, but this trope highlights human bias toward interactions that can be
+readily observed in the field. Animals have certain interactions that do not
+require proximity such as long-distance vocalization and olfactory signals
+(Carter et al., 2015). With the advancement of bio-logging technology, we have
+the ability to record social interactions that do not require proximity,
+particularly long-distance communication networks with devices like microphone
+arrays (Snijders & Naguib, 2017). The multilayer network framework further
+enables researchers to examine the relationship between social phenotypes and
+fitness across social scales and to test how good social proximity is as a proxy
+for social interactions in a holistic way.
 
-These different social scales can have different fitness repercussions for individuals.
-Rhesus macaques (*Macaca mulatta*) that had stronger, more stable social associates and grooming partners, but not more social partners, had higher survivorship than those who did not (Ellis, Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019).
-This finding highlights the need to investigate the effect of temporal and social scales on the relationship between social network positions and fitness.
-Multilayer networks provide an avenue to do so considering the whole social system rather than just one type of social interaction at a time, which is what has been done under most circumstances but is not very realistic.
+These different social scales can have different fitness repercussions for
+individuals. Rhesus macaques (*Macaca mulatta*) that had stronger, more stable
+social associates and grooming partners, but not more social partners, had
+higher survivorship than those who did not (Ellis, Snyder-Mackler,
+Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights the need to
+investigate the effect of temporal and social scales on the relationship between
+social network positions and fitness. Multilayer networks provide an avenue to
+do so considering the whole social system rather than just one type of social
+interaction at a time, which is what has been done under most circumstances but
+is not very realistic.
 
-Multilayer networks further provide unique challenges and opportunities for understanding the social phenotypes and environments of individuals and their fitness outcomes.
-Picking the proper temporal scale is important but a challenge because all layers in the multilayer network should reflect the same time period, and the period should be long enough for each layer to have enough data for robust networks (Farine, 2017).
-These considerations may be limiting factors when answering questions that require timeframes that are relevant to different individuals.
-On the other hand, multilayer network metrics provide an opportunity to simplify statistical models.
-Interactions that happen meters apart, proximity associations, and long-distance interactions can be encapsulated in a single multilayer network, and a single metric can be used to describe the various social scales of an individual’s network position.
-This multilevel network metric could be used to assess the relationship between an individual's social phenotype and fitness.
-It would also be a meaningful simplification of many network metrics that could help simplify statistical analyses and deal with the frequent correlations between social network metrics in different types of networks (Castles et al., 2014).
+Multilayer networks further provide unique challenges and opportunities for
+understanding the social phenotypes and environments of individuals and their
+fitness outcomes. Picking the proper temporal scale is important but a challenge
+because all layers in the multilayer network should reflect the same time
+period, and the period should be long enough for each layer to have enough data
+for robust networks (Farine, 2017). These considerations may be limiting factors
+when answering questions that require timeframes that are relevant to different
+individuals. On the other hand, multilayer network metrics provide an
+opportunity to simplify statistical models. Interactions that happen meters
+apart, proximity associations, and long-distance interactions can be
+encapsulated in a single multilayer network, and a single metric can be used to
+describe the various social scales of an individual’s network position. This
+multilevel network metric could be used to assess the relationship between an
+individual's social phenotype and fitness. It would also be a meaningful
+simplification of many network metrics that could help simplify statistical
+analyses and deal with the frequent correlations between social network metrics
+in different types of networks (Castles et al., 2014).
 
@@
 
-Animal movement undoubtedly affects an individual's social environment (Strandburg-Peshkin et al.
-2015).
-Movement is a dynamic process that is related to the resources an individual consumes within their home range and the space that they use (Van Moorter et al.
-2016).
-Collective movement can reduce group-level predation via detection-dilution trade-offs and improve information transfer about the quality or location of resources to other group members (Jolles et al.
-2019).
-Social processes, movement decisions, and space use are inextricably linked and multilayer networks represent a potential analytical framework for linking these processes (e.g.
-Mourier et al.
-2019).
+Animal movement undoubtedly affects an individual's social environment
+(Strandburg-Peshkin et al. 2015). Movement is a dynamic process that is related
+to the resources an individual consumes within their home range and the space
+that they use (Van Moorter et al. 2016). Collective movement can reduce
+group-level predation via detection-dilution trade-offs and improve information
+transfer about the quality or location of resources to other group members
+(Jolles et al. 2019). Social processes, movement decisions, and space use are
+inextricably linked and multilayer networks represent a potential analytical
+framework for linking these processes (e.g. Mourier et al. 2019).
 
 Although multilayer animal social networks are relatively novel (Silk et al.
-2018), movement behaviour within multilayer networks has already been considered in a couple studies.
-In vulturine gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate *monolayer* association networks within a multilayer network (Papageorgiou et al.
-2019).
-In addition, *spatial networks* are physical locations (nodes) which are connected in a network when individuals move between said locations (edges).
-For example, spatial networks were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus melanopterus*) between fixed location autonomous arrays.
-In this example, nodes represent locations within the array, *intralayer edges* represent individual movement frequency, and *interlayer edges* represent contact probability among individuals at a given node (Mourier et al.
-2019).
-While both studies integrate movement in some capacity, neither generate networks based on continuous measures of dyadic or collective movement (Long et al.
-2014).
+2018), movement behaviour within multilayer networks has already been considered
+in a couple studies. In vulturine gunieafowl (*Acryllium vulturinum*), GPS
+movement data were used to generate *monolayer* association networks within a
+multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks*
+are physical locations (nodes) which are connected in a network when individuals
+move between said locations (edges). For example, spatial networks were applied
+to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
+melanopterus*) between fixed location autonomous arrays. In this example, nodes
+represent locations within the array, *intralayer edges* represent individual
+movement frequency, and *interlayer edges* represent contact probability among
+individuals at a given node (Mourier et al. 2019). While both studies integrate
+movement in some capacity, neither generate networks based on continuous
+measures of dyadic or collective movement (Long et al. 2014).
 
-In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks can represent continuous and simultaneous movement trajectories of multiple animals.
-Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al.
-2015, 2017) and across scales.
-A collective movement layer could constitute similarity in movement for dyads (Long et al.
-2014) or groups (Bode et al.
-2011).
-This movement layer could be made at a fine (i.e.
-minute-to-minute: Cleasby et al.
-2019) or coarse scale (global migration: Flack et al.
-2018).
-Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g.
-Muller et al.
-2018; Finn et al.
-2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g.
-Smith-Aguilar et al.
-2019).
-Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al.
-2018).
+In contrast to spatial networks, where nodes represent spatial locations that
+are fixed in space, movement networks can represent continuous and simultaneous
+movement trajectories of multiple animals. Continuous collection of animal
+relocation data using GPS technology can be used to measure how groups of
+animals make collective movement decisions in the context of their local
+environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
+collective movement layer could constitute similarity in movement for dyads
+(Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be
+made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
+(global migration: Flack et al. 2018). Another potential application would be to
+generate social networks during times when animals are engaged in different
+behaviours, including traveling, interacting, or foraging (e.g. Muller et al.
+2018; Finn et al. 2019) and construct a multilayer network based on
+behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019).
+Importantly, the key to incorporating movement in multilayer networks across
+scales is the technological advancements available to overcome previous
+limitations (see Hughey et al. 2018).
 
-Given the existing framework for constructing multilayer networks from behavioural layers (e.g.
-Smith-Aguilar et al.
-2019), movement layers could be integrated with interaction or association layers.
-Integrating movement layers with habitat-specific social association layers could further shed light on the role of movement as a driver of the social and spatial environments an individual experiences (Webber and Vander Wal 2018).
-In our case study, we generated multilayer networks based on habitat-specific monolayers.
-Coordinated movement of dyads, or groups, could vary based on habitat, and the approach we outline could be used to explore mechanisms linking the social and spatial environments.
-For example, social processes may be an emergent property of the landscape because animals aggregate at resources, such as waterholes (Chamaillé-Jammes et al.
-2008).
-Movement to, from, or within habitat patches  or territories can also contribute to the formation of the social environment (Spiegel et al.
-2016).
-For example, in sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range edges, presumably driving territorial behaviour (Spiegel et al.
-2018).
-Incorporating movement ecology within a multilayer network framework is a logical next step for a burgeoning field.
-In particular, when association networks are habitat-specific, we suggest the integration of movement and space use in multilayer networks provides novel insights into the effects of habitat configuration on the formation of the social environment (He et al.
-2019).
+Given the existing framework for constructing multilayer networks from
+behavioural layers (e.g. Smith-Aguilar et al. 2019), movement layers could be
+integrated with interaction or association layers. Integrating movement layers
+with habitat-specific social association layers could further shed light on the
+role of movement as a driver of the social and spatial environments an
+individual experiences (Webber and Vander Wal 2018). In our case study, we
+generated multilayer networks based on habitat-specific monolayers. Coordinated
+movement of dyads, or groups, could vary based on habitat, and the approach we
+outline could be used to explore mechanisms linking the social and spatial
+environments. For example, social processes may be an emergent property of the
+landscape because animals aggregate at resources, such as waterholes
+(Chamaillé-Jammes et al. 2008). Movement to, from, or within habitat patches  or
+territories can also contribute to the formation of the social environment
+(Spiegel et al. 2016). For example, in sleepy lizards (*Tiliqua rugosa*) males
+interacted primarily at home range edges, presumably driving territorial
+behaviour (Spiegel et al. 2018). Incorporating movement ecology within a
+multilayer network framework is a logical next step for a burgeoning field. In
+particular, when association networks are habitat-specific, we suggest the
+integration of movement and space use in multilayer networks provides novel
+insights into the effects of habitat configuration on the formation of the
+social environment (He et al. 2019).
 
@@
 
-Silk et al.
-(2018) presented some key multilayer questions in animal behaviour research.
-While these questions represent an important starting point for multilayer networks, we present an additional set of questions relevant to the promise and problem of scale in mutlilayer networks:
+Silk et al. (2018) presented some key multilayer questions in animal behaviour
+research. While these questions represent an important starting point for
+multilayer networks, we present an additional set of questions relevant to the
+promise and problem of scale in mutlilayer networks:
 
-  1) How do social phenotypes across scales differently influence fitness? Are some temporal or social scales better predictors for different fitness metrics?
+1. How do social phenotypes across scales differently influence fitness? Are
+some temporal or social scales better predictors for different fitness metrics?
 
-  2) Why do individuals associate more strongly with certain conspecifics in some habitats? What, if any, is the role of movement in the context of habitat networks?
+1. Why do individuals associate more strongly with certain conspecifics in some
+habitats? What, if any, is the role of movement in the context of habitat
+networks?
 
-  3) How, and why, does the spatial scale of perception influence, e.g.
-auditory, visual, or chemotaxis, influence the  social environment across scales?
-What is the role of memory, and by extension social and spatial cognition, as animals navigate their environment and make decisions about where to move next?
+1. How, and why, does the spatial scale of perception influence, e.g. auditory,
+visual, or chemotaxis, influence the  social environment across scales? What is
+the role of memory, and by extension social and spatial cognition, as animals
+navigate their environment and make decisions about where to move next?
 
@@
 We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
-Kingdon, S.
-Boyle,  C.
-Prokopenko, I.
-Richmond, J.
-Hogg, and L.
-Newediuk for their comments on previous versions of this manuscript as well as D.
-Schneider for inspiration and helpful discussions about scale.
-Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.
+Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
+their comments on previous versions of this manuscript as well as D. Schneider
+for inspiration and helpful discussions about scale. Funding for this study was
+provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
+Grant to EVW.
 

### 2020-01-31 paper/manuscript.Rmd
use forest not closed

@@
 types at 30 x 30m resolution. We distilled the landcover types into three broad
-categories: foraging habitat, open habitat, and closed habitat. Foraging habitat
+categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
 consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
-and anthropogenic habitat types, while closed habitat consisted of coniferous
+and anthropogenic habitat types, while forest habitat consisted of coniferous
 forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
@@
 monolayers. Each layer was the social association network generated in one of
-three habitat types (lichen, open, and closed). For habitat-specific networks,
+three habitat types (lichen, open, and forest). For habitat-specific networks,
 all GPS relocations were assigned to the corresponding habitat type and

### 2020-01-31 paper/manuscript.Rmd
tidy net mets

@@
 For each multilayer network, we calculated four metrics.These included:
-multidegree, graph strength, redundancy/relevance, and  layer similarity.  GOING
+multidegree, graph strength, redundancy/relevance, and  layer similarity.
+
+<!-- GOING
 TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
 EXPLAINING THESE).
+-->
 
+<!-- 
 ALR: Reference for extending degree centrality to multilayer, neighbors,
@@
 multidimensional..."
+-->
 
-##### Multidegree
-
+* Multidegree
 * Degree centrality
@@
 * Degree deviation: standard deviation of degree across layers
-
-* Neighbors/neighborhood (number of unique actors directly connected to each focal)
-
-Neighbors = degree within a network layer
+* Neighbors/neighborhood (number of unique actors directly connected to each focal): Neighbors = degree within a network layer.
 But across a multilayer network with multiple layers, some neighbors are repeated.
-
-##### Graph strength
-
-Finally, some weighted variables:
-
-* eigenvector centrality, summed across layers as described in Boccaletti,
-Stefano, et al. "The structure and dynamics of multilayer networks." Physics
-Reports 544.1 (2014): 1-122.
-
-##### Redundancy/relevance
-
+* Graph strength
 * Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties
-
 * Relevance: neighborhood of specific layer  / neighbourhood of full ml net.
@@
 Comparing across, it tells you which layers are most important for each individual.
-
-##### Layer similarity
-
-Then there will be some layer similarity. Right now it's just a correlation of each season's asnipe SRI matrix
+* layer similarity
 

### 2020-01-31 paper/manuscript.Rmd
more portable y_{}

@@
 where x is the number of fixes where individuals A and B were within a given
-distance of each other, y<sub>A</sub> is the number of fixes from individual A
-when individual B did not have a simultaneous fix, y<sub>B</sub> is the number
+distance of each other, $y_{A}$ is the number of fixes from individual A
+when individual B did not have a simultaneous fix, $y_{B}$ is the number
 of fixes from individual B when individual A did not have a simultaneous fix,
-and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B
+and $y_{AB}$ is the number of simultaneous fixes from individuals A and B
 that were separated by more than the given distance (Farine & Whitehead 2015).

### 2020-01-31 paper/manuscript.Rmd
tidy manuscript

@@
 We altered social scale based on visual (short distance) and auditory (long
-distnace) sensory modalities of caribou (REF?). Specifically, we modified the
+distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified the
 distance threshold required for group assignment (see above) and re-assigned
@@
 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
-caribou during foraging (REF), while re-sampling at 1000m and 2500m represents
+caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents
 the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
@@
 
-**Observational scale** (temorary header): Studies of social network analysis
+**Observational scale** <!--(temorary header)-->: Studies of social network analysis
 vary in the number and frequency of observations as well as the data collection
@@
 
-Randomly select max number of observations - timegroups -  (right now 750). For
+Randomly select max number of observations - timegroups - <!-- (right now 750)-->. For
 each iteration, include n observations for each season for all individuals.
-Subsequent iterations include nstep more (right now 25), along with previously
+Subsequent iterations include nstep more <!--(right now 25)-->, along with previously
 included to remove stochasticity. Parallels with observation data.
@@
 transmission and fitness effects for individuals (Balasubramaniam et al., 2019;
-Chen et al., 2014). **[QW: I'm not sure what this paragraph adds - I think if we
-need to save space we could cut it]**
+Chen et al., 2014). <!-- **[QW: I'm not sure what this paragraph adds - I think if we
+need to save space we could cut it]**-->
 
@@
 
+<!-- add jack -->
+
 We thank all members of the Wildlife Evolutionary Ecology Lab, including K.

### 2020-01-31 paper/manuscript.Rmd
try knitcitations

@@
 
-references: ../references/refs.bib
+references: ../references/knitcite.bib
 ---
@@
 )
+
+library(knitcitations)
+options("citation_format" = "pandoc")
 ```
@@
 Our inference regarding the ecological processes underlying ecological patterns
-are directly linked to the scale at which they are observed (Levin 1992; Allen
+are directly linked to the scale at which they are observed `r citep("10.2307/1941447")` (Levin 1992; Allen
 et al. 2015). Animals are influenced across scales, through processes such as
@@
 ## References
+
+```{r, message=FALSE}
+write.bibtex(file="../references/knitcite.bib")
+```

### 2020-02-02 paper/manuscript.Rmd
it's bibliography: not references:

@@
 header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
-
 output: 
-    bookdown::word_document2:
-      reference_docx: template.docx
-    # github_document
-
-references: ../references/knitcite.bib
+    # bookdown::word_document2:
+      # reference_docx: template.docx
+    github_document
+bibliography: ../references/knitcite.bib
 ---

### 2020-02-02 paper/manuscript.Rmd
try knitcitations

@@
 Our inference regarding the ecological processes underlying ecological patterns
-are directly linked to the scale at which they are observed `r citep("10.2307/1941447")` (Levin 1992; Allen
-et al. 2015). Animals are influenced across scales, through processes such as
-species-specific as trophic interactions and resource availability (Legendre
-1993; Chave 2013) and global climate and productivity (Field et al. 2009).
+are directly linked to the scale at which they are observed `r citep(c('10.2307/1941447', '10.7312/alle06918'))`. Animals are influenced across scales, through processes such as
+species-specific as trophic interactions and resource availability `r citep(c('10.2307/1939924', '10.1111/ele.12048'))` and global climate and productivity `r citep('10.1111/j.1365-2699.2008.01963.x')`.
 Multiscale ecology has been integrated into species distribution modelling
-(Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs
-(Sugihara et al. 1989). Meanwhile, in the context of animal behaviour, certain
+`r citep('10.1146/annurev.ecolsys.110308.120159')`, habitat selection `r citep('10.1890/06-1672.1')`, and food webs
+`r citep('10.1126/science.2740915')`. Meanwhile, in the context of animal behaviour, certain
 behaviours are scale dependent, for example, acoustic communication in birds
-occurs over variable spatial scales (Luther 2009). We posit that animal
+occurs over variable spatial scales `r citep('10.1093/beheco/arp074')`. We posit that animal
 behaviour and, more specifically, the social environment that animals experience
@@
 ```{r, message=FALSE}
-write.bibtex(file="../references/knitcite.bib")
+write.bibtex(file = "../references/knitcite.bib")
 ```

### 2020-02-02 paper/citations.R
fst citations.R

@@ -1,0 +1,20 @@
+# Package
+library(knitcitations)
+
+# levin, allen
+citep(c('10.2307/1941447', '10.7312/alle06918'))
+
+# legendre 93, chave 2013
+citep(c('10.2307/1939924', '10.1111/ele.12048')) 
+
+# field 2009
+citep('10.1111/j.1365-2699.2008.01963.x')
+
+# eli 2009, mayo2007, sugihara 1989
+citep('10.1146/annurev.ecolsys.110308.120159')
+citep('10.1890/06-1672.1')
+citep('10.1126/science.2740915')
+
+# luthe2009
+citep('10.1093/beheco/arp074')
+

### 2020-02-02 paper/manuscript.Rmd
rm `r citep...`, for auto gen @Author_Year

@@
 Our inference regarding the ecological processes underlying ecological patterns
-are directly linked to the scale at which they are observed `r citep(c('10.2307/1941447', '10.7312/alle06918'))`. Animals are influenced across scales, through processes such as
-species-specific as trophic interactions and resource availability `r citep(c('10.2307/1939924', '10.1111/ele.12048'))` and global climate and productivity `r citep('10.1111/j.1365-2699.2008.01963.x')`.
-Multiscale ecology has been integrated into species distribution modelling
-`r citep('10.1146/annurev.ecolsys.110308.120159')`, habitat selection `r citep('10.1890/06-1672.1')`, and food webs
-`r citep('10.1126/science.2740915')`. Meanwhile, in the context of animal behaviour, certain
+are directly linked to the scale at which they are observed [@Levin_1993; @Allen_2015]. Animals are influenced across scales, through processes such as
+species-specific as trophic interactions and resource availability [@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
+Multiscale ecology has been integrated into species distribution modelling [@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs.
+Meanwhile, in the context of animal behaviour, certain
 behaviours are scale dependent, for example, acoustic communication in birds
-occurs over variable spatial scales `r citep('10.1093/beheco/arp074')`. We posit that animal
+occurs over variable spatial scales [@Luther_2009]. We posit that animal
 behaviour and, more specifically, the social environment that animals experience
@@
 Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
-their comments on previous versions of this manuscript as well as D. Schneider
+their comments on previous versions of this manuscript as well as D. C. Schneider
 for inspiration and helpful discussions about scale. Funding for this study was

### 2020-02-02 paper/citations.R
write bibtex out

@@ -1,6 +1,7 @@
 # Package
 library(knitcitations)
 
+
 # levin, allen
 citep(c('10.2307/1941447', '10.7312/alle06918'))
 
@@ -18,3 +19,5 @@ citep('10.1126/science.2740915')
 # luthe2009
 citep('10.1093/beheco/arp074')
 
+
+write.bibtex(file = "references/knitcite.bib")

### 2020-02-02 paper/manuscript.Rmd
reorg social, spatial, temp in case study

@@
 Our inference regarding the ecological processes underlying ecological patterns
-are directly linked to the scale at which they are observed [@Levin_1993; @Allen_2015]. Animals are influenced across scales, through processes such as
-species-specific as trophic interactions and resource availability [@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
-Multiscale ecology has been integrated into species distribution modelling [@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs.
-Meanwhile, in the context of animal behaviour, certain
-behaviours are scale dependent, for example, acoustic communication in birds
-occurs over variable spatial scales [@Luther_2009]. We posit that animal
-behaviour and, more specifically, the social environment that animals experience
-must also be scale-dependent.
+are directly linked to the scale at which they are observed [@Levin_1993;
+@Allen_2015]. Animals are influenced across scales, through processes such as
+species-specific as trophic interactions and resource availability
+[@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
+Multiscale ecology has been integrated into species distribution modelling
+[@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs.
+Meanwhile, in the context of animal behaviour, certain behaviours are scale
+dependent, for example, acoustic communication in birds occurs over variable
+spatial scales [@Luther_2009]. We posit that animal behaviour and, more
+specifically, the social environment that animals experience must also be
+scale-dependent.
 
@@
 
-Unlike traditional monolayer social networks,
-multilayer networks explicitly consider social systems across contexts,
-including scale-dependent contexts (Pilosof et al. 2017). Multilayer networks
-are made up of multiple layers, each representing different classes of
-individuals (e.g. male or female), types of behaviours (e.g. grooming,
-travelling, or foraging), spatial areas (e.g. local or regional), or temporal
-windows (e.g. daily or seasonal) (Kivela et al. 2014; Porter 2018). Multilayer
-networks are relatively novel to studies of animal behaviour (Finn et al. 2019;
-Silk et al. 2018), although they have been used to describe multidimensional
-human social systems, complex transportation networks, and neural networks (Silk
-et al. 2018). The role of scale within multilayer social networks remains
-unexplored but provides a unique opportunity to develop novel understanding of
-variation in the temporal or spatial scales associated with social systems.
+Unlike traditional monolayer social networks, multilayer networks explicitly
+consider social systems across contexts, including scale-dependent contexts
+(Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
+representing different classes of individuals (e.g. male or female), types of
+behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local
+or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014;
+Porter 2018). Multilayer networks are relatively novel to studies of animal
+behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to
+describe multidimensional human social systems, complex transportation networks,
+and neural networks (Silk et al. 2018). The role of scale within multilayer
+social networks remains unexplored but provides a unique opportunity to develop
+novel understanding of variation in the temporal or spatial scales associated
+with social systems.
 
@@
 Here, we use caribou as a case study to develop scale-dependent multilayer
-networks based on temporal (seasonal), spatial (habitat type), and social
-(visual and auditory perception). Caribou are gregarious ungulates with
-fission-fusion dynamics (Lesmerises et al. 2018) that display temporal (Peignier
-et al. 2019) and spatial (Webber et al. unpublished data) variation in social
-networks. In winter, caribou dig holes in the snow, termed craters to access
+networks based on social (visual and auditory perception), spatial (habitat
+type), and temporal (seasonal). Caribou are gregarious ungulates with
+fission-fusion dynamics (Lesmerises et al. 2018) that display temporal [@Peignier_2019] and spatial (Webber et al. unpublished data) variation in social
+networks. In winter, caribou dig holes in the snow, termed craters, to access
 forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters

### 2020-02-02 paper/citations.R
some cites caribou socioecology

@@ -1,7 +1,9 @@
-# Package
+### Packages ----
 library(knitcitations)
 
 
+### Sections ----
+## Introduction
 # levin, allen
 citep(c('10.2307/1941447', '10.7312/alle06918'))
 
@@ -20,4 +22,14 @@ citep('10.1126/science.2740915')
 citep('10.1093/beheco/arp074')
 
 
+## Case study
+## Caribou socioecology
+# TODO: Lesmerises 2018
+
+# peignier
+citep('10.1002/ece3.5071')
+
+
+
+### Write out bib ----
 write.bibtex(file = "references/knitcite.bib")

### 2020-02-02 paper/manuscript.Rmd
include variables?
fix season dates

@@
 options("citation_format" = "pandoc")
+
+source('../scripts/0-variables.R')
 ```
@@
 type), and temporal (seasonal). Caribou are gregarious ungulates with
-fission-fusion dynamics (Lesmerises et al. 2018) that display temporal [@Peignier_2019] and spatial (Webber et al. unpublished data) variation in social
-networks. In winter, caribou dig holes in the snow, termed craters, to access
-forage (Bergerud 1974). As a result, caribou tend to occupy and re-use craters
-once they are established and there is considerably less access to forage than
-when the landscape is snow-free. Importantly, craters exist on the landscape at
-multiple scales: the crater scale (a single crater), the feeding area scale
-(multiple craters in close proximity), and the winter range scale (all craters
-within an individual’s range) (Mayor et al. 2009). The distribution of forage
-for caribou is therefore seasonally heterogeneous, with greater access in
+fission-fusion dynamics (Lesmerises et al. 2018) that display temporal
+[@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
+social networks. In winter, caribou dig holes in the snow, termed craters, to
+access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use
+craters once they are established and there is considerably less access to
+forage than when the landscape is snow-free. Importantly, craters exist on the
+landscape at multiple scales: the crater scale (a single crater), the feeding
+area scale (multiple craters in close proximity), and the winter range scale
+(all craters within an individual’s range) [@Mayor_2009]. The distribution of
+forage for caribou is therefore seasonally heterogeneous, with greater access in
 snow-free seasons compared to winter as well as spatially heterogeneous in
@@
 access to vegetation in winter is highly variable for caribou. We therefore
-partitioned data into two discrete seasons: <!-- TODO update these --> *summer
-(3 August - 17 October) and winter (1 January – 16 March)* based on caribou
-socioecology (Peignier et al. 2019).
+partitioned data into two discrete seasons:  *summer (3 August - 20 September)
+and winter (1 January – 17 February)* based on caribou socioecology
+[@Peignier_2019].
 

### 2020-02-02 paper/citations.R
add socioecology and location refs/todos

@@ -23,11 +23,22 @@ citep('10.1093/beheco/arp074')
 
 
 ## Case study
-## Caribou socioecology
+### Caribou socioecology
 # TODO: Lesmerises 2018
 
 # peignier
 citep('10.1002/ece3.5071')
+
+# TODO: Bergerud 1974
+
+# mayor 2009
+citep('10.2980/16-2-3238')
+
+### Caribou location 
+# TODO: Schaefer and Mahoney (2013)
+# TODO: Bjørneraas et al (2010)
+
+
 
 
 

### 2020-02-02 paper/manuscript.Rmd
update years
todo check res, mention raster package?

@@
 ### Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2018. Adult
+We used GPS location data collected from Fogo Island caribou in 2017 and 2018. Adult
 female caribou were immobilized and fitted with global positioning system (GPS)
@@
 Wildlife Division. Available landcover classification included nine habitat
-types at 30 x 30m resolution. We distilled the landcover types into three broad
+types at <!-- TODO: double check --> 30m resolution. We reclassified the landcover types into three
 categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
@@
 Water habitat was excluded from all subsequent analyses. 
+<!-- using the raster package for R? -->
 

### 2020-02-02 paper/citations.R
add R, R packages section to citations

@@ -40,7 +40,9 @@ citep('10.2980/16-2-3238')
 
 
 
-
+### R, R Packages
+# R
+citep(citation())
 
 ### Write out bib ----
 write.bibtex(file = "references/knitcite.bib")

### 2020-02-02 paper/citations.R
add kivela cite

@@ -40,9 +40,14 @@ citep('10.2980/16-2-3238')
 
 
 
+### Caribou multilayer social networks
+# kivela 2014
+citep('10.1093/comnet/cnu016')
+
 ### R, R Packages
 # R
 citep(citation())
+
 
 ### Write out bib ----
 write.bibtex(file = "references/knitcite.bib")

### 2020-02-02 paper/manuscript.Rmd
reflow
rm write.bibtex from Rmd
rm italics seasons

@@
 access to vegetation in winter is highly variable for caribou. We therefore
-partitioned data into two discrete seasons:  *summer (3 August - 20 September)
-and winter (1 January – 17 February)* based on caribou socioecology
+partitioned data into two discrete seasons:  summer (3 August - 20 September)
+and winter (1 January – 17 February) based on caribou socioecology
 [@Peignier_2019].
@@
 ### Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2017 and 2018. Adult
-female caribou were immobilized and fitted with global positioning system (GPS)
-collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars, 1,250 g)
-as described by Schaefer and Mahoney (2013). Collars were programmed to collect
-location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
-discrete removed all erroneous and outlier GPS fixes following Bjørneraas et al.
-(2010). We did not collar all female caribou in the herd; however, we assumed
-that our sample of collared animals was random.
+We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
+Adult female caribou were immobilized and fitted with global positioning system
+(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
+1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to
+collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
+into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
+et al. (2010). We did not collar all female caribou in the herd; however, we
+assumed that our sample of collared animals was random.
 
@@
 Wildlife Division. Available landcover classification included nine habitat
-types at <!-- TODO: double check --> 30m resolution. We reclassified the landcover types into three
-categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
-consisted of lichen habitat, open habitat consisted of wetland, rocky barrens,
-and anthropogenic habitat types, while forest habitat consisted of coniferous
-forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
-Water habitat was excluded from all subsequent analyses. 
+types at <!-- TODO: double check --> 30m resolution. We reclassified the
+landcover types into three categories: foraging habitat, open habitat, and
+forest habitat. Foraging habitat consisted of lichen habitat, open habitat
+consisted of wetland, rocky barrens, and anthropogenic habitat types, while
+forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
+and mixed-wood forest habitat types. Water habitat was excluded from all
+subsequent analyses.
 <!-- using the raster package for R? -->
@@
 ## References
-
-```{r, message=FALSE}
-write.bibtex(file = "../references/knitcite.bib")
-```

### 2020-02-02 paper/citations.R
update refs

@@ -24,7 +24,8 @@ citep('10.1093/beheco/arp074')
 
 ## Case study
 ### Caribou socioecology
-# TODO: Lesmerises 2018
+# TODO: Lesmerises 2018 -- check that's right
+citep('10.1016/j.anbehav.2018.03.014')
 
 # peignier
 citep('10.1002/ece3.5071')

### 2020-02-02 paper/manuscript.Rmd
notes matching kivela syntax

@@
 #### Network types and construction (defining layers for the multilayer network)
+<!-- specific kivela name, 6 layer multilayer-->
+
+Following [@Kivela_2014]:
+
+* we generated a six layer multilayer social network consisting of two aspects
+(season and landcover)
+* elementary-layer sets for two seasons (winter and summer) and three landcover
+classes (open, forest and lichen).
+* This multilayer network is not node-aligned as not all individuals exist on
+all layers
+* This layer has both ordinal and categorical coupling
+
+Individuals were subset to ensure they had data collected in both seasons
 
@@
 all GPS relocations were assigned to the corresponding habitat type and
-proximity-based social network layers were generated using the R package spatsoc
-(Robitaille et al. 2019) in *R version* (R Core Team 2020).
+proximity-based social network layers were generated using the R package `spatsoc`
+[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].
 
@@
 individuals, even if some individuals within the buffer were not within the
-given distance of one another (Robitaille et al. 2019). Group assignment based
+given distance of one another [@Robitaille_2019]. Group assignment based
 on the chain rule has previously been applied to caribou at a distance of 50m
-(Peignier et al. 2019; Lesmerises et al. 2018). In all networks, nodes
+[@Peignier_2019; @Lesmerises_2018]. In all networks, nodes
 represented individuals, intralayer edges represented associations between

### 2020-02-02 paper/manuscript.Rmd
integrate kivela syntax, mv some to comment

@@
 #### Network types and construction (defining layers for the multilayer network)
-<!-- specific kivela name, 6 layer multilayer-->
 
+<!-- should use something like "using syntax from Kivela 2014..." or 
 Following [@Kivela_2014]:
-
-* we generated a six layer multilayer social network consisting of two aspects
-(season and landcover)
-* elementary-layer sets for two seasons (winter and summer) and three landcover
-classes (open, forest and lichen).
-* This multilayer network is not node-aligned as not all individuals exist on
-all layers
-* This layer has both ordinal and categorical coupling
+other info to maybe include: the multilayer network was not node-aligned since
+not all individuals were on all layers
+the temporal aspect is ordinal coupling and landcover aspect is categorical coupling
 
@@
 
-We generated seasonal multilayer social networks consisting of habitat-specific
-monolayers. Each layer was the social association network generated in one of
-three habitat types (lichen, open, and forest). For habitat-specific networks,
-all GPS relocations were assigned to the corresponding habitat type and
-proximity-based social network layers were generated using the R package `spatsoc`
-[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].
+-->
+
+We generated a multilayer social network consisting 16 individual nodes and two
+aspects (season and landcover). Two season elementary-layers (winter and summer)
+and three landcover elementary-layers (open, forest and lichen) combined for a
+total of six layers. Layers were the social association network generated in
+each season and landcover combination. Proximity-based social network layers
+were generated using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].
 

### 2020-02-02 paper/citations.R
update refs

@@ -40,10 +40,15 @@ citep('10.2980/16-2-3238')
 # TODO: Bjørneraas et al (2010)
 
 
-
 ### Caribou multilayer social networks
 # kivela 2014
 citep('10.1093/comnet/cnu016')
+
+# robitaille 2019
+citep('10.1111/2041-210X.13215')
+
+# farine whitehead 2015
+citep('10.1111/1365-2656.12418')
 
 ### R, R Packages
 # R

### 2020-02-02 paper/manuscript.Rmd
fix refs fst par intro

@@
 Our inference regarding the ecological processes underlying ecological patterns
-are directly linked to the scale at which they are observed [@Levin_1993;
+are directly linked to the scale at which they are observed [@Levin_1992;
 @Allen_2015]. Animals are influenced across scales, through processes such as
 species-specific as trophic interactions and resource availability
-[@Legendre_1993; @Chave2013] and global climate and productivity [@Field_2009].
+[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
 Multiscale ecology has been integrated into species distribution modelling
-[@Elith_2009; @Mayor_2007; @Sugihara_1989], habitat selection, and food webs.
+[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
 Meanwhile, in the context of animal behaviour, certain behaviours are scale

### 2020-02-02 paper/manuscript.Rmd
cite todos, fills and little fixes to ml description

@@
 we apply this framework to a case study of caribou (*Rangifer tarandus*) in
-Newfoundland, Canada (Peignier et al. 2019). We use this case study to address
+Newfoundland, Canada [@Peignier_2019]. We use this case study to address
 two principal questions associated with scale-dependent multilayer networks.
@@
 development and application of scale in multilayer networks with respect to
-landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber &
+landscape ecology (Schneider 2009)<!-- TODO-->, individual fitness and phenotypes (Webber &
 Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
@@
 type), and temporal (seasonal). Caribou are gregarious ungulates with
-fission-fusion dynamics (Lesmerises et al. 2018) that display temporal
+fission-fusion dynamics [@Lesmerises_2018] that display temporal
 [@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
 social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage (Bergerud 1974). As a result, caribou tend to occupy and re-use
-craters once they are established and there is considerably less access to
+access forage (Bergerud 1974)<!-- TODO-->. As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to
 forage than when the landscape is snow-free. Importantly, craters exist on the
@@
 into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
-et al. (2010). We did not collar all female caribou in the herd; however, we
+et al. (2010)<!-- TODO-->. We did not collar all female caribou in the herd; however, we
 assumed that our sample of collared animals was random.
@@
 #### Network types and construction (defining layers for the multilayer network)
-
 <!-- should use something like "using syntax from Kivela 2014..." or 
@@
 Individuals were subset to ensure they had data collected in both seasons
-
 -->
@@
 
-Within each habitat-specific monolayer network, we assumed individuals were
+Within each layer, we assumed individuals were
 associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
@@
 represented individuals, intralayer edges represented associations between
-individuals in a given habitat type, and interlayer edges represented
+individuals in a given habitat type and season, and interlayer edges represented
 connections between the same individuals across contexts.
@@
 We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index (SRI, Cairns and Schwager 1987):
+caribou using the simple ratio index (SRI, Cairns and Schwager 1987): <!-- TODO-->
 
@@
 and $y_{AB}$ is the number of simultaneous fixes from individuals A and B
-that were separated by more than the given distance (Farine & Whitehead 2015).
+that were separated by more than the given distance [@Farine_2015].
 Social groups were designated if two or more individuals occurred within a given

### 2020-02-02 paper/manuscript.Rmd
landcover clarifications

@@
 ### Landscape data and habitat classification
-Landscape classification data were provided by the Newfoundland and Labrador
+Landcover data were provided by the Newfoundland and Labrador
 Wildlife Division. Available landcover classification included nine habitat
-types at <!-- TODO: double check --> 30m resolution. We reclassified the
+types at <!-- TODO: double check --> 10m resolution. We reclassified the
 landcover types into three categories: foraging habitat, open habitat, and
-forest habitat. Foraging habitat consisted of lichen habitat, open habitat
+forest habitat. Foraging habitat <!-- or just lichen like figs?--> consisted of lichen habitat, open habitat
 consisted of wetland, rocky barrens, and anthropogenic habitat types, while

### 2020-02-02 paper/manuscript.Rmd
reflow

@@
 
-Within each layer, we assumed individuals were
-associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each
-other) were within a given distance of one another. Typically for ungulates and
-other gregarious mammals, the ‘chain rule’ is applied for group assignment. For
-GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes
-buffered by a given distance formed a contiguous buffer for two or more
-individuals, even if some individuals within the buffer were not within the
-given distance of one another [@Robitaille_2019]. Group assignment based
-on the chain rule has previously been applied to caribou at a distance of 50m
-[@Peignier_2019; @Lesmerises_2018]. In all networks, nodes
-represented individuals, intralayer edges represented associations between
-individuals in a given habitat type and season, and interlayer edges represented
-connections between the same individuals across contexts.
+Within each layer, we assumed individuals were associating if simultaneous GPS
+fixes (i.e., recorded within 5 minutes of each other) were within a given
+spatial distance of one another. Typically for ungulates and other gregarious
+mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
+chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
+distance formed a contiguous buffer for two or more individuals, even if some
+individuals within the buffer were not within the given distance of one another
+[@Robitaille_2019]. Group assignment based on the chain rule has previously been
+applied to caribou at a distance of 50m [@Peignier_2019; @Lesmerises_2018]. In
+all networks, nodes represented individuals, intralayer edges represented
+associations between individuals in a given habitat type and season, and
+interlayer edges represented connections between the same individuals across
+contexts.
 

### 2020-02-02 paper/manuscript.Rmd
edits spatial scale

@@
 We altered social scale based on visual (short distance) and auditory (long
-distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified the
-distance threshold required for group assignment (see above) and re-assigned
-groups at incremental distance between 5-500m. For example, at the finest social
-scale, only individuals within 5m of one another were considered in the same
-group, whereas at the coarset social scale, only individuals within 500m of one
-another were considered in the same group.
+distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
+the spatial distance threshold required for group assignment (see above) and
+re-assigned groups at incremental distance between 5-500m. For example, at the
+finest social scale, only individuals within 5m of one another were considered
+in the same group, whereas at the coarsest social scale, individuals within 500m
+of one another were considered in the same group.
 
@@
 
-To assess the influence of spatial scale on multilayer networks, we re-sampled
-our landcover classification map at varying scales. Specifically, we selected
-scales relevant to caribou ecology. We re-sampled landcover using the
-`grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m,
-1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
-caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents
-the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
-et al. 2017). Resampling occurred based on a modal moving window method, where
-**XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**
-
-For each landcover (the original resolution and modal resampled resolutions),
-seasonal network layers are combined in a multilayer network <!-- Each modal
-landcover, and the original are sampled and separate network layers constructed
-for each. **[QW: NOT SURE WHAT THIS MEANS]** -->
+To assess the influence of spatial scale on multilayer networks, we aggregated
+our landcover classification map at varying scales relevant to caribou ecology. We aggregated the 10m landcover raster using the R package
+`grainchanger` [@Graham_2019] at five scales: 100m, 250m, 500m, and 
+1000m.
+Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a].
+10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
+2017).
 

### 2020-02-02 paper/manuscript.Rmd
fix scales listed

@@
 Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a].
-10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
+10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
 2017).

### 2020-02-02 paper/manuscript.Rmd
fix typos

@@
 We altered social scale based on visual (short distance) and auditory (long
-distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
+distance) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
 the spatial distance threshold required for group assignment (see above) and
@@
 To assess the influence of spatial scale on multilayer networks, we aggregated
-our landcover classification map at varying scales relevant to caribou ecology. We aggregated the 10m landcover raster using the R package
-`grainchanger` [@Graham_2019] at five scales: 100m, 250m, 500m, and 
-1000m.
-Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a].
-10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al.
-2017).
+our landcover classification map at varying scales relevant to caribou ecology.
+We aggregated the 10m landcover raster using the R package `grainchanger`
+[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
+using a modal moving window method using a circular window corresponding to the
+above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
+for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m
+represents the scale at which caribou tend to select and avoid habitat
+(Bastille-Rousseau et al. 2017).
 
@@
 
-We altered the temporal scale of mutlilayer networks using a moving time-window
-approach to define seasons.
+We altered the temporal scale of multilayer networks using a moving time-window
+approach to define seasons and
 
@@
 
-**Observational scale** <!--(temorary header)-->: Studies of social network analysis
+**Observational scale** <!--(temporary header)-->: Studies of social network analysis
 vary in the number and frequency of observations as well as the data collection
@@
 
-* Neighbors: number of unique individuals adjacent to each actor. Considered in
+* Neighbours: number of unique individuals adjacent to each actor. Considered in
 a single layer, this is equal to the degree.
 
-* Neighborhood: number of unique individuals across all layers. High
-neighborhood = a high number of unique individuals connected to an actor.
+* Neighbourhood: number of unique individuals across all layers. High
+neighbourhood = a high number of unique individuals connected to an actor.
 
-* Relevance: layer centric metric, corresponding to the number of neighbors on a
-layer divided by the total neighborhood for each actor. High relevance means
+* Relevance: layer centric metric, corresponding to the number of neighbours on a
+layer divided by the total neighbourhood for each actor. High relevance means
 that the layer is highly relevant to the individuals connections. A low
-relevance means this layer does not contribute many neighbors to an individuals
-overall neighborhood.
+relevance means this layer does not contribute many neighbours to an individuals
+overall neighbourhood.
 
-* Connective redundancy: the total multilayer neighborhood divided by the
+* Connective redundancy: the total multilayer neighbourhood divided by the
 multidegree. High connective redundancy indicates a multilayer network that has
@@
 
-* Layer similarily: how similar each layer is (Brodka 2018). Pearson's
+* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
 correlation coefficient of degree vectors for each layer, comparing each
@@
 (ref:lcres) varying scale in landcover resolution.
-For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
@@
 (ref:winlen) varying scale in time window length.
-For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+For each time window length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
@@
 (ref:nobs) varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
@@
 (ref:winpos) varying scale in time window position.
-For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+For each time window position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.

### 2020-02-03 paper/manuscript.Rmd
reflow
move header-includes affiliation to date

@@
 author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
-header-includes: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
+date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
 output:
-    # bookdown::word_document2:
-      # reference_docx: template.docx
-    github_document
+  # bookdown::markdown_document2:
+  #   base_format: rmarkdown::pdf_document
+  # bookdown::pdf_document2
+  bookdown::word_document2:
+    reference_docx: template.docx
 bibliography: ../references/knitcite.bib
@@
 we apply this framework to a case study of caribou (*Rangifer tarandus*) in
-Newfoundland, Canada [@Peignier_2019]. We use this case study to address
-two principal questions associated with scale-dependent multilayer networks.
-First, to what degree does the social scale of relationships, spatial scale of
+Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
+principal questions associated with scale-dependent multilayer networks. First,
+to what degree does the social scale of relationships, spatial scale of
 landscapes, and temporal scale of analysis influence our ability to interpret
@@
 development and application of scale in multilayer networks with respect to
-landscape ecology (Schneider 2009)<!-- TODO-->, individual fitness and phenotypes (Webber &
-Vander Wal 2018), and movement ecology and collective movement (Jolles et al.
-2019).
+landscape ecology (Schneider 2009)<!-- TODO-->, individual fitness and
+phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
+movement (Jolles et al. 2019).
 
@@
 social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage (Bergerud 1974)<!-- TODO-->. As a result, caribou tend to occupy and re-use craters once they are established and there is considerably less access to
-forage than when the landscape is snow-free. Importantly, craters exist on the
-landscape at multiple scales: the crater scale (a single crater), the feeding
-area scale (multiple craters in close proximity), and the winter range scale
-(all craters within an individual’s range) [@Mayor_2009]. The distribution of
-forage for caribou is therefore seasonally heterogeneous, with greater access in
-snow-free seasons compared to winter as well as spatially heterogeneous in
-winter because the distribution of craters on the landscape varies meaning that
-access to vegetation in winter is highly variable for caribou. We therefore
-partitioned data into two discrete seasons:  summer (3 August - 20 September)
-and winter (1 January – 17 February) based on caribou socioecology
-[@Peignier_2019].
+access forage (Bergerud 1974)<!-- TODO-->. As a result, caribou tend to occupy
+and re-use craters once they are established and there is considerably less
+access to forage than when the landscape is snow-free. Importantly, craters
+exist on the landscape at multiple scales: the crater scale (a single crater),
+the feeding area scale (multiple craters in close proximity), and the winter
+range scale (all craters within an individual’s range) [@Mayor_2009]. The
+distribution of forage for caribou is therefore seasonally heterogeneous, with
+greater access in snow-free seasons compared to winter as well as spatially
+heterogeneous in winter because the distribution of craters on the landscape
+varies meaning that access to vegetation in winter is highly variable for
+caribou. We therefore partitioned data into two discrete seasons:  summer (3
+August - 20 September) and winter (1 January – 17 February) based on caribou
+socioecology [@Peignier_2019].
 
@@
 into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
-et al. (2010)<!-- TODO-->. We did not collar all female caribou in the herd; however, we
-assumed that our sample of collared animals was random.
+et al. (2010)<!-- TODO-->. We did not collar all female caribou in the herd;
+however, we assumed that our sample of collared animals was random.
 
 ### Landscape data and habitat classification
-Landcover data were provided by the Newfoundland and Labrador
-Wildlife Division. Available landcover classification included nine habitat
-types at <!-- TODO: double check --> 10m resolution. We reclassified the
-landcover types into three categories: foraging habitat, open habitat, and
-forest habitat. Foraging habitat <!-- or just lichen like figs?--> consisted of lichen habitat, open habitat
+Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
+Available landcover classification included nine habitat types at <!-- TODO:
+double check --> 10m resolution. We reclassified the landcover types into three
+categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
+<!-- or just lichen like figs?--> consisted of lichen habitat, open habitat
 consisted of wetland, rocky barrens, and anthropogenic habitat types, while
@@
 where x is the number of fixes where individuals A and B were within a given
-distance of each other, $y_{A}$ is the number of fixes from individual A
-when individual B did not have a simultaneous fix, $y_{B}$ is the number
-of fixes from individual B when individual A did not have a simultaneous fix,
-and $y_{AB}$ is the number of simultaneous fixes from individuals A and B
-that were separated by more than the given distance [@Farine_2015].
-Social groups were designated if two or more individuals occurred within a given
-distance of one another at any given time point.
+distance of each other, $y_{A}$ is the number of fixes from individual A when
+individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
+from individual B when individual A did not have a simultaneous fix, and
+$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
+separated by more than the given distance [@Farine_2015]. Social groups were
+designated if two or more individuals occurred within a given distance of one
+another at any given time point.
 

### 2020-02-03 paper/manuscript.Rmd
fix output fig width to linewidth

@@
     # message = FALSE,
-    eval = TRUE
+    eval = TRUE,
+    out.width = '\\linewidth'
 )
-
-library(knitcitations)
-options("citation_format" = "pandoc")
 

### 2020-02-03 paper/manuscript.Rmd
fix output options, render pdf + docx

@@
 output:
-  # bookdown::markdown_document2:
-  #   base_format: rmarkdown::pdf_document
-  # bookdown::pdf_document2
-  bookdown::word_document2:
-    reference_docx: template.docx
+  bookdown::pdf_document2
+  # bookdown::word_document2:
+  #   reference_docx: template.docx
 bibliography: ../references/knitcite.bib

### 2020-02-03 paper/manuscript.Rmd
update indiv fitness perspective

@@
 dolphins (e.g. Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds
-(e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). The effect
-of scale on the relationship between an individual’s social network position and
-fitness may depend on the hypotheses being tested and logistical constraints.
-Two scales that are important for understanding fitness consequences in the
-context of social network positions are temporal and social scales (Almeling,
-Hammerschmidt, Sennhenn-Reulen, Freund, & Fischer, 2016; Berger, Lemaître,
-Allainé, Gaillard, & Cohas, 2015; Brent et al., 2017).
+(e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). Both
+temporal, seasons and stages of life, and social scales, types of interactions,
+have emerged as important for understanding fitness consequences in the context
+of social network positions (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, &
+Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent,
+Ruiz-Lambides, & Platt, 2017; Holekamp, Smith, Strelioff, Van Horn, & Watts,
+2012). Multilayer networks provide a way to bridge these different scales so
+that we can examine social phenotypes in more holistic ways rather than looking
+at each scale separately as has traditionally been done.
 
-Social network structure depends on the timeframe of observation, which can make
-networks difficult to compare (Castles et al., 2014). Furthermore, social
-network structure can vary seasonally and indicate social environments that an
-individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede,
-Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, &
-Watts, 2012), or they can be consistent across time, which can be used to
-reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, &
-Shultz, 2018). Seasonal fluctuations have the potential to have disease
-transmission and fitness effects for individuals (Balasubramaniam et al., 2019;
-Chen et al., 2014). <!-- **[QW: I'm not sure what this paragraph adds - I think if we
-need to save space we could cut it]**-->
-
-In long-lived species, social phenotypes can change over their lifetimes in ways
-that can affect fitness (Berger et al., 2015; Brent et al., 2017). These
-findings highlight the necessity to carefully consider the temporal scale that
-is meaningful for the proposed hypotheses, especially for understanding the
-relationship between an individuals social phenotype and fitness. Further
-complicating the issue, social phenotypes can change over stages of ontogeny,
-although it is important to note that individuals progress through development
-at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This
-variation can make defining appropriate temporal scales for testing the fitness
-implications of an individual’s social phenotype over different stages of
-ontogeny even more difficult. However, considering fine temporal scales may
-provide insight across development stages that may otherwise be missed
-(CITE-myself??). Multilayer networks provide a framework to test hypotheses
-linking social phenotypes and fitness across temporal scales. Because of the
-non-independent nature of social interactions and associations, especially over
-time, it is hard to test hypotheses about social dynamics with a suitable null
-control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-Social scale is another major consideration for social network analysis,
-especially in the context of different types of interactions and associations in
-the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine,
-2015). It is a common trope that individuals must be associating to interact and
-most studies therefore assume that proximity is proxy for interacting (Farine,
-2015). For instance, baboons need to be in proximity in order to groom each
-other, but this trope highlights human bias toward interactions that can be
-readily observed in the field. Animals have certain interactions that do not
-require proximity such as long-distance vocalization and olfactory signals
-(Carter et al., 2015). With the advancement of bio-logging technology, we have
+For instance, social scale is major consideration for social network analysis,
+especially in the context of different types of relationships, such as grooming
+and association, that are typically examined separately while answering a single
+question (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
+Furthermore, it is a common trope that individuals must be associating to
+interact, and many studies therefore assume that proximity is proxy for
+interacting (Farine, 2015). For instance, baboons need to be in proximity in
+order to groom each other. However, animals have certain interactions that do
+not require proximity such as long-distance vocalization and olfactory signals
+(Carter et al., 2015). With the advancement of biologging technology, we have
 the ability to record social interactions that do not require proximity,
 particularly long-distance communication networks with devices like microphone
-arrays (Snijders & Naguib, 2017). The multilayer network framework further
-enables researchers to examine the relationship between social phenotypes and
-fitness across social scales and to test how good social proximity is as a proxy
-for social interactions in a holistic way.
+arrays (Snijders & Naguib, 2017). These varying social scales can have different
+fitness repercussions for individuals. Rhesus macaques (Macaca mulatta) had
+higher survivorship when they had fewer but stronger, more stable social
+associates and grooming partners rather than simply more associates (Ellis,
+Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights
+that different qualities of social scales have lasting consequences.
 
-These different social scales can have different fitness repercussions for
-individuals. Rhesus macaques (*Macaca mulatta*) that had stronger, more stable
-social associates and grooming partners, but not more social partners, had
-higher survivorship than those who did not (Ellis, Snyder-Mackler,
-Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights the need to
-investigate the effect of temporal and social scales on the relationship between
-social network positions and fitness. Multilayer networks provide an avenue to
-do so considering the whole social system rather than just one type of social
-interaction at a time, which is what has been done under most circumstances but
-is not very realistic.
+Temporal scale is also important for understanding the repercussions of social
+phenotypes. For instance, social phenotypes can change over ontogeny in ways
+that can affect fitness (Berger et al., 2015; Brent et al., 2017). Thus, it is
+critical to carefully consider the temporal scale that is meaningful for the
+proposed hypotheses. Further complicating the issue of selecting suitable time
+scales across ontogeny, individuals progress through development at different
+rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can
+make defining appropriate temporal scales for testing the fitness implications
+of an individual’s social phenotype over different stages of ontogeny even more
+difficult when they vary by individual. However, considering fine temporal
+scales provide insight across developmental stages that may otherwise be missed
+(Turner, Bills, & Holekamp, 2018).
 
-Multilayer networks further provide unique challenges and opportunities for
-understanding the social phenotypes and environments of individuals and their
-fitness outcomes. Picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks (Farine, 2017). These considerations may be limiting factors
-when answering questions that require timeframes that are relevant to different
-individuals. On the other hand, multilayer network metrics provide an
-opportunity to simplify statistical models. Interactions that happen meters
-apart, proximity associations, and long-distance interactions can be
-encapsulated in a single multilayer network, and a single metric can be used to
-describe the various social scales of an individual’s network position. This
-multilevel network metric could be used to assess the relationship between an
-individual's social phenotype and fitness. It would also be a meaningful
-simplification of many network metrics that could help simplify statistical
-analyses and deal with the frequent correlations between social network metrics
-in different types of networks (Castles et al., 2014).
+Multilayer networks provide unique opportunities and challenges, linking these
+various scales, for understanding the social phenotypes and environments of
+individuals and their fitness outcomes. The multilayer network framework enables
+researchers to examine these different social scales simultaneously rather than
+individually, which is what has been done under most circumstances, but is not
+very realistic. Metrics from multilayer networks provide an opportunity to
+simplify statistical models. Interactions that happen side-by-side, proximity
+associations, and long-distance interactions can be encapsulated in a single
+multilayer network, and a single metric can be used to describe the various
+social scales of an individual’s network position. This multilevel network
+metric could be used to assess the relationship between an individual’s social
+phenotype and fitness. It would also be a meaningful simplification of many
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks (Castles et al., 2014). Furthermore, multilayer networks provide a
+framework to test hypotheses linking social phenotypes and fitness across
+temporal scales. Because of the non-independent nature of social interactions
+and associations, especially over time, it is hard to test hypotheses about
+social dynamics with a suitable null control (Farine, 2017; Proskurnikov &
+Tempo, 2017). Using the framework of multilayer networks, making layers of
+different temporal periods provides a way to make appropriate null models to
+test questions about the dynamics of an individual’s social network position
+over multiple aggregated time periods.
+
+On the other hand, picking the proper temporal scale is important but a
+challenge because all layers in the multilayer network should reflect the same
+time period, and the period should be long enough for each layer to have enough
+data for robust networks (Farine, 2017). These considerations may be limiting
+factors when answering questions that require timeframes that are relevant to
+different individuals, for instance. In both mono- and multilayer networks, the
+effect of scale on the relationship between an individual’s social network
+position and fitness need to be considered based on the hypotheses being tested
+and logistical constraints.
 

### 2020-02-03 paper/manuscript.Rmd
fix italics

@@
 arrays (Snijders & Naguib, 2017). These varying social scales can have different
-fitness repercussions for individuals. Rhesus macaques (Macaca mulatta) had
+fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) had
 higher survivorship when they had fewer but stronger, more stable social

### 2020-02-03 paper/manuscript.Rmd
tidy interpret+cap
edit fig. 2 caption

@@
 
-(ref:lcres) varying scale in landcover resolution.
-For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+(ref:lcres) Varying scale in landcover resolution.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
@@
 B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
-C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+**[JWT: we need the orders to be the same in legend/discussion as the figure legends; I'm trying to catch it, but it may show up other places]**
+
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
 
@@
 ```
-
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
 
@@
 
+* increasing layer relevance as more individuals are connected with increasing buffer size
+* decrease in connective redundancy due an increase in summer forest degree at the last (500m) social threshold
+* increasing graph strength consistent with increasing strength in winter
+
 ```{r, fig.cap='(ref:socres)'}
@@
 ```
-
-* increasing layer relevance as more individuals are connected with increasing buffer size
-* decrease in connective redundancy due an increase in summer forest degree at the last (500m) social threshold
-* increasing graph strength consistent with increasing strength in winter
 

### 2020-02-03 paper/citations.R
more cites

@@ -52,9 +52,20 @@ citep('10.1111/1365-2656.12418')
 
 
 ### Varying scale in multilayer networks
+## social scale
+
+## landcover scale
 # grainchanger, Graham 2019
 citep(citation('grainchanger'))
 citep('10.1111/2041-210X.13177')
+
+
+## temporal scale
+# davis 2018
+
+# webber vander 2019
+
+
 
 ### R, R Packages
 # R

### 2020-02-03 paper/manuscript.Rmd
temporal scale

@@
 
-We altered the temporal scale of multilayer networks using a moving time-window
-approach to define seasons and
+We altered the temporal scale of multilayer networks by varying the length and
+position of the time window used to define seasons. The length of the time
+window varied from 40-100 days using a fixed start day for winter (1 January)
+and summer (3 August). The position of the time window was shifted by 1-48 days,
+using a fixed time window length of 48 days. These new time windows were
+iteratively used to partition data into two discrete seasons (winter, summer)
+and generate multilayer networks.
 
-1. time window length
-
-Varying length of time window (used to define seasons). Starting with a window
-of day 1-40 and using a moving window to go to day 1-100. Fixed start julian day
-for winter is day 1 and for summer is 215. Network layers for winter and summer
-are calculated for each window length.
-
-1. time window position
-Varying position of time window (used to define seasons). Fixed length at 48
-Window positions starting at 1, to + 48 So 1-48 is first iteration for winter
-and 48-96 is second iteration for "winter". Same for summer, starting at 215.
-Network layers for each season are constructed.
-
-**Observational scale** <!--(temporary header)-->: Studies of social network analysis
-vary in the number and frequency of observations as well as the data collection
-technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
-2019).
-
-Randomly select max number of observations - timegroups - <!-- (right now 750)-->. For
-each iteration, include n observations for each season for all individuals.
-Subsequent iterations include nstep more <!--(right now 25)-->, along with previously
-included to remove stochasticity. Parallels with observation data.
+Studies of social network analysis vary in the number and frequency of
+observations as well as the data collection technique used to generate networks
+(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
+temporal scale, we investigated the influence of the number of observations on
+resulting multilayer networks. We randomly selected 500 timesteps and
+iteratively included 25 additional observations, regenerating the multilayer
+network and calculating associations of individuals. Subsequent iterations
+included the previous set of observations to mimic observational data.
 
@@
 
-(ref:socres) varying scale in social threshold.
-For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
-B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m.
+(ref:socres) Varying scale in social threshold.
+For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.
+This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 **[JWT: Does this have units??]** at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
 C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
-D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.
+D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
+**[JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI.
+I would talk about it more about strong/weak connections.
+Networks can be sparse (few connections), but still have high strength if the ties have higher values]**
 
@@
 
-(ref:winlen) varying scale in time window length.
-For each time window length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+(ref:winlen) Varying scale in time window length.
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m.
-C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
-D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.
+B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window **[JWT: previously this was describing fig.
+3.
+I don't know if what I wrote best encapsulates what connnective redundancy does here.
+Length of time window seems to make connective redundancy highly variable as it changes.]**.
+C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
+**[see if you agree with my changes.
+B-D were based off fig.
+3 and not relevant to this figure]**
 
@@
 
-(ref:nobs) varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations.
+*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
+B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
 C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
 
@@
 
-(ref:winpos) varying scale in time window position.
-For each time window position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
-C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions.
+(ref:winpos) Varying scale in time window position.
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
+**[JWT: previously describing window length, not position.
+Check that you're ok with my changes]** B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
 D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.

### 2020-02-03 paper/manuscript.Rmd
md for now

--- 2020-02-03 paper/manuscript.Rmd
@@
 output:
-  bookdown::pdf_document2
+  github_document
+  # bookdown::pdf_document2
   # bookdown::word_document2:
@@
 
-For each multilayer network, we calculated four metrics.These included:
+For each multilayer network, we calculated four metrics. These included:
 multidegree, graph strength, redundancy/relevance, and  layer similarity.

### 2020-02-03 paper/citations.R
more cites

@@ -50,6 +50,9 @@ citep('10.1111/2041-210X.13215')
 # farine whitehead 2015
 citep('10.1111/1365-2656.12418')
 
+## metrics
+# berlingerio 2012
+citep('10.1007/s11280-012-0190-4')
 
 ### Varying scale in multilayer networks
 ## social scale
@@ -64,6 +67,7 @@ citep('10.1111/2041-210X.13177')
 # davis 2018
 
 # webber vander 2019
+
 
 
 

### 2020-02-03 paper/manuscript.Rmd
series of metrics...

@@
 #### Network metrics
+We used a series of metrics to characterize the multilayer networks focusing on the relevance of individual layers, 
+similarity of layers and the role of individuals.
+We calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
+Comparing the multidegree and number of unique neighbours, we measured the connective redundancy, the proportion of neighbours repeated in multiple layers, and the layer relevance, the proportion of neighbours present compared to the neighbourhood for each individual.
+To measure the role of individuals, we calculated the graph strength for each individual for each layer specific season and landcover context.
 
-For each multilayer network, we calculated four metrics.These included:
+e focused on four aspects
+of the network: “interlayer correlation and reducibility”
+(i.e., correlation between layers and similarities regarding
+the information contained in each one; “node versatility”
+(i.e., role of each node in the connectedness and information
+flow of the network); “community structure” (i.e., whether
+there are subsets of nodes more tightly connected among
+each other than with the rest); and “motif analysis” (i.e.,
+non-random patterns of interconnection between triads).
+
+Node based
+
+Calculated for each layer 
+and for multilayer total
+
+For each multilayer network, we calculated a series of metrics on individual layers and  four metrics. These included:
 multidegree, graph strength, redundancy/relevance, and  layer similarity.
@@
 * layer similarity
+
+* Multidegree: sum of degree across layers. High multidegree = connected to many
+individuals across layers. Low multidegree = not connected to many individuals
+across layers.
+
+* Degree deviation: deviation of degree across layers. High degree deviation =
+large difference between degree for an individual across layers. Low degree
+deviation = individuals are similarly connected across layers.
+
+* Graph strength: weighted version of degree. High graph strength = highly
+connected. Not summed in this case across layers.
+
+* Neighbours: number of unique individuals adjacent to each actor. Considered in
+a single layer, this is equal to the degree.
+
+* Neighbourhood: number of unique individuals across all layers. High
+neighbourhood = a high number of unique individuals connected to an actor.
+
+* Relevance: layer centric metric, corresponding to the number of neighbours on a
+layer divided by the total neighbourhood for each actor. High relevance means
+that the layer is highly relevant to the individuals connections. A low
+relevance means this layer does not contribute many neighbours to an individuals
+overall neighbourhood.
+
+* Connective redundancy: the total multilayer neighbourhood divided by the
+multidegree. High connective redundancy indicates a multilayer network that has
+many repeated edges across layers between an actor and its neighbours. Low
+connective redundancy indicates that each layer is important for preserving all
+social ties.
+
+* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
+correlation coefficient of degree vectors for each layer, comparing each
+landcover across seasons.
 

### 2020-02-03 paper/manuscript.Rmd
clarify

@@
 (Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
-temporal scale, we investigated the influence of the number of observations on
+temporal scale by adjusting the time window, we investigated the influence of the number of observations on
 resulting multilayer networks. We randomly selected 500 timesteps and

### 2020-02-03 paper/manuscript.Rmd
rm note order
dont number sections

@@
   github_document
-  # bookdown::pdf_document2
+  bookdown::pdf_document2:
+    number_sections: false
   # bookdown::word_document2:
@@
 D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
-**[JWT: we need the orders to be the same in legend/discussion as the figure legends; I'm trying to catch it, but it may show up other places]**
 

### 2020-02-03 paper/citations.R
cites

@@ -54,6 +54,9 @@ citep('10.1111/1365-2656.12418')
 # berlingerio 2012
 citep('10.1007/s11280-012-0190-4')
 
+# brodka
+citep('10.1098/rsos.171747')
+
 ### Varying scale in multilayer networks
 ## social scale
 

### 2020-02-03 paper/manuscript.Rmd
reflow
section headers

@@
 output:
-  github_document
-  bookdown::pdf_document2:
-    number_sections: false
+  #github_document
+   bookdown::pdf_document2
   # bookdown::word_document2:
@@
 
-## Abstract
+# Abstract
 Scale remains a seminal concept in ecology. Spatial scale, for instance, has
@@
 
-## Introduction
+# Introduction
 Our inference regarding the ecological processes underlying ecological patterns
@@
 
-## Scale in multilayer networks: a case study
+# Scale in multilayer networks: a case study
 
-### Caribou socioecology
+## Caribou socioecology
 Here, we use caribou as a case study to develop scale-dependent multilayer
@@
 
-### Caribou location data
+## Caribou location data
 We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
@@
 
-### Landscape data and habitat classification
+## Landscape data and habitat classification
 Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
@@
 
-### Caribou multilayer social networks
+## Caribou multilayer social networks
 
-#### Network types and construction (defining layers for the multilayer network)
+### Network types and construction (defining layers for the multilayer network)
 <!-- should use something like "using syntax from Kivela 2014..." or 
@@
 
-#### Network metrics
+### Network metrics
 We used a series of metrics to characterize the multilayer networks focusing on the relevance of individual layers, 
@@
 
-### Varying scale in multilayer networks
+## Varying scale in multilayer networks
 
-#### Social scale
+### Social scale
 
@@
 
-#### Spatial scale
+### Spatial scale
 
@@
 
-#### Temporal scale
+### Temporal scale
 
@@
 
-## Scale in multilayer networks in practice: case study results and discussion
+# Scale in multilayer networks in practice: case study results and discussion
 
-### Each metric's interpretation
+## Each metric's interpretation
 * Multidegree: sum of degree across layers. High multidegree = connected to many
@@
 
-### Figure captions and brief interpretations
+## Figure captions and brief interpretations
 
@@
 
-###
+##
 Results and interpretation of temporal scale
@@
 
-## Perspectives  to advance multilayer networks 
-### Habitat selection and space use
+# Perspectives  to advance multilayer networks 
+## Habitat selection and space use
 
@@
 
-### Individual fitness and phenotypes
+## Individual fitness and phenotypes
 
@@
 
-### Movement ecology and collective movement
+## Movement ecology and collective movement
 
@@
 
-## Conclusions
+# Conclusions
 
@@
 
-## Acknowledgements
+# Acknowledgements
 
@@
 
-## References
+# References

### 2020-02-03 paper/manuscript.Rmd
acknowledgements
fig2 caption

@@
 
-(ref:lcres) Varying scale in landcover resolution.
+(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
 For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated.
@@
 
-<!-- add jack -->
-
-We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
+We thank all members of the Wildlife Evolutionary Ecology Lab, including J. Hendrix, K.
 Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for

### 2020-02-03 paper/manuscript.Rmd
fig2 caption v2

@@
 output:
-  #github_document
-   bookdown::pdf_document2
+  github_document
+  # bookdown::pdf_document2:
+  #   number_sections: false
   # bookdown::word_document2:
@@
 ### Network metrics
-We used a series of metrics to characterize the multilayer networks focusing on the relevance of individual layers, 
-similarity of layers and the role of individuals.
-We calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
-Comparing the multidegree and number of unique neighbours, we measured the connective redundancy, the proportion of neighbours repeated in multiple layers, and the layer relevance, the proportion of neighbours present compared to the neighbourhood for each individual.
-To measure the role of individuals, we calculated the graph strength for each individual for each layer specific season and landcover context.
-
-e focused on four aspects
-of the network: “interlayer correlation and reducibility”
-(i.e., correlation between layers and similarities regarding
-the information contained in each one; “node versatility”
-(i.e., role of each node in the connectedness and information
-flow of the network); “community structure” (i.e., whether
-there are subsets of nodes more tightly connected among
-each other than with the rest); and “motif analysis” (i.e.,
-non-random patterns of interconnection between triads).
-
-Node based
-
-Calculated for each layer 
-and for multilayer total
-
-For each multilayer network, we calculated a series of metrics on individual layers and  four metrics. These included:
-multidegree, graph strength, redundancy/relevance, and  layer similarity.
-
-<!-- GOING
-TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
-EXPLAINING THESE).
--->
-
-<!-- 
-ALR: Reference for extending degree centrality to multilayer, neighbors,
-connective redundancy and relevance: Berlingerio 2011 "Foundations of
-multidimensional..."
--->
-
-* Multidegree
-* Degree centrality
-* Multidegree
-* Degree deviation: standard deviation of degree across layers
-* Neighbors/neighborhood (number of unique actors directly connected to each focal): Neighbors = degree within a network layer.
-But across a multilayer network with multiple layers, some neighbors are repeated.
-* Graph strength
-* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties
-* Relevance: neighborhood of specific layer  / neighbourhood of full ml net.
-This is the proportion of neighbors present on the layer of focus.
-Comparing across, it tells you which layers are most important for each individual.
-* layer similarity
-
-* Multidegree: sum of degree across layers. High multidegree = connected to many
-individuals across layers. Low multidegree = not connected to many individuals
-across layers.
-
-* Degree deviation: deviation of degree across layers. High degree deviation =
-large difference between degree for an individual across layers. Low degree
-deviation = individuals are similarly connected across layers.
-
-* Graph strength: weighted version of degree. High graph strength = highly
-connected. Not summed in this case across layers.
-
-* Neighbours: number of unique individuals adjacent to each actor. Considered in
-a single layer, this is equal to the degree.
-
-* Neighbourhood: number of unique individuals across all layers. High
-neighbourhood = a high number of unique individuals connected to an actor.
-
-* Relevance: layer centric metric, corresponding to the number of neighbours on a
-layer divided by the total neighbourhood for each actor. High relevance means
-that the layer is highly relevant to the individuals connections. A low
-relevance means this layer does not contribute many neighbours to an individuals
-overall neighbourhood.
-
-* Connective redundancy: the total multilayer neighbourhood divided by the
-multidegree. High connective redundancy indicates a multilayer network that has
-many repeated edges across layers between an actor and its neighbours. Low
-connective redundancy indicates that each layer is important for preserving all
-social ties.
-
-* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
-correlation coefficient of degree vectors for each layer, comparing each
-landcover across seasons.
+We used a series of metrics to characterize the multilayer networks focusing on
+the relevance of individual layers, similarity of layers and the role of
+individuals. We calculated multidegree, the sum of degree centrality across
+layers, and neighbourhood, the sum of unique neighbours to each individual
+[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
+unique neighbours, we measured the connective redundancy, the proportion of
+neighbours repeated in multiple layers, and the layer relevance, the proportion
+of neighbours present compared to the neighbourhood for each individual
+[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
+strength for each individual for each layer specific season and landcover
+context <!-- citation?-->. Finally, we calculated the similarity of layers
+between seasons, across landcover classes (e.g.: winter open compared to summer
+open) using the Pearson correlation coefficient [@Br_dka_2018].
 
 ## Varying scale in multilayer networks
-
 ### Social scale
@@
 (Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
-temporal scale by adjusting the time window, we investigated the influence of the number of observations on
-resulting multilayer networks. We randomly selected 500 timesteps and
-iteratively included 25 additional observations, regenerating the multilayer
-network and calculating associations of individuals. Subsequent iterations
-included the previous set of observations to mimic observational data.
+temporal scale by adjusting the time window, we investigated the influence of
+the number of observations on resulting multilayer networks. We randomly
+selected 500 timesteps and iteratively included 25 additional observations,
+regenerating the multilayer network and calculating associations of individuals.
+Subsequent iterations included the previous set of observations to mimic
+observational data.
 
@@
 
-(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
-For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
-Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
-B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
-C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
-D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
-
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
-
-```{r, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lcres.png')
-```
-
 (ref:socres) Varying scale in social threshold.
@@
 knitr::include_graphics('../graphics/figure-spatialthreshold.png')
+```
+
+(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+
+```{r, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
+<!-- RO first sentence... -->
+
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
+B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+
+* common, though at different points - more observations until stabilizing
+* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
+* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
+
+```{r, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
 ```
@@
 knitr::include_graphics('../graphics/figure-winlength.png')
-```
-
-<!-- RO first sentence... -->
-
-(ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
-B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
-C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
-
-* common, though at different points - more observations until stabilizing
-* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
-* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
-
-```{r, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-nobs.png')
 ```

### 2020-02-03 paper/manuscript.Rmd
network metrics

@@
 
-# Abstract
+## Abstract
 Scale remains a seminal concept in ecology. Spatial scale, for instance, has
@@
 
-# Introduction
+## Introduction
 Our inference regarding the ecological processes underlying ecological patterns
@@
 
-# Scale in multilayer networks: a case study
+## Scale in multilayer networks: a case study
 
-## Caribou socioecology
+### Caribou socioecology
 Here, we use caribou as a case study to develop scale-dependent multilayer
@@
 
-## Caribou location data
+### Caribou location data
 We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
@@
 
-## Landscape data and habitat classification
+### Landscape data and habitat classification
 Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
@@
 
-## Caribou multilayer social networks
+### Caribou multilayer social networks
 
-### Network types and construction (defining layers for the multilayer network)
+#### Network types and construction (defining layers for the multilayer network)
 <!-- should use something like "using syntax from Kivela 2014..." or 
@@
 
-### Network metrics
+#### Network metrics
 We used a series of metrics to characterize the multilayer networks focusing on
@@
 
-## Varying scale in multilayer networks
-### Social scale
+### Varying scale in multilayer networks
+#### Social scale
 
@@
 
-### Spatial scale
+#### Spatial scale
 
@@
 
-### Temporal scale
+#### Temporal scale
 
@@
 
-# Scale in multilayer networks in practice: case study results and discussion
+## Scale in multilayer networks in practice: case study results and discussion
 
-## Each metric's interpretation
+### Each metric's interpretation
 * Multidegree: sum of degree across layers. High multidegree = connected to many
@@
 
-## Figure captions and brief interpretations
+### Figure captions and brief interpretations
+
+(ref:lcres) Varying scale in landcover resolution.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+
+```{r, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
 
@@
 knitr::include_graphics('../graphics/figure-spatialthreshold.png')
-```
-
-(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
-For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
-Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
-B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
-C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
-D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
-
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
-
-```{r, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lcres.png')
-```
-
-<!-- RO first sentence... -->
-
-(ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
-B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
-C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
-
-* common, though at different points - more observations until stabilizing
-* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
-* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
-
-```{r, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-nobs.png')
 ```
@@
 
+<!-- RO first sentence... -->
+
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
+B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+
+* common, though at different points - more observations until stabilizing
+* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
+* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
+
+```{r, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
+```
+
 (ref:winpos) Varying scale in time window position.
@@
 
-##
+###
 Results and interpretation of temporal scale
@@
 
-# Perspectives  to advance multilayer networks 
-## Habitat selection and space use
+## Perspectives  to advance multilayer networks 
+### Habitat selection and space use
 
@@
 
-## Individual fitness and phenotypes
+### Individual fitness and phenotypes
 
@@
 
-## Movement ecology and collective movement
+### Movement ecology and collective movement
 
@@
 
-# Conclusions
+## Conclusions
 
@@
 
-# Acknowledgements
+## Acknowledgements
 
-We thank all members of the Wildlife Evolutionary Ecology Lab, including J. Hendrix, K.
+<!-- add jack -->
+
+We thank all members of the Wildlife Evolutionary Ecology Lab, including K.
 Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
@@
 
-# References
+## References

### 2020-02-03 paper/manuscript.Rmd

--- 2020-02-03 paper/manuscript.Rmd
@@
 
+(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+
+```{r, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
 (ref:socres) Varying scale in social threshold.
@@
 knitr::include_graphics('../graphics/figure-winlength.png')
+```
+
+<!-- RO first sentence... -->
+
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
+B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+
+* common, though at different points - more observations until stabilizing
+* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
+* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
+
+```{r, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
 ```

### 2020-02-03 paper/manuscript.Rmd
reorg figs
Update manuscript.Rmd and manuscript.pdf
social scale results

--- 2020-02-03 paper/manuscript.Rmd
@@
 
+We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale.
+
+In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season.
+As social scale increased, connective redundancy increased rapidly when groups were formed based on ~100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at ~500m (Figure 3b).
+Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c).
+Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).
+
+* increasing graph strength consistent with increasing strength in winter
+
 ## Each metric's interpretation
@@
 Networks can be sparse (few connections), but still have high strength if the ties have higher values]**
-
-* increasing layer relevance as more individuals are connected with increasing buffer size
-* decrease in connective redundancy due an increase in summer forest degree at the last (500m) social threshold
-* increasing graph strength consistent with increasing strength in winter
 
@@
 ```
-
-##
-Results and interpretation of temporal scale
-
-Results and interpretation of spatial scale
-
-Results and interpretation of social scale
 

### 2020-02-03 paper/manuscript.Rmd
social scale v2

@@
 output:
-  github_document
-  # bookdown::pdf_document2:
-  #   number_sections: false
+  #github_document
+  bookdown::pdf_document2:
+     number_sections: false
   # bookdown::word_document2:
@@
 Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).
-
-* increasing graph strength consistent with increasing strength in winter
+Taken together, these results suggest the optimal social scale at which groups should be assigned is likely somewhere between ~20-100m based on the rate at which network metrics stabilized.
+For ungulates, groups are often assigned based on 50m threshold (Lingle 2003; Lesmeries et al.
+2018; Peignier et al.
+2019), suggesting that given similar quantities of data, ~50m is likely an ideal social scale for generating social networks in caribou and similar species.
 

### 2020-02-03 paper/manuscript.Rmd
perspectives intro

@@
 development and application of scale in multilayer networks with respect to
-landscape ecology (Schneider 2009)<!-- TODO-->, individual fitness and
+habitat selection and space use (REF)<!-- TODO-->, individual fitness and
 phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
@@
 # Perspectives  to advance multilayer networks
+
+To date, behavioural ecology and social network researchers have made progress in describing the causes and consequences of the social environment in the context of (1) habitat selection and space use, (2) Individual fitness and phenotypes, and (3) movement ecology and collective movement.
+Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of spatial ecosystem ecology.
+
 ## Habitat selection and space use

### 2020-02-03 paper/citations.R
Update citations.R

@@ -82,6 +82,16 @@ citep('10.1098/rspb.2017.0515')
 #thompson 2019
 citep('10.1163/1568539X-00003552')
 
+#stanton 2011
+citep('10.1016/j.anbehav.2011.05.026')
+# stanton 2012
+citep('10.1371/journal.pone.0047508')
+
+# mcdonald 2007
+citep('10.1073/pnas.0701159104')
+# royle 2012
+citep('10.1098/rspb.2012.1701')
+
 
 ### R, R Packages
 # R

### 2020-02-03 paper/manuscript.tex
edit m

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The problem and promise of scale in multilayer networks},
            pdfauthor={Alec L. Robitaille1, Quinn M.R. Webber2, Julie W. Turner1, Eric Vander Wal1,2},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{The problem and promise of scale in multilayer networks}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Alec L. Robitaille\textsuperscript{1}, Quinn M.R. Webber\textsuperscript{2}, Julie W. Turner\textsuperscript{1}, Eric Vander Wal\textsuperscript{1,2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Department of Biology, Memorial University of Newfoundland, Canada; \textsuperscript{2}Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

Scale remains a seminal concept in ecology. Spatial scale, for instance, has
become a central consideration in the way we understand landscape ecology and
animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal's perception of scale, e.g., grain and extent. But
scale can affect multilayer network dynamics and how we build and interpret
them. Here, we discuss the role of scale in the context of multilayer networks
and provide a case study of caribou (\emph{Rangifer tarandus}) to illustrate the role
of social,spatial, and temporal scale on multilayer processes. We also present
perspectives on future development and application of scale in multilayer
networks with respect to habitat selection and space use, individual fitness and
phenotypes, and movement ecology and collective movement.Effective integration
of social and spatial processes, including biologically meaningful scales,
within the context of animal social networks is an emerging area of research;
our contribution uniquely incorporates perspectives on how the social
environment and spatial processes are linked across scales in a multilayer
framework. Based on social network and behavioural ecology theory as well as our
case study, we demonstrate potential for interconnectedness among individual
animals, their social environment, and the landscapes they occupy.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Our inference regarding the ecological processes underlying ecological patterns
are directly linked to the scale at which they are observed (Levin 1992; Allen and Hoekstra 2015). Animals are influenced across scales, through processes such as
species-specific as trophic interactions and resource availability
(Legendre 1993; Chave 2013) and global climate and productivity (Field et al. 2009).
Multiscale ecology has been integrated into species distribution modelling
(Elith and Leathwick 2009), habitat selection (Mayor et al. 2007), and food webs (Sugihara, Schoenly, and Trombla 1989).
Meanwhile, in the context of animal behaviour, certain behaviours are scale
dependent, for example, acoustic communication in birds occurs over variable
spatial scales (Luther 2009). We posit that animal behaviour and, more
specifically, the social environment that animals experience must also be
scale-dependent.

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods (e.g.~Carter et al.~2015), whereas social
association represents shared space use by members of the same social group
(Figure 1, Franks et al.~2010). Further, for social interactions or associations
to occur individuals must share space, and thus have overlapping home ranges. In
the context of the social environment, home range overlap is a relatively coarse
scale of sociality across which individuals share space over coarser spatial and
temporal scales (e.g.~Piza-Roca et al.~2018). Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of sociality, including social association and home range overlap, vary
predictably with social interaction (Castles et al.~2014; Farine 2015). Thus, we
define social scale as the type of social relationship observed that can be
explicitly defined and measured (Farine et al.~2015).

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems (Krause et
al.~2009; Wey et al.~2008; Croft et al.~2008). Social network analysis provides
insight into the structure of social communities and social network properties,
which can influence population dynamics and evolutionary processes
(Pinter-Wollman et al.~2014; Kurvers et al.~2014). Despite the widespread use
and innovation of traditional social network analysis (Webber \& Vander Wal
2019), it typically considers a single scale of sociality in a given network
(monolayer), drastically simplifying the potential complexity of animal social
systems (Finn et al.~2019).

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
(Pilosof et al.~2017). Multilayer networks are made up of multiple layers, each
representing different classes of individuals (e.g.~male or female), types of
behaviours (e.g.~grooming, travelling, or foraging), spatial areas (e.g.~local
or regional), or temporal windows (e.g.~daily or seasonal) (Kivela et al.~2014;
Porter 2018). Multilayer networks are relatively novel to studies of animal
behaviour (Finn et al.~2019; Silk et al.~2018), although they have been used to
describe multidimensional human social systems, complex transportation networks,
and neural networks (Silk et al.~2018). The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (\emph{Rangifer tarandus}) in
Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to
habitat selection and space use (REF), individual fitness and
phenotypes (Webber \& Vander Wal 2018), and movement ecology and collective
movement (Jolles et al.~2019).

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure1} \caption{Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.}\label{fig:unnamed-chunk-1}
\end{figure}

\hypertarget{scale-in-multilayer-networks-a-case-study}{%
\section{Scale in multilayer networks: a case study}\label{scale-in-multilayer-networks-a-case-study}}

\hypertarget{caribou-socioecology}{%
\subsection{Caribou socioecology}\label{caribou-socioecology}}

Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics (Lesmerises, Johnson, and St-Laurent 2018) that display temporal
(Peignier et al. 2019) and spatial (Webber et al.~unpublished data) variation in
social networks. In winter, caribou dig holes in the snow, termed craters, to
access forage (Bergerud 1974). As a result, caribou tend to occupy
and re-use craters once they are established and there is considerably less
access to forage than when the landscape is snow-free. Importantly, craters
exist on the landscape at multiple scales: the crater scale (a single crater),
the feeding area scale (multiple craters in close proximity), and the winter
range scale (all craters within an individual's range) (Mayor et al. 2009). The
distribution of forage for caribou is therefore seasonally heterogeneous, with
greater access in snow-free seasons compared to winter as well as spatially
heterogeneous in winter because the distribution of craters on the landscape
varies meaning that access to vegetation in winter is highly variable for
caribou. We therefore partitioned data into two discrete seasons: summer (3
August - 20 September) and winter (1 January -- 17 February) based on caribou
socioecology (Peignier et al. 2019).

\hypertarget{caribou-location-data}{%
\subsection{Caribou location data}\label{caribou-location-data}}

We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
Adult female caribou were immobilized and fitted with global positioning system
(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to
collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
et al. (2010). We did not collar all female caribou in the herd;
however, we assumed that our sample of collared animals was random.

\hypertarget{landscape-data-and-habitat-classification}{%
\subsection{Landscape data and habitat classification}\label{landscape-data-and-habitat-classification}}

Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at 10m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
 consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest habitat types. Water habitat was excluded from all
subsequent analyses.

\hypertarget{caribou-multilayer-social-networks}{%
\subsection{Caribou multilayer social networks}\label{caribou-multilayer-social-networks}}

\hypertarget{network-types-and-construction-defining-layers-for-the-multilayer-network}{%
\subsubsection{Network types and construction (defining layers for the multilayer network)}\label{network-types-and-construction-defining-layers-for-the-multilayer-network}}

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were the social association network generated in
each season and landcover combination. Proximity-based social network layers
were generated using the R package \texttt{spatsoc} (Robitaille, Webber, and Wal 2019) in R version 3.6.1 (2019-07-05) (R Core Team 2019).

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes (i.e., recorded within 5 minutes of each other) were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the `chain rule' is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
(Robitaille, Webber, and Wal 2019). Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises, Johnson, and St-Laurent 2018). In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts.

We weighted edges of social networks by the strength of association between
caribou using the simple ratio index (SRI, Cairns and Schwager 1987):

\[ SRI = \frac{x}{x + y_{AB} + y_{A} + y_{B}} \]

where x is the number of fixes where individuals A and B were within a given
distance of each other, \(y_{A}\) is the number of fixes from individual A when
individual B did not have a simultaneous fix, \(y_{B}\) is the number of fixes
from individual B when individual A did not have a simultaneous fix, and
\(y_{AB}\) is the number of simultaneous fixes from individuals A and B that were
separated by more than the given distance (Farine and Whitehead 2015). Social groups were
designated if two or more individuals occurred within a given distance of one
another at any given time point.

\hypertarget{network-metrics}{%
\subsubsection{Network metrics}\label{network-metrics}}

We used a series of metrics to characterize the multilayer networks focusing on
the relevance of individual layers, similarity of layers and the role of
individuals. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
(Berlingerio et al. 2012; Kivela et al. 2014). Comparing the multidegree and number of
unique neighbours, we measured the connective redundancy, the proportion of
neighbours repeated in multiple layers, and the layer relevance, the proportion
of neighbours present compared to the neighbourhood for each individual
(Berlingerio et al. 2012). To measure the role of individuals, we calculated the graph
strength for each individual for each layer specific season and landcover
context . Finally, we calculated the similarity of layers
between seasons, across landcover classes (e.g.: winter open compared to summer
open) using the Pearson correlation coefficient (Br\a'odka et al. 2018).

\hypertarget{varying-scale-in-multilayer-networks}{%
\subsection{Varying scale in multilayer networks}\label{varying-scale-in-multilayer-networks}}

\hypertarget{social-scale}{%
\subsubsection{Social scale}\label{social-scale}}

We altered social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou . Specifically, we modified
the spatial distance threshold required for group assignment (see above) and
re-assigned groups at incremental distance between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

\hypertarget{spatial-scale}{%
\subsubsection{Spatial scale}\label{spatial-scale}}

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover classification map at varying scales relevant to caribou ecology.
We aggregated the 10m landcover raster using the R package \texttt{grainchanger}
(L. Graham 2019) at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales (L. J. Graham et al. 2019). 10m and 100m represents fine-scale decision making
for caribou during foraging , while re-sampling at 500m and 1000m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al.~2017).

\hypertarget{temporal-scale}{%
\subsubsection{Temporal scale}\label{temporal-scale}}

We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (1 January)
and summer (3 August). The position of the time window was shifted by 1-48 days,
using a fixed time window length of 48 days. These new time windows were
iteratively used to partition data into two discrete seasons (winter, summer)
and generate multilayer networks.

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al.~2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of
the number of observations on resulting multilayer networks. We randomly
selected 500 timesteps and iteratively included 25 additional observations,
regenerating the multilayer network and calculating associations of individuals.
Subsequent iterations included the previous set of observations to mimic
observational data.

\hypertarget{scale-in-multilayer-networks-in-practice-case-study-results-and-discussion}{%
\section{Scale in multilayer networks in practice: case study results and discussion}\label{scale-in-multilayer-networks-in-practice-case-study-results-and-discussion}}

We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale.

In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season. As social scale increased, connective redundancy increased rapidly when groups were formed based on \textasciitilde{}100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at \textasciitilde{}500m (Figure 3b). Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c). Finally, somewhat predictably, graph strength for winter networks increased up to \textasciitilde{}100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d). Taken together, these results suggest the optimal social scale at which groups should be assigned is likely somewhere between \textasciitilde{}20-100m based on the rate at which network metrics stabilized. For ungulates, groups are often assigned based on 50m threshold (Lingle 2003; Lesmeries et al.~2018; Peignier et al.~2019), suggesting that given similar quantities of data, \textasciitilde{}50m is likely an ideal social scale for generating social networks in caribou and similar species.

\hypertarget{each-metrics-interpretation}{%
\subsection{Each metric's interpretation}\label{each-metrics-interpretation}}

\begin{itemize}
\item
  Multidegree: sum of degree across layers. High multidegree = connected to many
  individuals across layers. Low multidegree = not connected to many individuals
  across layers.
\item
  Degree deviation: deviation of degree across layers. High degree deviation =
  large difference between degree for an individual across layers. Low degree
  deviation = individuals are similarly connected across layers.
\item
  Graph strength: weighted version of degree. High graph strength = highly
  connected. Not summed in this case across layers.
\item
  Neighbours: number of unique individuals adjacent to each actor. Considered in
  a single layer, this is equal to the degree.
\item
  Neighbourhood: number of unique individuals across all layers. High
  neighbourhood = a high number of unique individuals connected to an actor.
\item
  Relevance: layer centric metric, corresponding to the number of neighbours on a
  layer divided by the total neighbourhood for each actor. High relevance means
  that the layer is highly relevant to the individuals connections. A low
  relevance means this layer does not contribute many neighbours to an individuals
  overall neighbourhood.
\item
  Connective redundancy: the total multilayer neighbourhood divided by the
  multidegree. High connective redundancy indicates a multilayer network that has
  many repeated edges across layers between an actor and its neighbours. Low
  connective redundancy indicates that each layer is important for preserving all
  social ties.
\item
  Layer similarity: how similar each layer is (Brodka 2018). Pearson's
  correlation coefficient of degree vectors for each layer, comparing each
  landcover across seasons.
\end{itemize}

\hypertarget{figure-captions-and-brief-interpretations}{%
\subsection{Figure captions and brief interpretations}\label{figure-captions-and-brief-interpretations}}

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure-spatialthreshold} \caption{Varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.\textbf{{[}JWT: what about forest. This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend{]}} B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau of about 0.65 \textbf{{[}JWT: Does this have units??{]}} at approximately a 50m \textbf{??} social threshold before decreasing between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections. \textbf{{[}JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI. I would talk about it more about strong/weak connections. Networks can be sparse (few connections), but still have high strength if the ties have higher values{]}}}\label{fig:unnamed-chunk-2}
\end{figure}

\begin{itemize}
\tightlist
\item
  decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
\item
  decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
\item
  decreasing winter lichen relevance because the degree + number of edges decreased
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure-lcres} \caption{Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions. D) Mean graph strength of individuals was weaker during the summer compared to the winter months.}\label{fig:unnamed-chunk-3}
\end{figure}

\begin{itemize}
\tightlist
\item
  common, though at different points - more observations until stabilizing
\item
  we dont see the stabilizing/full plateau for connective redundancy but appears to be coming..
\item
  still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure-nobs} \caption{Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. \emph{There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.} \textbf{Brief explanation of why two landcover don't have values at lower nobs??}. B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{itemize}
\tightlist
\item
  increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
\item
  increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
\item
  decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
\item
  layers are more similarly relevant at high window length
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure-winlength} \caption{Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window \textbf{{[}JWT: previously this was describing fig. 3. I don't know if what I wrote best encapsulates what connnective redundancy does here. Length of time window seems to make connective redundancy highly variable as it changes.{]}}. C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer. D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. \textbf{{[}see if you agree with my changes. B-D were based off fig. 3 and not relevant to this figure{]}}}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{itemize}
\tightlist
\item
  increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
\item
  same theme shown in the connective redundancy
\item
  quite variable layer similarity, not sure what to pull out of that one
\item
  increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{../graphics/figure-winpos} \caption{Varying scale in time window position. For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows. \textbf{{[}JWT: previously describing window length, not position. Check that you're ok with my changes{]}} B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.}\label{fig:unnamed-chunk-6}
\end{figure}

\hypertarget{perspectives-to-advance-multilayer-networks}{%
\section{Perspectives to advance multilayer networks}\label{perspectives-to-advance-multilayer-networks}}

The integration of behavioural and ecological theory has shown the value of considering the importance of scale to better understand and predict animal social networks, including demography (Shizuka and Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.~2017), and animal personality (Sih et al.~2017). While the number of studies integrating social network theory into a broader array of behavioural and ecological sub-disciplines is impressive, only recently has the role of animal space use been been considered in describing the causes and consequences of the social environment in the context of (1) Individual fitness and phenotypes (Webber \& Vander Wal 2018), (2) habitat selection and space use (He et al.~2019), and (3) movement ecology and collective movement (Bode et al.~2011). Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of social network theory and application.

\hypertarget{habitat-selection-and-space-use}{%
\subsection{Habitat selection and space use}\label{habitat-selection-and-space-use}}

\begin{itemize}
\tightlist
\item
  Mayor et al.~2009 paper
\item
  MRSF Laforge paper
\item
  van Beest et al.~2014 scale paper
\item
  1st/2nd/3rd order selection
\item
  Habitat--performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
\item
  Multi-scale habitat selection modeling: a review and outlook
\end{itemize}

\hypertarget{individual-fitness-and-phenotypes}{%
\subsection{Individual fitness and phenotypes}\label{individual-fitness-and-phenotypes}}

Social network positions are frequently used to represent the social environment
that an individual experiences or their social phenotype. Social phenotypes are
increasingly linked to important fitness for individuals of various species,
including primates (e.g.~Brent, Ruiz-Lambides, \& Platt, 2017; Thompson, 2019),
dolphins (e.g.~Stanton \& Mann, 2012; Stanton, Gibson, \& Mann, 2011), and birds
(e.g.~McDonald, 2007; Royle, Pike, Heeb, Richner, \& Kolliker, 2012). Both
temporal, seasons and stages of life, and social scales, types of interactions,
have emerged as important for understanding fitness consequences in the context
of social network positions (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, \&
Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, \& Cohas, 2015; Brent,
Ruiz-Lambides, \& Platt, 2017; Holekamp, Smith, Strelioff, Van Horn, \& Watts,
2012). Multilayer networks provide a way to bridge these different scales so
that we can examine social phenotypes in more holistic ways rather than looking
at each scale separately as has traditionally been done.

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question (Carter, Lee, \& Marshall, 2015; Castles et al., 2014; Farine, 2015).
Furthermore, it is a common trope that individuals must be associating to
interact, and many studies therefore assume that proximity is proxy for
interacting (Farine, 2015). For instance, baboons need to be in proximity in
order to groom each other. However, animals have certain interactions that do
not require proximity such as long-distance vocalization and olfactory signals
(Carter et al., 2015). With the advancement of biologging technology, we have
the ability to record social interactions that do not require proximity,
particularly long-distance communication networks with devices like microphone
arrays (Snijders \& Naguib, 2017). These varying social scales can have different
fitness repercussions for individuals. Rhesus macaques (\emph{Macaca mulatta}) had
higher survivorship when they had fewer but stronger, more stable social
associates and grooming partners rather than simply more associates (Ellis,
Snyder-Mackler, Ruiz-Lambides, Platt, \& Brent, 2019). This finding highlights
that different qualities of social scales have lasting consequences.

Temporal scale is also important for understanding the repercussions of social
phenotypes. For instance, social phenotypes can change over ontogeny in ways
that can affect fitness (Berger et al., 2015; Brent et al., 2017). Thus, it is
critical to carefully consider the temporal scale that is meaningful for the
proposed hypotheses. Further complicating the issue of selecting suitable time
scales across ontogeny, individuals progress through development at different
rates (Tarka, Guenther, Niemelä, Nakagawa, \& Noble, 2018). This variation can
make defining appropriate temporal scales for testing the fitness implications
of an individual's social phenotype over different stages of ontogeny even more
difficult when they vary by individual. However, considering fine temporal
scales provide insight across developmental stages that may otherwise be missed
(Turner, Bills, \& Holekamp, 2018).

Multilayer networks provide unique opportunities and challenges, linking these
various scales, for understanding the social phenotypes and environments of
individuals and their fitness outcomes. The multilayer network framework enables
researchers to examine these different social scales simultaneously rather than
individually, which is what has been done under most circumstances, but is not
very realistic. Metrics from multilayer networks provide an opportunity to
simplify statistical models. Interactions that happen side-by-side, proximity
associations, and long-distance interactions can be encapsulated in a single
multilayer network, and a single metric can be used to describe the various
social scales of an individual's network position. This multilevel network
metric could be used to assess the relationship between an individual's social
phenotype and fitness. It would also be a meaningful simplification of many
network metrics that could help simplify statistical analyses and deal with the
frequent correlations between social network metrics in different types of
networks (Castles et al., 2014). Furthermore, multilayer networks provide a
framework to test hypotheses linking social phenotypes and fitness across
temporal scales. Because of the non-independent nature of social interactions
and associations, especially over time, it is hard to test hypotheses about
social dynamics with a suitable null control (Farine, 2017; Proskurnikov \&
Tempo, 2017). Using the framework of multilayer networks, making layers of
different temporal periods provides a way to make appropriate null models to
test questions about the dynamics of an individual's social network position
over multiple aggregated time periods.

On the other hand, picking the proper temporal scale is important but a
challenge because all layers in the multilayer network should reflect the same
time period, and the period should be long enough for each layer to have enough
data for robust networks (Farine, 2017). These considerations may be limiting
factors when answering questions that require timeframes that are relevant to
different individuals, for instance. In both mono- and multilayer networks, the
effect of scale on the relationship between an individual's social network
position and fitness need to be considered based on the hypotheses being tested
and logistical constraints.

\hypertarget{movement-ecology-and-collective-movement}{%
\subsection{Movement ecology and collective movement}\label{movement-ecology-and-collective-movement}}

Animal movement undoubtedly affects an individual's social environment
(Strandburg-Peshkin et al.~2015). Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al.~2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al.~2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g.~Mourier et al.~2019).

Although multilayer animal social networks are relatively novel (Silk et
al.~2018), movement behaviour within multilayer networks has already been considered
in a couple studies. In vulturine gunieafowl (\emph{Acryllium vulturinum}), GPS
movement data were used to generate \emph{monolayer} association networks within a
multilayer network (Papageorgiou et al.~2019). In addition, \emph{spatial networks}
are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (\emph{Carcharhinus amblyrhynchos} and \emph{Carcharhinus
melanopterus}) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, \emph{intralayer edges} represent individual
movement frequency, and \emph{interlayer edges} represent contact probability among
individuals at a given node (Mourier et al.~2019). While both studies integrate
movement in some capacity, neither generate networks based on continuous
measures of dyadic or collective movement (Long et al.~2014).

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. Continuous collection of animal
relocation data using GPS technology can be used to measure how groups of
animals make collective movement decisions in the context of their local
environment (Strandburg-Peshkin et al.~2015, 2017) and across scales. A
collective movement layer could constitute similarity in movement for dyads
(Long et al.~2014) or groups (Bode et al.~2011). This movement layer could be
made at a fine (i.e.~minute-to-minute: Cleasby et al.~2019) or coarse scale
(global migration: Flack et al.~2018). Another potential application would be to
generate social networks during times when animals are engaged in different
behaviours, including traveling, interacting, or foraging (e.g.~Muller et
al.~2018; Finn et al.~2019) and construct a multilayer network based on
behaviour-specific monolayer networks (e.g.~Smith-Aguilar et al.~2019).
Importantly, the key to incorporating movement in multilayer networks across
scales is the technological advancements available to overcome previous
limitations (see Hughey et al.~2018).

Given the existing framework for constructing multilayer networks from
behavioural layers (e.g.~Smith-Aguilar et al.~2019), movement layers could be
integrated with interaction or association layers. Integrating movement layers
with habitat-specific social association layers could further shed light on the
role of movement as a driver of the social and spatial environments an
individual experiences (Webber and Vander Wal 2018). In our case study, we
generated multilayer networks based on habitat-specific monolayers. Coordinated
movement of dyads, or groups, could vary based on habitat, and the approach we
outline could be used to explore mechanisms linking the social and spatial
environments. For example, social processes may be an emergent property of the
landscape because animals aggregate at resources, such as waterholes
(Chamaillé-Jammes et al.~2008). Movement to, from, or within habitat patches or
territories can also contribute to the formation of the social environment
(Spiegel et al.~2016). For example, in sleepy lizards (\emph{Tiliqua rugosa}) males
interacted primarily at home range edges, presumably driving territorial
behaviour (Spiegel et al.~2018). Incorporating movement ecology within a
multilayer network framework is a logical next step for a burgeoning field. In
particular, when association networks are habitat-specific, we suggest the
integration of movement and space use in multilayer networks provides novel
insights into the effects of habitat configuration on the formation of the
social environment (He et al.~2019).

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

something something blah blah.

Silk et al. (2018) presented some key multilayer questions in animal behaviour
research. While these questions represent an important starting point for
multilayer networks, we present an additional set of questions relevant to the
promise and problem of scale in mutlilayer networks:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  How do social phenotypes across scales differently influence fitness? Are
  some temporal or social scales better predictors for different fitness metrics?
\item
  Why do individuals associate more strongly with certain conspecifics in some
  habitats? What, if any, is the role of movement in the context of habitat
  networks?
\item
  How, and why, does the spatial scale of perception influence, e.g.~auditory,
  visual, or chemotaxis, influence the social environment across scales? What is
  the role of memory, and by extension social and spatial cognition, as animals
  navigate their environment and make decisions about where to move next?
\end{enumerate}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

We thank all members of the Wildlife Evolutionary Ecology Lab, including J. Hendrix, K.
Kingdon, S. Boyle, C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
their comments on previous versions of this manuscript as well as D. C. Schneider
for inspiration and helpful discussions about scale. Funding for this study was
provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
Grant to EVW.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allen_2015}{}%
Allen, Timothy F. H., and Thomas W. Hoekstra. 2015. \emph{Toward a Unified Ecology}. Columbia University Press. \url{https://doi.org/10.7312/alle06918}.

\leavevmode\hypertarget{ref-Berlingerio_2012}{}%
Berlingerio, Michele, Michele Coscia, Fosca Giannotti, Anna Monreale, and Dino Pedreschi. 2012. ``Multidimensional Networks: Foundations of Structural Analysis.'' \emph{World Wide Web} 16 (5-6). Springer Science; Business Media LLC: 567--93. \url{https://doi.org/10.1007/s11280-012-0190-4}.

\leavevmode\hypertarget{ref-Br_dka_2018}{}%
Br\a'odka, Piotr, Anna Chmiel, Matteo Magnani, and Giancarlo Ragozini. 2018. ``Quantifying Layer Similarity in Multiplex Networks: A Systematic Study.'' \emph{Royal Society Open Science} 5 (8). The Royal Society: 171747. \url{https://doi.org/10.1098/rsos.171747}.

\leavevmode\hypertarget{ref-Chave_2013}{}%
Chave, J\a'erôme. 2013. ``The Problem of Pattern and Scale in Ecology: What Have We Learned in 20~Years?'' Edited by Jordi Bascompte. \emph{Ecology Letters} 16 (January). Wiley: 4--16. \url{https://doi.org/10.1111/ele.12048}.

\leavevmode\hypertarget{ref-Elith_2009}{}%
Elith, Jane, and John R. Leathwick. 2009. ``Species Distribution Models: Ecological Explanation and Prediction Across Space and Time.'' \emph{Annual Review of Ecology, Evolution, and Systematics} 40 (1). Annual Reviews: 677--97. \url{https://doi.org/10.1146/annurev.ecolsys.110308.120159}.

\leavevmode\hypertarget{ref-Farine_2015}{}%
Farine, Damien R., and Hal Whitehead. 2015. ``Constructing, Conducting and Interpreting Animal Social Network Analysis.'' Edited by Sonia Altizer. \emph{Journal of Animal Ecology} 84 (5). Wiley: 1144--63. \url{https://doi.org/10.1111/1365-2656.12418}.

\leavevmode\hypertarget{ref-Field_2009}{}%
Field, Richard, Bradford A. Hawkins, Howard V. Cornell, David J. Currie, J. Alexandre F. Diniz-Filho, Jean-François Gu\a'egan, Dawn M. Kaufman, et al. 2009. ``Spatial Species-Richness Gradients Across Scales: A Meta-Analysis.'' \emph{Journal of Biogeography} 36 (1). Wiley: 132--47. \url{https://doi.org/10.1111/j.1365-2699.2008.01963.x}.

\leavevmode\hypertarget{ref-Graham_2019}{}%
Graham, Laura. 2019. \emph{Grainchanger: Moving-Window and Direct Data Aggregation}. \url{https://github.com/ropensci/grainchanger}.

\leavevmode\hypertarget{ref-Graham_2019a}{}%
Graham, Laura J., Rebecca Spake, Simon Gillings, Kevin Watts, and Felix Eigenbrod. 2019. ``Incorporating Fine-Scale Environmental Heterogeneity into Broad-Extent Models.'' Edited by Nick Isaac. \emph{Methods in Ecology and Evolution} 10 (6). Wiley: 767--78. \url{https://doi.org/10.1111/2041-210x.13177}.

\leavevmode\hypertarget{ref-Kivela_2014}{}%
Kivela, M., A. Arenas, M. Barthelemy, J. P. Gleeson, Y. Moreno, and M. A. Porter. 2014. ``Multilayer Networks.'' \emph{Journal of Complex Networks} 2 (3). Oxford University Press (OUP): 203--71. \url{https://doi.org/10.1093/comnet/cnu016}.

\leavevmode\hypertarget{ref-Legendre_1993}{}%
Legendre, Pierre. 1993. ``Spatial Autocorrelation: Trouble or New Paradigm?'' \emph{Ecology} 74 (6). Wiley: 1659--73. \url{https://doi.org/10.2307/1939924}.

\leavevmode\hypertarget{ref-Lesmerises_2018}{}%
Lesmerises, Fr\a'ed\a'eric, Chris J. Johnson, and Martin-Hugues St-Laurent. 2018. ``Landscape Knowledge Is an Important Driver of the Fission Dynamics of an Alpine Ungulate.'' \emph{Animal Behaviour} 140 (June). Elsevier BV: 39--47. \url{https://doi.org/10.1016/j.anbehav.2018.03.014}.

\leavevmode\hypertarget{ref-Levin_1992}{}%
Levin, Simon A. 1992. ``The Problem of Pattern and Scale in Ecology: The Robert H. MacArthur Award Lecture.'' \emph{Ecology} 73 (6). Wiley: 1943--67. \url{https://doi.org/10.2307/1941447}.

\leavevmode\hypertarget{ref-Luther_2009}{}%
Luther, David. 2009. ``The Influence of the Acoustic Community on Songs of Birds in a Neotropical Rain Forest.'' \emph{Behavioral Ecology} 20 (4). Oxford University Press (OUP): 864--71. \url{https://doi.org/10.1093/beheco/arp074}.

\leavevmode\hypertarget{ref-Mayor_2007}{}%
Mayor, S. J., J. A. Schaefer, D. C. Schneider, and S. P. Mahoney. 2007. ``SPECTRUM OF SELECTION: NEW APPROACHES TO DETECTING THE SCALE-DEPENDENT RESPONSE TO HABITAT.'' \emph{Ecology} 88 (7). Wiley: 1634--40. \url{https://doi.org/10.1890/06-1672.1}.

\leavevmode\hypertarget{ref-Mayor_2009}{}%
Mayor, Stephen J., David C. Schneider, James A. Schaefer, and Shane P. Mahoney. 2009. ``Habitat Selection at Multiple Scales.'' \emph{Écoscience} 16 (2). Informa UK Limited: 238--47. \url{https://doi.org/10.2980/16-2-3238}.

\leavevmode\hypertarget{ref-Peignier_2019}{}%
Peignier, M\a'elissa, Quinn M. R. Webber, Erin L. Koen, Michel P. Laforge, Alec L. Robitaille, and Eric Vander Wal. 2019. ``Space Use and Social Association in a Gregarious Ungulate: Testing the Conspecific Attraction and Resource Dispersion Hypotheses.'' \emph{Ecology and Evolution} 9 (9). Wiley: 5133--45. \url{https://doi.org/10.1002/ece3.5071}.

\leavevmode\hypertarget{ref-R_Core_Team_2019}{}%
R Core Team. 2019. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.

\leavevmode\hypertarget{ref-Robitaille_2019}{}%
Robitaille, Alec L., Quinn M. R. Webber, and Eric Vander Wal. 2019. ``Conducting Social Network Analysis with Animal Telemetry Data: Applications and Methods Using Spatsoc.'' Edited by Nick Golding. \emph{Methods in Ecology and Evolution} 10 (8). Wiley: 1203--11. \url{https://doi.org/10.1111/2041-210x.13215}.

\leavevmode\hypertarget{ref-Sugihara_1989}{}%
Sugihara, G, K Schoenly, and A Trombla. 1989. ``Scale Invariance in Food Web Properties.'' \emph{Science} 245 (4913). American Association for the Advancement of Science (AAAS): 48--52. \url{https://doi.org/10.1126/science.2740915}.

\end{document}

### 2020-02-03 paper/manuscript.Rmd
reorg perspectives

@@
 
-To date, behavioural ecology and social network researchers have made progress in describing the causes and consequences of the social environment in the context of (1) habitat selection and space use, (2) Individual fitness and phenotypes, and (3) movement ecology and collective movement.
-Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of spatial ecosystem ecology.
-
-## Habitat selection and space use
-
-* Mayor et al. 2009 paper 
-* MRSF Laforge paper 
-* van Beest et al. 2014 scale paper 
-* 1st/2nd/3rd order selection
-* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
-* Multi-scale habitat selection modeling: a review and outlook
+The integration of behavioural and ecological theory has shown the value of considering the importance of scale to better understand and predict animal social networks, including demography (Shizuka and Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
+2017), and animal personality (Sih et al.
+2017).
+While the number of studies integrating social network theory into a broader array of behavioural and ecological sub-disciplines is impressive, only recently has the role of animal space use been been considered in describing the causes and consequences of the social environment in the context of (1) Individual fitness and phenotypes (Webber & Vander Wal 2018), (2) habitat selection and space use (He et al.
+2019), and (3) movement ecology and collective movement (Bode et al.
+2011).
+Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of social network theory and application.
 
@@
 
+## Habitat selection and space use
+
+* Mayor et al. 2009 paper 
+* MRSF Laforge paper 
+* van Beest et al. 2014 scale paper 
+* 1st/2nd/3rd order selection
+* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
+* Multi-scale habitat selection modeling: a review and outlook
+
 # Conclusions

### 2020-02-03 paper/manuscript.Rmd
unitless

@@
 ## Each metric's interpretation
+**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
+* Degree: the number of direct connections an individual has to other individuals in the network.
+High degree = connected to many indviduals in a single layer.
+Low degree = not connected to many individuals in a single layer.
+
 * Multidegree: sum of degree across layers. High multidegree = connected to many
@@
 
-* Degree deviation: deviation of degree across layers. High degree deviation =
+* Degree deviation: standard **[??]** deviation of degree across layers. High degree deviation =
 large difference between degree for an individual across layers. Low degree
@@
 
-* Graph strength: weighted version of degree. High graph strength = highly
-connected. Not summed in this case across layers.
+* Graph strength: the sum of all the edge weights directly connected to an actor, sometimes called weigthed degree.
+High graph strength = highly social, connected to many individuals and/or having stronger, high-valued connections between individuals.
+Low graph strength = not very social, connected to few individuals and/or having weak, low-valued connections between individuals.
+Not summed in this case across layers.
 
@@
 * Neighbourhood: number of unique individuals across all layers. High
-neighbourhood = a high number of unique individuals connected to an actor.
+neighbourhood = a high number of unique individuals connected to an actor. Low
+neighbourhood = a low number of unique individuals connected to an actor.
 
@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.
-This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 **[JWT: Does this have units??]** at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
+This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
 C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.

### 2020-02-03 paper/manuscript.Rmd
legend lines fixed

@@
 For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.
-This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
 C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.

### 2020-02-03 paper/manuscript.Rmd
editing Each metric's interpretation

--- 2020-02-03 paper/manuscript.Rmd
@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.
-This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
+This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 **[JWT: Does this have units??]** at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
 C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
@@
 Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of social network theory and application.
+
+## Habitat selection and space use
+
+* Mayor et al. 2009 paper 
+* MRSF Laforge paper 
+* van Beest et al. 2014 scale paper 
+* 1st/2nd/3rd order selection
+* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
+* Multi-scale habitat selection modeling: a review and outlook
 
@@
 
-## Habitat selection and space use
-
-* Mayor et al. 2009 paper 
-* MRSF Laforge paper 
-* van Beest et al. 2014 scale paper 
-* 1st/2nd/3rd order selection
-* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
-* Multi-scale habitat selection modeling: a review and outlook
-
 # Conclusions

### 2020-02-03 paper/manuscript.Rmd
reflow
mv metric interpretations into comment

--- 2020-02-03 paper/manuscript.Rmd
@@
 
-In general, individuals in multilayer networks became more connected as a function of social scale, however, this relationship varied by habitat type and season.
-As social scale increased, connective redundancy increased rapidly when groups were formed based on ~100m threshold, followed by a plateau and slight decrease at higher thresholds, presumably due to an increase in summer forest degree at ~500m (Figure 3b).
-Regardless of social scale, layer relevance did not change for any habitat types or seasons, which suggests habitat-by-season layers captured most, if not all, of the potential connections and individual would have across all networks (Figure 3c).
-Finally, somewhat predictably, graph strength for winter networks increased up to ~100-200m thresholds, followed by a plateau, while graph strength for summer networks did not change as the social threshold increased (Figure 3d).
-Taken together, these results suggest the optimal social scale at which groups should be assigned is likely somewhere between ~20-100m based on the rate at which network metrics stabilized.
-For ungulates, groups are often assigned based on 50m threshold (Lingle 2003; Lesmeries et al.
-2018; Peignier et al.
-2019), suggesting that given similar quantities of data, ~50m is likely an ideal social scale for generating social networks in caribou and similar species.
+In general, individuals in multilayer networks became more connected as a
+function of social scale, however, this relationship varied by habitat type and
+season. As social scale increased, connective redundancy increased rapidly when
+groups were formed based on ~100m threshold, followed by a plateau and slight
+decrease at higher thresholds, presumably due to an increase in summer forest
+degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not
+change for any habitat types or seasons, which suggests habitat-by-season layers
+captured most, if not all, of the potential connections and individual would
+have across all networks (Figure 3c). Finally, somewhat predictably, graph
+strength for winter networks increased up to ~100-200m thresholds, followed by a
+plateau, while graph strength for summer networks did not change as the social
+threshold increased (Figure 3d).  Taken together, these results suggest the
+optimal social scale at which groups should be assigned is likely somewhere
+between ~20-100m based on the rate at which network metrics stabilized. For
+ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
+Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
+quantities of data, ~50m is likely an ideal social scale for generating social
+networks in caribou and similar species.
 
+<!--
 ## Each metric's interpretation
+
 **[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
@@
 landcover across seasons.
+
+-->
 

### 2020-02-03 paper/manuscript.Rmd
rm header fig caps+interprets
edit network metrics

--- 2020-02-03 paper/manuscript.Rmd
@@
 ### Network metrics
-We used a series of metrics to characterize the multilayer networks focusing on
-the relevance of individual layers, similarity of layers and the role of
-individuals. We calculated multidegree, the sum of degree centrality across
-layers, and neighbourhood, the sum of unique neighbours to each individual
-[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
+We used a series of metrics to characterize the multilayer networks, focusing on
+the the role of individuals and the similarity and relevance of individual layers. Degree
+centrality, the number of direct connections an individual has to other individuals in the
+network, is the basis of many calculations. We calculated multidegree, the sum of degree
+centrality across layers, and neighbourhood, the sum of unique neighbours to each
+individual[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
 unique neighbours, we measured the connective redundancy, the proportion of
@@
 [@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
-strength for each individual for each layer specific season and landcover
-context <!-- citation?-->. Finally, we calculated the similarity of layers
-between seasons, across landcover classes (e.g.: winter open compared to summer
-open) using the Pearson correlation coefficient [@Br_dka_2018].
+strength, degree weighted by the values of the tie, for each individual for each 
+layer-specific season and landcover context <!-- citation?-->. Finally, we calculated the 
+similarity of layers between seasons, across landcover classes (e.g.: winter open compared 
+to summer open) using the Pearson correlation coefficient [@Br_dka_2018].
 
@@
 * Relevance: layer centric metric, corresponding to the number of neighbours on a
-layer divided by the total neighbourhood for each actor. High relevance means
-that the layer is highly relevant to the individuals connections. A low
+layer divided by the total neighbourhood for each actor. High relevance = the layer is highly relevant to the individuals connections. A low
 relevance means this layer does not contribute many neighbours to an individuals
@@
 Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of social network theory and application.
-
-## Habitat selection and space use
-
-* Mayor et al. 2009 paper 
-* MRSF Laforge paper 
-* van Beest et al. 2014 scale paper 
-* 1st/2nd/3rd order selection
-* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
-* Multi-scale habitat selection modeling: a review and outlook
 

### 2020-02-03 paper/manuscript.Rmd

--- 2020-02-03 paper/manuscript.Rmd
@@
 -->
-
-## Figure captions and brief interpretations
 

### 2020-02-03 paper/manuscript.Rmd
minor edits and proper todos

@@
 scale can affect multilayer network dynamics and how we build and interpret
-them. Here, we discuss the role of scale in the context of multilayer networks
+them. Here we discuss the role of scale in the context of multilayer networks
 and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role
-of social,spatial, and temporal scale on multilayer processes. We also present
+of social, spatial, and temporal scale on multilayer processes. We also present
 perspectives on future development and application of scale in multilayer
 networks with respect to habitat selection and space use, individual fitness and
-phenotypes, and movement ecology and collective movement.Effective integration
+phenotypes, and movement ecology and collective movement. Effective integration
 of social and spatial processes, including biologically meaningful scales,
@@
 development and application of scale in multilayer networks with respect to
-habitat selection and space use (REF)<!-- TODO-->, individual fitness and
+habitat selection and space use <!-- TODO: (REF)-->, individual fitness and
 phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
@@
 (ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
+
+<!-- TODO: units of spatial scale? -->
 
@@
 social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage (Bergerud 1974)<!-- TODO-->. As a result, caribou tend to occupy
+access forage (Bergerud 1974)<!-- TODO: get Bergerud ref-->. As a result, caribou tend to occupy
 and re-use craters once they are established and there is considerably less
@@
 into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
-et al. (2010)<!-- TODO-->. We did not collar all female caribou in the herd;
+et al. (2010)<!-- TODO: get Bjorneraas ref-->. We did not collar all female caribou in the herd;
 however, we assumed that our sample of collared animals was random.
@@
 Available landcover classification included nine habitat types at <!-- TODO:
-double check --> 10m resolution. We reclassified the landcover types into three
+double check lc res--> 10m resolution. We reclassified the landcover types into three
 categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
-<!-- or just lichen like figs?--> consisted of lichen habitat, open habitat
+<!-- TODO: "foraging" should be "lichen" ?--> consisted of lichen habitat, open habitat
 consisted of wetland, rocky barrens, and anthropogenic habitat types, while
@@
 subsequent analyses.
-<!-- using the raster package for R? -->
+<!-- TODO: cite the raster package for R? -->
 
@@
 ### Network types and construction (defining layers for the multilayer network)
-<!-- should use something like "using syntax from Kivela 2014..." or 
+<!-- TODO: should use something like "using syntax from Kivela 2014..." or 
 Following [@Kivela_2014]:
@@
 We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index (SRI, Cairns and Schwager 1987): <!-- TODO-->
+caribou using the simple ratio index (SRI, Cairns and Schwager 1987): <!-- TODO: get Cairns ref-->
 

### 2020-02-03 paper/manuscript.Rmd
edits metrics

@@
 We used a series of metrics to characterize the multilayer networks, focusing on
-the the role of individuals and the similarity and relevance of individual layers. Degree
-centrality, the number of direct connections an individual has to other individuals in the
-network, is the basis of many calculations. We calculated multidegree, the sum of degree
-centrality across layers, and neighbourhood, the sum of unique neighbours to each
-individual[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
-unique neighbours, we measured the connective redundancy, the proportion of
-neighbours repeated in multiple layers, and the layer relevance, the proportion
-of neighbours present compared to the neighbourhood for each individual
-[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
-strength, degree weighted by the values of the tie, for each individual for each 
-layer-specific season and landcover context <!-- citation?-->. Finally, we calculated the 
-similarity of layers between seasons, across landcover classes (e.g.: winter open compared 
-to summer open) using the Pearson correlation coefficient [@Br_dka_2018].
+the the role of individuals, relevance of individual layers and the similarity
+of different layers. To measure the role of individuals, we calculated the graph
+strength, degree weighted by the values of the edge, for each individual for
+each layer-specific season and landcover context <!-- TODO: citation for graph
+strength?-->. Degree centrality, the number of direct connections an individual
+has to other individuals in the network, is the basis of many calculations
+[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
+layers, and neighbourhood, the sum of unique neighbours to each individual
+[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
+we measured the connective redundancy, the proportion of neighbours repeated in
+multiple layers, and the layer relevance, the proportion of neighbours present
+in each layer compared to the neighbourhood for each individual
+[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
+seasons, across landcover classes (e.g.: winter open compared to summer open)
+using the Pearson correlation coefficient [@Br_dka_2018].
 

### 2020-02-03 paper/manuscript.Rmd
add raster cite

@@
 double check lc res--> 10m resolution. We reclassified the landcover types into three
-categories: foraging habitat, open habitat, and forest habitat. Foraging habitat
+categories: foraging habitat, open habitat, and forest habitat using the R package `raster` [@Hijmans_2019]. Foraging habitat
 <!-- TODO: "foraging" should be "lichen" ?--> consisted of lichen habitat, open habitat
@@
 subsequent analyses.
-<!-- TODO: cite the raster package for R? -->
 

### 2020-02-03 paper/citations.R

@@ -50,6 +50,9 @@ citep('10.1111/2041-210X.13215')
 # farine whitehead 2015
 citep('10.1111/1365-2656.12418')
 
+# raster package
+citep(citation('raster'))
+
 ## metrics
 # berlingerio 2012
 citep('10.1007/s11280-012-0190-4')

### 2020-02-03 paper/manuscript.Rmd
newpage
clarify edges and nodes
minor edits, todos

@@
 ```
+
+\newpage
 
@@
 and three landcover elementary-layers (open, forest and lichen) combined for a
-total of six layers. Layers were the social association network generated in
-each season and landcover combination. Proximity-based social network layers
-were generated using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019].
+total of six layers. Layers were composed of individuals represented as nodes
+and social associations represented as edges, for each season and landcover
+combination. Proximity-based social network layers were generated using the R
+package `spatsoc` [@Robitaille_2019] in `r version$version.string`
+[@R_Core_Team_2019].
 
@@
 
-We altered social scale based on visual (short distance) and auditory (long
-distance) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
-the spatial distance threshold required for group assignment (see above) and
-re-assigned groups at incremental distance between 5-500m. For example, at the
+We altered the social scale based on visual (short distance) and auditory (long
+distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we modified
+the spatial distance threshold required for group assignment using `spatsoc` [@Robitaille_2019] (see above) and
+re-assigned groups at incremental distances between 5-500m. For example, at the
 finest social scale, only individuals within 5m of one another were considered
@@
 To assess the influence of spatial scale on multilayer networks, we aggregated
-our landcover classification map at varying scales relevant to caribou ecology.
+our landcover raster at varying scales relevant to caribou ecology.
 We aggregated the 10m landcover raster using the R package `grainchanger`
@@
 above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
-for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m
+for caribou during foraging <!--TODO: REF-->, while re-sampling at 500m and 1000m
 represents the scale at which caribou tend to select and avoid habitat
@@
 ### Temporal scale
-
+<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
 We altered the temporal scale of multilayer networks by varying the length and
@@
 Subsequent iterations included the previous set of observations to mimic
-observational data.
+observational data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
 

### 2020-02-03 paper/manuscript.Rmd
reorg interpret points into results/discussion

@@
 
+<!-- landcover resolution
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+-->
+
+<!-- nobs 
+* common, though at different points - more observations until stabilizing
+* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
+* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
+-->
+
+<!-- win  length
+* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
+* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
+* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
+* layers are more similarly relevant at high window length
+-->
+
+<!-- win position
+* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
+* same theme shown in the connective redundancy
+* quite variable layer similarity, not sure what to pull out of that one
+* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
+-->
+
 <!--
 ## Each metric's interpretation
-
-**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
 * Degree: the number of direct connections an individual has to other individuals in the network.
@@
 
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
-
 ```{r, fig.cap='(ref:lcres)'}
@@
 
-<!-- RO first sentence... -->
-
+<!-- TODO: RO first sentence... -->
 (ref:nobs) Varying scale in number of observations.
@@
 D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
-
-* common, though at different points - more observations until stabilizing
-* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
-* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
 
@@
 
-* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
-* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
-* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
-* layers are more similarly relevant at high window length
-
 ```{r, fig.cap='(ref:winlen)'}
@@
 D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
-
-* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
-* same theme shown in the connective redundancy
-* quite variable layer similarity, not sure what to pull out of that one
-* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
 

### 2020-02-03 paper/manuscript.Rmd
switch fig cap comments to TODOs

@@
 For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest.]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
+<!--TODO: what about forest.--> B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m <!--TODO:**??**--> social threshold before decreasing between 400m and 500m.
 C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
 D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
-**[JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI.
-I would talk about it more about strong/weak connections.
-Networks can be sparse (few connections), but still have high strength if the ties have higher values]**
 
@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.
-B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+<!--TODO:*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.--> B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
 C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window **[JWT: previously this was describing fig.
+B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window <!--TODO:**[JWT: previously this was describing fig.
 3.
 I don't know if what I wrote best encapsulates what connnective redundancy does here.
-Length of time window seems to make connective redundancy highly variable as it changes.]**.
-C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
 D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
-**[see if you agree with my changes.
+<!--TODO:**[see if you agree with my changes.
 B-D were based off fig.
-3 and not relevant to this figure]**
+3 and not relevant to this figure]**-->
 
@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
-**[JWT: previously describing window length, not position.
-Check that you're ok with my changes]** B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+<!--TODO:**[JWT: previously describing window length, not position.
+Check that you're ok with my changes]**--> B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
 C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
@@
 
-something something blah blah.
-
 Silk et al. (2018) presented some key multilayer questions in animal behaviour

### 2020-02-04 paper/manuscript.Rmd
reflow
reflow and newpage for refs
fst draft habitat perspective

@@
 social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage (Bergerud 1974)<!-- TODO: get Bergerud ref-->. As a result, caribou tend to occupy
-and re-use craters once they are established and there is considerably less
-access to forage than when the landscape is snow-free. Importantly, craters
-exist on the landscape at multiple scales: the crater scale (a single crater),
-the feeding area scale (multiple craters in close proximity), and the winter
-range scale (all craters within an individual’s range) [@Mayor_2009]. The
-distribution of forage for caribou is therefore seasonally heterogeneous, with
-greater access in snow-free seasons compared to winter as well as spatially
-heterogeneous in winter because the distribution of craters on the landscape
-varies meaning that access to vegetation in winter is highly variable for
-caribou. We therefore partitioned data into two discrete seasons:  summer (3
-August - 20 September) and winter (1 January – 17 February) based on caribou
-socioecology [@Peignier_2019].
+access forage (Bergerud 1974)<!-- TODO: get Bergerud ref-->. As a result,
+caribou tend to occupy and re-use craters once they are established and there is
+considerably less access to forage than when the landscape is snow-free.
+Importantly, craters exist on the landscape at multiple scales: the crater scale
+(a single crater), the feeding area scale (multiple craters in close proximity),
+and the winter range scale (all craters within an individual’s range)
+[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
+heterogeneous, with greater access in snow-free seasons compared to winter as
+well as spatially heterogeneous in winter because the distribution of craters on
+the landscape varies meaning that access to vegetation in winter is highly
+variable for caribou. We therefore partitioned data into two discrete seasons:
+summer (3 August - 20 September) and winter (1 January – 17 February) based on
+caribou socioecology [@Peignier_2019].
 
@@
 into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
-et al. (2010)<!-- TODO: get Bjorneraas ref-->. We did not collar all female caribou in the herd;
-however, we assumed that our sample of collared animals was random.
+et al. (2010)<!-- TODO: get Bjorneraas ref-->. We did not collar all female
+caribou in the herd; however, we assumed that our sample of collared animals was
+random.
 
@@
 Available landcover classification included nine habitat types at <!-- TODO:
-double check lc res--> 10m resolution. We reclassified the landcover types into three
-categories: foraging habitat, open habitat, and forest habitat using the R package `raster` [@Hijmans_2019]. Foraging habitat
-<!-- TODO: "foraging" should be "lichen" ?--> consisted of lichen habitat, open habitat
-consisted of wetland, rocky barrens, and anthropogenic habitat types, while
-forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
-and mixed-wood forest habitat types. Water habitat was excluded from all
-subsequent analyses.
+double check lc res--> 10m resolution. We reclassified the landcover types into
+three categories: foraging habitat, open habitat, and forest habitat using the R
+package `raster` [@Hijmans_2019]. Foraging habitat <!-- TODO: "foraging" should
+be "lichen" ?--> consisted of lichen habitat, open habitat consisted of wetland,
+rocky barrens, and anthropogenic habitat types, while forest habitat consisted
+of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest
+habitat types. Water habitat was excluded from all subsequent analyses.
 
@@
 We altered the social scale based on visual (short distance) and auditory (long
-distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we modified
-the spatial distance threshold required for group assignment using `spatsoc` [@Robitaille_2019] (see above) and
-re-assigned groups at incremental distances between 5-500m. For example, at the
-finest social scale, only individuals within 5m of one another were considered
-in the same group, whereas at the coarsest social scale, individuals within 500m
-of one another were considered in the same group.
+distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we
+modified the spatial distance threshold required for group assignment using
+`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
+distances between 5-500m. For example, at the finest social scale, only
+individuals within 5m of one another were considered in the same group, whereas
+at the coarsest social scale, individuals within 500m of one another were
+considered in the same group.
 
@@
 
-The integration of behavioural and ecological theory has shown the value of considering the importance of scale to better understand and predict animal social networks, including demography (Shizuka and Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
-2017), and animal personality (Sih et al.
-2017).
-While the number of studies integrating social network theory into a broader array of behavioural and ecological sub-disciplines is impressive, only recently has the role of animal space use been been considered in describing the causes and consequences of the social environment in the context of (1) Individual fitness and phenotypes (Webber & Vander Wal 2018), (2) habitat selection and space use (He et al.
-2019), and (3) movement ecology and collective movement (Bode et al.
-2011).
-Here, we explore how mutlilayer networks may apply to these emerging fields to contribute to the development of social network theory and application.
+The integration of behavioural and ecological theory has shown the value of
+considering the importance of scale to better understand and predict animal
+social networks, including demography (Shizuka and Johnson 2019), evolutionary
+and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
+2017), and animal personality (Sih et al. 2017). While the number of studies
+integrating social network theory into a broader array of behavioural and
+ecological sub-disciplines is impressive, only recently has the role of animal
+space use been been considered in describing the causes and consequences of the
+social environment in the context of (1) Individual fitness and phenotypes
+(Webber & Vander Wal 2018), (2) habitat selection and space use (He et al.
+2019), and (3) movement ecology and collective movement (Bode et al. 2011).
+Here, we explore how mutlilayer networks may apply to these emerging fields to
+contribute to the development of social network theory and application.
 
@@
 ## Habitat selection and space use
+### 1
+Habitat selection and shared space use *link to social*
+Habitat selection depends on 
+species specific
+individual differences in home range and habitat selection
+percentage of home range overlap links to foraging quality and availability in herbivores
+multilayer networks are "a potential framework" for investigating social dynamics given shared space use and individual habitat selection
+
+### 2
+Sociality / multilayer have been used with habitat selection and space use
+... examples
+
+Fortin 2009 showed that "bison selection of habitat and landscape features was mediated
+by social group size, hypothesizing the predation risk avoidance is the strongest driver of habitat selection"
+
+Banks 2007 habitat fragmentation influences + increased mate availability given increased home range overlap when resource availability was higher
+
+mcloughlin2000 variable response bears to habitat quality and space use/home range overlap
+
+### 3
+Scale + habitat selection and space use
+types of scale to consider in these types of ML nets
+
+McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
+should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
+
+Johnson 1980 1st order = selection of the physical or geographical range of a species
+2nd order = selection of a home range of an individual or social group
+3rd order = selection of various habitat patches within the home range 
+4th order = selection of specific resources within a habitat patch
 
@@
 * van Beest et al. 2014 scale paper 
-* 1st/2nd/3rd order selection
 * Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
 * Multi-scale habitat selection modeling: a review and outlook
+
+### 4
+how to combine moving forward
+multilayer networks across landcover types
+in areas of high selection/low selection or favorable/unfavorable habitat
+combined with seasonality
+
+in our case study, we looked at increase spatial scales of landcover metrics
+
+we could define layers of the multilayer network according to home range overlap 
+instead of specific associations
+looking at broader temporal scales and coarser spatial resolutions
 
@@
 
-We thank all members of the Wildlife Evolutionary Ecology Lab, including J. Hendrix, K.
-Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for
-their comments on previous versions of this manuscript as well as D. C. Schneider
-for inspiration and helpful discussions about scale. Funding for this study was
-provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
-Grant to EVW.
+We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
+Hendrix, K. Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L.
+Newediuk for their comments on previous versions of this manuscript as well as
+D. C. Schneider for inspiration and helpful discussions about scale. Funding for
+this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a
+NSERC Discovery Grant to EVW.
+
+\newpage
 

### 2020-02-04 paper/manuscript.Rmd
add keywords
reorder persp

@@
 animals, their social environment, and the landscapes they occupy.
+
+## Keywords
+Landscape ecology, Movement ecology, Social network analysis, Space use
 
@@
 social environment in the context of (1) Individual fitness and phenotypes
-(Webber & Vander Wal 2018), (2) habitat selection and space use (He et al.
-2019), and (3) movement ecology and collective movement (Bode et al. 2011).
+(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode et al. 2011), 
+and (3) habitat selection and space use (He et al. 2019).
 Here, we explore how mutlilayer networks may apply to these emerging fields to

### 2020-02-04 paper/manuscript.Rmd
little todos and refs

@@
 Landscape ecology, Movement ecology, Social network analysis, Space use
+
+\newpage
 
@@
 package `spatsoc` [@Robitaille_2019] in `r version$version.string`
-[@R_Core_Team_2019].
+[@R_Core_Team_2019]. *FIX VANDER WAL IN SPATSOC REF*
 
@@
 above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
-for caribou during foraging <!--TODO: REF-->, while re-sampling at 500m and 1000m
+for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500m and 1000m
 represents the scale at which caribou tend to select and avoid habitat
@@
 position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for winter (1 January)
-and summer (3 August). The position of the time window was shifted by 1-48 days,
+window varied from 40-100 days using a fixed start day for winter (starting at 1 January)
+and summer (starting at 3 August). The position of the time window was shifted by 1-48 days,
 using a fixed time window length of 48 days. These new time windows were
@@
 
-1. Why do individuals associate more strongly with certain conspecifics in some
+2. Why do individuals associate more strongly with certain conspecifics in some
 habitats? What, if any, is the role of movement in the context of habitat
@@
 
-1. How, and why, does the spatial scale of perception influence, e.g. auditory,
+3. How, and why, does the spatial scale of perception influence, e.g. auditory,
 visual, or chemotaxis, influence the  social environment across scales? What is

### 2020-02-04 paper/manuscript.Rmd
refs

@@
 We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index (SRI, Cairns and Schwager 1987): <!-- TODO: get Cairns ref-->
+caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): <!-- TODO: get Cairns ref-->
 
@@
 Animal movement undoubtedly affects an individual's social environment
-(Strandburg-Peshkin et al. 2015). Movement is a dynamic process that is related
+[@Strandburg-Peshkin2015]. Movement is a dynamic process that is related
 to the resources an individual consumes within their home range and the space

### 2020-02-04 paper/citations.R

@@ -50,6 +50,9 @@ citep('10.1111/2041-210X.13215')
 # farine whitehead 2015
 citep('10.1111/1365-2656.12418')
 
+# Cairns and Schwaeger 1987
+citep('10.1016/S0003-3472(87)80018-0')
+
 # raster package
 citep(citation('raster'))
 
@@ -95,6 +98,9 @@ citep('10.1073/pnas.0701159104')
 # royle 2012
 citep('10.1098/rspb.2012.1701')
 
+## movement
+# Strandburg-Peshkin 2015
+citep('10.1126/science.aaa5099 ')
 
 ### R, R Packages
 # R

### 2020-02-04 paper/citations.R
ref

@@ -100,7 +100,7 @@ citep('10.1098/rspb.2012.1701')
 
 ## movement
 # Strandburg-Peshkin 2015
-citep('10.1126/science.aaa5099 ')
+citep('10.1126/science.aaa5099')
 
 ### R, R Packages
 # R

### 2020-02-04 paper/manuscript.Rmd
ref
catching a few typos

@@
 A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window <!--TODO:**[JWT: previously this was describing fig.
+B) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig.
 3.
 I don't know if what I wrote best encapsulates what connnective redundancy does here.
-Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
 D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
@@
 ecological sub-disciplines is impressive, only recently has the role of animal
-space use been been considered in describing the causes and consequences of the
+space use been considered in describing the causes and consequences of the
 social environment in the context of (1) Individual fitness and phenotypes
@@
 Animal movement undoubtedly affects an individual's social environment
-[@Strandburg-Peshkin2015]. Movement is a dynamic process that is related
+[@Strandburg-Peshkin_2015]. Movement is a dynamic process that is related
 to the resources an individual consumes within their home range and the space

### 2020-02-04 scripts/8-plots.R
update figs lichen -> forage

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'winpos'
+var <- 'nobs'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -32,10 +32,10 @@ alloc.col(DT)
 
 
 # Recode landcover
-# 1 = open, 2 = forest, 3 = lichen
+# 1 = open, 2 = forest, 3 = foraging (lichen)
 DT[get(lccol) == 1, c('lcname', 'layernm') := .('open', paste0(season, '-open'))]
 DT[get(lccol) == 2, c('lcname', 'layernm') := .('forest', paste0(season, '-forest'))]
-DT[get(lccol) == 3, c('lcname', 'layernm') := .('lichen', paste0(season, '-lichen'))]
+DT[get(lccol) == 3, c('lcname', 'layernm') := .('forage', paste0(season, '-forage'))]
 
 
 # Var x lab names

### 2020-02-04 paper/manuscript.Rmd
couple added todos

@@
 ### Network metrics
+<!-- TODO: expand + simplify + examples individual A, B etc -->
 We used a series of metrics to characterize the multilayer networks, focusing on
@@
 
+<!-- remove italics from terms? -->
 Although multilayer animal social networks are relatively novel (Silk et al.

### 2020-02-04 paper/manuscript.Rmd
landcover res results

@@
 networks in caribou and similar species.
+
+Larger landcover resolution scale resulted in decreased proportion of rare and
+patchy habitats and low connectivity of individuals in these habitats. In
+winter, layer relevance was stable for open and forest habitats but decreased
+for forage habitats (Figure 3c). Connective redundancy decreased with increasing
+landcover resolution due the decrease in connectivity of individuals in winter
+forage habitats, resulting in a multilayer network where neighbours were less
+frequently repeated in multiple layers (Figure 3b). Layer similarity was
+generally stable for forest and open habitats except for a contrasting increase
+in similarity for forest and decrease in similarity for open habitats at 250m
+landcover resolution (Figure 3a). Layer similarity was not possible to calculate
+between winter and summer forage because, at all landcover resolutions greater
+than 10m there were no individuals connected in the network layers. <!--
+individuals still used forage but in much lower proportion + lowered opportunity
+to associate --> These results indicate the importance of matching landcover
+resolution to scale of selection as well as ensuring the landcover product used
+has a resolution fine enough to detect relevant landscape features and habitats.
 

### 2020-02-04 paper/manuscript.Rmd
nobs results

@@
 winter, layer relevance was stable for open and forest habitats but decreased
-for forage habitats (Figure 3c). Connective redundancy decreased with increasing
+for forage habitats (Figure 4c). Connective redundancy decreased with increasing
 landcover resolution due the decrease in connectivity of individuals in winter
 forage habitats, resulting in a multilayer network where neighbours were less
-frequently repeated in multiple layers (Figure 3b). Layer similarity was
+frequently repeated in multiple layers (Figure 4b). Layer similarity was
 generally stable for forest and open habitats except for a contrasting increase
 in similarity for forest and decrease in similarity for open habitats at 250m
-landcover resolution (Figure 3a). Layer similarity was not possible to calculate
+landcover resolution (Figure 4a). Layer similarity was not possible to calculate
 between winter and summer forage because, at all landcover resolutions greater
@@
 -->
+
+As the number of observations used to generate multilayer networks increased,
+individuals became more connected and metrics generally appeared to stabilize.
+Like coarse landcover resolution (above), low number of observations were not
+sufficient for capturing individuals in all contexts and layer similarity could
+not be calculated below ~75 observations for forest, ~210 observations for open
+and ~300 observations for forage (Figure 5a). Once sufficient observations were
+used, layer similarity stabilized with additional for all three landcover
+classes at ~200 observations for forest, ~300 observations for open and forage.
+Connective redundancy increased with increasing number of observations as
+individuals became more connected to neighbours in multiple layers (Figure 5b).
+Given the overall trend of these multilayer metrics stabilizing after a certain
+number of observations are included, the results suggest this sensitivity method
+could be useful for determining the number of observations necessary for
+sufficiently describing the social dynamics across contexts.
 

### 2020-02-04 paper/manuscript.Rmd
add todo
winlen results

@@
 We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale. 
+<!-- TODO: make sure we clarify these are means of all individuals? -->
 
@@
 
+<!-- landcover resolution
+* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
+* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
+* decreasing winter lichen relevance because the degree + number of edges decreased
+-->
+
 Larger landcover resolution scale resulted in decreased proportion of rare and
@@
 has a resolution fine enough to detect relevant landscape features and habitats.
-
-<!-- landcover resolution
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
--->
 
@@
 -->
+
+Contrasting winter and summer seasons became more similar with increasing window
+length. Layer similarity between seasons increased consistently across landcover
+class (Figure 6a). Individual graph strength and layer relevance increased for
+all summer layers as individuals became more connected with increasing window
+lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
+length, especially for the summer season, may be resulting in less precisely
+defined seasons that are not clearly capturing periods of aggregation and
+dissaggregation according to resource availability and presence of conspecifics.
 

### 2020-02-04 paper/manuscript.Rmd
reorg so figs are before results

@@
 # Scale in multilayer networks in practice: case study results and discussion
+<!-- FIGURES ----------------------- -->
+
+(ref:socres) Varying scale in social threshold.
+For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
+<!--TODO: what about forest.--> B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m <!--TODO:**??**--> social threshold before decreasing between 400m and 500m.
+C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
+D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
+
+```{r socres, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-spatialthreshold.png')
+```
+
+(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
+For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+
+```{r lcres, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
+<!-- TODO: RO first sentence... -->
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+<!--TODO:*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.--> B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+
+```{r nobs, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
+```
+
+(ref:winlen) Varying scale in time window length.
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
+B) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig.
+3.
+I don't know if what I wrote best encapsulates what connnective redundancy does here.
+Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
+<!--TODO:**[see if you agree with my changes.
+B-D were based off fig.
+3 and not relevant to this figure]**-->
+
+```{r winlen, fig.cap='(ref:winlen)'}
+knitr::include_graphics('../graphics/figure-winlength.png')
+```
+
+(ref:winpos) Varying scale in time window position.
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated.
+A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
+<!--TODO:**[JWT: previously describing window length, not position.
+Check that you're ok with my changes]**--> B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
+D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+
+```{r winpos, fig.cap='(ref:winpos)'}
+knitr::include_graphics('../graphics/figure-winpos.png')
+```
+
+<!-- RESULTS / DISCUSSION --------------------------- -->
 

### 2020-02-04 paper/manuscript.Rmd
nvm reorg, just fix \@ref{(fig:socres)}

--- 2020-02-04 paper/manuscript.Rmd
@@
 decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not
+degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer relevance did not
 change for any habitat types or seasons, which suggests habitat-by-season layers
@@
 defined seasons that are not clearly capturing periods of aggregation and
-dissaggregation according to resource availability and presence of conspecifics.
+dissaggregation according to resource availability and presence of conspecifics. Similarly,
 
@@
 -->
+
+Shifting window position results showed increasing layer similarity
+
+In general, individuals in multilayer networks became more connected as a
+function of social scale, however, this relationship varied by habitat type and
+season. As social scale increased, connective redundancy increased rapidly when
+groups were formed based on ~100m threshold, followed by a plateau and slight
+decrease at higher thresholds, presumably due to an increase in summer forest
+degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not
+change for any habitat types or seasons, which suggests habitat-by-season layers
+captured most, if not all, of the potential connections and individual would
+have across all networks (Figure 3c). Finally, somewhat predictably, graph
+strength for winter networks increased up to ~100-200m thresholds, followed by a
+plateau, while graph strength for summer networks did not change as the social
+threshold increased (Figure 3d).  Taken together, these results suggest the
+optimal social scale at which groups should be assigned is likely somewhere
+between ~20-100m based on the rate at which network metrics stabilized. For
+ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
+Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
+quantities of data, ~50m is likely an ideal social scale for generating social
+networks in caribou and similar species.
 
@@
 
-```{r, fig.cap='(ref:socres)'}
+```{r socres, fig.cap='(ref:socres)'}
 knitr::include_graphics('../graphics/figure-spatialthreshold.png')

### 2020-02-04 paper/manuscript.Rmd
fin use \@ref(fig:xyz)

@@
 association represents shared space use by members of the same social group
-(Figure 1, Franks et al. 2010). Further, for social interactions or associations
-to occur individuals must share space, and thus have overlapping home ranges. In
-the context of the social environment, home range overlap is a relatively coarse
-scale of sociality across which individuals share space over coarser spatial and
-temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
-clearly scales spatially and temporally, it remains unclear whether coarser
-scales of sociality, including social association and home range overlap, vary
-predictably with social interaction (Castles et al. 2014; Farine 2015). Thus, we
-define social scale as the type of social relationship observed that can be
-explicitly defined and measured (Farine et al. 2015).
+(Figure \@ref(fig:spacetime), Franks et al. 2010). Further, for social
+interactions or associations to occur individuals must share space, and thus
+have overlapping home ranges. In the context of the social environment, home
+range overlap is a relatively coarse scale of sociality across which individuals
+share space over coarser spatial and temporal scales (e.g. Piza-Roca et al.
+2018). Although the social environment clearly scales spatially and temporally,
+it remains unclear whether coarser scales of sociality, including social
+association and home range overlap, vary predictably with social interaction
+(Castles et al. 2014; Farine 2015). Thus, we define social scale as the type of
+social relationship observed that can be explicitly defined and measured (Farine
+et al. 2015).
 
@@
 
-```{r, fig.cap='(ref:spacetime)'}
+```{r spacetime, fig.cap='(ref:spacetime)'}
 knitr::include_graphics('../graphics/figure1.png')
@@
 decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer relevance did not
-change for any habitat types or seasons, which suggests habitat-by-season layers
-captured most, if not all, of the potential connections and individual would
-have across all networks (Figure 3c). Finally, somewhat predictably, graph
-strength for winter networks increased up to ~100-200m thresholds, followed by a
-plateau, while graph strength for summer networks did not change as the social
-threshold increased (Figure 3d).  Taken together, these results suggest the
-optimal social scale at which groups should be assigned is likely somewhere
-between ~20-100m based on the rate at which network metrics stabilized. For
-ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
-Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
-quantities of data, ~50m is likely an ideal social scale for generating social
-networks in caribou and similar species.
+degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer
+relevance did not change for any habitat types or seasons, which suggests
+habitat-by-season layers captured most, if not all, of the potential connections
+and individual would have across all networks (Figure \@ref(fig:socres)c).
+Finally, somewhat predictably, graph strength for winter networks increased up
+to ~100-200m thresholds, followed by a plateau, while graph strength for summer
+networks did not change as the social threshold increased (Figure
+\@ref(fig:socres)d).  Taken together, these results suggest the optimal social
+scale at which groups should be assigned is likely somewhere between ~20-100m
+based on the rate at which network metrics stabilized. For ungulates, groups are
+often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018;
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is
+likely an ideal social scale for generating social networks in caribou and
+similar species.
 
@@
 winter, layer relevance was stable for open and forest habitats but decreased
-for forage habitats (Figure 4c). Connective redundancy decreased with increasing
-landcover resolution due the decrease in connectivity of individuals in winter
-forage habitats, resulting in a multilayer network where neighbours were less
-frequently repeated in multiple layers (Figure 4b). Layer similarity was
-generally stable for forest and open habitats except for a contrasting increase
-in similarity for forest and decrease in similarity for open habitats at 250m
-landcover resolution (Figure 4a). Layer similarity was not possible to calculate
-between winter and summer forage because, at all landcover resolutions greater
-than 10m there were no individuals connected in the network layers. <!--
-individuals still used forage but in much lower proportion + lowered opportunity
-to associate --> These results indicate the importance of matching landcover
+for forage habitats (Figure \@ref(fig:lcres)c). Connective redundancy decreased
+with increasing landcover resolution due the decrease in connectivity of
+individuals in winter forage habitats, resulting in a multilayer network where
+neighbours were less frequently repeated in multiple layers (Figure
+\@ref(fig:lcres)b). Layer similarity was generally stable for forest and open
+habitats except for a contrasting increase in similarity for forest and decrease
+in similarity for open habitats at 250m landcover resolution (Figure
+\@ref(fig:lcres)a). Layer similarity was not possible to calculate between
+winter and summer forage because, at all landcover resolutions greater than 10m
+there were no individuals connected in the network layers. <!-- individuals
+still used forage but in much lower proportion + lowered opportunity to
+associate --> These results indicate the importance of matching landcover
 resolution to scale of selection as well as ensuring the landcover product used
@@
 not be calculated below ~75 observations for forest, ~210 observations for open
-and ~300 observations for forage (Figure 5a). Once sufficient observations were
-used, layer similarity stabilized with additional for all three landcover
-classes at ~200 observations for forest, ~300 observations for open and forage.
-Connective redundancy increased with increasing number of observations as
-individuals became more connected to neighbours in multiple layers (Figure 5b).
-Given the overall trend of these multilayer metrics stabilizing after a certain
-number of observations are included, the results suggest this sensitivity method
-could be useful for determining the number of observations necessary for
-sufficiently describing the social dynamics across contexts.
+and ~300 observations for forage (Figure \@ref(fig:nobs)a). Once sufficient
+observations were used, layer similarity stabilized with additional for all
+three landcover classes at ~200 observations for forest, ~300 observations for
+open and forage. Connective redundancy increased with increasing number of
+observations as individuals became more connected to neighbours in multiple
+layers (Figure \@ref(fig:nobs)b). Given the overall trend of these multilayer
+metrics stabilizing after a certain number of observations are included, the
+results suggest this sensitivity method could be useful for determining the
+number of observations necessary for sufficiently describing the social dynamics
+across contexts.
 
@@
 length. Layer similarity between seasons increased consistently across landcover
-class (Figure 6a). Individual graph strength and layer relevance increased for
-all summer layers as individuals became more connected with increasing window
-lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
-length, especially for the summer season, may be resulting in less precisely
-defined seasons that are not clearly capturing periods of aggregation and
-dissaggregation according to resource availability and presence of conspecifics. Similarly,
+class (Figure \@ref(fig:winlen)a). Individual graph strength and layer relevance
+increased for all summer layers as individuals became more connected with
+increasing window lengths (Figure \@ref(fig:winlen)c, Figure
+\@ref(fig:winlen)d). These results suggest that an increasing window length,
+especially for the summer season, may be resulting in less precisely defined
+seasons that are not clearly capturing periods of aggregation and
+dissaggregation according to resource availability and presence of conspecifics.
+Similarly,
 
@@
 Shifting window position results showed increasing layer similarity
-
-In general, individuals in multilayer networks became more connected as a
-function of social scale, however, this relationship varied by habitat type and
-season. As social scale increased, connective redundancy increased rapidly when
-groups were formed based on ~100m threshold, followed by a plateau and slight
-decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500m (Figure 3b). Regardless of social scale, layer relevance did not
-change for any habitat types or seasons, which suggests habitat-by-season layers
-captured most, if not all, of the potential connections and individual would
-have across all networks (Figure 3c). Finally, somewhat predictably, graph
-strength for winter networks increased up to ~100-200m thresholds, followed by a
-plateau, while graph strength for summer networks did not change as the social
-threshold increased (Figure 3d).  Taken together, these results suggest the
-optimal social scale at which groups should be assigned is likely somewhere
-between ~20-100m based on the rate at which network metrics stabilized. For
-ungulates, groups are often assigned based on 50m threshold (Lingle 2003;
-Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
-quantities of data, ~50m is likely an ideal social scale for generating social
-networks in caribou and similar species.
 
@@
 
-```{r, fig.cap='(ref:lcres)'}
+```{r lcres, fig.cap='(ref:lcres)'}
 knitr::include_graphics('../graphics/figure-lcres.png')
@@
 
-```{r, fig.cap='(ref:nobs)'}
+```{r nobs, fig.cap='(ref:nobs)'}
 knitr::include_graphics('../graphics/figure-nobs.png')
@@
 
-```{r, fig.cap='(ref:winlen)'}
+```{r winlen, fig.cap='(ref:winlen)'}
 knitr::include_graphics('../graphics/figure-winlength.png')
@@
 
-```{r, fig.cap='(ref:winpos)'}
+```{r winpos, fig.cap='(ref:winpos)'}
 knitr::include_graphics('../graphics/figure-winpos.png')

### 2020-02-04 paper/manuscript.Rmd
edits to case study results/discussion

@@
 
-We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale. 
 <!-- TODO: make sure we clarify these are means of all individuals? -->
 
-In general, individuals in multilayer networks became more connected as a
-function of social scale, however, this relationship varied by habitat type and
+<!-- TODO: discuss layer similarity for social threshold -->
+In general, individuals in multilayer networks became more connected as social scale 
+increased; however, this relationship varied by habitat type and
 season. As social scale increased, connective redundancy increased rapidly when
-groups were formed based on ~100m threshold, followed by a plateau and slight
+groups were formed up to approximately 100m threshold, followed by a plateau and slight
 decrease at higher thresholds, presumably due to an increase in summer forest
@@
 habitat-by-season layers captured most, if not all, of the potential connections
-and individual would have across all networks (Figure \@ref(fig:socres)c).
+an individual would have across all networks (Figure \@ref(fig:socres)c).
 Finally, somewhat predictably, graph strength for winter networks increased up
@@
 --> 
-
-Larger landcover resolution scale resulted in decreased proportion of rare and
+<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
+Increasing the scale of landcover resolution resulted in decreased proportion of rare and
 patchy habitats and low connectivity of individuals in these habitats. In
@@
 individuals in winter forage habitats, resulting in a multilayer network where
-neighbours were less frequently repeated in multiple layers (Figure
-\@ref(fig:lcres)b). Layer similarity was generally stable for forest and open
+neighbours were less frequently repeated in multiple layers <!-- TODO: I'm having a hard 
+time understanding this previous sentence --> (Figure\@ref(fig:lcres)b). Layer similarity 
+was generally stable for forest and open
 habitats except for a contrasting increase in similarity for forest and decrease
@@
 resolution to scale of selection as well as ensuring the landcover product used
-has a resolution fine enough to detect relevant landscape features and habitats.
+has a resolution fine enough to detect relevant landscape features and habitats. <!-- TODO: how? This isn't clear enough for me to follow yet -->
 
@@
 individuals became more connected and metrics generally appeared to stabilize.
-Like coarse landcover resolution (above), low number of observations were not
+Like coarse landcover resolution (above), low numbers of observations were not
 sufficient for capturing individuals in all contexts and layer similarity could
-not be calculated below ~75 observations for forest, ~210 observations for open
-and ~300 observations for forage (Figure \@ref(fig:nobs)a). Once sufficient
-observations were used, layer similarity stabilized with additional for all
-three landcover classes at ~200 observations for forest, ~300 observations for
-open and forage. Connective redundancy increased with increasing number of
+not be calculated below approximately 75 observations for forest, approximately 210 
+observations for openand approximately 300 observations for forage (Figure 
+\@ref(fig:nobs)a). Once sufficient observations were obtained, layer similarity stabilized 
+for all three landcover classes at approximately 200 observations for forest and approximately 300 observations for open and forage landcover types.
+Connective redundancy increased with increasing number of
 observations as individuals became more connected to neighbours in multiple
@@
 across contexts.
+<!-- TODO: I'm not sure this is relevant since this is the main way it is already done, can we make this thought more relevant to picking scales or multilayer networks in general?
+I think it's important for building robust networks -->
 
@@
 dissaggregation according to resource availability and presence of conspecifics.
-Similarly,
+Similarly,<!-- TODO: ?? -->
+<!-- TODO: end with something highlighting this shows it's important to properly define your season -->
 
@@
 Shifting window position results showed increasing layer similarity 
+<!-- TODO: haha, good conclusion -->
 

### 2020-02-04 paper/manuscript.Rmd
rm todo, reflow

@@
 Shifting window position results showed increasing layer similarity
-<!-- TODO: haha, good conclusion -->
 
@@
 space use been considered in describing the causes and consequences of the
-social environment in the context of (1) Individual fitness and phenotypes
-(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode et al. 2011), 
-and (3) habitat selection and space use (He et al. 2019).
-Here, we explore how mutlilayer networks may apply to these emerging fields to
-contribute to the development of social network theory and application.
+social environment in the context of (1) individual fitness and phenotypes
+(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
+et al. 2011), and (3) habitat selection and space use (He et al. 2019). Here, we
+explore how mutlilayer networks may apply to these emerging fields to contribute
+to the development of social network theory and application.
 

### 2020-02-04 paper/manuscript.Rmd
hab perspect p1

@@
 ## Habitat selection and space use
-### 1
-Habitat selection and shared space use *link to social*
-Habitat selection depends on 
-species specific
-individual differences in home range and habitat selection
-percentage of home range overlap links to foraging quality and availability in herbivores
-multilayer networks are "a potential framework" for investigating social dynamics given shared space use and individual habitat selection
+<!--
+* Social structure is influenced by large scale processes such as resource availability and seasonality [@Peigner_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
+* Habitat selection definition
+* johnson's four scales of selection and Mayor 2009 habitat selection across scales
+* habitat selection influences social structure since resource availability + quality influence home range size and overlap
+* individuals must share space to interact [@Farine_2015]
+* multilayer networks represent a novel framework for considering habitat selection and space use on sociality across scales
+
+individual differences in habitat selection
+-->
+
+Social structure is influenced by large scale processes such as resource
+availability and seasonality [@Peigner_2019], configuration [@He_2019] and
+fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
+available" [@Mayor_2009] landscape resources or features by animals. Johnson
+(1980) identified four orders of habitat selection: (1) the geographical range
+of a species, (2) the home range of an individual, (3) the habitat patches
+within the home range and (4) specific resources within a habitat patch.
+Combined, habitat selection and social structure are intimately linked as
+individuals must share space to interact [@Farine_2015] and resource
+availability and quality influence home range size and overlap. Multilayer
+networks represent a novel framework for considering the influence of habitat
+selection and space use on sociality across scales.
 
 ### 2
+
 Sociality / multilayer have been used with habitat selection and space use

### 2020-02-04 paper/manuscript.Rmd
p2

@@
 ### 2
+<!--
+* multilayer networks are new but folks have looked at habitat selection + sociality
+  * Fortin
+  * Banks
+  * McLoughlin
 
-Sociality / multilayer have been used with habitat selection and space use
-... examples
+* none use a multilayer framework to explicitly combine
+-->
 
-Fortin 2009 showed that "bison selection of habitat and landscape features was mediated
-by social group size, hypothesizing the predation risk avoidance is the strongest driver of habitat selection"
-
-Banks 2007 habitat fragmentation influences + increased mate availability given increased home range overlap when resource availability was higher
-
-mcloughlin2000 variable response bears to habitat quality and space use/home range overlap
+Despite not in a multilayer network context, the link between habitat and
+sociality has been previously investigated. Fortin et al. (2009) evaluated
+habitat selection and group formation and division in bison. They observed
+contrasting group sizes in meadows and forests as well as identified predation
+risk avoidance as a main factor in their habitat selection [@Fortin_2009]. A
+review of the influence of habitat fragmentation on sociality noted decreased
+group size in small patches compared to large, continuous landscapes
+[@Banks_2007]. Finally, McLoughlin (2000) showed variable responses in brown
+bears (*Ursus arctos*) to seasonality, a proxy in this case for habitat quality,
+showing high home range overlap in areas of low and high seasonality and low
+home range overlap in areas of moderate seasonality. Despite these, *missing
+multilayer approach*.
 

### 2020-02-04 paper/manuscript.Rmd
rough p3, p4

@@
 
-### 2
 <!--
@@
 
-### 3
+<!--
+
 Scale + habitat selection and space use
@@
 * Multi-scale habitat selection modeling: a review and outlook
+-->
+Scale in habitat selection... Mayor (2019)
 
-### 4
+<!--
 how to combine moving forward
@@
 looking at broader temporal scales and coarser spatial resolutions
+-->
+How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
+Sociality across scales eg home range overlap and interactions
+Layers defined by habitat/landcover
 

### 2020-02-04 paper/manuscript.Rmd
reorg panels and text refs throughout

@@
 package `spatsoc` [@Robitaille_2019] in `r version$version.string`
-[@R_Core_Team_2019]. *FIX VANDER WAL IN SPATSOC REF*
+[@R_Core_Team_2019]. <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
 
@@
 decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500m (Figure \@ref(fig:socres)b). Regardless of social scale, layer
+degree at ~500m (Figure \@ref(fig:socres)d). Regardless of social scale, layer
 relevance did not change for any habitat types or seasons, which suggests
 habitat-by-season layers captured most, if not all, of the potential connections
-an individual would have across all networks (Figure \@ref(fig:socres)c).
+an individual would have across all networks (Figure \@ref(fig:socres)b).
 Finally, somewhat predictably, graph strength for winter networks increased up
@@
 networks did not change as the social threshold increased (Figure
-\@ref(fig:socres)d).  Taken together, these results suggest the optimal social
+\@ref(fig:socres)a).  Taken together, these results suggest the optimal social
 scale at which groups should be assigned is likely somewhere between ~20-100m
@@
 winter, layer relevance was stable for open and forest habitats but decreased
-for forage habitats (Figure \@ref(fig:lcres)c). Connective redundancy decreased
+for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
 with increasing landcover resolution due the decrease in connectivity of
@@
 neighbours were less frequently repeated in multiple layers <!-- TODO: I'm having a hard 
-time understanding this previous sentence --> (Figure\@ref(fig:lcres)b). Layer similarity 
+time understanding this previous sentence --> (Figure\@ref(fig:lcres)d). Layer similarity 
 was generally stable for forest and open
@@
 in similarity for open habitats at 250m landcover resolution (Figure
-\@ref(fig:lcres)a). Layer similarity was not possible to calculate between
+\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
 winter and summer forage because, at all landcover resolutions greater than 10m
@@
 not be calculated below approximately 75 observations for forest, approximately 210 
-observations for openand approximately 300 observations for forage (Figure 
-\@ref(fig:nobs)a). Once sufficient observations were obtained, layer similarity stabilized 
+observations for open and approximately 300 observations for forage (Figure 
+\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity stabilized 
 for all three landcover classes at approximately 200 observations for forest and approximately 300 observations for open and forage landcover types.
@@
 observations as individuals became more connected to neighbours in multiple
-layers (Figure \@ref(fig:nobs)b). Given the overall trend of these multilayer
+layers (Figure \@ref(fig:nobs)d). Given the overall trend of these multilayer
 metrics stabilizing after a certain number of observations are included, the
@@
 length. Layer similarity between seasons increased consistently across landcover
-class (Figure \@ref(fig:winlen)a). Individual graph strength and layer relevance
+class (Figure \@ref(fig:winlen)b). Individual graph strength and layer relevance
 increased for all summer layers as individuals became more connected with
-increasing window lengths (Figure \@ref(fig:winlen)c, Figure
-\@ref(fig:winlen)d). These results suggest that an increasing window length,
+increasing window lengths (Figure \@ref(fig:winlen)a, Figure
+\@ref(fig:winlen)b). These results suggest that an increasing window length,
 especially for the summer season, may be resulting in less precisely defined
@@
 dissaggregation according to resource availability and presence of conspecifics.
-Similarly,<!-- TODO: ?? -->
+<!-- TODO: ?? -->
 <!-- TODO: end with something highlighting this shows it's important to properly define your season -->
+
+Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance
 
@@
 For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
-<!--TODO: what about forest.--> B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m <!--TODO:**??**--> social threshold before decreasing between 400m and 500m.
-C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
-D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
+A) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
+B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
+<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m <!--TODO:**??**--> social threshold before decreasing between 400m and 500m.
 
@@
 For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
+A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
 Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
-B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
-C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
-D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
 
@@
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-<!--TODO:*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.--> B) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
-C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
+<!--TODO:*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.--> D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
 
@@
 For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-B) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig.
+A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
+<!--TODO:**[see if you agree with my changes.
+B-D were based off fig.
+3 and not relevant to this figure]**-->  B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
+D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig.
 3.
 I don't know if what I wrote best encapsulates what connnective redundancy does here.
-Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
-D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
-<!--TODO:**[see if you agree with my changes.
-B-D were based off fig.
-3 and not relevant to this figure]**-->
+Length of time window seems to make connective redundancy highly variable as it changes.]**.-->
 
@@
 For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated.
-A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
+A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
 <!--TODO:**[JWT: previously describing window length, not position.
-Check that you're ok with my changes]**--> B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
-C) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
-D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+Check that you're ok with my changes]**--> D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
 

### 2020-02-04 scripts/8-plots.R

@@ -127,7 +127,7 @@ g8 <- base3 + geom_line(aes(y = mngraphstrength), size = linesize) + ylab('Graph
 
 
 # Patchwork
-(fig <- (g1 + g5) / (g7 + g8) +
+(fig <- (g8 + g7) / (g1 + g5) +
     plot_annotation(tag_levels = 'A') & 
     theme(plot.tag = element_text(size = 14, hjust = 0, vjust = 0),
           legend.key.width = unit(1.4,"cm")) &

### 2020-02-04 paper/manuscript.Rmd
fix lab pos winlen, winpos

@@
 
-Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance
+<!-- Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance  -->
 
@@
 
-Shifting window position results showed increasing layer similarity
+<!-- Shifting window position results showed increasing layer similarity  -->
+
+**Missing: discussion of window position..**
 

### 2020-02-04 scripts/8-plots.R

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'winpos'
+var <- 'winlength'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -60,8 +60,8 @@ DT[, paste0('mn', metriccols) := lapply(.SD, mean, na.rm = TRUE),
 ## Theme
 # Legend position
 if (var %in% c('winpos', 'winlength')) {
-  pos1 <- c(0.85,0.12)
-  pos2 <- c(0.85,0.1)
+  pos1 <- c(0.85,0.11)
+  pos2 <- c(0.85,0.075)
 } else if (var %in% c('spatialthreshold')) {
   pos1 <- c(0.85,0.42)
   pos2 <- c(0.85,0.4)
@@ -70,8 +70,7 @@ if (var %in% c('winpos', 'winlength')) {
   pos2 <- c(0.85,0.2)
 }
 
-p <- theme(legend.position = pos1,
-           legend.text = element_text(size = 12, color = "black"),
+p <- theme(legend.text = element_text(size = 12, color = "black"),
            legend.title = element_blank(),
            legend.spacing = unit(-0.5, 'cm'),
            legend.background = element_blank(),
@@ -103,7 +102,9 @@ linesize <- 1.3
 base1 <- ggplot(unique(DT[, .SD, .SDcols = c(var, 'lcname', 'layersim')]), 
             aes(x = get(var), linetype = lcname))
 
-g1 <- base1 + geom_line(aes(y = (layersim)), size = linesize) + ylab('Layer Similarity')
+g1 <- base1 + geom_line(aes(y = (layersim)), size = linesize) + 
+  ylab('Layer Similarity') +
+  theme(legend.position = pos1)
 
 # Plot full, across
 base2 <- ggplot(DT[, .SD[1], by = var], 
@@ -117,13 +118,14 @@ g5 <- base2 + geom_line(aes(y = mnconnredund), size = linesize) + ylab('Connecti
 
 # Plot within
 base3 <- ggplot(DT, aes(x = get(var), color = season, linetype = lcname)) +
-  scale_color_manual(values = c(cols$hex[1], cols$hex[5]))
+  scale_color_manual(values = c(cols$hex[1], cols$hex[5])) 
 
[…]

### 2020-02-04 scripts/8-plots.R
fix lab pos lcres, nobs

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'winlength'
+var <- 'nobs'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -66,8 +66,8 @@ if (var %in% c('winpos', 'winlength')) {
   pos1 <- c(0.85,0.42)
   pos2 <- c(0.85,0.4)
 } else if (var %in% c('nobs', 'lcres')){
-  pos1 <- c(0.85,0.22)
-  pos2 <- c(0.85,0.2)
+  pos1 <- c(0.85,0.11)
+  pos2 <- c(0.85,0.35)
 }
 
 p <- theme(legend.text = element_text(size = 12, color = "black"),

### 2020-02-04 scripts/8-plots.R
fix lab pos spatial threshold

@@ -14,7 +14,7 @@ source('scripts/0-variables.R')
 
 
 ### Data ----
-var <- 'nobs'
+var <- 'spatialthreshold'
 
 if (var == 'lcres') {
   DT <- readRDS('data/derived-data/2-landcover-scale-metrics.Rds')[lcres<2000]
@@ -62,10 +62,7 @@ DT[, paste0('mn', metriccols) := lapply(.SD, mean, na.rm = TRUE),
 if (var %in% c('winpos', 'winlength')) {
   pos1 <- c(0.85,0.11)
   pos2 <- c(0.85,0.075)
-} else if (var %in% c('spatialthreshold')) {
-  pos1 <- c(0.85,0.42)
-  pos2 <- c(0.85,0.4)
-} else if (var %in% c('nobs', 'lcres')){
+} else if (var %in% c('nobs', 'lcres', 'spatialthreshold')){
   pos1 <- c(0.85,0.11)
   pos2 <- c(0.85,0.35)
 }

### 2020-02-04 paper/manuscript.Rmd
update pdf, docx

@@
 output:
-  #github_document
-  bookdown::pdf_document2:
-     number_sections: false
-  # bookdown::word_document2:
-  #   reference_docx: template.docx
+  # github_document
+  # bookdown::pdf_document2:
+  #    number_sections: false
+  bookdown::word_document2:
+    reference_docx: template.docx
 bibliography: ../references/knitcite.bib

### 2020-02-07 paper/manuscript.Rmd
update title
rm grain, extent

@@
 ---
-title: The problem and promise of scale in multilayer networks
+title: The problem and promise of scale in animal social multilayer networks
 author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 there remains an important biological and methodological gap in our
-understanding of an animal’s perception of scale, e.g., grain and extent. But
+understanding of an animal’s perception of scale. But
 scale can affect multilayer network dynamics and how we build and interpret

### 2020-02-07 paper/manuscript.Rmd
abstract edits

@@
 them. Here we discuss the role of scale in the context of multilayer networks
-and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role
+and provide a social ungulate case study to illustrate the role
 of social, spatial, and temporal scale on multilayer processes. We also present
 perspectives on future development and application of scale in multilayer
-networks with respect to habitat selection and space use, individual fitness and
-phenotypes, and movement ecology and collective movement. Effective integration
+networks with respect to: habitat selection and space use; phenotypes and individual fitness; and movement ecology and collective movement. Effective integration
 of social and spatial processes, including biologically meaningful scales,
 within the context of animal social networks is an emerging area of research;
-our contribution uniquely incorporates perspectives on how the social
+our contribution incorporates perspectives on how the social
 environment and spatial processes are linked across scales in a multilayer
-framework. Based on social network and behavioural ecology theory as well as our
-case study, we demonstrate potential for interconnectedness among individual
-animals, their social environment, and the landscapes they occupy.
 

### 2020-02-07 paper/manuscript.Rmd
keyword notes
intro edits

@@
 ## Keywords
-Landscape ecology, Movement ecology, Social network analysis, Space use
+<!-- TODO: is this the final list ? -->
+Social network analysis, Landscape ecology, Movement ecology, Space use
 
@@
 (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
-representing different classes of individuals (e.g. male or female), types of
-behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local
-or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014;
+representing (i) different classes of individuals, e.g.
+male or female; (ii) types of behaviours, e.g.
+grooming, travelling, or foraging; and (iii) spatial areas, e.g.
+local or regional, or temporal windows, e.g.
+daily or seasonal  (Kivela et al.
+2014;
 Porter 2018). Multilayer networks are relatively novel to studies of animal
@@
 landscapes, and temporal scale of analysis influence our ability to interpret
-complex social systems? Second, can variation in social, spatial, and temporal
+complex social systems? Second, can variation in the social, spatial, and temporal
 improve predictions associated with biological differences in seasonal resource
 availability and social association? We conclude with perspectives for further
-development and application of scale in multilayer networks with respect to
-habitat selection and space use <!-- TODO: (REF)-->, individual fitness and
-phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
-movement (Jolles et al. 2019).
+development and application of scale in multilayer networks with respect to phenotypes and individual fitness (Webber & Vander Wal 2018), movement ecology and collective
+movement (Jolles et al. 2019), and habitat selection and space use <!-- TODO: (REF)-->,  and .
 

### 2020-02-07 paper/manuscript.Rmd
space units

@@
 Available landcover classification included nine habitat types at <!-- TODO:
-double check lc res--> 10m resolution. We reclassified the landcover types into
+double check lc res--> 10 m resolution. We reclassified the landcover types into
 three categories: foraging habitat, open habitat, and forest habitat using the R
@@
 [@Robitaille_2019]. Group assignment based on the chain rule has previously been
-applied to caribou at a distance of 50m [@Peignier_2019; @Lesmerises_2018]. In
+applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
 all networks, nodes represented individuals, intralayer edges represented
@@
 `spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
-distances between 5-500m. For example, at the finest social scale, only
-individuals within 5m of one another were considered in the same group, whereas
-at the coarsest social scale, individuals within 500m of one another were
+distances between 5-500 m. For example, at the finest social scale, only
+individuals within 5 m of one another were considered in the same group, whereas
+at the coarsest social scale, individuals within 500 m of one another were
 considered in the same group.
@@
 our landcover raster at varying scales relevant to caribou ecology.
-We aggregated the 10m landcover raster using the R package `grainchanger`
-[@Graham_2019] at five scales: 100m, 250m, 500m, and 1000m. Aggregation occurred
+We aggregated the 10 m landcover raster using the R package `grainchanger`
+[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation occurred
 using a modal moving window method using a circular window corresponding to the
-above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making
-for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500m and 1000m
+above scales [@Graham_2019a]. 10 m and 100 m represents fine-scale decision making
+for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500 m and 1000 m
 represents the scale at which caribou tend to select and avoid habitat
@@
 season. As social scale increased, connective redundancy increased rapidly when
-groups were formed up to approximately 100m threshold, followed by a plateau and slight
+groups were formed up to approximately 100 m threshold, followed by a plateau and slight
 decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500m (Figure \@ref(fig:socres)d). Regardless of social scale, layer
+degree at ~500 m (Figure \@ref(fig:socres)d). Regardless of social scale, layer
 relevance did not change for any habitat types or seasons, which suggests
@@
 Finally, somewhat predictably, graph strength for winter networks increased up
-to ~100-200m thresholds, followed by a plateau, while graph strength for summer
+to ~100-200 m thresholds, followed by a plateau, while graph strength for summer
 networks did not change as the social threshold increased (Figure
 \@ref(fig:socres)a).  Taken together, these results suggest the optimal social
-scale at which groups should be assigned is likely somewhere between ~20-100m
+scale at which groups should be assigned is likely somewhere between ~20-100 m
 based on the rate at which network metrics stabilized. For ungulates, groups are
-often assigned based on 50m threshold (Lingle 2003; Lesmeries et al. 2018;
-Peignier et al. 2019), suggesting that given similar quantities of data, ~50m is
+often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m is
 likely an ideal social scale for generating social networks in caribou and
@@
 habitats except for a contrasting increase in similarity for forest and decrease
-in similarity for open habitats at 250m landcover resolution (Figure
+in similarity for open habitats at 250 m landcover resolution (Figure
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-winter and summer forage because, at all landcover resolutions greater than 10m
+winter and summer forage because, at all landcover resolutions greater than 10 m
 there were no individuals connected in the network layers. <!-- individuals
@@
 (ref:socres) Varying scale in social threshold.
-For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections.
+For each social threshold (5 m, 50 m, 100 m, 150 m, 200 m, 250 m, 300 m, 350 m, 400 m, 450 m, 500 m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections.
 B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
 C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
-<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m <!--TODO:**??**--> social threshold before decreasing between 400m and 500m.
+<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.
 
@@
 (ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
-For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
+For each landcover resolution (10 m, 100 m, 250 m, 500 m and 1000 m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
 A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
 B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m.
-Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution.
+C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m.
+Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10 m landcover resolution.
 D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.

### 2020-02-07 paper/manuscript.Rmd
little edits throughout

@@
 Within each layer, we assumed individuals were associating if simultaneous GPS
-fixes (i.e., recorded within 5 minutes of each other) were within a given
+fixes, i.e., recorded within 5 minutes of each other, were within a given
 spatial distance of one another. Typically for ungulates and other gregarious
@@
 `spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
-distances between 5-500 m. For example, at the finest social scale, only
+distances between 5 - 500 m. For example, at the finest social scale, only
 individuals within 5 m of one another were considered in the same group, whereas
@@
 using a modal moving window method using a circular window corresponding to the
-above scales [@Graham_2019a]. 10 m and 100 m represents fine-scale decision making
+above scales [@Graham_2019a]. We assume 10 m and 100 m represents fine-scale decision making
 for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500 m and 1000 m
@@
 space use been considered in describing the causes and consequences of the
-social environment in the context of (1) individual fitness and phenotypes
+social environment in the context of (1) phenotypes and individual fitness
 (Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
@@
 
-## Individual fitness and phenotypes
+## Phenotypes and Individual fitness
 

### 2020-02-08 paper/manuscript.Rmd
reflow

@@
 <!-- TODO: discuss layer similarity for social threshold -->
-In general, individuals in multilayer networks became more connected as social scale 
-increased; however, this relationship varied by habitat type and
-season. As social scale increased, connective redundancy increased rapidly when
-groups were formed up to approximately 100 m threshold, followed by a plateau and slight
-decrease at higher thresholds, presumably due to an increase in summer forest
-degree at ~500 m (Figure \@ref(fig:socres)d). Regardless of social scale, layer
-relevance did not change for any habitat types or seasons, which suggests
+In general, individuals in multilayer networks became more connected as social
+scale increased; however, this relationship varied by habitat type and season.
+As social scale increased, connective redundancy increased rapidly when groups
+were formed up to approximately 100 m threshold, followed by a plateau and
+slight decrease at higher thresholds, presumably due to an increase in summer
+forest degree at ~500 m (Figure \@ref(fig:socres)d). Regardless of social scale,
+layer relevance did not change for any habitat types or seasons, which suggests
 habitat-by-season layers captured most, if not all, of the potential connections
@@
 often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
-Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m is
-likely an ideal social scale for generating social networks in caribou and
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
+is likely an ideal social scale for generating social networks in caribou and
 similar species.
@@
 <!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
-Increasing the scale of landcover resolution resulted in decreased proportion of rare and
-patchy habitats and low connectivity of individuals in these habitats. In
-winter, layer relevance was stable for open and forest habitats but decreased
+Increasing the scale of landcover resolution resulted in decreased proportion of
+rare and patchy habitats and low connectivity of individuals in these habitats.
+In winter, layer relevance was stable for open and forest habitats but decreased
 for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
@@
 individuals in winter forage habitats, resulting in a multilayer network where
-neighbours were less frequently repeated in multiple layers <!-- TODO: I'm having a hard 
-time understanding this previous sentence --> (Figure\@ref(fig:lcres)d). Layer similarity 
-was generally stable for forest and open
-habitats except for a contrasting increase in similarity for forest and decrease
-in similarity for open habitats at 250 m landcover resolution (Figure
+neighbours were less frequently repeated in multiple layers <!-- TODO: I'm
+having a hard time understanding this previous sentence -->
+(Figure\@ref(fig:lcres)d). Layer similarity was generally stable for forest and
+open habitats except for a contrasting increase in similarity for forest and
+decrease in similarity for open habitats at 250 m landcover resolution (Figure
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
@@
 resolution to scale of selection as well as ensuring the landcover product used
-has a resolution fine enough to detect relevant landscape features and habitats. <!-- TODO: how? This isn't clear enough for me to follow yet -->
+has a resolution fine enough to detect relevant landscape features and habitats.
+<!-- TODO: how? This isn't clear enough for me to follow yet -->
 
-<!-- nobs 
-* common, though at different points - more observations until stabilizing
-* we dont see the stabilizing/full plateau for connective redundancy but appears to be coming.. 
-* still some variability, especially for graph strength because individuals are differently connected but broad strokes - they stabilize with more observations
--->
-
+<!-- nobs * common, though at different points - more observations until
+stabilizing * we dont see the stabilizing/full plateau for connective redundancy
+but appears to be coming.. * still some variability, especially for graph
+strength because individuals are differently connected but broad strokes - they
+stabilize with more observations -->
 As the number of observations used to generate multilayer networks increased,
@@
 sufficient for capturing individuals in all contexts and layer similarity could
-not be calculated below approximately 75 observations for forest, approximately 210 
-observations for open and approximately 300 observations for forage (Figure 
-\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity stabilized 
-for all three landcover classes at approximately 200 observations for forest and approximately 300 observations for open and forage landcover types.
-Connective redundancy increased with increasing number of
-observations as individuals became more connected to neighbours in multiple
-layers (Figure \@ref(fig:nobs)d). Given the overall trend of these multilayer
-metrics stabilizing after a certain number of observations are included, the
-results suggest this sensitivity method could be useful for determining the
-number of observations necessary for sufficiently describing the social dynamics
-across contexts.
-<!-- TODO: I'm not sure this is relevant since this is the main way it is already done, can we make this thought more relevant to picking scales or multilayer networks in general?
-I think it's important for building robust networks -->
+not be calculated below approximately 75 observations for forest, approximately
+210 observations for open and approximately 300 observations for forage (Figure
+\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
+stabilized for all three landcover classes at approximately 200 observations for
+forest and approximately 300 observations for open and forage landcover types.
+Connective redundancy increased with increasing number of observations as
+individuals became more connected to neighbours in multiple layers (Figure
+\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
+stabilizing after a certain number of observations are included, the results
+suggest this sensitivity method could be useful for determining the number of
+observations necessary for sufficiently describing the social dynamics across
+contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it
+is already done, can we make this thought more relevant to picking scales or
+multilayer networks in general? I think it's important for building robust
+networks -->
 
-<!-- win  length
-* increasing window length = increasingly similar layers and increasingly redundant edges. more individuals have the opportunity to interact
-* increasing window length also leads to increasing similarity between seasons because seasons are less well defined/include more shoulder seasons
-* decreasing graph strength at the upper end of window length in winter showing again inclusion of more shoulder season
-* layers are more similarly relevant at high window length
--->
-
+<!-- win  length * increasing window length = increasingly similar layers and
+increasingly redundant edges. more individuals have the opportunity to interact
+* increasing window length also leads to increasing similarity between seasons
+because seasons are less well defined/include more shoulder seasons * decreasing
+graph strength at the upper end of window length in winter showing again
+inclusion of more shoulder season * layers are more similarly relevant at high
+window length -->
 Contrasting winter and summer seasons became more similar with increasing window
@@
 dissaggregation according to resource availability and presence of conspecifics.
-<!-- TODO: ?? -->
-<!-- TODO: end with something highlighting this shows it's important to properly define your season -->
-
-<!-- Similarly, shifting window position of the summer season resulted in an increase in number of connections between individuals. Layer relevance  -->
-
-<!-- win position
-* increasing network connectivity in summer when the window position is moved - these seasons are more similar than the original window position
-* same theme shown in the connective redundancy
-* quite variable layer similarity, not sure what to pull out of that one
-* increased graph strength for winter down the middle, with generally increasing summer layers - again where the season is including more shoulder season potentially
--->
-
+<!-- TODO: ?? --> <!-- TODO: end with something highlighting this shows it's
+important to properly define your season -->
+<!-- Similarly, shifting window position of the summer season resulted in an
+increase in number of connections between individuals. Layer relevance  -->
+<!-- win position * increasing network connectivity in summer when the window
+position is moved - these seasons are more similar than the original window
+position * same theme shown in the connective redundancy * quite variable layer
+similarity, not sure what to pull out of that one * increased graph strength for
+winter down the middle, with generally increasing summer layers - again where
+the season is including more shoulder season potentially -->
 <!-- Shifting window position results showed increasing layer similarity  -->
-
 **Missing: discussion of window position..**

### 2020-02-08 paper/manuscript.Rmd
network metrics reshuffle/clarifications

@@
 We used a series of metrics to characterize the multilayer networks, focusing on
-the the role of individuals, relevance of individual layers and the similarity
-of different layers. To measure the role of individuals, we calculated the graph
-strength, degree weighted by the values of the edge, for each individual for
-each layer-specific season and landcover context <!-- TODO: citation for graph
-strength?-->. Degree centrality, the number of direct connections an individual
-has to other individuals in the network, is the basis of many calculations
-[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
-layers, and neighbourhood, the sum of unique neighbours to each individual
-[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
-we measured the connective redundancy, the proportion of neighbours repeated in
-multiple layers, and the layer relevance, the proportion of neighbours present
-in each layer compared to the neighbourhood for each individual
+the role of individuals, importance of individual layers and the similarity
+of different layers.
+To measure the role of individuals, we calculated degree centrality and graph strength.
+Degree centrality is the number of direct connections an individual has to other individuals in a network layer.
+Graph strength is the degree weighted by the strength of association, in this case SRI, in each layer-specific season and landcover context <!-- TODO: citation for graph
+strength?-->.
+Extending degree centrality, we calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
+We evaluated the relevance and redundancy of layers by combining the multidegree and neighbourhood to calculate connective redundancy and layer relevance.
+Connective redundancy is the proportion of neighbours repeated in multiple layers, and layer relevance is the proportion of neighbours present in each layer compared to the neighbourhood for each individual
 [@Berlingerio_2012].  Finally, we calculated the similarity of layers between
@@
 using the Pearson correlation coefficient [@Br_dka_2018].
+
+<!-- TODO: EVW "parallelism"? -->
 

### 2020-02-08 paper/manuscript.Rmd
reflow it
todo add examples with "individual A" "layer 2"

@@
 ### Network metrics
+
 <!-- TODO: expand + simplify + examples individual A, B etc --> 
-We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals, importance of individual layers and the similarity
-of different layers.
-To measure the role of individuals, we calculated degree centrality and graph strength.
-Degree centrality is the number of direct connections an individual has to other individuals in a network layer.
-Graph strength is the degree weighted by the strength of association, in this case SRI, in each layer-specific season and landcover context <!-- TODO: citation for graph
-strength?-->.
-Extending degree centrality, we calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
-We evaluated the relevance and redundancy of layers by combining the multidegree and neighbourhood to calculate connective redundancy and layer relevance.
-Connective redundancy is the proportion of neighbours repeated in multiple layers, and layer relevance is the proportion of neighbours present in each layer compared to the neighbourhood for each individual
-[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
-seasons, across landcover classes (e.g.: winter open compared to summer open)
-using the Pearson correlation coefficient [@Br_dka_2018].
+<!-- TODO: EVW "parallelism"? -->
 
-<!-- TODO: EVW "parallelism"? -->
+We used a series of metrics to characterize the multilayer networks,
+focusing on the role of individuals, importance of individual layers and the
+similarity of different layers. To measure the role of individuals, we
+calculated degree centrality and graph strength. Degree centrality is the number
+of direct connections an individual has to other individuals in a network layer.
+Graph strength is the degree weighted by the strength of association, in this
+case SRI, in each layer-specific season and landcover context <!-- TODO:
+citation for graph strength?-->. Extending degree centrality, we calculated
+multidegree, the sum of degree centrality across layers, and neighbourhood, the
+sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
+We evaluated the relevance and redundancy of layers by combining the multidegree
+and neighbourhood to calculate connective redundancy and layer relevance.
+Connective redundancy is the proportion of neighbours repeated in multiple
+layers, and layer relevance is the proportion of neighbours present in each
+layer compared to the neighbourhood for each individual [@Berlingerio_2012].
+Finally, we calculated the similarity of layers between seasons, across
+landcover classes (e.g.: winter open compared to summer open) using the Pearson
+correlation coefficient [@Br_dka_2018].
 

### 2020-02-09 paper/manuscript.Rmd
intro to perspectives

@@
 
-The integration of behavioural and ecological theory has shown the value of
-considering the importance of scale to better understand and predict animal
-social networks, including demography (Shizuka and Johnson 2019), evolutionary
-and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
-2017), and animal personality (Sih et al. 2017). While the number of studies
-integrating social network theory into a broader array of behavioural and
-ecological sub-disciplines is impressive, only recently has the role of animal
-space use been considered in describing the causes and consequences of the
-social environment in the context of (1) phenotypes and individual fitness
-(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
-et al. 2011), and (3) habitat selection and space use (He et al. 2019). Here, we
-explore how mutlilayer networks may apply to these emerging fields to contribute
-to the development of social network theory and application.
+The integration of behavioural and ecological theory has shown the value of considering 
+the importance of various ecological disciplines to better understand and predict animal 
+social networks, including demography (Shizuka and Johnson 2019), evolutionary and 
+quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al. 2017), 
+and animal personality (Sih et al. 2017). While the number of studies integrating 
+social network theory into a broader array of behavioural and ecological 
+sub-disciplines is impressive, only recently has the role of animal space use been 
+considered in describing the causes and consequences of the social environment in the 
+context of (1) phenotypes and individual fitness (Webber & Vander Wal 2018), (2) 
+movement ecology and collective movement (Bode et al. 2011), and (3) habitat 
+selection and space use (He et al. 2019). Importantly, much of the work linking 
+space use and the social environment has been theoretical and empirical studies 
+are lacking (but see Peignier et al. 2019; Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). 
+Here, we discuss the role mutlilayer networks within the emerging integration 
+of social and spatial ecology within the behavioural ecology literature.
 

### 2020-02-09 paper/manuscript.Rmd
Update manuscript.Rmd

@@
 
-Animal movement undoubtedly affects an individual's social environment
-[@Strandburg-Peshkin_2015]. Movement is a dynamic process that is related
-to the resources an individual consumes within their home range and the space
-that they use (Van Moorter et al. 2016). Collective movement can reduce
-group-level predation via detection-dilution trade-offs and improve information
-transfer about the quality or location of resources to other group members
-(Jolles et al. 2019). Social processes, movement decisions, and space use are
-inextricably linked and multilayer networks represent a potential analytical
-framework for linking these processes (e.g. Mourier et al. 2019).
+Social processes, movement decisions, and space use are inextricably linked 
+and multilayer networks represent a potential analytical framework for linking 
+these processes (e.g. Mourier et al. 2019). Movement as a collective group can 
+reduce per capita predation risk via detection-dilution trade-offs and improve 
+information transfer about the quality or location of resources to other group 
+members (Jolles et al. 2019). In our case study, we integrate proximity based 
+social networks that inherently rely on animal collective movement and, in general, 
+we found that movement is likely an important mechanism driving social network 
+connectivity within and between habitat types.
 

### 2020-02-09 paper/manuscript.Rmd
P2 movement persp

@@
 
-<!-- remove italics from terms? -->
 Although multilayer animal social networks are relatively novel (Silk et al.
-2018), movement behaviour within multilayer networks has already been considered
-in a couple studies. In vulturine gunieafowl (*Acryllium vulturinum*), GPS
-movement data were used to generate *monolayer* association networks within a
-multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks*
-are physical locations (nodes) which are connected in a network when individuals
+2018), movement behaviour within multilayer networks has been considered.  Spatial
+networks are physical locations (nodes) which are connected in a network when individuals
 move between said locations (edges). For example, spatial networks were applied
@@
 movement frequency, and *interlayer edges* represent contact probability among
-individuals at a given node (Mourier et al. 2019). While both studies integrate
-movement in some capacity, neither generate networks based on continuous
-measures of dyadic or collective movement (Long et al. 2014).
+individuals at a given node (Mourier et al. 2019). Although movement between 
+fixed arrays is inherent, networks are not constructed based on continuous 
+measures of dyadic or collective movement (Long et al. 2014). Our case study 
+builds on the work of Mourier et al. (2019) and explicitly integrates 
+continuous and simultaneous measures of animal movement through space 
+and time as layers of a multilayer social network.
 

### 2020-02-09 paper/manuscript.Rmd
P3 move persp

@@
 are fixed in space, movement networks can represent continuous and simultaneous
-movement trajectories of multiple animals. Continuous collection of animal
-relocation data using GPS technology can be used to measure how groups of
+movement trajectories of multiple animals. In a recent study of vulturine 
+gunieafowl (Acryllium vulturinum), GPS movement data were used to generate 
+monolayer association networks within a multilayer network (Papageorgiou et al. 2019). 
+However, despite potential to generate networks in different spatial or social contexts, 
+layers in the multilayer network represented social associations within and 
+between groups. Continuous collection of animal relocation data using GPS 
+technology can be used to measure how groups of
 animals make collective movement decisions in the context of their local
@@
 made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
-(global migration: Flack et al. 2018). Another potential application would be to
+(global migration: Flack et al. 2018). Our case study integrates variation 
+in temporal and spatial scale to assess the role of scale in predicting 
+multilayer networks. As one might expect, we found increasing spatial 
+scale results in saturation of potential social connections (Figure 3), 
+while increasing temporal scale had little effect on habitat-specific 
+networks (Figure 5). Another potential application would be to
 generate social networks during times when animals are engaged in different
@@
 behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019).
+
 Importantly, the key to incorporating movement in multilayer networks across
 scales is the technological advancements available to overcome previous
-limitations (see Hughey et al. 2018).
+limitations (Hughey et al. 2018).
 

### 2020-02-09 paper/manuscript.Rmd
add P4 remotely sensed behv to move persp

@@
 scales is the technological advancements available to overcome previous
-limitations (Hughey et al. 2018).
+limitations (Hughey et al. 2018). Biologging and wildlife tracking technology 
+has advanced to the point where relocations can be programmed to occur as 
+frequently as each second (Börger 2016), a practice which has been applied 
+to questions of collective movement (e.g Strandburg-Peskin et al. 2015). 
+Meanwhile, remote sensing technology, including unmanned aerial vehicles 
+and satellites, can be used to track the fine-scalemovements of  
+groups over large distances and time scales (Torney et al. 2019). Using 
+technology to infer behaviour has therefore become standard operating procedure
+for many species in many systems. Our ability to collect and process 
+remotely sensed data and infer social processes based on animal movement 
+provides an opportunity to use multilayer social network analysis to answer
+complex questions about animal socioecology.
 

### 2020-02-09 paper/manuscript.Rmd
P5 move persp + some refs

@@
 output:
-  # github_document
+   github_document
   # bookdown::pdf_document2:
   #    number_sections: false
-  bookdown::word_document2:
-    reference_docx: template.docx
+  #bookdown::word_document2:
+   # reference_docx: template.docx
 bibliography: ../references/knitcite.bib
@@
 availability and social association? We conclude with perspectives for further
-development and application of scale in multilayer networks with respect to phenotypes and individual fitness (Webber & Vander Wal 2018), movement ecology and collective
+development and application of scale in multilayer networks with respect to phenotypes and individual fitness [@Webber_2018], movement ecology and collective
 movement (Jolles et al. 2019), and habitat selection and space use <!-- TODO: (REF)-->,  and .
@@
 considered in describing the causes and consequences of the social environment in the 
-context of (1) phenotypes and individual fitness (Webber & Vander Wal 2018), (2) 
+context of (1) phenotypes and individual fitness [@Webber_2018], (2) 
 movement ecology and collective movement (Bode et al. 2011), and (3) habitat 
@@
 between groups. Continuous collection of animal relocation data using GPS 
-technology can be used to measure how groups of
-animals make collective movement decisions in the context of their local
-environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
+technology can be used to measure how groups of animals make collective 
+movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
 collective movement layer could constitute similarity in movement for dyads
@@
 Meanwhile, remote sensing technology, including unmanned aerial vehicles 
-and satellites, can be used to track the fine-scalemovements of  
-groups over large distances and time scales (Torney et al. 2019). Using 
+and satellites, can be used to track the fine-scale movements of groups 
+over large distances and time scales (Torney et al. 2019). Using 
 technology to infer behaviour has therefore become standard operating procedure
@@
 Given the existing framework for constructing multilayer networks from
-behavioural layers (e.g. Smith-Aguilar et al. 2019), movement layers could be
-integrated with interaction or association layers. Integrating movement layers
+behavioural layers (e.g. Smith-Aguilar et al. 2019), monolayer networks that
+explicity quantify movement paramters could be itnegrated. For example, edges 
+could represent measures of dyadic or collective movement based on dynamic 
+interaction metrics (Long et al. 2014). Integrating movement layers
 with habitat-specific social association layers could further shed light on the
 role of movement as a driver of the social and spatial environments an
-individual experiences (Webber and Vander Wal 2018). In our case study, we
+individual experiences [@Webber_2018]. In our case study, we
 generated multilayer networks based on habitat-specific monolayers. Coordinated

### 2020-02-09 paper/citations.R

@@ -138,6 +138,9 @@ citep('10.1016/j.arcontrol.2017.03.002')
 # Strandburg-Peshkin 2015
 citep('10.1126/science.aaa5099')
 
+# Webber & Vander wal 2018
+citep('10.1111/1365-2656.12773')
+
 ### R, R Packages
 # R
 citep(citation())

### 2020-02-09 paper/manuscript.Rmd
refs

@@
 (Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
-representing (i) different classes of individuals, e.g.
-male or female; (ii) types of behaviours, e.g.
-grooming, travelling, or foraging; and (iii) spatial areas, e.g.
-local or regional, or temporal windows, e.g.
-daily or seasonal  (Kivela et al.
-2014;
-Porter 2018). Multilayer networks are relatively novel to studies of animal
+representing (i) different classes of individuals, e.g. male or female; (ii) types 
+of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial areas,
+e.g. local or regional, or temporal windows, e.g. daily or seasonal 
+(Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal
 behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to
 describe multidimensional human social systems, complex transportation networks,
-and neural networks (Silk et al. 2018). The role of scale within multilayer
+and neural networks [@Silk_2018]. The role of scale within multilayer
 social networks remains unexplored but provides a unique opportunity to develop
@@
 availability and social association? We conclude with perspectives for further
-development and application of scale in multilayer networks with respect to phenotypes and individual fitness [@Webber_2018], movement ecology and collective
-movement (Jolles et al. 2019), and habitat selection and space use <!-- TODO: (REF)-->,  and .
+development and application of scale in multilayer networks with respect to 
+phenotypes and individual fitness [@Webber_2018], movement ecology and collective
+movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->,  and .
 
@@
 and multilayer networks represent a potential analytical framework for linking 
-these processes (e.g. Mourier et al. 2019). Movement as a collective group can 
+these processes [@Mourier_2019]. Movement as a collective group can 
 reduce per capita predation risk via detection-dilution trade-offs and improve 
 information transfer about the quality or location of resources to other group 
-members (Jolles et al. 2019). In our case study, we integrate proximity based 
+members [@Jolles_2019]. In our case study, we integrate proximity based 
 social networks that inherently rely on animal collective movement and, in general, 
@@
 
-Although multilayer animal social networks are relatively novel (Silk et al.
-2018), movement behaviour within multilayer networks has been considered.  Spatial
+Although multilayer animal social networks are relatively novel [@Silk_2018], 
+movement behaviour within multilayer networks has been considered.  Spatial
 networks are physical locations (nodes) which are connected in a network when individuals
@@
 movement frequency, and *interlayer edges* represent contact probability among
-individuals at a given node (Mourier et al. 2019). Although movement between 
+individuals at a given node [@Mourier_2019]. Although movement between 
 fixed arrays is inherent, networks are not constructed based on continuous 
-measures of dyadic or collective movement (Long et al. 2014). Our case study 
+measures of dyadic or collective movement [@Long_2014]. Our case study 
 builds on the work of Mourier et al. (2019) and explicitly integrates 
@@
 collective movement layer could constitute similarity in movement for dyads
-(Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be
+[@Long_2014] or groups (Bode et al. 2011). This movement layer could be
 made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
@@
 could represent measures of dyadic or collective movement based on dynamic 
-interaction metrics (Long et al. 2014). Integrating movement layers
+interaction metrics [@Long_2014]. Integrating movement layers
 with habitat-specific social association layers could further shed light on the

### 2020-02-09 paper/citations.R

@@ -138,8 +138,21 @@ citep('10.1016/j.arcontrol.2017.03.002')
 # Strandburg-Peshkin 2015
 citep('10.1126/science.aaa5099')
 
+# Jolles et al 2019
+citep('10.1016/j.tree.2019.11.001')
+
+# Long et al. 2015
+citep('10.1111/1365-2656.12198')
+
+# Mourier et al. 2019 (pre-print)
+citep('10.1101/749085')
+
+# Silk et al. 2018
+citep('10.1016/j.tree.2018.03.008')
+
 # Webber & Vander wal 2018
 citep('10.1111/1365-2656.12773')
+
 
 ### R, R Packages
 # R

### 2020-02-09 paper/manuscript.Rmd
reffffz

@@
 context of (1) phenotypes and individual fitness [@Webber_2018], (2) 
-movement ecology and collective movement (Bode et al. 2011), and (3) habitat 
-selection and space use (He et al. 2019). Importantly, much of the work linking 
+movement ecology and collective movement [@Bode_2011], and (3) habitat 
+selection and space use [@He_2019]. Importantly, much of the work linking 
 space use and the social environment has been theoretical and empirical studies 
@@
 gunieafowl (Acryllium vulturinum), GPS movement data were used to generate 
-monolayer association networks within a multilayer network (Papageorgiou et al. 2019). 
+monolayer association networks within a multilayer network [@Papageorgiou_2019]. 
 However, despite potential to generate networks in different spatial or social contexts, 
@@
 collective movement layer could constitute similarity in movement for dyads
-[@Long_2014] or groups (Bode et al. 2011). This movement layer could be
-made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale
+[@Long_2014] or groups  [@Bode_2011]. This movement layer could be
+made at a fine (i.e. minute-to-minute: [@Cleasby_2019] or coarse scale
 (global migration: Flack et al. 2018). Our case study integrates variation 
@@
 insights into the effects of habitat configuration on the formation of the
-social environment (He et al. 2019).
+social environment [@He_2019].
 

### 2020-02-09 paper/citations.R

@@ -135,8 +135,17 @@ citep('10.1111/1365-2656.12764')
 citep('10.1016/j.arcontrol.2017.03.002')
 
 ## movement
+# Bode 2011
+citep('10.1016/j.anbehav.2011.04.011')
+
+# Cleasby 2019
+citep('10.1007/s00265-019-2761-1')
+
 # Strandburg-Peshkin 2015
 citep('10.1126/science.aaa5099')
+
+# He et al. 2019
+citep('10.1007/s00265-018-2602-7')
 
 # Jolles et al 2019
 citep('10.1016/j.tree.2019.11.001')
@@ -146,6 +155,9 @@ citep('10.1111/1365-2656.12198')
 
 # Mourier et al. 2019 (pre-print)
 citep('10.1101/749085')
+
+# Papageorgiou 2019
+citep('10.1016/j.cub.2019.09.072')
 
 # Silk et al. 2018
 citep('10.1016/j.tree.2018.03.008')

### 2020-02-09 paper/manuscript.Rmd
more refz

@@
 [@Long_2014] or groups  [@Bode_2011]. This movement layer could be
-made at a fine (i.e. minute-to-minute: [@Cleasby_2019] or coarse scale
-(global migration: Flack et al. 2018). Our case study integrates variation 
+made at a fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale
+[global migration: @Flack_2018]. Our case study integrates variation 
 in temporal and spatial scale to assess the role of scale in predicting 
@@
 generate social networks during times when animals are engaged in different
-behaviours, including traveling, interacting, or foraging (e.g. Muller et al.
-2018; Finn et al. 2019) and construct a multilayer network based on
-behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019).
+behaviours, including traveling, interacting, or foraging [@Muller_2018; @Finn_2019] 
+and construct a multilayer network based on behaviour-specific monolayer 
+networks [e.g. @Smith_Aguilar_2019].
 
@@
 scales is the technological advancements available to overcome previous
-limitations (Hughey et al. 2018). Biologging and wildlife tracking technology 
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology 
 has advanced to the point where relocations can be programmed to occur as 
-frequently as each second (Börger 2016), a practice which has been applied 
+frequently as each second [@Börger_2016], a practice which has been applied 
 to questions of collective movement (e.g Strandburg-Peskin et al. 2015). 
@@
 Given the existing framework for constructing multilayer networks from
-behavioural layers (e.g. Smith-Aguilar et al. 2019), monolayer networks that
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that
 explicity quantify movement paramters could be itnegrated. For example, edges 

### 2020-02-09 paper/citations.R

@@ -138,14 +138,26 @@ citep('10.1016/j.arcontrol.2017.03.002')
 # Bode 2011
 citep('10.1016/j.anbehav.2011.04.011')
 
+# Borger 2016
+citep('10.1111/1365-2656.12464')
+
 # Cleasby 2019
 citep('10.1007/s00265-019-2761-1')
+
+# Finn 2019
+citep('10.1016/j.anbehav.2018.12.016')
+
+# Flack 2018
+citep('10.1126/science.aap7781 ')
 
 # Strandburg-Peshkin 2015
 citep('10.1126/science.aaa5099')
 
 # He et al. 2019
 citep('10.1007/s00265-018-2602-7')
+
+# Hughey et al 2018
+citep('10.1098/rstb.2017.0005')
 
 # Jolles et al 2019
 citep('10.1016/j.tree.2019.11.001')
@@ -156,11 +168,17 @@ citep('10.1111/1365-2656.12198')
 # Mourier et al. 2019 (pre-print)
 citep('10.1101/749085')
 
+# Muller 2018
+citep('10.1016/j.anbehav.2018.10.006')
+
 # Papageorgiou 2019
 citep('10.1016/j.cub.2019.09.072')
 
 # Silk et al. 2018
 citep('10.1016/j.tree.2018.03.008')
+
+#Smith-Aguilar et al. 2019
+citep('10.1007/s10329-018-0686-3')
 
 # Webber & Vander wal 2018
 citep('10.1111/1365-2656.12773')

### 2020-02-09 paper/manuscript.Rmd
m-m-m-more refzzzzz

@@
 and multilayer networks represent a potential analytical framework for linking 
-these processes [@Mourier_2019]. Movement as a collective group can 
+these processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group can 
 reduce per capita predation risk via detection-dilution trade-offs and improve 
@@
 movement frequency, and *interlayer edges* represent contact probability among
-individuals at a given node [@Mourier_2019]. Although movement between 
+individuals at a given node [@Mourier_2019] (Mourier et al. 2019). Although movement between 
 fixed arrays is inherent, networks are not constructed based on continuous 
@@
 movement trajectories of multiple animals. In a recent study of vulturine 
-gunieafowl (Acryllium vulturinum), GPS movement data were used to generate 
+gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate 
 monolayer association networks within a multilayer network [@Papageorgiou_2019]. 
@@
 technology can be used to measure how groups of animals make collective 
-movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A
+movement decisions in the context of their local environment 
+[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
 collective movement layer could constitute similarity in movement for dyads
@@
 frequently as each second [@Börger_2016], a practice which has been applied 
-to questions of collective movement (e.g Strandburg-Peskin et al. 2015). 
+to questions of collective movement [e.g @Strandburg_Peshkin_2015]. 
 Meanwhile, remote sensing technology, including unmanned aerial vehicles 
 and satellites, can be used to track the fine-scale movements of groups 
-over large distances and time scales (Torney et al. 2019). Using 
+over large distances and time scales [@Torney_2018]. Using 
 technology to infer behaviour has therefore become standard operating procedure
@@
 landscape because animals aggregate at resources, such as waterholes
-(Chamaillé-Jammes et al. 2008). Movement to, from, or within habitat patches  or
+[@Chamaillé_Jammes_2008]. Movement to, from, or within habitat patches  or
 territories can also contribute to the formation of the social environment

### 2020-02-09 paper/citations.R

@@ -144,14 +144,14 @@ citep('10.1111/1365-2656.12464')
 # Cleasby 2019
 citep('10.1007/s00265-019-2761-1')
 
+#Chanaille-Jammes
+citep('10.1111/j.1365-2656.2007.01307.x')
+
 # Finn 2019
 citep('10.1016/j.anbehav.2018.12.016')
 
 # Flack 2018
 citep('10.1126/science.aap7781 ')
-
-# Strandburg-Peshkin 2015
-citep('10.1126/science.aaa5099')
 
 # He et al. 2019
 citep('10.1007/s00265-018-2602-7')
@@ -179,6 +179,15 @@ citep('10.1016/j.tree.2018.03.008')
 
 #Smith-Aguilar et al. 2019
 citep('10.1007/s10329-018-0686-3')
+
+# Strandburg-Peshkin 2015
+citep('10.1126/science.aaa5099')
+
+# Strandburg-Peshkin 2017
+citep('10.7554/eLife.19505')
+
+# Torney et al 2018
+citep('10.1098/rstb.2017.0385')
 
 # Webber & Vander wal 2018
 citep('10.1111/1365-2656.12773')

### 2020-02-09 paper/manuscript.Rmd
spiegel refs

@@
 association and home range overlap, vary predictably with social interaction
-(Castles et al. 2014; Farine 2015). Thus, we define social scale as the type of
-social relationship observed that can be explicitly defined and measured (Farine
-et al. 2015).
+ [@Castles_2014; @Farine2015a]. Thus, we define social scale as the type of
+social relationship observed that can be explicitly defined and measured [@Farine_2015a].
 
@@
 (monolayer), drastically simplifying the potential complexity of animal social
-systems (Finn et al. 2019).
+systems [@Finn_2019].
 
@@
 (Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal
-behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to
+behaviour [Silk_2018; @Finn_2019], although they have been used to
 describe multidimensional human social systems, complex transportation networks,
@@
 collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
-into a discrete removed all erroneous and outlier GPS fixes following Bjørneraas
-et al. (2010)<!-- TODO: get Bjorneraas ref-->. We did not collar all female
-caribou in the herd; however, we assumed that our sample of collared animals was
-random.
+into a discrete removed all erroneous and outlier GPS fixes following [@Bjørneraas_2010]. 
+We did not collar all female caribou in the herd; however, we assumed that our 
+sample of collared animals was random.
 
@@
 and association, that are typically examined separately while answering a single
-question (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
+question [@Castles_2014; @Cater_2015; @Farine_2015a].
 Furthermore, it is a common trope that individuals must be associating to
@@
 not require proximity such as long-distance vocalization and olfactory signals
-(Carter et al., 2015). With the advancement of biologging technology, we have
+[@Carter_2015] With the advancement of biologging technology, we have
 the ability to record social interactions that do not require proximity,
@@
 frequent correlations between social network metrics in different types of
-networks (Castles et al., 2014). Furthermore, multilayer networks provide a
+networks [@Castles_2014]. Furthermore, multilayer networks provide a
 framework to test hypotheses linking social phenotypes and fitness across
@@
 territories can also contribute to the formation of the social environment
-(Spiegel et al. 2016). For example, in sleepy lizards (*Tiliqua rugosa*) males
+[@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*) males
 interacted primarily at home range edges, presumably driving territorial
-behaviour (Spiegel et al. 2018). Incorporating movement ecology within a
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a
 multilayer network framework is a logical next step for a burgeoning field. In

### 2020-02-09 paper/citations.R

@@ -37,8 +37,9 @@ citep('10.2980/16-2-3238')
 
 ### Caribou location 
 # TODO: Schaefer and Mahoney (2013)
-# TODO: Bjørneraas et al (2010)
 
+## Bjorness 2010
+citep('10.1111/j.1937-2817.2010.tb01258.x')
 
 ### Caribou multilayer social networks
 # kivela 2014
@@ -179,6 +180,12 @@ citep('10.1016/j.tree.2018.03.008')
 
 #Smith-Aguilar et al. 2019
 citep('10.1007/s10329-018-0686-3')
+
+# Spiegel et al 2016
+citep('10.1111/2041-210X.12553')
+
+# Spiegel et al. 2018
+citep('10.1016/j.anbehav.2017.09.008')
 
 # Strandburg-Peshkin 2015
 citep('10.1126/science.aaa5099')

### 2020-02-10 paper/manuscript.Rmd
work hab sel perspective

@@
 
+Social structure influenced by large scale processes, eg resources
+Animals select for these same processes, habitat selection, as measured by RSF
+All of these processes are influenced by scale: 
+RSFs are are influenced
+Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered
+sociality across scales of sociality + temporal and spatial as shown above
+ML networks present a framework for this
+
 Social structure is influenced by large scale processes such as resource
@@
 fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
-available" [@Mayor_2009] landscape resources or features by animals. Johnson
+available" [@Mayor_2009] landscape resources or features by animals. Combined, habitat selection and social structure are intimately linked as
+individuals must share space to interact [@Farine_2015] and resource
+availability and quality influence home range size and overlap. Johnson
 (1980) identified four orders of habitat selection: (1) the geographical range
@@
 within the home range and (4) specific resources within a habitat patch.
-Combined, habitat selection and social structure are intimately linked as
-individuals must share space to interact [@Farine_2015] and resource
-availability and quality influence home range size and overlap. Multilayer
+ Multilayer
 networks represent a novel framework for considering the influence of habitat

### 2020-02-10 paper/manuscript.Rmd
foundational >> seminal/germinal
Fig1 caption

@@
 # Abstract
-Scale remains a seminal concept in ecology. Spatial scale, for instance, has
+Scale remains a foundational concept in ecology. Spatial scale, for instance, has
 become a central consideration in the way we understand landscape ecology and
@@
 phenotypes and individual fitness [@Webber_2018], movement ecology and collective
-movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->,  and .
+movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->.
 
-(ref:spacetime) Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
+(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent 
+required for different types of social and communication processes for four species, including 
+hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions,
+e.g. mating, grooming, or aggression, are similar for most species because physical contact between 
+two individuals is required for most social interactions. The logical extension is that spatial and temporal extent for
+social interaction is nested within the spatial and temporal extent for social association because individuals must 
+shared space to interact. By contrast, different species have potential for  greater spatial and 
+temporal extents, for example, temporal extent for vocal communication is similar 
+for most species because most vocal calls only persist in the environment for seconds, but spatial 
+extent for vocal communication is highly variable with elephant calls extending the great distance and 
+passerine calls extending the shortest distance.
 

### 2020-02-10 paper/manuscript.Rmd
so many more refs

@@
 example, grooming requires close spatial proximity between conspecifics and
-occurs over brief time periods (e.g. Carter et al. 2015), whereas social
+occurs over brief time periods [e.g. @Carter_2015], whereas social
 association represents shared space use by members of the same social group
-(Figure \@ref(fig:spacetime), Franks et al. 2010). Further, for social
+[Figure \@ref(fig:spacetime), @Franks_2010]. Further, for social
 interactions or associations to occur individuals must share space, and thus
@@
 range overlap is a relatively coarse scale of sociality across which individuals
-share space over coarser spatial and temporal scales (e.g. Piza-Roca et al.
-2018). Although the social environment clearly scales spatially and temporally,
+share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018]. 
+Although the social environment clearly scales spatially and temporally,
 it remains unclear whether coarser scales of sociality, including social
@@
 Animal social network analysis is a well-developed tool used to measure the
-relationships of individuals and organization of social systems (Krause et al.
-2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides
+relationships of individuals and organization of social systems 
+[@Krause_2009; @Wey_2008; @Croft_2011]. Social network analysis provides
 insight into the structure of social communities and social network properties,
 which can influence population dynamics and evolutionary processes
-(Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use
-and innovation of traditional social network analysis (Webber & Vander Wal
-2019), it typically considers a single scale of sociality in a given network
+[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use
+and innovation of traditional social network analysis [@Webber_2019], 
+it typically considers a single scale of sociality in a given network
 (monolayer), drastically simplifying the potential complexity of animal social
@@
 consider social systems across contexts, including scale-dependent contexts
-(Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
+[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
 representing (i) different classes of individuals, e.g. male or female; (ii) types 
@@
 e.g. local or regional, or temporal windows, e.g. daily or seasonal 
-(Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal
+ [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
 behaviour [Silk_2018; @Finn_2019], although they have been used to
@@
 observations as well as the data collection technique used to generate networks
-(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
+[@Davis_2018; @Webber_2019]. In addition to altering the
 temporal scale by adjusting the time window, we investigated the influence of

### 2020-02-10 paper/citations.R

@@ -4,14 +4,24 @@ library(knitcitations)
 
 ### Sections ----
 ## Introduction
+
+# Croft 2008
+citep('10.1016/j.tree.2011.05.012')
+
 # levin, allen
 citep(c('10.2307/1941447', '10.7312/alle06918'))
 
 # legendre 93, chave 2013
 citep(c('10.2307/1939924', '10.1111/ele.12048')) 
 
+# Davis 2018
+citep('10.1016/j.anbehav.2018.04.012')
+
 # field 2009
 citep('10.1111/j.1365-2699.2008.01963.x')
+
+# Franks 2010
+citep('10.1007/s00265-009-0865-8')
 
 # eli 2009, mayo2007, sugihara 1989
 citep('10.1146/annurev.ecolsys.110308.120159')
@@ -21,6 +31,32 @@ citep('10.1126/science.2740915')
 # luthe2009
 citep('10.1093/beheco/arp074')
 
+# Kivela 2014
+citep('10.1093/comnet/cnu016')
+
+# Krause 2009
+citep('10.1007/s00265-009-0747-0')
+
+# Kurvers et al 2014
+citep('10.1016/j.tree.2014.04.002')
+
+# Pinter-Wollman 2014
+citep('10.1093/beheco/art047')
+
+#Piza-Roca 2018
+citep('10.1016/j.anbehav.2018.08.001')
+
+# Pilosof et al 2017
+citep('s41559-017-0101')
+
+# Porter 2018
+citep('10.1090/noti1746')
+
+# Webber and Vander Wal 2019
+citep('10.1016/j.anbehav.2019.01.010')
+
+# Wey et al 2008
+citep('10.1016/j.anbehav.2007.06.020')
 
 ## Case study
 ### Caribou socioecology

### 2020-02-10 paper/manuscript.Rmd
refs blah refs

@@
 occurs over brief time periods [e.g. @Carter_2015], whereas social
-association represents shared space use by members of the same social group
-[Figure \@ref(fig:spacetime), @Franks_2010]. Further, for social
-interactions or associations to occur individuals must share space, and thus
+association represents shared space use by members of the same social group [Figure 1, @Franks_2009].
+<!--Figure \@ref(fig:spacetime) TODO: something broken here?? --> 
+Further, for social interactions or associations to occur individuals must share space, and thus
 have overlapping home ranges. In the context of the social environment, home
@@
 association and home range overlap, vary predictably with social interaction
- [@Castles_2014; @Farine2015a]. Thus, we define social scale as the type of
+ [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the type of
 social relationship observed that can be explicitly defined and measured [@Farine_2015a]. 
+<!-- Farine references comes out as D.R. Farine 2015 -->
 
@@
  [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
-behaviour [Silk_2018; @Finn_2019], although they have been used to
+behaviour [@Silk_2018; @Finn_2019], although they have been used to
 describe multidimensional human social systems, complex transportation networks,
@@
 development and application of scale in multilayer networks with respect to 
-phenotypes and individual fitness [@Webber_2018], movement ecology and collective
-movement [@Jolles_2019], and habitat selection and space use <!-- TODO: (REF)-->.
+phenotypes and individual fitness [@Webber_2018] <!-- TODO: ref should be 2018, but defaulting to 2017-->, 
+movement ecology and collective
+movement [@Jolles_2019], and habitat selection and space use. <!-- TODO: (REF)-->
 
@@
 social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage (Bergerud 1974)<!-- TODO: get Bergerud ref-->. As a result,
-caribou tend to occupy and re-use craters once they are established and there is
+access forage [@Bergerud_1974]. As a result, caribou tend to occupy and re-use 
+craters once they are established and there is
 considerably less access to forage than when the landscape is snow-free.
@@
 (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
-1,250 g) as described by Schaefer and Mahoney (2013). Collars were programmed to
+1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
 collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes

### 2020-02-10 paper/citations.R

@@ -47,7 +47,7 @@ citep('10.1093/beheco/art047')
 citep('10.1016/j.anbehav.2018.08.001')
 
 # Pilosof et al 2017
-citep('s41559-017-0101')
+citep('10.1038/s41559-017-0101')
 
 # Porter 2018
 citep('10.1090/noti1746')
@@ -63,16 +63,17 @@ citep('10.1016/j.anbehav.2007.06.020')
 # TODO: Lesmerises 2018 -- check that's right
 citep('10.1016/j.anbehav.2018.03.014')
 
+## Schaefer and Mahoney
+citep('10.1139/cjz-2013-0132')
+
 # peignier
 citep('10.1002/ece3.5071')
 
-# TODO: Bergerud 1974
+# Bergerud 1974
+citep('10.2307/3543960')
 
 # mayor 2009
 citep('10.2980/16-2-3238')
-
-### Caribou location 
-# TODO: Schaefer and Mahoney (2013)
 
 ## Bjorness 2010
 citep('10.1111/j.1937-2817.2010.tb01258.x')
@@ -110,10 +111,6 @@ citep('10.1111/2041-210X.13177')
 
 
 ## temporal scale
-# davis 2018
-
-# webber vander 2019
-
 
 ## perspectives
 

### 2020-02-10 paper/manuscript.Rmd
refs blah blah

@@
 increasingly linked to important fitness for individuals of various species,
-including primates (e.g. Brent, Ruiz-Lambides, & Platt, 2017; Thompson, 2019),
-dolphins (e.g. Stanton & Mann, 2012; Stanton, Gibson, & Mann, 2011), and birds
-(e.g. McDonald, 2007; Royle, Pike, Heeb, Richner, & Kolliker, 2012). Both
+including primates [@Brent_2017; @Thompson_2019],
+dolphins [@Stanton_2012; @Stanton_2011], and birds
+[@McDonald_2007; @Royle_2012]. Both
 temporal, seasons and stages of life, and social scales, types of interactions,
 have emerged as important for understanding fitness consequences in the context
-of social network positions (Almeling, Hammerschmidt, Sennhenn-Reulen, Freund, &
-Fischer, 2016; Berger, Lemaître, Allainé, Gaillard, & Cohas, 2015; Brent,
-Ruiz-Lambides, & Platt, 2017; Holekamp, Smith, Strelioff, Van Horn, & Watts,
-2012). Multilayer networks provide a way to bridge these different scales so
+of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017, @Holekamp_2012]. Multilayer networks provide a way to bridge these different scales so
 that we can examine social phenotypes in more holistic ways rather than looking
@@
 interact, and many studies therefore assume that proximity is proxy for
-interacting (Farine, 2015). For instance, baboons need to be in proximity in
+interacting [@Farine_2015a]. For instance, baboons need to be in proximity in
 order to groom each other. However, animals have certain interactions that do
@@
 particularly long-distance communication networks with devices like microphone
-arrays (Snijders & Naguib, 2017). These varying social scales can have different
+arrays [Snijders_2017]. These varying social scales can have different
 fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) had
 higher survivorship when they had fewer but stronger, more stable social
-associates and grooming partners rather than simply more associates (Ellis,
-Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights
+associates and grooming partners rather than simply more associates [Ellis_2019]. This finding highlights
 that different qualities of social scales have lasting consequences.
@@
 phenotypes. For instance, social phenotypes can change over ontogeny in ways
-that can affect fitness (Berger et al., 2015; Brent et al., 2017). Thus, it is
+that can affect fitness [@Berger_2015, @Brent_2017]. Thus, it is
 critical to carefully consider the temporal scale that is meaningful for the
@@
 scales across ontogeny, individuals progress through development at different
-rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can
+rates [@Tarka_2018]. This variation can
 make defining appropriate temporal scales for testing the fitness implications
@@
 scales provide insight across developmental stages that may otherwise be missed
-(Turner, Bills, & Holekamp, 2018).
+[@Turner_2018].
 
@@
 and associations, especially over time, it is hard to test hypotheses about
-social dynamics with a suitable null control (Farine, 2017; Proskurnikov &
-Tempo, 2017). Using the framework of multilayer networks, making layers of
+social dynamics with a suitable null control [@Farine_2017, @Proskurnikov_2017]. Using the framework of multilayer networks, making layers of
 different temporal periods provides a way to make appropriate null models to
@@
 time period, and the period should be long enough for each layer to have enough
-data for robust networks (Farine, 2017). These considerations may be limiting
+data for robust networks [@Farine_2017]. These considerations may be limiting
 factors when answering questions that require timeframes that are relevant to

### 2020-02-10 paper/manuscript.Rmd
fiddly refs

@@
 landscapes, and temporal scale of analysis influence our ability to interpret
-complex social systems? Second, can variation in the social, spatial, and temporal
-improve predictions associated with biological differences in seasonal resource
-availability and social association? We conclude with perspectives for further
-development and application of scale in multilayer networks with respect to 
-phenotypes and individual fitness [@Webber_2018] <!-- TODO: ref should be 2018, but defaulting to 2017-->, 
-movement ecology and collective
-movement [@Jolles_2019], and habitat selection and space use. <!-- TODO: (REF)-->
+complex social systems? Second, can variation in the social, spatial, and
+temporal improve predictions associated with biological differences in seasonal
+resource availability and social association? We conclude with perspectives for
+further development and application of scale in multilayer networks with respect
+to phenotypes and individual fitness [@Webber_2018], movement ecology and
+collective movement [@Jolles_2019], and habitat selection and space use. <!--
+TODO: (REF)--> <!-- TODO: Webber reference should be 2018, but defaulting to
+2017-->
 

### 2020-02-10 paper/manuscript.Rmd
reflow, including fig caps

@@
 output:
-   github_document
-  # bookdown::pdf_document2:
-  #    number_sections: false
+   # github_document
+  bookdown::pdf_document2:
+     number_sections: false
   #bookdown::word_document2:
@@
 # Abstract
-Scale remains a foundational concept in ecology. Spatial scale, for instance, has
-become a central consideration in the way we understand landscape ecology and
-animal space use. Meanwhile, social processes can also scale from fine-scale
+Scale remains a foundational concept in ecology. Spatial scale, for instance,
+has become a central consideration in the way we understand landscape ecology
+and animal space use. Meanwhile, social processes can also scale from fine-scale
 interactions to co-occurrence to overlapping home ranges. Multilayer networks
@@
 there remains an important biological and methodological gap in our
-understanding of an animal’s perception of scale. But
-scale can affect multilayer network dynamics and how we build and interpret
-them. Here we discuss the role of scale in the context of multilayer networks
-and provide a social ungulate case study to illustrate the role
-of social, spatial, and temporal scale on multilayer processes. We also present
-perspectives on future development and application of scale in multilayer
-networks with respect to: habitat selection and space use; phenotypes and individual fitness; and movement ecology and collective movement. Effective integration
-of social and spatial processes, including biologically meaningful scales,
-within the context of animal social networks is an emerging area of research;
-our contribution incorporates perspectives on how the social
-environment and spatial processes are linked across scales in a multilayer
+understanding of an animal’s perception of scale. But scale can affect
+multilayer network dynamics and how we build and interpret them. Here we discuss
+the role of scale in the context of multilayer networks and provide a social
+ungulate case study to illustrate the role of social, spatial, and temporal
+scale on multilayer processes. We also present perspectives on future
+development and application of scale in multilayer networks with respect to:
+habitat selection and space use; phenotypes and individual fitness; and movement
+ecology and collective movement. Effective integration of social and spatial
+processes, including biologically meaningful scales, within the context of
+animal social networks is an emerging area of research; our contribution
+incorporates perspectives on how the social environment and spatial processes
+are linked across scales in a multilayer
 
@@
 example, grooming requires close spatial proximity between conspecifics and
-occurs over brief time periods [e.g. @Carter_2015], whereas social
-association represents shared space use by members of the same social group [Figure 1, @Franks_2009].
-<!--Figure \@ref(fig:spacetime) TODO: something broken here?? --> 
-Further, for social interactions or associations to occur individuals must share space, and thus
-have overlapping home ranges. In the context of the social environment, home
-range overlap is a relatively coarse scale of sociality across which individuals
-share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018]. 
-Although the social environment clearly scales spatially and temporally,
-it remains unclear whether coarser scales of sociality, including social
-association and home range overlap, vary predictably with social interaction
- [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the type of
-social relationship observed that can be explicitly defined and measured [@Farine_2015a]. 
-<!-- Farine references comes out as D.R. Farine 2015 -->
+occurs over brief time periods [e.g. @Carter_2015], whereas social association
+represents shared space use by members of the same social group [Figure 1,
+@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
+Further, for social interactions or associations to occur individuals must share
+space, and thus have overlapping home ranges. In the context of the social
+environment, home range overlap is a relatively coarse scale of sociality across
+which individuals share space over coarser spatial and temporal scales [e.g.
+@Piza_Roca_2018]. Although the social environment clearly scales spatially and
+temporally, it remains unclear whether coarser scales of sociality, including
+social association and home range overlap, vary predictably with social
+interaction [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the
+type of social relationship observed that can be explicitly defined and measured
+[@Farine_2015a]. <!-- Farine references comes out as D.R. Farine 2015 -->
 
 Animal social network analysis is a well-developed tool used to measure the
-relationships of individuals and organization of social systems 
-[@Krause_2009; @Wey_2008; @Croft_2011]. Social network analysis provides
-insight into the structure of social communities and social network properties,
-which can influence population dynamics and evolutionary processes
-[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use
-and innovation of traditional social network analysis [@Webber_2019], 
-it typically considers a single scale of sociality in a given network
-(monolayer), drastically simplifying the potential complexity of animal social
-systems [@Finn_2019].
+relationships of individuals and organization of social systems [@Krause_2009;
+@Wey_2008; @Croft_2011]. Social network analysis provides insight into the
+structure of social communities and social network properties, which can
+influence population dynamics and evolutionary processes [@Pinter_Wollman_2013;
+@Kurvers_2014]. Despite the widespread use and innovation of traditional social
+network analysis [@Webber_2019], it typically considers a single scale of
+sociality in a given network (monolayer), drastically simplifying the potential
+complexity of animal social systems [@Finn_2019].
 
@@
 [@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
-representing (i) different classes of individuals, e.g. male or female; (ii) types 
-of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial areas,
-e.g. local or regional, or temporal windows, e.g. daily or seasonal 
- [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
-behaviour [@Silk_2018; @Finn_2019], although they have been used to
-describe multidimensional human social systems, complex transportation networks,
-and neural networks [@Silk_2018]. The role of scale within multilayer
+representing (i) different classes of individuals, e.g. male or female; (ii)
+types of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial
+areas, e.g. local or regional, or temporal windows, e.g. daily or seasonal
+[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
+studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
+used to describe multidimensional human social systems, complex transportation
+networks, and neural networks [@Silk_2018]. The role of scale within multilayer
 social networks remains unexplored but provides a unique opportunity to develop
@@
 
-(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent 
-required for different types of social and communication processes for four species, including 
-hyaena, passerine birds, sleepy lizards, and elephants. Spatial and temporal extent for social interactions,
-e.g. mating, grooming, or aggression, are similar for most species because physical contact between 
-two individuals is required for most social interactions. The logical extension is that spatial and temporal extent for
-social interaction is nested within the spatial and temporal extent for social association because individuals must 
-shared space to interact. By contrast, different species have potential for  greater spatial and 
-temporal extents, for example, temporal extent for vocal communication is similar 
-for most species because most vocal calls only persist in the environment for seconds, but spatial 
-extent for vocal communication is highly variable with elephant calls extending the great distance and 
-passerine calls extending the shortest distance.
+(ref:spacetime) Space-time diagram displaying variation the relative spatial and
+temporal extent required for different types of social and communication
+processes for four species, including hyaena, passerine birds, sleepy lizards,
+and elephants. Spatial and temporal extent for social interactions, e.g. mating,
+grooming, or aggression, are similar for most species because physical contact
+between two individuals is required for most social interactions. The logical
+extension is that spatial and temporal extent for social interaction is nested
+within the spatial and temporal extent for social association because
+individuals must shared space to interact. By contrast, different species have
+potential for  greater spatial and temporal extents, for example, temporal
+extent for vocal communication is similar for most species because most vocal
+calls only persist in the environment for seconds, but spatial extent for vocal
+communication is highly variable with elephant calls extending the great
+distance and passerine calls extending the shortest distance.
 
@@
 access forage [@Bergerud_1974]. As a result, caribou tend to occupy and re-use
-craters once they are established and there is
-considerably less access to forage than when the landscape is snow-free.
-Importantly, craters exist on the landscape at multiple scales: the crater scale
-(a single crater), the feeding area scale (multiple craters in close proximity),
-and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
-heterogeneous, with greater access in snow-free seasons compared to winter as
-well as spatially heterogeneous in winter because the distribution of craters on
-the landscape varies meaning that access to vegetation in winter is highly
-variable for caribou. We therefore partitioned data into two discrete seasons:
-summer (3 August - 20 September) and winter (1 January – 17 February) based on
-caribou socioecology [@Peignier_2019].
+craters once they are established and there is considerably less access to
+forage than when the landscape is snow-free. Importantly, craters exist on the
+landscape at multiple scales: the crater scale (a single crater), the feeding
+area scale (multiple craters in close proximity), and the winter range scale
+(all craters within an individual’s range) [@Mayor_2009]. The distribution of
+forage for caribou is therefore seasonally heterogeneous, with greater access in
+snow-free seasons compared to winter as well as spatially heterogeneous in
+winter because the distribution of craters on the landscape varies meaning that
+access to vegetation in winter is highly variable for caribou. We therefore
+partitioned data into two discrete seasons: summer (3 August - 20 September) and
+winter (1 January – 17 February) based on caribou socioecology [@Peignier_2019].
 
@@
 (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
-1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
-collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
-into a discrete removed all erroneous and outlier GPS fixes following [@Bjørneraas_2010]. 
-We did not collar all female caribou in the herd; however, we assumed that our 
-sample of collared animals was random.
+1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
+location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
+discrete removed all erroneous and outlier GPS fixes following
+[@Bjørneraas_2010]. We did not collar all female caribou in the herd; however,
+we assumed that our sample of collared animals was random.
 
@@
 We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): <!-- TODO: get Cairns ref-->
+caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): 
+<!-- TODO: get Cairns ref-->
 
@@
 
-We used a series of metrics to characterize the multilayer networks,
-focusing on the role of individuals, importance of individual layers and the
-similarity of different layers. To measure the role of individuals, we
-calculated degree centrality and graph strength. Degree centrality is the number
-of direct connections an individual has to other individuals in a network layer.
-Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer-specific season and landcover context <!-- TODO:
-citation for graph strength?-->. Extending degree centrality, we calculated
-multidegree, the sum of degree centrality across layers, and neighbourhood, the
-sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014].
-We evaluated the relevance and redundancy of layers by combining the multidegree
-and neighbourhood to calculate connective redundancy and layer relevance.
-Connective redundancy is the proportion of neighbours repeated in multiple
-layers, and layer relevance is the proportion of neighbours present in each
-layer compared to the neighbourhood for each individual [@Berlingerio_2012].
-Finally, we calculated the similarity of layers between seasons, across
-landcover classes (e.g.: winter open compared to summer open) using the Pearson
-correlation coefficient [@Br_dka_2018].
+We used a series of metrics to characterize the multilayer networks, focusing on
+the role of individuals, importance of individual layers and the similarity of
+different layers. To measure the role of individuals, we calculated degree
+centrality and graph strength. Degree centrality is the number of direct
+connections an individual has to other individuals in a network layer. Graph
+strength is the degree weighted by the strength of association, in this case
+SRI, in each layer-specific season and landcover context <!-- TODO: citation for
+graph strength?-->. Extending degree centrality, we calculated multidegree, the
+sum of degree centrality across layers, and neighbourhood, the sum of unique
+neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
+the relevance and redundancy of layers by combining the multidegree and
+neighbourhood to calculate connective redundancy and layer relevance. Connective
+redundancy is the proportion of neighbours repeated in multiple layers, and
+layer relevance is the proportion of neighbours present in each layer compared
+to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
+calculated the similarity of layers between seasons, across landcover classes
+(e.g.: winter open compared to summer open) using the Pearson correlation
+coefficient [@Br_dka_2018].
 
@@
 To assess the influence of spatial scale on multilayer networks, we aggregated
-our landcover raster at varying scales relevant to caribou ecology.
-We aggregated the 10 m landcover raster using the R package `grainchanger`
-[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation occurred
-using a modal moving window method using a circular window corresponding to the
-above scales [@Graham_2019a]. We assume 10 m and 100 m represents fine-scale decision making
-for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500 m and 1000 m
-represents the scale at which caribou tend to select and avoid habitat
-(Bastille-Rousseau et al. 2017).
+our landcover raster at varying scales relevant to caribou ecology. We
+aggregated the 10 m landcover raster using the R package `grainchanger`
+[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
+occurred using a modal moving window method using a circular window
+corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
+represents fine-scale decision making for caribou during foraging (Webber et al.
+unpublished data), while re-sampling at 500 m and 1000 m represents the scale at
+which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).
 
@@
 position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for winter (starting at 1 January)
-and summer (starting at 3 August). The position of the time window was shifted by 1-48 days,
-using a fixed time window length of 48 days. These new time windows were
-iteratively used to partition data into two discrete seasons (winter, summer)
-and generate multilayer networks.
+window varied from 40-100 days using a fixed start day for winter (starting at 1
+January) and summer (starting at 3 August). The position of the time window was
+shifted by 1-48 days, using a fixed time window length of 48 days. These new
+time windows were iteratively used to partition data into two discrete seasons
+(winter, summer) and generate multilayer networks.
 
@@
 observations as well as the data collection technique used to generate networks
-[@Davis_2018; @Webber_2019]. In addition to altering the
-temporal scale by adjusting the time window, we investigated the influence of
-the number of observations on resulting multilayer networks. We randomly
-selected 500 timesteps and iteratively included 25 additional observations,
-regenerating the multilayer network and calculating associations of individuals.
-Subsequent iterations included the previous set of observations to mimic
-observational data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
+[@Davis_2018; @Webber_2019]. In addition to altering the temporal scale by
+adjusting the time window, we investigated the influence of the number of
+observations on resulting multilayer networks. We randomly selected 500
+timesteps and iteratively included 25 additional observations, regenerating the
+multilayer network and calculating associations of individuals. Subsequent
+iterations included the previous set of observations to mimic observational
+data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
 
@@
 
-(ref:socres) Varying scale in social threshold.
-For each social threshold (5 m, 50 m, 100 m, 150 m, 200 m, 250 m, 300 m, 350 m, 400 m, 450 m, 500 m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections.
-B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.
-<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.
+(ref:socres) Varying scale in social threshold. For each social threshold (5 m,
+50 m, 100 m, 150 m, 200 m, 250 m, 300 m, 350 m, 400 m, 450 m, 500 m), multilayer
+networks were constructed for each landcover class (forest, lichen and open)
+across two seasons (summer and winter) and four network metrics calculated.  A)
+Mean graph strength across individuals showed an increase for winter network
+layers at 50 m through 500 m while summer network layers had consistently weak
+connections. B) Mean layer relevance was relatively stable across social
+thresholds for each season and landcover layer. C) Similarity of landcover
+network layers between seasons (e.g.: open summer compared to open winter)
+showed different responses to changing landcover scale with an overall increase
+in similarity for open layers and decrease in similarity for lichen layers.
+<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
+increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
+approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
+between 400 m and 500 m.
 
@@
 
-(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
-For each landcover resolution (10 m, 100 m, 250 m, 500 m and 1000 m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
-A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
-B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m.
-Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10 m landcover resolution.
-D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+(ref:lcres) Variation in multilayer network metrics as a function of changes in
+landcover resolution, a metric which we interpret as spatial scale. For each
+landcover resolution (10 m, 100 m, 250 m, 500 m and 1000 m), multilayer networks
+were constructed for each landcover class (forest, lichen and open) across two
+seasons (summer and winter), and four network metrics were calculated and we
+examined how network metrics changed as a function of changes in spatial scale.
+A) Mean graph strength of individuals was weaker during the summer compared to
+the winter months. B) Mean layer relevance showed sparse connectivity in summer
+compared to winter networks and a decrease in winter lichen layer relevance at
+higher landcover resolutions. C) Similarity of landcover network layers between
+seasons (e.g.: open summer compared to open winter) showed different responses
+to changing landcover scale with an increase in similarity for forest layers at
+250 m and decrease in similarity for open layers at 250 m. Note that lichen
+layer similarity is not shown because individuals did not interact in lichen
+habitats greater greater than 10 m landcover resolution. D) Mean connective
+redundancy across individuals showed a decreasing trend with increasing
+landcover resolution.
 
@@
 <!-- TODO: RO first sentence... -->
-(ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
-B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open.
-<!--TODO:*There were observations of individuals in lichen and open areas at lower numbers of observations during the winter, so layer similarity could not be calculated at these values.* **Brief explanation of why two landcover don't have values at lower nobs??**.--> D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+(ref:nobs) Varying scale in number of observations. For each iteration, a number
+of observations (10-485 observations in steps of 25) were selected from the
+complete data set to construct multilayer networks with layers defined by each
+landcover class (forest, lichen and open) across two seasons (summer and winter)
+and four network metrics calculated. A) Mean graph strength across individuals
+varied for winter layers becoming relatively stable at 200 observations and
+remained weak throughout for summer layers. B) Mean layer relevance across
+individuals increased for winter layers and slightly increased for summer
+layers. C) Similarity of landcover network layers between seasons (e.g.: open
+summer compared to open winter) showed a stabilizing layer similarity at 200
+observations for forest and 300 observations for lichen and open.
+<!--TODO:*There were observations of individuals in lichen and open areas at
+lower numbers of observations during the winter, so layer similarity could not
+be calculated at these values.* **Brief explanation of why two landcover don't
+have values at lower nobs??**.--> D) Mean connective redundancy across
+individuals increased with increasing number of observations, which begins to
+plateau around 100 observations.
 
@@
 
-(ref:winlen) Varying scale in time window length.
-For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated.
-A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
-<!--TODO:**[see if you agree with my changes.
-B-D were based off fig.
-3 and not relevant to this figure]**-->  B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig.
-3.
-I don't know if what I wrote best encapsulates what connnective redundancy does here.
-Length of time window seems to make connective redundancy highly variable as it changes.]**.-->
+(ref:winlen) Varying scale in time window length. For each time window length
+(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
+were constructed for each landcover class (forest, lichen and open) across two
+seasons (summer and winter) and four network metrics calculated. A) Mean graph
+strength across individuals was relatively stable over increasing time window
+lengths, though there was more variation in strength between landcover types as
+window length increased. <!--TODO:**[see if you agree with my changes. B-D were
+based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
+generally increased during the summer months but was relatively stable across
+time window lengths for each landcover layer. C) Similarity of landcover network
+layers between seasons (e.g.: open summer compared to open winter) showed
+increasing similarity consistent across landcover layers with increasing window
+length. D) Mean connective redundancy across individuals varied dramatically
+depending on the length of the time window <!--TODO:**[JWT: previously this was
+describing fig. 3. I don't know if what I wrote best encapsulates what
+connnective redundancy does here. Length of time window seems to make connective
+redundancy highly variable as it changes.]**.-->
 
@@
 
-(ref:winpos) Varying scale in time window position.
-For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, lichen and ope) across two seasons (summer and winter) and four network metrics calculated.
-A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
-B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and greater connectivity in summer layers at later window positions.
-C) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
-<!--TODO:**[JWT: previously describing window length, not position.
-Check that you're ok with my changes]**--> D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+(ref:winpos) Varying scale in time window position. For each time window
+position (shifting the start date of the time window used to define seasons 1 to
+48 days from the original), multilayer networks were constructed for each
+landcover class (forest, lichen and ope) across two seasons (summer and winter)
+and four network metrics calculated. A) Mean graph strength across individuals
+increased in summer network layers at window position 25 and increased between
+window position 20 and 40 for winter network layers. B) Mean layer relevance
+slightly decreased for winter layers and increased for summer layers, showing
+decreasing connectivity in shifted winter time windows and greater connectivity
+in summer layers at later window positions. C) Similarity of landcover network
+layers between seasons (e.g.: open summer compared to open winter) showed
+fluctuations in layer similarity across landcover types with shifted time
+windows. <!--TODO:**[JWT: previously describing window length, not position.
+Check that you're ok with my changes]**--> D) Mean connective redundancy across
+individuals increased between window position 12 through 48 due to increased
+connectivity in the summer network layers.
 
@@
 
-The integration of behavioural and ecological theory has shown the value of considering 
-the importance of various ecological disciplines to better understand and predict animal 
-social networks, including demography (Shizuka and Johnson 2019), evolutionary and 
-quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al. 2017), 
-and animal personality (Sih et al. 2017). While the number of studies integrating 
-social network theory into a broader array of behavioural and ecological 
-sub-disciplines is impressive, only recently has the role of animal space use been 
-considered in describing the causes and consequences of the social environment in the 
-context of (1) phenotypes and individual fitness [@Webber_2018], (2) 
-movement ecology and collective movement [@Bode_2011], and (3) habitat 
-selection and space use [@He_2019]. Importantly, much of the work linking 
-space use and the social environment has been theoretical and empirical studies 
-are lacking (but see Peignier et al. 2019; Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). 
-Here, we discuss the role mutlilayer networks within the emerging integration 
-of social and spatial ecology within the behavioural ecology literature.
+The integration of behavioural and ecological theory has shown the value of
+considering the importance of various ecological disciplines to better
+understand and predict animal social networks, including demography (Shizuka and
+Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017),
+disease ecology (Silk et al. 2017), and animal personality (Sih et al. 2017).
+While the number of studies integrating social network theory into a broader
+array of behavioural and ecological sub-disciplines is impressive, only recently
+has the role of animal space use been considered in describing the causes and
+consequences of the social environment in the context of (1) phenotypes and
+individual fitness [@Webber_2018], (2) movement ecology and collective movement
+[@Bode_2011], and (3) habitat selection and space use [@He_2019]. Importantly,
+much of the work linking space use and the social environment has been
+theoretical and empirical studies are lacking (but see Peignier et al. 2019;
+Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). Here, we discuss the
+role mutlilayer networks within the emerging integration of social and spatial
+ecology within the behavioural ecology literature.
 
@@
 increasingly linked to important fitness for individuals of various species,
-including primates [@Brent_2017; @Thompson_2019],
-dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Both
-temporal, seasons and stages of life, and social scales, types of interactions,
-have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017, @Holekamp_2012]. Multilayer networks provide a way to bridge these different scales so
-that we can examine social phenotypes in more holistic ways rather than looking
-at each scale separately as has traditionally been done.
+including primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
+@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both temporal, seasons
+and stages of life, and social scales, types of interactions, have emerged as
+important for understanding fitness consequences in the context of social
+network positions [@Almeling_2016, @Berger_2015, @Brent_2017, @Holekamp_2012].
+Multilayer networks provide a way to bridge these different scales so that we
+can examine social phenotypes in more holistic ways rather than looking at each
+scale separately as has traditionally been done.
 
@@
 and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Cater_2015; @Farine_2015a].
-Furthermore, it is a common trope that individuals must be associating to
-interact, and many studies therefore assume that proximity is proxy for
-interacting [@Farine_2015a]. For instance, baboons need to be in proximity in
-order to groom each other. However, animals have certain interactions that do
-not require proximity such as long-distance vocalization and olfactory signals
-[@Carter_2015] With the advancement of biologging technology, we have
-the ability to record social interactions that do not require proximity,
-particularly long-distance communication networks with devices like microphone
-arrays [Snijders_2017]. These varying social scales can have different
-fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) had
-higher survivorship when they had fewer but stronger, more stable social
-associates and grooming partners rather than simply more associates [Ellis_2019]. This finding highlights
-that different qualities of social scales have lasting consequences.
+question [@Castles_2014; @Cater_2015; @Farine_2015a]. Furthermore, it is a
+common trope that individuals must be associating to interact, and many studies
+therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
+instance, baboons need to be in proximity in order to groom each other. However,
+animals have certain interactions that do not require proximity such as
+long-distance vocalization and olfactory signals [@Carter_2015] With the
+advancement of biologging technology, we have the ability to record social
+interactions that do not require proximity, particularly long-distance
+communication networks with devices like microphone arrays [Snijders_2017].
+These varying social scales can have different fitness repercussions for
+individuals. Rhesus macaques (*Macaca mulatta*) had higher survivorship when
+they had fewer but stronger, more stable social associates and grooming partners
+rather than simply more associates [Ellis_2019]. This finding highlights that
+different qualities of social scales have lasting consequences.
 
@@
 phenotypes. For instance, social phenotypes can change over ontogeny in ways
-that can affect fitness [@Berger_2015, @Brent_2017]. Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses. Further complicating the issue of selecting suitable time
-scales across ontogeny, individuals progress through development at different
-rates [@Tarka_2018]. This variation can
-make defining appropriate temporal scales for testing the fitness implications
-of an individual’s social phenotype over different stages of ontogeny even more
-difficult when they vary by individual. However, considering fine temporal
-scales provide insight across developmental stages that may otherwise be missed
-[@Turner_2018].
+that can affect fitness [@Berger_2015, @Brent_2017]. Thus, it is critical to
+carefully consider the temporal scale that is meaningful for the proposed
+hypotheses. Further complicating the issue of selecting suitable time scales
+across ontogeny, individuals progress through development at different rates
+[@Tarka_2018]. This variation can make defining appropriate temporal scales for
+testing the fitness implications of an individual’s social phenotype over
+different stages of ontogeny even more difficult when they vary by individual.
+However, considering fine temporal scales provide insight across developmental
+stages that may otherwise be missed [@Turner_2018].
 
@@
 frequent correlations between social network metrics in different types of
-networks [@Castles_2014]. Furthermore, multilayer networks provide a
-framework to test hypotheses linking social phenotypes and fitness across
-temporal scales. Because of the non-independent nature of social interactions
-and associations, especially over time, it is hard to test hypotheses about
-social dynamics with a suitable null control [@Farine_2017, @Proskurnikov_2017]. Using the framework of multilayer networks, making layers of
-different temporal periods provides a way to make appropriate null models to
-test questions about the dynamics of an individual’s social network position
-over multiple aggregated time periods.
+networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
+to test hypotheses linking social phenotypes and fitness across temporal scales.
+Because of the non-independent nature of social interactions and associations,
+especially over time, it is hard to test hypotheses about social dynamics with a
+suitable null control [@Farine_2017, @Proskurnikov_2017]. Using the framework of
+multilayer networks, making layers of different temporal periods provides a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods.
 
@@
 
-Social processes, movement decisions, and space use are inextricably linked 
-and multilayer networks represent a potential analytical framework for linking 
-these processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group can 
-reduce per capita predation risk via detection-dilution trade-offs and improve 
-information transfer about the quality or location of resources to other group 
-members [@Jolles_2019]. In our case study, we integrate proximity based 
-social networks that inherently rely on animal collective movement and, in general, 
-we found that movement is likely an important mechanism driving social network 
-connectivity within and between habitat types.
+Social processes, movement decisions, and space use are inextricably linked and
+multilayer networks represent a potential analytical framework for linking these
+processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group
+can reduce per capita predation risk via detection-dilution trade-offs and
+improve information transfer about the quality or location of resources to other
+group members [@Jolles_2019]. In our case study, we integrate proximity based
+social networks that inherently rely on animal collective movement and, in
+general, we found that movement is likely an important mechanism driving social
+network connectivity within and between habitat types.
 
@@
 movement behaviour within multilayer networks has been considered.  Spatial
-networks are physical locations (nodes) which are connected in a network when individuals
-move between said locations (edges). For example, spatial networks were applied
-to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
-melanopterus*) between fixed location autonomous arrays. In this example, nodes
-represent locations within the array, *intralayer edges* represent individual
-movement frequency, and *interlayer edges* represent contact probability among
-individuals at a given node [@Mourier_2019] (Mourier et al. 2019). Although movement between 
-fixed arrays is inherent, networks are not constructed based on continuous 
-measures of dyadic or collective movement [@Long_2014]. Our case study 
-builds on the work of Mourier et al. (2019) and explicitly integrates 
-continuous and simultaneous measures of animal movement through space 
-and time as layers of a multilayer social network.
+networks are physical locations (nodes) which are connected in a network when
+individuals move between said locations (edges). For example, spatial networks
+were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
+*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
+example, nodes represent locations within the array, *intralayer edges*
+represent individual movement frequency, and *interlayer edges* represent
+contact probability among individuals at a given node [@Mourier_2019] (Mourier
+et al. 2019). Although movement between fixed arrays is inherent, networks are
+not constructed based on continuous measures of dyadic or collective movement
+[@Long_2014]. Our case study builds on the work of Mourier et al. (2019) and
+explicitly integrates continuous and simultaneous measures of animal movement
+through space and time as layers of a multilayer social network.
 
@@
 monolayer association networks within a multilayer network [@Papageorgiou_2019].
-However, despite potential to generate networks in different spatial or social contexts, 
-layers in the multilayer network represented social associations within and 
-between groups. Continuous collection of animal relocation data using GPS 
-technology can be used to measure how groups of animals make collective 
+However, despite potential to generate networks in different spatial or social
+contexts, layers in the multilayer network represented social associations
+within and between groups. Continuous collection of animal relocation data using
+GPS technology can be used to measure how groups of animals make collective
 movement decisions in the context of their local environment
@@
 collective movement layer could constitute similarity in movement for dyads
-[@Long_2014] or groups  [@Bode_2011]. This movement layer could be
-made at a fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale
-[global migration: @Flack_2018]. Our case study integrates variation 
-in temporal and spatial scale to assess the role of scale in predicting 
-multilayer networks. As one might expect, we found increasing spatial 
-scale results in saturation of potential social connections (Figure 3), 
-while increasing temporal scale had little effect on habitat-specific 
-networks (Figure 5). Another potential application would be to
-generate social networks during times when animals are engaged in different
-behaviours, including traveling, interacting, or foraging [@Muller_2018; @Finn_2019] 
-and construct a multilayer network based on behaviour-specific monolayer 
-networks [e.g. @Smith_Aguilar_2019].
+[@Long_2014] or groups  [@Bode_2011]. This movement layer could be made at a
+fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
+@Flack_2018]. Our case study integrates variation in temporal and spatial scale
+to assess the role of scale in predicting multilayer networks. As one might
+expect, we found increasing spatial scale results in saturation of potential
+social connections (Figure 3), while increasing temporal scale had little effect
+on habitat-specific networks (Figure 5). Another potential application would be
+to generate social networks during times when animals are engaged in different
+behaviours, including traveling, interacting, or foraging [@Muller_2018;
+@Finn_2019] and construct a multilayer network based on behaviour-specific
+monolayer networks [e.g. @Smith_Aguilar_2019].
 
@@
 scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology 
-has advanced to the point where relocations can be programmed to occur as 
-frequently as each second [@Börger_2016], a practice which has been applied 
-to questions of collective movement [e.g @Strandburg_Peshkin_2015]. 
-Meanwhile, remote sensing technology, including unmanned aerial vehicles 
-and satellites, can be used to track the fine-scale movements of groups 
-over large distances and time scales [@Torney_2018]. Using 
-technology to infer behaviour has therefore become standard operating procedure
-for many species in many systems. Our ability to collect and process 
-remotely sensed data and infer social processes based on animal movement 
-provides an opportunity to use multilayer social network analysis to answer
-complex questions about animal socioecology.
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
+advanced to the point where relocations can be programmed to occur as frequently
+as each second [@Börger_2016], a practice which has been applied to questions of
+collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
+technology, including unmanned aerial vehicles and satellites, can be used to
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]. Using technology to infer behaviour has therefore become
+standard operating procedure for many species in many systems. Our ability to
+collect and process remotely sensed data and infer social processes based on
+animal movement provides an opportunity to use multilayer social network
+analysis to answer complex questions about animal socioecology.
 
 Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that
-explicity quantify movement paramters could be itnegrated. For example, edges 
-could represent measures of dyadic or collective movement based on dynamic 
-interaction metrics [@Long_2014]. Integrating movement layers
-with habitat-specific social association layers could further shed light on the
-role of movement as a driver of the social and spatial environments an
-individual experiences [@Webber_2018]. In our case study, we
-generated multilayer networks based on habitat-specific monolayers. Coordinated
-movement of dyads, or groups, could vary based on habitat, and the approach we
-outline could be used to explore mechanisms linking the social and spatial
-environments. For example, social processes may be an emergent property of the
-landscape because animals aggregate at resources, such as waterholes
-[@Chamaillé_Jammes_2008]. Movement to, from, or within habitat patches  or
-territories can also contribute to the formation of the social environment
-[@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*) males
-interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a
-multilayer network framework is a logical next step for a burgeoning field. In
-particular, when association networks are habitat-specific, we suggest the
-integration of movement and space use in multilayer networks provides novel
-insights into the effects of habitat configuration on the formation of the
-social environment [@He_2019].
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
+quantify movement paramters could be itnegrated. For example, edges could
+represent measures of dyadic or collective movement based on dynamic interaction
+metrics [@Long_2014]. Integrating movement layers with habitat-specific social
+association layers could further shed light on the role of movement as a driver
+of the social and spatial environments an individual experiences [@Webber_2018].
+In our case study, we generated multilayer networks based on habitat-specific
+monolayers. Coordinated movement of dyads, or groups, could vary based on
+habitat, and the approach we outline could be used to explore mechanisms linking
+the social and spatial environments. For example, social processes may be an
+emergent property of the landscape because animals aggregate at resources, such
+as waterholes [@Chamaillé_Jammes_2008]. Movement to, from, or within habitat
+patches  or territories can also contribute to the formation of the social
+environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
+males interacted primarily at home range edges, presumably driving territorial
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
+network framework is a logical next step for a burgeoning field. In particular,
+when association networks are habitat-specific, we suggest the integration of
+movement and space use in multilayer networks provides novel insights into the
+effects of habitat configuration on the formation of the social environment
+[@He_2019].
 

### 2020-02-10 paper/manuscript.Rmd

@@
 type), and temporal (seasonal). Caribou are gregarious ungulates with
-fission-fusion dynamics [@Lesmerises_2018] that display temporal
-[@Peignier_2019] and spatial (Webber et al. unpublished data) variation in
-social networks. In winter, caribou dig holes in the snow, termed craters, to
-access forage [@Bergerud_1974]. As a result, caribou tend to occupy and re-use
-craters once they are established and there is considerably less access to
-forage than when the landscape is snow-free. Importantly, craters exist on the
-landscape at multiple scales: the crater scale (a single crater), the feeding
-area scale (multiple craters in close proximity), and the winter range scale
-(all craters within an individual’s range) [@Mayor_2009]. The distribution of
-forage for caribou is therefore seasonally heterogeneous, with greater access in
-snow-free seasons compared to winter as well as spatially heterogeneous in
-winter because the distribution of craters on the landscape varies meaning that
-access to vegetation in winter is highly variable for caribou. We therefore
-partitioned data into two discrete seasons: summer (3 August - 20 September) and
-winter (1 January – 17 February) based on caribou socioecology [@Peignier_2019].
+fission-fusion dynamics [@Lesmerises_2018] that display temporal and spatial
+variation in social networks [@Peignier_2019]. In winter, caribou dig holes in
+the snow, termed craters, to access forage [@Bergerud_1974]. As a result,
+caribou tend to occupy and re-use craters once they are established and there is
+considerably less access to forage than when the landscape is snow-free.
+Importantly, craters exist on the landscape at multiple scales: the crater scale
+(a single crater), the feeding area scale (multiple craters in close proximity),
+and the winter range scale (all craters within an individual’s range)
+[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
+heterogeneous, with greater access in snow-free seasons compared to winter as
+well as spatially heterogeneous in winter because the distribution of craters on
+the landscape varies meaning that access to vegetation in winter is highly
+variable for caribou. We therefore partitioned data into two discrete seasons:
+summer (3 August - 20 September) and winter (1 January – 17 February) based on
+caribou socioecology [@Peignier_2019].
 
@@
 discrete removed all erroneous and outlier GPS fixes following
-[@Bjørneraas_2010]. We did not collar all female caribou in the herd; however,
+[@BJ_RNERAAS_2010]. We did not collar all female caribou in the herd; however,
 we assumed that our sample of collared animals was random.
@@
 corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
-represents fine-scale decision making for caribou during foraging (Webber et al.
-unpublished data), while re-sampling at 500 m and 1000 m represents the scale at
-which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).
+represents fine-scale decision making for caribou during foraging, while
+re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
+select and avoid habitat (Bastille-Rousseau et al. 2017).
 

### 2020-02-10 paper/manuscript.Rmd
edit fig captions

@@
 interlayer edges represented connections between the same individuals across
-contexts.
+contexts (Figure 2).
 
@@
 
-(ref:socres) Varying scale in social threshold. For each social threshold (5 m,
-50 m, 100 m, 150 m, 200 m, 250 m, 300 m, 350 m, 400 m, 450 m, 500 m), multilayer
+(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
 networks were constructed for each landcover class (forest, lichen and open)
@@
 landcover resolution, a metric which we interpret as spatial scale. For each
-landcover resolution (10 m, 100 m, 250 m, 500 m and 1000 m), multilayer networks
+landcover resolution, multilayer networks
 were constructed for each landcover class (forest, lichen and open) across two

### 2020-02-10 paper/manuscript.Rmd
fig captions

@@
 calculated the similarity of layers between seasons, across landcover classes
-(e.g.: winter open compared to summer open) using the Pearson correlation
+(e.g. winter open compared to summer open) using the Pearson correlation
 coefficient [@Br_dka_2018].
@@
 
+<!-- Figure 3: metrics by social scale -->
 (ref:socres) Varying scale in social threshold. For each social threshold, multilayer
@@
 thresholds for each season and landcover layer. C) Similarity of landcover
-network layers between seasons (e.g.: open summer compared to open winter)
+network layers between seasons (e.g. open summer compared to open winter)
 showed different responses to changing landcover scale with an overall increase
@@
 
+<!-- Figure 4: metrics by landcover resolution -->
 (ref:lcres) Variation in multilayer network metrics as a function of changes in
 landcover resolution, a metric which we interpret as spatial scale. For each
-landcover resolution, multilayer networks
-were constructed for each landcover class (forest, lichen and open) across two
-seasons (summer and winter), and four network metrics were calculated and we
-examined how network metrics changed as a function of changes in spatial scale.
-A) Mean graph strength of individuals was weaker during the summer compared to
-the winter months. B) Mean layer relevance showed sparse connectivity in summer
-compared to winter networks and a decrease in winter lichen layer relevance at
-higher landcover resolutions. C) Similarity of landcover network layers between
-seasons (e.g.: open summer compared to open winter) showed different responses
-to changing landcover scale with an increase in similarity for forest layers at
-250 m and decrease in similarity for open layers at 250 m. Note that lichen
-layer similarity is not shown because individuals did not interact in lichen
-habitats greater greater than 10 m landcover resolution. D) Mean connective
-redundancy across individuals showed a decreasing trend with increasing
-landcover resolution.
+landcover resolution, multilayer networks were constructed for each landcover
+class (forest, lichen and open) across two seasons (summer and winter), and four
+network metrics were calculated and we examined how network metrics changed as a
+function of changes in spatial scale. A) Mean graph strength of individuals was
+weaker during the summer compared to the winter months. B) Mean layer relevance
+showed sparse connectivity in summer compared to winter networks and a decrease
+in winter lichen layer relevance at higher landcover resolutions. C) Similarity
+of landcover network layers between seasons (e.g. open summer compared to open
+winter) showed different responses to changing landcover scale with an increase
+in similarity for forest layers at 250 m and decrease in similarity for open
+layers at 250 m. Note that lichen layer similarity is not shown because
+individuals did not interact in lichen habitats greater greater than 10 m
+landcover resolution. D) Mean connective redundancy across individuals showed a
+decreasing trend with increasing landcover resolution.
 
@@
 
+<!-- Figure 5: metrics by number of observations -->
 <!-- TODO: RO first sentence... -->
@@
 individuals increased for winter layers and slightly increased for summer
-layers. C) Similarity of landcover network layers between seasons (e.g.: open
+layers. C) Similarity of landcover network layers between seasons (e.g. open
 summer compared to open winter) showed a stabilizing layer similarity at 200
@@
 time window lengths for each landcover layer. C) Similarity of landcover network
-layers between seasons (e.g.: open summer compared to open winter) showed
+layers between seasons (e.g. open summer compared to open winter) showed
 increasing similarity consistent across landcover layers with increasing window
@@
 in summer layers at later window positions. C) Similarity of landcover network
-layers between seasons (e.g.: open summer compared to open winter) showed
+layers between seasons (e.g. open summer compared to open winter) showed
 fluctuations in layer similarity across landcover types with shifted time

### 2020-02-10 paper/manuscript.Rmd
who gives an eff about an oxford comma

@@
 (ref:socres) Varying scale in social threshold. For each social threshold, multilayer
-networks were constructed for each landcover class (forest, lichen and open)
+networks were constructed for each landcover class (forest, forage, and open)
 across two seasons (summer and winter) and four network metrics calculated.  A)
@@
 landcover resolution, multilayer networks were constructed for each landcover
-class (forest, lichen and open) across two seasons (summer and winter), and four
+class (forest, forage, and open) across two seasons (summer and winter), and four
 network metrics were calculated and we examined how network metrics changed as a
@@
 complete data set to construct multilayer networks with layers defined by each
-landcover class (forest, lichen and open) across two seasons (summer and winter)
+landcover class (forest, forage, and open) across two seasons (summer and winter)
 and four network metrics calculated. A) Mean graph strength across individuals
@@
 individuals increased with increasing number of observations, which begins to
-plateau around 100 observations.
+plateau around 100 observations. Note, data in panel C are truncated because 
+there were observations of individuals in lichen and open areas at
+lower numbers of observations during the winter, so layer similarity could not
+be calculated at these values.
 

### 2020-02-10 paper/manuscript.Rmd
fig 5 caption

@@
 complete data set to construct multilayer networks with layers defined by each
-landcover class (forest, forage, and open) across two seasons (summer and winter)
-and four network metrics calculated. A) Mean graph strength across individuals
-varied for winter layers becoming relatively stable at 200 observations and
-remained weak throughout for summer layers. B) Mean layer relevance across
-individuals increased for winter layers and slightly increased for summer
-layers. C) Similarity of landcover network layers between seasons (e.g. open
-summer compared to open winter) showed a stabilizing layer similarity at 200
-observations for forest and 300 observations for lichen and open. 
+landcover class (forest, forage, and open) across two seasons (summer and
+winter) and four network metrics calculated. A) Mean graph strength across
+individuals varied for winter layers becoming relatively stable at 200
+observations and remained weak throughout for summer layers. B) Mean layer
+relevance across individuals increased for winter layers and slightly increased
+for summer layers. C) Similarity of landcover network layers between seasons
+(e.g. open summer compared to open winter) showed a stabilizing layer similarity
+at 200 observations for forest and 300 observations for lichen and open.
 <!--TODO:*There were observations of individuals in lichen and open areas at
@@
 plateau around 100 observations. Note, data in panel C are truncated because
-there were observations of individuals in lichen and open areas at
-lower numbers of observations during the winter, so layer similarity could not
-be calculated at these values.
+there were few observations of individuals in foraging and open habitats during
+the winter, resulting in inability to calculate layer similarity at lower number
+of observations.
 

### 2020-02-10 paper/manuscript.Rmd
reflow, reflow, reflow

@@
 (e.g. open summer compared to open winter) showed a stabilizing layer similarity
-at 200 observations for forest and 300 observations for lichen and open.
-<!--TODO:*There were observations of individuals in lichen and open areas at
-lower numbers of observations during the winter, so layer similarity could not
-be calculated at these values.* **Brief explanation of why two landcover don't
-have values at lower nobs??**.--> D) Mean connective redundancy across
-individuals increased with increasing number of observations, which begins to
-plateau around 100 observations. Note, data in panel C are truncated because
-there were few observations of individuals in foraging and open habitats during
-the winter, resulting in inability to calculate layer similarity at lower number
-of observations.
+at 200 observations for forest and 300 observations for lichen and open. D) Mean
+connective redundancy across individuals increased with increasing number of
+observations, which begins to plateau around 100 observations. Note, data in
+panel C are truncated because there were few observations of individuals in
+foraging and open habitats during the winter, resulting in inability to
+calculate layer similarity at lower number of observations.
 

### 2020-02-10 paper/manuscript.Rmd
forage > lichen

@@
 aspects (season and landcover). Two season elementary-layers (winter and summer)
-and three landcover elementary-layers (open, forest and lichen) combined for a
+and three landcover elementary-layers (forest, forage, and open) combined for a
 total of six layers. Layers were composed of individuals represented as nodes
@@
 showed different responses to changing landcover scale with an overall increase
-in similarity for open layers and decrease in similarity for lichen layers.
+in similarity for open layers and decrease in similarity for forage layers.
 <!--TODO: what about forest.--> D) Mean connective redundancy across individuals
@@
 showed sparse connectivity in summer compared to winter networks and a decrease
-in winter lichen layer relevance at higher landcover resolutions. C) Similarity
+in winter forage layer relevance at higher landcover resolutions. C) Similarity
 of landcover network layers between seasons (e.g. open summer compared to open
@@
 in similarity for forest layers at 250 m and decrease in similarity for open
-layers at 250 m. Note that lichen layer similarity is not shown because
-individuals did not interact in lichen habitats greater greater than 10 m
+layers at 250 m. Note that forage layer similarity is not shown because
+individuals did not interact in forage habitats greater greater than 10 m
 landcover resolution. D) Mean connective redundancy across individuals showed a
@@
 (e.g. open summer compared to open winter) showed a stabilizing layer similarity
-at 200 observations for forest and 300 observations for lichen and open. D) Mean
+at 200 observations for forest and 300 observations for forage and open habitats. D) Mean
 connective redundancy across individuals increased with increasing number of
@@
 (40 to 100 days in length increasing by 5 days in sequence), multilayer networks
-were constructed for each landcover class (forest, lichen and open) across two
+were constructed for each landcover class (forest, forage, and open) across two
 seasons (summer and winter) and four network metrics calculated. A) Mean graph
@@
 48 days from the original), multilayer networks were constructed for each
-landcover class (forest, lichen and ope) across two seasons (summer and winter)
+landcover class (forest, forage, and open) across two seasons (summer and winter)
 and four network metrics calculated. A) Mean graph strength across individuals

### 2020-02-10 paper/manuscript.Rmd
reflow hab class section

@@
 three categories: foraging habitat, open habitat, and forest habitat using the R
-package `raster` [@Hijmans_2019]. Foraging habitat <!-- TODO: "foraging" should
-be "lichen" ?--> consisted of lichen habitat, open habitat consisted of wetland,
-rocky barrens, and anthropogenic habitat types, while forest habitat consisted
-of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest
-habitat types. Water habitat was excluded from all subsequent analyses.
+package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
+open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
+types, while forest habitat consisted of coniferous forest, conifer scrub,
+broadleaf forest, and mixed-wood forest habitat types. Water habitat was
+excluded from all subsequent analyses.
 

### 2020-02-10 paper/manuscript.Rmd
caribou socioecology section

@@
 Here, we use caribou as a case study to develop scale-dependent multilayer
-networks based on social (visual and auditory perception), spatial (habitat
-type), and temporal (seasonal). Caribou are gregarious ungulates with
-fission-fusion dynamics [@Lesmerises_2018] that display temporal and spatial
-variation in social networks [@Peignier_2019]. In winter, caribou dig holes in
-the snow, termed craters, to access forage [@Bergerud_1974]. As a result,
-caribou tend to occupy and re-use craters once they are established and there is
-considerably less access to forage than when the landscape is snow-free.
-Importantly, craters exist on the landscape at multiple scales: the crater scale
-(a single crater), the feeding area scale (multiple craters in close proximity),
-and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
-heterogeneous, with greater access in snow-free seasons compared to winter as
-well as spatially heterogeneous in winter because the distribution of craters on
-the landscape varies meaning that access to vegetation in winter is highly
-variable for caribou. We therefore partitioned data into two discrete seasons:
-summer (3 August - 20 September) and winter (1 January – 17 February) based on
-caribou socioecology [@Peignier_2019].
+networks based on predicted social (visual and auditory perception), spatial
+(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
+with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
+spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
+holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
+is presumed to be a costly behaviour and as a result, caribou tend to occupy and
+re-use craters once they are established and there is considerably less access
+to forage than when the landscape is snow-free. Importantly, craters exist on
+the landscape at multiple scales: the crater scale (a single crater), the
+feeding area scale (multiple craters in close proximity), and the winter range
+scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
+of forage for caribou is therefore seasonally heterogeneous because the
+distribution of craters on the landscape varies meaning that access to
+vegetation in winter is highly variable for caribou. Caribou therefore have
+greater access to forage in snow-free seasons. We  partitioned data into two
+discrete seasons: summer (3 August - 20 September) and winter (1 January – 17
+February) based on caribou socioecology [@Peignier_2019].
 

### 2020-02-10 paper/manuscript.Rmd
caribou loc section

@@
 discrete removed all erroneous and outlier GPS fixes following
-[@BJ_RNERAAS_2010]. We did not collar all female caribou in the herd; however,
-we assumed that our sample of collared animals was random.
+[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all female
+caribou in the herd; however, the proportion of marked adult females was
+approximately 15% and we assumed these individuals were randomly distributed
+throughout the population.
 

### 2020-02-10 paper/manuscript.Rmd
conclusion edits

@@
 
-Silk et al. (2018) presented some key multilayer questions in animal behaviour
-research. While these questions represent an important starting point for
-multilayer networks, we present an additional set of questions relevant to the
-promise and problem of scale in mutlilayer networks:
+Silk et al. (2018) summarized some key multilayer questions in animal behaviour
+research. While these questions are important for linking animal behaviour and
+multilayer networks, we present an additional set of questions posed through the
+lense of spatial ecology and relevant to the promise and problem of scale in
+mutlilayer networks:
 
-1. How do social phenotypes across scales differently influence fitness? Are
+1. How do social phenotypes vary across social scales and differentially influence fitness? Are
 some temporal or social scales better predictors for different fitness metrics?
@@
 3. How, and why, does the spatial scale of perception influence, e.g. auditory,
-visual, or chemotaxis, influence the  social environment across scales? What is
+visual, or chemotaxis, influence the  social environment? What is
 the role of memory, and by extension social and spatial cognition, as animals

### 2020-02-10 paper/manuscript.Rmd
title
conclusion - 1st draft

@@
 ---
-title: The problem and promise of scale in animal social multilayer networks
+title: The problem and promise of scale in multilayer animal social networks
 author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 complex social systems? Second, can variation in the social, spatial, and
-temporal improve predictions associated with biological differences in seasonal
+temporal scale improve predictions associated with biological differences in seasonal
 resource availability and social association? We conclude with perspectives for
@@
 
-Silk et al. (2018) summarized some key multilayer questions in animal behaviour
-research. While these questions are important for linking animal behaviour and
-multilayer networks, we present an additional set of questions posed through the
-lense of spatial ecology and relevant to the promise and problem of scale in
-mutlilayer networks:
+With our caribou case stuyd, we show that (1) multilayer social networks can be,
+but are not always, scale dependent and (2) that the use of multilayer networks
+could be useful for identifying habitat or season-specific social processes. Our
+analyses of social, spatial, and temporal scales in multilayer network framework
+highlight potential to identify scales at which variation in properties of
+layers within a multilayer network show the most variability. Our analysis of
+caribou multilayer networks incorporated high resolution GPS telemetry data and
+spatial landcover data, thus allowing us ground our broader discussion of
+multilayer networks in the context of observed animal social networks.
+<!--QW: I am not very happy with this paragraph, but it's a start -->
 
-1. How do social phenotypes vary across social scales and differentially influence fitness? Are
-some temporal or social scales better predictors for different fitness metrics?
+Multilayer networks remain a nascent tool in animal behavioural ecology. We
+demonstrate novel analyses that vary social, spatial, and temporal scale within
+a multilayer framework and we discuss the potential integration of individual
+phenotypes and fitness, collective movememtn, and habitat selection for future
+analyses considering spatial ecology  using multilayer networks. Silk et al.
+(2018) summarized some key multilayer questions in animal behaviour research.
+While these questions are important for linking animal behaviour and multilayer
+networks, we summarize our perspectives on the future of multilayer networks
+with an additional set of questions posed through the lense of spatial ecology
+that are relevant to the promise and problem of scale in mutlilayer networks:
 
+1. How do social phenotypes vary across social scales and differentially
+influence fitness? Are some temporal or social scales better predictors for
+different fitness metrics?
 2. Why do individuals associate more strongly with certain conspecifics in some
@@
 networks?
-
 3. How, and why, does the spatial scale of perception influence, e.g. auditory,
-visual, or chemotaxis, influence the  social environment? What is
-the role of memory, and by extension social and spatial cognition, as animals
-navigate their environment and make decisions about where to move next?
+visual, or chemotaxis, influence the  social environment? What is the role of
+memory, and by extension social and spatial cognition, as animals navigate their
+environment and make decisions about where to move next?
 

### 2020-02-10 scripts/2-landcover-scale.R
lc is 30

@@ -47,12 +47,12 @@ group_times(
 var <- 'lcres'
 
 # Also include original raster
-lsres <- c(10, lsres)
+lsres <- c(30, lsres)
 lslc <- c(lc, lslc)
 splitBy <- 'season'
 
 nets <- lapply(lsres, function(res) {
-  col <- ifelse(res == 10, 'lc', paste0('lc', res))
+  col <- ifelse(res == 30, 'lc', paste0('lc', res))
   splitBy <- c(splitBy, col)
   
   sub <- na.omit(DT, cols = splitBy)

### 2020-02-10 paper/manuscript.Rmd
concl
lc is 30 in manuscript

@@
 Available landcover classification included nine habitat types at <!-- TODO:
-double check lc res--> 10 m resolution. We reclassified the landcover types into
+double check lc res--> 30 m resolution. We reclassified the landcover types into
 three categories: foraging habitat, open habitat, and forest habitat using the R
@@
 our landcover raster at varying scales relevant to caribou ecology. We
-aggregated the 10 m landcover raster using the R package `grainchanger`
+aggregated the 30 m landcover raster using the R package `grainchanger`
 [@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
 occurred using a modal moving window method using a circular window
-corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
+corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
 represents fine-scale decision making for caribou during foraging, while
@@
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-winter and summer forage because, at all landcover resolutions greater than 10 m
+winter and summer forage because, at all landcover resolutions greater than 30 m
 there were no individuals connected in the network layers. <!-- individuals
@@
 layers at 250 m. Note that forage layer similarity is not shown because
-individuals did not interact in forage habitats greater greater than 10 m
+individuals did not interact in forage habitats greater greater than 30 m
 landcover resolution. D) Mean connective redundancy across individuals showed a
@@
 
+In summary, blah blah
+
 # Acknowledgements

### 2020-02-11 paper/manuscript.Rmd
update renders, add section numbers

@@
   bookdown::pdf_document2:
-     number_sections: false
-  #bookdown::word_document2:
+     number_sections: true
+  # bookdown::word_document2:
   #   reference_docx: template.docx
@@
 # Scale in multilayer networks in practice: case study results and discussion
+<!-- TODO: Add intro/general to results? with mention figures are means of inds-->
 

### 2020-02-11 paper/manuscript.Rmd
add todo
reorg, edits social scale results

@@
 <!-- TODO: units of spatial scale? --> 
+<!-- TODO: citations? -->
 
@@
 scale increased; however, this relationship varied by habitat type and season.
-As social scale increased, connective redundancy increased rapidly when groups
-were formed up to approximately 100 m threshold, followed by a plateau and
-slight decrease at higher thresholds, presumably due to an increase in summer
-forest degree at ~500 m (Figure \@ref(fig:socres)d). Regardless of social scale,
-layer relevance did not change for any habitat types or seasons, which suggests
-habitat-by-season layers captured most, if not all, of the potential connections
-an individual would have across all networks (Figure \@ref(fig:socres)b).
-Finally, somewhat predictably, graph strength for winter networks increased up
-to ~100-200 m thresholds, followed by a plateau, while graph strength for summer
+As social scale increased, graph strength for winter networks increased to
+~100-200 m thresholds, followed by a plateau, while graph strength for summer
 networks did not change as the social threshold increased (Figure
-\@ref(fig:socres)a).  Taken together, these results suggest the optimal social
-scale at which groups should be assigned is likely somewhere between ~20-100 m
-based on the rate at which network metrics stabilized. For ungulates, groups are
-often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
-Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
-is likely an ideal social scale for generating social networks in caribou and
-similar species.
+\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
+50 m social thresholds, then did not change for any habitat types which suggests
+the winter habitat layers captured most, if not all, of the potential
+connections an individual would have across all networks (Figure
+\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
+rapidly when groups were formed up to approximately 100 m threshold, followed by
+a plateau and slight decrease at higher thresholds, presumably due to an
+increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
+together, these results suggest the optimal social scale at which groups should
+be assigned is likely somewhere between ~20-100 m based on the rate at which
+network metrics stabilized. For ungulates, groups are often assigned based on 50
+m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
+suggesting that given similar quantities of data, ~50 m is likely an ideal
+social scale for generating social networks in caribou and similar species.
 

### 2020-02-11 paper/manuscript.Rmd
fin results reorg

@@
 the winter habitat layers captured most, if not all, of the potential
-connections an individual would have across all networks (Figure
+connections an individual would have across these networks (Figure
 \@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
-rapidly when groups were formed up to approximately 100 m threshold, followed by
+rapidly when groups were formed up to ~100 m threshold, followed by
 a plateau and slight decrease at higher thresholds, presumably due to an
@@
 Increasing the scale of landcover resolution resulted in decreased proportion of
-rare and patchy habitats and low connectivity of individuals in these habitats.
+rare and patchy habitats, and low connectivity of individuals in these habitats.
 In winter, layer relevance was stable for open and forest habitats but decreased
-for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
-with increasing landcover resolution due the decrease in connectivity of
-individuals in winter forage habitats, resulting in a multilayer network where
-neighbours were less frequently repeated in multiple layers <!-- TODO: I'm
-having a hard time understanding this previous sentence -->
-(Figure\@ref(fig:lcres)d). Layer similarity was generally stable for forest and
-open habitats except for a contrasting increase in similarity for forest and
-decrease in similarity for open habitats at 250 m landcover resolution (Figure
-\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-winter and summer forage because, at all landcover resolutions greater than 30 m
-there were no individuals connected in the network layers. <!-- individuals
-still used forage but in much lower proportion + lowered opportunity to
-associate --> These results indicate the importance of matching landcover
-resolution to scale of selection as well as ensuring the landcover product used
-has a resolution fine enough to detect relevant landscape features and habitats.
-<!-- TODO: how? This isn't clear enough for me to follow yet -->
+for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
+stable for forest and open habitats except for a contrasting increase in
+similarity for forest and decrease in similarity for open habitats 250 m
+landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
+possible to calculate between winter and summer forage because, at all landcover
+resolutions greater than 30 m there were no individuals connected in the network
+layers. <!-- individuals still used forage but in much lower proportion +
+lowered opportunity to associate --> Connective redundancy decreased with
+increasing landcover resolution due the decrease in connectivity of individuals
+in winter forage habitats, resulting in a multilayer network where neighbours
+were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
+time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
+results indicate the importance of matching landcover resolution to scale of
+selection as well as ensuring the landcover product used has a resolution fine
+enough to detect relevant landscape features and habitats. <!-- TODO: how? This
+isn't clear enough for me to follow yet -->
 
@@
 stabilize with more observations -->
+
 As the number of observations used to generate multilayer networks increased,
@@
 observations necessary for sufficiently describing the social dynamics across
-contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it
+contexts.
+
+<!-- TODO: I'm not sure this is relevant since this is the main way it
 is already done, can we make this thought more relevant to picking scales or
@@
 window length -->
+
 Contrasting winter and summer seasons became more similar with increasing window
-length. Layer similarity between seasons increased consistently across landcover
-class (Figure \@ref(fig:winlen)b). Individual graph strength and layer relevance
-increased for all summer layers as individuals became more connected with
-increasing window lengths (Figure \@ref(fig:winlen)a, Figure
+length. Individual graph strength and layer relevance increased for all summer
+layers as individuals became more connected with increasing window lengths
+(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
+seasons increased consistently across landcover class (Figure
 \@ref(fig:winlen)b).  These results suggest that an increasing window length,
@@
 dissaggregation according to resource availability and presence of conspecifics.
-<!-- TODO: ?? --> <!-- TODO: end with something highlighting this shows it's
+
+<!-- TODO: end with something highlighting this shows it's
 important to properly define your season -->
+
 <!-- Similarly, shifting window position of the summer season resulted in an

### 2020-02-11 paper/manuscript.Rmd
rm old bullet results

@@
 <!-- TODO: Add intro/general to results? with mention figures are means of inds-->
+<!-- TODO: make sure we clarify these are means of all individuals? -->
+<!-- TODO: discuss layer similarity for social threshold -->
 
-<!-- TODO: make sure we clarify these are means of all individuals? -->
-
-<!-- TODO: discuss layer similarity for social threshold -->
 In general, individuals in multilayer networks became more connected as social
@@
 
-<!-- landcover resolution
-* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
-* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
-* decreasing winter lichen relevance because the degree + number of edges decreased
---> 
-<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
 Increasing the scale of landcover resolution resulted in decreased proportion of
@@
 isn't clear enough for me to follow yet -->
-
-<!-- nobs * common, though at different points - more observations until
-stabilizing * we dont see the stabilizing/full plateau for connective redundancy
-but appears to be coming.. * still some variability, especially for graph
-strength because individuals are differently connected but broad strokes - they
-stabilize with more observations -->
 
@@
 
-<!-- win  length * increasing window length = increasingly similar layers and
-increasingly redundant edges. more individuals have the opportunity to interact
-* increasing window length also leads to increasing similarity between seasons
-because seasons are less well defined/include more shoulder seasons * decreasing
-graph strength at the upper end of window length in winter showing again
-inclusion of more shoulder season * layers are more similarly relevant at high
-window length -->
-
 Contrasting winter and summer seasons became more similar with increasing window
@@
 
-<!-- Similarly, shifting window position of the summer season resulted in an
-increase in number of connections between individuals. Layer relevance  -->
-<!-- win position * increasing network connectivity in summer when the window
-position is moved - these seasons are more similar than the original window
-position * same theme shown in the connective redundancy * quite variable layer
-similarity, not sure what to pull out of that one * increased graph strength for
-winter down the middle, with generally increasing summer layers - again where
-the season is including more shoulder season potentially -->
-<!-- Shifting window position results showed increasing layer similarity  -->
 **Missing: discussion of window position..**

### 2020-02-11 paper/glossary.rmd
gloss
rm metric interpretations to glossay

@@
 
-**Spatial network**: Networks of locations, which be linked with social networks of animals that move between the locations (Silk et al. 2018.
+**Spatial network**: Networks of locations, which be linked with social networks of animals that move between the locations (Silk et al. 2018).
+
+<!--
+## Each metric's interpretation
+* Degree: the number of direct connections an individual has to other individuals in the network.
+High degree = connected to many indviduals in a single layer.
+Low degree = not connected to many individuals in a single layer.
+
+* Multidegree: sum of degree across layers. High multidegree = connected to many
+individuals across layers. Low multidegree = not connected to many individuals
+across layers.
+
+* Degree deviation: standard **[??]** deviation of degree across layers. High degree deviation =
+large difference between degree for an individual across layers. Low degree
+deviation = individuals are similarly connected across layers.
+
+* Graph strength: the sum of all the edge weights directly connected to an actor, sometimes called weigthed degree.
+High graph strength = highly social, connected to many individuals and/or having stronger, high-valued connections between individuals.
+Low graph strength = not very social, connected to few individuals and/or having weak, low-valued connections between individuals.
+Not summed in this case across layers.
+
+* Neighbours: number of unique individuals adjacent to each actor. Considered in
+a single layer, this is equal to the degree.
+
+* Neighbourhood: number of unique individuals across all layers. High
+neighbourhood = a high number of unique individuals connected to an actor. Low
+neighbourhood = a low number of unique individuals connected to an actor.
+
+* Relevance: layer centric metric, corresponding to the number of neighbours on a
+layer divided by the total neighbourhood for each actor. High relevance = the layer is highly relevant to the individuals connections. A low
+relevance means this layer does not contribute many neighbours to an individuals
+overall neighbourhood.
+
+* Connective redundancy: the total multilayer neighbourhood divided by the
+multidegree. High connective redundancy indicates a multilayer network that has
+many repeated edges across layers between an actor and its neighbours. Low
+connective redundancy indicates that each layer is important for preserving all
+social ties.
+
+* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
+correlation coefficient of degree vectors for each layer, comparing each
+landcover across seasons.
+
+-->
 

### 2020-02-11 paper/manuscript.Rmd
rm metric interpretations to glossay

@@
 **Missing: discussion of window position..**
-
-<!--
-## Each metric's interpretation
-* Degree: the number of direct connections an individual has to other individuals in the network.
-High degree = connected to many indviduals in a single layer.
-Low degree = not connected to many individuals in a single layer.
-
-* Multidegree: sum of degree across layers. High multidegree = connected to many
-individuals across layers. Low multidegree = not connected to many individuals
-across layers.
-
-* Degree deviation: standard **[??]** deviation of degree across layers. High degree deviation =
-large difference between degree for an individual across layers. Low degree
-deviation = individuals are similarly connected across layers.
-
-* Graph strength: the sum of all the edge weights directly connected to an actor, sometimes called weigthed degree.
-High graph strength = highly social, connected to many individuals and/or having stronger, high-valued connections between individuals.
-Low graph strength = not very social, connected to few individuals and/or having weak, low-valued connections between individuals.
-Not summed in this case across layers.
-
-* Neighbours: number of unique individuals adjacent to each actor. Considered in
-a single layer, this is equal to the degree.
-
-* Neighbourhood: number of unique individuals across all layers. High
-neighbourhood = a high number of unique individuals connected to an actor. Low
-neighbourhood = a low number of unique individuals connected to an actor.
-
-* Relevance: layer centric metric, corresponding to the number of neighbours on a
-layer divided by the total neighbourhood for each actor. High relevance = the layer is highly relevant to the individuals connections. A low
-relevance means this layer does not contribute many neighbours to an individuals
-overall neighbourhood.
-
-* Connective redundancy: the total multilayer neighbourhood divided by the
-multidegree. High connective redundancy indicates a multilayer network that has
-many repeated edges across layers between an actor and its neighbours. Low
-connective redundancy indicates that each layer is important for preserving all
-social ties.
-
-* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
-correlation coefficient of degree vectors for each layer, comparing each
-landcover across seasons.
-
--->
 

### 2020-02-11 paper/manuscript.Rmd
tidy, rm todos, fig caps

@@
 
-<!-- Figure 3: metrics by social scale -->
+<!-- Figure: metrics by social scale -->
 (ref:socres) Varying scale in social threshold. For each social threshold, multilayer
@@
 
-<!-- Figure 4: metrics by landcover resolution -->
+<!-- Figure: metrics by landcover resolution -->
 (ref:lcres) Variation in multilayer network metrics as a function of changes in
@@
 
-<!-- Figure 5: metrics by number of observations -->
+<!-- Figure: metrics by number of observations -->
 <!-- TODO: RO first sentence... -->
@@
 (e.g. open summer compared to open winter) showed a stabilizing layer similarity
-at 200 observations for forest and 300 observations for forage and open habitats. D) Mean
-connective redundancy across individuals increased with increasing number of
-observations, which begins to plateau around 100 observations. Note, data in
-panel C are truncated because there were few observations of individuals in
-foraging and open habitats during the winter, resulting in inability to
-calculate layer similarity at lower number of observations.
+at 200 observations for forest and 300 observations for forage and open
+habitats. D) Mean connective redundancy across individuals increased with
+increasing number of observations, which begins to plateau around 100
+observations. Note, data in panel C are truncated because there were few
+observations of individuals in foraging and open habitats during the winter,
+resulting in inability to calculate layer similarity at lower number of
+observations.
 
@@
 
+<!-- Figure: Window length -->
 (ref:winlen) Varying scale in time window length. For each time window length
@@
 lengths, though there was more variation in strength between landcover types as
-window length increased. <!--TODO:**[see if you agree with my changes. B-D were
-based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
-generally increased during the summer months but was relatively stable across
-time window lengths for each landcover layer. C) Similarity of landcover network
-layers between seasons (e.g. open summer compared to open winter) showed
-increasing similarity consistent across landcover layers with increasing window
-length. D) Mean connective redundancy across individuals varied dramatically
-depending on the length of the time window <!--TODO:**[JWT: previously this was
-describing fig. 3. I don't know if what I wrote best encapsulates what
-connnective redundancy does here. Length of time window seems to make connective
-redundancy highly variable as it changes.]**.-->
+window length increased. B) Mean layer relevance generally increased during the
+summer months but was relatively stable across time window lengths for each
+landcover layer. C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed increasing similarity consistent
+across landcover layers with increasing window length. D) Mean connective
+redundancy across individuals varied dramatically depending on the length of the
+time window.
 
@@
 
+<!-- Figure: Window position -->
 (ref:winpos) Varying scale in time window position. For each time window
@@
 48 days from the original), multilayer networks were constructed for each
-landcover class (forest, forage, and open) across two seasons (summer and winter)
-and four network metrics calculated. A) Mean graph strength across individuals
-increased in summer network layers at window position 25 and increased between
-window position 20 and 40 for winter network layers. B) Mean layer relevance
-slightly decreased for winter layers and increased for summer layers, showing
-decreasing connectivity in shifted winter time windows and greater connectivity
-in summer layers at later window positions. C) Similarity of landcover network
-layers between seasons (e.g. open summer compared to open winter) showed
-fluctuations in layer similarity across landcover types with shifted time
-windows. <!--TODO:**[JWT: previously describing window length, not position.
-Check that you're ok with my changes]**--> D) Mean connective redundancy across
-individuals increased between window position 12 through 48 due to increased
-connectivity in the summer network layers.
+landcover class (forest, forage, and open) across two seasons (summer and
+winter) and four network metrics calculated. A) Mean graph strength across
+individuals increased in summer network layers at window position 25 and
+increased between window position 20 and 40 for winter network layers. B) Mean
+layer relevance slightly decreased for winter layers and increased for summer
+layers, showing decreasing connectivity in shifted winter time windows and
+greater connectivity in summer layers at later window positions. C) Similarity
+of landcover network layers between seasons (e.g. open summer compared to open
+winter) showed fluctuations in layer similarity across landcover types with
+shifted time windows. D) Mean connective redundancy across individuals increased
+between window position 12 through 48 due to increased connectivity in the
+summer network layers.
 

### 2020-02-11 paper/manuscript.Rmd
temporal scale subsections

@@
 greater access to forage in snow-free seasons. We  partitioned data into two
-discrete seasons: summer (3 August - 20 September) and winter (1 January – 17
-February) based on caribou socioecology [@Peignier_2019].
+discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
+February 2018) based on caribou socioecology [@Peignier_2019].
 
@@
 ### Temporal scale
-<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
+#### Time window length and position
 We altered the temporal scale of multilayer networks by varying the length and
@@
 
+#### Number of observations
 Studies of social network analysis vary in the number and frequency of

### 2020-02-11 paper/manuscript.Rmd
incorporating case study indiv fitness perspective

@@
 and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Cater_2015; @Farine_2015a]. Furthermore, it is a
+question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
 common trope that individuals must be associating to interact, and many studies
 therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity in order to groom each other. However,
-animals have certain interactions that do not require proximity such as
-long-distance vocalization and olfactory signals [@Carter_2015] With the
-advancement of biologging technology, we have the ability to record social
-interactions that do not require proximity, particularly long-distance
-communication networks with devices like microphone arrays [Snijders_2017].
-These varying social scales can have different fitness repercussions for
-individuals. Rhesus macaques (*Macaca mulatta*) had higher survivorship when
-they had fewer but stronger, more stable social associates and grooming partners
-rather than simply more associates [Ellis_2019]. This finding highlights that
-different qualities of social scales have lasting consequences.
+instance, baboons need to be in proximity to groom each other. However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015] With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
+study results indicate that there are different social patterns in different
+habitat types, likely indicating different types of interactions. When the
+social threshold is greater than approximately 50 m during the summer **check**,
+individuals demonstrate dramatically different graph strength **cite spatial threshold fig** 
+in different habitat types, having dramatically higher graph
+strength in forage and open habitats than forest where they can likely see each
+other better and still interact with visual cues. Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) 
+had higher survivorship when they had fewer but stronger, more stable
+social associates and grooming partners rather than simply more associates
+[@Ellis_2019]. This finding highlights that different qualities of social scales
+have lasting consequences.
 
 Temporal scale is also important for understanding the repercussions of social
-phenotypes. For instance, social phenotypes can change over ontogeny in ways
-that can affect fitness [@Berger_2015, @Brent_2017]. Thus, it is critical to
-carefully consider the temporal scale that is meaningful for the proposed
-hypotheses. Further complicating the issue of selecting suitable time scales
-across ontogeny, individuals progress through development at different rates
-[@Tarka_2018]. This variation can make defining appropriate temporal scales for
-testing the fitness implications of an individual’s social phenotype over
-different stages of ontogeny even more difficult when they vary by individual.
-However, considering fine temporal scales provide insight across developmental
-stages that may otherwise be missed [@Turner_2018].
+phenotypes. Varying the time window length and position for caribou, we found
+there was a lot of variation in the multilayer network metrics **cite winpos and winlen**. 
+These changes in the outcome depending on how the time window is
+defined highlight how critical it is to properly define the time window
+appropriately to address the questions and hypotheses of interest. For instance,
+social phenotypes can change over ontogeny in ways that can affect fitness
+[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
+temporal scale that is meaningful for the proposed hypotheses. Further
+complicating the issue of selecting suitable time scales across ontogeny,
+individuals progress through development at different rates [@Tarka_2018]. This
+variation can make defining appropriate temporal scales for testing the fitness
+implications of an individual’s social phenotype over different stages of
+ontogeny even more difficult when they vary by individual. However, considering
+fine temporal scales provide insight across developmental stages that may
+otherwise be missed [@Turner_2018].
 
@@
 
-On the other hand, picking the proper temporal scale is important but a
-challenge because all layers in the multilayer network should reflect the same
-time period, and the period should be long enough for each layer to have enough
-data for robust networks [@Farine_2017]. These considerations may be limiting
-factors when answering questions that require timeframes that are relevant to
-different individuals, for instance. In both mono- and multilayer networks, the
-effect of scale on the relationship between an individual’s social network
-position and fitness need to be considered based on the hypotheses being tested
-and logistical constraints.
+Conversely, picking the proper temporal scale is important but a challenge
+because all layers in the multilayer network should reflect the same time
+period, and the period should be long enough for each layer to have enough data
+for robust networks [@Farine_2017]. These considerations may be limiting factors
+when answering questions that require timeframes that are relevant to different
+individuals, for instance. In both mono- and multilayer networks, the effect of
+scale on the relationship between an individual’s social network position and
+fitness need to be considered based on the hypotheses being tested and
+logistical constraints.
 

### 2020-02-11 paper/manuscript.Rmd
inc more mlnet indiv fitness perspective

@@
 Social network positions are frequently used to represent the social environment
-that an individual experiences or their social phenotype. Social phenotypes are
-increasingly linked to important fitness for individuals of various species,
-including primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
-@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both temporal, seasons
-and stages of life, and social scales, types of interactions, have emerged as
-important for understanding fitness consequences in the context of social
-network positions [@Almeling_2016, @Berger_2015, @Brent_2017, @Holekamp_2012].
-Multilayer networks provide a way to bridge these different scales so that we
-can examine social phenotypes in more holistic ways rather than looking at each
-scale separately as has traditionally been done.
+that an individual experiences or their social phenotype. Multilayer networks
+provide a way to bridge these different scales so that we can examine social
+phenotypes in more holistic ways rather than looking at each scale separately as
+has traditionally been done. From a monolayer network perspective, social
+phenotypes are increasingly linked to important fitness for individuals of
+various species, including primates [@Brent_2017; @Thompson_2019], dolphins
+[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
+social scales, types of interactions, and temporal, seasons and stages of life,
+have emerged as important for understanding fitness consequences in the context
+of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017,
+@Holekamp_2012].
 
@@
 individuals demonstrate dramatically different graph strength **cite spatial threshold fig**
-in different habitat types, having dramatically higher graph
-strength in forage and open habitats than forest where they can likely see each
-other better and still interact with visual cues. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) 
-had higher survivorship when they had fewer but stronger, more stable
+in different habitat types, having higher graph strength in
+forage and open habitats where they can likely see each other and still interact
+with visual cues than in forest habitats. Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca
+mulatta*) had higher survivorship when they had fewer but stronger, more stable
 social associates and grooming partners rather than simply more associates
 [@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences.
+have lasting consequences. Multilayer networks provide the opportunity to
+address these types of questions involving social scale with all the individual
+layers of interaction integrated in a holistic way.
 
@@
 fine temporal scales provide insight across developmental stages that may
-otherwise be missed [@Turner_2018].
+otherwise be missed [@Turner_2018]. Defining temporal scales is a challenge in
+multilayer networks just as in monolayer networks; however, multilayer networks
+provide metrics that enable researchers to look at similarities and differences
+in separate layers representing different stages of ontogeny, or seasons as in
+our case study, which can be difficult to detect.
 

### 2020-02-11 paper/manuscript.Rmd
indiv fitness perspective check season and fig refs

@@
 habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the summer **check**,
-individuals demonstrate dramatically different graph strength **cite spatial threshold fig**
+social threshold is greater than approximately 50 m during the winter,
+individuals demonstrate dramatically different graph strength (Figure \@ref(fig:socres))
 in different habitat types, having higher graph strength in
@@
 phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics **cite winpos and winlen**. 
+there was a lot of variation in the multilayer network metrics (Figure \@ref(fig:winlen), Figure \@ref(fig:winpos)). 
 These changes in the outcome depending on how the time window is

### 2020-02-11 paper/manuscript.Rmd
work paragraph 1 habitat selection

@@
 ## Habitat selection and space use
-<!--
-* Social structure is influenced by large scale processes such as resource availability and seasonality [@Peigner_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
-* Habitat selection definition
-* johnson's four scales of selection and Mayor 2009 habitat selection across scales
-* habitat selection influences social structure since resource availability + quality influence home range size and overlap
-* individuals must share space to interact [@Farine_2015]
-* multilayer networks represent a novel framework for considering habitat selection and space use on sociality across scales
+Animals use space for resource, considering conspecifics
 
-individual differences in habitat selection
--->
+social structure is influenced by resources
 
-Social structure influenced by large scale processes, eg resources
-Animals select for these same processes, habitat selection, as measured by RSF
-All of these processes are influenced by scale: 
-RSFs are are influenced
-Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered
-sociality across scales of sociality + temporal and spatial as shown above
-ML networks present a framework for this
+animals selectively use resources + can be measured by RSFs
 
+<!-- Social structure influenced by large scale processes, eg resources -->
+<!-- Animals select for these same processes, habitat selection, as measured by RSF -->
+<!-- All of these processes are influenced by scale:  -->
+<!-- RSFs are are influenced -->
+<!-- Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered -->
+<!-- sociality across scales of sociality + temporal and spatial as shown above -->
+<!-- ML networks present a framework for this -->
+
+<!-- TODO: Gerard ‘openness’ paper -->
 Social structure is influenced by large scale processes such as resource
 availability and seasonality [@Peigner_2019], configuration [@He_2019] and
-fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
-available" [@Mayor_2009] landscape resources or features by animals. Combined, habitat selection and social structure are intimately linked as
-individuals must share space to interact [@Farine_2015] and resource
-availability and quality influence home range size and overlap. Johnson
+fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
+available resources or features by animals [@Manly_1993; @Boyce_1999]. Combined,
+social structure and habitat selection are intimately linked as individuals must
+share space to interact and distribution of resources influence home range size
+and group dynamics [@Webber_2018]. <!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
+
+Johnson
 (1980) identified four orders of habitat selection: (1) the geographical range
@@
 within the home range and (4) specific resources within a habitat patch.
- Multilayer
-networks represent a novel framework for considering the influence of habitat
-selection and space use on sociality across scales.
 
@@
 
-With our caribou case stuyd, we show that (1) multilayer social networks can be,
-but are not always, scale dependent and (2) that the use of multilayer networks
+Multilayer networks remain a nascent but powerful tool in animal behavioural ecology. We
+demonstrate novel analyses that vary social, spatial, and temporal scale within
+a multilayer framework. In our caribou case study, we show that (1) multilayer social networks can be,
+but are not always, scale dependent, and (2) the use of multilayer networks
 could be useful for identifying habitat or season-specific social processes. Our
 analyses of social, spatial, and temporal scales in multilayer network framework
-highlight potential to identify scales at which variation in properties of
-layers within a multilayer network show the most variability. Our analysis of
-caribou multilayer networks incorporated high resolution GPS telemetry data and
-spatial landcover data, thus allowing us ground our broader discussion of
-multilayer networks in the context of observed animal social networks.
+highlight potential to identify scales at which different properties of
+layers within a multilayer network show the most variability.
+Furthermore, we discuss the potential integration of individual phenotypes and fitness, collective movement, and habitat selection for future
+analyses considering spatial ecology  using multilayer networks.
+
 <!--QW: I am not very happy with this paragraph, but it's a start -->
+Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement.
+Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
+spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
 
-Multilayer networks remain a nascent tool in animal behavioural ecology. We
-demonstrate novel analyses that vary social, spatial, and temporal scale within
-a multilayer framework and we discuss the potential integration of individual
-phenotypes and fitness, collective movememtn, and habitat selection for future
-analyses considering spatial ecology  using multilayer networks. Silk et al.
-(2018) summarized some key multilayer questions in animal behaviour research.
+Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
 While these questions are important for linking animal behaviour and multilayer

### 2020-02-11 paper/manuscript.Rmd
messing with conclusion arrangement

--- 2020-02-11 paper/manuscript.Rmd
@@
 
-With our caribou case stuyd, we show that (1) multilayer social networks can be,
-but are not always, scale dependent and (2) that the use of multilayer networks
+Multilayer networks remain a nascent but powerful tool in animal behavioural ecology. We
+demonstrate novel analyses that vary social, spatial, and temporal scale within
+a multilayer framework. In our caribou case study, we show that (1) multilayer social networks can be,
+but are not always, scale dependent, and (2) the use of multilayer networks
 could be useful for identifying habitat or season-specific social processes. Our
 analyses of social, spatial, and temporal scales in multilayer network framework
-highlight potential to identify scales at which variation in properties of
-layers within a multilayer network show the most variability. Our analysis of
-caribou multilayer networks incorporated high resolution GPS telemetry data and
-spatial landcover data, thus allowing us ground our broader discussion of
-multilayer networks in the context of observed animal social networks.
+highlight potential to identify scales at which different properties of
+layers within a multilayer network show the most variability.
+Furthermore, we discuss the potential integration of individual phenotypes and fitness, collective movement, and habitat selection for future
+analyses considering spatial ecology  using multilayer networks.
+
 <!--QW: I am not very happy with this paragraph, but it's a start -->
 
-Multilayer networks remain a nascent tool in animal behavioural ecology. We
-demonstrate novel analyses that vary social, spatial, and temporal scale within
-a multilayer framework and we discuss the potential integration of individual
-phenotypes and fitness, collective movememtn, and habitat selection for future
-analyses considering spatial ecology  using multilayer networks. Silk et al.
-(2018) summarized some key multilayer questions in animal behaviour research.
+Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
+spatial landcover data, thus allowing us to ground our broader discussion of
+multilayer networks in the context of observed animal social networks.
+
+Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
 While these questions are important for linking animal behaviour and multilayer

### 2020-02-11 paper/manuscript.Rmd
more hab selection

--- 2020-02-11 paper/manuscript.Rmd
@@
 fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
-available resources or features by animals [@Manly_1993; @Boyce_1999]. Combined,
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999]. Combined,
 social structure and habitat selection are intimately linked as individuals must
-share space to interact and distribution of resources influence home range size
-and group dynamics [@Webber_2018]. <!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
+share space to interact and the distribution of resources influences home range size
+and group dynamics [@Webber_2018].
+
+Habitat selection is a scale-sensitive process
+Animals select habitats at multiple scales
+
+<!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
 

### 2020-02-11 paper/manuscript.Rmd
saving Conc while I pause

--- 2020-02-11 paper/manuscript.Rmd
@@
 <!--QW: I am not very happy with this paragraph, but it's a start -->
-
+Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement.
 Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
-spatial landcover data, thus allowing us to ground our broader discussion of
-multilayer networks in the context of observed animal social networks.
+spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
 

### 2020-02-11 paper/manuscript.Rmd
tidy + setup hab sel

--- 2020-02-11 paper/manuscript.Rmd
@@
 ## Habitat selection and space use
-Animals use space for resource, considering conspecifics
-
-social structure is influenced by resources
-
-animals selectively use resources + can be measured by RSFs
-
-<!-- Social structure influenced by large scale processes, eg resources -->
-<!-- Animals select for these same processes, habitat selection, as measured by RSF -->
-<!-- All of these processes are influenced by scale:  -->
-<!-- RSFs are are influenced -->
-<!-- Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered -->
-<!-- sociality across scales of sociality + temporal and spatial as shown above -->
-<!-- ML networks present a framework for this -->
-
 <!-- TODO: Gerard ‘openness’ paper -->
@@
 fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999]. Combined,
-social structure and habitat selection are intimately linked as individuals must
-share space to interact and the distribution of resources influences home range size
-and group dynamics [@Webber_2018].
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999].
+Combined, social structure and habitat selection are intimately linked as
+individuals must share space to interact and the distribution of resources
+influences home range size and group dynamics [@Webber_2018]. Animals select
+habitats are multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
+networks represent a novel framework for considering the influence of habitat
+selection and space use on sociality across scales.
 
-Habitat selection is a scale-sensitive process
-Animals select habitats at multiple scales
+<!-- Relationship between sociality and habitat -->
+<!-- more from Webber, He, etc -->
+<!-- Merkle’s memory and patches for bison (and leaders) -->
+<!-- Emergent  Properties  of  Conspecific  Attraction  inFragmented  Landscapes-->
+<!-- Conspecific Attraction and Aggregation in Territorial Species-->
+<!-- Energy and the Scaling of Animal Space Use-->
 
-<!-- Mayor scale --> Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
-
-Johnson
-(1980) identified four orders of habitat selection: (1) the geographical range
-of a species, (2) the home range of an individual, (3) the habitat patches
-within the home range and (4) specific resources within a habitat patch.
-
-<!--
-* multilayer networks are new but folks have looked at habitat selection + sociality
-  * Fortin
-  * Banks
-  * McLoughlin
-
-* none use a multilayer framework to explicitly combine
+<!-- The relationship between sociality has been discussed both theoretically  -->
+<!-- and tested explicitly ... CAH, etc then Fortin, McLouglin-->
+<!-- https://www.pnas.org/content/pnas/105/49/19114.full.pdf
+https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2600907/pdf/rspb20071688.pdf
 -->
@@
 multilayer approach*.
+
+Habitat selection - can be measured by RSFs and importance of scale:
+
+*  Johnson (1980) identified four orders of habitat selection: (1) the geographical range of a species, (2) the home range of an individual, (3) the habitat patches within the home range and (4) specific resources within a habitat patch.
+
+What new insights will multilayer networks lead to
 
@@
 -->
+
 Scale in habitat selection... Mayor (2019)

### 2020-02-11 paper/manuscript.Rmd
getting thoughts down and reflowing conc

@@
 
-Multilayer networks remain a nascent but powerful tool in animal behavioural ecology. We
-demonstrate novel analyses that vary social, spatial, and temporal scale within
-a multilayer framework. In our caribou case study, we show that (1) multilayer social networks can be,
-but are not always, scale dependent, and (2) the use of multilayer networks
-could be useful for identifying habitat or season-specific social processes. Our
-analyses of social, spatial, and temporal scales in multilayer network framework
-highlight potential to identify scales at which different properties of
-layers within a multilayer network show the most variability.
-Furthermore, we discuss the potential integration of individual phenotypes and fitness, collective movement, and habitat selection for future
+Multilayer networks remain a nascent but powerful tool in animal behavioural
+ecology. We demonstrate novel analyses that vary social, spatial, and temporal
+scale within a multilayer framework. In our caribou case study, we show that (1)
+multilayer social networks can be, but are not always, scale dependent, and (2)
+the use of multilayer networks could be useful for identifying habitat or
+season-specific social processes. Our analyses of social, spatial, and temporal
+scales in multilayer network framework highlight potential to identify scales at
+which different properties of layers within a multilayer network show the most
+variability. Furthermore, we discuss the potential integration of individual
+phenotypes and fitness, collective movement, and habitat selection for future
 analyses considering spatial ecology  using multilayer networks.
@@
 spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
+<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
+It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data.
+-->
 

### 2020-02-11 paper/manuscript.Rmd
conc edits

@@
 
-<!--QW: I am not very happy with this paragraph, but it's a start -->
-Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement.
-Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
-spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
+<!-- Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->
+
+Multilayer networks are complicated in that they can incorporate data as varied
+as social interactions, landscape features, and seasons, all of which exist at
+different scales and units of measurement. Our analysis of caribou multilayer
+networks incorporated high resolution GPS telemetry data and spatial landcover
+data is grounded in the context of observed animal social networks, as the
+scales we chose to explore (e.g., number of observations, sociality across space
+and time) are ones that can be observed as has traditionally been done. Thus, we
+highlight ways in which scale ought to be considered for both observed and
+remotely-sensed data when building social networks. Furthermore, GPS telemetry
+data provides a link between large scale landscape properties and fine scale
+social interactions as animal movement occurs across the landscape, and when
+taken into account with multiple individuals can indicate association patterns.
+Thus, a layer incorporating relocation data could be a great boon linking
+spatial and social layer in multilayer networks.
 <!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
@@
 networks, we summarize our perspectives on the future of multilayer networks
-with an additional set of questions posed through the lense of spatial ecology
+with an additional set of questions posed through the lens of spatial ecology
 that are relevant to the promise and problem of scale in mutlilayer networks:
 
-1. How do social phenotypes vary across social scales and differentially
-influence fitness? Are some temporal or social scales better predictors for
+1. How do social phenotypes vary across social, temporal, and spatial scales and
+differentially influence fitness? Are some scales better predictors for
 different fitness metrics?
@@
 
-In summary, blah blah
+<!-- In summary, blah blah  -->
 

### 2020-02-11 paper/manuscript.Rmd
trying to fix citations, some aren't working right

@@
 have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016, @Berger_2015, @Brent_2017,
-@Holekamp_2012].
+of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011].
 
@@
 social phenotypes can change over ontogeny in ways that can affect fitness
-[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
+[@Berger_2015; @Brent_2017]. Thus, it is critical to carefully consider the
 temporal scale that is meaningful for the proposed hypotheses. Further
@@
 fine temporal scales provide insight across developmental stages that may
-otherwise be missed [@Turner_2018]. Defining temporal scales is a challenge in
+otherwise be missed [@Turner_2017]. Defining temporal scales is a challenge in
 multilayer networks just as in monolayer networks; however, multilayer networks
@@
 especially over time, it is hard to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017, @Proskurnikov_2017]. Using the framework of
+suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
 multilayer networks, making layers of different temporal periods provides a way

### 2020-02-11 paper/citations.R

@@ -136,7 +136,7 @@ citep('10.1098/rspb.2012.1701')
 citep('10.1016/j.cub.2016.04.066')
 
 # berger 2015
-citep('10.1111/j.1365-2656.2007.01351.x')
+citep('10.1098/rspb.2015.1167')
 
 # holekamp 2012
 citep('10.1111/j.1365-294X.2011.05240.x')

### 2020-02-12 paper/manuscript.Rmd
hab sel start conclusion

@@
 
+Multilayer networks can be combined to consider habitat selection, across scales
+
+Animal social systems can be parsed by spatial contexts, defined by habitat types or connectivity, each represented in a layer within a multilayer framework
+Seasonality of resources can be directly measured by investigating differences in habitat selection and sociality between seasonal layers
+
+Taken together, these novel and explicit integrations of habitat selection and space use in multilayer netwokr
+
 # Conclusions

### 2020-02-12 paper/manuscript.Rmd
hab sel fst para

@@
 fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999].
+available resources resources or features by animals [@Manly_1993; @Boyce_1999].
 Combined, social structure and habitat selection are intimately linked as
 individuals must share space to interact and the distribution of resources
-influences home range size and group dynamics [@Webber_2018]. Animals select
-habitats are multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
+influences group dynamics and home range size [@Webber_2018]. Animals select
+habitats at multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
 networks represent a novel framework for considering the influence of habitat

### 2020-02-12 paper/manuscript.Rmd
hab sel fst scale para

@@
 
+Habitat selection depends on the scale at which it is measured and a singular
+scale is insufficient for generalizing across scales. Habitat selection is often
+measured using resource selection functions (RSFs) and species distribution
+models (SDMs). Both of these methods are based on the proportion of used
+resources and available resources for an animal. Johnson (1980) identified four
+orders of habitat selection: (1) the geographical range of a species, (2) the
+home range of an individual, (3) the habitat patches within the home range and
+(4) specific resources within a habitat patch. Extending beyond this
+hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and
+
 Habitat selection - can be measured by RSFs and importance of scale: 
+Scale in habitat selection... Mayor (2019)
 
-*  Johnson (1980) identified four orders of habitat selection: (1) the geographical range of a species, (2) the home range of an individual, (3) the habitat patches within the home range and (4) specific resources within a habitat patch.
+Habitat selection is scale dependent and 
+*  Johnson (1980)
 

### 2020-02-12 paper/manuscript.Rmd
rm, mv comments

@@
 
+<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
+should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
+MRSF Laforge paper 
+van Beest et al. 2014 scale paper 
+Habitat–performance relationships: finding the right metric at a given spatial scale
+Multi-scale habitat selection modeling: a review and outlook
+-->
 Habitat selection depends on the scale at which it is measured and a singular
@@
 hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and
-
-Habitat selection - can be measured by RSFs and importance of scale: 
-Scale in habitat selection... Mayor (2019)
-
-Habitat selection is scale dependent and 
-*  Johnson (1980)
-
-What new insights will multilayer networks lead to
-
-<!--
-
-Scale + habitat selection and space use
-types of scale to consider in these types of ML nets
-
-McGarigal 2016 organisms select habitat at multiple scales, temporal spatial 
-should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
-
-Johnson 1980 1st order = selection of the physical or geographical range of a species
-2nd order = selection of a home range of an individual or social group
-3rd order = selection of various habitat patches within the home range 
-4th order = selection of specific resources within a habitat patch
-
-* Mayor et al. 2009 paper 
-* MRSF Laforge paper 
-* van Beest et al. 2014 scale paper 
-* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
-* Multi-scale habitat selection modeling: a review and outlook
--->
-
-Scale in habitat selection... Mayor (2019)
 

### 2020-02-12 paper/manuscript.Rmd
reorg hab sel fst para

@@
 <!-- TODO: Gerard ‘openness’ paper -->
-Social structure is influenced by large scale processes such as resource
-availability and seasonality [@Peigner_2019], configuration [@He_2019] and
-fragmentation [@Banks_2007]. Habitat selection is the disproportionate use of
-available resources resources or features by animals [@Manly_1993; @Boyce_1999].
+Social structure is influenced by resource
+availability and seasonality [@Peignier_2019], configuration [@He_2019] and
+fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999], is a scale dependent process [@Mayor_2009].
 Combined, social structure and habitat selection are intimately linked as
 individuals must share space to interact and the distribution of resources
-influences group dynamics and home range size [@Webber_2018]. Animals select
-habitats at multiple scales ... (Mayor) <!-- Mayor scale --> Multilayer
+influences group dynamics and home range size [@Webber_2018]. <!--Animals select
+habitats at multiple scales ... (Mayor)  Mayor scale --> Multilayer
 networks represent a novel framework for considering the influence of habitat

### 2020-02-12 paper/manuscript.Rmd
hab sel scale

@@
 
+The link between habitat and sociality has been
+
 Despite not in a multilayer network context, the link between habitat and
@@
 should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
+
+Mayor 2007 - scale paper
 MRSF Laforge paper 
@@
 Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales. Habitat selection is often
-measured using resource selection functions (RSFs) and species distribution
-models (SDMs). Both of these methods are based on the proportion of used
-resources and available resources for an animal. Johnson (1980) identified four
-orders of habitat selection: (1) the geographical range of a species, (2) the
-home range of an individual, (3) the habitat patches within the home range and
-(4) specific resources within a habitat patch. Extending beyond this
-hierarchical perspective, Mayor (2009) reviewed scale in habitat selection and
+scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
+selection is measured using resource selection functions (RSFs), based on the
+proportion of used and available resources for an animal [@Manly_1993;
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, (3)
+the habitat patches within the home range and (4) specific resources within a
+habitat patch. Moving past this hierarchical perspective, Mayor (2009)
+reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection.
+For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.
 
@@
 -->
+
+conversely, one might envision generating a multilayer network where
+nodes are individual patches
+selection,
+similarity, 
+connectivity
+
 How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks

### 2020-02-12 paper/manuscript.Rmd
reln between social and hab para

@@
 <!-- TODO: Gerard ‘openness’ paper -->
-Social structure is influenced by resource
-availability and seasonality [@Peignier_2019], configuration [@He_2019] and
-fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999], is a scale dependent process [@Mayor_2009].
-Combined, social structure and habitat selection are intimately linked as
-individuals must share space to interact and the distribution of resources
-influences group dynamics and home range size [@Webber_2018]. <!--Animals select
-habitats at multiple scales ... (Mayor)  Mayor scale --> Multilayer
-networks represent a novel framework for considering the influence of habitat
-selection and space use on sociality across scales.
+Social structure is influenced by resource availability and seasonality
+[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
+Habitat selection, the disproportionate use of available resources or landscape
+features by animals [@Manly_1993; @Boyce_1999], is a scale dependent process
+[@Mayor_2009]. Combined, social structure and habitat selection are intimately
+linked as individuals must share space to interact and the distribution of
+resources influences group dynamics and home range size [@Webber_2018].
+<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
+Multilayer networks represent a novel framework for considering the influence of
+habitat selection and space use on sociality across scales.
 
@@
 
-The link between habitat and sociality has been
-
-Despite not in a multilayer network context, the link between habitat and
-sociality has been previously investigated. Fortin et al. (2009) evaluated
-habitat selection and group formation and division in bison. They observed
-contrasting group sizes in meadows and forests as well as identified predation
-risk avoidance as a main factor in their habitat selection [@Fortin_2009]. A
-review of the influence of habitat fragmentation on sociality noted decreased
-group size in small patches compared to large, continuous landscapes
-[@Banks_2007]. Finally, McLoughlin (2000) showed variable responses in brown
-bears (*Ursus arctos*) to seasonality, a proxy in this case for habitat quality,
-showing high home range overlap in areas of low and high seasonality and low
-home range overlap in areas of moderate seasonality. Despite these, *missing
-multilayer approach*.
+The emergent relationship between habitat and sociality has been explored by the
+distribution and phenology of resources and use of social information. Cougars
+had increased home range overlap in regions with high hunting opportunity, a
+proxy for resource richness [@Elbroch_2016]. Caribou showed seasonal differences
+in sociality, where social associations were high in winter and contrastingly
+low in summer when resource availability is homogenous [@Peigner_2019]. Bison
+(*Bison bison*) showed stronger habitat selection when group size was larger and
+avoidance of predation risk was a main factor contributing to their habitat
+selection [@Fortin_2009]. <!--Despite these, *missing multilayer approach*.-->
 

### 2020-02-12 paper/manuscript.Rmd
blah

@@
 
+<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
+should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
+
+Mayor 2007 - scale paper
+MRSF Laforge paper 
+van Beest et al. 2014 scale paper 
+Habitat–performance relationships: finding the right metric at a given spatial scale
+Multi-scale habitat selection modeling: a review and outlook
+-->
+
+<!-- TODO: point to figure 1 -->
+Habitat selection depends on the scale at which it is measured and a singular
+scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
+selection is measured using resource selection functions (RSFs), based on the
+proportion of used and available resources for an animal [@Manly_1993;
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, (3)
+the habitat patches within the home range and (4) specific resources within a
+habitat patch. Moving past this hierarchical perspective, Mayor (2009)
+reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection.
+For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.
+
 <!-- Relationship between sociality and habitat -->
@@
 avoidance of predation risk was a main factor contributing to their habitat
-selection [@Fortin_2009]. <!--Despite these, *missing multilayer approach*.-->
-
-<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
-should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
-
-Mayor 2007 - scale paper
-MRSF Laforge paper 
-van Beest et al. 2014 scale paper 
-Habitat–performance relationships: finding the right metric at a given spatial scale
-Multi-scale habitat selection modeling: a review and outlook
--->
-Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
-selection is measured using resource selection functions (RSFs), based on the
-proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, (3)
-the habitat patches within the home range and (4) specific resources within a
-habitat patch. Moving past this hierarchical perspective, Mayor (2009)
-reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection.
-For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.
+selection [@Fortin_2009]. These examples are implicitly multilayered, comparing sociality across contexts of seasonality or spatial context. <!--Despite these, *missing multilayer approach*.-->
 
@@
 how to combine moving forward
-multilayer networks across landcover types
 in areas of high selection/low selection or favorable/unfavorable habitat
@@
 
-conversely, one might envision generating a multilayer network where
-nodes are individual patches
-selection,
-similarity, 
-connectivity
-
-How to combine moving forward: habitat selection, space use, multiple scales, multilayer networks
-Sociality across scales eg home range overlap and interactions
-Layers defined by habitat/landcover
-
-Multilayer networks can be combined to consider habitat selection, across scales
-
-Animal social systems can be parsed by spatial contexts, defined by habitat types or connectivity, each represented in a layer within a multilayer framework
-Seasonality of resources can be directly measured by investigating differences in habitat selection and sociality between seasonal layers
-
-Taken together, these novel and explicit integrations of habitat selection and space use in multilayer netwokr
+Multilayer networks can be used to explicitly consider habitat selection and sociality across scales.
+Animal social systems can be parsed by spatial contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
+The influence of resource phenology can be directly measured by differences in habitat selection and sociality across temporal layers.
+Habitat selection can be explicitly integrated using network layers defined by similarity of selection coefficients between individuals.
+These explicit integrations of habitat selection and sociality across social, spatial and temporal scales highlight the potential for novel insights from multilayer networks.
 

### 2020-02-12 paper/manuscript.Rmd
skip cites for now, leave keys throughout

@@
   #   reference_docx: template.docx
-bibliography: ../references/knitcite.bib
+# bibliography: ../references/knitcite.bib
 ---

### 2020-02-12 paper/manuscript.Rmd
double coarser?

@@
 environment, home range overlap is a relatively coarse scale of sociality across
-which individuals share space over coarser spatial and temporal scales [e.g.
-@Piza_Roca_2018]. Although the social environment clearly scales spatially and
+which individuals share space over larger spatial and temporal scales [e.g.
+@Piza_Roca_2018]. <!-- what is going on here -->Although the social environment clearly scales spatially and
 temporally, it remains unclear whether coarser scales of sociality, including

### 2020-02-12 paper/manuscript.Rmd
rm potential

@@
 network analysis [@Webber_2019], it typically considers a single scale of
-sociality in a given network (monolayer), drastically simplifying the potential
+sociality in a given network (monolayer), drastically simplifying the
 complexity of animal social systems [@Finn_2019].

### 2020-02-12 paper/manuscript.Rmd
add laforge

@@
 Further, for social interactions or associations to occur individuals must share
-space, and thus have overlapping home ranges. In the context of the social
+space, and thus have overlapping home ranges [@Laforge_2014]. In the context of the social
 environment, home range overlap is a relatively coarse scale of sociality across
 which individuals share space over larger spatial and temporal scales [e.g.
-@Piza_Roca_2018]. <!-- what is going on here -->Although the social environment clearly scales spatially and
+@Piza_Roca_2018]. <!-- double coarse -->Although the social environment clearly scales spatially and
 temporally, it remains unclear whether coarser scales of sociality, including

### 2020-02-12 paper/manuscript.Rmd
fix cite laforge
reflow intro
edit double coarse

--- 2020-02-12 paper/manuscript.Rmd
@@
 Further, for social interactions or associations to occur individuals must share
-space, and thus have overlapping home ranges. In the context of the social
-environment, home range overlap is a relatively coarse scale of sociality across
-which individuals share space over larger spatial and temporal scales [e.g.
-@Piza_Roca_2018]. <!-- what is going on here -->Although the social environment clearly scales spatially and
-temporally, it remains unclear whether coarser scales of sociality, including
-social association and home range overlap, vary predictably with social
-interaction [@Castles_2014; @Farine_2015a]. Thus, we define social scale as the
-type of social relationship observed that can be explicitly defined and measured
-[@Farine_2015a]. <!-- Farine references comes out as D.R. Farine 2015 -->
+space, and thus have overlapping home ranges [@VanderWal_2014]. In the context
+of the social environment, home range overlap is an example of how animals share
+space over coarser spatial and temporal scales (e.g. Piza-Roca et al. 2018).
+Although the social environment clearly scales spatially and temporally, it
+remains unclear whether coarser scales of sociality, including social
+association and home range overlap, vary predictably with social interaction
+[@Castles_2014;
+@Farine_2015a]. Thus, we define social scale as the type of social relationship
+observed that can be explicitly defined and measured [@Farine_2015a]. <!--
+Farine references comes out as D.R. Farine 2015 -->
 
@@
 complex social systems? Second, can variation in the social, spatial, and
-temporal scale improve predictions associated with biological differences in seasonal
-resource availability and social association? We conclude with perspectives for
-further development and application of scale in multilayer networks with respect
-to phenotypes and individual fitness [@Webber_2018], movement ecology and
-collective movement [@Jolles_2019], and habitat selection and space use. <!--
-TODO: (REF)--> <!-- TODO: Webber reference should be 2018, but defaulting to
-2017-->
+temporal scale improve predictions associated with biological differences in
+seasonal resource availability and social association? We conclude with
+perspectives for further development and application of scale in multilayer
+networks with respect to phenotypes and individual fitness [@Webber_2018],
+movement ecology and collective movement [@Jolles_2019], and habitat selection
+and space use. <!-- TODO: (REF)--> <!-- TODO: Webber reference should be 2018,
+but defaulting to 2017-->
 

### 2020-02-12 paper/manuscript.Rmd
add todo hance lc cite

@@
 ## Landscape data and habitat classification
+<!-- TODO: update citation for lc product from Hance -->
 Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
-Available landcover classification included nine habitat types at <!-- TODO:
-double check lc res--> 30 m resolution. We reclassified the landcover types into
-three categories: foraging habitat, open habitat, and forest habitat using the R
-package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
-open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
-types, while forest habitat consisted of coniferous forest, conifer scrub,
-broadleaf forest, and mixed-wood forest habitat types. Water habitat was
-excluded from all subsequent analyses.
+Available landcover classification included nine habitat types at 30 m
+resolution. We reclassified the landcover types into three categories: foraging
+habitat, open habitat, and forest habitat using the R package `raster`
+[@Hijmans_2019]. Foraging habitat consisted of lichen habitat, open habitat
+consisted of wetland, rocky barrens, and anthropogenic habitat types, while
+forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
+and mixed-wood forest habitat types. Water habitat was excluded from all
+subsequent analyses.
 

### 2020-02-12 paper/manuscript.Rmd
fst fig2 + quick cap

@@
 another at any given time point.
+
+<!-- TODO: work this cap -->
+(ref:ml) Visualization of multilayer network for social ungulate case study.
+Six layers are presented with individuals shown as nodes, fixed in space across layers.
+Layer represent combinations of two seasons (winter and summer) and three landcover class (open, forest and forage).
+Edges connect individuals that associated according to spatial and temporal thresholds described above.
+
+```{r ml, fig.cap='(ref:ml)'}
+knitr::include_graphics('../graphics/figure-2.png')
+```
 

### 2020-02-12 paper/manuscript.Rmd
add todo
edits nobs

@@
 We altered the social scale based on visual (short distance) and auditory (long
-distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we
+distance) sensory modalities of caribou<!-- TODO: REF? / see EVW comment-->. Specifically, we
 modified the spatial distance threshold required for group assignment using
@@
 observations as well as the data collection technique used to generate networks
-[@Davis_2018; @Webber_2019]. In addition to altering the temporal scale by
-adjusting the time window, we investigated the influence of the number of
-observations on resulting multilayer networks. We randomly selected 500
-timesteps and iteratively included 25 additional observations, regenerating the
-multilayer network and calculating associations of individuals. Subsequent
-iterations included the previous set of observations to mimic observational
-data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
+[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
+fixed rate (eg every $x$ minutes or hours) continuously throughout the study
+period. We investigated the influence of the number of observations on resulting
+multilayer networks. We randomly selected 500 timesteps and iteratively included
+25 additional observations, regenerating the multilayer network and calculating
+associations of individuals. Subsequent iterations included the previous set of
+observations to mimic collection of observational data. <!-- TODO: bah conclude
+/ this sentence falls off a cliff -->
 

### 2020-02-12 paper/manuscript.Rmd
reflow fst para results

@@
 connections an individual would have across these networks (Figure
-\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
-rapidly when groups were formed up to ~100 m threshold, followed by
-a plateau and slight decrease at higher thresholds, presumably due to an
-increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
-together, these results suggest the optimal social scale at which groups should
-be assigned is likely somewhere between ~20-100 m based on the rate at which
-network metrics stabilized. For ungulates, groups are often assigned based on 50
-m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
-suggesting that given similar quantities of data, ~50 m is likely an ideal
-social scale for generating social networks in caribou and similar species.
+\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
+formed up to ~100 m threshold, followed by a plateau and slight decrease at
+higher thresholds, presumably due to an increase in summer forest degree at ~500
+m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
+social scale at which groups should be assigned is likely somewhere between
+~20-100 m based on the rate at which network metrics stabilized. For ungulates,
+groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
+2018; Peignier et al. 2019), suggesting that given similar quantities of data,
+~50 m is likely an ideal social scale for generating social networks in caribou
+and similar species.
+<!-- TODO: missing summer relevance and all layer similarily-->
 

### 2020-02-12 paper/manuscript.Rmd
appropriate

@@
 social scale at which groups should be assigned is likely somewhere between
-~20-100 m based on the rate at which network metrics stabilized. For ungulates,
+~20 - 100 m based on the rate at which network metrics stabilized. For ungulates,
 groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
 2018; Peignier et al. 2019), suggesting that given similar quantities of data,
-~50 m is likely an ideal social scale for generating social networks in caribou
+~50 m is likely an appropriate social scale for generating social networks in caribou
 and similar species.

### 2020-02-12 paper/manuscript.Rmd
related to

@@
 seasons that are not clearly capturing periods of aggregation and
-dissaggregation according to resource availability and presence of conspecifics.
+dissaggregation related to resource availability.
 

### 2020-02-12 paper/manuscript.Rmd
lots of todos for results

@@
 possible to calculate between winter and summer forage because, at all landcover
-resolutions greater than 30 m there were no individuals connected in the network
+resolutions greater than 30 m, there were no individuals connected in the network
 layers. <!-- individuals still used forage but in much lower proportion +
@@
 
+<!-- TODO: update this..... -->
 As the number of observations used to generate multilayer networks increased,
@@
 
+<!-- TODO: update.....-->
 Contrasting winter and summer seasons became more similar with increasing window

### 2020-02-12 paper/manuscript.Rmd
fst win pos

@@
 
-**Missing: discussion of window position..**
+Moving winter and summer seasons showed increasing connectivity of individuals.
+Graph strength and layer relevance increased at time window position ~20 for summer layers (Figure \@ref(fig:winpos)a, Figure \@ref(fig:winpos)b).
+Layer similarity...
+<!-- TODO: between
+seasons increased consistently across landcover class (Figure
+\@ref(fig:winlen)b).--> Connective redundancy was stable throughout the shifting window positions (Figure \@ref(fig:winpos)).
+Similar to window length, increasing window position results in a mismatch between expected periods of resource seasonality and corresponding sociality.
 

### 2020-02-12 paper/manuscript.Rmd
unflow ugh word

@@
   # github_document
-  bookdown::pdf_document2:
-     number_sections: true
-  # bookdown::word_document2:
-  #   reference_docx: template.docx
+  # bookdown::pdf_document2:
+  #    number_sections: true
+  bookdown::word_document2:
+    reference_docx: template.docx
 # bibliography: ../references/knitcite.bib
@@
 
-(ref:spacetime) Space-time diagram displaying variation the relative spatial and
-temporal extent required for different types of social and communication
-processes for four species, including hyaena, passerine birds, sleepy lizards,
-and elephants. Spatial and temporal extent for social interactions, e.g. mating,
-grooming, or aggression, are similar for most species because physical contact
-between two individuals is required for most social interactions. The logical
-extension is that spatial and temporal extent for social interaction is nested
-within the spatial and temporal extent for social association because
-individuals must shared space to interact. By contrast, different species have
-potential for  greater spatial and temporal extents, for example, temporal
-extent for vocal communication is similar for most species because most vocal
-calls only persist in the environment for seconds, but spatial extent for vocal
-communication is highly variable with elephant calls extending the great
-distance and passerine calls extending the shortest distance.
+(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including hyaena, passerine birds, sleepy lizards, and elephants.
+Spatial and temporal extent for social interactions, e.g.
+mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for most social interactions.
+The logical extension is that spatial and temporal extent for social interaction is nested within the spatial and temporal extent for social association because individuals must shared space to interact.
+By contrast, different species have potential for  greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.
 
@@
 <!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
-networks were constructed for each landcover class (forest, forage, and open)
-across two seasons (summer and winter) and four network metrics calculated.  A)
-Mean graph strength across individuals showed an increase for winter network
-layers at 50 m through 500 m while summer network layers had consistently weak
-connections. B) Mean layer relevance was relatively stable across social
-thresholds for each season and landcover layer. C) Similarity of landcover
-network layers between seasons (e.g. open summer compared to open winter)
-showed different responses to changing landcover scale with an overall increase
-in similarity for open layers and decrease in similarity for forage layers.
-<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
-increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
-approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
-between 400 m and 500 m.
+(ref:socres) Varying scale in social threshold.
+For each social threshold, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections.
+B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for forage layers.
+<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.
 
@@
 <!-- Figure: metrics by landcover resolution -->
-(ref:lcres) Variation in multilayer network metrics as a function of changes in
-landcover resolution, a metric which we interpret as spatial scale. For each
-landcover resolution, multilayer networks were constructed for each landcover
-class (forest, forage, and open) across two seasons (summer and winter), and four
-network metrics were calculated and we examined how network metrics changed as a
-function of changes in spatial scale. A) Mean graph strength of individuals was
-weaker during the summer compared to the winter months. B) Mean layer relevance
-showed sparse connectivity in summer compared to winter networks and a decrease
-in winter forage layer relevance at higher landcover resolutions. C) Similarity
-of landcover network layers between seasons (e.g. open summer compared to open
-winter) showed different responses to changing landcover scale with an increase
-in similarity for forest layers at 250 m and decrease in similarity for open
-layers at 250 m. Note that forage layer similarity is not shown because
-individuals did not interact in forage habitats greater greater than 30 m
-landcover resolution. D) Mean connective redundancy across individuals showed a
-decreasing trend with increasing landcover resolution.
+(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
+For each landcover resolution, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
+A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m.
+Note that forage layer similarity is not shown because individuals did not interact in forage habitats greater greater than 30 m landcover resolution.
+D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
 
@@
 <!-- TODO: RO first sentence... -->
-(ref:nobs) Varying scale in number of observations. For each iteration, a number
-of observations (10-485 observations in steps of 25) were selected from the
-complete data set to construct multilayer networks with layers defined by each
-landcover class (forest, forage, and open) across two seasons (summer and
-winter) and four network metrics calculated. A) Mean graph strength across
-individuals varied for winter layers becoming relatively stable at 200
-observations and remained weak throughout for summer layers. B) Mean layer
-relevance across individuals increased for winter layers and slightly increased
-for summer layers. C) Similarity of landcover network layers between seasons
-(e.g. open summer compared to open winter) showed a stabilizing layer similarity
-at 200 observations for forest and 300 observations for forage and open
-habitats. D) Mean connective redundancy across individuals increased with
-increasing number of observations, which begins to plateau around 100
-observations. Note, data in panel C are truncated because there were few
-observations of individuals in foraging and open habitats during the winter,
-resulting in inability to calculate layer similarity at lower number of
-observations.
+(ref:nobs) Varying scale in number of observations.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
+B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for forage and open habitats.
+D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
+Note, data in panel C are truncated because there were few observations of individuals in foraging and open habitats during the winter, resulting in inability to calculate layer similarity at lower number of observations.
 
@@
 <!-- Figure: Window length -->
-(ref:winlen) Varying scale in time window length. For each time window length
-(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
-were constructed for each landcover class (forest, forage, and open) across two
-seasons (summer and winter) and four network metrics calculated. A) Mean graph
-strength across individuals was relatively stable over increasing time window
-lengths, though there was more variation in strength between landcover types as
-window length increased. B) Mean layer relevance generally increased during the
-summer months but was relatively stable across time window lengths for each
-landcover layer. C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed increasing similarity consistent
-across landcover layers with increasing window length. D) Mean connective
-redundancy across individuals varied dramatically depending on the length of the
-time window.
+(ref:winlen) Varying scale in time window length.
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
+B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
+D) Mean connective
+redundancy across individuals varied dramatically depending on the length of the time window.
 
@@
 <!-- Figure: Window position -->
-(ref:winpos) Varying scale in time window position. For each time window
-position (shifting the start date of the time window used to define seasons 1 to
-48 days from the original), multilayer networks were constructed for each
-landcover class (forest, forage, and open) across two seasons (summer and
-winter) and four network metrics calculated. A) Mean graph strength across
-individuals increased in summer network layers at window position 25 and
-increased between window position 20 and 40 for winter network layers. B) Mean
-layer relevance slightly decreased for winter layers and increased for summer
-layers, showing decreasing connectivity in shifted winter time windows and
-greater connectivity in summer layers at later window positions. C) Similarity
-of landcover network layers between seasons (e.g. open summer compared to open
-winter) showed fluctuations in layer similarity across landcover types with
-shifted time windows. D) Mean connective redundancy across individuals increased
-between window position 12 through 48 due to increased connectivity in the
-summer network layers.
+(ref:winpos) Varying scale in time window position.
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
+D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
 

### 2020-02-13 scripts/figures/figure1.R
fig1

@@ -62,8 +62,8 @@ aa <- ggplot() +
   ylab("Relative spatial scale") +
   xlab("") +
   scale_x_continuous(limit = c(-1, 14), breaks=c(0, 2.5, 5, 7.5, 10, 12.5), 
-                     labels= c("1 Second", "1 Minute",
-                             "1 Hour", "1 Day", "1 Month", "1 Year")) +
+                     labels= c("Seconds", "Minutes",
+                             "Hours", "Days", "Months", "Years")) +
   scale_y_continuous(limits = c(0.5, 10000000000), trans = log2_trans(),
                      breaks = trans_breaks("log10", function(x) 10^x),
                      labels = trans_format("log10", math_format(10^.x))) +
@@ -89,8 +89,8 @@ bb <- ggplot() +
   ylab("") +
   xlab("") +
   scale_x_continuous(limit = c(-1, 14), breaks=c(0, 2.5, 5, 7.5, 10, 12.5), 
-                     labels= c("1 Second", "1 Minute",
-                               "1 Hour", "1 Day", "1 Month", "1 Year")) +
+                     labels= c("Seconds", "Minutes",
+                               "Hours", "Days", "Months", "Years")) +
   scale_y_continuous(limits = c(0.25, 10000000000), 
                      trans = log2_trans(),
                      breaks = trans_breaks("log10", function(x) 10^x),
@@ -116,8 +116,8 @@ cc <- ggplot() +
   ylab("Relative spatial scale") +
   xlab("Relative time scale") +
   scale_x_continuous(limit = c(-1, 14), breaks=c(0, 2.5, 5, 7.5, 10, 12.5), 
-                     labels= c("1 Second", "1 Minute",
-                               "1 Hour", "1 Day", "1 Month", "1 Year")) +
+                     labels= c("Seconds", "Minutes",
+                               "Hours", "Days", "Months", "Years")) +
   scale_y_continuous(limits = c(0.25, 10000000000), 
                      trans = log2_trans(),
                      breaks = trans_breaks("log10", function(x) 10^x),
@@ -146,8 +146,8 @@ dd <- ggplot() +
   ylab("") +
   xlab("Relative time scale") +
   scale_x_continuous(limit = c(-1, 14), breaks=c(0, 2.5, 5, 7.5, 10, 12.5), 
-                     labels= c("1 Second", "1 Minute",
-                               "1 Hour", "1 Day", "1 Month", "1 Year")) +
+                     labels= c("Seconds", "Minutes",
[…]

### 2020-02-13 paper/manuscript.Rmd
percents

@@
 discrete removed all erroneous and outlier GPS fixes following
-[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all female
-caribou in the herd; however, the proportion of marked adult females was
-approximately 15% and we assumed these individuals were randomly distributed
-throughout the population.
+[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all caribou in
+the herd; however, the proportion of marked adult females was ~10% of all adult
+females and ~5% of all individuals in the herd. We assumed these individuals
+were randomly distributed throughout the population.
 

### 2020-02-13 paper/manuscript.Rmd
reductionalist

@@
 metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful simplification of many
+phenotype and fitness. It would also be a meaningful reduction of many
 network metrics that could help simplify statistical analyses and deal with the

### 2020-02-13 paper/manuscript.Rmd
refs

@@
 considering the importance of various ecological disciplines to better
-understand and predict animal social networks, including demography (Shizuka and
-Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017),
-disease ecology (Silk et al. 2017), and animal personality (Sih et al. 2017).
-While the number of studies integrating social network theory into a broader
-array of behavioural and ecological sub-disciplines is impressive, only recently
-has the role of animal space use been considered in describing the causes and
-consequences of the social environment in the context of (1) phenotypes and
-individual fitness [@Webber_2018], (2) movement ecology and collective movement
-[@Bode_2011], and (3) habitat selection and space use [@He_2019]. Importantly,
-much of the work linking space use and the social environment has been
-theoretical and empirical studies are lacking (but see Peignier et al. 2019;
-Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). Here, we discuss the
-role mutlilayer networks within the emerging integration of social and spatial
+understand and predict animal social networks, including demography
+[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
+ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
+studies integrating social network theory into a broader array of behavioural
+and ecological sub-disciplines is impressive, only recently has the role of
+animal space use been considered in describing the causes and consequences of
+the social environment in the context of (1) phenotypes and individual fitness
+[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
+(3) habitat selection and space use [@He_2019]. Importantly, much of the work
+linking space use and the social environment has been theoretical and empirical
+studies are lacking [but see @Peignier_2019;
+@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
+mutlilayer networks within the emerging integration of social and spatial
 ecology within the behavioural ecology literature.

### 2020-02-13 paper/citations.R

@@ -112,7 +112,19 @@ citep('10.1111/2041-210X.13177')
 
 ## temporal scale
 
-## perspectives
+## perspectives intro
+
+# Shizuka and Johnson 2020
+citep('10.1093/beheco/arz083')
+
+# Fisher and McAdam
+citep('10.1111/jeb.13195')
+
+# Sih et al 2018
+citep('10.1016/j.anbehav.2017.09.008')
+
+# Silk 2017
+citep('10.1111/2041-210X.12770')
 
 #landscape
 

### 2020-02-14 paper/manuscript.Rmd
abstract edits

@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges. Multilayer networks
+interactions to co-occurrence to overlapping home ranges. <!-- TODO: add temporal scale --> Multilayer networks
 promise the integration of monolayer animal social networks with the complexity
@@
 there remains an important biological and methodological gap in our
-understanding of an animal’s perception of scale. But scale can affect
-multilayer network dynamics and how we build and interpret them. Here we discuss
+understanding of an animal’s perception of scale. Here we discuss
 the role of scale in the context of multilayer networks and provide a social
@@
 processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research; our contribution
+animal social networks is an emerging area of research, as such our contribution
 incorporates perspectives on how the social environment and spatial processes
-are linked across scales in a multilayer
+are linked across scales in a multilayer context.
 

### 2020-02-14 paper/manuscript.Rmd
intro edits

@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges. <!-- TODO: add temporal scale --> Multilayer networks
-promise the integration of monolayer animal social networks with the complexity
-and importance of animal space use and movement in heterogeneous landscapes.
-Despite the complex interplay between social networks and how animals use space,
-there remains an important biological and methodological gap in our
-understanding of an animal’s perception of scale. Here we discuss
-the role of scale in the context of multilayer networks and provide a social
-ungulate case study to illustrate the role of social, spatial, and temporal
-scale on multilayer processes. We also present perspectives on future
-development and application of scale in multilayer networks with respect to:
-habitat selection and space use; phenotypes and individual fitness; and movement
-ecology and collective movement. Effective integration of social and spatial
-processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research, as such our contribution
-incorporates perspectives on how the social environment and spatial processes
-are linked across scales in a multilayer context.
+interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
+temporal scale --> Multilayer networks promise the integration of monolayer
+animal social networks with the complexity and importance of animal space use
+and movement in heterogeneous landscapes. Despite the complex interplay between
+social networks and how animals use space, there remains an important biological
+and methodological gap in our understanding of an animal’s perception of scale.
+Here we discuss the role of scale in the context of multilayer networks and
+provide a social ungulate case study to illustrate the role of social, spatial,
+and temporal scale on multilayer processes. We also present perspectives on
+future development and application of scale in multilayer networks with respect
+to: habitat selection and space use; phenotypes and individual fitness; and
+movement ecology and collective movement. Effective integration of social and
+spatial processes, including biologically meaningful scales, within the context
+of animal social networks is an emerging area of research, as such our
+contribution incorporates perspectives on how the social environment and spatial
+processes are linked across scales in a multilayer context.
 
@@
 Multiscale ecology has been integrated into species distribution modelling
-[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
-Meanwhile, in the context of animal behaviour, certain behaviours are scale
-dependent, for example, acoustic communication in birds occurs over variable
-spatial scales [@Luther_2009]. We posit that animal behaviour and, more
-specifically, the social environment that animals experience must also be
-scale-dependent.
+[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989], among others.
+Meanwhile, in the context of animal behaviour, certain behaviours are scale-dependent; for example, acoustic communication in birds varies with spatial scales [@Luther_2009].
+We posit that it is important to consider that animal behavior within the social environment will be scale-dependent.
 
@@
 
-Our study is motivated by behavioural, landscape, and spatial ecology to build a
+Our examinations is motivated by behavioural, landscape, and spatial ecology to build a
 conceptual and analytical framework for scale-dependent multilayer networks and
@@
 movement ecology and collective movement [@Jolles_2019], and habitat selection
-and space use. <!-- TODO: (REF)--> <!-- TODO: Webber reference should be 2018,
-but defaulting to 2017-->
+and space use<!-- TODO: (REF)--> . 
+<!-- TODO: we answer the first question in the discussion, but not the second-->
+<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
 

### 2020-02-14 paper/manuscript.Rmd
reflow
spacetime cap edits

@@
 Multiscale ecology has been integrated into species distribution modelling
-[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989], among others.
-Meanwhile, in the context of animal behaviour, certain behaviours are scale-dependent; for example, acoustic communication in birds varies with spatial scales [@Luther_2009].
-We posit that it is important to consider that animal behavior within the social environment will be scale-dependent.
+[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
+among others. Meanwhile, in the context of animal behaviour, certain behaviours
+are scale-dependent; for example, acoustic communication in birds varies with
+spatial scales [@Luther_2009]. We posit that it is important to consider that
+animal behavior within the social environment will be scale-dependent.
 
@@
 
-Our examinations is motivated by behavioural, landscape, and spatial ecology to build a
-conceptual and analytical framework for scale-dependent multilayer networks and
-we apply this framework to a case study of caribou (*Rangifer tarandus*) in
-Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
-principal questions associated with scale-dependent multilayer networks. First,
-to what degree does the social scale of relationships, spatial scale of
-landscapes, and temporal scale of analysis influence our ability to interpret
-complex social systems? Second, can variation in the social, spatial, and
-temporal scale improve predictions associated with biological differences in
+Our examinations is motivated by behavioural, landscape, and spatial ecology to
+build a conceptual and analytical framework for scale-dependent multilayer
+networks and we apply this framework to a case study of caribou (*Rangifer
+tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
+address two principal questions associated with scale-dependent multilayer
+networks. First, to what degree does the social scale of relationships, spatial
+scale of landscapes, and temporal scale of analysis influence our ability to
+interpret complex social systems? Second, can variation in the social, spatial,
+and temporal scale improve predictions associated with biological differences in
 seasonal resource availability and social association? We conclude with
@@
 mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for most social interactions.
-The logical extension is that spatial and temporal extent for social interaction is nested within the spatial and temporal extent for social association because individuals must shared space to interact.
+The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must shared space to interact.
 By contrast, different species have potential for  greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

### 2020-02-14 paper/citations.R
add net mets package cites

@@ -249,6 +249,15 @@ citep('10.1111/1365-2656.12773')
 # R
 citep(citation())
 
+# data.table
+citep(citation('data.table'))
+
+# igraph
+citep(citation('igraph'))
+
+# asnipe
+citep(citation('asnipe'))
+
 
 ### Write out bib ----
 write.bibtex(file = "references/knitcite.bib")

### 2020-02-14 paper/manuscript.Rmd
add net mets package cites
rm "habitat types"

@@
 forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
-and mixed-wood forest habitat types. Water habitat was excluded from all
+and mixed-wood forest. Water habitat was excluded from all
 subsequent analyses.
@@
 (e.g. winter open compared to summer open) using the Pearson correlation
-coefficient [@Br_dka_2018].
+coefficient [@Br_dka_2018]. Network metrics were calculated using the R packages 
+`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
 

### 2020-02-14 scripts/9-figure-2.R
interlayer edges

@@ -118,7 +118,11 @@ zzbox[layer %in% c('winter-1', 'summer-1'),
       c('modx', 'mody') := .(slideright * (.GRP - 1), 3), by = layer]
 
 
-# Edges between same individuals
+#Edges between same individuals
+zzz[layer == 'summer-3', c('xendsame', 'yendsame') := .(shearx + slideright, sheary)]
+zzz[layer == 'summer-2', c('xendsame', 'yendsame') := .(shearx + slideright, sheary + mody)]
+zzz[layer == 'summer-1', c('xendsame', 'yendsame') := .(shearx + slideright, sheary + mody)]
+
 # a <- zzz[!is.na(xend) & !is.na(yend)][vertex.names == 'FO2016004', .SD]
 # merge(a, a[, .(V1e = V1, V2e = V2, vertex.names)], allow.cartesian = TRUE)
 
@@ -153,20 +157,19 @@ labels <- data.table(
   ) +
     geom_polygon(aes(group = layer), data = zzbox[order(ord)],
                  alpha = 0.25) + 
-    geom_edges(aes(group = layer,
-                   xend = shearxend + modx,
+    geom_edges(aes(xend = shearxend + modx,
                    yend = shearyend + mody,
-                   size = weight),
-               alpha = 1
+                   size = weight)
     ) +
     scale_size(range = c(0.1, 2)) + 
-    # geom_edges(aes(group = layer,
-    #                xend = shearxend + modx,
-    #                yend = shearyend + mody
-    # ), data = zzz[, .SD[order(vertex.names, modx, mody)]]) +
+    geom_edges(aes(xend = xendsame,
+                   yend = yendsame),
+               size = 0.1,
+               alpha = 0.5
+    ) +
     geom_nodes(aes(color = vertex.names), size = 5) +
     scale_color_viridis_d() + 
-    guides(color = FALSE) +
+    guides(color = FALSE, size = FALSE) +
     geom_text(aes(x, y, xend = NULL, yend = NULL, label = label), data = labels) + 
   p
 )

### 2020-02-14 paper/manuscript.Rmd
add placeholder lc cite

@@
 <!-- TODO: update citation for lc product from Hance --> 
-Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
-Available landcover classification included nine habitat types at 30 m
-resolution. We reclassified the landcover types into three categories: foraging
-habitat, open habitat, and forest habitat using the R package `raster`
-[@Hijmans_2019]. Foraging habitat consisted of lichen habitat, open habitat
-consisted of wetland, rocky barrens, and anthropogenic habitat types, while
-forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
-and mixed-wood forest. Water habitat was excluded from all
+Landcover data were provided by the Newfoundland and Labrador Wildlife Division
+[@Integrated_2013]. Available landcover classification included nine habitat
+types at 30 m resolution. We reclassified the landcover types into three
+categories: foraging habitat, open habitat, and forest habitat using the R
+package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
+open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
+types, while forest habitat consisted of coniferous forest, conifer scrub,
+broadleaf forest, and mixed-wood forest. Water habitat was excluded from all
 subsequent analyses.

### 2020-02-14 paper/manuscript.Rmd
rm net types comments

@@
 
-### Network types and construction (defining layers for the multilayer network)
-<!-- TODO: should use something like "using syntax from Kivela 2014..." or 
-Following [@Kivela_2014]:
-other info to maybe include: the multilayer network was not node-aligned since
-not all individuals were on all layers
-the temporal aspect is ordinal coupling and landcover aspect is categorical coupling
-
-Individuals were subset to ensure they had data collected in both seasons
--->
-
+### Network types and construction
 We generated a multilayer social network consisting 16 individual nodes and two
@@
 package `spatsoc` [@Robitaille_2019] in `r version$version.string`
-[@R_Core_Team_2019]. <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
+[@R_Core_Team_2019]. 
+<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
 

### 2020-02-14 paper/manuscript.Rmd
add data pull for n individuals

@@
 source('../scripts/0-variables.R')
+
+DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')
 ```
@@
 ### Network types and construction
-We generated a multilayer social network consisting 16 individual nodes and two
-aspects (season and landcover). Two season elementary-layers (winter and summer)
-and three landcover elementary-layers (forest, forage, and open) combined for a
-total of six layers. Layers were composed of individuals represented as nodes
-and social associations represented as edges, for each season and landcover
-combination. Proximity-based social network layers were generated using the R
-package `spatsoc` [@Robitaille_2019] in `r version$version.string`
-[@R_Core_Team_2019]. 
+We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
+individual nodes and two aspects (season and landcover). Two season
+elementary-layers (winter and summer) and three landcover elementary-layers
+(forest, forage, and open) combined for a total of six layers. Layers were
+composed of individuals represented as nodes and social associations represented
+as edges, for each season and landcover combination. Proximity-based social
+network layers were generated using the R package `spatsoc` [@Robitaille_2019]
+in `r version$version.string` [@R_Core_Team_2019].
 <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

### 2020-02-14 paper/manuscript.Rmd
fig 2 cap

@@
 interlayer edges represented connections between the same individuals across
-contexts (Figure 2).
+seasons and within habitat classes (Figure 2).
+<!-- eg this is connecting contexts used to calculate layer similarity -->
 
@@
 
-<!-- TODO: work this cap -->
-(ref:ml) Visualization of multilayer network for social ungulate case study.
-Six layers are presented with individuals shown as nodes, fixed in space across layers.
-Layer represent combinations of two seasons (winter and summer) and three landcover class (open, forest and forage).
-Edges connect individuals that associated according to spatial and temporal thresholds described above.
+(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color.
+Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage).
+Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+Interlayer edges connect individuals to themselves across seasons and within habitat classes (eg.
+individual "A" in summer, forest and individual "A" in winter, forest).
 

### 2020-02-14 scripts/8-plots.R
add vline to layer sim plots

@@ -102,7 +102,8 @@ base1 <- ggplot(unique(DT[, .SD, .SDcols = c(var, 'lcname', 'layersim')]),
 g1 <- base1 + geom_line(aes(y = (layersim)), size = linesize) + 
   ylab('Layer Similarity') +
   theme(legend.position = pos1) +
-  expand_limits(y = c(-1, 1))
+  expand_limits(y = c(-1, 1)) +
+  geom_vline(xintercept = 0)
 
 # Plot full, across
 base2 <- ggplot(DT[, .SD[1], by = var], 

### 2020-02-14 paper/manuscript.Rmd
social scale edits

@@
 
-We altered the social scale based on visual (short distance) and auditory (long
-distance) sensory modalities of caribou<!-- TODO: REF? / see EVW comment-->. Specifically, we
-modified the spatial distance threshold required for group assignment using
+We modified the spatial distance threshold required for group assignment using
 `spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
@@
 at the coarsest social scale, individuals within 500 m of one another were
-considered in the same group.
+considered in the same group. We assumed these scales represented visual (short distance) to auditory (long distance) sensory modalities of caribou.
 

### 2020-02-14 paper/manuscript.Rmd
add 750m

@@
 aggregated the 30 m landcover raster using the R package `grainchanger`
-[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
+[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
 occurred using a modal moving window method using a circular window
@@
 represents fine-scale decision making for caribou during foraging, while
-re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
+re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
 select and avoid habitat (Bastille-Rousseau et al. 2017).

### 2020-02-14 paper/manuscript.Rmd
nobs edits
reflow
why opt

@@
 [@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
-fixed rate (eg every $x$ minutes or hours) continuously throughout the study
+fixed rate, eg. every $x$ minutes or hours, continuously throughout the study
 period. We investigated the influence of the number of observations on resulting
@@
 <!-- TODO: Add intro/general to results? with mention figures are means of inds-->
+
 <!-- TODO: make sure we clarify these are means of all individuals? -->
@@
 m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
-social scale at which groups should be assigned is likely somewhere between
-~20 - 100 m based on the rate at which network metrics stabilized. For ungulates,
+<!-- TODO: why optimal -->
+social scale at which groups should be assigned is likely somewhere between ~20
+- 100 m based on the rate at which network metrics stabilized. For ungulates,
 groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
 2018; Peignier et al. 2019), suggesting that given similar quantities of data,
-~50 m is likely an appropriate social scale for generating social networks in caribou
-and similar species.
+~50 m is likely an appropriate social scale for generating social networks in
+caribou and similar species.
 <!-- TODO: missing summer relevance and all layer similarily-->

### 2020-02-14 paper/manuscript.Rmd
little space

@@
 were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
-time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
+time understanding this previous sentence --> (Figure \@ref(fig:lcres)d).  These
 results indicate the importance of matching landcover resolution to scale of

### 2020-02-14 paper/manuscript.Rmd
add n caribou, fogo, years to all case study fig caps

@@
 (ref:socres) Varying scale in social threshold.
-For each social threshold, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
 A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections.
@@
 (ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
-For each landcover resolution, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale.
+For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+We examined how network metrics changed as a function of changes in spatial scale.
 A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
@@
 (ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
 A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
@@
 (ref:winlen) Varying scale in time window length.
-For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
 A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
@@
 open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-D) Mean connective
-redundancy across individuals varied dramatically depending on the length of the time window.
+D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window.
 
@@
 (ref:winpos) Varying scale in time window position.
-For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
 A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.

### 2020-02-14 paper/manuscript.Rmd
fix DT path in manuscript.Rmd

@@
   # github_document
-  # bookdown::pdf_document2:
-  #    number_sections: true
-  bookdown::word_document2:
-    reference_docx: template.docx
+  bookdown::pdf_document2:
+     number_sections: true
+  # bookdown::word_document2:
+  #   reference_docx: template.docx
 # bibliography: ../references/knitcite.bib
@@
 
-DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')
+DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
 ```

### 2020-02-14 paper/manuscript.Rmd
need data.table (always)
update socres fig cap

@@
 
+library(data.table)
 DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
@@
 For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
-A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections.
-B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer.
-C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for forage layers.
-<!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.
+A) Mean graph strength across individuals showed an increase for winter network layers while summer network layers had consistently weak connections.
+B) Mean layer relevance was increased for winter layers between 5 m and 50 m, otherwise stable for all social thresholds >50 m for winter and all social thresholds for summer.
+C) Similarity of network layers across seasons and within habitat classes (e.g.
+open summer compared to open winter) was relatively stable for all habitat class layers.
+D) Mean connective redundancy across individuals showed an increase between 5 m and 50 m before remaining stable through all other social thresholds.
 

### 2020-02-14 paper/manuscript.Rmd
update socres discussion

@@
 scale increased; however, this relationship varied by habitat type and season.
-As social scale increased, graph strength for winter networks increased to
-~100-200 m thresholds, followed by a plateau, while graph strength for summer
+As social scale increased, graph strength for winter networks increased rapidly between 5 m and 50 m thresholds, followed by a plateau, while graph strength for summer
 networks did not change as the social threshold increased (Figure
@@
 connections an individual would have across these networks (Figure
-\@ref(fig:socres)b). Connective redundancy increased rapidly when groups were
-formed up to ~100 m threshold, followed by a plateau and slight decrease at
-higher thresholds, presumably due to an increase in summer forest degree at ~500
-m (Figure \@ref(fig:socres)d). Taken together, these results suggest the optimal
+\@ref(fig:socres)b).
+Layer similarity (Figure \@ref(fig:socres)c) and connective redundancy (Figure \@ref(fig:socres)d) were relatively stable across social thresholds.
+Taken together, these results suggest the optimal
 <!-- TODO: why optimal -->
@@
 caribou and similar species.
-<!-- TODO: missing summer relevance and all layer similarily-->
+<!-- TODO: missing summer relevance -->
 

### 2020-02-14 paper/manuscript.Rmd
update lcres fig cap

@@
 <!-- Figure: metrics by landcover resolution -->
-(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale.
+(ref:lcres) Varying spatial scale in landcover resolution.
 For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
-We examined how network metrics changed as a function of changes in spatial scale.
-A) Mean graph strength of individuals was weaker during the summer compared to the winter months.
+A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
+Individuals in summer layers had consistent weak connections.
 B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
 C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m.
-Note that forage layer similarity is not shown because individuals did not interact in forage habitats greater greater than 30 m landcover resolution.
-D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.
+open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m.
+Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated.
+D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
 

### 2020-02-14 paper/manuscript.Rmd
update lcres discussion

@@
 caribou and similar species.
-<!-- TODO: missing summer relevance -->
+<!-- TODO: missing summer relevance .. the actual value of layer sim?-->
 
-Increasing the scale of landcover resolution resulted in decreased proportion of
-rare and patchy habitats, and low connectivity of individuals in these habitats.
-In winter, layer relevance was stable for open and forest habitats but decreased
-for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
-stable for forest and open habitats except for a contrasting increase in
-similarity for forest and decrease in similarity for open habitats 250 m
-landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
+(ref:lcres) Varying spatial scale in landcover resolution.
+For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
+Individuals in summer layers had consistent weak connections.
+B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m.
+Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated.
+D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
+
+Increasing landcover resolution resulted in a decreased proportion of forage, a
+rare and patchy habitat, and corresponding low connectivity of individuals in these habitats.
+Mean graph strength increased consistently in winter forest and open habitats.
+Mean graph strength in winter forage <!-- TODO: check this fig A/C similar lines--> Individuals in summer layers had consistent weak connections.
+Layer relevance was stable in winter for open and forest habitats but decreased for forage habitats (Figure \@ref(fig:lcres)b).
+Layer relevance was stable for all habitat classes in summer layers.
+Layer similarity was stable for forest and open, except for a sharp decrease in layer similarity in open at 100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure \@ref(fig:lcres)c).
+Layer similarity was not
 possible to calculate between winter and summer forage because, at all landcover
 resolutions greater than 30 m, there were no individuals connected in the network
-layers. <!-- individuals still used forage but in much lower proportion +
-lowered opportunity to associate --> Connective redundancy decreased with
-increasing landcover resolution due the decrease in connectivity of individuals
-in winter forage habitats, resulting in a multilayer network where neighbours
-were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
-time understanding this previous sentence --> (Figure \@ref(fig:lcres)d).  These
+layers.
+Individuals still used forage habitats but given a lower availability due to increasing landcover resolution, at a much lower rate.
+Connective redundancy slightly decreased as landcover resolution increased (Figure \@ref(fig:lcres)d).
+These
 results indicate the importance of matching landcover resolution to scale of
 selection as well as ensuring the landcover product used has a resolution fine
-enough to detect relevant landscape features and habitats. <!-- TODO: how? This
-isn't clear enough for me to follow yet -->
+enough to detect landscape features and habitats relevant to study species. 
+<!-- TODO: how? This isn't clear enough for me to follow yet -->
 

### 2020-02-14 paper/manuscript.Rmd
reflow

@@
 scale increased; however, this relationship varied by habitat type and season.
-As social scale increased, graph strength for winter networks increased rapidly between 5 m and 50 m thresholds, followed by a plateau, while graph strength for summer
-networks did not change as the social threshold increased (Figure
+As social scale increased, graph strength for winter networks increased rapidly
+between 5 m and 50 m thresholds, followed by a plateau, while graph strength for
+summer networks did not change as the social threshold increased (Figure
 \@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
@@
 connections an individual would have across these networks (Figure
-\@ref(fig:socres)b).
-Layer similarity (Figure \@ref(fig:socres)c) and connective redundancy (Figure \@ref(fig:socres)d) were relatively stable across social thresholds.
-Taken together, these results suggest the optimal
+\@ref(fig:socres)b). Layer similarity (Figure \@ref(fig:socres)c) and connective
+redundancy (Figure \@ref(fig:socres)d) were relatively stable across social
+thresholds. Taken together, these results suggest the optimal 
 <!-- TODO: why optimal --> 
-social scale at which groups should be assigned is likely somewhere between ~20
-- 100 m based on the rate at which network metrics stabilized. For ungulates,
-groups are often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al.
-2018; Peignier et al. 2019), suggesting that given similar quantities of data,
-~50 m is likely an appropriate social scale for generating social networks in
-caribou and similar species.
+social scale at which groups should be assigned is likely somewhere
+between ~20 - 100 m based on the rate at which network metrics stabilized. For
+ungulates, groups are often assigned based on 50 m threshold (Lingle 2003;
+Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
+quantities of data, ~50 m is likely an appropriate social scale for generating
+social networks in caribou and similar species.
 <!-- TODO: missing summer relevance .. the actual value of layer sim?-->
 
-(ref:lcres) Varying spatial scale in landcover resolution.
-For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
-A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
-Individuals in summer layers had consistent weak connections.
-B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
-C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m.
-Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated.
-D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
-
 Increasing landcover resolution resulted in a decreased proportion of forage, a
-rare and patchy habitat, and corresponding low connectivity of individuals in these habitats.
-Mean graph strength increased consistently in winter forest and open habitats.
-Mean graph strength in winter forage <!-- TODO: check this fig A/C similar lines--> Individuals in summer layers had consistent weak connections.
-Layer relevance was stable in winter for open and forest habitats but decreased for forage habitats (Figure \@ref(fig:lcres)b).
-Layer relevance was stable for all habitat classes in summer layers.
-Layer similarity was stable for forest and open, except for a sharp decrease in layer similarity in open at 100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure \@ref(fig:lcres)c).
-Layer similarity was not
-possible to calculate between winter and summer forage because, at all landcover
-resolutions greater than 30 m, there were no individuals connected in the network
-layers.
-Individuals still used forage habitats but given a lower availability due to increasing landcover resolution, at a much lower rate.
-Connective redundancy slightly decreased as landcover resolution increased (Figure \@ref(fig:lcres)d).
-These
-results indicate the importance of matching landcover resolution to scale of
-selection as well as ensuring the landcover product used has a resolution fine
-enough to detect landscape features and habitats relevant to study species. 
-<!-- TODO: how? This isn't clear enough for me to follow yet -->
+rare and patchy habitat, and corresponding low connectivity of individuals in
+these habitats. Mean graph strength increased consistently in winter forest and
+open habitats. Mean graph strength in winter forage <!-- TODO: check this fig
+A/C similar lines--> Individuals in summer layers had consistent weak
+connections. Layer relevance was stable in winter for open and forest habitats
+but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance
+was stable for all habitat classes in summer layers. Layer similarity was stable
+for forest and open, except for a sharp decrease in layer similarity in open at
+100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure
+\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
+winter and summer forage because, at all landcover resolutions greater than 30
+m, there were no individuals connected in the network layers. Individuals still
+used forage habitats but given a lower availability due to increasing landcover
+resolution, at a much lower rate. Connective redundancy slightly decreased as
+landcover resolution increased (Figure \@ref(fig:lcres)d). These results
+indicate the importance of matching landcover resolution to scale of selection
+as well as ensuring the landcover product used has a resolution fine enough to
+detect landscape features and habitats relevant to study species. <!-- TODO:
+how? This isn't clear enough for me to follow yet -->
 

### 2020-02-14 paper/manuscript.Rmd
update nobs fig cap

@@
 <!-- Figure: metrics by number of observations -->
-<!-- TODO: RO first sentence... -->
 (ref:nobs) Varying scale in number of observations.
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
-A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers.
-B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers.
-C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for forage and open habitats.
-D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations.
-Note, data in panel C are truncated because there were few observations of individuals in foraging and open habitats during the winter, resulting in inability to calculate layer similarity at lower number of observations.
+A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers.
+B) Mean layer relevance across individuals increased sharply for winter layers between ~10 - ~50 observations before stabilizing.
+Summer layers had consistent low layer relevance.
+C) Similarity of network layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was relatively consistent across number of observations for forest habitats.
+<!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers.
+D) Mean connective redundancy across individuals increased rapidly between ~10 - ~50 observations and then remained constant.
 

### 2020-02-14 paper/manuscript.Rmd
update (ish) nobs discussion

@@
 as well as ensuring the landcover product used has a resolution fine enough to
-detect landscape features and habitats relevant to study species. <!-- TODO:
-how? This isn't clear enough for me to follow yet -->
+detect landscape features and habitats relevant to study species.
 
-<!-- TODO: update this..... -->
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics generally appeared to stabilize.
+individuals became more connected and metrics appeared to stabilize.
+Mean graph strength varied in winter layers becoming stable at ~200 m and remained consistently weak in summer layers (Figure \@ref(fig:nobs)a).
+Layer relevance in winter layers increased between ~10 - ~50 observations, remaining stable with additional observations (Figure \@ref(fig:nobs)b).
+<!-- TODO: update with fix for open/rerun -->
 Like coarse landcover resolution (above), low numbers of observations were not
-sufficient for capturing individuals in all contexts and layer similarity could
-not be calculated below approximately 75 observations for forest, approximately
+sufficient for capturing individuals in all contexts and therefore layer similarity could
+not be calculated below approximately <!--TODO: update these -->75 observations for forest, approximately 
 210 observations for open and approximately 300 observations for forage (Figure
@@
 forest and approximately 300 observations for open and forage landcover types.
-Connective redundancy increased with increasing number of observations as
-individuals became more connected to neighbours in multiple layers (Figure
-\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
+Connective redundancy increased dramatically between ~10 - ~50 observations before stabilizing with all new observations included (Figure \@ref(fig:nobs)d). 
+Given the observed trend of these multilayer metrics
 stabilizing after a certain number of observations are included, the results
 suggest this sensitivity method could be useful for determining the number of
-observations necessary for sufficiently describing the social dynamics across
+observations necessary for sufficiently describing social dynamics across
 contexts.

### 2020-02-14 paper/manuscript.Rmd
render

@@
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics appeared to stabilize.
-Mean graph strength varied in winter layers becoming stable at ~200 m and remained consistently weak in summer layers (Figure \@ref(fig:nobs)a).
-Layer relevance in winter layers increased between ~10 - ~50 observations, remaining stable with additional observations (Figure \@ref(fig:nobs)b).
-<!-- TODO: update with fix for open/rerun -->
-Like coarse landcover resolution (above), low numbers of observations were not
-sufficient for capturing individuals in all contexts and therefore layer similarity could
-not be calculated below approximately <!--TODO: update these -->75 observations for forest, approximately 
-210 observations for open and approximately 300 observations for forage (Figure
-\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
-stabilized for all three landcover classes at approximately 200 observations for
-forest and approximately 300 observations for open and forage landcover types.
-Connective redundancy increased dramatically between ~10 - ~50 observations before stabilizing with all new observations included (Figure \@ref(fig:nobs)d). 
-Given the observed trend of these multilayer metrics
-stabilizing after a certain number of observations are included, the results
-suggest this sensitivity method could be useful for determining the number of
-observations necessary for sufficiently describing social dynamics across
-contexts.
+individuals became more connected and metrics appeared to stabilize. Mean graph
+strength varied in winter layers becoming stable at ~200 m and remained
+consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
+winter layers increased between ~10 - ~50 observations, remaining stable with
+additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
+for open/rerun --> Like coarse landcover resolution (above), low numbers of
+observations were not sufficient for capturing individuals in all contexts and
+therefore layer similarity could not be calculated below approximately <!--TODO:
+update these -->75 observations for forest, approximately 210 observations for
+open and approximately 300 observations for forage (Figure \@ref(fig:nobs)c).
+Once sufficient observations were obtained, layer similarity stabilized for all
+three landcover classes at approximately 200 observations for forest and
+approximately 300 observations for open and forage landcover types. Connective
+redundancy increased dramatically between ~10 - ~50 observations before
+stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
+the observed trend of these multilayer metrics stabilizing after a certain
+number of observations are included, the results suggest this sensitivity method
+could be useful for determining the number of observations necessary for
+sufficiently describing social dynamics across contexts.
 

### 2020-02-14 paper/manuscript.Rmd
better less ~ then -

@@
 consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
-winter layers increased between ~10 - ~50 observations, remaining stable with
+winter layers increased between ~10 m and ~50 m observations, remaining stable with
 additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
@@
 approximately 300 observations for open and forage landcover types. Connective
-redundancy increased dramatically between ~10 - ~50 observations before
+redundancy increased dramatically between ~10 m and ~50 m observations before
 stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
@@
 A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers.
-B) Mean layer relevance across individuals increased sharply for winter layers between ~10 - ~50 observations before stabilizing.
+B) Mean layer relevance across individuals increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing.
 Summer layers had consistent low layer relevance.
@@
 <!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers.
-D) Mean connective redundancy across individuals increased rapidly between ~10 - ~50 observations and then remained constant.
+D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
 

### 2020-02-14 paper/manuscript.Rmd
update winpos fig cap

@@
 <!-- Figure: Window length -->
-(ref:winlen) Varying scale in time window length.
+(ref:winlen) Varying temporal scale in time window length.
 For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
-A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased.
-B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer.
-C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length.
-D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window.
+A) Mean graph strength across individuals was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
+Summer layers an increase in strength for open and forage habitats.
+B) Mean layer relevance was stable for winter layers and increased for summer layers across habitat classes.
+C) Similarity of layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was relatively stable.
+D) Mean connective redundancy across individuals increased marginally with increasing window length.
 

### 2020-02-14 paper/manuscript.Rmd
update winpos discussion

@@
 consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
-winter layers increased between ~10 m and ~50 m observations, remaining stable with
-additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
-for open/rerun --> Like coarse landcover resolution (above), low numbers of
-observations were not sufficient for capturing individuals in all contexts and
-therefore layer similarity could not be calculated below approximately <!--TODO:
-update these -->75 observations for forest, approximately 210 observations for
-open and approximately 300 observations for forage (Figure \@ref(fig:nobs)c).
-Once sufficient observations were obtained, layer similarity stabilized for all
-three landcover classes at approximately 200 observations for forest and
-approximately 300 observations for open and forage landcover types. Connective
-redundancy increased dramatically between ~10 m and ~50 m observations before
-stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
-the observed trend of these multilayer metrics stabilizing after a certain
-number of observations are included, the results suggest this sensitivity method
-could be useful for determining the number of observations necessary for
-sufficiently describing social dynamics across contexts.
+winter layers increased between ~10 m and ~50 m observations, remaining stable
+with additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with
+fix for open/rerun --> Like coarse landcover resolution (Figure
+\@ref(fig:lcres)), low numbers of observations were not sufficient for capturing
+individuals in all contexts and therefore layer similarity could not be
+calculated below approximately <!--TODO: update these -->75 observations for
+forest, approximately 210 observations for open and approximately 300
+observations for forage (Figure \@ref(fig:nobs)c). Once sufficient observations
+were obtained, layer similarity stabilized for all three landcover classes at
+approximately 200 observations for forest and approximately 300 observations for
+open and forage landcover types. Connective redundancy increased dramatically
+between ~10 m and ~50 m observations before stabilizing with all new
+observations included (Figure \@ref(fig:nobs)d). Given the observed trend of
+these multilayer metrics stabilizing after a certain number of observations are
+included, the results suggest this sensitivity method could be useful for
+determining the number of observations necessary for sufficiently describing
+social dynamics across contexts.
 
@@
 
-<!-- TODO: update.....-->
-Contrasting winter and summer seasons became more similar with increasing window
-length. Individual graph strength and layer relevance increased for all summer
-layers as individuals became more connected with increasing window lengths
-(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
-seasons increased consistently across landcover class (Figure
-\@ref(fig:winlen)b).  These results suggest that an increasing window length,
-especially for the summer season, may be resulting in less precisely defined
-seasons that are not clearly capturing periods of aggregation and
-dissaggregation related to resource availability.
-
-<!-- TODO: end with something highlighting this shows it's
-important to properly define your season -->
+<!-- TODO: this first sentence is not about layer similarity - so hopefully it isn't
+guiding the reader the wrong way -->
+Contrasting seasons of sociality become more similarly connected with window
+length. Mean graph strength and layer relevance increased for summer layers as
+individuals became more connected with increasing window lengths (Figure
+\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). In contrast, mean graph strength
+and layer relevance was relatively stable for winter layers. Similarity of
+layers across habitat classes and between seasons (e.g. open summer compared to
+open winter) was variable across window lengths (Figure \@ref(fig:winlen)c).
+Connective redundancy increased marginally with increasing window length. These
+results suggest that an increasing window length, especially for the summer
+season, may be resulting in less precisely defined seasons that are not clearly
+capturing periods of aggregation and dissaggregation related to resource
+availability.
 

### 2020-02-14 paper/manuscript.Rmd
update winpos fig cap

@@
 
+, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions.
 Moving winter and summer seasons showed increasing connectivity of individuals.
@@
 <!-- Figure: Window position -->
-(ref:winpos) Varying scale in time window position.
+(ref:winpos) Varying temporal scale in time window position.
 For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
 A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
-B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions.
-C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows.
-D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
+B) Mean layer relevance slightly decreased for winter layers and increased for summer layers.
+C) Similarity of layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was relatively stable until window position ~28 where forage and open layer similarity decreased.
+D) Mean connective redundancy across individuals increased marginally with advancing time window position.
 

### 2020-02-14 paper/manuscript.Rmd
update winpos discussion

@@
 
-, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions.
-Moving winter and summer seasons showed increasing connectivity of individuals.
-Graph strength and layer relevance increased at time window position ~20 for summer layers (Figure \@ref(fig:winpos)a, Figure \@ref(fig:winpos)b).
-Layer similarity...
-<!-- TODO: between
-seasons increased consistently across landcover class (Figure
-\@ref(fig:winlen)b).--> Connective redundancy was stable throughout the shifting window positions (Figure \@ref(fig:winpos)).
-Similar to window length, increasing window position results in a mismatch between expected periods of resource seasonality and corresponding sociality.
+Moving window positions defining seasons showed an increase in connectivity of
+individuals in summer layers. Graph strength increased at time window position
+~20 for summer and winter layers  and, while summer layers continued to
+increase, winter layers showed a decrease in graph strength at time window
+position ~35 (Figure \@ref(fig:winpos)a). Layer relevance increased across
+moving window positions for summer layers and was relatively stable for winter
+layers (Figure \@ref(fig:winpos)b). These results indicate slight decreasing
+connectivity and increased connectivity in summer layers at shifted winter time
+windows. Layer similarity was relatively stable across moving window positions
+except for a sharp decline at window position ~28 in forage and open layers
+(Figure \@ref(fig:winpos) c). Connective redundancy showed a marginal increase
+with increasing window position (Figure \@ref(fig:winpos) d). Similar to window
+length, changing the position of the time window in this case results in a
+mismatch between expected periods of resource seasonality and corresponding
+sociality, highlighting the importance of carefully selecting temporal scale of
+analysis.
 

### 2020-02-14 paper/manuscript.Rmd
rm junk

@@
 networks -->
-
-<!-- TODO: this first sentence is not about layer similarity - so hopefully it isn't
-guiding the reader the wrong way -->
-Contrasting seasons of sociality become more similarly connected with window
-length. Mean graph strength and layer relevance increased for summer layers as
-individuals became more connected with increasing window lengths (Figure
-\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). In contrast, mean graph strength
-and layer relevance was relatively stable for winter layers. Similarity of
-layers across habitat classes and between seasons (e.g. open summer compared to
-open winter) was variable across window lengths (Figure \@ref(fig:winlen)c).
-Connective redundancy increased marginally with increasing window length. These
-results suggest that an increasing window length, especially for the summer
-season, may be resulting in less precisely defined seasons that are not clearly
-capturing periods of aggregation and dissaggregation related to resource
-availability.
 

### 2020-02-14 paper/manuscript.Rmd
little mov perspective edits

@@
 multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019] (Mourier et al. 2019). Movement as a collective group
+processes [@Mourier_2019]. Movement as a collective group
 can reduce per capita predation risk via detection-dilution trade-offs and
@@
 represent individual movement frequency, and *interlayer edges* represent
-contact probability among individuals at a given node [@Mourier_2019] (Mourier
-et al. 2019). Although movement between fixed arrays is inherent, networks are
+contact probability among individuals at a given node [@Mourier_2019]. Although movement between fixed arrays is inherent, networks are
 not constructed based on continuous measures of dyadic or collective movement
@@
 metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further shed light on the role of movement as a driver
+association layers could further illuminate the role of movement as a driver
 of the social and spatial environments an individual experiences [@Webber_2018].
@@
 effects of habitat configuration on the formation of the social environment
-[@He_2019].
+[@He_2019; @Webber_2018].
 

### 2020-02-14 paper/manuscript.Rmd
conclusion edits

@@
 Habitat selection, the disproportionate use of available resources or landscape
-features by animals [@Manly_1993; @Boyce_1999], is a scale dependent process
+features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
 [@Mayor_2009]. Combined, social structure and habitat selection are intimately
@@
 reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection.
-For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviours.
+For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviors.
 
@@
 Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate novel analyses that vary social, spatial, and temporal
+ecology. We demonstrate the potential novel analyses that vary social, spatial, and temporal
 scale within a multilayer framework. In our caribou case study, we show that (1)
-multilayer social networks can be, but are not always, scale dependent, and (2)
+multilayer social networks can be, but are not always, scale-dependent, and (2)
 the use of multilayer networks could be useful for identifying habitat or
@@
 data is grounded in the context of observed animal social networks, as the
-scales we chose to explore (e.g., number of observations, sociality across space
-and time) are ones that can be observed as has traditionally been done. Thus, we
+scales we chose to explore, e.g., number of observations, sociality across space
+and time, are ones that can be observed as has traditionally been done in ethology. Thus, we
 highlight ways in which scale ought to be considered for both observed and
@@
 1. How do social phenotypes vary across social, temporal, and spatial scales and
-differentially influence fitness? Are some scales better predictors for
+at which scale might these influence fitness? Are some scales better predictors for
 different fitness metrics?

### 2020-02-14 paper/manuscript.Rmd
reflow
hab perspective wg edits

@@
 features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
-[@Mayor_2009]. Combined, social structure and habitat selection are intimately
-linked as individuals must share space to interact and the distribution of
+[@Mayor_2009]. Social structure and habitat selection are intimately
+linked: as individuals must share space to interact, and the distribution of
 resources influences group dynamics and home range size [@Webber_2018].
@@
 the habitat patches within the home range and (4) specific resources within a
-habitat patch. Moving past this hierarchical perspective, Mayor (2009)
-reviewed types of scale relevant in measurement of habitat selection and recommend using a continuum of scales for identifying characteristic scales of selection.
-For example, @Mayor_2007 showed caribou selection for shallow snow across all sales and used to a continuum of scales to avoid bias from narrowing the measurements to scales assumed to be associated with certain behaviors.
+habitat patch. Moving past this hierarchical perspective, Mayor (2009) reviewed
+types of scale relevant in measurement of habitat selection and recommend using
+a continuum of scales for identifying characteristic scales of selection. For
+example, @Mayor_2007 showed caribou select for shallow snow at all scales
+and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.
 
@@
 The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. Cougars
-had increased home range overlap in regions with high hunting opportunity, a
-proxy for resource richness [@Elbroch_2016]. Caribou showed seasonal differences
-in sociality, where social associations were high in winter and contrastingly
-low in summer when resource availability is homogenous [@Peigner_2019]. Bison
-(*Bison bison*) showed stronger habitat selection when group size was larger and
+distribution and phenology of resources and use of social information. Cougar
+home ranges overlapped more in regions with high hunting opportunity, a
+proxy for resource richness [@Elbroch_2016]. Caribou sociality differed between seasons, where social associations were stronger in winter and contrastingly
+low in summer when resource availability are more homogenous [@Peigner_2019]. Bison
+(*Bison bison*) showed stronger habitat selection in larger groups and
 avoidance of predation risk was a main factor contributing to their habitat
-selection [@Fortin_2009]. These examples are implicitly multilayered, comparing sociality across contexts of seasonality or spatial context. <!--Despite these, *missing multilayer approach*.-->
+selection [@Fortin_2009].
+These examples, comparing sociality and habitat selection across temporal or spatial contexts, are implicitly multilayer analyses.
+<!--Despite these, *missing multilayer approach*.-->
 
@@
 
-Multilayer networks can be used to explicitly consider habitat selection and sociality across scales.
-Animal social systems can be parsed by spatial contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
-The influence of resource phenology can be directly measured by differences in habitat selection and sociality across temporal layers.
-Habitat selection can be explicitly integrated using network layers defined by similarity of selection coefficients between individuals.
-These explicit integrations of habitat selection and sociality across social, spatial and temporal scales highlight the potential for novel insights from multilayer networks.
+Multilayer networks explicitly consider habitat selection and
+sociality across scales. Animal social systems can be parsed by spatial
+contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
+The effect of resource phenology can be directly measured by differences in
+habitat selection and sociality across temporal layers. Habitat selection can be
+explicitly integrated using network layers defined by similarity of selection
+coefficients between individuals. These explicit integrations of habitat
+selection and sociality across social, spatial and temporal scales highlight the
+potential for novel insights from multilayer networks.
 
@@
 Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate the potential novel analyses that vary social, spatial, and temporal
-scale within a multilayer framework. In our caribou case study, we show that (1)
-multilayer social networks can be, but are not always, scale-dependent, and (2)
-the use of multilayer networks could be useful for identifying habitat or
-season-specific social processes. Our analyses of social, spatial, and temporal
-scales in multilayer network framework highlight potential to identify scales at
-which different properties of layers within a multilayer network show the most
-variability. Furthermore, we discuss the potential integration of individual
-phenotypes and fitness, collective movement, and habitat selection for future
-analyses considering spatial ecology using multilayer networks.
+ecology. We demonstrate the potential novel analyses that vary social, spatial,
+and temporal scale within a multilayer framework. In our caribou case study, we
+show that (1) multilayer social networks can be, but are not always,
+scale-dependent, and (2) the use of multilayer networks could be useful for
+identifying habitat or season-specific social processes. Our analyses of social,
+spatial, and temporal scales in multilayer network framework highlight potential
+to identify scales at which different properties of layers within a multilayer
+network show the most variability. Furthermore, we discuss the potential
+integration of individual phenotypes and fitness, collective movement, and
+habitat selection for future analyses considering spatial ecology using
+multilayer networks.
 
@@
 scales we chose to explore, e.g., number of observations, sociality across space
-and time, are ones that can be observed as has traditionally been done in ethology. Thus, we
-highlight ways in which scale ought to be considered for both observed and
-remotely-sensed data when building social networks. Furthermore, GPS telemetry
-data provides a link between large scale landscape properties and fine scale
-social interactions as animal movement occurs across the landscape, and when
-taken into account with multiple individuals can indicate association patterns.
-Thus, a layer incorporating relocation data could be a great boon linking
-spatial and social layer in multilayer networks.
+and time, are ones that can be observed as has traditionally been done in
+ethology. Thus, we highlight ways in which scale ought to be considered for both
+observed and remotely-sensed data when building social networks. Furthermore,
+GPS telemetry data provides a link between large scale landscape properties and
+fine scale social interactions as animal movement occurs across the landscape,
+and when taken into account with multiple individuals can indicate association
+patterns. Thus, a layer incorporating relocation data could be a great boon
+linking spatial and social layer in multilayer networks.
+
 <!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
@@
 
-Silk et al. (2018) summarized some key multilayer questions in animal behaviour research.
-While these questions are important for linking animal behaviour and multilayer
-networks, we summarize our perspectives on the future of multilayer networks
-with an additional set of questions posed through the lens of spatial ecology
-that are relevant to the promise and problem of scale in mutlilayer networks:
+Silk et al. (2018) summarized some key multilayer questions in animal behaviour
+research. While these questions are important for linking animal behaviour and
+multilayer networks, we summarize our perspectives on the future of multilayer
+networks with an additional set of questions posed through the lens of spatial
+ecology that are relevant to the promise and problem of scale in mutlilayer
+networks:
 
 1. How do social phenotypes vary across social, temporal, and spatial scales and
-at which scale might these influence fitness? Are some scales better predictors for
-different fitness metrics?
-2. Why do individuals associate more strongly with certain conspecifics in some
-habitats? What, if any, is the role of movement in the context of habitat
-networks?
-3. How, and why, does the spatial scale of perception influence, e.g. auditory,
-visual, or chemotaxis, influence the  social environment? What is the role of
-memory, and by extension social and spatial cognition, as animals navigate their
-environment and make decisions about where to move next?
+at which scale might these influence fitness? Are some scales better predictors
+for different fitness metrics?
+
+2. Why do individuals associate more strongly
+with certain conspecifics in some habitats? What, if any, is the role of
+movement in the context of habitat networks?
+
+3. How, and why, does the spatial
+scale of perception influence, e.g. auditory, visual, or chemotaxis, influence
+the  social environment? What is the role of memory, and by extension social and
+spatial cognition, as animals navigate their environment and make decisions
+about where to move next?
 

### 2020-02-14 paper/manuscript.Rmd
hab persp intro

@@
 <!-- TODO: Gerard ‘openness’ paper -->
+Social structure and habitat selection are intimately
+linked: individuals must share space to interact and the distribution of
+resources influences group dynamics and home range size [@Webber_2018].
 Social structure is influenced by resource availability and seasonality
@@
 features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
-[@Mayor_2009]. Social structure and habitat selection are intimately
-linked: as individuals must share space to interact, and the distribution of
-resources influences group dynamics and home range size [@Webber_2018].
+[@Mayor_2009]. Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
+
 <!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
-Multilayer networks represent a novel framework for considering the influence of
-habitat selection and space use on sociality across scales.
 

### 2020-02-14 paper/manuscript.Rmd
rm johnson numbers

@@
 proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, (3)
-the habitat patches within the home range and (4) specific resources within a
-habitat patch. Moving past this hierarchical perspective, Mayor (2009) reviewed
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
+the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
+habitat patch. 
+Moving past this hierarchical perspective, Mayor (2009) reviewed
 types of scale relevant in measurement of habitat selection and recommend using
-a continuum of scales for identifying characteristic scales of selection. For
-example, @Mayor_2007 showed caribou select for shallow snow at all scales
+a continuum of scales for identifying characteristic scales of selection. 
+<!-- highlight this -->A continuum of scales allows xyz advantage
+
+For
+example, @Mayor_2007 showed caribou select for shallow snow at all scales and <!--what else higlight-->
 and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.

### 2020-02-14 paper/manuscript.Rmd
reflow

@@
 ## Habitat selection and space use
-<!-- TODO: Gerard ‘openness’ paper -->
-Social structure and habitat selection are intimately
-linked: individuals must share space to interact and the distribution of
-resources influences group dynamics and home range size [@Webber_2018].
-Social structure is influenced by resource availability and seasonality
-[@Peignier_2019], configuration [@He_2019] and fragmentation [@Banks_2007].
-Habitat selection, the disproportionate use of available resources or landscape
-features by animals [@Manly_1993; @Boyce_1999], is a scale-dependent process
-[@Mayor_2009]. Multilayer networks represent a novel framework for considering the influence of habitat selection and space use on sociality across scales.
+Social structure and habitat selection are intimately linked: individuals must
+share space to interact and the distribution of resources influences group
+dynamics and home range size [@Webber_2018]. Social structure is influenced by
+resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
+and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
+novel framework for considering the influence of habitat selection and space use
+on sociality across scales.
 
-<!--Animals select habitats at multiple scales ... (Mayor)  Mayor scale -->
+<!-- 
+TODO: Gerard ‘openness’ paper
 
-<!-- McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
+McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
 should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
 
-Mayor 2007 - scale paper
 MRSF Laforge paper 

### 2020-02-14 paper/manuscript.Rmd
add conclusion para todos

@@
 identifying habitat or season-specific social processes. Our analyses of social,
-spatial, and temporal scales in multilayer network framework highlight potential
+spatial, and temporal scales in a multilayer network framework highlight the potential
 to identify scales at which different properties of layers within a multilayer
@@
 
-<!-- Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->
+<!-- 
+TODO: Schneider 2001, Levin og,
+
+Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->
 

### 2020-02-14 paper/manuscript.Rmd
halfway edits hab sel perspective

@@
 the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
-habitat patch. 
-Moving past this hierarchical perspective, Mayor (2009) reviewed
-types of scale relevant in measurement of habitat selection and recommend using
-a continuum of scales for identifying characteristic scales of selection. 
-<!-- highlight this -->A continuum of scales allows xyz advantage
+habitat patch. <!-- examples of hierarchical hab sel Kie 2002-->
+Moving past this hierarchical perspective, Mayor (2007) emphasized the importance of considering a broad continuum of scales to reveal scale-dependent selection and avoid the bias of predefined scales assumed to be associated with certain behaviors.
+
+Then to Mayor 2009
+
+<!-- And more recent? -->
+
+Despite this, still not widely adopted McGarigal 2016
 
 For
-example, @Mayor_2007 showed caribou select for shallow snow at all scales and <!--what else higlight-->
-and by using a continuum of scales, avoided the bias of predefined scales assumed to be associated with certain behaviors.
+example, @Mayor_2007 showed caribou select for shallow snow at all scales 
+and by using a continuum of scales, .
 
 <!-- Relationship between sociality and habitat -->
-<!-- more from Webber, He, etc -->
 <!-- Merkle’s memory and patches for bison (and leaders) -->
@@
 distribution and phenology of resources and use of social information. Cougar
-home ranges overlapped more in regions with high hunting opportunity, a
-proxy for resource richness [@Elbroch_2016]. Caribou sociality differed between seasons, where social associations were stronger in winter and contrastingly
-low in summer when resource availability are more homogenous [@Peigner_2019]. Bison
-(*Bison bison*) showed stronger habitat selection in larger groups and
-avoidance of predation risk was a main factor contributing to their habitat
-selection [@Fortin_2009].
-These examples, comparing sociality and habitat selection across temporal or spatial contexts, are implicitly multilayer analyses.
-<!--Despite these, *missing multilayer approach*.-->
+(*Puma concolor*) home ranges overlapped more in regions with high hunting
+opportunity, a proxy for resource richness [@Elbroch_2016]. Caribou (*Rangifer
+tarandus*) sociality differed between seasons, where social associations were
+stronger in winter and contrastingly low in summer when resource availability
+are more homogenous [@Peigner_2019]. Bison (*Bison bison*) showed stronger
+habitat selection in larger groups and avoidance of predation risk was a main
+factor contributing to their habitat selection [@Fortin_2009]. These examples,
+comparing sociality and habitat selection across temporal or spatial contexts,
+are implicitly multilayer analyses.
 

### 2020-02-14 paper/manuscript.Rmd
update lcres and nobs results

@@
 
-<!-- TODO: make sure we clarify these are means of all individuals? -->
-<!-- TODO: discuss layer similarity for social threshold -->
-
 In general, individuals in multilayer networks became more connected as social
@@
 these habitats. Mean graph strength increased consistently in winter forest and
-open habitats. Mean graph strength in winter forage <!-- TODO: check this fig
-A/C similar lines--> Individuals in summer layers had consistent weak
-connections. Layer relevance was stable in winter for open and forest habitats
-but decreased for forage habitats (Figure \@ref(fig:lcres)b). Layer relevance
-was stable for all habitat classes in summer layers. Layer similarity was stable
-for forest and open, except for a sharp decrease in layer similarity in open at
-100 m and 250 m<!-- TODO: check this fig A/C similar lines--> (Figure
+open habitats. Mean graph strength in winter forage varied across landcover
+resolutions with an increase at 250 m and decrease at 500 m. Individuals in
+summer layers had consistent weak connections. Layer relevance was stable in
+winter for open and forest habitats but decreased for forage habitats (Figure
+\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
+layers. Layer similarity was stable for forest and open, except for a sharp
+decrease in layer similarity in open at 100 m and 250 m (Figure
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
@@
 individuals became more connected and metrics appeared to stabilize. Mean graph
-strength varied in winter layers becoming stable at ~200 m and remained
-consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
-winter layers increased between ~10 m and ~50 m observations, remaining stable
-with additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with
-fix for open/rerun --> Like coarse landcover resolution (Figure
-\@ref(fig:lcres)), low numbers of observations were not sufficient for capturing
-individuals in all contexts and therefore layer similarity could not be
-calculated below approximately <!--TODO: update these -->75 observations for
-forest, approximately 210 observations for open and approximately 300
-observations for forage (Figure \@ref(fig:nobs)c). Once sufficient observations
-were obtained, layer similarity stabilized for all three landcover classes at
-approximately 200 observations for forest and approximately 300 observations for
-open and forage landcover types. Connective redundancy increased dramatically
-between ~10 m and ~50 m observations before stabilizing with all new
-observations included (Figure \@ref(fig:nobs)d). Given the observed trend of
-these multilayer metrics stabilizing after a certain number of observations are
-included, the results suggest this sensitivity method could be useful for
-determining the number of observations necessary for sufficiently describing
-social dynamics across contexts.
+strength varied in winter layers at low number of observations, becoming stable
+at ~75 observations and was consistently weak in summer layers (Figure
+\@ref(fig:nobs)a). Layer relevance in winter layers increased between ~10 m and
+~100 m observations, remaining stable with additional observations (Figure
+\@ref(fig:nobs)b). Like coarse landcover resolution (Figure \@ref(fig:lcres)),
+low numbers of observations were not sufficient for capturing individuals in all
+contexts and therefore layer similarity could not be calculated below ~30
+observations for forest, approximately ~80 observations for open (Figure
+\@ref(fig:nobs)c). Layer similarity was not possible to calculate for forage
+layers because there were no connected individuals in summer forage. Once
+sufficient observations were obtained, layer similarity was relatively stable
+for forest and open layers. Connective redundancy increased dramatically between
+~10 m and ~50 m observations before stabilizing with all new observations
+included (Figure \@ref(fig:nobs)d). Given the observed trend of these multilayer
+metrics stabilizing after a certain number of observations are included, the
+results suggest this sensitivity method could be useful for determining the
+number of observations necessary for sufficiently describing social dynamics
+across contexts.
 

### 2020-02-14 paper/manuscript.Rmd
update nobs fig cap

@@
 C) Similarity of network layers across habitat classes and between seasons (e.g.
-open summer compared to open winter) was relatively consistent across number of observations for forest habitats.
-<!-- TODO: fix for open -->Note, open and forage habitats are not shown given no individuals interacted in the summer open and forage layers.
+open summer compared to open winter) was relatively consistent across number of observations for forest and open habitats.
+Note, forage habitats are not shown given no individuals interacted in the summer forage layer.
 D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.

### 2020-02-14 paper/manuscript.Rmd
replace winlen result

@@
 networks -->
+
+Mean graph strength and layer relevance increased for all summer layers as
+individuals became more connected with increasing window lengths (Figure
+\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Winter layers showed relatively
+stable mean graph strength and layer relevance. Layer similarity between seasons
+and across habitat layers increased consistently  (Figure \@ref(fig:winlen)c).
+Connective redundancy increased marginally with increasing window length (Figure
+\@ref(fig:winlen)d). These results suggest that an increasing window length,
+especially for the summer season, may be resulting in less precisely defined
+seasons that are not clearly capturing periods of aggregation and
+dissaggregation related to resource availability.
 

### 2020-02-15 paper/manuscript.Rmd
small edits

@@
 and temporal scale on multilayer processes. We also present perspectives on
-future development and application of scale in multilayer networks with respect
-to: habitat selection and space use; phenotypes and individual fitness; and
-movement ecology and collective movement. Effective integration of social and
+future development and applications of scale in multilayer networks with respect
+to: phenotypes and individual fitness, movement ecology and collective movement, and habitat selection and space use. Effective integration of social and
 spatial processes, including biologically meaningful scales, within the context
@@
 linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019;
-@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
-mutlilayer networks within the emerging integration of social and spatial
-ecology within the behavioural ecology literature.
+studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
+mutlilayer networks<!-- TODO: withinwithin--> in the emerging integration of
+social and spatial ecology within the behavioural ecology literature.
 
@@
 social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure \@ref(fig:socres))
-in different habitat types, having higher graph strength in
+individuals demonstrate dramatically different graph strength (Figure 
+\@ref(fig:socres)) in different habitat types, having higher graph strength in
 forage and open habitats where they can likely see each other and still interact
@@
 
-2. Why do individuals associate more strongly
-with certain conspecifics in some habitats? What, if any, is the role of
-movement in the context of habitat networks?
+2. Why do individuals associate more strongly with certain conspecifics in some
+habitats? What, if any, is the role of movement in the context of habitat
+networks?
 
-3. How, and why, does the spatial
-scale of perception influence, e.g. auditory, visual, or chemotaxis, influence
-the  social environment? What is the role of memory, and by extension social and
-spatial cognition, as animals navigate their environment and make decisions
-about where to move next?
+3. How, and why, does the spatial scale of perception influence, e.g. auditory,
+visual, or chemotaxis, influence the  social environment? What is the role of
+memory, and by extension social and spatial cognition, as animals navigate their
+environment and make decisions about where to move next?
 

### 2020-02-15 paper/manuscript.Rmd
e.g.

@@
 [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
-studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
+studies of animal behavior [@Silk_2018; @Finn_2019], although they have been
 used to describe multidimensional human social systems, complex transportation
@@
 Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
-Interlayer edges connect individuals to themselves across seasons and within habitat classes (eg.
+Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
 individual "A" in summer, forest and individual "A" in winter, forest).
@@
 [@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
-fixed rate, eg. every $x$ minutes or hours, continuously throughout the study
+fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
 period. We investigated the influence of the number of observations on resulting

### 2020-02-15 paper/manuscript.Rmd
social, spatial, temporal

@@
 [@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
-representing (i) different classes of individuals, e.g. male or female; (ii)
-types of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial
-areas, e.g. local or regional, or temporal windows, e.g. daily or seasonal
+representing (i) different classes of individuals, e.g. male or female, (ii)
+types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
+areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
 [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
@@
 social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the temporal or spatial scales associated
+novel understanding of variation in the social, spatial or temporal scales associated
 with social systems.
@@
 
-1. How do social phenotypes vary across social, temporal, and spatial scales and
+1. How do social phenotypes vary across social, spatial, and temporal scales and
 at which scale might these influence fitness? Are some scales better predictors

### 2020-02-15 paper/manuscript.Rmd
rm unnecessary cite

@@
 build a conceptual and analytical framework for scale-dependent multilayer
-networks and we apply this framework to a case study of caribou (*Rangifer
+networks, and we apply this framework to a case study of caribou (*Rangifer
 tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
@@
 perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness [@Webber_2018],
-movement ecology and collective movement [@Jolles_2019], and habitat selection
-and space use<!-- TODO: (REF)--> .
+networks with respect to phenotypes and individual fitness,
+movement ecology and collective movement, and habitat selection
+and space use.
 <!-- TODO: we answer the first question in the discussion, but not the second-->

### 2020-02-15 paper/manuscript.Rmd
edits spacetime cap

@@
 
-(ref:spacetime) Space-time diagram displaying variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including hyaena, passerine birds, sleepy lizards, and elephants.
+(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants.
 Spatial and temporal extent for social interactions, e.g.
-mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for most social interactions.
-The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must shared space to interact.
+mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions.
+The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact.
 By contrast, different species have potential for  greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.

### 2020-02-15 paper/manuscript.Rmd
summer and winter

@@
 individual nodes and two aspects (season and landcover). Two season
-elementary-layers (winter and summer) and three landcover elementary-layers
-(forest, forage, and open) combined for a total of six layers. Layers were
-composed of individuals represented as nodes and social associations represented
-as edges, for each season and landcover combination. Proximity-based social
+elementary-layers (summer and winter) and three landcover elementary-layers
+(forest, forage, and open) combined for a total of six layers. Single layers were
+composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
 network layers were generated using the R package `spatsoc` [@Robitaille_2019]
@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color.
-Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage).
+Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
 Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
@@
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-winter and summer forage because, at all landcover resolutions greater than 30
+summer and winter forage because, at all landcover resolutions greater than 30
 m, there were no individuals connected in the network layers. Individuals still

### 2020-02-15 paper/manuscript.Rmd
better edge descriptions

@@
 distribution of craters on the landscape varies meaning that access to
-vegetation in winter is highly variable for caribou. Caribou therefore have
+vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
 greater access to forage in snow-free seasons. We  partitioned data into two
@@
 applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
-all networks, nodes represented individuals, intralayer edges represented
-associations between individuals in a given habitat type and season, and
-interlayer edges represented connections between the same individuals across
-seasons and within habitat classes (Figure 2).
+all networks, individual caribou were represented as nodes, associations between
+individuals in a given habitat type and season were represented as intralayer
+edges, and connections between the same individuals across seasons and within
+habitat classes were represented as interlayer edges (Figure 2) .
 <!-- eg this is connecting contexts used to calculate layer similarity -->

### 2020-02-15 paper/manuscript.Rmd
net mets edits

@@
 We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals, importance of individual layers and the similarity of
+the role of individuals, importance of individual layers, and the similarity of
 different layers. To measure the role of individuals, we calculated degree
@@
 strength is the degree weighted by the strength of association, in this case
-SRI, in each layer-specific season and landcover context <!-- TODO: citation for
-graph strength?-->. Extending degree centrality, we calculated multidegree, the
-sum of degree centrality across layers, and neighbourhood, the sum of unique
-neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated
+SRI, in each layer-specific season and landcover context. Extending degree centrality, we calculated multidegree, the
+sum of degree centrality of individuals across layers, and neighbourhood, the sum of unique
+neighbours to each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
 the relevance and redundancy of layers by combining the multidegree and
-neighbourhood to calculate connective redundancy and layer relevance. Connective
+neighbourhood to calculate layer relevance and connective redundancy. Layer relevance is the proportion of neighbours present in each layer compared
+to the neighbourhood for each individual and connective
 redundancy is the proportion of neighbours repeated in multiple layers, and
-layer relevance is the proportion of neighbours present in each layer compared
-to the neighbourhood for each individual [@Berlingerio_2012]. Finally, we
+ [@Berlingerio_2012]. Finally, we
 calculated the similarity of layers between seasons, across landcover classes
-(e.g. winter open compared to summer open) using the Pearson correlation
+(e.g. summer open compared to winter open) using the Pearson correlation
 coefficient [@Br_dka_2018]. Network metrics were calculated using the R packages 

### 2020-02-15 paper/manuscript.Rmd
hereafter

@@
 (ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each indiviual is represented by a unique color.
 Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
@@
 
-We modified the spatial distance threshold required for group assignment using
-`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
+We modified the distance threshold, hereafter the social threshold, required for group assignment using
+`spatsoc` [@Robitaille_2019] and re-assigned groups at incremental
 distances between 5 - 500 m. For example, at the finest social scale, only

### 2020-02-15 paper/manuscript.Rmd
reflow
include years

@@
 
-We modified the distance threshold, hereafter the social threshold, required for group assignment using
-`spatsoc` [@Robitaille_2019] and re-assigned groups at incremental
-distances between 5 - 500 m. For example, at the finest social scale, only
-individuals within 5 m of one another were considered in the same group, whereas
-at the coarsest social scale, individuals within 500 m of one another were
-considered in the same group. We assumed these scales represented visual (short distance) to auditory (long distance) sensory modalities of caribou.
+We modified the distance threshold, hereafter the social threshold, required for
+group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
+incremental distances between 5 - 500 m. For example, at the finest social
+scale, only individuals within 5 m of one another were considered in the same
+group, whereas at the coarsest social scale, individuals within 500 m of one
+another were considered in the same group. We assumed these scales represented
+visual (short distance) to auditory (long distance) sensory modalities of
+caribou.
 
@@
 position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for winter (starting at 1
-January) and summer (starting at 3 August). The position of the time window was
+window varied from 40-100 days using a fixed start day for summer (starting at 3 August 2017) and winter (starting at 1
+January 2018). The position of the time window was
 shifted by 1-48 days, using a fixed time window length of 48 days. These new
 time windows were iteratively used to partition data into two discrete seasons
-(winter, summer) and generate multilayer networks.
+(summer and winter) and generate multilayer networks.
 

### 2020-02-15 paper/manuscript.Rmd
clarify nobs

@@
 ### Temporal scale
+#### Number of observations
+Studies of social network analysis vary in the number and frequency of
+observations as well as the data collection technique used to generate networks
+[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
+fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
+period. Fix rate is a reflection of number of observations an individual would
+have been observed and recorded in traditional ethological studies.We
+investigated the influence of the number of observations on resulting multilayer
+networks. We randomly selected a maximum 500 timesteps for each season to
+represent all possible observations. We regenerated multilayer networks and
+calculated associations of individuals with 25 additional observations at each
+iteration. Subsequent iterations included the previous set of observations to
+mimic collection of observational data. <!-- TODO: bah conclude / this sentence
+falls off a cliff -->
+
 #### Time window length and position
@@
 (summer and winter) and generate multilayer networks.
-
-#### Number of observations
-Studies of social network analysis vary in the number and frequency of
-observations as well as the data collection technique used to generate networks
-[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
-fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
-period. We investigated the influence of the number of observations on resulting
-multilayer networks. We randomly selected 500 timesteps and iteratively included
-25 additional observations, regenerating the multilayer network and calculating
-associations of individuals. Subsequent iterations included the previous set of
-observations to mimic collection of observational data. <!-- TODO: bah conclude
-/ this sentence falls off a cliff -->
 

### 2020-02-15 paper/manuscript.Rmd
reflow
social threshold results

@@
 position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for summer (starting at 3 August 2017) and winter (starting at 1
-January 2018). The position of the time window was
-shifted by 1-48 days, using a fixed time window length of 48 days. These new
-time windows were iteratively used to partition data into two discrete seasons
-(summer and winter) and generate multilayer networks.
+window varied from 40-100 days using a fixed start day for summer (starting at 3
+August 2017) and winter (starting at 1 January 2018). The position of the time
+window was shifted by 1-48 days, using a fixed time window length of 48 days.
+These new time windows were iteratively used to partition data into two discrete
+seasons (summer and winter) and generate multilayer networks.
 
@@
 scale increased; however, this relationship varied by habitat type and season.
-As social scale increased, graph strength for winter networks increased rapidly
-between 5 m and 50 m thresholds, followed by a plateau, while graph strength for
-summer networks did not change as the social threshold increased (Figure
-\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
-50 m social thresholds, then did not change for any habitat types which suggests
+As social scale increased, mean graph strength for summer networks did not
+change as the social threshold increased, but graph strength in winter networks
+increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
+\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
+increased for winter networks between 5 and 50 m social thresholds, then did not
+change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
 the winter habitat layers captured most, if not all, of the potential
-connections an individual would have across these networks (Figure
-\@ref(fig:socres)b). Layer similarity (Figure \@ref(fig:socres)c) and connective
-redundancy (Figure \@ref(fig:socres)d) were relatively stable across social
-thresholds. Taken together, these results suggest the optimal 
-<!-- TODO: why optimal --> 
-social scale at which groups should be assigned is likely somewhere
-between ~20 - 100 m based on the rate at which network metrics stabilized. For
-ungulates, groups are often assigned based on 50 m threshold (Lingle 2003;
-Lesmeries et al. 2018; Peignier et al. 2019), suggesting that given similar
-quantities of data, ~50 m is likely an appropriate social scale for generating
-social networks in caribou and similar species.
-<!-- TODO: missing summer relevance .. the actual value of layer sim?-->
+connections an individual would have across these networks. Layer similarity was
+not very strong for any habitat type, indicating that summer and winter networks
+are only weakly correlated. Furthermore, layer similarity in open habitats
+showed more variation as social threshold increased compared to forage and
+forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
+relatively stable across social thresholds, especially after 50 m (Figure
+\@ref(fig:socres)d). Taken together, these results suggest the optimal social
+scale at which groups should be assigned is likely somewhere between ~20 - 100 m
+based on the rate at which network metrics stabilized. For ungulates, groups are
+often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
+is likely an appropriate social scale for generating social networks in caribou
+and similar species.
 

### 2020-02-15 paper/manuscript.Rmd
landcover res results

@@
 
-Increasing landcover resolution resulted in a decreased proportion of forage, a
+Increasing landcover resolution resulted in a decreased availability of forage, a
 rare and patchy habitat, and corresponding low connectivity of individuals in
-these habitats. Mean graph strength increased consistently in winter forest and
-open habitats. Mean graph strength in winter forage varied across landcover
-resolutions with an increase at 250 m and decrease at 500 m. Individuals in
-summer layers had consistent weak connections. Layer relevance was stable in
-winter for open and forest habitats but decreased for forage habitats (Figure
-\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
-layers. Layer similarity was stable for forest and open, except for a sharp
+these habitats. Individuals in
+summer layers had consistent weak connections (Figure
+\@ref(fig:lcres)a). Mean graph strength increased consistently in winter forest and
+open habitats but varied in winter forage varied across landcover
+resolutions with an increase at 250 m and decrease at 500 m (Figure
+\@ref(fig:lcres)a).  Layer relevance was stable for all habitat classes in summer
+layers; layer relevance was significantly higher in winter and stable in open and forest habitats but decreased for forage habitats (Figure
+\@ref(fig:lcres)b).
+<!--This pattern during the winter indicates that individuals had fewer neighbours in forage habitat habitats compared to their overall neighbourhood across habitats, likely due to the patchy nature of forage-->Layer similarity was low but stable for forest and open, except for a sharp
 decrease in layer similarity in open at 100 m and 250 m (Figure
@@
 m, there were no individuals connected in the network layers. Individuals still
-used forage habitats but given a lower availability due to increasing landcover
-resolution, at a much lower rate. Connective redundancy slightly decreased as
-landcover resolution increased (Figure \@ref(fig:lcres)d). These results
+used forage habitats, but given the lower availability due to increasing landcover
+resolution, at a much lower rate. Connective redundancy was moderately high but decreased slightly as
+landcover resolution increased, indicating that many neighbours were the same between layers, but the proportion of neighbours in each layer slightly decreased at increasing landcover resolutions (Figure \@ref(fig:lcres)d).
+Overall, these results
 indicate the importance of matching landcover resolution to scale of selection
 as well as ensuring the landcover product used has a resolution fine enough to
-detect landscape features and habitats relevant to study species.
+detect landscape features and habitats relevant to study species, such as important patchy and rare habitats.
 

### 2020-02-15 paper/manuscript.Rmd
winpos results

@@
 
-Mean graph strength and layer relevance increased for all summer layers as
-individuals became more connected with increasing window lengths (Figure
-\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Winter layers showed relatively
-stable mean graph strength and layer relevance. Layer similarity between seasons
-and across habitat layers increased consistently  (Figure \@ref(fig:winlen)c).
-Connective redundancy increased marginally with increasing window length (Figure
-\@ref(fig:winlen)d). These results suggest that an increasing window length,
-especially for the summer season, may be resulting in less precisely defined
-seasons that are not clearly capturing periods of aggregation and
-dissaggregation related to resource availability.
+Some multilayer network metrics were strongly influenced by the length of the time window.
+Mean graph strength was weak but became slightly stronger with increasing time window length during the summer, but the higher mean graph strength during the winter showed a slight increase then decrease with increasing winter length (Figure \@ref(fig:winlen)a).
+Layer relevance increased for all summer layers as individuals became more connected with increasing window lengths, but winter layers showed relatively stable but high layer relevance (Figure \@ref(fig:winlen)b).
+This pattern indicates that the proportion of neighbours that were the same across layers increased with a longer time frame during the summer, butthere were a high proportion of neighbors that remained the same across layers during the winter, regardless of time length.
+Furthermore, though the layers were generally not very similar between the summer and winter, the length of the time window created slight variability in this metric, particularly for forage and open habitat types (Figure \@ref(fig:winlen)c).
+Connective redundancy increased marginally with increasing window length, indicating that the proportions of neighbours that were the same across layers, though relatively high in general, slightly increased when time length was greater (Figure \@ref(fig:winlen)d).
+These results suggest that an increasing window length, especially for the summer season, may be resulting in less precisely defined seasons that are not clearly capturing periods of aggregation and dissaggregation related to resource availability.
 
-Moving window positions defining seasons showed an increase in connectivity of
-individuals in summer layers. Graph strength increased at time window position
+Moving window positions defining seasons showed some dramatic changes in the multilayer network metrics as the seasons were redefined. Graph strength increased at time window position
 ~20 for summer and winter layers  and, while summer layers continued to
@@
 position ~35 (Figure \@ref(fig:winpos)a). Layer relevance increased across
-moving window positions for summer layers and was relatively stable for winter
-layers (Figure \@ref(fig:winpos)b). These results indicate slight decreasing
-connectivity and increased connectivity in summer layers at shifted winter time
+moving window positions for summer layers and slightly decreased for winter
+layers (Figure \@ref(fig:winpos)b). These results indicate increased connectivity in summer layers and slightly decreasing connectivity at shifted winter time
 windows. Layer similarity was relatively stable across moving window positions
@@
 (Figure \@ref(fig:winpos) c). Connective redundancy showed a marginal increase
-with increasing window position (Figure \@ref(fig:winpos) d). Similar to window
+with increasing window position indicating individuals had more of the same neighbours in each habitat network (Figure \@ref(fig:winpos) d). Similar to window
 length, changing the position of the time window in this case results in a
 mismatch between expected periods of resource seasonality and corresponding
-sociality, highlighting the importance of carefully selecting temporal scale of
+sociality, particularly for the summer, highlighting the importance of carefully selecting temporal scale of
 analysis.

### 2020-02-15 paper/manuscript.Rmd
fix double space
nobs results

@@
 individuals became more connected and metrics appeared to stabilize. Mean graph
-strength varied in winter layers at low number of observations, becoming stable
-at ~75 observations and was consistently weak in summer layers (Figure
-\@ref(fig:nobs)a). Layer relevance in winter layers increased between ~10 m and
-~100 m observations, remaining stable with additional observations (Figure
-\@ref(fig:nobs)b). Like coarse landcover resolution (Figure \@ref(fig:lcres)),
-low numbers of observations were not sufficient for capturing individuals in all
-contexts and therefore layer similarity could not be calculated below ~30
-observations for forest, approximately ~80 observations for open (Figure
-\@ref(fig:nobs)c). Layer similarity was not possible to calculate for forage
-layers because there were no connected individuals in summer forage. Once
-sufficient observations were obtained, layer similarity was relatively stable
-for forest and open layers. Connective redundancy increased dramatically between
-~10 m and ~50 m observations before stabilizing with all new observations
-included (Figure \@ref(fig:nobs)d). Given the observed trend of these multilayer
-metrics stabilizing after a certain number of observations are included, the
-results suggest this sensitivity method could be useful for determining the
-number of observations necessary for sufficiently describing social dynamics
-across contexts.
+strength was consistently weak in summer layers but varied in winter layers at
+low number of observations, becoming stable at ~75 observations (Figure
+\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
+winter layers increased between approximately 10  and 100  observations,
+remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
+coarse landcover resolution (Figure 4), low numbers of observations were not
+sufficient for capturing individuals in all contexts and therefore layer
+similarity could not be calculated below ~30 observations for forest,
+approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
+similarity was not possible to calculate for forage layers because there were no
+connected individuals in summer forage. Once sufficient observations were
+obtained, layer similarity showed some variability with increasing numbers of
+observations for forest and was relatively stable in open layers. Connective
+redundancy increased dramatically between ~10 and ~50 observations before
+stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
+Given the observed trend of these multilayer metrics stabilizing after a certain
+number of observations are included, the results suggest this sensitivity method
+could be useful for determining the number of observations necessary for
+sufficiently describing social dynamics across contexts.
 

### 2020-02-15 paper/manuscript.Rmd
reflow

@@
 
-Increasing landcover resolution resulted in a decreased availability of forage, a
-rare and patchy habitat, and corresponding low connectivity of individuals in
-these habitats. Individuals in
-summer layers had consistent weak connections (Figure
-\@ref(fig:lcres)a). Mean graph strength increased consistently in winter forest and
-open habitats but varied in winter forage varied across landcover
+Increasing landcover resolution resulted in a decreased availability of forage,
+a rare and patchy habitat, and corresponding low connectivity of individuals in
+these habitats. Individuals in summer layers had consistent weak connections
+(Figure \@ref(fig:lcres)a). Mean graph strength increased consistently in winter
+forest and open habitats but varied in winter forage varied across landcover
 resolutions with an increase at 250 m and decrease at 500 m (Figure
 \@ref(fig:lcres)a). Layer relevance was stable for all habitat classes in summer
-layers; layer relevance was significantly higher in winter and stable in open and forest habitats but decreased for forage habitats (Figure
-\@ref(fig:lcres)b).
-<!--This pattern during the winter indicates that individuals had fewer neighbours in forage habitat habitats compared to their overall neighbourhood across habitats, likely due to the patchy nature of forage-->Layer similarity was low but stable for forest and open, except for a sharp
-decrease in layer similarity in open at 100 m and 250 m (Figure
+layers; layer relevance was significantly higher in winter and stable in open
+and forest habitats but decreased for forage habitats (Figure
+\@ref(fig:lcres)b). <!--This pattern during the winter indicates that
+individuals had fewer neighbours in forage habitat habitats compared to their
+overall neighbourhood across habitats, likely due to the patchy nature of
+forage-->Layer similarity was low but stable for forest and open, except for a
+sharp decrease in layer similarity in open at 100 m and 250 m (Figure
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
@@
 m, there were no individuals connected in the network layers. Individuals still
-used forage habitats, but given the lower availability due to increasing landcover
-resolution, at a much lower rate. Connective redundancy was moderately high but decreased slightly as
-landcover resolution increased, indicating that many neighbours were the same between layers, but the proportion of neighbours in each layer slightly decreased at increasing landcover resolutions (Figure \@ref(fig:lcres)d).
-Overall, these results
-indicate the importance of matching landcover resolution to scale of selection
-as well as ensuring the landcover product used has a resolution fine enough to
-detect landscape features and habitats relevant to study species, such as important patchy and rare habitats.
+used forage habitats, but given the lower availability due to increasing
+landcover resolution, at a much lower rate. Connective redundancy was moderately
+high but decreased slightly as landcover resolution increased, indicating that
+many neighbours were the same between layers, but the proportion of neighbours
+in each layer slightly decreased at increasing landcover resolutions (Figure
+\@ref(fig:lcres)d). Overall, these results indicate the importance of matching
+landcover resolution to scale of selection as well as ensuring the landcover
+product used has a resolution fine enough to detect landscape features and
+habitats relevant to study species, such as important patchy and rare habitats.
 
@@
 
-Some multilayer network metrics were strongly influenced by the length of the time window.
-Mean graph strength was weak but became slightly stronger with increasing time window length during the summer, but the higher mean graph strength during the winter showed a slight increase then decrease with increasing winter length (Figure \@ref(fig:winlen)a).
-Layer relevance increased for all summer layers as individuals became more connected with increasing window lengths, but winter layers showed relatively stable but high layer relevance (Figure \@ref(fig:winlen)b).
-This pattern indicates that the proportion of neighbours that were the same across layers increased with a longer time frame during the summer, butthere were a high proportion of neighbors that remained the same across layers during the winter, regardless of time length.
-Furthermore, though the layers were generally not very similar between the summer and winter, the length of the time window created slight variability in this metric, particularly for forage and open habitat types (Figure \@ref(fig:winlen)c).
-Connective redundancy increased marginally with increasing window length, indicating that the proportions of neighbours that were the same across layers, though relatively high in general, slightly increased when time length was greater (Figure \@ref(fig:winlen)d).
-These results suggest that an increasing window length, especially for the summer season, may be resulting in less precisely defined seasons that are not clearly capturing periods of aggregation and dissaggregation related to resource availability.
+Some multilayer network metrics were strongly influenced by the length of the
+time window. Mean graph strength was weak but became slightly stronger with
+increasing time window length during the summer, but the higher mean graph
+strength during the winter showed a slight increase then decrease with
+increasing winter length (Figure \@ref(fig:winlen)a). Layer relevance increased
+for all summer layers as individuals became more connected with increasing
+window lengths, but winter layers showed relatively stable but high layer
+relevance (Figure \@ref(fig:winlen)b). This pattern indicates that the
+proportion of neighbours that were the same across layers increased with a
+longer time frame during the summer, butthere were a high proportion of
+neighbors that remained the same across layers during the winter, regardless of
+time length. Furthermore, though the layers were generally not very similar
+between the summer and winter, the length of the time window created slight
+variability in this metric, particularly for forage and open habitat types
+(Figure \@ref(fig:winlen)c). Connective redundancy increased marginally with
+increasing window length, indicating that the proportions of neighbours that
+were the same across layers, though relatively high in general, slightly
+increased when time length was greater (Figure \@ref(fig:winlen)d). These
+results suggest that an increasing window length, especially for the summer
+season, may be resulting in less precisely defined seasons that are not clearly
+capturing periods of aggregation and dissaggregation related to resource
+availability.
 
-Moving window positions defining seasons showed some dramatic changes in the multilayer network metrics as the seasons were redefined. Graph strength increased at time window position
-~20 for summer and winter layers and, while summer layers continued to
-increase, winter layers showed a decrease in graph strength at time window
-position ~35 (Figure \@ref(fig:winpos)a). Layer relevance increased across
-moving window positions for summer layers and slightly decreased for winter
-layers (Figure \@ref(fig:winpos)b). These results indicate increased connectivity in summer layers and slightly decreasing connectivity at shifted winter time
-windows. Layer similarity was relatively stable across moving window positions
-except for a sharp decline at window position ~28 in forage and open layers
-(Figure \@ref(fig:winpos) c). Connective redundancy showed a marginal increase
-with increasing window position indicating individuals had more of the same neighbours in each habitat network (Figure \@ref(fig:winpos) d). Similar to window
-length, changing the position of the time window in this case results in a
-mismatch between expected periods of resource seasonality and corresponding
-sociality, particularly for the summer, highlighting the importance of carefully selecting temporal scale of
-analysis.
+Moving window positions defining seasons showed some dramatic changes in the
+multilayer network metrics as the seasons were redefined. Graph strength
+increased at time window position ~20 for summer and winter layers and, while
+summer layers continued to increase, winter layers showed a decrease in graph
+strength at time window position ~35 (Figure \@ref(fig:winpos)a). Layer
+relevance increased across moving window positions for summer layers and
+slightly decreased for winter layers (Figure \@ref(fig:winpos)b). These results
+indicate increased connectivity in summer layers and slightly decreasing
+connectivity at shifted winter time windows. Layer similarity was relatively
+stable across moving window positions except for a sharp decline at window
+position ~28 in forage and open layers (Figure \@ref(fig:winpos) c). Connective
+redundancy showed a marginal increase with increasing window position indicating
+individuals had more of the same neighbours in each habitat network (Figure
+\@ref(fig:winpos) d). Similar to window length, changing the position of the
+time window in this case results in a mismatch between expected periods of
+resource seasonality and corresponding sociality, particularly for the summer,
+highlighting the importance of carefully selecting temporal scale of analysis.
 

### 2020-02-15 paper/manuscript.Rmd
forage, forest, open

@@
 elementary-layers (summer and winter) and three landcover elementary-layers
-(forest, forage, and open) combined for a total of six layers. Single layers were
+(forage, forest, and open) combined for a total of six layers. Single layers were
 composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
@@
 (ref:socres) Varying scale in social threshold.
-For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength across individuals showed an increase for winter network layers while summer network layers had consistently weak connections.
@@
 (ref:lcres) Varying spatial scale in landcover resolution.
-For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
@@
 (ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers.
@@
 (ref:winlen) Varying temporal scale in time window length.
-For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength across individuals was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
@@
 (ref:winpos) Varying temporal scale in time window position.
-For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open).
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
@@
 to assess the role of scale in predicting multilayer networks. As one might
-expect, we found increasing spatial scale results in saturation of potential
-social connections (Figure 3), while increasing temporal scale had little effect
-on habitat-specific networks (Figure 5). Another potential application would be
+expect, we found increasing social threshold results in saturation of potential
+social connections (Figure \@ref(fig:socres)), while increasing temporal scale had little effect
+<!-- TODO:.........-->
+on habitat-specific networks (Figure \@ref(fig:)). Another potential application would be
 to generate social networks during times when animals are engaged in different

### 2020-02-15 paper/manuscript.Rmd
fin caps

@@
 investigated the influence of the number of observations on resulting multilayer
-networks. We randomly selected a maximum 500 timesteps for each season to
+networks. We randomly selected a maximum 485 timesteps for each season to
 represent all possible observations. We regenerated multilayer networks and
 calculated associations of individuals with 25 additional observations at each
-iteration. Subsequent iterations included the previous set of observations to
+iteration (10 - 485 observations). Subsequent iterations included the previous set of observations to
 mimic collection of observational data. <!-- TODO: bah conclude / this sentence
@@
 For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength of individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
-Individuals in summer layers had consistent weak connections.
+A) Mean graph strength of individuals in summer layers had consistent weak connections.
+Individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
 B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
 C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) was relatively stable for forest and open, except for a sharp decrease in open at 100 m and 250 m.
-Note that layer similarity in summer forage is not shown because individuals did not interact at landcover resolutions greater than 30 m and therefore layer similarity could not be calculated.
+open summer compared to open winter) orage and forest habitats but showed more variation in open habitats with increasing social thresholds.
+Note that layer similarity in forage is not shown because individuals did not interact at landcover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
 D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
@@
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 100 observations and remained weak throughout for summer layers.
-B) Mean layer relevance across individuals increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing.
-Summer layers had consistent low layer relevance.
+A) Mean graph strength across individuals remained weak throughout for summer layers and varied for winter layers becoming relatively stable by 100 observations.
+B) Mean layer relevance across individuals in summer layers had consistent low layer relevance but increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing.
 C) Similarity of network layers across habitat classes and between seasons (e.g.
@@
 For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
-Summer layers an increase in strength for open and forage habitats.
-B) Mean layer relevance was stable for winter layers and increased for summer layers across habitat classes.
+A) Mean graph strength across individuals in summer layers was weak but stable across increasing lengths of time except for a slight increase in strength for open and forage habitats when the season lasted more than 70 days.
+Mean graph strength was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
+B) Mean layer relevance increased for summer layers across habitat classes and was stable for winter layers.
 C) Similarity of layers across habitat classes and between seasons (e.g.
-open summer compared to open winter) was relatively stable.
+open summer compared to open winter) was variable with increasing window lengths, particularly for forage and open habitat types.
 D) Mean connective redundancy across individuals increased marginally with increasing window length.
@@
 A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
-B) Mean layer relevance slightly decreased for winter layers and increased for summer layers.
+B) Mean layer relevance increased for summer layers and slightly decreased for winter layers.
 C) Similarity of layers across habitat classes and between seasons (e.g.
@@
 linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
-mutlilayer networks<!-- TODO: withinwithin--> in the emerging integration of
+studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role of scale and 
+mutlilayer networks in the emerging integration of
 social and spatial ecology within the behavioural ecology literature.

### 2020-02-15 paper/manuscript.Rmd
reflow

@@
 occurs over brief time periods [e.g. @Carter_2015], whereas social association
-represents shared space use by members of the same social group [Figure 1,
-@Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO: something broken here?? -->
-Further, for social interactions or associations to occur individuals must share
-space, and thus have overlapping home ranges [@VanderWal_2014]. In the context
-of the social environment, home range overlap is an example of how animals share
-space over coarser spatial and temporal scales (e.g. Piza-Roca et al. 2018).
-Although the social environment clearly scales spatially and temporally, it
-remains unclear whether coarser scales of sociality, including social
-association and home range overlap, vary predictably with social interaction
-[@Castles_2014;
+represents shared space use by members of the same social group [Figure
+\@ref(fig:spacetime), @Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO:
+something broken here?? --> Further, for social interactions or associations to
+occur individuals must share space, and thus have overlapping home ranges
+[@VanderWal_2014]. In the context of the social environment, home range overlap
+is an example of how animals share space over coarser spatial and temporal
+scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
+scales spatially and temporally, it remains unclear whether coarser scales of
+sociality, including social association and home range overlap, vary predictably
+with social interaction [@Castles_2014;
 @Farine_2015a]. Thus, we define social scale as the type of social relationship
@@
 strength is the degree weighted by the strength of association, in this case
-SRI, in each layer-specific season and landcover context. Extending degree centrality, we calculated multidegree, the
-sum of degree centrality of individuals across layers, and neighbourhood, the sum of unique
-neighbours to each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
+SRI, in each layer-specific season and landcover context. Extending degree
+centrality, we calculated multidegree, the sum of degree centrality of
+individuals across layers, and neighbourhood, the sum of unique neighbours to
+each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
 the relevance and redundancy of layers by combining the multidegree and
-neighbourhood to calculate layer relevance and connective redundancy. Layer relevance is the proportion of neighbours present in each layer compared
-to the neighbourhood for each individual and connective
-redundancy is the proportion of neighbours repeated in multiple layers, and
- [@Berlingerio_2012]. Finally, we
+neighbourhood to calculate layer relevance and connective redundancy. Layer
+relevance is the proportion of neighbours present in each layer compared to the
+neighbourhood for each individual and connective redundancy is the proportion of
+neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
 calculated the similarity of layers between seasons, across landcover classes
@@
 calculated associations of individuals with 25 additional observations at each
-iteration (10 - 485 observations). Subsequent iterations included the previous set of observations to
-mimic collection of observational data. <!-- TODO: bah conclude / this sentence
-falls off a cliff -->
+iteration (10 - 485 observations). Subsequent iterations included the previous
+set of observations to mimic collection of observational data.
 
@@
 # Scale in multilayer networks in practice: case study results and discussion
-<!-- TODO: Add intro/general to results? with mention figures are means of inds-->
+<!-- TODO: Add intro/general to results?-->
 
@@
 have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015] With the advancement of
+vocalization and olfactory signals [@Carter_2015]. With the advancement of
 biologging technology, we have the ability to record social interactions that do
@@
 forage and open habitats where they can likely see each other and still interact
-with visual cues than in forest habitats. Varying social scales can have
+with visual cues unlike in forest habitats. Varying social scales can have
 different fitness repercussions for individuals. Rhesus macaques (*Macaca
@@
 group members [@Jolles_2019]. In our case study, we integrate proximity based
-social networks that inherently rely on animal collective movement and, in
+social networks that inherently rely on animal collective movement, and, in
 general, we found that movement is likely an important mechanism driving social

### 2020-02-15 paper/manuscript.Rmd
fix hard coded figure numbers

@@
 edges, and connections between the same individuals across seasons and within
-habitat classes were represented as interlayer edges (Figure 2) .
+habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
 <!-- eg this is connecting contexts used to calculate layer similarity -->
@@
 remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
-coarse landcover resolution (Figure 4), low numbers of observations were not
-sufficient for capturing individuals in all contexts and therefore layer
-similarity could not be calculated below ~30 observations for forest,
-approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
+coarse landcover resolution (Figure \@ref(fig:lcres)), low numbers of
+observations were not sufficient for capturing individuals in all contexts and
+therefore layer similarity could not be calculated below ~30 observations for
+forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
 similarity was not possible to calculate for forage layers because there were no

### 2020-02-15 paper/manuscript.Rmd
comment out confusing

@@
 linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role of scale and 
-mutlilayer networks in the emerging integration of
-social and spatial ecology within the behavioural ecology literature.
+studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
+@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and mutlilayer
+networks in the emerging integration of social and spatial ecology within the
+behavioural ecology literature.
 
@@
 expect, we found increasing social threshold results in saturation of potential
-social connections (Figure \@ref(fig:socres)), while increasing temporal scale had little effect
-<!-- TODO:.........-->
-on habitat-specific networks (Figure \@ref(fig:)). Another potential application would be
+social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
+on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
 to generate social networks during times when animals are engaged in different

### 2020-02-15 paper/manuscript.Rmd
add kie

@@
 @Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
-the geographical range of a species, the home range of an individual, the habitat patches within the home range and specific resources within a
-habitat patch. <!-- examples of hierarchical hab sel Kie 2002-->
+(1) the geographical range of a species, (2) the home range of an individual, the (3) habitat patches within the home range and (4) specific resources within a
+habitat patch.
+Kie et al.
+[-@Kie_2002] found that, independently, third order of selection was insufficient for capturing landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
 Moving past this hierarchical perspective, Mayor (2007) emphasized the importance of considering a broad continuum of scales to reveal scale-dependent selection and avoid the bias of predefined scales assumed to be associated with certain behaviors.

### 2020-02-15 paper/manuscript.Rmd
add mcgarigal

@@
 proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
-(1) the geographical range of a species, (2) the home range of an individual, the (3) habitat patches within the home range and (4) specific resources within a
-habitat patch.
-Kie et al.
-[-@Kie_2002] found that, independently, third order of selection was insufficient for capturing landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the importance of considering a broad continuum of scales to reveal scale-dependent selection and avoid the bias of predefined scales assumed to be associated with certain behaviors.
-
-Then to Mayor 2009
-
-<!-- And more recent? -->
-
-Despite this, still not widely adopted McGarigal 2016
-
-For
-example, @Mayor_2007 showed caribou select for shallow snow at all scales 
-and by using a continuum of scales, .
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, the
+(3) habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Moving past this hierarchical perspective, Mayor (2007) emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviors. Despite animals selecting for different landscape attributes
+at different scales [@Mayor_2009], the use of multiscale analyses for habitat
+selection is still critically lacking [@McGarigal_2016].
 
@@
 
-Multilayer networks explicitly consider habitat selection and
+Multilayer networks can be used to explicitly consider habitat selection and
 sociality across scales. Animal social systems can be parsed by spatial

### 2020-02-15 paper/manuscript.Rmd
weak

@@
 
-<!--
-how to combine moving forward
-in areas of high selection/low selection or favorable/unfavorable habitat
-combined with seasonality
-
-in our case study, we looked at increase spatial scales of landcover metrics
-
-we could define layers of the multilayer network according to home range overlap 
-instead of specific associations
-looking at broader temporal scales and coarser spatial resolutions
--->
-
+<!-- TODO: weak -->
 Multilayer networks can be used to explicitly consider habitat selection and
@@
 contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
-The effect of resource phenology can be directly measured by differences in
+The effect of seasonality of resources can can be directly measured by differences in
 habitat selection and sociality across temporal layers. Habitat selection can be

### 2020-02-15 paper/manuscript.Rmd
add corresponding email

@@
 title: The problem and promise of scale in multilayer animal social networks
-author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
-date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
+author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
+date: |
+  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
+  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
+  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
 output:
   # github_document
-  # bookdown::pdf_document2:
-  #    number_sections: true
-  bookdown::word_document2:
-    reference_docx: template.docx
-# bibliography: ../references/knitcite.bib
+  bookdown::pdf_document2:
+     number_sections: true
+     toc: false
+  # bookdown::word_document2:
+  #   reference_docx: template.docx
+bibliography: ../references/knitcite.bib
 ---
+
+\newpage
 

### 2020-02-15 paper/manuscript.Rmd
mv figures all to bottom
dont let figures into references
add most of missing refs

@@
 occur individuals must share space, and thus have overlapping home ranges
-[@VanderWal_2014]. In the context of the social environment, home range overlap
+[@Vander_Wal_2013]. In the context of the social environment, home range overlap
 is an example of how animals share space over coarser spatial and temporal
@@
 <!-- TODO: citations? -->
-
-```{r spacetime, fig.cap='(ref:spacetime)'}
-knitr::include_graphics('../graphics/figure1.png')
-```
 
@@
 individual "A" in summer, forest and individual "A" in winter, forest).
-
-```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-2.png')
-```
 
@@
 
-```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-spatialthreshold.png')
-```
-
 <!-- Figure: metrics by landcover resolution -->
@@
 
-```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lcres.png')
-```
-
 <!-- Figure: metrics by number of observations -->
@@
 D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
-
-```{r nobs, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-nobs.png')
-```
 
@@
 
-```{r winlen, fig.cap='(ref:winlen)'}
-knitr::include_graphics('../graphics/figure-winlength.png')
-```
-
 <!-- Figure: Window position -->
@@
 D) Mean connective redundancy across individuals increased marginally with advancing time window position.
-
-```{r winpos, fig.cap='(ref:winpos)'}
-knitr::include_graphics('../graphics/figure-winpos.png')
-```
 
@@
 emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaillé_Jammes_2008]. Movement to, from, or within habitat
+as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
 patches or territories can also contribute to the formation of the social
@@
 (*Puma concolor*) home ranges overlapped more in regions with high hunting
-opportunity, a proxy for resource richness [@Elbroch_2016]. Caribou (*Rangifer
+opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
 tarandus*) sociality differed between seasons, where social associations were
 stronger in winter and contrastingly low in summer when resource availability
-are more homogenous [@Peigner_2019]. Bison (*Bison bison*) showed stronger
+are more homogenous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
 habitat selection in larger groups and avoidance of predation risk was a main
@@
 
+```{r spacetime, fig.cap='(ref:spacetime)'}
+knitr::include_graphics('../graphics/figure1.png')
+```
+
+\newpage
+
+```{r ml, fig.cap='(ref:ml)'}
+knitr::include_graphics('../graphics/figure-2.png')
+```
+
+\newpage
+
+```{r socres, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-spatialthreshold.png')
+```
+
+\newpage
+
+```{r lcres, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-lcres.png')
+```
+
+\newpage
+
+```{r nobs, fig.cap='(ref:nobs)'}
+knitr::include_graphics('../graphics/figure-nobs.png')
+```
+
+\newpage
+
+```{r winlen, fig.cap='(ref:winlen)'}
+knitr::include_graphics('../graphics/figure-winlength.png')
+```
+
+\newpage
+
+```{r winpos, fig.cap='(ref:winpos)'}
+knitr::include_graphics('../graphics/figure-winpos.png')
+```
+
+\newpage
+\clearpage
+
 # References

### 2020-02-15 paper/citations.R

@@ -4,6 +4,8 @@ library(knitcitations)
 
 ### Sections ----
 ## Introduction
+# Vander Wal 2014
+citep('10.1007/s00265-013-1652-0')
 
 # Croft 2008
 citep('10.1016/j.tree.2011.05.012')
@@ -126,8 +128,6 @@ citep('10.1016/j.anbehav.2017.09.008')
 # Silk 2017
 citep('10.1111/2041-210X.12770')
 
-#landscape
-
 # indiv fitness
 # brent 2017
 citep('10.1098/rspb.2017.0515')
@@ -212,7 +212,8 @@ citep('10.1016/j.tree.2019.11.001')
 citep('10.1111/1365-2656.12198')
 
 # Mourier et al. 2019 (pre-print)
-citep('10.1101/749085')
+#TODO: broken
+# citep('10.1101/749085')
 
 # Muller 2018
 citep('10.1016/j.anbehav.2018.10.006')
@@ -258,6 +259,18 @@ citep(citation('igraph'))
 # asnipe
 citep(citation('asnipe'))
 
+## habitat selection
+citep('10.1139/z07-094')
+citep('10.2307/2680033')
+citep('10.1007/s10980-016-0374-x')
+citep('10.1111/1365-2656.12447')
+citep('10.1016/s0169-5347(99)01593-1')
+citep('10.1007/978-94-011-1558-2')
+citep('10.1890/06-1672.1')
+citep('10.2980/16-2-3238')
+citep('10.1890/08-0345.1')
+
 
 ### Write out bib ----
 write.bibtex(file = "references/knitcite.bib")
+

### 2020-02-15 paper/manuscript.Rmd
fix vander wal

@@
 ## Keywords
-<!-- TODO: is this the final list ? -->
 Social network analysis, Landscape ecology, Movement ecology, Space use
@@
 represents shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. <!--Figure \@ref(fig:spacetime) TODO:
-something broken here?? --> Further, for social interactions or associations to
+\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
 occur individuals must share space, and thus have overlapping home ranges

### 2020-02-15 paper/manuscript.Rmd
rm editors

@@
 bibliography: ../references/knitcite.bib
+csl: csl.csl
 ---
@@
 @Farine_2015a]. Thus, we define social scale as the type of social relationship
-observed that can be explicitly defined and measured [@Farine_2015a]. <!--
-Farine references comes out as D.R. Farine 2015 -->
+observed that can be explicitly defined and measured [@Farine_2015a].
 

### 2020-02-15 paper/citations.R
zzz dont overwrite

@@ -272,5 +272,5 @@ citep('10.1890/08-0345.1')
 
 
 ### Write out bib ----
-write.bibtex(file = "references/knitcite.bib")
+write.bibtex(file = "references/knitcite-zzz.bib")
 

### 2020-02-15 paper/manuscript.Rmd
couple keys, couple capitals
rm todos, fix spaces, reflow, etc

@@
 discrete removed all erroneous and outlier GPS fixes following
-[@BJ_RNERAAS_2010] <!--TODO: fix this ref-->. We did not collar all caribou in
+[@Bjorneraas_2010]. We did not collar all caribou in
 the herd; however, the proportion of marked adult females was ~10% of all adult
@@
 ## Landscape data and habitat classification
-<!-- TODO: update citation for lc product from Hance --> 
 Landcover data were provided by the Newfoundland and Labrador Wildlife Division
@@
 in `r version$version.string` [@R_Core_Team_2019].
-<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->
 
@@
 We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index (SRI, Cairns and Schwaeger 1987): 
-<!-- TODO: get Cairns ref-->
+caribou using the simple ratio index [SRI, @Cairns_1987]:
 
@@
 ### Network metrics 
-
 <!-- TODO: expand + simplify + examples individual A, B etc -->
-<!-- TODO: EVW "parallelism"? -->
 
@@
 <!-- TODO: Add intro/general to results?-->
-
 In general, individuals in multilayer networks became more connected as social
@@
 phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics (Figure \@ref(fig:winlen), Figure \@ref(fig:winpos)). 
-These changes in the outcome depending on how the time window is
-defined highlight how critical it is to properly define the time window
-appropriately to address the questions and hypotheses of interest. For instance,
-social phenotypes can change over ontogeny in ways that can affect fitness
-[@Berger_2015; @Brent_2017]. Thus, it is critical to carefully consider the
-temporal scale that is meaningful for the proposed hypotheses. Further
-complicating the issue of selecting suitable time scales across ontogeny,
-individuals progress through development at different rates [@Tarka_2018]. This
-variation can make defining appropriate temporal scales for testing the fitness
-implications of an individual’s social phenotype over different stages of
-ontogeny even more difficult when they vary by individual. However, considering
-fine temporal scales provide insight across developmental stages that may
-otherwise be missed [@Turner_2017]. Defining temporal scales is a challenge in
-multilayer networks just as in monolayer networks; however, multilayer networks
-provide metrics that enable researchers to look at similarities and differences
-in separate layers representing different stages of ontogeny, or seasons as in
-our case study, which can be difficult to detect.
+there was a lot of variation in the multilayer network metrics (Figure
+\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
+depending on how the time window is defined highlight how critical it is to
+properly define the time window appropriately to address the questions and
+hypotheses of interest. For instance, social phenotypes can change over ontogeny
+in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
+critical to carefully consider the temporal scale that is meaningful for the
+proposed hypotheses. Further complicating the issue of selecting suitable time
+scales across ontogeny, individuals progress through development at different
+rates [@Tarka_2018]. This variation can make defining appropriate temporal
+scales for testing the fitness implications of an individual’s social phenotype
+over different stages of ontogeny even more difficult when they vary by
+individual. However, considering fine temporal scales provide insight across
+developmental stages that may otherwise be missed [@Turner_2017]. Defining
+temporal scales is a challenge in multilayer networks just as in monolayer
+networks; however, multilayer networks provide metrics that enable researchers
+to look at similarities and differences in separate layers representing
+different stages of ontogeny, or seasons as in our case study, which can be
+difficult to detect.
 
@@
 multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Movement as a collective group
-can reduce per capita predation risk via detection-dilution trade-offs and
-improve information transfer about the quality or location of resources to other
-group members [@Jolles_2019]. In our case study, we integrate proximity based
-social networks that inherently rely on animal collective movement, and, in
-general, we found that movement is likely an important mechanism driving social
-network connectivity within and between habitat types.
+processes [@Mourier_2019]. Movement as a collective group can reduce per capita
+predation risk via detection-dilution trade-offs and improve information
+transfer about the quality or location of resources to other group members
+[@Jolles_2019]. In our case study, we integrate proximity based social networks
+that inherently rely on animal collective movement, and, in general, we found
+that movement is likely an important mechanism driving social network
+connectivity within and between habitat types.
 
@@
 represent individual movement frequency, and *interlayer edges* represent
-contact probability among individuals at a given node [@Mourier_2019]. Although movement between fixed arrays is inherent, networks are
-not constructed based on continuous measures of dyadic or collective movement
-[@Long_2014]. Our case study builds on the work of Mourier et al. (2019) and
-explicitly integrates continuous and simultaneous measures of animal movement
-through space and time as layers of a multilayer social network.
+contact probability among individuals at a given node [@Mourier_2019]. Although
+movement between fixed arrays is inherent, networks are not constructed based on
+continuous measures of dyadic or collective movement [@Long_2014]. Our case
+study builds on the work of Mourier et al. (2019) and explicitly integrates
+continuous and simultaneous measures of animal movement through space and time
+as layers of a multilayer social network.
 
@@
 
-<!-- 
-TODO: Gerard ‘openness’ paper
-
-McGarigal 2016 organisms select habitat at multiple scales, temporal spatial
-should investigate scale dependency. linking ecological processes to scale eg foraging or predator-prey dynamics
-
-MRSF Laforge paper 
-van Beest et al. 2014 scale paper 
-Habitat–performance relationships: finding the right metric at a given spatial scale
-Multi-scale habitat selection modeling: a review and outlook
--->
-
 <!-- TODO: point to figure 1 -->
@@
 selection is still critically lacking [@McGarigal_2016].
-
-<!-- Relationship between sociality and habitat -->
-<!-- Merkle’s memory and patches for bison (and leaders) -->
-<!-- Emergent Properties of Conspecific Attraction inFragmented Landscapes-->
-<!-- Conspecific Attraction and Aggregation in Territorial Species-->
-<!-- Energy and the Scaling of Animal Space Use-->
-
-<!-- The relationship between sociality has been discussed both theoretically -->
-<!-- and tested explicitly ... CAH, etc then Fortin, McLouglin-->
-<!-- https://www.pnas.org/content/pnas/105/49/19114.full.pdf
-https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2600907/pdf/rspb20071688.pdf
--->
 
@@
 
-<!-- In summary, blah blah -->
+<!-- TODO: In summary, -->
 

### 2020-02-15 paper/manuscript.Rmd
typos

@@
 ## Landscape data and habitat classification
-Landcover data were provided by the Newfoundland and Labrador Wildlife Division
+Land cover data were provided by the Newfoundland and Labrador Wildlife Division
 [@Integrated_2013]. Available landcover classification included nine habitat
@@
 types, while forest habitat consisted of coniferous forest, conifer scrub,
-broadleaf forest, and mixed-wood forest. Water habitat was excluded from all
+broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
 subsequent analyses.
@@
 (forage, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
+composed of individuals linked by social associations, for each season and landcover combination. Proximity-based social
 network layers were generated using the R package `spatsoc` [@Robitaille_2019]
@@
 (ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each indiviual is represented by a unique color.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
 Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
@@
 proportion of neighbours that were the same across layers increased with a
-longer time frame during the summer, butthere were a high proportion of
+longer time frame during the summer, but there were a high proportion of
 neighbors that remained the same across layers during the winter, regardless of
@@
 C) Similarity of landcover network layers between seasons (e.g.
-open summer compared to open winter) orage and forest habitats but showed more variation in open habitats with increasing social thresholds.
+open summer compared to open winter) forage and forest habitats but showed more variation in open habitats with increasing social thresholds.
 Note that layer similarity in forage is not shown because individuals did not interact at landcover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
@@
 studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
-@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and mutlilayer
+@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
 networks in the emerging integration of social and spatial ecology within the
@@
 for robust networks [@Farine_2017]. These considerations may be limiting factors
-when answering questions that require timeframes that are relevant to different
+when answering questions that require time frames that are relevant to different
 individuals, for instance. In both mono- and multilayer networks, the effect of
@@
 to generate social networks during times when animals are engaged in different
-behaviours, including traveling, interacting, or foraging [@Muller_2018;
+behaviours, including travelling, interacting, or foraging [@Muller_2018;
 @Finn_2019] and construct a multilayer network based on behaviour-specific
@@
 Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicity
-quantify movement paramters could be itnegrated. For example, edges could
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
+quantify movement parameters could be integrated. For example, edges could
 represent measures of dyadic or collective movement based on dynamic interaction
@@
 stronger in winter and contrastingly low in summer when resource availability
-are more homogenous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
+are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
 habitat selection in larger groups and avoidance of predation risk was a main
@@
 explicitly integrated using network layers defined by similarity of selection
-coefficients between individuals. These explicit integrations of habitat
+coefficients between individuals. These explicit integration of habitat
 selection and sociality across social, spatial and temporal scales highlight the
@@
 networks with an additional set of questions posed through the lens of spatial
-ecology that are relevant to the promise and problem of scale in mutlilayer
+ecology that are relevant to the promise and problem of scale in multilayer
 networks:

### 2020-02-15 paper/manuscript.Rmd
less but still weak

@@
 <!-- TODO: weak --> 
-Multilayer networks can be used to explicitly consider habitat selection and
-sociality across scales. Animal social systems can be parsed by spatial
-contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
-The effect of seasonality of resources can can be directly measured by differences in
-habitat selection and sociality across temporal layers. Habitat selection can be
-explicitly integrated using network layers defined by similarity of selection
-coefficients between individuals. These explicit integration of habitat
-selection and sociality across social, spatial and temporal scales highlight the
-potential for novel insights from multilayer networks.
+Multilayer networks can be used to explicitly consider
+habitat selection and sociality across scales. Animal social systems can be
+parsed by spatial contexts, defined, for example, by habitat types as in Figure
+\@ref(fig:lcres). The effect of seasonality of resources can can be directly
+measured by differences in habitat selection and sociality across temporal
+layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
+selection can be explicitly integrated using network layers defined by selection
+coefficients for individuals. These examples of explicit integrations of habitat selection
+and sociality across social, spatial and temporal scales highlight the potential
+for novel insights from multilayer networks.
 

### 2020-02-15 paper/manuscript.Rmd
middle conclusion para

@@
 
-<!-- 
-TODO: Schneider 2001, Levin og,
-
-Alec, I think you need to include a paragraph reflecting on the importance of scale and ~3 critical things we should take away from this (maybe especially in light of including spatial data?) -->
+Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
+to an increased attention to the scale at which ecological processes are
+observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
+advances have lead to increased data complexity and resolution. Remotely sensed
+imagery collected by modern satellites provide, for example, 10 m spatial
+resolution optical imagery at a temporal revisit period of five days at the
+equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
+allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
+at a higher temporal resolution [@Börger_2016]. Given this increased
+availability of complex data, it is important to consider using a broad
+continuum of scales to fully capture ecological processes, carefully select and
+combine sources of data with different temporal and spatial scales, and
+establish a clear link between scales of observation and meaningful biology.
 
@@
 different scales and units of measurement. Our analysis of caribou multilayer
-networks incorporated high resolution GPS telemetry data and spatial landcover
+networks which incorporated high resolution GPS telemetry data and spatial landcover
 data is grounded in the context of observed animal social networks, as the
@@
 and time, are ones that can be observed as has traditionally been done in
-ethology. Thus, we highlight ways in which scale ought to be considered for both
+ethology. We highlight ways in which scale ought to be considered for both
 observed and remotely-sensed data when building social networks. Furthermore,

### 2020-02-15 paper/manuscript.Rmd
consistent?

@@
 spatial scales [@Luther_2009]. We posit that it is important to consider that
-animal behavior within the social environment will be scale-dependent.
+animal behaviour within the social environment will be scale-dependent.
 
@@
 [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
-studies of animal behavior [@Silk_2018; @Finn_2019], although they have been
+studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
 used to describe multidimensional human social systems, complex transportation
@@
 (e.g. summer open compared to winter open) using the Pearson correlation
-coefficient [@Br_dka_2018]. Network metrics were calculated using the R packages
+coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
 `igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
@@
 selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviors. Despite animals selecting for different landscape attributes
+certain behaviours. Despite animals selecting for different landscape attributes
 at different scales [@Mayor_2009], the use of multiscale analyses for habitat

### 2020-02-15 paper/manuscript.Rmd
fix last few refs

@@
 advanced to the point where relocations can be programmed to occur as frequently
-as each second [@Börger_2016], a practice which has been applied to questions of
+as each second [@B_rger_2016], a practice which has been applied to questions of
 collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
@@
 allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
-at a higher temporal resolution [@Börger_2016]. Given this increased
+at a higher temporal resolution [@B_rger_2016]. Given this increased
 availability of complex data, it is important to consider using a broad

### 2020-05-25 README.Rmd
fst grep TODOs
grep include scripts/
add manuscript todos to README
rm badges
update README

@@
 
-<!-- badges: start -->
-<!-- badges: end -->
-
 # The problem and promise of scale in multilayer networks
@@
 
-## Info
-[Special Column info](https://academic.oup.com/CZ/pages/animal_social_system)
-
-### Deadlines
-* ~~Abstract submission: 30 August 2019~~
-* Manuscript submission: 31 January 2020
-* Printing: June 2020
-
-### Guidelines
-[General Instructions page](https://academic.oup.com/cz/pages/General_Instructions)
+## TODO
+```{bash}
+grep -rni 'R/' -e 'TODO' || true;
+grep -rni 'scripts/' -e 'TODO' || true;
+grep -rni 'paper/manuscript.Rmd' -e 'TODO' || true;
+```

### 2020-05-25 paper/manuscript.Rmd
use double output

@@
 output:
-  # github_document
-  bookdown::pdf_document2:
-     number_sections: true
-     toc: false
-  # bookdown::word_document2:
-  #   reference_docx: template.docx
+   github_document: default
+   bookdown::word_document2:
+     reference_docx: template.docx
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(inputFile, encoding = encoding,
+  output_format = "all") })
 bibliography: ../references/knitcite.bib
@@
 ## Landscape data and habitat classification
-Land cover data were provided by the Newfoundland and Labrador Wildlife Division
+landcover data were provided by the Newfoundland and Labrador Wildlife Division
 [@Integrated_2013]. Available landcover classification included nine habitat

### 2020-05-25 paper/manuscript-trad.Rmd
explore two alternatives

--- 2020-05-25 paper/manuscript.Rmd
@@
 
-# Scale in multilayer networks: a case study
+# Methods
 
@@
 
-# Scale in multilayer networks in practice: case study results and discussion
-<!-- TODO: Add intro/general to results?-->
+# Results
+
 In general, individuals in multilayer networks became more connected as social
@@
 increased for winter networks between 5 and 50 m social thresholds, then did not
-change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
-the winter habitat layers captured most, if not all, of the potential
-connections an individual would have across these networks. Layer similarity was
+change for any habitat types (Figure \@ref(fig:socres)b). Layer similarity was
 not very strong for any habitat type, indicating that summer and winter networks
@@
 relatively stable across social thresholds, especially after 50 m (Figure
-\@ref(fig:socres)d). Taken together, these results suggest the optimal social
-scale at which groups should be assigned is likely somewhere between ~20 - 100 m
-based on the rate at which network metrics stabilized. For ungulates, groups are
-often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
-Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
-is likely an appropriate social scale for generating social networks in caribou
-and similar species.
+\@ref(fig:socres)d).
 
@@
 in each layer slightly decreased at increasing landcover resolutions (Figure
-\@ref(fig:lcres)d). Overall, these results indicate the importance of matching
-landcover resolution to scale of selection as well as ensuring the landcover
-product used has a resolution fine enough to detect landscape features and
-habitats relevant to study species, such as important patchy and rare habitats.
+\@ref(fig:lcres)d).
 
@@
 stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
-Given the observed trend of these multilayer metrics stabilizing after a certain
-number of observations are included, the results suggest this sensitivity method
-could be useful for determining the number of observations necessary for
-sufficiently describing social dynamics across contexts.
-
-<!-- TODO: I'm not sure this is relevant since this is the main way it
-is already done, can we make this thought more relevant to picking scales or
-multilayer networks in general? I think it's important for building robust
-networks -->
 
@@
 window lengths, but winter layers showed relatively stable but high layer
-relevance (Figure \@ref(fig:winlen)b). This pattern indicates that the
-proportion of neighbours that were the same across layers increased with a
-longer time frame during the summer, but there were a high proportion of
-neighbors that remained the same across layers during the winter, regardless of
-time length. Furthermore, though the layers were generally not very similar
+relevance (Figure \@ref(fig:winlen)b).  Furthermore, though the layers were generally not very similar
 between the summer and winter, the length of the time window created slight
@@
 (Figure \@ref(fig:winlen)c). Connective redundancy increased marginally with
-increasing window length, indicating that the proportions of neighbours that
-were the same across layers, though relatively high in general, slightly
-increased when time length was greater (Figure \@ref(fig:winlen)d). These
-results suggest that an increasing window length, especially for the summer
-season, may be resulting in less precisely defined seasons that are not clearly
-capturing periods of aggregation and dissaggregation related to resource
-availability.
+increasing window length,
 
@@
 individuals had more of the same neighbours in each habitat network (Figure
-\@ref(fig:winpos) d). Similar to window length, changing the position of the
-time window in this case results in a mismatch between expected periods of
-resource seasonality and corresponding sociality, particularly for the summer,
-highlighting the importance of carefully selecting temporal scale of analysis.
+\@ref(fig:winpos) d).
 
@@
 
-# Perspectives to advance multilayer networks
+# Discussion
+<!-- Social scale -->
+This pattern suggests
+the winter habitat layers captured most, if not all, of the potential
+connections an individual would have across these networks.
+
+ Taken together, these results suggest the optimal social
+scale at which groups should be assigned is likely somewhere between ~20 - 100 m
+based on the rate at which network metrics stabilized. For ungulates, groups are
+often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
+is likely an appropriate social scale for generating social networks in caribou
+and similar species.
+
+<!-- spatial/lc -->
+Overall, these results indicate the importance of matching
+landcover resolution to scale of selection as well as ensuring the landcover
+product used has a resolution fine enough to detect landscape features and
+habitats relevant to study species, such as important patchy and rare habitats.
+
+<!-- number of observations -->
+
+Given the observed trend of these multilayer metrics stabilizing after a certain
+number of observations are included, the results suggest this sensitivity method
+could be useful for determining the number of observations necessary for
+sufficiently describing social dynamics across contexts.
+
+<!-- length time window -->
+This pattern indicates that the
+proportion of neighbours that were the same across layers increased with a
+longer time frame during the summer, but there were a high proportion of
+neighbors that remained the same across layers during the winter, regardless of
+time length.
+
+These
+results suggest that an increasing window length, especially for the summer
+season, may be resulting in less precisely defined seasons that are not clearly
+capturing periods of aggregation and dissaggregation related to resource
+availability.
+
+Connective redundancy increased marginally with
+increasing window length, indicating that the proportions of neighbours that
+were the same across layers, though relatively high in general, slightly
+increased when time length was greater (Figure \@ref(fig:winlen)d).
+
+<!-- time window position -->
+Similar to window length, changing the position of the
+time window in this case results in a mismatch between expected periods of
+resource seasonality and corresponding sociality, particularly for the summer,
+highlighting the importance of carefully selecting temporal scale of analysis.
+
+<!-- # Perspectives to advance multilayer networks  -->
 
@@
 
-## Phenotypes and Individual fitness
-
 Social network positions are frequently used to represent the social environment
 that an individual experiences or their social phenotype. Multilayer networks
-provide a way to bridge these different scales so that we can examine social
+provide a way to bridge these different scales to examine social
 phenotypes in more holistic ways rather than looking at each scale separately as
@@
 
-For instance, social scale is major consideration for social network analysis,
-especially in the context of different types of relationships, such as grooming
-and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
-study results indicate that there are different social patterns in different
-habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure 
-\@ref(fig:socres)) in different habitat types, having higher graph strength in
-forage and open habitats where they can likely see each other and still interact
-with visual cues unlike in forest habitats. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
-
-Temporal scale is also important for understanding the repercussions of social
-phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics (Figure
-\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
-depending on how the time window is defined highlight how critical it is to
-properly define the time window appropriately to address the questions and
-hypotheses of interest. For instance, social phenotypes can change over ontogeny
-in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses. Further complicating the issue of selecting suitable time
-scales across ontogeny, individuals progress through development at different
-rates [@Tarka_2018]. This variation can make defining appropriate temporal
-scales for testing the fitness implications of an individual’s social phenotype
-over different stages of ontogeny even more difficult when they vary by
-individual. However, considering fine temporal scales provide insight across
-developmental stages that may otherwise be missed [@Turner_2017]. Defining
-temporal scales is a challenge in multilayer networks just as in monolayer
-networks; however, multilayer networks provide metrics that enable researchers
-to look at similarities and differences in separate layers representing
-different stages of ontogeny, or seasons as in our case study, which can be
-difficult to detect.
-
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes. The multilayer network framework enables
-researchers to examine these different social scales simultaneously rather than
-individually, which is what has been done under most circumstances, but is not
-very realistic. Metrics from multilayer networks provide an opportunity to
-simplify statistical models. Interactions that happen side-by-side, proximity
-associations, and long-distance interactions can be encapsulated in a single
-multilayer network, and a single metric can be used to describe the various
-social scales of an individual’s network position. This multilevel network
-metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
-to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations,
-especially over time, it is hard to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-Conversely, picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks [@Farine_2017]. These considerations may be limiting factors
+These considerations may be limiting factors
 when answering questions that require time frames that are relevant to different

### 2020-05-25 paper/manuscript-trad.Rmd
fst trad

@@
 
+<!-- fitness -->
 Social network positions are frequently used to represent the social environment
@@
 logistical constraints.
-
-## Movement ecology and collective movement
 
@@
 
-## Habitat selection and space use
+<!-- ## Habitat selection and space use -->
 Social structure and habitat selection are intimately linked: individuals must

### 2020-05-25 paper/manuscript-rev.Rmd
use github_document2

--- 2020-05-25 paper/manuscript.Rmd
@@
 output:
-   github_document: default
+   bookdown::github_document2: default
    bookdown::word_document2:

### 2020-05-27 paper/manuscript-rev.Rmd
fst rev

@@
 and space use.
-<!-- TODO: we answer the first question in the discussion, but not the second-->
-<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
 
-(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants.
-Spatial and temporal extent for social interactions, e.g.
-mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions.
-The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact.
-By contrast, different species have potential for greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.
+<!-- # Perspectives to advance multilayer networks  -->
 
-<!-- TODO: units of spatial scale? --> 
-<!-- TODO: citations? -->
+<!-- The integration of behavioural and ecological theory has shown the value of -->
+<!-- considering the importance of various ecological disciplines to better -->
+<!-- understand and predict animal social networks, including demography -->
+<!-- [@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease -->
+<!-- ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of -->
+<!-- studies integrating social network theory into a broader array of behavioural -->
+<!-- and ecological sub-disciplines is impressive, only recently has the role of -->
+<!-- animal space use been considered in describing the causes and consequences of -->
+<!-- the social environment in the context of (1) phenotypes and individual fitness -->
+<!-- [@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and -->
+<!-- (3) habitat selection and space use [@He_2019]. Importantly, much of the work -->
+<!-- linking space use and the social environment has been theoretical and empirical -->
+<!-- studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; -->
+<!-- @Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer -->
+<!-- networks in the emerging integration of social and spatial ecology within the -->
+<!-- behavioural ecology literature. -->
 
+# Phenotypes and Individual fitness
+
+Social network positions are frequently used to represent the social environment
+that an individual experiences or their social phenotype. Multilayer networks
+provide a way to bridge these different scales so that we can examine social
+phenotypes in more holistic ways rather than looking at each scale separately as
+has traditionally been done. From a monolayer network perspective, social
+phenotypes are increasingly linked to important fitness for individuals of
+various species, including primates [@Brent_2017; @Thompson_2019], dolphins
+[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
+social scales, types of interactions, and temporal, seasons and stages of life,
+have emerged as important for understanding fitness consequences in the context
+of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011].
+
+For instance, social scale is major consideration for social network analysis,
+especially in the context of different types of relationships, such as grooming
+and association, that are typically examined separately while answering a single
+question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
+common trope that individuals must be associating to interact, and many studies
+therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
+instance, baboons need to be in proximity to groom each other. However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015]. With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
+study results indicate that there are different social patterns in different
+habitat types, likely indicating different types of interactions. When the
+social threshold is greater than approximately 50 m during the winter,
+individuals demonstrate dramatically different graph strength (Figure 
+\@ref(fig:socres)) in different habitat types, having higher graph strength in
+forage and open habitats where they can likely see each other and still interact
+with visual cues unlike in forest habitats. Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca
+mulatta*) had higher survivorship when they had fewer but stronger, more stable
+social associates and grooming partners rather than simply more associates
+[@Ellis_2019]. This finding highlights that different qualities of social scales
+have lasting consequences. Multilayer networks provide the opportunity to
+address these types of questions involving social scale with all the individual
+layers of interaction integrated in a holistic way.
+
+Temporal scale is also important for understanding the repercussions of social
+phenotypes. Varying the time window length and position for caribou, we found
+there was a lot of variation in the multilayer network metrics (Figure
+\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
+depending on how the time window is defined highlight how critical it is to
+properly define the time window appropriately to address the questions and
+hypotheses of interest. For instance, social phenotypes can change over ontogeny
+in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
+critical to carefully consider the temporal scale that is meaningful for the
+proposed hypotheses. Further complicating the issue of selecting suitable time
+scales across ontogeny, individuals progress through development at different
+rates [@Tarka_2018]. This variation can make defining appropriate temporal
+scales for testing the fitness implications of an individual’s social phenotype
+over different stages of ontogeny even more difficult when they vary by
+individual. However, considering fine temporal scales provide insight across
+developmental stages that may otherwise be missed [@Turner_2017]. Defining
+temporal scales is a challenge in multilayer networks just as in monolayer
+networks; however, multilayer networks provide metrics that enable researchers
+to look at similarities and differences in separate layers representing
+different stages of ontogeny, or seasons as in our case study, which can be
+difficult to detect.
+
+Multilayer networks provide unique opportunities and challenges, linking these
+various scales, for understanding the social phenotypes and environments of
+individuals and their fitness outcomes. The multilayer network framework enables
+researchers to examine these different social scales simultaneously rather than
+individually, which is what has been done under most circumstances, but is not
+very realistic. Metrics from multilayer networks provide an opportunity to
+simplify statistical models. Interactions that happen side-by-side, proximity
+associations, and long-distance interactions can be encapsulated in a single
+multilayer network, and a single metric can be used to describe the various
+social scales of an individual’s network position. This multilevel network
+metric could be used to assess the relationship between an individual’s social
+phenotype and fitness. It would also be a meaningful reduction of many
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
+to test hypotheses linking social phenotypes and fitness across temporal scales.
+Because of the non-independent nature of social interactions and associations,
+especially over time, it is hard to test hypotheses about social dynamics with a
+suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
+multilayer networks, making layers of different temporal periods provides a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods.
+
+Conversely, picking the proper temporal scale is important but a challenge
+because all layers in the multilayer network should reflect the same time
+period, and the period should be long enough for each layer to have enough data
+for robust networks [@Farine_2017]. These considerations may be limiting factors
+when answering questions that require time frames that are relevant to different
+individuals, for instance. In both mono- and multilayer networks, the effect of
+scale on the relationship between an individual’s social network position and
+fitness need to be considered based on the hypotheses being tested and
+logistical constraints.
+
+# Movement ecology and collective movement
+
+Social processes, movement decisions, and space use are inextricably linked and
+multilayer networks represent a potential analytical framework for linking these
+processes [@Mourier_2019]. Movement as a collective group can reduce per capita
+predation risk via detection-dilution trade-offs and improve information
+transfer about the quality or location of resources to other group members
+[@Jolles_2019]. In our case study, we integrate proximity based social networks
+that inherently rely on animal collective movement, and, in general, we found
+that movement is likely an important mechanism driving social network
+connectivity within and between habitat types.
+
+Although multilayer animal social networks are relatively novel [@Silk_2018],
+movement behaviour within multilayer networks has been considered. Spatial
+networks are physical locations (nodes) which are connected in a network when
+individuals move between said locations (edges). For example, spatial networks
+were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
+*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
+example, nodes represent locations within the array, *intralayer edges*
+represent individual movement frequency, and *interlayer edges* represent
+contact probability among individuals at a given node [@Mourier_2019]. Although
+movement between fixed arrays is inherent, networks are not constructed based on
+continuous measures of dyadic or collective movement [@Long_2014]. Our case
+study builds on the work of Mourier et al. (2019) and explicitly integrates
+continuous and simultaneous measures of animal movement through space and time
+as layers of a multilayer social network.
+
+In contrast to spatial networks, where nodes represent spatial locations that
+are fixed in space, movement networks can represent continuous and simultaneous
+movement trajectories of multiple animals. In a recent study of vulturine
+gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
+monolayer association networks within a multilayer network [@Papageorgiou_2019].
+However, despite potential to generate networks in different spatial or social
+contexts, layers in the multilayer network represented social associations
+within and between groups. Continuous collection of animal relocation data using
+GPS technology can be used to measure how groups of animals make collective
+movement decisions in the context of their local environment
+[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
+collective movement layer could constitute similarity in movement for dyads
+[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
+fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
+@Flack_2018]. Our case study integrates variation in temporal and spatial scale
+to assess the role of scale in predicting multilayer networks. As one might
+expect, we found increasing social threshold results in saturation of potential
+social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
+on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
+to generate social networks during times when animals are engaged in different
+behaviours, including travelling, interacting, or foraging [@Muller_2018;
+@Finn_2019] and construct a multilayer network based on behaviour-specific
+monolayer networks [e.g. @Smith_Aguilar_2019].
+
+Importantly, the key to incorporating movement in multilayer networks across
+scales is the technological advancements available to overcome previous
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
+advanced to the point where relocations can be programmed to occur as frequently
+as each second [@B_rger_2016], a practice which has been applied to questions of
+collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
+technology, including unmanned aerial vehicles and satellites, can be used to
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]. Using technology to infer behaviour has therefore become
+standard operating procedure for many species in many systems. Our ability to
+collect and process remotely sensed data and infer social processes based on
+animal movement provides an opportunity to use multilayer social network
+analysis to answer complex questions about animal socioecology.
+
+Given the existing framework for constructing multilayer networks from
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
+quantify movement parameters could be integrated. For example, edges could
+represent measures of dyadic or collective movement based on dynamic interaction
+metrics [@Long_2014]. Integrating movement layers with habitat-specific social
+association layers could further illuminate the role of movement as a driver
+of the social and spatial environments an individual experiences [@Webber_2018].
+In our case study, we generated multilayer networks based on habitat-specific
+monolayers. Coordinated movement of dyads, or groups, could vary based on
+habitat, and the approach we outline could be used to explore mechanisms linking
+the social and spatial environments. For example, social processes may be an
+emergent property of the landscape because animals aggregate at resources, such
+as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
+patches or territories can also contribute to the formation of the social
+environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
+males interacted primarily at home range edges, presumably driving territorial
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
+network framework is a logical next step for a burgeoning field. In particular,
+when association networks are habitat-specific, we suggest the integration of
+movement and space use in multilayer networks provides novel insights into the
+effects of habitat configuration on the formation of the social environment
+[@He_2019; @Webber_2018].
+
+# Habitat selection and space use
+Social structure and habitat selection are intimately linked: individuals must
+share space to interact and the distribution of resources influences group
+dynamics and home range size [@Webber_2018]. Social structure is influenced by
+resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
+and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
+novel framework for considering the influence of habitat selection and space use
+on sociality across scales.
+
+<!-- TODO: point to figure 1 -->
+Habitat selection depends on the scale at which it is measured and a singular
+scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
+selection is measured using resource selection functions (RSFs), based on the
+proportion of used and available resources for an animal [@Manly_1993;
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, the
+(3) habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Moving past this hierarchical perspective, Mayor (2007) emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviours. Despite animals selecting for different landscape attributes
+at different scales [@Mayor_2009], the use of multiscale analyses for habitat
+selection is still critically lacking [@McGarigal_2016].
+
+The emergent relationship between habitat and sociality has been explored by the
+distribution and phenology of resources and use of social information. Cougar
+(*Puma concolor*) home ranges overlapped more in regions with high hunting
+opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
+tarandus*) sociality differed between seasons, where social associations were
+stronger in winter and contrastingly low in summer when resource availability
+are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
+habitat selection in larger groups and avoidance of predation risk was a main
+factor contributing to their habitat selection [@Fortin_2009]. These examples,
+comparing sociality and habitat selection across temporal or spatial contexts,
+are implicitly multilayer analyses.
+
+<!-- TODO: weak --> 
+Multilayer networks can be used to explicitly consider
+habitat selection and sociality across scales. Animal social systems can be
+parsed by spatial contexts, defined, for example, by habitat types as in Figure
+\@ref(fig:lcres). The effect of seasonality of resources can can be directly
+measured by differences in habitat selection and sociality across temporal
+layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
+selection can be explicitly integrated using network layers defined by selection
+coefficients for individuals. These examples of explicit integrations of habitat selection
+and sociality across social, spatial and temporal scales highlight the potential
+for novel insights from multilayer networks.
+
+---
 # Scale in multilayer networks: a case study
@@
 
-# Perspectives to advance multilayer networks
-
-The integration of behavioural and ecological theory has shown the value of
-considering the importance of various ecological disciplines to better
-understand and predict animal social networks, including demography
-[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
-ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
-studies integrating social network theory into a broader array of behavioural
-and ecological sub-disciplines is impressive, only recently has the role of
-animal space use been considered in describing the causes and consequences of
-the social environment in the context of (1) phenotypes and individual fitness
-[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
-(3) habitat selection and space use [@He_2019]. Importantly, much of the work
-linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
-@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
-networks in the emerging integration of social and spatial ecology within the
-behavioural ecology literature.
-
-## Phenotypes and Individual fitness
-
-Social network positions are frequently used to represent the social environment
-that an individual experiences or their social phenotype. Multilayer networks
-provide a way to bridge these different scales so that we can examine social
-phenotypes in more holistic ways rather than looking at each scale separately as
-has traditionally been done. From a monolayer network perspective, social
-phenotypes are increasingly linked to important fitness for individuals of
-various species, including primates [@Brent_2017; @Thompson_2019], dolphins
-[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
-social scales, types of interactions, and temporal, seasons and stages of life,
-have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011].
-
-For instance, social scale is major consideration for social network analysis,
-especially in the context of different types of relationships, such as grooming
-and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
-study results indicate that there are different social patterns in different
-habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure 
-\@ref(fig:socres)) in different habitat types, having higher graph strength in
-forage and open habitats where they can likely see each other and still interact
-with visual cues unlike in forest habitats. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
-
-Temporal scale is also important for understanding the repercussions of social
-phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics (Figure
-\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
-depending on how the time window is defined highlight how critical it is to
-properly define the time window appropriately to address the questions and
-hypotheses of interest. For instance, social phenotypes can change over ontogeny
-in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses. Further complicating the issue of selecting suitable time
-scales across ontogeny, individuals progress through development at different
-rates [@Tarka_2018]. This variation can make defining appropriate temporal
-scales for testing the fitness implications of an individual’s social phenotype
-over different stages of ontogeny even more difficult when they vary by
-individual. However, considering fine temporal scales provide insight across
-developmental stages that may otherwise be missed [@Turner_2017]. Defining
-temporal scales is a challenge in multilayer networks just as in monolayer
-networks; however, multilayer networks provide metrics that enable researchers
-to look at similarities and differences in separate layers representing
-different stages of ontogeny, or seasons as in our case study, which can be
-difficult to detect.
-
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes. The multilayer network framework enables
-researchers to examine these different social scales simultaneously rather than
-individually, which is what has been done under most circumstances, but is not
-very realistic. Metrics from multilayer networks provide an opportunity to
-simplify statistical models. Interactions that happen side-by-side, proximity
-associations, and long-distance interactions can be encapsulated in a single
-multilayer network, and a single metric can be used to describe the various
-social scales of an individual’s network position. This multilevel network
-metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
-to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations,
-especially over time, it is hard to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-Conversely, picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks [@Farine_2017]. These considerations may be limiting factors
-when answering questions that require time frames that are relevant to different
-individuals, for instance. In both mono- and multilayer networks, the effect of
-scale on the relationship between an individual’s social network position and
-fitness need to be considered based on the hypotheses being tested and
-logistical constraints.
-
-## Movement ecology and collective movement
-
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Movement as a collective group can reduce per capita
-predation risk via detection-dilution trade-offs and improve information
-transfer about the quality or location of resources to other group members
-[@Jolles_2019]. In our case study, we integrate proximity based social networks
-that inherently rely on animal collective movement, and, in general, we found
-that movement is likely an important mechanism driving social network
-connectivity within and between habitat types.
-
-Although multilayer animal social networks are relatively novel [@Silk_2018],
-movement behaviour within multilayer networks has been considered. Spatial
-networks are physical locations (nodes) which are connected in a network when
-individuals move between said locations (edges). For example, spatial networks
-were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
-*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
-example, nodes represent locations within the array, *intralayer edges*
-represent individual movement frequency, and *interlayer edges* represent
-contact probability among individuals at a given node [@Mourier_2019]. Although
-movement between fixed arrays is inherent, networks are not constructed based on
-continuous measures of dyadic or collective movement [@Long_2014]. Our case
-study builds on the work of Mourier et al. (2019) and explicitly integrates
-continuous and simultaneous measures of animal movement through space and time
-as layers of a multilayer social network.
-
-In contrast to spatial networks, where nodes represent spatial locations that
-are fixed in space, movement networks can represent continuous and simultaneous
-movement trajectories of multiple animals. In a recent study of vulturine
-gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
-monolayer association networks within a multilayer network [@Papageorgiou_2019].
-However, despite potential to generate networks in different spatial or social
-contexts, layers in the multilayer network represented social associations
-within and between groups. Continuous collection of animal relocation data using
-GPS technology can be used to measure how groups of animals make collective
-movement decisions in the context of their local environment
-[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
-collective movement layer could constitute similarity in movement for dyads
-[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
-fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
-@Flack_2018]. Our case study integrates variation in temporal and spatial scale
-to assess the role of scale in predicting multilayer networks. As one might
-expect, we found increasing social threshold results in saturation of potential
-social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
-on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
-to generate social networks during times when animals are engaged in different
-behaviours, including travelling, interacting, or foraging [@Muller_2018;
-@Finn_2019] and construct a multilayer network based on behaviour-specific
-monolayer networks [e.g. @Smith_Aguilar_2019].
-
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
-
-Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-In our case study, we generated multilayer networks based on habitat-specific
-monolayers. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
-## Habitat selection and space use
-Social structure and habitat selection are intimately linked: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
-novel framework for considering the influence of habitat selection and space use
-on sociality across scales.
-
-<!-- TODO: point to figure 1 -->
-Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
-selection is measured using resource selection functions (RSFs), based on the
-proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours. Despite animals selecting for different landscape attributes
-at different scales [@Mayor_2009], the use of multiscale analyses for habitat
-selection is still critically lacking [@McGarigal_2016].
-
-The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. Cougar
-(*Puma concolor*) home ranges overlapped more in regions with high hunting
-opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
-tarandus*) sociality differed between seasons, where social associations were
-stronger in winter and contrastingly low in summer when resource availability
-are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
-habitat selection in larger groups and avoidance of predation risk was a main
-factor contributing to their habitat selection [@Fortin_2009]. These examples,
-comparing sociality and habitat selection across temporal or spatial contexts,
-are implicitly multilayer analyses.
-
-<!-- TODO: weak --> 
-Multilayer networks can be used to explicitly consider
-habitat selection and sociality across scales. Animal social systems can be
-parsed by spatial contexts, defined, for example, by habitat types as in Figure
-\@ref(fig:lcres). The effect of seasonality of resources can can be directly
-measured by differences in habitat selection and sociality across temporal
-layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
-selection can be explicitly integrated using network layers defined by selection
-coefficients for individuals. These examples of explicit integrations of habitat selection
-and sociality across social, spatial and temporal scales highlight the potential
-for novel insights from multilayer networks.
+---
 

### 2020-05-28 paper/manuscript-rev.Rmd
add toc

@@
 output:
-   bookdown::github_document2: default
-   bookdown::word_document2:
-     reference_docx: template.docx
+   bookdown::github_document2:
+     toc: true
+   # bookdown::word_document2:
+   #   reference_docx: template.docx
 knit: (function(inputFile, encoding) {

### 2020-05-28 paper/manuscript-trad.Rmd
add toc

--- 2020-05-25 paper/manuscript-trad.Rmd
@@
 output:
-   github_document: default
-   bookdown::word_document2:
-     reference_docx: template.docx
+   bookdown::github_document2: 
+     toc: true
+   # bookdown::word_document2:
+   #   reference_docx: template.docx
 knit: (function(inputFile, encoding) {

### 2020-05-29 scripts/04-time-window-length.R
start adjust sensitivity -> ordinal

@@ -24,10 +24,6 @@ alloc.col(DT)
 
 
 # Chunk time --------------------------------------------------------------
-# Remove season column from 1-data-prep.R
-DT[, season := NULL]
-
-
 nchunk <- 8
 
 # TODO: check consistent N by cut * year
@@ -44,54 +40,49 @@ group_times(
 
 
 # Generate network for each time chunk ------------------------------------
-var <- 'winlength'
+var <- 'timecut'
+splitBy <- var
 
-nets <- lapply(winlengths, function(len) {
-  col <- paste0('season', len)
-  splitBy <- c(col, lccol)
-  
-  sub <- na.omit(DT, cols = splitBy)
-  
-  # Spatial grouping with spatsoc
-  group_pts(
-    sub,
-    threshold = spatthresh,
-    id = idcol,
-    coords = projCols,
-    timegroup = 'timegroup',
-    splitBy = splitBy
-  )
+# Spatial grouping with spatsoc
+# TODO: double fixes
+group_pts(
+  DT,
+  threshold = spatthresh,
+  id = idcol,
+  coords = projCols,
+  timegroup = 'timegroup',
+  splitBy = splitBy
+)
   
   
-  # GBI 
-  gbiLs <- list_gbi(sub, idcol, splitBy)
+# GBI
+gbiLs <- list_gbi(DT, idcol, splitBy)
 
-  # Generate networks
-  netLs <- list_nets(gbiLs)
-  
-  # Generate graphs
-  gLs <- list_graphs(netLs)
-  names(gLs) <- names(gbiLs)
-  
-  # Calculate eigenvector centrality
-  stren <- layer_strength(gLs)
-  stren[, (splitBy) := tstrsplit(layer, '-', type.convert = TRUE)]
-  setnames(stren, 'ind', idcol)
-  
-  # Calculate neighbors
-  layer_neighbors(sub, idcol, splitBy = splitBy)
+# Generate networks
+netLs <- list_nets(gbiLs)
 
-  # and tidy output, prep for merge
-  outcols <- c('neigh', 'splitNeigh', idcol, splitBy)
-  out <- unique(sub[, .SD, .SDcols = outcols])
-  
-  # Merge eigcent+correlations with neighbors
-  out <- out[stren, on = c(idcol, splitBy)]
-  setnames(out, col, gsub('[0-9]', '', col))
-  
-  # Preserve window length
-  set(out, j = var, value = len)
-})
[…]

### 2020-05-29 paper/manuscript.Rmd
fix paths from 0 to 00

@@
 
-source('../scripts/0-variables.R')
+source('../scripts/00-variables.R')
 

### 2020-05-29 scripts/01-data-prep.R

@@ -8,7 +8,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 

### 2020-05-29 scripts/02-landcover-scale.R

@@ -14,7 +14,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 # Input -------------------------------------------------------------------
 DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')

### 2020-05-29 scripts/03-spatial-threshold.R

@@ -12,7 +12,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 # Input -------------------------------------------------------------------

### 2020-05-29 scripts/04-time-window-length.R

@@ -14,7 +14,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 # Input -------------------------------------------------------------------

### 2020-05-29 scripts/05-number-of-observations.R

@@ -13,7 +13,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 # Input -------------------------------------------------------------------

### 2020-05-29 scripts/06-time-window-position.R

@@ -12,7 +12,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 ### Variables ----
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 ### Data ----

### 2020-05-29 scripts/07-metrics.R

@@ -8,7 +8,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 # Input -------------------------------------------------------------------

### 2020-05-29 scripts/08-plots.R

@@ -10,7 +10,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 # Variables ---------------------------------------------------------------
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 # Input -------------------------------------------------------------------

### 2020-05-29 scripts/try-behavioural-states.R

@@ -13,7 +13,7 @@ p <- lapply(pkgs, library, character.only = TRUE)
 
 
 ### Variables ----
-source('scripts/0-variables.R')
+source('scripts/00-variables.R')
 
 
 ### Data ----

### 2020-06-02 scripts/02-landcover-scale.R
drop seasons from land cover scale sensitivity

@@ -17,7 +17,8 @@ p <- lapply(pkgs, library, character.only = TRUE)
 source('scripts/00-variables.R')
 
 # Input -------------------------------------------------------------------
-DT <- readRDS('data/derived-data/1-sub-seasons-fogo-caribou.Rds')
+# TODO: switch back to sub seasons?
+DT <- readRDS('data/derived-data/1-sub-fogo-caribou.Rds')
 alloc.col(DT)
 
 lc <- readRDS('data/derived-data/1-reclass-lc.Rds')
@@ -53,7 +54,8 @@ var <- 'lcres'
 # Also include original raster
 lsres <- c(30, lsres)
 lslc <- c(lc, lslc)
-splitBy <- 'season'
+# TODO: switch back to seasons?
+splitBy <- c()
 
 nets <- lapply(lsres, function(res) {
   col <- ifelse(res == 30, 'lc', paste0('lc', res))

### 2020-06-10 scripts/02-landcover-scale.R
use full seq lc

@@ -34,7 +34,7 @@ lsres <- as.integer(gsub(".tif", "", unlist(tstrsplit(
 ))))
 names(lslc) <- lsres
 
-# lsres <- c(100, 300, 500, 700, 900, 1000)
+# lsres <- seq(100, 1000, by = 100)
 # lslc <- lapply(lsres, function(res) {
 #   w <- winmove(lc, res, type = 'circle', win_fun = modal)
 #   w[is.na(lc)] <- NA

### 2020-06-10 paper/manuscript.Rmd
new title
fst manuscript edits

@@
 ---
-title: The problem and promise of scale in multilayer animal social networks
+title: Considering scale in multilayer animal social networks
 author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 future development and applications of scale in multilayer networks with respect
-to: phenotypes and individual fitness, movement ecology and collective movement, and habitat selection and space use. Effective integration of social and
-spatial processes, including biologically meaningful scales, within the context
-of animal social networks is an emerging area of research, as such our
-contribution incorporates perspectives on how the social environment and spatial
-processes are linked across scales in a multilayer context.
+to: phenotypes and individual fitness, movement ecology and collective movement,
+and habitat selection and space use. Effective integration of social and spatial
+processes, including biologically meaningful scales, within the context of
+animal social networks is an emerging area of research, as such our contribution
+incorporates perspectives on how the social environment and spatial processes
+are linked across scales in a multilayer context.
 
@@
 # Introduction
-Our inference regarding the ecological processes underlying ecological patterns
+Our inference regarding the processes underlying ecological patterns
 are directly linked to the scale at which they are observed [@Levin_1992;
@@
 represents shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
-occur individuals must share space, and thus have overlapping home ranges
-[@Vander_Wal_2013]. In the context of the social environment, home range overlap
-is an example of how animals share space over coarser spatial and temporal
-scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
-scales spatially and temporally, it remains unclear whether coarser scales of
-sociality, including social association and home range overlap, vary predictably
-with social interaction [@Castles_2014;
+\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
+associations to occur individuals must share space, and thus have overlapping
+home ranges [@Vander_Wal_2013]. In the context of the social environment, home
+range overlap is an example of how animals share space over coarser spatial and
+temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
+clearly scales spatially and temporally, it remains unclear whether coarser
+scales of sociality, including social association and home range overlap, vary
+predictably with social interaction [@Castles_2014;
 @Farine_2015a]. Thus, we define social scale as the type of social relationship
@@
 Unlike traditional monolayer social networks, multilayer networks explicitly
-consider social systems across contexts, including scale-dependent contexts
+consider social systems across scale-dependent contexts
 [@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
@@
 `igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
+<!-- add used spatsoc -->
 
@@
 
-We modified the distance threshold, hereafter the social threshold, required for
+We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
 group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at

### 2020-06-10 paper/manuscript.Rmd
adjust h

@@
 
-# Scale in multilayer networks in practice: case study results and discussion
+# Results
+
 <!-- TODO: Add intro/general to results?-->
@@
 
-# Perspectives to advance multilayer networks
+# Discussion
 

### 2020-06-11 paper/manuscript.Rmd
start update methods with caribou socioecology

@@
 ## Caribou socioecology
-Here, we use caribou as a case study to develop scale-dependent multilayer
+<!--Here, we use caribou as a case study to develop scale-dependent multilayer
 networks based on predicted social (visual and auditory perception), spatial
-(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
+(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious ungulates
 with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
@@
 vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
-greater access to forage in snow-free seasons. We partitioned data into two
+greater access to forage in snow-free seasons. <!--We partitioned data into two
 discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
-February 2018) based on caribou socioecology [@Peignier_2019].
+February 2018) based on caribou socioecology [@Peignier_2019].-->
 
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
+We used GPS location data collected from Fogo Island caribou in 2017, 2018 and 2019.
 Adult female caribou were immobilized and fitted with global positioning system

### 2020-06-11 paper/manuscript.Rmd
landcover is land cover

@@
 ## Landscape data and habitat classification
-landcover data were provided by the Newfoundland and Labrador Wildlife Division
-[@Integrated_2013]. Available landcover classification included nine habitat
-types at 30 m resolution. We reclassified the landcover types into three
+Land cover data were provided by the Newfoundland and Labrador Wildlife Division
+[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification included nine habitat
+types at 30 m resolution. We reclassified the land cover types into three
 categories: foraging habitat, open habitat, and forest habitat using the R
@@
 We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
-individual nodes and two aspects (season and landcover). Two season
-elementary-layers (summer and winter) and three landcover elementary-layers
+individual nodes and two aspects (season and land cover). Two season
+elementary-layers (summer and winter) and three land cover elementary-layers
 (forage, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals linked by social associations, for each season and landcover combination. Proximity-based social
+composed of individuals linked by social associations, for each season and land cover combination. Proximity-based social
 network layers were generated using the R package `spatsoc` [@Robitaille_2019]
@@
 strength is the degree weighted by the strength of association, in this case
-SRI, in each layer-specific season and landcover context. Extending degree
+SRI, in each layer-specific season and land cover context. Extending degree
 centrality, we calculated multidegree, the sum of degree centrality of
@@
 neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
-calculated the similarity of layers between seasons, across landcover classes
+calculated the similarity of layers between seasons, across land cover classes
 (e.g. summer open compared to winter open) using the Pearson correlation
@@
 To assess the influence of spatial scale on multilayer networks, we aggregated
-our landcover raster at varying scales relevant to caribou ecology. We
-aggregated the 30 m landcover raster using the R package `grainchanger`
+our land cover raster at varying scales relevant to caribou ecology. We
+aggregated the 30 m land cover raster using the R package `grainchanger`
 [@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
@@
 
-Increasing landcover resolution resulted in a decreased availability of forage,
+Increasing land cover resolution resulted in a decreased availability of forage,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
@@
 (Figure \@ref(fig:lcres)a). Mean graph strength increased consistently in winter
-forest and open habitats but varied in winter forage varied across landcover
+forest and open habitats but varied in winter forage varied across land cover
 resolutions with an increase at 250 m and decrease at 500 m (Figure
@@
 \@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-summer and winter forage because, at all landcover resolutions greater than 30
+summer and winter forage because, at all land cover resolutions greater than 30
 m, there were no individuals connected in the network layers. Individuals still
 used forage habitats, but given the lower availability due to increasing
-landcover resolution, at a much lower rate. Connective redundancy was moderately
-high but decreased slightly as landcover resolution increased, indicating that
+land cover resolution, at a much lower rate. Connective redundancy was moderately
+high but decreased slightly as land cover resolution increased, indicating that
 many neighbours were the same between layers, but the proportion of neighbours
-in each layer slightly decreased at increasing landcover resolutions (Figure
+in each layer slightly decreased at increasing land cover resolutions (Figure
 \@ref(fig:lcres)d). Overall, these results indicate the importance of matching
-landcover resolution to scale of selection as well as ensuring the landcover
+land cover resolution to scale of selection as well as ensuring the land cover
 product used has a resolution fine enough to detect landscape features and
@@
 remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
-coarse landcover resolution (Figure \@ref(fig:lcres)), low numbers of
+coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
 observations were not sufficient for capturing individuals in all contexts and
@@
 
-<!-- Figure: metrics by landcover resolution -->
-(ref:lcres) Varying spatial scale in landcover resolution.
-For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+<!-- Figure: metrics by land cover resolution -->
+(ref:lcres) Varying spatial scale in land cover resolution.
+For each land cover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
 A) Mean graph strength of individuals in summer layers had consistent weak connections.
 Individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
-B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
-C) Similarity of landcover network layers between seasons (e.g.
+B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher land cover resolutions.
+C) Similarity of land cover network layers between seasons (e.g.
 open summer compared to open winter) forage and forest habitats but showed more variation in open habitats with increasing social thresholds.
-Note that layer similarity in forage is not shown because individuals did not interact at landcover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
-D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
+Note that layer similarity in forage is not shown because individuals did not interact at land cover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
+D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing land cover resolution.
 
@@
 A) Mean graph strength across individuals in summer layers was weak but stable across increasing lengths of time except for a slight increase in strength for open and forage habitats when the season lasted more than 70 days.
-Mean graph strength was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
+Mean graph strength was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between land cover types as window length increased.
 B) Mean layer relevance increased for summer layers across habitat classes and was stable for winter layers.
@@
 different scales and units of measurement. Our analysis of caribou multilayer
-networks which incorporated high resolution GPS telemetry data and spatial landcover
+networks which incorporated high resolution GPS telemetry data and spatial land cover
 data is grounded in the context of observed animal social networks, as the

### 2020-06-11 paper/manuscript.Rmd
just render md for now

@@
    bookdown::github_document2: default
-   bookdown::word_document2:
-     reference_docx: template.docx
+   # bookdown::word_document2:
+   #   reference_docx: template.docx
 knit: (function(inputFile, encoding) {

### 2020-06-11 paper/manuscript.Rmd
adjust input DT
adjust fig paths

@@
 library(data.table)
-DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
+DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
 ```
@@
 ```{r spacetime, fig.cap='(ref:spacetime)'}
-knitr::include_graphics('../graphics/figure1.png')
+knitr::include_graphics('../graphics/figure-1.png')
 ```
@@
 
-```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-spatialthreshold.png')
+```{r lcres, fig.cap='(ref:lcres)'}
+knitr::include_graphics('../graphics/figure-3.png')
 ```
@@
 
-```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lcres.png')
+<!-- TODO: fix to temp -->
+```{r winlen, fig.cap='(ref:winlen)'}
+knitr::include_graphics('../graphics/figure-4.png')
+```
+
+\newpage
+
+```{r socres, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-5.png')
 ```
@@
 ```{r nobs, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-nobs.png')
-```
-
-\newpage
-
-```{r winlen, fig.cap='(ref:winlen)'}
-knitr::include_graphics('../graphics/figure-winlength.png')
-```
-
-\newpage
-
-```{r winpos, fig.cap='(ref:winpos)'}
-knitr::include_graphics('../graphics/figure-winpos.png')
+knitr::include_graphics('../graphics/figure-6.png')
 ```

### 2020-06-11 paper/manuscript.Rmd
car socio

@@
 is presumed to be a costly behaviour and as a result, caribou tend to occupy and
-re-use craters once they are established and there is considerably less access
-to forage than when the landscape is snow-free. Importantly, craters exist on
+re-use craters once they are established. <!-- and there is considerably less access
+to forage than when the landscape is snow-free.--> Importantly, craters exist on
 the landscape at multiple scales: the crater scale (a single crater), the
 feeding area scale (multiple craters in close proximity), and the winter range
-scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
-of forage for caribou is therefore seasonally heterogeneous because the
-distribution of craters on the landscape varies meaning that access to
-vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
-greater access to forage in snow-free seasons. <!--We partitioned data into two
+scale (all craters within an individual’s range) [@Mayor_2009]. Access to forage is 
+seasonally heterogeneous depending on snow cover and, in winter, variable distribution of craters on the 
+landscape. <!--We partitioned data into two
 discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2017, 2018 and 2019.
-Adult female caribou were immobilized and fitted with global positioning system
-(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
-1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
-location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
-discrete removed all erroneous and outlier GPS fixes following
-[@Bjorneraas_2010]. We did not collar all caribou in
-the herd; however, the proportion of marked adult females was ~10% of all adult
-females and ~5% of all individuals in the herd. We assumed these individuals
-were randomly distributed throughout the population.
+We used GPS location data collected from Fogo Island caribou in 2017, 2018 and
+2019. Adult female caribou were immobilized and fitted with global positioning
+system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
+collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
+collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
+to remove all erroneous and outlier GPS fixes following
+[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
+proportion of marked adult females was ~10% of all adult females and ~5% of all
+individuals in the herd. We assumed these individuals were randomly distributed
+throughout the population.
 

### 2020-06-11 paper/manuscript.Rmd
min max date
lc

@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou in 2017, 2018 and
-2019. Adult female caribou were immobilized and fitted with global positioning
+We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Adult female caribou were immobilized and fitted with global positioning
 system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
@@
 types at 30 m resolution. We reclassified the land cover types into three
-categories: foraging habitat, open habitat, and forest habitat using the R
-package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
-open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
-types, while forest habitat consisted of coniferous forest, conifer scrub,
+categories using the R
+package `raster` [@Hijmans_2019]: foraging, open, and forest habitats. Foraging habitat consisted of lichen,
+open habitat consisted of wetland, rocky barrens, and anthropogenic, while forest habitat consisted of coniferous forest, conifer scrub,
 broad leaf forest, and mixed-wood forest. Water habitat was excluded from all

### 2020-06-11 paper/manuscript.Rmd
start layers

@@
 
-### Network types and construction
-We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
+### Network layer construction
+<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
 individual nodes and two aspects (season and land cover). Two season
@@
 network layers were generated using the R package `spatsoc` [@Robitaille_2019]
-in `r version$version.string` [@R_Core_Team_2019].
+in `r version$version.string` [@R_Core_Team_2019].-->
 
-Within each layer, we assumed individuals were associating if simultaneous GPS
-fixes, i.e., recorded within 5 minutes of each other, were within a given
-spatial distance of one another. Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
+<!-- TODO: better lead in -->
+Within each layer, we generated proximity-based social networks using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We 
+assumed individuals were associating if simultaneous GPS
+fixes, i.e., recorded within 5 minutes of each other, were within the spatial distance 
+threshold of one another. Typically for ungulates and other gregarious
+mammals, the ‘chain rule’ is applied for group assignment. <!-- TODO: simplify here-->For GPS data, the
 chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
@@
 $y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
-separated by more than the given distance [@Farine_2015]. Social groups were
+separated by more than the given distance [@Farine_2015]. <!-- TODO: rm repeat?-->Social groups were
 designated if two or more individuals occurred within a given distance of one
@@
 visual (short distance) to auditory (long distance) sensory modalities of
-caribou.
+caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->
 

### 2020-06-11 paper/manuscript.Rmd
network construction

@@
 
-<!-- TODO: better lead in -->
-Within each layer, we generated proximity-based social networks using the R package `spatsoc` [@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We 
-assumed individuals were associating if simultaneous GPS
-fixes, i.e., recorded within 5 minutes of each other, were within the spatial distance 
-threshold of one another. Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is applied for group assignment. <!-- TODO: simplify here-->For GPS data, the
-chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
-distance formed a contiguous buffer for two or more individuals, even if some
-individuals within the buffer were not within the given distance of one another
-[@Robitaille_2019]. Group assignment based on the chain rule has previously been
-applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
+We generated proximity-based social networks using the R package `spatsoc`
+[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
+individuals were associating if simultaneous GPS fixes were within the spatial
+distance threshold of one another. Typically for ungulates and other gregarious
+mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
+data, the chain rule is applied by assigning a group identifier to the union of
+buffered GPS fixes at each time step. As such, individuals in a group are within
+the spatial distance threshold of at least one other though not necessarily all
+other individuals [@Robitaille_2019]. Group assignment based on the chain rule
+has previously been applied to caribou using a temporal treshold of 5 minutes
+and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].
+
+<!--In
 all networks, individual caribou were represented as nodes, associations between
@@
 edges, and connections between the same individuals across seasons and within
-habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
+habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .-->
 <!-- eg this is connecting contexts used to calculate layer similarity -->

### 2020-06-11 paper/manuscript.Rmd
sri

@@
 
-where x is the number of fixes where individuals A and B were within a given
-distance of each other, $y_{A}$ is the number of fixes from individual A when
-individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
-from individual B when individual A did not have a simultaneous fix, and
-$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
-separated by more than the given distance [@Farine_2015]. <!-- TODO: rm repeat?-->Social groups were
-designated if two or more individuals occurred within a given distance of one
-another at any given time point.
-
-(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
-Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
-Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
-individual "A" in summer, forest and individual "A" in winter, forest).
+where x is the number of fixes where individuals A and B were in the same group,
+$y_{A}$ is the number of fixes from individual A when individual B did not have
+a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
+individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
+simultaneous fixes from individuals A and B that were separated by more than the
+spatial distance threshold [@Farine_2015].
 

### 2020-06-11 paper/manuscript.Rmd
mv

@@
 
+(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
+Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
+Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
+individual "A" in summer, forest and individual "A" in winter, forest).
+
 ```{r ml, fig.cap='(ref:ml)'}

### 2020-06-11 scripts/05-number-of-observations.R
calc multidegree

@@ -72,8 +72,11 @@ graphs <- lapply(seq(10, maxn, by = nstep), function(n) {
   # Calculate neighbors
   layer_neighbors(sub, idcol, splitBy = splitBy)
   
+  # Calculate multidegree
+  multi_degree(sub, 'splitNeigh', idcol, splitBy)
+  
   # and tidy output, prep for merge
-  outcols <- c('neigh', 'splitNeigh', idcol, splitBy)
+  outcols <- c('neigh', 'splitNeigh', 'multideg', idcol, splitBy)
   usub <- unique(sub[, .SD, .SDcols = outcols])
   usub[, layer := paste(lc, n, sep = '-')]
   
@@ -99,7 +102,7 @@ eLs <- list_edges(gLs)
 eovr <- edge_overlap(eLs)
 eovr[, c('lc', 'nobs') := tstrsplit(layer, '-', type.convert = TRUE)]
 
-out <- outLs[eovr, on = c('lc', 'nobs')]
+out <- outLs[eovr, on = 'layer']
 
 # Output ------------------------------------------------------------------
 saveRDS(out, 'data/derived-data/05-number-of-observations.Rds')

### 2020-06-11 paper/manuscript.Rmd
reflow, tidy

@@
 Land cover data were provided by the Newfoundland and Labrador Wildlife Division
-[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification included nine habitat
-types at 30 m resolution. We reclassified the land cover types into three
-categories using the R
-package `raster` [@Hijmans_2019]: foraging, open, and forest habitats. Foraging habitat consisted of lichen,
-open habitat consisted of wetland, rocky barrens, and anthropogenic, while forest habitat consisted of coniferous forest, conifer scrub,
-broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
-subsequent analyses.
+[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification
+included nine habitat types at 30 m resolution. We reclassified the land cover
+types into three categories using the R package `raster` [@Hijmans_2019]:
+foraging, open, and forest habitats. Foraging habitat consisted of lichen, open
+habitat consisted of wetland, rocky barrens, and anthropogenic, while forest
+habitat consisted of coniferous forest, conifer scrub, broad leaf forest, and
+mixed-wood forest. Water habitat was excluded from all subsequent analyses.
 
@@
 (forage, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals linked by social associations, for each season and land cover combination. Proximity-based social
-network layers were generated using the R package `spatsoc` [@Robitaille_2019]
-in `r version$version.string` [@R_Core_Team_2019].-->
+composed of individuals linked by social associations, for each season and land cover combination.-->
 
@@
 other individuals [@Robitaille_2019]. Group assignment based on the chain rule
-has previously been applied to caribou using a temporal treshold of 5 minutes
+has previously been applied to caribou using a temporal threshold of 5 minutes
 and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].
@@
 coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
-`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
-<!-- add used spatsoc -->
+`igraph` [@Csardi_2006], `asnipe` [@Farine_2019], `spatsoc`
+[@Robitaille_2019] and `data.table` [@Dowle_2019].
 

### 2020-06-11 scripts/05-number-of-observations.R
not necessary

@@ -100,7 +100,6 @@ eLs <- list_edges(gLs)
 
 # Calculate edge overlap
 eovr <- edge_overlap(eLs)
-eovr[, c('lc', 'nobs') := tstrsplit(layer, '-', type.convert = TRUE)]
 
 out <- outLs[eovr, on = 'layer']
 

### 2020-06-11 paper/manuscript.Rmd
net mets

@@
 We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals, importance of individual layers, and the similarity of
-different layers. To measure the role of individuals, we calculated degree
-centrality and graph strength. Degree centrality is the number of direct
-connections an individual has to other individuals in a network layer. Graph
-strength is the degree weighted by the strength of association, in this case
-SRI, in each layer-specific season and land cover context. Extending degree
-centrality, we calculated multidegree, the sum of degree centrality of
-individuals across layers, and neighbourhood, the sum of unique neighbours to
-each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
-the relevance and redundancy of layers by combining the multidegree and
-neighbourhood to calculate layer relevance and connective redundancy. Layer
-relevance is the proportion of neighbours present in each layer compared to the
-neighbourhood for each individual and connective redundancy is the proportion of
-neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
-calculated the similarity of layers between seasons, across land cover classes
-(e.g. summer open compared to winter open) using the Pearson correlation
-coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
-`igraph` [@Csardi_2006], `asnipe` [@Farine_2019], `spatsoc`
-[@Robitaille_2019] and `data.table` [@Dowle_2019].
+the role of individuals within and across layers, and the similarity of
+different layers. To measure the role of individuals within layers, we
+calculated degree centrality and graph strength. Degree centrality is the number
+of direct connections an individual has to other individuals in a network layer.
+Graph strength is the degree weighted by the strength of association, in this
+case SRI, in each layer. Extending degree centrality, we calculated multidegree,
+the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
+@Kivela_2014]. <!--We evaluated the relevance and redundancy of layers by
+combining the multidegree and neighbourhood to calculate layer relevance and
+connective redundancy. Layer relevance is the proportion of neighbours present
+in each layer compared to the neighbourhood for each individual and connective
+redundancy is the proportion of neighbours repeated in multiple layers, and
+[@Berlingerio_2012].--> Finally, we measured the similarity of layers by
+calculating edge overlap. Edge overlap is defined as the proportion of edges
+present in each network layer out of all observed edges  [@Battiston_2014].
+<!--between seasons, across land cover classes (e.g. summer open compared to
+winter open) using the Pearson correlation coefficient [@Brodka_2018].-->
+Network metrics were calculated using the R packages `igraph` [@Csardi_2006],
+`asnipe` [@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table`
+[@Dowle_2019].
 
@@
 # Results
+
+<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
 

### 2020-06-11 scripts/05-number-of-observations.R
more n obs

@@ -31,7 +31,7 @@ group_times(
 
 # Generate networks for each n observations -------------------------------
 maxn <- 1000
-nstep <- 50
+nstep <- 10
 
 # Randomly select n max observations
 randobs <- DT[!is.na(lc), sample(unique(timegroup), size = maxn), lc]

### 2020-06-11 paper/manuscript.Rmd
parse scales, edits social scale

@@
 ## Varying scale in multilayer networks
+<!--
+
+social scale: variable is spatial distance threshold
+spatial scale: variable is land cover resolution
+temporal scale: variable is temporal window
+temporal scale: variable is number of observations
+-->
+
 ### Social scale
 
-We modified the distance threshold, hereafter the social <!--distance-->threshold, required for
+We modified the spatial distance threshold used for
 group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
-incremental distances between 5 - 500 m. For example, at the finest social
+incremental distances between 5 and 500 m (5, 25, 50, 75, 100, 250, 500). For example, at the finest
 scale, only individuals within 5 m of one another were considered in the same
-group, whereas at the coarsest social scale, individuals within 500 m of one
+group, whereas at the coarsest scale, individuals within 500 m of one
 another were considered in the same group. We assumed these scales represented

### 2020-06-11 paper/manuscript.Rmd
soc scale

@@
 
-We modified the spatial distance threshold used for
-group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
-incremental distances between 5 and 500 m (5, 25, 50, 75, 100, 250, 500). For example, at the finest
-scale, only individuals within 5 m of one another were considered in the same
-group, whereas at the coarsest scale, individuals within 500 m of one
-another were considered in the same group. We assumed these scales represented
-visual (short distance) to auditory (long distance) sensory modalities of
-caribou. <!-- TODO: clarify not attempting ML with multiple behaviours -->
+We generated multilayer networks across a series of spatial distance thresholds
+for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
+500 m) represented a range of visual (short distance) to auditory (long
+distance) sensory modalities of caribou. Multilayer networks consisted of the
+social association between `r DT[, uniqueN(get(idcol))]` individuals across
+three habitat layers (open, forest and forage). At the finest scale, individuals
+within 5 m of one another were considered in the same group, whereas at the
+coarsest scale, individuals within 500 m of one another were considered in the
+same group. We calculated graph strength and multidegree for each habitat layer
+and spatial distance threshold, and edge overlap across the entire series of
+networks to determine proportion of total edges observed in each combination of
+habitat layer and spatial distance threshold.
 
@@
 To assess the influence of spatial scale on multilayer networks, we aggregated
-our land cover raster at varying scales relevant to caribou ecology. We
+our land cover raster at varying scales <!--relevant to caribou ecology. We
 aggregated the 30 m land cover raster using the R package `grainchanger`

### 2020-06-11 paper/manuscript.Rmd
spat scale

@@
 social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and forage). At the finest scale, individuals
+three habitat layers (open, forest and forage) for the entire study period. At the finest scale, individuals
 within 5 m of one another were considered in the same group, whereas at the
@@
 
-To assess the influence of spatial scale on multilayer networks, we aggregated
-our land cover raster at varying scales <!--relevant to caribou ecology. We
-aggregated the 30 m land cover raster using the R package `grainchanger`
-[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
-occurred using a modal moving window method using a circular window
-corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
-represents fine-scale decision making for caribou during foraging, while
-re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
-select and avoid habitat (Bastille-Rousseau et al. 2017).
+To assess the influence of spatial scale, we aggregated our land cover raster at
+varying scales relevant to caribou ecology. We aggregated the original 30 m land
+cover raster using the R package `grainchanger` [@Graham_2019] across a series
+of scales (100 - 1000 m by 100 m steps) The land cover raster was aggregated
+using a modal moving window method using a circular window corresponding to the
+above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
+decision making for caribou during foraging, while re-sampling at 500 m , 750 m
+and 1000 m represents the scale at which caribou tend to select and avoid
+habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
+multilayer network consisting of the social association between `r DT[,
+uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
+forage) for the entire study period. We calculated graph strength and
+multidegree for each habitat layer and spatial scale, and edge overlap across
+the entire series of networks to determine proportion of total edges observed in
+each combination of habitat layer and spatial scale.
 

### 2020-06-11 paper/manuscript.Rmd
reorder

@@
 ### Temporal scale
+#### Time window length and position
+We altered the temporal scale of multilayer networks by varying the length and
+position of the time window used to define seasons. The length of the time
+window varied from 40-100 days using a fixed start day for summer (starting at 3
+August 2017) and winter (starting at 1 January 2018). The position of the time
+window was shifted by 1-48 days, using a fixed time window length of 48 days.
+These new time windows were iteratively used to partition data into two discrete
+seasons (summer and winter) and generate multilayer networks.
+
 #### Number of observations
@@
 set of observations to mimic collection of observational data.
-
-#### Time window length and position
-We altered the temporal scale of multilayer networks by varying the length and
-position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for summer (starting at 3
-August 2017) and winter (starting at 1 January 2018). The position of the time
-window was shifted by 1-48 days, using a fixed time window length of 48 days.
-These new time windows were iteratively used to partition data into two discrete
-seasons (summer and winter) and generate multilayer networks.
 

### 2020-06-11 paper/manuscript.Rmd
start temp scale

@@
 
-To assess the influence of spatial scale, we aggregated our land cover raster at
+To assess the influence of spatial scale, we aggregated the land cover raster at
 varying scales relevant to caribou ecology. We aggregated the original 30 m land
@@
 ### Temporal scale
+We used a temporal multilayer network to assess seasonality of caribou social
+associations. We generated layers
+
 #### Time window length and position

### 2020-06-11 paper/manuscript.Rmd
rename, rm fig numbs from scripts and output pngs

@@
 <!-- Figure: metrics by number of observations -->
-(ref:nobs) Varying scale in number of observations.
+<!-- TODO: update to temp -->
+<!-- (ref:nobs) Varying scale in number of observations.
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
@@
 D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
+-->
 
 <!-- Figure: Window length -->
-(ref:winlen) Varying temporal scale in time window length.
+<!-- (ref:winlen) Varying temporal scale in time window length.
 For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
@@
 D) Mean connective redundancy across individuals increased marginally with increasing window length.
+-->
 
@@
 ```{r spacetime, fig.cap='(ref:spacetime)'}
-knitr::include_graphics('../graphics/figure-1.png')
+knitr::include_graphics('../graphics/figure-scales.png')
 ```
@@
 ```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-2.png')
+knitr::include_graphics('../graphics/figure-ml.png')
 ```
@@
 ```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-3.png')
+knitr::include_graphics('../graphics/figure-lc.png')
 ```
@@
 
-<!-- TODO: fix to temp -->
-```{r winlen, fig.cap='(ref:winlen)'}
-knitr::include_graphics('../graphics/figure-4.png')
+```{r temp, fig.cap='(ref:temp)'}
+knitr::include_graphics('../graphics/figure-temp.png')
 ```
@@
 ```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-5.png')
+knitr::include_graphics('../graphics/figure-soc.png')
 ```
@@
 ```{r nobs, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-6.png')
+knitr::include_graphics('../graphics/figure-nobs.png')
 ```

### 2020-06-11 scripts/figures/figure-lc.R

@@ -1,4 +1,4 @@
-# === Figure 3 ------------------------------------------------------------
+# === Figure: Land Cover Resolution ---------------------------------------
 # Land Cover Resolution
 # Alec Robitaille
 
@@ -117,7 +117,7 @@ layout <- 'AABBCC
 
 
 # Output ------------------------------------------------------------------
-ggsave('graphics/figure-3.png',
+ggsave('graphics/figure-lc.png',
        g, width = 10, height = 10)
 
 ggsave('graphics/supp-count-lc.png',

### 2020-06-11 paper/manuscript.Rmd
temp scale

@@
 social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and forage) for the entire study period. At the finest scale, individuals
-within 5 m of one another were considered in the same group, whereas at the
-coarsest scale, individuals within 500 m of one another were considered in the
-same group. We calculated graph strength and multidegree for each habitat layer
-and spatial distance threshold, and edge overlap across the entire series of
-networks to determine proportion of total edges observed in each combination of
-habitat layer and spatial distance threshold.
+three habitat layers (open, forest and forage) for the entire study period. At
+the finest scale, individuals within 5 m of one another were considered in the
+same group, whereas at the coarsest scale, individuals within 500 m of one
+another were considered in the same group. We calculated graph strength and
+multidegree for each habitat layer and spatial distance threshold, and edge
+overlap across the entire series of networks to determine proportion of total
+edges observed in each combination of habitat layer and spatial distance
+threshold.
 
@@
 uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
-forage) for the entire study period. We calculated graph strength and
-multidegree for each habitat layer and spatial scale, and edge overlap across
-the entire series of networks to determine proportion of total edges observed in
-each combination of habitat layer and spatial scale.
+forage) for the entire study period. Social associations of individuals were
+defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
+strength and multidegree for each habitat layer and spatial scale, and edge
+overlap across the entire series of networks to determine proportion of total
+edges observed in each combination of habitat layer and spatial scale.
 
 ### Temporal scale
-We used a temporal multilayer network to assess seasonality of caribou social
-associations. We generated layers
+#### Time windows
 
-#### Time window length and position
-We altered the temporal scale of multilayer networks by varying the length and
-position of the time window used to define seasons. The length of the time
-window varied from 40-100 days using a fixed start day for summer (starting at 3
-August 2017) and winter (starting at 1 January 2018). The position of the time
-window was shifted by 1-48 days, using a fixed time window length of 48 days.
-These new time windows were iteratively used to partition data into two discrete
-seasons (summer and winter) and generate multilayer networks.
+We used a temporal multilayer network to assess the seasonality of caribou
+sociality. Multilayer networks consisted of the social association between `r
+DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
+days from the entire study period. Social associations of individuals were
+defined by spatiotemporal overlap within 5 minutes and 50 m. Within each time
+window, we calculated individual's graph strength and multidegree. We calculated
+edge overlap across the entire series of networks to determine proportion of
+total edges observed in each time window.
 
@@
 period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies.We
+have been observed and recorded in traditional ethological studies. We
 investigated the influence of the number of observations on resulting multilayer

### 2020-06-11 paper/manuscript.Rmd
nobs

@@
 cover raster using the R package `grainchanger` [@Graham_2019] across a series
-of scales (100 - 1000 m by 100 m steps) The land cover raster was aggregated
+of scales (100 - 1000 m by steps of 100 m) The land cover raster was aggregated
 using a modal moving window method using a circular window corresponding to the
@@
 habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social association between `r DT[,
-uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
+multilayer network consisting of the social association between 
+`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
 forage) for the entire study period. Social associations of individuals were
@@
 We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social association between `r
-DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
-days from the entire study period. Social associations of individuals were
-defined by spatiotemporal overlap within 5 minutes and 50 m. Within each time
-window, we calculated individual's graph strength and multidegree. We calculated
-edge overlap across the entire series of networks to determine proportion of
+sociality. Multilayer networks consisted of the social association between 
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
+days taken from the entire study period. Social associations were
+defined by spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
+window, we calculated individual graph strength and multidegree, and across the series of networks, we calculated edge overlap to determine proportion of
 total edges observed in each time window.
@@
 period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies. We
-investigated the influence of the number of observations on resulting multilayer
-networks. We randomly selected a maximum 485 timesteps for each season to
-represent all possible observations. We regenerated multilayer networks and
-calculated associations of individuals with 25 additional observations at each
-iteration (10 - 485 observations). Subsequent iterations included the previous
-set of observations to mimic collection of observational data.
+have been observed and recorded in traditional ethological studies.
+To investigate the influence of number of observations, we generated multilayer networks of social association between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and forage) using $N$ randomly selected observations.
+We first generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to ensure previously included timesteps, and resulting associations, were accumulated with subsequent observations to mimic collection of observational data.
+Within each multilayer network with $N$ observations, we calculated individual graph strength and multidegree.
+We calculated
+edge overlap across the entire series of networks to determine proportion of
+total edges as number of observations increased.
 

### 2020-06-11 paper/manuscript.Rmd
add todo spat scale

@@
 ### Spatial scale
-
-To assess the influence of spatial scale, we aggregated the land cover raster at
-varying scales relevant to caribou ecology. We aggregated the original 30 m land
-cover raster using the R package `grainchanger` [@Graham_2019] across a series
-of scales (100 - 1000 m by steps of 100 m) The land cover raster was aggregated
+<!-- TODO: Increased spatial scale of land cover corresponds to xyz -->
+To assess the influence of spatial scale, we aggregated the land cover raster using the R package `grainchanger` [@Graham_2019] across a series
+of scales (100 - 1000 m by steps of 100 m). The land cover raster was aggregated
 using a modal moving window method using a circular window corresponding to the

### 2020-06-11 paper/manuscript.Rmd
start caps

@@
 <!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in social threshold.
-For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals showed an increase for winter network layers while summer network layers had consistently weak connections.
-B) Mean layer relevance was increased for winter layers between 5 m and 50 m, otherwise stable for all social thresholds >50 m for winter and all social thresholds for summer.
-C) Similarity of network layers across seasons and within habitat classes (e.g.
-open summer compared to open winter) was relatively stable for all habitat class layers.
-D) Mean connective redundancy across individuals showed an increase between 5 m and 50 m before remaining stable through all other social thresholds.
+(ref:socres) Varying scale in spatial distance threshold.
+For each spatial distance threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+Graph strength showed a sharp increase between 5 m and 100 m for all habitat classes.
+After 100 m, graph strength continued to increase at a slower rate.
+Open and forage layers showed higher variation in graph strength between individuals while the forest layer had
+
+less variation, overall lower strength
 
 <!-- Figure: metrics by land cover resolution -->
-(ref:lcres) Varying spatial scale in land cover resolution.
-For each land cover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength of individuals in summer layers had consistent weak connections.
-Individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
-B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher land cover resolutions.
-C) Similarity of land cover network layers between seasons (e.g.
-open summer compared to open winter) forage and forest habitats but showed more variation in open habitats with increasing social thresholds.
-Note that layer similarity in forage is not shown because individuals did not interact at land cover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
-D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing land cover resolution.
+(ref:lcres) Varying spatial scale of land cover raster.
+
+For each land cover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+A, B, C) Three land cover rasters include the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
+D) Edge overlap of habitat layers across spatial resolutions.
+Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m.
+Above 600 m, the forage layers are stable
+
+E) Graph strength within habitat layers across spatial resolution.
+
+high variability and maximum in  forage
+relatively stable in forest
+moderate variability in open
 
@@
 <!-- TODO: update to temp -->
-<!-- (ref:nobs) Varying scale in number of observations.
+(ref:nobs) Varying scale in number of observations.
 For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
@@
 D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
--->
 
 <!-- Figure: Window length -->
-<!-- (ref:winlen) Varying temporal scale in time window length.
-For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals in summer layers was weak but stable across increasing lengths of time except for a slight increase in strength for open and forage habitats when the season lasted more than 70 days.
-Mean graph strength was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between land cover types as window length increased.
-B) Mean layer relevance increased for summer layers across habitat classes and was stable for winter layers.
-C) Similarity of layers across habitat classes and between seasons (e.g.
-open summer compared to open winter) was variable with increasing window lengths, particularly for forage and open habitat types.
-D) Mean connective redundancy across individuals increased marginally with increasing window length.
--->
-
-<!-- Figure: Window position -->
-(ref:winpos) Varying temporal scale in time window position.
-For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
-B) Mean layer relevance increased for summer layers and slightly decreased for winter layers.
-C) Similarity of layers across habitat classes and between seasons (e.g.
-open summer compared to open winter) was relatively stable until window position ~28 where forage and open layer similarity decreased.
-D) Mean connective redundancy across individuals increased marginally with advancing time window position.
+(ref:temp) Varying temporal scale in time window length.
 
 # Discussion
+
+<!-- TODO: caveat social scale could also be diff types of relationships but GPS but point to hmm -->
 

### 2020-06-12 paper/manuscript.Rmd
todo conc
fin soc cap

@@
 For each spatial distance threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-Graph strength showed a sharp increase between 5 m and 100 m for all habitat classes.
+Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
 After 100 m, graph strength continued to increase at a slower rate.
 Open and forage layers showed higher variation in graph strength between individuals while the forest layer had
-
-less variation, overall lower strength
+less variation and lower mean graph strength.
 
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-
 For each land cover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-A, B, C) Three land cover rasters include the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
+A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
 D) Edge overlap of habitat layers across spatial resolutions.
 Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m.
-Above 600 m, the forage layers are stable
-
+Above 600 m, the forage layers are stable.
 E) Graph strength within habitat layers across spatial resolution.
@@
 
+<!-- TODO: push gps data, HMM networks, etc-->
+
 Multilayer networks remain a nascent but powerful tool in animal behavioural

### 2020-06-12 paper/manuscript.Rmd
fin lc cap

@@
 Above 600 m, the forage layers are stable.
-E) Graph strength within habitat layers across spatial resolution.
-
-high variability and maximum in  forage
-relatively stable in forest
-moderate variability in open
+E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
+Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
+Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
 

### 2020-06-12 paper/manuscript.Rmd
add nobs data to man
fix path
fin nobs cap

@@
 DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
+nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
 ```
@@
 (ref:socres) Varying scale in spatial distance threshold.
-For each spatial distance threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
 After 100 m, graph strength continued to increase at a slower rate.
-Open and forage layers showed higher variation in graph strength between individuals while the forest layer had
-less variation and lower mean graph strength.
+Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
 
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
-A) Mean graph strength across individuals remained weak throughout for summer layers and varied for winter layers becoming relatively stable by 100 observations.
-B) Mean layer relevance across individuals in summer layers had consistent low layer relevance but increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing.
-C) Similarity of network layers across habitat classes and between seasons (e.g.
-open summer compared to open winter) was relatively consistent across number of observations for forest and open habitats.
-Note, forage habitats are not shown given no individuals interacted in the summer forage layer.
-D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
+Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
+B) Edge overlap increased for all habitat layers with increasing number of observations.
+Open and forage layers had higher edge overlap than forest layers.
+C) Multidegree increased for all individuals with increasing number of observations.
+Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
 

### 2020-06-12 paper/manuscript.Rmd
fin temp cap

@@
 `r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
-days taken from the entire study period. Social associations were
-defined by spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
-window, we calculated individual graph strength and multidegree, and across the series of networks, we calculated edge overlap to determine proportion of
-total edges observed in each time window.
+days taken from the entire study period. Social associations were defined by
+spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
+window, we calculated individual graph strength and multidegree, and across the
+series of networks, we calculated edge overlap to determine proportion of total
+edges observed in each time window.
 
@@
 <!-- Figure: Window length -->
-(ref:temp) Varying temporal scale in time window length.
+(ref:temp) Varying temporal scale in multilayer networks.  
+Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
+B) Ordinal network layers showing unweighted edges between individuals within time windows.
+Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
+C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
+Graph strength peaked in time window 9, with noticeable higher strength than the following year.
+
+<!-- a bit more for g strength? -->
 

### 2020-06-13 paper/manuscript.Rmd
soc result

@@
 # Results
+<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
+<!-- TODO: Add intro/general to results?-->
+<!-- major points then details -->
 
-<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
-
-<!-- TODO: Add intro/general to results?-->
-In general, individuals in multilayer networks became more connected as social
-scale increased; however, this relationship varied by habitat type and season.
-As social scale increased, mean graph strength for summer networks did not
-change as the social threshold increased, but graph strength in winter networks
-increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
-\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
-increased for winter networks between 5 and 50 m social thresholds, then did not
-change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
-the winter habitat layers captured most, if not all, of the potential
-connections an individual would have across these networks. Layer similarity was
-not very strong for any habitat type, indicating that summer and winter networks
-are only weakly correlated. Furthermore, layer similarity in open habitats
-showed more variation as social threshold increased compared to forage and
-forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
-relatively stable across social thresholds, especially after 50 m (Figure
-\@ref(fig:socres)d). Taken together, these results suggest the optimal social
-scale at which groups should be assigned is likely somewhere between ~20 - 100 m
-based on the rate at which network metrics stabilized. For ungulates, groups are
-often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
-Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
-is likely an appropriate social scale for generating social networks in caribou
-and similar species.
+In general, individuals in multilayer networks became more connected as the
+spatial distance threshold defining caribou social associations increased. Mean
+graph strength differed across habitat layers with similar and higher graph
+strength in open and forage layers, and lower strength in forest layers (Figure
+\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
+100 m across habitat classes followed by decrease in rate after 100 m. These
+results suggest the optimal social scale at which groups should be assigned is
+likely somewhere between ~20 - 100 m based on the rate at which network metrics
+stabilized. For ungulates, groups are often assigned based on 50 m threshold
+(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
+given similar quantities of data, ~50 m is likely an appropriate social scale
+for generating social networks in caribou and similar species.
 

### 2020-06-13 paper/manuscript.Rmd
lc result

@@
 a rare and patchy habitat, and corresponding low connectivity of individuals in
-these habitats. Individuals in summer layers had consistent weak connections
-(Figure \@ref(fig:lcres)a). Mean graph strength increased consistently in winter
-forest and open habitats but varied in winter forage varied across land cover
-resolutions with an increase at 250 m and decrease at 500 m (Figure
-\@ref(fig:lcres)a). Layer relevance was stable for all habitat classes in summer
-layers; layer relevance was significantly higher in winter and stable in open
-and forest habitats but decreased for forage habitats (Figure
-\@ref(fig:lcres)b). <!--This pattern during the winter indicates that
-individuals had fewer neighbours in forage habitat habitats compared to their
-overall neighbourhood across habitats, likely due to the patchy nature of
-forage-->Layer similarity was low but stable for forest and open, except for a
-sharp decrease in layer similarity in open at 100 m and 250 m (Figure
-\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
-summer and winter forage because, at all land cover resolutions greater than 30
-m, there were no individuals connected in the network layers. Individuals still
-used forage habitats, but given the lower availability due to increasing
-land cover resolution, at a much lower rate. Connective redundancy was moderately
-high but decreased slightly as land cover resolution increased, indicating that
-many neighbours were the same between layers, but the proportion of neighbours
-in each layer slightly decreased at increasing land cover resolutions (Figure
-\@ref(fig:lcres)d). Overall, these results indicate the importance of matching
-land cover resolution to scale of selection as well as ensuring the land cover
-product used has a resolution fine enough to detect landscape features and
-habitats relevant to study species, such as important patchy and rare habitats.
+these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
+and edge overlap was relatively consistent across land cover resolutions for
+forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
+sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
+1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
+forage layers across land cover resolutions than open and forest (Figure
+\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
+increased with increasing spatial resolution, while decreasing in forage habitat
+(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
+matching land cover resolution to scale of selection as well as ensuring the
+land cover product used has a resolution fine enough to detect landscape
+features and habitats relevant to study species, such as important patchy and
+rare habitats.
 

### 2020-06-13 paper/manuscript.Rmd
reorg mv temp above nobs
start temp
tidy, rm

@@
 
+The ordinal multilayer network generated from discrete time windows indicated 
+within-year periods of increased caribou sociality. Edge overlap
+
+(Figure \@ref(fig:temp) )
+These
+results suggest that an increasing window length, especially for the summer
+season, may be resulting in less precisely defined seasons that are not clearly
+capturing periods of aggregation and dissaggregation related to resource
+availability.
+
+changing the position of the
+time window in this case results in a mismatch between expected periods of
+resource seasonality and corresponding sociality, particularly for the summer,
+highlighting the importance of carefully selecting temporal scale of analysis.
+
 As the number of observations used to generate multilayer networks increased,
@@
 networks -->
-
-Some multilayer network metrics were strongly influenced by the length of the
-time window. Mean graph strength was weak but became slightly stronger with
-increasing time window length during the summer, but the higher mean graph
-strength during the winter showed a slight increase then decrease with
-increasing winter length (Figure \@ref(fig:winlen)a). Layer relevance increased
-for all summer layers as individuals became more connected with increasing
-window lengths, but winter layers showed relatively stable but high layer
-relevance (Figure \@ref(fig:winlen)b). This pattern indicates that the
-proportion of neighbours that were the same across layers increased with a
-longer time frame during the summer, but there were a high proportion of
-neighbors that remained the same across layers during the winter, regardless of
-time length. Furthermore, though the layers were generally not very similar
-between the summer and winter, the length of the time window created slight
-variability in this metric, particularly for forage and open habitat types
-(Figure \@ref(fig:winlen)c). Connective redundancy increased marginally with
-increasing window length, indicating that the proportions of neighbours that
-were the same across layers, though relatively high in general, slightly
-increased when time length was greater (Figure \@ref(fig:winlen)d). These
-results suggest that an increasing window length, especially for the summer
-season, may be resulting in less precisely defined seasons that are not clearly
-capturing periods of aggregation and dissaggregation related to resource
-availability.
-
-Moving window positions defining seasons showed some dramatic changes in the
-multilayer network metrics as the seasons were redefined. Graph strength
-increased at time window position ~20 for summer and winter layers and, while
-summer layers continued to increase, winter layers showed a decrease in graph
-strength at time window position ~35 (Figure \@ref(fig:winpos)a). Layer
-relevance increased across moving window positions for summer layers and
-slightly decreased for winter layers (Figure \@ref(fig:winpos)b). These results
-indicate increased connectivity in summer layers and slightly decreasing
-connectivity at shifted winter time windows. Layer similarity was relatively
-stable across moving window positions except for a sharp decline at window
-position ~28 in forage and open layers (Figure \@ref(fig:winpos) c). Connective
-redundancy showed a marginal increase with increasing window position indicating
-individuals had more of the same neighbours in each habitat network (Figure
-\@ref(fig:winpos) d). Similar to window length, changing the position of the
-time window in this case results in a mismatch between expected periods of
-resource seasonality and corresponding sociality, particularly for the summer,
-highlighting the importance of carefully selecting temporal scale of analysis.
 
@@
 
-<!-- Figure: Window length -->
+<!-- Figure: Time window -->
 (ref:temp) Varying temporal scale in multilayer networks.
@@
 
-<!-- a bit more for g strength? -->
+<!-- TODO: a bit more for g strength? -->
 

### 2020-06-13 paper/manuscript.Rmd
todo

@@
 
-The ordinal multilayer network generated from discrete time windows indicated 
-within-year periods of increased caribou sociality. Edge overlap
+<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
 
-(Figure \@ref(fig:temp) )
+The ordinal multilayer network generated from discrete time windows indicate
+within-year periods of increased caribou sociality.
+Edge overlap was higher in time windows 1, 6-11 and 15-20 than time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A).
+These periods between approximately October and May
+
+increasing graph strength with overall peak in 2018 but still increases in 2019
+note graph connectedness is evident panel B
+
+<!-- Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
+B) Ordinal network layers showing unweighted edges between individuals within time windows.
+Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
+C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
+Graph strength peaked in time window 9, with noticeable higher strength than the following year.
+-->
 These
@@
 
+<!-- TODO: reduce to this version -->
 As the number of observations used to generate multilayer networks increased,

### 2020-06-14 paper/manuscript.Rmd
add time defs

@@
 nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
+timedefs <- fread('../data/supp-data/timecut-defs.csv')
 ```

### 2020-06-14 paper/manuscript.Rmd
small edits lc results

@@
 
-In general, individuals in multilayer networks became more connected as the
-spatial distance threshold defining caribou social associations increased. Mean
+Individuals in multilayer networks became more connected as the
+spatial distance threshold increased. Mean
 graph strength differed across habitat layers with similar and higher graph
@@
 \@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
-100 m across habitat classes followed by decrease in rate after 100 m. These
+100 m in all three habitat classes followed by a decrease in rate after 100 m. These
 results suggest the optimal social scale at which groups should be assigned is

### 2020-06-14 paper/supplement.Rmd
fst supplement

--- 2020-06-14 paper/manuscript.Rmd
@@
 ---
-title: Considering scale in multilayer animal social networks
+title: Supplement\: Considering scale in multilayer animal social networks
 author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 
-\newpage
+Table S1: Time cut definitions
 
-# Abstract
-Scale remains a foundational concept in ecology. Spatial scale, for instance,
-has become a central consideration in the way we understand landscape ecology
-and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
-temporal scale --> Multilayer networks promise the integration of monolayer
-animal social networks with the complexity and importance of animal space use
-and movement in heterogeneous landscapes. Despite the complex interplay between
-social networks and how animals use space, there remains an important biological
-and methodological gap in our understanding of an animal’s perception of scale.
-Here we discuss the role of scale in the context of multilayer networks and
-provide a social ungulate case study to illustrate the role of social, spatial,
-and temporal scale on multilayer processes. We also present perspectives on
-future development and applications of scale in multilayer networks with respect
-to: phenotypes and individual fitness, movement ecology and collective movement,
-and habitat selection and space use. Effective integration of social and spatial
-processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research, as such our contribution
-incorporates perspectives on how the social environment and spatial processes
-are linked across scales in a multilayer context.
-
-## Keywords
-Social network analysis, Landscape ecology, Movement ecology, Space use
-
-\newpage
-
-# Introduction
-Our inference regarding the processes underlying ecological patterns
-are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales, through processes such as
-species-specific as trophic interactions and resource availability
-[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
-Multiscale ecology has been integrated into species distribution modelling
-[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
-among others. Meanwhile, in the context of animal behaviour, certain behaviours
-are scale-dependent; for example, acoustic communication in birds varies with
-spatial scales [@Luther_2009]. We posit that it is important to consider that
-animal behaviour within the social environment will be scale-dependent.
-
-Sociality exists across both temporal and spatial scales (Whitehead 2008). For
-example, grooming requires close spatial proximity between conspecifics and
-occurs over brief time periods [e.g. @Carter_2015], whereas social association
-represents shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
-associations to occur individuals must share space, and thus have overlapping
-home ranges [@Vander_Wal_2013]. In the context of the social environment, home
-range overlap is an example of how animals share space over coarser spatial and
-temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
-clearly scales spatially and temporally, it remains unclear whether coarser
-scales of sociality, including social association and home range overlap, vary
-predictably with social interaction [@Castles_2014;
-@Farine_2015a]. Thus, we define social scale as the type of social relationship
-observed that can be explicitly defined and measured [@Farine_2015a].
-
-Animal social network analysis is a well-developed tool used to measure the
-relationships of individuals and organization of social systems [@Krause_2009;
-@Wey_2008; @Croft_2011]. Social network analysis provides insight into the
-structure of social communities and social network properties, which can
-influence population dynamics and evolutionary processes [@Pinter_Wollman_2013;
-@Kurvers_2014]. Despite the widespread use and innovation of traditional social
-network analysis [@Webber_2019], it typically considers a single scale of
-sociality in a given network (monolayer), drastically simplifying the
-complexity of animal social systems [@Finn_2019].
-
-Unlike traditional monolayer social networks, multilayer networks explicitly
-consider social systems across scale-dependent contexts
-[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
-representing (i) different classes of individuals, e.g. male or female, (ii)
-types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
-areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
-[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
-studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
-used to describe multidimensional human social systems, complex transportation
-networks, and neural networks [@Silk_2018]. The role of scale within multilayer
-social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the social, spatial or temporal scales associated
-with social systems.
-
-Our examinations is motivated by behavioural, landscape, and spatial ecology to
-build a conceptual and analytical framework for scale-dependent multilayer
-networks, and we apply this framework to a case study of caribou (*Rangifer
-tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
-address two principal questions associated with scale-dependent multilayer
-networks. First, to what degree does the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influence our ability to
-interpret complex social systems? Second, can variation in the social, spatial,
-and temporal scale improve predictions associated with biological differences in
-seasonal resource availability and social association? We conclude with
-perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness,
-movement ecology and collective movement, and habitat selection
-and space use.
-<!-- TODO: we answer the first question in the discussion, but not the second-->
-<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
-
-(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants.
-Spatial and temporal extent for social interactions, e.g.
-mating, grooming, or aggression, are similar for most species because physical contact between two individuals is required for many social interactions.
-The logical extension is that spatial and temporal extent for social interaction is hierarchically nested within the spatial and temporal extent for social association because individuals must share space to interact.
-By contrast, different species have potential for greater spatial and temporal extents, for example, temporal extent for vocal communication is similar for most species because most vocal calls only persist in the environment for seconds, but spatial extent for vocal communication is highly variable with elephant calls extending the great distance and passerine calls extending the shortest distance.
-
-<!-- TODO: units of spatial scale? --> 
-<!-- TODO: citations? -->
-
-# Methods
-
-## Caribou socioecology
-<!--Here, we use caribou as a case study to develop scale-dependent multilayer
-networks based on predicted social (visual and auditory perception), spatial
-(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious ungulates
-with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
-spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
-holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
-is presumed to be a costly behaviour and as a result, caribou tend to occupy and
-re-use craters once they are established. <!-- and there is considerably less access
-to forage than when the landscape is snow-free.--> Importantly, craters exist on
-the landscape at multiple scales: the crater scale (a single crater), the
-feeding area scale (multiple craters in close proximity), and the winter range
-scale (all craters within an individual’s range) [@Mayor_2009]. Access to forage is 
-seasonally heterogeneous depending on snow cover and, in winter, variable distribution of craters on the 
-landscape. <!--We partitioned data into two
-discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
-February 2018) based on caribou socioecology [@Peignier_2019].-->
-
-## Caribou location data
-We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Adult female caribou were immobilized and fitted with global positioning
-system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
-collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
-collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
-to remove all erroneous and outlier GPS fixes following
-[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
-proportion of marked adult females was ~10% of all adult females and ~5% of all
-individuals in the herd. We assumed these individuals were randomly distributed
-throughout the population.
-
-## Landscape data and habitat classification
-Land cover data were provided by the Newfoundland and Labrador Wildlife Division
-[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification
-included nine habitat types at 30 m resolution. We reclassified the land cover
-types into three categories using the R package `raster` [@Hijmans_2019]:
-foraging, open, and forest habitats. Foraging habitat consisted of lichen, open
-habitat consisted of wetland, rocky barrens, and anthropogenic, while forest
-habitat consisted of coniferous forest, conifer scrub, broad leaf forest, and
-mixed-wood forest. Water habitat was excluded from all subsequent analyses.
-
-## Caribou multilayer social networks
-
-### Network layer construction
-<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
-individual nodes and two aspects (season and land cover). Two season
-elementary-layers (summer and winter) and three land cover elementary-layers
-(forage, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals linked by social associations, for each season and land cover combination.-->
-
-We generated proximity-based social networks using the R package `spatsoc`
-[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
-individuals were associating if simultaneous GPS fixes were within the spatial
-distance threshold of one another. Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
-data, the chain rule is applied by assigning a group identifier to the union of
-buffered GPS fixes at each time step. As such, individuals in a group are within
-the spatial distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. Group assignment based on the chain rule
-has previously been applied to caribou using a temporal threshold of 5 minutes
-and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].
-
-<!--In
-all networks, individual caribou were represented as nodes, associations between
-individuals in a given habitat type and season were represented as intralayer
-edges, and connections between the same individuals across seasons and within
-habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .-->
-<!-- eg this is connecting contexts used to calculate layer similarity -->
-
-We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index [SRI, @Cairns_1987]:
-
-$$ SRI = \frac{x}{x + y_{AB} + y_{A} + y_{B}} $$
-
-where x is the number of fixes where individuals A and B were in the same group,
-$y_{A}$ is the number of fixes from individual A when individual B did not have
-a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
-individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
-simultaneous fixes from individuals A and B that were separated by more than the
-spatial distance threshold [@Farine_2015].
-
-### Network metrics 
-<!-- TODO: expand + simplify + examples individual A, B etc -->
-
-We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals within and across layers, and the similarity of
-different layers. To measure the role of individuals within layers, we
-calculated degree centrality and graph strength. Degree centrality is the number
-of direct connections an individual has to other individuals in a network layer.
-Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. Extending degree centrality, we calculated multidegree,
-the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
-@Kivela_2014]. <!--We evaluated the relevance and redundancy of layers by
-combining the multidegree and neighbourhood to calculate layer relevance and
-connective redundancy. Layer relevance is the proportion of neighbours present
-in each layer compared to the neighbourhood for each individual and connective
-redundancy is the proportion of neighbours repeated in multiple layers, and
-[@Berlingerio_2012].--> Finally, we measured the similarity of layers by
-calculating edge overlap. Edge overlap is defined as the proportion of edges
-present in each network layer out of all observed edges  [@Battiston_2014].
-<!--between seasons, across land cover classes (e.g. summer open compared to
-winter open) using the Pearson correlation coefficient [@Brodka_2018].-->
-Network metrics were calculated using the R packages `igraph` [@Csardi_2006],
-`asnipe` [@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table`
-[@Dowle_2019].
-
-## Varying scale in multilayer networks
-<!--
-
-social scale: variable is spatial distance threshold
-spatial scale: variable is land cover resolution
-temporal scale: variable is temporal window
-temporal scale: variable is number of observations
--->
-
-### Social scale
-
-We generated multilayer networks across a series of spatial distance thresholds
-for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
-500 m) represented a range of visual (short distance) to auditory (long
-distance) sensory modalities of caribou. Multilayer networks consisted of the
-social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and forage) for the entire study period. At
-the finest scale, individuals within 5 m of one another were considered in the
-same group, whereas at the coarsest scale, individuals within 500 m of one
-another were considered in the same group. We calculated graph strength and
-multidegree for each habitat layer and spatial distance threshold, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial distance
-threshold.
-
-### Spatial scale
-<!-- TODO: Increased spatial scale of land cover corresponds to xyz -->
-To assess the influence of spatial scale, we aggregated the land cover raster using the R package `grainchanger` [@Graham_2019] across a series
-of scales (100 - 1000 m by steps of 100 m). The land cover raster was aggregated
-using a modal moving window method using a circular window corresponding to the
-above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
-decision making for caribou during foraging, while re-sampling at 500 m , 750 m
-and 1000 m represents the scale at which caribou tend to select and avoid
-habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
-forage) for the entire study period. Social associations of individuals were
-defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
-strength and multidegree for each habitat layer and spatial scale, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial scale.
-
-### Temporal scale
-#### Time windows
-
-We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
-days taken from the entire study period. Social associations were defined by
-spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
-window, we calculated individual graph strength and multidegree, and across the
-series of networks, we calculated edge overlap to determine proportion of total
-edges observed in each time window.
-
-#### Number of observations
-Studies of social network analysis vary in the number and frequency of
-observations as well as the data collection technique used to generate networks
-[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
-fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
-period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies.
-To investigate the influence of number of observations, we generated multilayer networks of social association between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and forage) using $N$ randomly selected observations.
-We first generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to ensure previously included timesteps, and resulting associations, were accumulated with subsequent observations to mimic collection of observational data.
-Within each multilayer network with $N$ observations, we calculated individual graph strength and multidegree.
-We calculated
-edge overlap across the entire series of networks to determine proportion of
-total edges as number of observations increased.
-
-# Results
-<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
-<!-- TODO: Add intro/general to results?-->
-<!-- major points then details -->
-
-Individuals in multilayer networks became more connected as the
-spatial distance threshold increased. Mean
-graph strength differed across habitat layers with similar and higher graph
-strength in open and forage layers, and lower strength in forest layers (Figure
-\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
-100 m in all three habitat classes followed by a decrease in rate after 100 m. These
-results suggest the optimal social scale at which groups should be assigned is
-likely somewhere between ~20 - 100 m based on the rate at which network metrics
-stabilized. For ungulates, groups are often assigned based on 50 m threshold
-(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
-given similar quantities of data, ~50 m is likely an appropriate social scale
-for generating social networks in caribou and similar species.
-
-Increasing land cover resolution resulted in a decreased availability of forage,
-a rare and patchy habitat, and corresponding low connectivity of individuals in
-these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
-and edge overlap was relatively consistent across land cover resolutions for
-forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
-sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
-1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
-forage layers across land cover resolutions than open and forest (Figure
-\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
-increased with increasing spatial resolution, while decreasing in forage habitat
-(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
-matching land cover resolution to scale of selection as well as ensuring the
-land cover product used has a resolution fine enough to detect landscape
-features and habitats relevant to study species, such as important patchy and
-rare habitats.
-
-<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
-
-The ordinal multilayer network generated from discrete time windows indicate
-within-year periods of increased caribou sociality.
-Edge overlap was higher in time windows 1, 6-11 and 15-20 than time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A).
-These periods between approximately October and May
-
-increasing graph strength with overall peak in 2018 but still increases in 2019
-note graph connectedness is evident panel B
-
-<!-- Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
-B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
-Graph strength peaked in time window 9, with noticeable higher strength than the following year.
--->
-These
-results suggest that an increasing window length, especially for the summer
-season, may be resulting in less precisely defined seasons that are not clearly
-capturing periods of aggregation and dissaggregation related to resource
-availability.
-
-changing the position of the
-time window in this case results in a mismatch between expected periods of
-resource seasonality and corresponding sociality, particularly for the summer,
-highlighting the importance of carefully selecting temporal scale of analysis.
-
-<!-- TODO: reduce to this version -->
-As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics appeared to stabilize. Mean graph
-strength was consistently weak in summer layers but varied in winter layers at
-low number of observations, becoming stable at ~75 observations (Figure
-\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
-winter layers increased between approximately 10  and 100  observations,
-remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
-coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
-observations were not sufficient for capturing individuals in all contexts and
-therefore layer similarity could not be calculated below ~30 observations for
-forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
-similarity was not possible to calculate for forage layers because there were no
-connected individuals in summer forage. Once sufficient observations were
-obtained, layer similarity showed some variability with increasing numbers of
-observations for forest and was relatively stable in open layers. Connective
-redundancy increased dramatically between ~10 and ~50 observations before
-stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
-Given the observed trend of these multilayer metrics stabilizing after a certain
-number of observations are included, the results suggest this sensitivity method
-could be useful for determining the number of observations necessary for
-sufficiently describing social dynamics across contexts.
-
-<!-- TODO: I'm not sure this is relevant since this is the main way it
-is already done, can we make this thought more relevant to picking scales or
-multilayer networks in general? I think it's important for building robust
-networks -->
-
-<!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in spatial distance threshold.
-For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
-After 100 m, graph strength continued to increase at a slower rate.
-Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
-
-<!-- Figure: metrics by land cover resolution -->
-(ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
-D) Edge overlap of habitat layers across spatial resolutions.
-Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m.
-Above 600 m, the forage layers are stable.
-E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
-Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
-Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
-
-<!-- Figure: metrics by number of observations -->
-<!-- TODO: update to temp -->
-(ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
-B) Edge overlap increased for all habitat layers with increasing number of observations.
-Open and forage layers had higher edge overlap than forest layers.
-C) Multidegree increased for all individuals with increasing number of observations.
-Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
-
-<!-- Figure: Time window -->
-(ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
-B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
-Graph strength peaked in time window 9, with noticeable higher strength than the following year.
-
-<!-- TODO: a bit more for g strength? -->
-
-# Discussion
-
-<!-- TODO: caveat social scale could also be diff types of relationships but GPS but point to hmm -->
-
-The integration of behavioural and ecological theory has shown the value of
-considering the importance of various ecological disciplines to better
-understand and predict animal social networks, including demography
-[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
-ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
-studies integrating social network theory into a broader array of behavioural
-and ecological sub-disciplines is impressive, only recently has the role of
-animal space use been considered in describing the causes and consequences of
-the social environment in the context of (1) phenotypes and individual fitness
-[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
-(3) habitat selection and space use [@He_2019]. Importantly, much of the work
-linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
-@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
-networks in the emerging integration of social and spatial ecology within the
-behavioural ecology literature.
-
-## Phenotypes and Individual fitness
-
-Social network positions are frequently used to represent the social environment
-that an individual experiences or their social phenotype. Multilayer networks
-provide a way to bridge these different scales so that we can examine social
-phenotypes in more holistic ways rather than looking at each scale separately as
-has traditionally been done. From a monolayer network perspective, social
-phenotypes are increasingly linked to important fitness for individuals of
-various species, including primates [@Brent_2017; @Thompson_2019], dolphins
-[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
-social scales, types of interactions, and temporal, seasons and stages of life,
-have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011].
-
-For instance, social scale is major consideration for social network analysis,
-especially in the context of different types of relationships, such as grooming
-and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
-study results indicate that there are different social patterns in different
-habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure 
-\@ref(fig:socres)) in different habitat types, having higher graph strength in
-forage and open habitats where they can likely see each other and still interact
-with visual cues unlike in forest habitats. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
-
-Temporal scale is also important for understanding the repercussions of social
-phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics (Figure
-\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
-depending on how the time window is defined highlight how critical it is to
-properly define the time window appropriately to address the questions and
-hypotheses of interest. For instance, social phenotypes can change over ontogeny
-in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses. Further complicating the issue of selecting suitable time
-scales across ontogeny, individuals progress through development at different
-rates [@Tarka_2018]. This variation can make defining appropriate temporal
-scales for testing the fitness implications of an individual’s social phenotype
-over different stages of ontogeny even more difficult when they vary by
-individual. However, considering fine temporal scales provide insight across
-developmental stages that may otherwise be missed [@Turner_2017]. Defining
-temporal scales is a challenge in multilayer networks just as in monolayer
-networks; however, multilayer networks provide metrics that enable researchers
-to look at similarities and differences in separate layers representing
-different stages of ontogeny, or seasons as in our case study, which can be
-difficult to detect.
-
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes. The multilayer network framework enables
-researchers to examine these different social scales simultaneously rather than
-individually, which is what has been done under most circumstances, but is not
-very realistic. Metrics from multilayer networks provide an opportunity to
-simplify statistical models. Interactions that happen side-by-side, proximity
-associations, and long-distance interactions can be encapsulated in a single
-multilayer network, and a single metric can be used to describe the various
-social scales of an individual’s network position. This multilevel network
-metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
-to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations,
-especially over time, it is hard to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-Conversely, picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks [@Farine_2017]. These considerations may be limiting factors
-when answering questions that require time frames that are relevant to different
-individuals, for instance. In both mono- and multilayer networks, the effect of
-scale on the relationship between an individual’s social network position and
-fitness need to be considered based on the hypotheses being tested and
-logistical constraints.
-
-## Movement ecology and collective movement
-
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Movement as a collective group can reduce per capita
-predation risk via detection-dilution trade-offs and improve information
-transfer about the quality or location of resources to other group members
-[@Jolles_2019]. In our case study, we integrate proximity based social networks
-that inherently rely on animal collective movement, and, in general, we found
-that movement is likely an important mechanism driving social network
-connectivity within and between habitat types.
-
-Although multilayer animal social networks are relatively novel [@Silk_2018],
-movement behaviour within multilayer networks has been considered. Spatial
-networks are physical locations (nodes) which are connected in a network when
-individuals move between said locations (edges). For example, spatial networks
-were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
-*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
-example, nodes represent locations within the array, *intralayer edges*
-represent individual movement frequency, and *interlayer edges* represent
-contact probability among individuals at a given node [@Mourier_2019]. Although
-movement between fixed arrays is inherent, networks are not constructed based on
-continuous measures of dyadic or collective movement [@Long_2014]. Our case
-study builds on the work of Mourier et al. (2019) and explicitly integrates
-continuous and simultaneous measures of animal movement through space and time
-as layers of a multilayer social network.
-
-In contrast to spatial networks, where nodes represent spatial locations that
-are fixed in space, movement networks can represent continuous and simultaneous
-movement trajectories of multiple animals. In a recent study of vulturine
-gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
-monolayer association networks within a multilayer network [@Papageorgiou_2019].
-However, despite potential to generate networks in different spatial or social
-contexts, layers in the multilayer network represented social associations
-within and between groups. Continuous collection of animal relocation data using
-GPS technology can be used to measure how groups of animals make collective
-movement decisions in the context of their local environment
-[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
-collective movement layer could constitute similarity in movement for dyads
-[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
-fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
-@Flack_2018]. Our case study integrates variation in temporal and spatial scale
-to assess the role of scale in predicting multilayer networks. As one might
-expect, we found increasing social threshold results in saturation of potential
-social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
-on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
-to generate social networks during times when animals are engaged in different
-behaviours, including travelling, interacting, or foraging [@Muller_2018;
-@Finn_2019] and construct a multilayer network based on behaviour-specific
-monolayer networks [e.g. @Smith_Aguilar_2019].
-
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
-
-Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-In our case study, we generated multilayer networks based on habitat-specific
-monolayers. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
-## Habitat selection and space use
-Social structure and habitat selection are intimately linked: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
-novel framework for considering the influence of habitat selection and space use
-on sociality across scales.
-
-<!-- TODO: point to figure 1 -->
-Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
-selection is measured using resource selection functions (RSFs), based on the
-proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours. Despite animals selecting for different landscape attributes
-at different scales [@Mayor_2009], the use of multiscale analyses for habitat
-selection is still critically lacking [@McGarigal_2016].
-
-The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. Cougar
-(*Puma concolor*) home ranges overlapped more in regions with high hunting
-opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
-tarandus*) sociality differed between seasons, where social associations were
-stronger in winter and contrastingly low in summer when resource availability
-are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
-habitat selection in larger groups and avoidance of predation risk was a main
-factor contributing to their habitat selection [@Fortin_2009]. These examples,
-comparing sociality and habitat selection across temporal or spatial contexts,
-are implicitly multilayer analyses.
-
-<!-- TODO: weak --> 
-Multilayer networks can be used to explicitly consider
-habitat selection and sociality across scales. Animal social systems can be
-parsed by spatial contexts, defined, for example, by habitat types as in Figure
-\@ref(fig:lcres). The effect of seasonality of resources can can be directly
-measured by differences in habitat selection and sociality across temporal
-layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
-selection can be explicitly integrated using network layers defined by selection
-coefficients for individuals. These examples of explicit integrations of habitat selection
-and sociality across social, spatial and temporal scales highlight the potential
-for novel insights from multilayer networks.
-
-# Conclusions
-
-<!-- TODO: push gps data, HMM networks, etc-->
-
-Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate the potential novel analyses that vary social, spatial,
-and temporal scale within a multilayer framework. In our caribou case study, we
-show that (1) multilayer social networks can be, but are not always,
-scale-dependent, and (2) the use of multilayer networks could be useful for
-identifying habitat or season-specific social processes. Our analyses of social,
-spatial, and temporal scales in a multilayer network framework highlight the potential
-to identify scales at which different properties of layers within a multilayer
-network show the most variability. Furthermore, we discuss the potential
-integration of individual phenotypes and fitness, collective movement, and
-habitat selection for future analyses considering spatial ecology using
-multilayer networks.
-
-Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
-to an increased attention to the scale at which ecological processes are
-observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
-advances have lead to increased data complexity and resolution. Remotely sensed
-imagery collected by modern satellites provide, for example, 10 m spatial
-resolution optical imagery at a temporal revisit period of five days at the
-equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
-allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
-at a higher temporal resolution [@B_rger_2016]. Given this increased
-availability of complex data, it is important to consider using a broad
-continuum of scales to fully capture ecological processes, carefully select and
-combine sources of data with different temporal and spatial scales, and
-establish a clear link between scales of observation and meaningful biology.
-
-Multilayer networks are complicated in that they can incorporate data as varied
-as social interactions, landscape features, and seasons, all of which exist at
-different scales and units of measurement. Our analysis of caribou multilayer
-networks which incorporated high resolution GPS telemetry data and spatial land cover
-data is grounded in the context of observed animal social networks, as the
-scales we chose to explore, e.g., number of observations, sociality across space
-and time, are ones that can be observed as has traditionally been done in
-ethology. We highlight ways in which scale ought to be considered for both
-observed and remotely-sensed data when building social networks. Furthermore,
-GPS telemetry data provides a link between large scale landscape properties and
-fine scale social interactions as animal movement occurs across the landscape,
-and when taken into account with multiple individuals can indicate association
-patterns. Thus, a layer incorporating relocation data could be a great boon
-linking spatial and social layer in multilayer networks.
-
-<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
-It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data.
--->
-
-Silk et al. (2018) summarized some key multilayer questions in animal behaviour
-research. While these questions are important for linking animal behaviour and
-multilayer networks, we summarize our perspectives on the future of multilayer
-networks with an additional set of questions posed through the lens of spatial
-ecology that are relevant to the promise and problem of scale in multilayer
-networks:
-
-1. How do social phenotypes vary across social, spatial, and temporal scales and
-at which scale might these influence fitness? Are some scales better predictors
-for different fitness metrics?
-
-2. Why do individuals associate more strongly with certain conspecifics in some
-habitats? What, if any, is the role of movement in the context of habitat
-networks?
-
-3. How, and why, does the spatial scale of perception influence, e.g. auditory,
-visual, or chemotaxis, influence the social environment? What is the role of
-memory, and by extension social and spatial cognition, as animals navigate their
-environment and make decisions about where to move next?
-
-<!-- TODO: In summary, -->
-
-# Acknowledgements
-
-We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
-Hendrix, K. Kingdon, S. Boyle, C. Prokopenko, I. Richmond, J. Hogg, and L.
-Newediuk for their comments on previous versions of this manuscript as well as
-D. C. Schneider for inspiration and helpful discussions about scale. Funding for
-this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a
-NSERC Discovery Grant to EVW.
-
-\newpage
-
-```{r spacetime, fig.cap='(ref:spacetime)'}
-knitr::include_graphics('../graphics/figure-scales.png')
+```{r}
+knitr::kable(timedefs)
 ```
 
-\newpage
+Figure S1: n individuals
 
-(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
-Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
-Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
-individual "A" in summer, forest and individual "A" in winter, forest).
-
-```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-ml.png')
+```{r}
+knitr::include_graphics(')
 ```
-
-\newpage
-
-```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lc.png')
-```
-
-\newpage
-
-```{r temp, fig.cap='(ref:temp)'}
-knitr::include_graphics('../graphics/figure-temp.png')
-```
-
-\newpage
-
-```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-soc.png')
-```
-
-\newpage
-
-```{r nobs, fig.cap='(ref:nobs)'}
-knitr::include_graphics('../graphics/figure-nobs.png')
-```
-
-\newpage
-\clearpage
-
-# References

### 2020-06-14 paper/supplement.Rmd
add two sup figs and sup tab to sup

@@
 ---
-title: Supplement\: Considering scale in multilayer animal social networks
+title: Supplement - Considering scale in multilayer animal social networks
 author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 
-Figure S1: n individuals
+Figure S1: lc count by res
 
 ```{r}
-knitr::include_graphics(')
+knitr::include_graphics('../graphics/supp-count-lc.png')
 ```
+
+Figure S2: n individuals by time
+
+```{r}
+knitr::include_graphics('../graphics/supp-temp-nid.png')
+```

### 2020-06-14 paper/manuscript.Rmd
consistent "time window"

@@
 
-Increasing land cover resolution resulted in a decreased availability of forage,
+Increasing land cover resolution resulted in decreased availability of forage,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
 these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
-and edge overlap was relatively consistent across land cover resolutions for
+and edge overlap were relatively consistent across land cover resolutions for
 forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
@@
 
-The ordinal multilayer network generated from discrete time windows indicate
-within-year periods of increased caribou sociality.
-Edge overlap was higher in time windows 1, 6-11 and 15-20 than time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A).
-These periods between approximately October and May
-
-increasing graph strength with overall peak in 2018 but still increases in 2019
-note graph connectedness is evident panel B
-
-<!-- Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
-B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
-Graph strength peaked in time window 9, with noticeable higher strength than the following year.
--->
-These
-results suggest that an increasing window length, especially for the summer
-season, may be resulting in less precisely defined seasons that are not clearly
-capturing periods of aggregation and dissaggregation related to resource
-availability.
-
-changing the position of the
-time window in this case results in a mismatch between expected periods of
-resource seasonality and corresponding sociality, particularly for the summer,
-highlighting the importance of carefully selecting temporal scale of analysis.
+The ordinal multilayer network generated indicated
+within-year time windows of increased caribou sociality.
+Edge overlap was higher in time windows 1, 6-11 and 15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A).
+Time windows of higher edge overlap, between approximately October and May, had correspondingly higher graph strength compared to time windows of lower edge overlap, between approximately May and October (Figure \@ref(fig:temp) C).
+Graph strength peaked across the time series in periods 9 and 10.
+These results suggest that ordinal multilayer networks
+can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.
 

### 2020-06-14 paper/manuscript.Rmd
nobs results

@@
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics appeared to stabilize. Mean graph
-strength was consistently weak in summer layers but varied in winter layers at
-low number of observations, becoming stable at ~75 observations (Figure
-\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
-winter layers increased between approximately 10  and 100  observations,
-remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
-coarse land cover resolution (Figure \@ref(fig:lcres)), low numbers of
-observations were not sufficient for capturing individuals in all contexts and
-therefore layer similarity could not be calculated below ~30 observations for
-forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
-similarity was not possible to calculate for forage layers because there were no
-connected individuals in summer forage. Once sufficient observations were
-obtained, layer similarity showed some variability with increasing numbers of
-observations for forest and was relatively stable in open layers. Connective
-redundancy increased dramatically between ~10 and ~50 observations before
-stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
+individuals became more connected and metrics generally appeared to stabilize. Graph
+strength across individuals in all three habitat layers was highly variable at low number of observations and stabilized after ~100 observations (Figure \@ref(fig:nobs) A).
+Edge overlap increased across all three habitat layers with increasing number of observations (Figure \@ref(fig:nobs) B).
+Similarly, multidegree for all individuals increased quickly between 10 and 100 observations, and continued to increase until 1000 observations (Figure \@ref(fig:nobs) C).
 Given the observed trend of these multilayer metrics stabilizing after a certain
@@
 
-<!-- TODO: I'm not sure this is relevant since this is the main way it
-is already done, can we make this thought more relevant to picking scales or
-multilayer networks in general? I think it's important for building robust
-networks -->
+<!-- sufficient observations is essential for capturing reliable networ -->
 

### 2020-06-14 scripts/figures/theme.R
drop strip bg fill

@@ -24,8 +24,8 @@ base <-
       colour = 'black',
       fill = NA,
       size = 1
-    )
-  
+    ),
+    strip.background = element_rect(fill = NA, color = 'black')
 )
 
 

### 2020-06-14 paper/manuscript.Rmd
tidy

@@
 networks based on predicted social (visual and auditory perception), spatial
-(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious ungulates
-with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
-spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
-holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
-is presumed to be a costly behaviour and as a result, caribou tend to occupy and
-re-use craters once they are established. <!-- and there is considerably less access
-to forage than when the landscape is snow-free.--> Importantly, craters exist on
-the landscape at multiple scales: the crater scale (a single crater), the
-feeding area scale (multiple craters in close proximity), and the winter range
-scale (all craters within an individual’s range) [@Mayor_2009]. Access to forage is 
-seasonally heterogeneous depending on snow cover and, in winter, variable distribution of craters on the 
-landscape. <!--We partitioned data into two
-discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
-February 2018) based on caribou socioecology [@Peignier_2019].-->
+(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious
+ungulates with fission-fusion dynamics [@Lesmerises_2018] that display temporal
+and spatial variation in social networks [@Peignier_2019]. In winter, caribou
+dig holes in the snow, termed craters, to access forage [@Bergerud_1974].
+Cratering is presumed to be a costly behaviour and as a result, caribou tend to
+occupy and re-use craters once they are established. <!-- and there is
+considerably less access to forage than when the landscape is snow-free.-->
+Importantly, craters exist on the landscape at multiple scales: the crater scale
+(a single crater), the feeding area scale (multiple craters in close proximity),
+and the winter range scale (all craters within an individual’s range)
+[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
+cover and, in winter, variable distribution of craters on the landscape.
 
@@
 has previously been applied to caribou using a temporal threshold of 5 minutes
-and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].
-
-<!--In
-all networks, individual caribou were represented as nodes, associations between
-individuals in a given habitat type and season were represented as intralayer
-edges, and connections between the same individuals across seasons and within
-habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .-->
-<!-- eg this is connecting contexts used to calculate layer similarity -->
+and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
+all networks, individual caribou were represented as nodes and associations between
+individuals in a given network layer were represented as intralayer
+edges. <!-- (Figure \@ref(fig:ml)) .-->
 
@@
 ### Network metrics 
-<!-- TODO: expand + simplify + examples individual A, B etc -->
-
 We used a series of metrics to characterize the multilayer networks, focusing on
@@
 the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
-@Kivela_2014]. <!--We evaluated the relevance and redundancy of layers by
-combining the multidegree and neighbourhood to calculate layer relevance and
-connective redundancy. Layer relevance is the proportion of neighbours present
-in each layer compared to the neighbourhood for each individual and connective
-redundancy is the proportion of neighbours repeated in multiple layers, and
-[@Berlingerio_2012].--> Finally, we measured the similarity of layers by
-calculating edge overlap. Edge overlap is defined as the proportion of edges
-present in each network layer out of all observed edges  [@Battiston_2014].
-<!--between seasons, across land cover classes (e.g. summer open compared to
-winter open) using the Pearson correlation coefficient [@Brodka_2018].-->
-Network metrics were calculated using the R packages `igraph` [@Csardi_2006],
-`asnipe` [@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table`
-[@Dowle_2019].
+@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
+overlap. Edge overlap is defined as the proportion of edges present in each
+network layer out of all observed edges  [@Battiston_2014]. Network metrics were
+calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
+[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].
 
 ## Varying scale in multilayer networks
-<!--
-
-social scale: variable is spatial distance threshold
-spatial scale: variable is land cover resolution
-temporal scale: variable is temporal window
-temporal scale: variable is number of observations
--->
 
@@
 #### Time windows 
-
 We used a temporal multilayer network to assess the seasonality of caribou
@@
 # Results
-<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
 <!-- TODO: Add intro/general to results?-->
-<!-- major points then details -->
 
@@
 increased with increasing spatial resolution, while decreasing in forage habitat
-(Supp. 1 <!-- todo-->).  Overall, these results indicate the importance of
+(Supp. 1 <!-- TODO-->).  Overall, these results indicate the importance of
 matching land cover resolution to scale of selection as well as ensuring the
@@
 
-<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
+The ordinal multilayer network generated indicated within-year time windows of
+increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
+15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
+windows of higher edge overlap, between approximately October and May, had
+correspondingly higher graph strength compared to time windows of lower edge
+overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
+strength peaked across the time series in periods 9 and 10. These results
+suggest that ordinal multilayer networks can effectively capture discrete time
+windows of aggregation and dissaggregation related to resource availability, and
+highlight the importance of carefully selecting the temporal scale of analysis.
 
-The ordinal multilayer network generated indicated
-within-year time windows of increased caribou sociality.
-Edge overlap was higher in time windows 1, 6-11 and 15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A).
-Time windows of higher edge overlap, between approximately October and May, had correspondingly higher graph strength compared to time windows of lower edge overlap, between approximately May and October (Figure \@ref(fig:temp) C).
-Graph strength peaked across the time series in periods 9 and 10.
-These results suggest that ordinal multilayer networks
-can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.
-
-<!-- TODO: reduce to this version -->
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics generally appeared to stabilize. Graph
-strength across individuals in all three habitat layers was highly variable at low number of observations and stabilized after ~100 observations (Figure \@ref(fig:nobs) A).
-Edge overlap increased across all three habitat layers with increasing number of observations (Figure \@ref(fig:nobs) B).
-Similarly, multidegree for all individuals increased quickly between 10 and 100 observations, and continued to increase until 1000 observations (Figure \@ref(fig:nobs) C).
-Given the observed trend of these multilayer metrics stabilizing after a certain
-number of observations are included, the results suggest this sensitivity method
-could be useful for determining the number of observations necessary for
-sufficiently describing social dynamics across contexts.
-
-<!-- sufficient observations is essential for capturing reliable networ -->
+individuals became more connected and metrics generally appeared to stabilize.
+Graph strength across individuals in all three habitat layers was highly
+variable at low number of observations and stabilized after ~100 observations
+(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
+layers with increasing number of observations (Figure \@ref(fig:nobs) B).
+Similarly, multidegree for all individuals increased quickly between 10 and 100
+observations, and continued to increase until 1000 observations (Figure
+\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
+stabilizing after a certain number of observations are included, the results
+suggest this sensitivity method could be useful for determining the number of
+observations necessary for sufficiently describing social dynamics across
+contexts.
 
@@
 <!-- Figure: metrics by number of observations -->
-<!-- TODO: update to temp -->
 (ref:nobs) Varying scale in number of observations.
@@
 
-<!-- TODO: a bit more for g strength? -->
-
 # Discussion
+<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
+<!-- sufficient observations is essential for capturing reliable networ -->
 
 <!-- TODO: caveat social scale could also be diff types of relationships but GPS but point to hmm -->
+
+<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
 

### 2020-06-15 paper/manuscript.Rmd
tidy

@@
 <!-- TODO: we answer the first question in the discussion, but not the second-->
-<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
 
@@
 
-Individuals in multilayer networks became more connected as the
-spatial distance threshold increased. Mean
-graph strength differed across habitat layers with similar and higher graph
-strength in open and forage layers, and lower strength in forest layers (Figure
-\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
-100 m in all three habitat classes followed by a decrease in rate after 100 m. These
-results suggest the optimal social scale at which groups should be assigned is
-likely somewhere between ~20 - 100 m based on the rate at which network metrics
-stabilized. For ungulates, groups are often assigned based on 50 m threshold
-(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
-given similar quantities of data, ~50 m is likely an appropriate social scale
-for generating social networks in caribou and similar species.
+Individuals in multilayer networks became more connected as the spatial distance
+threshold increased. Mean graph strength differed across habitat layers with
+similar and higher graph strength in open and forage layers, and lower strength
+in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
+sharply between 5 m and 100 m in all three habitat classes followed by a
+decrease in rate after 100 m. These results suggest the optimal social scale at
+which groups should be assigned is likely somewhere between ~20 - 100 m based on
+the rate at which network metrics stabilized. For ungulates, groups are often
+assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
+et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
+an appropriate social scale for generating social networks in caribou and
+similar species.
 

### 2020-06-15 paper/manuscript.Rmd
big discuss

@@
 # Discussion
+
 <!-- TODO: edge overlap can indicate if some associations are dependent on context -->
@@
 <!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
+<!-- -------------------------------------------------- -->
 
-The integration of behavioural and ecological theory has shown the value of
-considering the importance of various ecological disciplines to better
-understand and predict animal social networks, including demography
-[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
-ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
-studies integrating social network theory into a broader array of behavioural
-and ecological sub-disciplines is impressive, only recently has the role of
-animal space use been considered in describing the causes and consequences of
-the social environment in the context of (1) phenotypes and individual fitness
-[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
-(3) habitat selection and space use [@He_2019]. Importantly, much of the work
-linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
-@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
-networks in the emerging integration of social and spatial ecology within the
-behavioural ecology literature.
+<!-- 1: refresh why and what  -->
+<!-- importance of scale in ml -->
+Our results highlight the influence of social, spatial and temporal scale on multilayer networks. We found increasing connectedness between individuals with increasing
 
-## Phenotypes and Individual fitness
+Our examinations is motivated by behavioural, landscape, and spatial ecology to
+build a conceptual and analytical framework for scale-dependent multilayer
+networks, and we apply this framework to a case study of caribou (*Rangifer
+tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
+address two principal questions associated with scale-dependent multilayer
+networks. First, to what degree does the social scale of relationships, spatial
+scale of landscapes, and temporal scale of analysis influence our ability to
+interpret complex social systems? Second, can variation in the social, spatial,
+and temporal scale improve predictions associated with biological differences in
+seasonal resource availability and social association? We conclude with
+perspectives for further development and application of scale in multilayer
+networks with respect to phenotypes and individual fitness,
+movement ecology and collective movement, and habitat selection
+and space use.
 
-Social network positions are frequently used to represent the social environment
-that an individual experiences or their social phenotype. Multilayer networks
-provide a way to bridge these different scales so that we can examine social
-phenotypes in more holistic ways rather than looking at each scale separately as
-has traditionally been done. From a monolayer network perspective, social
-phenotypes are increasingly linked to important fitness for individuals of
-various species, including primates [@Brent_2017; @Thompson_2019], dolphins
-[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
-social scales, types of interactions, and temporal, seasons and stages of life,
-have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011].
+<!-- 2: measuring sociality is powerful, fitness -->
 
-For instance, social scale is major consideration for social network analysis,
+Monolayer network approaches have been increasingly used to link social network
+position with individual fitness, including in primates [@Brent_2017;
+@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
+[@McDonald_2007; @Royle_2012]. Social scale have emerged as important for
+understanding fitness consequences in the context of social network positions
+<!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011]. Defining the social scale at which to generate networks is an
+essential consideration for social network analysis with direct impacts on
+outcomes <!--blah-->[@Castles_2014; @Carter_2015; @Farine_2015a].
+Proximity-based social networks generated using GPS location data require using a social scale, specifically a spatial distance threshold, that defines social associations.
+In 
+threshold to
+
+Multilayer networks
+
+In contrast to multilayer networks formed by combining layers defined
+by different types of interactions, multilayer networks with GPS data are limited to 
+proximity based measures. An alternative which has been explored is using 
+hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
+
+<!-- types of relationships, ML nets -->
+<!-- GPS caveat HMM -->
+
+Furthermore, it is a
+common trope that individuals must be associating to interact, and many studies
+therefore assume that proximity is proxy for interacting [@Farine_2015a].
+
+For
+instance, baboons need to be in proximity to groom each other. However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015]. With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017].
+
+Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca
+mulatta*) had higher survivorship when they had fewer but stronger, more stable
+social associates and grooming partners rather than simply more associates
+[@Ellis_2019]. This finding highlights that different qualities of social scales
+have lasting consequences. Multilayer networks provide the opportunity to
+address these types of questions involving social scale with all the individual
+layers of interaction integrated in a holistic way.
+
+social scale results
+
+## Social scale
+
+Social scale is a major consideration for social network analysis,
 especially in the context of different types of relationships, such as grooming
@@
 
+Given the existing framework for constructing multilayer networks from
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
+quantify movement parameters could be integrated. For example, edges could
+represent measures of dyadic or collective movement based on dynamic interaction
+metrics [@Long_2014]. Integrating movement layers with habitat-specific social
+association layers could further illuminate the role of movement as a driver
+of the social and spatial environments an individual experiences [@Webber_2018].
+In our case study, we generated multilayer networks based on habitat-specific
+monolayers. Coordinated movement of dyads, or groups, could vary based on
+habitat, and the approach we outline could be used to explore mechanisms linking
+the social and spatial environments. For example, social processes may be an
+emergent property of the landscape because animals aggregate at resources, such
+as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
+patches or territories can also contribute to the formation of the social
+environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
+males interacted primarily at home range edges, presumably driving territorial
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
+network framework is a logical next step for a burgeoning field. In particular,
+when association networks are habitat-specific, we suggest the integration of
+movement and space use in multilayer networks provides novel insights into the
+effects of habitat configuration on the formation of the social environment
+[@He_2019; @Webber_2018].
+
+Social structure and habitat selection are intimately linked: individuals must
+share space to interact and the distribution of resources influences group
+dynamics and home range size [@Webber_2018]. Social structure is influenced by
+resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
+and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
+novel framework for considering the influence of habitat selection and space use
+on sociality across scales.
+
+## Spatial scale
+
+Habitat selection depends on the scale at which it is measured and a singular
+scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
+selection is measured using resource selection functions (RSFs), based on the
+proportion of used and available resources for an animal [@Manly_1993;
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, the
+(3) habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Moving past this hierarchical perspective, Mayor (2007) emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviours. Despite animals selecting for different landscape attributes
+at different scales [@Mayor_2009], the use of multiscale analyses for habitat
+selection is still critically lacking [@McGarigal_2016].
+
+The emergent relationship between habitat and sociality has been explored by the
+distribution and phenology of resources and use of social information. Cougar
+(*Puma concolor*) home ranges overlapped more in regions with high hunting
+opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
+tarandus*) sociality differed between seasons, where social associations were
+stronger in winter and contrastingly low in summer when resource availability
+are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
+habitat selection in larger groups and avoidance of predation risk was a main
+factor contributing to their habitat selection [@Fortin_2009]. These examples,
+comparing sociality and habitat selection across temporal or spatial contexts,
+are implicitly multilayer analyses.
+
+Multilayer networks can be used to explicitly consider
+habitat selection and sociality across scales. Animal social systems can be
+parsed by spatial contexts, defined, for example, by habitat types as in Figure
+\@ref(fig:lcres). The effect of seasonality of resources can can be directly
+measured by differences in habitat selection and sociality across temporal
+layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
+selection can be explicitly integrated using network layers defined by selection
+coefficients for individuals. These examples of explicit integrations of habitat selection
+and sociality across social, spatial and temporal scales highlight the potential
+for novel insights from multilayer networks.
+
+## Temporal scale
 Temporal scale is also important for understanding the repercussions of social
@@
 
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes. The multilayer network framework enables
-researchers to examine these different social scales simultaneously rather than
-individually, which is what has been done under most circumstances, but is not
-very realistic. Metrics from multilayer networks provide an opportunity to
-simplify statistical models. Interactions that happen side-by-side, proximity
-associations, and long-distance interactions can be encapsulated in a single
-multilayer network, and a single metric can be used to describe the various
-social scales of an individual’s network position. This multilevel network
-metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
+Furthermore, multilayer networks provide a framework
 to test hypotheses linking social phenotypes and fitness across temporal scales.
@@
 
+## Synth
+
+Importantly, the key to incorporating movement in multilayer networks across
+scales is the technological advancements available to overcome previous
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
+advanced to the point where relocations can be programmed to occur as frequently
+as each second [@B_rger_2016], a practice which has been applied to questions of
+collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
+technology, including unmanned aerial vehicles and satellites, can be used to
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]. Using technology to infer behaviour has therefore become
+standard operating procedure for many species in many systems. Our ability to
+collect and process remotely sensed data and infer social processes based on
+animal movement provides an opportunity to use multilayer social network
+analysis to answer complex questions about animal socioecology.
+
+## Etc
+
+The integration of behavioural and ecological theory has shown the value of
+considering the importance of various ecological disciplines to better
+understand and predict animal social networks, including demography
+[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
+ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
+studies integrating social network theory into a broader array of behavioural
+and ecological sub-disciplines is impressive, only recently has the role of
+animal space use been considered in describing the causes and consequences of
+the social environment in the context of (1) phenotypes and individual fitness
+[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
+(3) habitat selection and space use [@He_2019]. Importantly, much of the work
+linking space use and the social environment has been theoretical and empirical
+studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
+@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
+networks in the emerging integration of social and spatial ecology within the
+behavioural ecology literature.
+
+Social network positions are frequently used to represent the social environment
+that an individual experiences or their social phenotype. Multilayer networks
+provide a way to bridge these different scales so that we can examine social
+phenotypes in more holistic ways rather than looking at each scale separately as
+has traditionally been done. From a monolayer network perspective, social
+phenotypes are increasingly linked to important fitness for individuals of
+various species, including primates [@Brent_2017; @Thompson_2019], dolphins
+[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
+social scales, types of interactions, and temporal, seasons and stages of life,
+have emerged as important for understanding fitness consequences in the context
+of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011].
+
+Multilayer networks provide unique opportunities and challenges, linking these
+various scales, for understanding the social phenotypes and environments of
+individuals and their fitness outcomes.
+
+This multilevel network
+metric could be used to assess the relationship between an individual’s social
+phenotype and fitness. It would also be a meaningful reduction of many
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks [@Castles_2014].
+
 ## Movement ecology and collective movement
@@
 
+<!-- fixed array -->
 Although multilayer animal social networks are relatively novel [@Silk_2018],
@@
 fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
-@Flack_2018]. Our case study integrates variation in temporal and spatial scale
+@Flack_2018].
+
+Our case study integrates variation in temporal and spatial scale
 to assess the role of scale in predicting multilayer networks. As one might
@@
 
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
-
-Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-In our case study, we generated multilayer networks based on habitat-specific
-monolayers. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
 ## Habitat selection and space use
-Social structure and habitat selection are intimately linked: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
-novel framework for considering the influence of habitat selection and space use
-on sociality across scales.
-
-<!-- TODO: point to figure 1 -->
-Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
-selection is measured using resource selection functions (RSFs), based on the
-proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours. Despite animals selecting for different landscape attributes
-at different scales [@Mayor_2009], the use of multiscale analyses for habitat
-selection is still critically lacking [@McGarigal_2016].
-
-The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. Cougar
-(*Puma concolor*) home ranges overlapped more in regions with high hunting
-opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
-tarandus*) sociality differed between seasons, where social associations were
-stronger in winter and contrastingly low in summer when resource availability
-are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
-habitat selection in larger groups and avoidance of predation risk was a main
-factor contributing to their habitat selection [@Fortin_2009]. These examples,
-comparing sociality and habitat selection across temporal or spatial contexts,
-are implicitly multilayer analyses.
-
-<!-- TODO: weak --> 
-Multilayer networks can be used to explicitly consider
-habitat selection and sociality across scales. Animal social systems can be
-parsed by spatial contexts, defined, for example, by habitat types as in Figure
-\@ref(fig:lcres). The effect of seasonality of resources can can be directly
-measured by differences in habitat selection and sociality across temporal
-layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
-selection can be explicitly integrated using network layers defined by selection
-coefficients for individuals. These examples of explicit integrations of habitat selection
-and sociality across social, spatial and temporal scales highlight the potential
-for novel insights from multilayer networks.
 
@@
 and temporal scale within a multilayer framework. In our caribou case study, we
-show that (1) multilayer social networks can be, but are not always,
-scale-dependent, and (2) the use of multilayer networks could be useful for
+show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
 identifying habitat or season-specific social processes. Our analyses of social,
@@
 to identify scales at which different properties of layers within a multilayer
-network show the most variability. Furthermore, we discuss the potential
+network show the most variability.
+
+Furthermore, we discuss the potential
 integration of individual phenotypes and fitness, collective movement, and
@@
 
+<!-- y -->
 Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
@@
 establish a clear link between scales of observation and meaningful biology.
+<!-- y -->
 
@@
 linking spatial and social layer in multilayer networks.
-
-<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
-It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data.
--->
 
@@
 # Acknowledgements
-
+<!-- jbf -->
 We thank all members of the Wildlife Evolutionary Ecology Lab, including J.

### 2020-06-15 paper/manuscript.Rmd
remind qs

@@
 # Discussion
+<!-- 1)
+First, to what degree does the social scale of relationships, spatial
+scale of landscapes, and temporal scale of analysis influence our ability to
+interpret complex social systems? 
+-->
+
+<!-- 2)
+Second, can variation in the social, spatial,
+and temporal scale improve predictions associated with biological differences in
+seasonal resource availability and social association?
+
++
+We conclude with
+perspectives for further development and application of scale in multilayer
+networks with respect to phenotypes and individual fitness,
+movement ecology and collective movement, and habitat selection
+and space use.
+-->
 

### 2020-06-15 paper/manuscript.Rmd
fst and soc

@@
 <!-- importance of scale in ml -->
-Our results highlight the influence of social, spatial and temporal scale on multilayer networks. We found increasing connectedness between individuals with increasing
-
-Our examinations is motivated by behavioural, landscape, and spatial ecology to
-build a conceptual and analytical framework for scale-dependent multilayer
-networks, and we apply this framework to a case study of caribou (*Rangifer
-tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
-address two principal questions associated with scale-dependent multilayer
-networks. First, to what degree does the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influence our ability to
-interpret complex social systems? Second, can variation in the social, spatial,
-and temporal scale improve predictions associated with biological differences in
-seasonal resource availability and social association? We conclude with
-perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness,
-movement ecology and collective movement, and habitat selection
-and space use.
+Our results highlight the influence of social, spatial and temporal scale on
+multilayer networks. For social scale, we found individuals became more
+connected with increasing spatial distance threshold. Increasing land cover
+resolution lead to a decrease in availability of patchy and rare habitats and,
+correspondingly, lower connectivity of individuals in these habitats. Temporal
+windows highlighted clear periods of increased sociality across individuals.
+Finally, increasing number of observations lead to a stabilizing in network
+measures. As such, scale is inherently tied to the generation  of multilayer
+networks and metrics evaluating them, as well as the individual layers that make
+them up.
 
@@
 @Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Social scale have emerged as important for
-understanding fitness consequences in the context of social network positions
-<!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
+for understanding fitness consequences in the context of social network
+positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
 @Holekamp_2011]. Defining the social scale at which to generate networks is an
-essential consideration for social network analysis with direct impacts on
-outcomes <!--blah-->[@Castles_2014; @Carter_2015; @Farine_2015a].
-Proximity-based social networks generated using GPS location data require using a social scale, specifically a spatial distance threshold, that defines social associations.
-In 
-threshold to
-
-Multilayer networks
+essential consideration for social network analysis <!-- with direct impacts on
+outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
+social networks generated using GPS location data require using a social scale,
+specifically a spatial distance threshold, to define social associations. We
+found increasing individual graph strength across three habitat layers with
+increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
+habitat layers differed in their response to spatial distance threshold, with
+open and forage have a much larger increase in graph strength and variation
+across individuals. These results emphasize that multilayer network metrics are
+directly influenced by social scale, in this case the spatial distance
+threshold.
 

### 2020-06-15 paper/manuscript.Rmd
lc

@@
 
-In contrast to multilayer networks formed by combining layers defined
-by different types of interactions, multilayer networks with GPS data are limited to 
-proximity based measures. An alternative which has been explored is using 
-hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
+Social structure and habitat selection are intimately linked: individuals must
+share space to interact and the distribution of resources influences group
+dynamics and home range size [@Webber_2018]. Social structure is influenced by
+resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
+and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
+novel framework for considering the influence of habitat selection and space use
+on sociality.
 
-<!-- types of relationships, ML nets -->
-<!-- GPS caveat HMM -->
+Given that habitat data are available across a wide range of spatial scales, we
+evaluated the influence of spatial resolution on multilayer network metrics. The
+results indicate varied influence of increasing spatial resolution depending on
+the habitat layer. As spatial resolution increased, edge overlap decreased in
+forage while remaining stable in open and forest habitats (Figure
+\@ref(fig:socres) D). Forage is a rare and patchy habitat on Fogo Island, as is
+indicated by a decrease in the proportion of relocations in this habitat type
+with increasing spatial resolution (Figure S1)<!--TODO-->. Similar to increasing
+spatial distance threshold, the influence of increasing spatial resolution on
+graph strength was notably different between habitat layers. Forest layers
+showed little change in graph strength with increasing spatial resolution and
+variation between individuals. Forage and open layers had greater individual
+variation in graph strength, while forage was the sole layer to show large
+responses in graph strength to increasing spatial resolution (Figure
+\@ref(fig:socres) E). As such, multilayer network measures related to habitat
+are explicitly dependent on spatial scale. Edge overlap can indicate if some
+associations between individuals are dependent on the habitat-context
+[@Battiston_2014]. If the spatial resolution of the habitat data are
+insufficient to capture rare habitats, context-specific relationships between
+individuals may not be captured by multilayer networks.
 
-Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a].
-
-For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017].
-
-Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
-
-social scale results
-
-## Social scale
-
-Social scale is a major consideration for social network analysis,
-especially in the context of different types of relationships, such as grooming
-and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
-study results indicate that there are different social patterns in different
-habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure 
-\@ref(fig:socres)) in different habitat types, having higher graph strength in
-forage and open habitats where they can likely see each other and still interact
-with visual cues unlike in forest habitats. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
+<!-- Multilayer network extensions:
+movement
 
@@
 
-Social structure and habitat selection are intimately linked: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
-novel framework for considering the influence of habitat selection and space use
-on sociality across scales.
+GPS caveat HMM
+
+Multilayer networks can be built with different types of interactions, a differ
+In contrast to multilayer networks formed by combining layers defined
+by different types of interactions, multilayer networks with GPS data are limited to 
+proximity based measures. An alternative which has been explored is using 
+hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
+-->
 
@@
 ## Etc
+<!-- soc -->
+Social scale is a major consideration for social network analysis,
+especially in the context of different types of relationships, such as grooming
+and association, that are typically examined separately while answering a single
+question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
+common trope that individuals must be associating to interact, and many studies
+therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
+instance, baboons need to be in proximity to groom each other. However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015]. With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
+study results indicate that there are different social patterns in different
+habitat types, likely indicating different types of interactions. When the
+social threshold is greater than approximately 50 m during the winter,
+individuals demonstrate dramatically different graph strength (Figure 
+\@ref(fig:socres)) in different habitat types, having higher graph strength in
+forage and open habitats where they can likely see each other and still interact
+with visual cues unlike in forest habitats. Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca
+mulatta*) had higher survivorship when they had fewer but stronger, more stable
+social associates and grooming partners rather than simply more associates
+[@Ellis_2019]. This finding highlights that different qualities of social scales
+have lasting consequences. Multilayer networks provide the opportunity to
+address these types of questions involving social scale with all the individual
+layers of interaction integrated in a holistic way.
 

### 2020-06-15 paper/manuscript.Rmd
integrate hab sel

@@
 
-<!-- 1: refresh why and what  -->
-<!-- importance of scale in ml -->
 Our results highlight the influence of social, spatial and temporal scale on
@@
 them up.
-
-<!-- 2: measuring sociality is powerful, fitness -->
 
@@
 
-Social structure and habitat selection are intimately linked: individuals must
+Social structure and habitat selection are intimately related: individuals must
 share space to interact and the distribution of resources influences group
@@
 available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
-novel framework for considering the influence of habitat selection and space use
-on sociality.
+is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, the
+(3) habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Moving past this hierarchical perspective, Mayor (2007) emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviours.
 
-Given that habitat data are available across a wide range of spatial scales, we
-evaluated the influence of spatial resolution on multilayer network metrics. The
-results indicate varied influence of increasing spatial resolution depending on
-the habitat layer. As spatial resolution increased, edge overlap decreased in
-forage while remaining stable in open and forest habitats (Figure
-\@ref(fig:socres) D). Forage is a rare and patchy habitat on Fogo Island, as is
-indicated by a decrease in the proportion of relocations in this habitat type
-with increasing spatial resolution (Figure S1)<!--TODO-->. Similar to increasing
-spatial distance threshold, the influence of increasing spatial resolution on
-graph strength was notably different between habitat layers. Forest layers
-showed little change in graph strength with increasing spatial resolution and
-variation between individuals. Forage and open layers had greater individual
-variation in graph strength, while forage was the sole layer to show large
-responses in graph strength to increasing spatial resolution (Figure
-\@ref(fig:socres) E). As such, multilayer network measures related to habitat
-are explicitly dependent on spatial scale. Edge overlap can indicate if some
-associations between individuals are dependent on the habitat-context
-[@Battiston_2014]. If the spatial resolution of the habitat data are
-insufficient to capture rare habitats, context-specific relationships between
-individuals may not be captured by multilayer networks.
+The emergent relationship between habitat and sociality has been explored by the
+distribution and phenology of resources and use of social information. For
+example, cougar (*Puma concolor*) home ranges overlapped more in regions with
+high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
+(*Rangifer tarandus*) sociality differed between seasons, where social
+associations were stronger in winter and contrastingly low in summer when
+resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
+bison*) showed stronger habitat selection in larger groups and avoidance of
+predation risk was a main factor contributing to their habitat selection
+[@Fortin_2009]. These examples, comparing sociality and habitat selection across
+temporal or spatial contexts, are implicitly multilayer analyses.
+
+Multilayer networks represent a novel framework for explicitly scale on the
+influence of habitat selection and space use on sociality. Animal social systems
+can be parsed by spatial contexts, defined, for example, by habitat types as in
+Figure \@ref(fig:lcres). Given that habitat data are available across a wide
+range of spatial scales, we evaluated the influence of land cover spatial
+resolution on multilayer network metrics. The results indicate varied influence
+of increasing spatial resolution depending on the habitat layer. As spatial
+resolution increased, edge overlap decreased in forage while remaining stable in
+open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
+patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
+of relocations in this habitat type with increasing spatial resolution (Figure
+S1)<!--TODO-->. Similar to increasing spatial distance threshold, the influence
+of increasing spatial resolution on graph strength was notably different between
+habitat layers. Forest layers showed little change in graph strength with
+increasing spatial resolution and variation between individuals. Forage and open
+layers had greater individual variation in graph strength, while forage was the
+sole layer to show large responses in graph strength to increasing spatial
+resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
+related to habitat are explicitly dependent on spatial scale. Edge overlap can
+indicate if some associations between individuals are dependent on the
+habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
+are insufficient to capture rare habitats, context-specific relationships
+between individuals may not be captured by multilayer networks.
+
+The effect of seasonality of resources on sociality can be directly
+measured by differences in association between individuals across time windows of resource availability.
+Using an ordinal multilayer network consisting of 20 discrete time windows throughout the study period, we observed periods of increased sociality
+in caribou on Fogo Island (Figure \@ref(fig:temp))
+
+<!-- These examples of explicit integrations of habitat -->
+<!-- selection and sociality across social, spatial and temporal scales highlight the -->
+<!-- potential for novel insights from multilayer networks. -->
 
@@
 
-## Spatial scale
-
 Habitat selection depends on the scale at which it is measured and a singular
@@
 are implicitly multilayer analyses.
-
-Multilayer networks can be used to explicitly consider
-habitat selection and sociality across scales. Animal social systems can be
-parsed by spatial contexts, defined, for example, by habitat types as in Figure
-\@ref(fig:lcres). The effect of seasonality of resources can can be directly
-measured by differences in habitat selection and sociality across temporal
-layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
-selection can be explicitly integrated using network layers defined by selection
-coefficients for individuals. These examples of explicit integrations of habitat selection
-and sociality across social, spatial and temporal scales highlight the potential
-for novel insights from multilayer networks.
 

### 2020-06-15 paper/manuscript.Rmd
tidy
silly crashing...

@@
 
-Multilayer networks represent a novel framework for explicitly scale on the
-influence of habitat selection and space use on sociality. Animal social systems
-can be parsed by spatial contexts, defined, for example, by habitat types as in
+Multilayer networks represents a novel framework for explicitly testing the
+influence of habitat selection on sociality across scales. Animal social systems
+can be parsed by spatial contexts, defined by habitat types as in
 Figure \@ref(fig:lcres). Given that habitat data are available across a wide
-range of spatial scales, we evaluated the influence of land cover spatial
+range of spatial scales, we evaluated the influence of habitat spatial
 resolution on multilayer network metrics. The results indicate varied influence
@@
 
-Habitat selection depends on the scale at which it is measured and a singular
-scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
-selection is measured using resource selection functions (RSFs), based on the
-proportion of used and available resources for an animal [@Manly_1993;
-@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours. Despite animals selecting for different landscape attributes
-at different scales [@Mayor_2009], the use of multiscale analyses for habitat
-selection is still critically lacking [@McGarigal_2016].
-
-The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. Cougar
-(*Puma concolor*) home ranges overlapped more in regions with high hunting
-opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
-tarandus*) sociality differed between seasons, where social associations were
-stronger in winter and contrastingly low in summer when resource availability
-are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
-habitat selection in larger groups and avoidance of predation risk was a main
-factor contributing to their habitat selection [@Fortin_2009]. These examples,
-comparing sociality and habitat selection across temporal or spatial contexts,
-are implicitly multilayer analyses.
-
 ## Temporal scale
@@
 ## Etc
-<!-- soc -->
-Social scale is a major consideration for social network analysis,
-especially in the context of different types of relationships, such as grooming
-and association, that are typically examined separately while answering a single
-question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
-common trope that individuals must be associating to interact, and many studies
-therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
-instance, baboons need to be in proximity to groom each other. However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015]. With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
-study results indicate that there are different social patterns in different
-habitat types, likely indicating different types of interactions. When the
-social threshold is greater than approximately 50 m during the winter,
-individuals demonstrate dramatically different graph strength (Figure 
-\@ref(fig:socres)) in different habitat types, having higher graph strength in
-forage and open habitats where they can likely see each other and still interact
-with visual cues unlike in forest habitats. Varying social scales can have
-different fitness repercussions for individuals. Rhesus macaques (*Macaca
-mulatta*) had higher survivorship when they had fewer but stronger, more stable
-social associates and grooming partners rather than simply more associates
-[@Ellis_2019]. This finding highlights that different qualities of social scales
-have lasting consequences. Multilayer networks provide the opportunity to
-address these types of questions involving social scale with all the individual
-layers of interaction integrated in a holistic way.
-
 The integration of behavioural and ecological theory has shown the value of
@@
 behavioural ecology literature.
-
-Social network positions are frequently used to represent the social environment
-that an individual experiences or their social phenotype. Multilayer networks
-provide a way to bridge these different scales so that we can examine social
-phenotypes in more holistic ways rather than looking at each scale separately as
-has traditionally been done. From a monolayer network perspective, social
-phenotypes are increasingly linked to important fitness for individuals of
-various species, including primates [@Brent_2017; @Thompson_2019], dolphins
-[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
-social scales, types of interactions, and temporal, seasons and stages of life,
-have emerged as important for understanding fitness consequences in the context
-of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011].
 

### 2020-06-15 paper/manuscript.Rmd
temp

@@
 correspondingly, lower connectivity of individuals in these habitats. Temporal
-windows highlighted clear periods of increased sociality across individuals.
-Finally, increasing number of observations lead to a stabilizing in network
-measures. As such, scale is inherently tied to the generation  of multilayer
+windows highlighted clear periods of increased sociality among individuals.
+Finally, increasing number of observations lead to a general stabilizing in network
+metrics. As such, scale is inherently tied to the generation  of multilayer
 networks and metrics evaluating them, as well as the individual layers that make
@@
 habitat layers differed in their response to spatial distance threshold, with
-open and forage have a much larger increase in graph strength and variation
+open and forage with a larger increase in graph strength and greater variation
 across individuals. These results emphasize that multilayer network metrics are
@@
 
-Multilayer networks represents a novel framework for explicitly testing the
+Multilayer networks represent a novel framework for explicitly testing the
 influence of habitat selection on sociality across scales. Animal social systems
-can be parsed by spatial contexts, defined by habitat types as in
+can be parsed by spatial contexts, for example as defined by habitat types as in
 Figure \@ref(fig:lcres). Given that habitat data are available across a wide
@@
 
-The effect of seasonality of resources on sociality can be directly
-measured by differences in association between individuals across time windows of resource availability.
-Using an ordinal multilayer network consisting of 20 discrete time windows throughout the study period, we observed periods of increased sociality
-in caribou on Fogo Island (Figure \@ref(fig:temp))
+The effect of seasonality of resources on sociality can be directly measured by
+differences in sociality in discrete time windows. Using an ordinal multilayer
+network consisting of 20 discrete time windows throughout the study period, we
+observed periods of increased sociality in caribou on Fogo Island (Figure
+\@ref(fig:temp)). Edge overlap was higher between approximately October and May
+(time windows 1, 6-11, 15-20) compared to between approximately May and October
+(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A).
+<!-- not done -->
 
-<!-- These examples of explicit integrations of habitat -->
-<!-- selection and sociality across social, spatial and temporal scales highlight the -->
-<!-- potential for novel insights from multilayer networks. -->
+Furthermore, the selection of time windows is essential for both capturing life
+stages of interest and having sufficient data to construct robust networks.
+Social phenotypes can change over ontogeny in ways that can affect fitness
+[@Berger_2015; @Brent_2017]. Further complicating the issue, individuals can
+vary in their rate of development [@Tarka_2018]. This variation can make
+defining the appropriate temporal scale for testing the fitness implications of
+an individual’s social phenotype over different stages of ontogeny difficult.
+However, considering fine temporal scales has been show to provide insight across developmental
+stages that may otherwise be missed [@Turner_2017]. Furthermore, given the non-independent nature of social interactions and associations,
+especially over time, it can be challenging to test hypotheses about social dynamics with a
+suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
+multilayer networks, ordinal layers of discrete time windows provide a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods. <!--hmm-->
+
+Conversely, picking the proper temporal scale is important but a challenge
+because all layers in the multilayer network should reflect the same time
+period, and the period should be long enough for each layer to have enough data
+for robust networks [@Farine_2017]. These considerations may be limiting factors
+when answering questions that require time frames that are relevant to different
+individuals, for instance. In both mono- and multilayer networks, the effect of
+scale on the relationship between an individual’s social network position and
+fitness need to be considered based on the hypotheses being tested and
+logistical constraints.
+
+These results
+suggest that ordinal multilayer networks can effectively capture discrete time
+windows of aggregation and dissaggregation related to resource availability, and
+highlight the importance of carefully selecting the temporal scale of analysis.
 
@@
 
-## Temporal scale
-Temporal scale is also important for understanding the repercussions of social
-phenotypes. Varying the time window length and position for caribou, we found
-there was a lot of variation in the multilayer network metrics (Figure
-\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
+<!-- temp -->
+These changes in the outcome
 depending on how the time window is defined highlight how critical it is to
 properly define the time window appropriately to address the questions and
-hypotheses of interest. For instance, social phenotypes can change over ontogeny
-in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses. Further complicating the issue of selecting suitable time
-scales across ontogeny, individuals progress through development at different
-rates [@Tarka_2018]. This variation can make defining appropriate temporal
-scales for testing the fitness implications of an individual’s social phenotype
-over different stages of ontogeny even more difficult when they vary by
-individual. However, considering fine temporal scales provide insight across
-developmental stages that may otherwise be missed [@Turner_2017]. Defining
-temporal scales is a challenge in multilayer networks just as in monolayer
-networks; however, multilayer networks provide metrics that enable researchers
-to look at similarities and differences in separate layers representing
-different stages of ontogeny, or seasons as in our case study, which can be
-difficult to detect.
-
-Furthermore, multilayer networks provide a framework
-to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations,
-especially over time, it is hard to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-Conversely, picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks [@Farine_2017]. These considerations may be limiting factors
-when answering questions that require time frames that are relevant to different
-individuals, for instance. In both mono- and multilayer networks, the effect of
-scale on the relationship between an individual’s social network position and
-fitness need to be considered based on the hypotheses being tested and
-logistical constraints.
+hypotheses of interest.
 

### 2020-06-15 paper/manuscript.Rmd
more temp

@@
 The effect of seasonality of resources on sociality can be directly measured by
-differences in sociality in discrete time windows. Using an ordinal multilayer
-network consisting of 20 discrete time windows throughout the study period, we
-observed periods of increased sociality in caribou on Fogo Island (Figure
-\@ref(fig:temp)). Edge overlap was higher between approximately October and May
+differences across discrete time windows. Using an ordinal multilayer network
+consisting of 20 discrete time windows throughout the study period, we observed
+periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
+Edge overlap was higher between approximately October and May
 (time windows 1, 6-11, 15-20) compared to between approximately May and October
-(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A).
-<!-- not done -->
+(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
+overlap correspond to seasons of low resource availability [Peigner_2019].
+Similarly, individual graph strength was also highest in these periods (Figure
+\@ref(fig:temp) B).
 
-Furthermore, the selection of time windows is essential for both capturing life
-stages of interest and having sufficient data to construct robust networks.
-Social phenotypes can change over ontogeny in ways that can affect fitness
-[@Berger_2015; @Brent_2017]. Further complicating the issue, individuals can
-vary in their rate of development [@Tarka_2018]. This variation can make
-defining the appropriate temporal scale for testing the fitness implications of
-an individual’s social phenotype over different stages of ontogeny difficult.
-However, considering fine temporal scales has been show to provide insight across developmental
-stages that may otherwise be missed [@Turner_2017]. Furthermore, given the non-independent nature of social interactions and associations,
-especially over time, it can be challenging to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, ordinal layers of discrete time windows provide a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods. <!--hmm-->
+The selection of time windows is essential for capturing sociality in specific
+life stages of interest. Social phenotypes can change over ontogeny in ways that
+can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
+individuals can vary in their rate of development [@Tarka_2018]. This variation
+can make defining the appropriate temporal scale for testing the fitness
+implications of an individual’s social phenotype over different stages of
+ontogeny difficult. However, considering fine temporal scales has been show to
+provide insight across developmental stages that may otherwise be missed
+[@Turner_2017]. Furthermore, given the non-independent nature of social
+interactions and associations, especially over time, it can be challenging to
+test hypotheses about social dynamics with a suitable null control
+[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
+ordinal layers of discrete time windows provide a way to make appropriate null
+models to test questions about the dynamics of an individual’s social network
+position over multiple aggregated time periods.
+
+Finally, it is crucial to consider sufficient data to construct robust networks
+when selecting time windows and study periods.
 

### 2020-06-15 paper/manuscript.Rmd
nobs

@@
 Similarly, individual graph strength was also highest in these periods (Figure
-\@ref(fig:temp) B).
+\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
+in separate layers, multilayer networks provide a detailed and dynamic perspective at
+animal social networks.
 
@@
 Finally, it is crucial to consider sufficient data to construct robust networks
-when selecting time windows and study periods.
+when selecting time windows and study periods. Time windows should be long
+enough for each layer to have enough data for robust networks [@Farine_2017]. To
+test the influence of data quantity on multilayer networks, we used a subset of
+observations to generate multilayer networks. All network metrics across all
+three habitat layers appeared to stabilize with increasing number of
+observations. Individual graph strength showed high variability at low number of
+observations, while edge overlap and multidegree increased sharply. After
+approximately 200 observations, the rate of change for all metrics decreased and
+and graph strength remained relatively static, while edge overlap and
+multidegree continued to increase slowly. As more observations were added, more
+and rarer relationships were recorded revealing the value of this form of
+sensitivity analysis.
 
-Conversely, picking the proper temporal scale is important but a challenge
-because all layers in the multilayer network should reflect the same time
-period, and the period should be long enough for each layer to have enough data
-for robust networks [@Farine_2017]. These considerations may be limiting factors
-when answering questions that require time frames that are relevant to different
-individuals, for instance. In both mono- and multilayer networks, the effect of
-scale on the relationship between an individual’s social network position and
-fitness need to be considered based on the hypotheses being tested and
-logistical constraints.
-
-These results
-suggest that ordinal multilayer networks can effectively capture discrete time
-windows of aggregation and dissaggregation related to resource availability, and
-highlight the importance of carefully selecting the temporal scale of analysis.
+<!-- First, to what degree does the social scale of relationships, spatial -->
+<!-- scale of landscapes, and temporal scale of analysis influence our ability to -->
+<!-- interpret complex social systems?  -->
+<!-- Second, can variation in the social, spatial, -->
+<!-- and temporal scale improve predictions associated with biological differences in -->
+<!-- seasonal resource availability and social association?  -->
 

### 2020-06-15 paper/manuscript.Rmd
little abs

@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
-temporal scale --> Multilayer networks promise the integration of monolayer
+interactions to co-occurrence to overlapping home ranges, and vary within and 
+across seasons. Multilayer networks promise the integration of monolayer
 animal social networks with the complexity and importance of animal space use
 and movement in heterogeneous landscapes. Despite the complex interplay between
-social networks and how animals use space, there remains an important biological
+social networks and animal space use, there remains an important biological
 and methodological gap in our understanding of an animal’s perception of scale.
@@
 provide a social ungulate case study to illustrate the role of social, spatial,
-and temporal scale on multilayer processes. We also present perspectives on
+and temporal scale on multilayer processes. <!--We also present perspectives on
 future development and applications of scale in multilayer networks with respect
 to: phenotypes and individual fitness, movement ecology and collective movement,
-and habitat selection and space use. Effective integration of social and spatial
+and habitat selection and space use.--> Effective integration of social and spatial
 processes, including biologically meaningful scales, within the context of

### 2020-06-15 paper/manuscript.Rmd
more tidy

@@
 and space use.
-<!-- TODO: we answer the first question in the discussion, but not the second-->
 
@@
 
-<!-- TODO: units of spatial scale? --> 
-<!-- TODO: citations? -->
-
 # Methods
@@
 ## Caribou socioecology
-<!--Here, we use caribou as a case study to develop scale-dependent multilayer
-networks based on predicted social (visual and auditory perception), spatial
-(habitat type), and temporal (seasonal) scales.--> Caribou are gregarious
+Caribou are gregarious
 ungulates with fission-fusion dynamics [@Lesmerises_2018] that display temporal
@@
 ### Spatial scale
-<!-- TODO: Increased spatial scale of land cover corresponds to xyz -->
 To assess the influence of spatial scale, we aggregated the land cover raster using the R package `grainchanger` [@Graham_2019] across a series
@@
 # Results
-<!-- TODO: Add intro/general to results?-->
-
 Individuals in multilayer networks became more connected as the spatial distance
@@
 B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time window 1, 6-11, and 15-20, compared to 2-5 and 12-15.
+Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15.
 C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
@@
 hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
+
+t bon
+
 -->
 
-<!-- temp -->
-These changes in the outcome
-depending on how the time window is defined highlight how critical it is to
-properly define the time window appropriately to address the questions and
-hypotheses of interest.
-
-## Synth
-
+<!-- put this in -->
 Importantly, the key to incorporating movement in multilayer networks across

### 2020-06-15 paper/manuscript.Rmd
reflow, tidy
include mvmt

@@
 individuals in a given network layer were represented as intralayer
-edges. <!-- (Figure \@ref(fig:ml)) .-->
+edges.
 
@@
 ### Spatial scale
-To assess the influence of spatial scale, we aggregated the land cover raster using the R package `grainchanger` [@Graham_2019] across a series
-of scales (100 - 1000 m by steps of 100 m). The land cover raster was aggregated
-using a modal moving window method using a circular window corresponding to the
-above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
-decision making for caribou during foraging, while re-sampling at 500 m , 750 m
-and 1000 m represents the scale at which caribou tend to select and avoid
-habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
+To assess the influence of spatial scale, we aggregated the land cover raster
+using the R package `grainchanger` [@Graham_2019] across a series of scales (100
+- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
+moving window method using a circular window corresponding to the above scales
+[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
+for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
+represents the scale at which caribou tend to select and avoid habitat
+(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
 multilayer network consisting of the social association between 
@@
 period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies.
-To investigate the influence of number of observations, we generated multilayer networks of social association between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and forage) using $N$ randomly selected observations.
-We first generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to ensure previously included timesteps, and resulting associations, were accumulated with subsequent observations to mimic collection of observational data.
-Within each multilayer network with $N$ observations, we calculated individual graph strength and multidegree.
-We calculated
-edge overlap across the entire series of networks to determine proportion of
-total edges as number of observations increased.
+have been observed and recorded in traditional ethological studies. To
+investigate the influence of number of observations, we generated multilayer
+networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
+across three habitat layers (open, forest and forage) using $N$ randomly
+selected observations. We first generated a maximum of 1000 timesteps and
+iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to
+ensure previously included timesteps, and resulting associations, were
+accumulated with subsequent observations to mimic collection of observational
+data. Within each multilayer network with $N$ observations, we calculated
+individual graph strength and multidegree. We calculated edge overlap across the
+entire series of networks to determine proportion of total edges as number of
+observations increased.
 
@@
 between individuals may not be captured by multilayer networks.
+<!-- --- -->
+
+Another extension of multilayer networks using GPS location data is integrating
+movement. Given the existing framework for constructing multilayer networks from
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
+quantify movement parameters could be integrated. For example, edges could
+represent measures of dyadic or collective movement based on dynamic interaction
+metrics [@Long_2014]. Integrating movement layers with habitat-specific social
+association layers could further illuminate the role of movement as a driver
+of the social and spatial environments an individual experiences [@Webber_2018].
+We generated multilayer networks based on habitat-specific layers of 
+social association. Coordinated movement of dyads, or groups, could vary based on
+habitat, and the approach we outline could be used to explore mechanisms linking
+the social and spatial environments. For example, social processes may be an
+emergent property of the landscape because animals aggregate at resources, such
+as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
+patches or territories can also contribute to the formation of the social
+environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
+males interacted primarily at home range edges, presumably driving territorial
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
+network framework is a logical next step for a burgeoning field. In particular,
+when association networks are habitat-specific, we suggest the integration of
+movement and space use in multilayer networks provides novel insights into the
+effects of habitat configuration on the formation of the social environment
+[@He_2019; @Webber_2018].
+
+Importantly, the key to incorporating movement in multilayer networks across
+scales is the technological advancements available to overcome previous
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
+advanced to the point where relocations can be programmed to occur as frequently
+as each second [@B_rger_2016], a practice which has been applied to questions of
+collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
+technology, including unmanned aerial vehicles and satellites, can be used to
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]. Using technology to infer behaviour has therefore become
+standard operating procedure for many species in many systems. Our ability to
+collect and process remotely sensed data and infer social processes based on
+animal movement provides an opportunity to use multilayer social network
+analysis to answer complex questions about animal socioecology.
 
@@
 
-<!-- Multilayer network extensions:
-movement
+<!--
+Multilayer networks can be built with different types of interactions
 
-Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-In our case study, we generated multilayer networks based on habitat-specific
-monolayers. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
-GPS caveat HMM
-
-Multilayer networks can be built with different types of interactions, a differ
 In contrast to multilayer networks formed by combining layers defined
@@
 
-t bon
-
+netTS
 -->
-
-<!-- put this in -->
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
 

### 2020-06-15 paper/manuscript.Rmd
tidy

@@
 
-<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
-<!-- sufficient observations is essential for capturing reliable networ -->
-
-<!-- TODO: caveat social scale could also be diff types of relationships but GPS but point to hmm -->
-
-<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
-<!-- -------------------------------------------------- -->
-
 Our results highlight the influence of social, spatial and temporal scale on
@@
 transfer about the quality or location of resources to other group members
-[@Jolles_2019]. In our case study, we integrate proximity based social networks
+[@Jolles_2019]. We integrate proximity based social networks
 that inherently rely on animal collective movement, and, in general, we found
@@
 movement between fixed arrays is inherent, networks are not constructed based on
-continuous measures of dyadic or collective movement [@Long_2014]. Our case
+continuous measures of dyadic or collective movement [@Long_2014]. Our
 study builds on the work of Mourier et al. (2019) and explicitly integrates
@@
 ecology. We demonstrate the potential novel analyses that vary social, spatial,
-and temporal scale within a multilayer framework. In our caribou case study, we
+and temporal scale within a multilayer framework. We
 show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
@@
 to identify scales at which different properties of layers within a multilayer
-network show the most variability.
-
-Furthermore, we discuss the potential
+network show the most variability. Furthermore, we discuss the potential
 integration of individual phenotypes and fitness, collective movement, and
@@
 
-<!-- y -->
 Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
@@
 establish a clear link between scales of observation and meaningful biology.
-<!-- y -->
 
@@
 scales we chose to explore, e.g., number of observations, sociality across space
-and time, are ones that can be observed as has traditionally been done in
+and time, are ones that can be observed as has <!-- edit-->traditionally been done in
 ethology. We highlight ways in which scale ought to be considered for both
-observed and remotely-sensed data when building social networks. Furthermore,
-GPS telemetry data provides a link between large scale landscape properties and
+observed and remotely-sensed data when building social networks. GPS telemetry 
+data provides a link between large scale landscape properties and
 fine scale social interactions as animal movement occurs across the landscape,
-and when taken into account with multiple individuals can indicate association
+and when taken into account with multiple individuals<!-- edit--> can indicate association
 patterns. Thus, a layer incorporating relocation data could be a great boon

### 2020-06-15 paper/manuscript.Rmd
jbf
fix sup

@@
 increased with increasing spatial resolution, while decreasing in forage habitat
-(Supp. 1 <!-- TODO-->).  Overall, these results indicate the importance of
+(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
 matching land cover resolution to scale of selection as well as ensuring the
@@
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
-of relocations in this habitat type with increasing spatial resolution (Figure
-S1)<!--TODO-->. Similar to increasing spatial distance threshold, the influence
+of relocations in this habitat type with increasing spatial resolution (Supplementary 1
+Figure 1). Similar to increasing spatial distance threshold, the influence
 of increasing spatial resolution on graph strength was notably different between
@@
 between individuals may not be captured by multilayer networks.
-<!-- --- -->
 
@@
 # Acknowledgements
-<!-- jbf -->
+
 We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
-Hendrix, K. Kingdon, S. Boyle, C. Prokopenko, I. Richmond, J. Hogg, and L.
+Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J. Hogg, and L.
 Newediuk for their comments on previous versions of this manuscript as well as

### 2020-06-15 paper/supplement.Rmd
add text refs+caps to sup

--- 2020-06-14 paper/supplement.Rmd
@@
 ---
-title: Supplement\: Considering scale in multilayer animal social networks
+title: Supplementary 1 - Considering scale in multilayer animal social networks
 author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 
-Table S1: Time cut definitions
+(ref:cutdefs) Time cut definitions
 
-```{r}
-knitr::kable(timedefs)
+```{r cutdefs}
+knitr::kable(timedefs, caption = '(ref:cutdefs)')
 ```
 
-Figure S1: n individuals
+(ref:lccount) lc count by res
 
-```{r}
-knitr::include_graphics(')
+```{r lccount, fig.cap = '(ref:lccount)'}
+knitr::include_graphics('../graphics/supp-count-lc.png')
 ```
+
+(ref:nid) n individuals by time
+
+```{r nid, fig.cap = '(ref:nid)'}
+knitr::include_graphics('../graphics/supp-temp-nid.png')
+```

### 2020-06-15 paper/manuscript.Rmd
add new ml viz

@@
 
-(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
+(ref:ml) Visualization of multilayer network representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
+Twelve layers represent combinations of four time windows and three habitat classes (open, forest and forage).
 Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
-Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
-individual "A" in summer, forest and individual "A" in winter, forest).
 
 ```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-ml.png')
+knitr::include_graphics('../graphics/figure-fogo-ml.png')
 ```

### 2020-06-15 paper/manuscript.Rmd
rm

@@
 
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes.
-
-This multilevel network
-metric could be used to assess the relationship between an individual’s social
-phenotype and fitness. It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014].
-
 ## Movement ecology and collective movement

### 2020-06-15 paper/manuscript.Rmd
tidy

@@
 
+Another potential application would be
+to generate social networks during times when animals are engaged in different
+behaviours, including travelling, interacting, or foraging [@Muller_2018;
+@Finn_2019] and construct a multilayer network based on behaviour-specific
+monolayer networks [e.g. @Smith_Aguilar_2019].
+
 netTS
+
+However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015].
+
+With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017].
+
 -->
@@
 
-Our case study integrates variation in temporal and spatial scale
-to assess the role of scale in predicting multilayer networks. As one might
-expect, we found increasing social threshold results in saturation of potential
-social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
-on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
-to generate social networks during times when animals are engaged in different
-behaviours, including travelling, interacting, or foraging [@Muller_2018;
-@Finn_2019] and construct a multilayer network based on behaviour-specific
-monolayer networks [e.g. @Smith_Aguilar_2019].
-
-## Habitat selection and space use
-
 # Conclusions
-
-<!-- TODO: push gps data, HMM networks, etc-->
-
 Multilayer networks remain a nascent but powerful tool in animal behavioural
@@
 
-<!-- TODO: In summary, -->
-
 # Acknowledgements

### 2020-06-15 paper/manuscript.Rmd
combine more mov
tidy

@@
 
-Another extension of multilayer networks using GPS location data is integrating
-movement. Given the existing framework for constructing multilayer networks from
+Social processes, movement decisions, and space use are inextricably linked and
+multilayer networks represent a potential analytical framework for linking these
+processes [@Mourier_2019]. Movement as a collective group can reduce per capita
+predation risk via detection-dilution trade-offs and improve information
+transfer about the quality or location of resources to other group members
+[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
 behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
@@
 
-<!-- First, to what degree does the social scale of relationships, spatial -->
-<!-- scale of landscapes, and temporal scale of analysis influence our ability to -->
-<!-- interpret complex social systems?  -->
-<!-- Second, can variation in the social, spatial, -->
-<!-- and temporal scale improve predictions associated with biological differences in -->
-<!-- seasonal resource availability and social association?  -->
-
 <!--
@@
 -->
-
-## Etc
-The integration of behavioural and ecological theory has shown the value of
-considering the importance of various ecological disciplines to better
-understand and predict animal social networks, including demography
-[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
-ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
-studies integrating social network theory into a broader array of behavioural
-and ecological sub-disciplines is impressive, only recently has the role of
-animal space use been considered in describing the causes and consequences of
-the social environment in the context of (1) phenotypes and individual fitness
-[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
-(3) habitat selection and space use [@He_2019]. Importantly, much of the work
-linking space use and the social environment has been theoretical and empirical
-studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
-@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
-networks in the emerging integration of social and spatial ecology within the
-behavioural ecology literature.
-
-## Movement ecology and collective movement
-
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Movement as a collective group can reduce per capita
-predation risk via detection-dilution trade-offs and improve information
-transfer about the quality or location of resources to other group members
-[@Jolles_2019]. We integrate proximity based social networks
-that inherently rely on animal collective movement, and, in general, we found
-that movement is likely an important mechanism driving social network
-connectivity within and between habitat types.
-
-<!-- fixed array -->
-Although multilayer animal social networks are relatively novel [@Silk_2018],
-movement behaviour within multilayer networks has been considered. Spatial
-networks are physical locations (nodes) which are connected in a network when
-individuals move between said locations (edges). For example, spatial networks
-were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
-*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
-example, nodes represent locations within the array, *intralayer edges*
-represent individual movement frequency, and *interlayer edges* represent
-contact probability among individuals at a given node [@Mourier_2019]. Although
-movement between fixed arrays is inherent, networks are not constructed based on
-continuous measures of dyadic or collective movement [@Long_2014]. Our
-study builds on the work of Mourier et al. (2019) and explicitly integrates
-continuous and simultaneous measures of animal movement through space and time
-as layers of a multilayer social network.
-
-In contrast to spatial networks, where nodes represent spatial locations that
-are fixed in space, movement networks can represent continuous and simultaneous
-movement trajectories of multiple animals. In a recent study of vulturine
-gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
-monolayer association networks within a multilayer network [@Papageorgiou_2019].
-However, despite potential to generate networks in different spatial or social
-contexts, layers in the multilayer network represented social associations
-within and between groups. Continuous collection of animal relocation data using
-GPS technology can be used to measure how groups of animals make collective
-movement decisions in the context of their local environment
-[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
-collective movement layer could constitute similarity in movement for dyads
-[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
-fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
-@Flack_2018].
 

### 2020-06-15 paper/manuscript.Rmd
mv ml net viz down
render both

@@
    bookdown::github_document2: default
-   # bookdown::word_document2:
-   #   reference_docx: template.docx
+   bookdown::word_document2:
+     reference_docx: template.docx
 knit: (function(inputFile, encoding) {
@@
 
-# Conclusions
+# Conclusion
 Multilayer networks remain a nascent but powerful tool in animal behavioural
@@
 
-(ref:ml) Visualization of multilayer network representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Twelve layers represent combinations of four time windows and three habitat classes (open, forest and forage).
-Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
-
-```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-fogo-ml.png')
-```
-
-\newpage
-
 ```{r lcres, fig.cap='(ref:lcres)'}
@@
 \newpage
+
+(ref:ml) Visualization of multilayer network representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
+Twelve layers represent combinations of four time windows and three habitat classes (open, forest and forage).
+Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+
+```{r ml, fig.cap='(ref:ml)'}
+knitr::include_graphics('../graphics/figure-fogo-ml.png')
+```
+
+\newpage
 \clearpage

### 2020-06-15 paper/manuscript.Rmd
minor change - practice push on q branch

--- 2020-06-15 paper/manuscript.Rmd
@@
 ---
-title: Considering scale in multilayer animal social networks
+title: The problem and promise of scale in multilayer animal social networks
 author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
@@
 output:
-   bookdown::github_document2: default
-   # bookdown::word_document2:
-   #   reference_docx: template.docx
-knit: (function(inputFile, encoding) {
-  rmarkdown::render(inputFile, encoding = encoding,
-  output_format = "all") })
+  # github_document
+  # bookdown::pdf_document2:
+  #    number_sections: true
+  #    toc: false
+  bookdown::word_document2:
+    reference_docx: template.docx
 bibliography: ../references/knitcite.bib
@@
 
-source('../scripts/00-variables.R')
+source('../scripts/0-variables.R')
 
 library(data.table)
-DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
-nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
-timedefs <- fread('../data/supp-data/timecut-defs.csv')
+DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
 ```
@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges, and vary within and 
-across seasons. Multilayer networks promise the integration of monolayer
+interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
+temporal scale --> Multilayer networks promise the integration of monolayer
 animal social networks with the complexity and importance of animal space use
 and movement in heterogeneous landscapes. Despite the complex interplay between
-social networks and animal space use, there remains an important biological
+social networks and how animals use space, there remains an important biological
 and methodological gap in our understanding of an animal’s perception of scale.
@@
 provide a social ungulate case study to illustrate the role of social, spatial,
-and temporal scale on multilayer processes. <!--We also present perspectives on
+and temporal scale on multilayer processes. We also present perspectives on
 future development and applications of scale in multilayer networks with respect
-to: phenotypes and individual fitness, movement ecology and collective movement,
-and habitat selection and space use.--> Effective integration of social and spatial
-processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research, as such our contribution
-incorporates perspectives on how the social environment and spatial processes
-are linked across scales in a multilayer context.
+to: phenotypes and individual fitness, movement ecology and collective movement, and habitat selection and space use. Effective integration of social and
+spatial processes, including biologically meaningful scales, within the context
+of animal social networks is an emerging area of research, as such our
+contribution incorporates perspectives on how the social environment and spatial
+processes are linked across scales in a multilayer context.
 
@@
 # Introduction
-Our inference regarding the processes underlying ecological patterns
+Our inference regarding the ecological processes underlying ecological patterns
 are directly linked to the scale at which they are observed [@Levin_1992;
@@
 represents shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
-associations to occur individuals must share space, and thus have overlapping
-home ranges [@Vander_Wal_2013]. In the context of the social environment, home
-range overlap is an example of how animals share space over coarser spatial and
-temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
-clearly scales spatially and temporally, it remains unclear whether coarser
-scales of sociality, including social association and home range overlap, vary
-predictably with social interaction [@Castles_2014;
+\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or associations to
+occur individuals must share space, and thus have overlapping home ranges
+[@Vander_Wal_2013]. In the context of the social environment, home range overlap
+is an example of how animals share space over coarser spatial and temporal
+scales (e.g. Piza-Roca et al. 2018). Although the social environment clearly
+scales spatially and temporally, it remains unclear whether coarser scales of
+sociality, including social association and home range overlap, vary predictably
+with social interaction [@Castles_2014;
 @Farine_2015a]. Thus, we define social scale as the type of social relationship
@@
 Unlike traditional monolayer social networks, multilayer networks explicitly
-consider social systems across scale-dependent contexts
+consider social systems across contexts, including scale-dependent contexts
 [@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
@@
 and space use.
+<!-- TODO: we answer the first question in the discussion, but not the second-->
+<!-- TODO: Webber reference should be 2018, but defaulting to 2017-->
 
@@
 
-# Methods
+<!-- TODO: units of spatial scale? --> 
+<!-- TODO: citations? -->
+
+# Scale in multilayer networks: a case study
 
 ## Caribou socioecology
-Caribou are gregarious
-ungulates with fission-fusion dynamics [@Lesmerises_2018] that display temporal
-and spatial variation in social networks [@Peignier_2019]. In winter, caribou
-dig holes in the snow, termed craters, to access forage [@Bergerud_1974].
-Cratering is presumed to be a costly behaviour and as a result, caribou tend to
-occupy and re-use craters once they are established. <!-- and there is
-considerably less access to forage than when the landscape is snow-free.-->
-Importantly, craters exist on the landscape at multiple scales: the crater scale
-(a single crater), the feeding area scale (multiple craters in close proximity),
-and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
-cover and, in winter, variable distribution of craters on the landscape.
+Here, we use caribou as a case study to develop scale-dependent multilayer
+networks based on predicted social (visual and auditory perception), spatial
+(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
+with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
+spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
+holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
+is presumed to be a costly behaviour and as a result, caribou tend to occupy and
+re-use craters once they are established and there is considerably less access
+to forage than when the landscape is snow-free. Importantly, craters exist on
+the landscape at multiple scales: the crater scale (a single crater), the
+feeding area scale (multiple craters in close proximity), and the winter range
+scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
+of forage for caribou is therefore seasonally heterogeneous because the
+distribution of craters on the landscape varies meaning that access to
+vegetation in winter is highly variable for caribou in winter compared to summer. Caribou therefore have
+greater access to forage in snow-free seasons. We partitioned data into two
+discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
+February 2018) based on caribou socioecology [@Peignier_2019].
 
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Adult female caribou were immobilized and fitted with global positioning
-system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
-collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
-collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
-to remove all erroneous and outlier GPS fixes following
-[@Bjorneraas_2010]. We did not collar all caribou in the herd; however, the
-proportion of marked adult females was ~10% of all adult females and ~5% of all
-individuals in the herd. We assumed these individuals were randomly distributed
-throughout the population.
+We used GPS location data collected from Fogo Island caribou in 2017 and 2018.
+Adult female caribou were immobilized and fitted with global positioning system
+(GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M collars,
+1,250 g) as described by [@Schaefer_2013]. Collars were programmed to collect
+location fixes every 2 hours. Prior to analyses, we subset GPS fixes into a
+discrete removed all erroneous and outlier GPS fixes following
+[@Bjorneraas_2010]. We did not collar all caribou in
+the herd; however, the proportion of marked adult females was ~10% of all adult
+females and ~5% of all individuals in the herd. We assumed these individuals
+were randomly distributed throughout the population.
 
 ## Landscape data and habitat classification
-Land cover data were provided by the Newfoundland and Labrador Wildlife Division
-[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification
-included nine habitat types at 30 m resolution. We reclassified the land cover
-types into three categories using the R package `raster` [@Hijmans_2019]:
-foraging, open, and forest habitats. Foraging habitat consisted of lichen, open
-habitat consisted of wetland, rocky barrens, and anthropogenic, while forest
-habitat consisted of coniferous forest, conifer scrub, broad leaf forest, and
-mixed-wood forest. Water habitat was excluded from all subsequent analyses.
+landcover data were provided by the Newfoundland and Labrador Wildlife Division
+[@Integrated_2013]. Available landcover classification included nine habitat
+types at 30 m resolution. We reclassified the landcover types into three
+categories: foraging habitat, open habitat, and forest habitat using the R
+package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
+open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
+types, while forest habitat consisted of coniferous forest, conifer scrub,
+broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
+subsequent analyses.
 
@@
 
-### Network layer construction
-<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
-individual nodes and two aspects (season and land cover). Two season
-elementary-layers (summer and winter) and three land cover elementary-layers
+### Network types and construction
+We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
+individual nodes and two aspects (season and landcover). Two season
+elementary-layers (summer and winter) and three landcover elementary-layers
 (forage, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals linked by social associations, for each season and land cover combination.-->
+composed of individuals linked by social associations, for each season and landcover combination. Proximity-based social
+network layers were generated using the R package `spatsoc` [@Robitaille_2019]
+in `r version$version.string` [@R_Core_Team_2019].
 
-We generated proximity-based social networks using the R package `spatsoc`
-[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
-individuals were associating if simultaneous GPS fixes were within the spatial
-distance threshold of one another. Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
-data, the chain rule is applied by assigning a group identifier to the union of
-buffered GPS fixes at each time step. As such, individuals in a group are within
-the spatial distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. Group assignment based on the chain rule
-has previously been applied to caribou using a temporal threshold of 5 minutes
-and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
-all networks, individual caribou were represented as nodes and associations between
-individuals in a given network layer were represented as intralayer
-edges.
+Within each layer, we assumed individuals were associating if simultaneous GPS
+fixes, i.e., recorded within 5 minutes of each other, were within a given
+spatial distance of one another. Typically for ungulates and other gregarious
+mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
+chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
+distance formed a contiguous buffer for two or more individuals, even if some
+individuals within the buffer were not within the given distance of one another
+[@Robitaille_2019]. Group assignment based on the chain rule has previously been
+applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
+all networks, individual caribou were represented as nodes, associations between
+individuals in a given habitat type and season were represented as intralayer
+edges, and connections between the same individuals across seasons and within
+habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
+<!-- eg this is connecting contexts used to calculate layer similarity -->
 
@@
 
-where x is the number of fixes where individuals A and B were in the same group,
-$y_{A}$ is the number of fixes from individual A when individual B did not have
-a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
-individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
-simultaneous fixes from individuals A and B that were separated by more than the
-spatial distance threshold [@Farine_2015].
+where x is the number of fixes where individuals A and B were within a given
+distance of each other, $y_{A}$ is the number of fixes from individual A when
+individual B did not have a simultaneous fix, $y_{B}$ is the number of fixes
+from individual B when individual A did not have a simultaneous fix, and
+$y_{AB}$ is the number of simultaneous fixes from individuals A and B that were
+separated by more than the given distance [@Farine_2015]. Social groups were
+designated if two or more individuals occurred within a given distance of one
+another at any given time point.
+
+(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
+Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage).
+Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g.
+individual "A" in summer, forest and individual "A" in winter, forest).
 
 ### Network metrics 
+<!-- TODO: expand + simplify + examples individual A, B etc -->
+
 We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals within and across layers, and the similarity of
-different layers. To measure the role of individuals within layers, we
-calculated degree centrality and graph strength. Degree centrality is the number
-of direct connections an individual has to other individuals in a network layer.
-Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. Extending degree centrality, we calculated multidegree,
-the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
-@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
-overlap. Edge overlap is defined as the proportion of edges present in each
-network layer out of all observed edges  [@Battiston_2014]. Network metrics were
-calculated using the R packages `igraph` [@Csardi_2006], `asnipe`
-[@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table` [@Dowle_2019].
+the role of individuals, importance of individual layers, and the similarity of
+different layers. To measure the role of individuals, we calculated degree
+centrality and graph strength. Degree centrality is the number of direct
+connections an individual has to other individuals in a network layer. Graph
+strength is the degree weighted by the strength of association, in this case
+SRI, in each layer-specific season and landcover context. Extending degree
+centrality, we calculated multidegree, the sum of degree centrality of
+individuals across layers, and neighbourhood, the sum of unique neighbours to
+each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
+the relevance and redundancy of layers by combining the multidegree and
+neighbourhood to calculate layer relevance and connective redundancy. Layer
+relevance is the proportion of neighbours present in each layer compared to the
+neighbourhood for each individual and connective redundancy is the proportion of
+neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
+calculated the similarity of layers between seasons, across landcover classes
+(e.g. summer open compared to winter open) using the Pearson correlation
+coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
+`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
 
 ## Varying scale in multilayer networks
-
 ### Social scale
 
-We generated multilayer networks across a series of spatial distance thresholds
-for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
-500 m) represented a range of visual (short distance) to auditory (long
-distance) sensory modalities of caribou. Multilayer networks consisted of the
-social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and forage) for the entire study period. At
-the finest scale, individuals within 5 m of one another were considered in the
-same group, whereas at the coarsest scale, individuals within 500 m of one
-another were considered in the same group. We calculated graph strength and
-multidegree for each habitat layer and spatial distance threshold, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial distance
-threshold.
+We modified the distance threshold, hereafter the social threshold, required for
+group assignment using `spatsoc` [@Robitaille_2019] and re-assigned groups at
+incremental distances between 5 - 500 m. For example, at the finest social
+scale, only individuals within 5 m of one another were considered in the same
+group, whereas at the coarsest social scale, individuals within 500 m of one
+another were considered in the same group. We assumed these scales represented
+visual (short distance) to auditory (long distance) sensory modalities of
+caribou.
 
 ### Spatial scale
-To assess the influence of spatial scale, we aggregated the land cover raster
-using the R package `grainchanger` [@Graham_2019] across a series of scales (100
-- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
-moving window method using a circular window corresponding to the above scales
-[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
-for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
-represents the scale at which caribou tend to select and avoid habitat
-(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
-forage) for the entire study period. Social associations of individuals were
-defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
-strength and multidegree for each habitat layer and spatial scale, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial scale.
+
+To assess the influence of spatial scale on multilayer networks, we aggregated
+our landcover raster at varying scales relevant to caribou ecology. We
+aggregated the 30 m landcover raster using the R package `grainchanger`
+[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
+occurred using a modal moving window method using a circular window
+corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
+represents fine-scale decision making for caribou during foraging, while
+re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
+select and avoid habitat (Bastille-Rousseau et al. 2017).
 
 ### Temporal scale
-#### Time windows 
-We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
-days taken from the entire study period. Social associations were defined by
-spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
-window, we calculated individual graph strength and multidegree, and across the
-series of networks, we calculated edge overlap to determine proportion of total
-edges observed in each time window.
-
 #### Number of observations
@@
 period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies. To
-investigate the influence of number of observations, we generated multilayer
-networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
-across three habitat layers (open, forest and forage) using $N$ randomly
-selected observations. We first generated a maximum of 1000 timesteps and
-iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to
-ensure previously included timesteps, and resulting associations, were
-accumulated with subsequent observations to mimic collection of observational
-data. Within each multilayer network with $N$ observations, we calculated
-individual graph strength and multidegree. We calculated edge overlap across the
-entire series of networks to determine proportion of total edges as number of
-observations increased.
+have been observed and recorded in traditional ethological studies.We
+investigated the influence of the number of observations on resulting multilayer
+networks. We randomly selected a maximum 485 timesteps for each season to
+represent all possible observations. We regenerated multilayer networks and
+calculated associations of individuals with 25 additional observations at each
+iteration (10 - 485 observations). Subsequent iterations included the previous
+set of observations to mimic collection of observational data.
 
-# Results
-Individuals in multilayer networks became more connected as the spatial distance
-threshold increased. Mean graph strength differed across habitat layers with
-similar and higher graph strength in open and forage layers, and lower strength
-in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a
-decrease in rate after 100 m. These results suggest the optimal social scale at
-which groups should be assigned is likely somewhere between ~20 - 100 m based on
-the rate at which network metrics stabilized. For ungulates, groups are often
-assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
-et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
-an appropriate social scale for generating social networks in caribou and
-similar species.
+#### Time window length and position
+We altered the temporal scale of multilayer networks by varying the length and
+position of the time window used to define seasons. The length of the time
+window varied from 40-100 days using a fixed start day for summer (starting at 3
+August 2017) and winter (starting at 1 January 2018). The position of the time
+window was shifted by 1-48 days, using a fixed time window length of 48 days.
+These new time windows were iteratively used to partition data into two discrete
+seasons (summer and winter) and generate multilayer networks.
 
-Increasing land cover resolution resulted in decreased availability of forage,
+# Scale in multilayer networks in practice: case study results and discussion
+<!-- TODO: Add intro/general to results?-->
+In general, individuals in multilayer networks became more connected as social
+scale increased; however, this relationship varied by habitat type and season.
+As social scale increased, mean graph strength for summer networks did not
+change as the social threshold increased, but graph strength in winter networks
+increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
+\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
+increased for winter networks between 5 and 50 m social thresholds, then did not
+change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
+the winter habitat layers captured most, if not all, of the potential
+connections an individual would have across these networks. Layer similarity was
+not very strong for any habitat type, indicating that summer and winter networks
+are only weakly correlated. Furthermore, layer similarity in open habitats
+showed more variation as social threshold increased compared to forage and
+forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
+relatively stable across social thresholds, especially after 50 m (Figure
+\@ref(fig:socres)d). Taken together, these results suggest the optimal social
+scale at which groups should be assigned is likely somewhere between ~20 - 100 m
+based on the rate at which network metrics stabilized. For ungulates, groups are
+often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
+Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
+is likely an appropriate social scale for generating social networks in caribou
+and similar species.
+
+Increasing landcover resolution resulted in a decreased availability of forage,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
-these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
-and edge overlap were relatively consistent across land cover resolutions for
-forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
-sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
-1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
-forage layers across land cover resolutions than open and forest (Figure
-\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
-increased with increasing spatial resolution, while decreasing in forage habitat
-(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
-matching land cover resolution to scale of selection as well as ensuring the
-land cover product used has a resolution fine enough to detect landscape
-features and habitats relevant to study species, such as important patchy and
-rare habitats.
-
-The ordinal multilayer network generated indicated within-year time windows of
-increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
-windows of higher edge overlap, between approximately October and May, had
-correspondingly higher graph strength compared to time windows of lower edge
-overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
-strength peaked across the time series in periods 9 and 10. These results
-suggest that ordinal multilayer networks can effectively capture discrete time
-windows of aggregation and dissaggregation related to resource availability, and
-highlight the importance of carefully selecting the temporal scale of analysis.
+these habitats. Individuals in summer layers had consistent weak connections
+(Figure \@ref(fig:lcres)a). Mean graph strength increased consistently in winter
+forest and open habitats but varied in winter forage varied across landcover
+resolutions with an increase at 250 m and decrease at 500 m (Figure
+\@ref(fig:lcres)a). Layer relevance was stable for all habitat classes in summer
+layers; layer relevance was significantly higher in winter and stable in open
+and forest habitats but decreased for forage habitats (Figure
+\@ref(fig:lcres)b). <!--This pattern during the winter indicates that
+individuals had fewer neighbours in forage habitat habitats compared to their
+overall neighbourhood across habitats, likely due to the patchy nature of
+forage-->Layer similarity was low but stable for forest and open, except for a
+sharp decrease in layer similarity in open at 100 m and 250 m (Figure
+\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
+summer and winter forage because, at all landcover resolutions greater than 30
+m, there were no individuals connected in the network layers. Individuals still
+used forage habitats, but given the lower availability due to increasing
+landcover resolution, at a much lower rate. Connective redundancy was moderately
+high but decreased slightly as landcover resolution increased, indicating that
+many neighbours were the same between layers, but the proportion of neighbours
+in each layer slightly decreased at increasing landcover resolutions (Figure
+\@ref(fig:lcres)d). Overall, these results indicate the importance of matching
+landcover resolution to scale of selection as well as ensuring the landcover
+product used has a resolution fine enough to detect landscape features and
+habitats relevant to study species, such as important patchy and rare habitats.
 
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics generally appeared to stabilize.
-Graph strength across individuals in all three habitat layers was highly
-variable at low number of observations and stabilized after ~100 observations
-(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
-layers with increasing number of observations (Figure \@ref(fig:nobs) B).
-Similarly, multidegree for all individuals increased quickly between 10 and 100
-observations, and continued to increase until 1000 observations (Figure
-\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
-stabilizing after a certain number of observations are included, the results
-suggest this sensitivity method could be useful for determining the number of
-observations necessary for sufficiently describing social dynamics across
-contexts.
+individuals became more connected and metrics appeared to stabilize. Mean graph
+strength was consistently weak in summer layers but varied in winter layers at
+low number of observations, becoming stable at ~75 observations (Figure
+\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
+winter layers increased between approximately 10  and 100  observations,
+remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
+coarse landcover resolution (Figure \@ref(fig:lcres)), low numbers of
+observations were not sufficient for capturing individuals in all contexts and
+therefore layer similarity could not be calculated below ~30 observations for
+forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
+similarity was not possible to calculate for forage layers because there were no
+connected individuals in summer forage. Once sufficient observations were
+obtained, layer similarity showed some variability with increasing numbers of
+observations for forest and was relatively stable in open layers. Connective
+redundancy increased dramatically between ~10 and ~50 observations before
+stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
+Given the observed trend of these multilayer metrics stabilizing after a certain
+number of observations are included, the results suggest this sensitivity method
+could be useful for determining the number of observations necessary for
+sufficiently describing social dynamics across contexts.
+
+<!-- TODO: I'm not sure this is relevant since this is the main way it
+is already done, can we make this thought more relevant to picking scales or
+multilayer networks in general? I think it's important for building robust
+networks -->
+
+Some multilayer network metrics were strongly influenced by the length of the
+time window. Mean graph strength was weak but became slightly stronger with
+increasing time window length during the summer, but the higher mean graph
+strength during the winter showed a slight increase then decrease with
+increasing winter length (Figure \@ref(fig:winlen)a). Layer relevance increased
+for all summer layers as individuals became more connected with increasing
+window lengths, but winter layers showed relatively stable but high layer
+relevance (Figure \@ref(fig:winlen)b). This pattern indicates that the
+proportion of neighbours that were the same across layers increased with a
+longer time frame during the summer, but there were a high proportion of
+neighbors that remained the same across layers during the winter, regardless of
+time length. Furthermore, though the layers were generally not very similar
+between the summer and winter, the length of the time window created slight
+variability in this metric, particularly for forage and open habitat types
+(Figure \@ref(fig:winlen)c). Connective redundancy increased marginally with
+increasing window length, indicating that the proportions of neighbours that
+were the same across layers, though relatively high in general, slightly
+increased when time length was greater (Figure \@ref(fig:winlen)d). These
+results suggest that an increasing window length, especially for the summer
+season, may be resulting in less precisely defined seasons that are not clearly
+capturing periods of aggregation and dissaggregation related to resource
+availability.
+
+Moving window positions defining seasons showed some dramatic changes in the
+multilayer network metrics as the seasons were redefined. Graph strength
+increased at time window position ~20 for summer and winter layers and, while
+summer layers continued to increase, winter layers showed a decrease in graph
+strength at time window position ~35 (Figure \@ref(fig:winpos)a). Layer
+relevance increased across moving window positions for summer layers and
+slightly decreased for winter layers (Figure \@ref(fig:winpos)b). These results
+indicate increased connectivity in summer layers and slightly decreasing
+connectivity at shifted winter time windows. Layer similarity was relatively
+stable across moving window positions except for a sharp decline at window
+position ~28 in forage and open layers (Figure \@ref(fig:winpos) c). Connective
+redundancy showed a marginal increase with increasing window position indicating
+individuals had more of the same neighbours in each habitat network (Figure
+\@ref(fig:winpos) d). Similar to window length, changing the position of the
+time window in this case results in a mismatch between expected periods of
+resource seasonality and corresponding sociality, particularly for the summer,
+highlighting the importance of carefully selecting temporal scale of analysis.
 
 <!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in spatial distance threshold.
-For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
-After 100 m, graph strength continued to increase at a slower rate.
-Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
+(ref:socres) Varying scale in social threshold.
+For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+A) Mean graph strength across individuals showed an increase for winter network layers while summer network layers had consistently weak connections.
+B) Mean layer relevance was increased for winter layers between 5 m and 50 m, otherwise stable for all social thresholds >50 m for winter and all social thresholds for summer.
+C) Similarity of network layers across seasons and within habitat classes (e.g.
+open summer compared to open winter) was relatively stable for all habitat class layers.
+D) Mean connective redundancy across individuals showed an increase between 5 m and 50 m before remaining stable through all other social thresholds.
 
-<!-- Figure: metrics by land cover resolution -->
-(ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
-D) Edge overlap of habitat layers across spatial resolutions.
-Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m.
-Above 600 m, the forage layers are stable.
-E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
-Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
-Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
+<!-- Figure: metrics by landcover resolution -->
+(ref:lcres) Varying spatial scale in landcover resolution.
+For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+A) Mean graph strength of individuals in summer layers had consistent weak connections.
+Individuals in winter forest and open habitats increased consistently while winter forage varied with a peak at 250 m and valley at 500 m.
+B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions.
+C) Similarity of landcover network layers between seasons (e.g.
+open summer compared to open winter) forage and forest habitats but showed more variation in open habitats with increasing social thresholds.
+Note that layer similarity in forage is not shown because individuals did not interact at landcover resolutions greater than 30 m during the summer in forage habitats, so layer similarity could not be calculated.
+D) Mean connective redundancy across individuals showed a slight decreasing trend with increasing landcover resolution.
 
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
-A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
-B) Edge overlap increased for all habitat layers with increasing number of observations.
-Open and forage layers had higher edge overlap than forest layers.
-C) Multidegree increased for all individuals with increasing number of observations.
-Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
+For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+A) Mean graph strength across individuals remained weak throughout for summer layers and varied for winter layers becoming relatively stable by 100 observations.
+B) Mean layer relevance across individuals in summer layers had consistent low layer relevance but increased sharply for winter layers between ~10 m and ~50 m observations before stabilizing.
+C) Similarity of network layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was relatively consistent across number of observations for forest and open habitats.
+Note, forage habitats are not shown given no individuals interacted in the summer forage layer.
+D) Mean connective redundancy across individuals increased rapidly between ~10 m and ~50 m observations and then remained constant.
 
-<!-- Figure: Time window -->
-(ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
-B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
-Graph strength peaked in time window 9, with noticeable higher strength than the following year.
+<!-- Figure: Window length -->
+(ref:winlen) Varying temporal scale in time window length.
+For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+A) Mean graph strength across individuals in summer layers was weak but stable across increasing lengths of time except for a slight increase in strength for open and forage habitats when the season lasted more than 70 days.
+Mean graph strength was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased.
+B) Mean layer relevance increased for summer layers across habitat classes and was stable for winter layers.
+C) Similarity of layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was variable with increasing window lengths, particularly for forage and open habitat types.
+D) Mean connective redundancy across individuals increased marginally with increasing window length.
 
-# Discussion
-<!-- 1)
-First, to what degree does the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influence our ability to
-interpret complex social systems? 
--->
+<!-- Figure: Window position -->
+(ref:winpos) Varying temporal scale in time window position.
+For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forage, forest, and open).
+A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
+B) Mean layer relevance increased for summer layers and slightly decreased for winter layers.
+C) Similarity of layers across habitat classes and between seasons (e.g.
+open summer compared to open winter) was relatively stable until window position ~28 where forage and open layer similarity decreased.
+D) Mean connective redundancy across individuals increased marginally with advancing time window position.
 
-<!-- 2)
-Second, can variation in the social, spatial,
-and temporal scale improve predictions associated with biological differences in
-seasonal resource availability and social association?
+# Perspectives to advance multilayer networks
 
-+
-We conclude with
-perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness,
-movement ecology and collective movement, and habitat selection
-and space use.
--->
-
-Our results highlight the influence of social, spatial and temporal scale on
-multilayer networks. For social scale, we found individuals became more
-connected with increasing spatial distance threshold. Increasing land cover
-resolution lead to a decrease in availability of patchy and rare habitats and,
-correspondingly, lower connectivity of individuals in these habitats. Temporal
-windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations lead to a general stabilizing in network
-metrics. As such, scale is inherently tied to the generation  of multilayer
-networks and metrics evaluating them, as well as the individual layers that make
-them up.
-
-Monolayer network approaches have been increasingly used to link social network
-position with individual fitness, including in primates [@Brent_2017;
-@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
-for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale at which to generate networks is an
-essential consideration for social network analysis <!-- with direct impacts on
-outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
-social networks generated using GPS location data require using a social scale,
-specifically a spatial distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
-habitat layers differed in their response to spatial distance threshold, with
-open and forage with a larger increase in graph strength and greater variation
-across individuals. These results emphasize that multilayer network metrics are
-directly influenced by social scale, in this case the spatial distance
-threshold.
-
-Social structure and habitat selection are intimately related: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours.
-
-The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. For
-example, cougar (*Puma concolor*) home ranges overlapped more in regions with
-high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*Rangifer tarandus*) sociality differed between seasons, where social
-associations were stronger in winter and contrastingly low in summer when
-resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
-bison*) showed stronger habitat selection in larger groups and avoidance of
-predation risk was a main factor contributing to their habitat selection
-[@Fortin_2009]. These examples, comparing sociality and habitat selection across
-temporal or spatial contexts, are implicitly multilayer analyses.
-
-Multilayer networks represent a novel framework for explicitly testing the
-influence of habitat selection on sociality across scales. Animal social systems
-can be parsed by spatial contexts, for example as defined by habitat types as in
-Figure \@ref(fig:lcres). Given that habitat data are available across a wide
-range of spatial scales, we evaluated the influence of habitat spatial
-resolution on multilayer network metrics. The results indicate varied influence
-of increasing spatial resolution depending on the habitat layer. As spatial
-resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
-patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
-of relocations in this habitat type with increasing spatial resolution (Supplementary 1
-Figure 1). Similar to increasing spatial distance threshold, the influence
-of increasing spatial resolution on graph strength was notably different between
-habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Forage and open
-layers had greater individual variation in graph strength, while forage was the
-sole layer to show large responses in graph strength to increasing spatial
-resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
-related to habitat are explicitly dependent on spatial scale. Edge overlap can
-indicate if some associations between individuals are dependent on the
-habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
-are insufficient to capture rare habitats, context-specific relationships
-between individuals may not be captured by multilayer networks.
-
-Another extension of multilayer networks using GPS location data is integrating
-movement. Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-We generated multilayer networks based on habitat-specific layers of 
-social association. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
-
-The effect of seasonality of resources on sociality can be directly measured by
-differences across discrete time windows. Using an ordinal multilayer network
-consisting of 20 discrete time windows throughout the study period, we observed
-periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
-Edge overlap was higher between approximately October and May
-(time windows 1, 6-11, 15-20) compared to between approximately May and October
-(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
-overlap correspond to seasons of low resource availability [Peigner_2019].
-Similarly, individual graph strength was also highest in these periods (Figure
-\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
-in separate layers, multilayer networks provide a detailed and dynamic perspective at
-animal social networks.
-
-The selection of time windows is essential for capturing sociality in specific
-life stages of interest. Social phenotypes can change over ontogeny in ways that
-can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
-individuals can vary in their rate of development [@Tarka_2018]. This variation
-can make defining the appropriate temporal scale for testing the fitness
-implications of an individual’s social phenotype over different stages of
-ontogeny difficult. However, considering fine temporal scales has been show to
-provide insight across developmental stages that may otherwise be missed
-[@Turner_2017]. Furthermore, given the non-independent nature of social
-interactions and associations, especially over time, it can be challenging to
-test hypotheses about social dynamics with a suitable null control
-[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
-ordinal layers of discrete time windows provide a way to make appropriate null
-models to test questions about the dynamics of an individual’s social network
-position over multiple aggregated time periods.
-
-Finally, it is crucial to consider sufficient data to construct robust networks
-when selecting time windows and study periods. Time windows should be long
-enough for each layer to have enough data for robust networks [@Farine_2017]. To
-test the influence of data quantity on multilayer networks, we used a subset of
-observations to generate multilayer networks. All network metrics across all
-three habitat layers appeared to stabilize with increasing number of
-observations. Individual graph strength showed high variability at low number of
-observations, while edge overlap and multidegree increased sharply. After
-approximately 200 observations, the rate of change for all metrics decreased and
-and graph strength remained relatively static, while edge overlap and
-multidegree continued to increase slowly. As more observations were added, more
-and rarer relationships were recorded revealing the value of this form of
-sensitivity analysis.
-
-<!-- First, to what degree does the social scale of relationships, spatial -->
-<!-- scale of landscapes, and temporal scale of analysis influence our ability to -->
-<!-- interpret complex social systems?  -->
-<!-- Second, can variation in the social, spatial, -->
-<!-- and temporal scale improve predictions associated with biological differences in -->
-<!-- seasonal resource availability and social association?  -->
-
-<!--
-Multilayer networks can be built with different types of interactions
-
-In contrast to multilayer networks formed by combining layers defined
-by different types of interactions, multilayer networks with GPS data are limited to 
-proximity based measures. An alternative which has been explored is using 
-hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
-
-Another potential application would be
-to generate social networks during times when animals are engaged in different
-behaviours, including travelling, interacting, or foraging [@Muller_2018;
-@Finn_2019] and construct a multilayer network based on behaviour-specific
-monolayer networks [e.g. @Smith_Aguilar_2019].
-
-netTS
-
-However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015].
-
-With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017].
-
--->
-
-## Etc
 The integration of behavioural and ecological theory has shown the value of
@@
 
+## Phenotypes and Individual fitness
+
+Social network positions are frequently used to represent the social environment
+that an individual experiences or their social phenotype. Multilayer networks
+provide a way to bridge these different scales so that we can examine social
+phenotypes in more holistic ways rather than looking at each scale separately as
+has traditionally been done. From a monolayer network perspective, social
+phenotypes are increasingly linked to important fitness for individuals of
+various species, including primates [@Brent_2017; @Thompson_2019], dolphins
+[@Stanton_2012; @Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Both
+social scales, types of interactions, and temporal, seasons and stages of life,
+have emerged as important for understanding fitness consequences in the context
+of social network positions [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011].
+
+For instance, social scale is major consideration for social network analysis,
+especially in the context of different types of relationships, such as grooming
+and association, that are typically examined separately while answering a single
+question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
+common trope that individuals must be associating to interact, and many studies
+therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
+instance, baboons need to be in proximity to groom each other. However, animals
+have certain interactions that do not require proximity such as long-distance
+vocalization and olfactory signals [@Carter_2015]. With the advancement of
+biologging technology, we have the ability to record social interactions that do
+not require proximity, particularly long-distance communication networks with
+devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
+study results indicate that there are different social patterns in different
+habitat types, likely indicating different types of interactions. When the
+social threshold is greater than approximately 50 m during the winter,
+individuals demonstrate dramatically different graph strength (Figure 
+\@ref(fig:socres)) in different habitat types, having higher graph strength in
+forage and open habitats where they can likely see each other and still interact
+with visual cues unlike in forest habitats. Varying social scales can have
+different fitness repercussions for individuals. Rhesus macaques (*Macaca
+mulatta*) had higher survivorship when they had fewer but stronger, more stable
+social associates and grooming partners rather than simply more associates
+[@Ellis_2019]. This finding highlights that different qualities of social scales
+have lasting consequences. Multilayer networks provide the opportunity to
+address these types of questions involving social scale with all the individual
+layers of interaction integrated in a holistic way.
+
+Temporal scale is also important for understanding the repercussions of social
+phenotypes. Varying the time window length and position for caribou, we found
+there was a lot of variation in the multilayer network metrics (Figure
+\@ref(fig:winlen), Figure \@ref(fig:winpos)). These changes in the outcome
+depending on how the time window is defined highlight how critical it is to
+properly define the time window appropriately to address the questions and
+hypotheses of interest. For instance, social phenotypes can change over ontogeny
+in ways that can affect fitness [@Berger_2015; @Brent_2017]. Thus, it is
+critical to carefully consider the temporal scale that is meaningful for the
+proposed hypotheses. Further complicating the issue of selecting suitable time
+scales across ontogeny, individuals progress through development at different
+rates [@Tarka_2018]. This variation can make defining appropriate temporal
+scales for testing the fitness implications of an individual’s social phenotype
+over different stages of ontogeny even more difficult when they vary by
+individual. However, considering fine temporal scales provide insight across
+developmental stages that may otherwise be missed [@Turner_2017]. Defining
+temporal scales is a challenge in multilayer networks just as in monolayer
+networks; however, multilayer networks provide metrics that enable researchers
+to look at similarities and differences in separate layers representing
+different stages of ontogeny, or seasons as in our case study, which can be
+difficult to detect.
+
+Multilayer networks provide unique opportunities and challenges, linking
+various scales, for understanding the social phenotypes and environments of
+individuals and their fitness outcomes. The multilayer network framework enables
+researchers to examine these different social scales simultaneously rather than
+individually, which is what has been done under most circumstances, but is not
+very realistic. Metrics from multilayer networks provide an opportunity to
+simplify statistical models. Interactions that happen side-by-side, proximity
+associations, and long-distance interactions can be encapsulated in a single
+multilayer network, and a single metric can be used to describe the various
+social scales of an individual’s network position. This multilevel network
+metric could be used to assess the relationship between an individual’s social
+phenotype and fitness. It would also be a meaningful reduction of many
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks [@Castles_2014]. Furthermore, multilayer networks provide a framework
+to test hypotheses linking social phenotypes and fitness across temporal scales.
+Because of the non-independent nature of social interactions and associations,
+especially over time, it is hard to test hypotheses about social dynamics with a
+suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
+multilayer networks, making layers of different temporal periods provides a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods.
+
+Conversely, picking the proper temporal scale is important but a challenge
+because all layers in the multilayer network should reflect the same time
+period, and the period should be long enough for each layer to have enough data
+for robust networks [@Farine_2017]. These considerations may be limiting factors
+when answering questions that require time frames that are relevant to different
+individuals, for instance. In both mono- and multilayer networks, the effect of
+scale on the relationship between an individual’s social network position and
+fitness need to be considered based on the hypotheses being tested and
+logistical constraints.
+
 ## Movement ecology and collective movement
@@
 transfer about the quality or location of resources to other group members
-[@Jolles_2019]. We integrate proximity based social networks
+[@Jolles_2019]. In our case study, we integrate proximity based social networks
 that inherently rely on animal collective movement, and, in general, we found
@@
 
-<!-- fixed array -->
 Although multilayer animal social networks are relatively novel [@Silk_2018],
@@
 movement between fixed arrays is inherent, networks are not constructed based on
-continuous measures of dyadic or collective movement [@Long_2014]. Our
+continuous measures of dyadic or collective movement [@Long_2014]. Our case
 study builds on the work of Mourier et al. (2019) and explicitly integrates
@@
 fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
-@Flack_2018].
+@Flack_2018]. Our case study integrates variation in temporal and spatial scale
+to assess the role of scale in predicting multilayer networks. As one might
+expect, we found increasing social threshold results in saturation of potential
+social connections (Figure \@ref(fig:socres)).<!--TODO: what??, while increasing temporal scale had little effect
+on habitat-specific networks (Figure \@ref(fig:))-->. Another potential application would be
+to generate social networks during times when animals are engaged in different
+behaviours, including travelling, interacting, or foraging [@Muller_2018;
+@Finn_2019] and construct a multilayer network based on behaviour-specific
+monolayer networks [e.g. @Smith_Aguilar_2019].
+
+Importantly, the key to incorporating movement in multilayer networks across
+scales is the technological advancements available to overcome previous
+limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
+advanced to the point where relocations can be programmed to occur as frequently
+as each second [@B_rger_2016], a practice which has been applied to questions of
+collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
+technology, including unmanned aerial vehicles and satellites, can be used to
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]. Using technology to infer behaviour has therefore become
+standard operating procedure for many species in many systems. Our ability to
+collect and process remotely sensed data and infer social processes based on
+animal movement provides an opportunity to use multilayer social network
+analysis to answer complex questions about animal socioecology.
+
+Given the existing framework for constructing multilayer networks from
+behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
+quantify movement parameters could be integrated. For example, edges could
+represent measures of dyadic or collective movement based on dynamic interaction
+metrics [@Long_2014]. Integrating movement layers with habitat-specific social
+association layers could further illuminate the role of movement as a driver
+of the social and spatial environments an individual experiences [@Webber_2018].
+In our case study, we generated multilayer networks based on habitat-specific
+monolayers. Coordinated movement of dyads, or groups, could vary based on
+habitat, and the approach we outline could be used to explore mechanisms linking
+the social and spatial environments. For example, social processes may be an
+emergent property of the landscape because animals aggregate at resources, such
+as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
+patches or territories can also contribute to the formation of the social
+environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
+males interacted primarily at home range edges, presumably driving territorial
+behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
+network framework is a logical next step for a burgeoning field. In particular,
+when association networks are habitat-specific, we suggest the integration of
+movement and space use in multilayer networks provides novel insights into the
+effects of habitat configuration on the formation of the social environment
+[@He_2019; @Webber_2018].
+
+## Habitat selection and space use
+Social structure and habitat selection are intimately linked: individuals must
+share space to interact and the distribution of resources influences group
+dynamics and home range size [@Webber_2018]. Social structure is influenced by
+resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
+and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009]. Multilayer networks represent a
+novel framework for considering the influence of habitat selection and space use
+on sociality across scales.
+
+<!-- TODO: point to figure 1 -->
+Habitat selection depends on the scale at which it is measured and a singular
+scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
+selection is measured using resource selection functions (RSFs), based on the
+proportion of used and available resources for an animal [@Manly_1993;
+@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
+the geographical range of a species, (2) the home range of an individual, the
+(3) habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Moving past this hierarchical perspective, Mayor (2007) emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviours. Despite animals selecting for different landscape attributes
+at different scales [@Mayor_2009], the use of multiscale analyses for habitat
+selection is still critically lacking [@McGarigal_2016].
+
+The emergent relationship between habitat and sociality has been explored by the
+distribution and phenology of resources and use of social information. Cougar
+(*Puma concolor*) home ranges overlapped more in regions with high hunting
+opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou (*Rangifer
+tarandus*) sociality differed between seasons, where social associations were
+stronger in winter and contrastingly low in summer when resource availability
+are more homogeneous [@Peignier_2019]. Bison (*Bison bison*) showed stronger
+habitat selection in larger groups and avoidance of predation risk was a main
+factor contributing to their habitat selection [@Fortin_2009]. These examples,
+comparing sociality and habitat selection across temporal or spatial contexts,
+are implicitly multilayer analyses.
+
+<!-- TODO: weak --> 
+Multilayer networks can be used to explicitly consider
+habitat selection and sociality across scales. Animal social systems can be
+parsed by spatial contexts, defined, for example, by habitat types as in Figure
+\@ref(fig:lcres). The effect of seasonality of resources can can be directly
+measured by differences in habitat selection and sociality across temporal
+layers as in Figure \@ref(fig:winpos) and Figure \@ref(fig:winlen). Habitat
+selection can be explicitly integrated using network layers defined by selection
+coefficients for individuals. These examples of explicit integrations of habitat selection
+and sociality across social, spatial and temporal scales highlight the potential
+for novel insights from multilayer networks.
 
 # Conclusions
+
 Multilayer networks remain a nascent but powerful tool in animal behavioural
 ecology. We demonstrate the potential novel analyses that vary social, spatial,
-and temporal scale within a multilayer framework. We
-show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
+and temporal scale within a multilayer framework. In our caribou case study, we
+show that (1) multilayer social networks can be, but are not always,
+scale-dependent, and (2) the use of multilayer networks could be useful for
 identifying habitat or season-specific social processes. Our analyses of social,
@@
 different scales and units of measurement. Our analysis of caribou multilayer
-networks which incorporated high resolution GPS telemetry data and spatial land cover
+networks which incorporated high resolution GPS telemetry data and spatial landcover
 data is grounded in the context of observed animal social networks, as the
 scales we chose to explore, e.g., number of observations, sociality across space
-and time, are ones that can be observed as has <!-- edit-->traditionally been done in
+and time, are ones that can be observed as has traditionally been done in
 ethology. We highlight ways in which scale ought to be considered for both
-observed and remotely-sensed data when building social networks. GPS telemetry 
-data provides a link between large scale landscape properties and
+observed and remotely-sensed data when building social networks. Furthermore,
+GPS telemetry data provides a link between large scale landscape properties and
 fine scale social interactions as animal movement occurs across the landscape,
-and when taken into account with multiple individuals<!-- edit--> can indicate association
+and when taken into account with multiple individuals can indicate association
 patterns. Thus, a layer incorporating relocation data could be a great boon
 linking spatial and social layer in multilayer networks.
+
+<!-- JWT: I'm having a hard time getting to where I want to go, but basically I want to highlight that using GPS relocation data is reflective of more traditional observed networks like they wanted when they accepted our abstract, and this provides opportunities for social networks, particularly multilayer networks.
+It may be easier to scale relocation data and other landscape variables and can link to smaller scale observed interactions, providing a bridge between different types of data.
+-->
 
@@
 
+<!-- TODO: In summary, -->
+
 # Acknowledgements
@@
 We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
-Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J. Hogg, and L.
+Hendrix, K. Kingdon, S. Boyle, C. Prokopenko, I. Richmond, J. Hogg, and L.
 Newediuk for their comments on previous versions of this manuscript as well as
@@
 ```{r spacetime, fig.cap='(ref:spacetime)'}
-knitr::include_graphics('../graphics/figure-scales.png')
+knitr::include_graphics('../graphics/figure1.png')
 ```
@@
 
-(ref:ml) Visualization of multilayer network representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Twelve layers represent combinations of four time windows and three habitat classes (open, forest and forage).
-Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+```{r ml, fig.cap='(ref:ml)'}
+knitr::include_graphics('../graphics/figure-2.png')
+```
 
-```{r ml, fig.cap='(ref:ml)'}
-knitr::include_graphics('../graphics/figure-fogo-ml.png')
+\newpage
+
+```{r socres, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-spatialthreshold.png')
 ```
@@
 ```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lc.png')
-```
-
-\newpage
-
-```{r temp, fig.cap='(ref:temp)'}
-knitr::include_graphics('../graphics/figure-temp.png')
-```
-
-\newpage
-
-```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-soc.png')
+knitr::include_graphics('../graphics/figure-lcres.png')
 ```
@@
 \newpage
+
+```{r winlen, fig.cap='(ref:winlen)'}
+knitr::include_graphics('../graphics/figure-winlength.png')
+```
+
+\newpage
+
+```{r winpos, fig.cap='(ref:winpos)'}
+knitr::include_graphics('../graphics/figure-winpos.png')
+```
+
+\newpage
 \clearpage

### 2020-06-15 paper/manuscript.Rmd
Revert "minor change - practice push on q branch"
This reverts commit cb306a2d1f8a5d3f27f02bc6f1e73a63b70031b5.

@@
 
-Multilayer networks provide unique opportunities and challenges, linking
+Multilayer networks provide unique opportunities and challenges, linking these
 various scales, for understanding the social phenotypes and environments of

### 2020-06-16 paper/manuscript.Rmd
ecological processes

--- 2020-06-15 paper/manuscript.Rmd
@@
 are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales, through processes such as
+@Allen_2015]. Animals are influenced across scales, through ecological processes such as
 species-specific as trophic interactions and resource availability
-[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
+[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
 Multiscale ecology has been integrated into species distribution modelling

### 2020-06-16 paper/manuscript.Rmd
last sentence of intro paragraph
last sentence P2

@@
 animal behaviour within the social environment will be scale-dependent. 
+<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->
 
@@
 predictably with social interaction [@Castles_2014;
-@Farine_2015a]. Thus, we define social scale as the type of social relationship
-observed that can be explicitly defined and measured [@Farine_2015a].
+@Farine_2015a]. We therefore define social scale as the type of social relationship
+observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
+potential for adaptive variance in social relationships is also scale-dependent. 
+<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
+under the expectation that there is some scale at which variance is greatest, and presumably
+it is this scale that has the greatest effect on fitness or other traits-->
 

### 2020-06-16 paper/manuscript.Rmd
are > is

@@
 
-Our examinations is motivated by behavioural, landscape, and spatial ecology to
+Our examinations are motivated by behavioural, landscape, and spatial ecology to
 build a conceptual and analytical framework for scale-dependent multilayer

### 2020-06-16 paper/manuscript.Rmd
question 35-36 days

@@
 sociality. Multilayer networks consisted of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
 days taken from the entire study period. Social associations were defined by

### 2020-06-16 paper/manuscript.Rmd
tweak sentence - add figure

@@
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a
-decrease in rate after 100 m. These results suggest the optimal social scale at
+sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
+the rate of increase after 100 m (figure XX). These results suggest the optimal social scale at
 which groups should be assigned is likely somewhere between ~20 - 100 m based on

### 2020-06-16 paper/manuscript.Rmd
TODO - add figure

--- 2020-06-16 paper/manuscript.Rmd
@@
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a
-decrease in rate after 100 m. These results suggest the optimal social scale at
+sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
+the rate of increase after 100 m (<!--TODO: figure XX-->). 
+These results suggest the optimal social scale at
 which groups should be assigned is likely somewhere between ~20 - 100 m based on

### 2020-06-16 paper/manuscript.Rmd
which metrics?

@@
 These results suggest the optimal social scale at
-which groups should be assigned is likely somewhere between ~20 - 100 m based on
-the rate at which network metrics stabilized. For ungulates, groups are often
+which groups should be assigned is between ~20 - 100 m based on
+the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
 assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier

### 2020-06-16 paper/manuscript.Rmd
question about last sentence

@@
 an appropriate social scale for generating social networks in caribou and
-similar species.
+similar species. <!--QW: I'm not sure about this statement. Should it be more about 
+how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
+the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
+any Clutton-Brock red deer paper that uses group size data)-->
 

### 2020-06-16 paper/manuscript.Rmd
foraging habitat > forage

@@
 
-Increasing land cover resolution resulted in decreased availability of forage,
+Increasing land cover resolution resulted in decreased availability of foraging habitat 
+<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
+refers to the thing an animal is eating-->,
 a rare and patchy habitat, and corresponding low connectivity of individuals in

### 2020-06-16 paper/manuscript.Rmd
foraging habitat - add habitat after open/forest
foraging > forage

@@
 1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
-forage layers across land cover resolutions than open and forest (Figure
+foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
 \@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
-increased with increasing spatial resolution, while decreasing in forage habitat
+increased with increasing spatial resolution, while decreasing in foraging habitat
 (Supplementary 1 Figure 1).  Overall, these results indicate the importance of

### 2020-06-16 paper/manuscript.Rmd
question about sentence 1

@@
 The ordinal multilayer network generated indicated within-year time windows of
-increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
+increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
+Edge overlap was higher in time windows 1, 6-11 and
 15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time

### 2020-06-16 paper/manuscript.Rmd
dates vs. window number

@@
 Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
+15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
 windows of higher edge overlap, between approximately October and May, had

### 2020-06-16 paper/manuscript.Rmd
question about use of word ordinal
variance decreased instead of stabilize

@@
 rare habitats.
-
+<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
 The ordinal multilayer network generated indicated within-year time windows of
@@
 
-As the number of observations used to generate multilayer networks increased,
-individuals became more connected and metrics generally appeared to stabilize.
+As one might expect, when the number of observations used to generate multilayer networks increased,
+individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
 Graph strength across individuals in all three habitat layers was highly

### 2020-06-16 paper/manuscript.Rmd
rare vs patchy

@@
 resolution lead to a decrease in availability of patchy and rare habitats and, 
+<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
+Could you just say 'less common' or even just 'patchy'?-->
 correspondingly, lower connectivity of individuals in these habitats. Temporal

### 2020-06-16 paper/manuscript.Rmd
intro to discussion comment

@@
 them up.
+<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
+You could focus on just talking about the importance of scale for behavioural and spatial ecology.
+Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
+Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
+above with what you already have-->
 

### 2020-06-16 paper/manuscript.Rmd
minor edits in discussion

@@
 positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale at which to generate networks is an
+@Holekamp_2011]. Defining the social scale to generate networks is an
 essential consideration for social network analysis <!-- with direct impacts on
@@
 specifically a spatial distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
+found increasing individual graph strength across three habitat types with
 increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*Rangifer tarandus*) sociality differed between seasons, where social
-associations were stronger in winter and contrastingly low in summer when
+(*Rangifer tarandus*) social network graph strength differed between seasons, where 
+graph strength was stronger in winter and contrastingly low in summer when
 resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison

### 2020-06-16 paper/manuscript.Rmd
lichen > forage

@@
 resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
+open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion

### 2020-06-16 paper/manuscript.Rmd
what % of the landscape is lichen?

--- 2020-06-16 paper/manuscript.Rmd
@@
 resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
+open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion

### 2020-06-16 paper/manuscript.Rmd
minor edits in discussion

@@
 habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Forage and open
-layers had greater individual variation in graph strength, while forage was the
-sole layer to show large responses in graph strength to increasing spatial
+increasing spatial resolution and variation between individuals. Lichen and open
+layers had greater individual variation in graph strength, while lichen was the
+only layer to show large responses in graph strength to increasing spatial
 resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
@@
 
-The selection of time windows is essential for capturing sociality in specific
+Selection of appropriate time windows is essential for capturing sociality in specific
 life stages of interest. Social phenotypes can change over ontogeny in ways that

### 2020-06-17 paper/manuscript.Rmd
edit abstract

@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges, and vary within and 
+interactions to co-occurrence to overlapping home ranges and vary within and 
 across seasons. Multilayer networks promise the integration of monolayer
@@
 processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research, as such our contribution
-incorporates perspectives on how the social environment and spatial processes
+animal social networks is an emerging area of research. Here, we
+incorporate perspectives on how the social environment and spatial processes
 are linked across scales in a multilayer context.

### 2020-06-17 paper/manuscript.Rmd
intro p1

@@
 @Allen_2015]. Animals are influenced across scales, through ecological processes such as
-species-specific as trophic interactions and resource availability
+species-specific trophic interactions, resource availability
 [@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
+<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
 Multiscale ecology has been integrated into species distribution modelling
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
-among others. Meanwhile, in the context of animal behaviour, certain behaviours
+among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
 are scale-dependent; for example, acoustic communication in birds varies with

### 2020-06-17 paper/manuscript.Rmd
rest of intro edits

@@
 social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the social, spatial or temporal scales associated
+novel understanding of variation in the social, spatial, or temporal scales associated
 with social systems.
@@
 and space use.
+<!-- JWT: This part may have to change depending on how we do the disc -->
 

### 2020-06-17 paper/manuscript.Rmd
methods through network metrics edits

@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+We used GPS location data collected from Fogo Island caribou between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 Adult female caribou were immobilized and fitted with global positioning
@@
 Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. Extending degree centrality, we calculated multidegree,
+case SRI, in each layer. Extending degree centrality to multiple layers, we calculated multidegree,
 the sum of degree centrality of individuals across layers  [@Berlingerio_2012;

### 2020-06-17 paper/manuscript.Rmd
rest of methods edits

@@
 We generated multilayer networks across a series of spatial distance thresholds 
+that relate to behavioural interactions that could occur within those distances
+<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
 for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
@@
 multidegree for each habitat layer and spatial distance threshold, and edge
+<!-- JWT: can we call spatial distance social distance? -->
 overlap across the entire series of networks to determine proportion of total
@@
 (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social association between 
+multilayer network consisting of the social associations between 
 `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
@@
 edges observed in each combination of habitat layer and spatial scale.
+<!-- JWT: Your graphs present things in the order of Forage, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->
 
@@
 We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social association between 
+sociality. Multilayer networks consisted of the social associations between 
 `r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->

### 2020-06-17 paper/manuscript.Rmd
results edits

@@
 Individuals in multilayer networks became more connected as the spatial distance
+<!-- JWT: I really think calling it spatial distance is misleading given we want to represent social scale.
+Even if we stick with calling it spatial distance (I see you call it social distance in the graph), we need to lead in calling it social scale so the reader knows that's what we're referencing.
+-->
 threshold increased. Mean graph strength differed across habitat layers with
@@
 foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
-\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
+\@ref(fig:lcres) D).
+<!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again.
+I think this should be reordered so it's easier to follow.
+-->
+The proportion of relocations in forest and open habitats
 increased with increasing spatial resolution, while decreasing in foraging habitat
@@
 <!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in spatial distance threshold.
-For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+(ref:socres) Varying scale in social distance threshold.
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*R.
+tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*R.
+tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*R.
+tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (*R.
+tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 Graph strength peaked in time window 9, with noticeable higher strength than the following year.
+
+<!-- JWT: edge overlap, graph strength, and multidegree are presented in different orders in the graphs.
+They should be presented in the same order each time even if the combination of what you show changes.
+-->
 

### 2020-06-17 paper/manuscript.Rmd
Disc p 1 and 2

@@
 windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations lead to a general stabilizing in network
+Finally, increasing number of observations led to a general stabilization in network
 metrics. As such, scale is inherently tied to the generation  of multilayer
@@
 for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
 @Holekamp_2011]. Defining the social scale to generate networks is an
@@
 found increasing individual graph strength across three habitat types with
-increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
+increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
 habitat layers differed in their response to spatial distance threshold, with
 open and forage with a larger increase in graph strength and greater variation
-across individuals. These results emphasize that multilayer network metrics are
+across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
 directly influenced by social scale, in this case the spatial distance

### 2020-06-17 paper/manuscript.Rmd
more disc edits

@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*Rangifer tarandus*) social network graph strength differed between seasons, where 
+(*R. tarandus*) social network graph strength differed between seasons, where 
 graph strength was stronger in winter and contrastingly low in summer when
 resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
-bison*) showed stronger habitat selection in larger groups and avoidance of
+bison*) showed stronger habitat selection in larger groups, and avoidance of
 predation risk was a main factor contributing to their habitat selection
@@
 of relocations in this habitat type with increasing spatial resolution (Supplementary 1
-Figure 1). Similar to increasing spatial distance threshold, the influence
+Figure 1). Similar to increasing social distance threshold, the influence
 of increasing spatial resolution on graph strength was notably different between

### 2020-06-17 paper/manuscript.Rmd
rest of disc comments

@@
 habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
+the social and spatial environments.<!--  <- long sentence with two coulds -->For example, social processes may be an 
 emergent property of the landscape because animals aggregate at resources, such
@@
 provide insight across developmental stages that may otherwise be missed
-[@Turner_2017]. Furthermore, given the non-independent nature of social
+[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. --> 
+Furthermore, given the non-independent nature of social
 interactions and associations, especially over time, it can be challenging to

### 2020-06-17 scripts/render/render-manuscript.R
fix render scripts

@@ -1,4 +1,4 @@
-manuscript = render(
+rmarkdown::render(
   'paper/manuscript.Rmd',
   output_format = 'all',
   quiet = TRUE

### 2020-06-17 scripts/render/render-supplement.R

@@ -1,4 +1,4 @@
-manuscript = render(
+rmarkdown::render(
   'paper/supplement.Rmd',
   output_format = 'all',
   quiet = TRUE

### 2020-06-17 paper/manuscript.Rmd
comment on ending
fix render line in knit

--- 2020-06-17 paper/manuscript.Rmd
@@
      reference_docx: template.docx
-knit: (function(inputFile, encoding) {
-  rmarkdown::render(inputFile, encoding = encoding,
-  output_format = "all") })
+knit: (function(inputFile) {
+  rmarkdown::render(inputFile, output_format = "all") })
 bibliography: ../references/knitcite.bib
@@
 and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges and vary within and 
+interactions to co-occurrence to overlapping home ranges, and vary within and 
 across seasons. Multilayer networks promise the integration of monolayer
@@
 processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research. Here, we
-incorporate perspectives on how the social environment and spatial processes
+animal social networks is an emerging area of research, as such our contribution
+incorporates perspectives on how the social environment and spatial processes
 are linked across scales in a multilayer context.
@@
 are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales, through ecological processes such as
-species-specific trophic interactions, resource availability
-[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
-<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
+@Allen_2015]. Animals are influenced across scales, through processes such as
+species-specific as trophic interactions and resource availability
+[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
 Multiscale ecology has been integrated into species distribution modelling
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
-among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
+among others. Meanwhile, in the context of animal behaviour, certain behaviours
 are scale-dependent; for example, acoustic communication in birds varies with
@@
 animal behaviour within the social environment will be scale-dependent.
-<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->
 
@@
 predictably with social interaction [@Castles_2014;
-@Farine_2015a]. We therefore define social scale as the type of social relationship
-observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
-potential for adaptive variance in social relationships is also scale-dependent. 
-<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
-under the expectation that there is some scale at which variance is greatest, and presumably
-it is this scale that has the greatest effect on fitness or other traits-->
+@Farine_2015a]. Thus, we define social scale as the type of social relationship
+observed that can be explicitly defined and measured [@Farine_2015a].
 
@@
 social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the social, spatial, or temporal scales associated
+novel understanding of variation in the social, spatial or temporal scales associated
 with social systems.
 
-Our examinations are motivated by behavioural, landscape, and spatial ecology to
+Our examinations is motivated by behavioural, landscape, and spatial ecology to
 build a conceptual and analytical framework for scale-dependent multilayer
@@
 and space use.
-<!-- JWT: This part may have to change depending on how we do the disc -->
 
@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+We used GPS location data collected from Fogo Island caribou in between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 Adult female caribou were immobilized and fitted with global positioning
@@
 Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. Extending degree centrality to multiple layers, we calculated multidegree,
+case SRI, in each layer. Extending degree centrality, we calculated multidegree,
 the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
@@
 We generated multilayer networks across a series of spatial distance thresholds
-that relate to behavioural interactions that could occur within those distances
-<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
 for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
@@
 multidegree for each habitat layer and spatial distance threshold, and edge
-<!-- JWT: can we call spatial distance social distance? -->
 overlap across the entire series of networks to determine proportion of total
@@
 (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social associations between 
+multilayer network consisting of the social association between 
 `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
@@
 edges observed in each combination of habitat layer and spatial scale.
-<!-- JWT: Your graphs present things in the order of Forage, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->
 
@@
 We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
+sociality. Multilayer networks consisted of the social association between 
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
 days taken from the entire study period. Social associations were defined by
@@
 Individuals in multilayer networks became more connected as the spatial distance
-<!-- JWT: I really think calling it spatial distance is misleading given we want to represent social scale.
-Even if we stick with calling it spatial distance (I see you call it social distance in the graph), we need to lead in calling it social scale so the reader knows that's what we're referencing.
--->
 threshold increased. Mean graph strength differed across habitat layers with
@@
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
-the rate of increase after 100 m (<!--TODO: figure XX-->). 
-These results suggest the optimal social scale at
-which groups should be assigned is between ~20 - 100 m based on
-the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
+sharply between 5 m and 100 m in all three habitat classes followed by a
+decrease in rate after 100 m. These results suggest the optimal social scale at
+which groups should be assigned is likely somewhere between ~20 - 100 m based on
+the rate at which network metrics stabilized. For ungulates, groups are often
 assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
@@
 an appropriate social scale for generating social networks in caribou and
-similar species. <!--QW: I'm not sure about this statement. Should it be more about 
-how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
-the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
-any Clutton-Brock red deer paper that uses group size data)-->
+similar species.
 
-Increasing land cover resolution resulted in decreased availability of foraging habitat 
-<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
-refers to the thing an animal is eating-->,
+Increasing land cover resolution resulted in decreased availability of forage,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
@@
 1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
-foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
-\@ref(fig:lcres) D).
-<!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again.
-I think this should be reordered so it's easier to follow.
--->
-The proportion of relocations in forest and open habitats
-increased with increasing spatial resolution, while decreasing in foraging habitat
+forage layers across land cover resolutions than open and forest (Figure
+\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
+increased with increasing spatial resolution, while decreasing in forage habitat
 (Supplementary 1 Figure 1).  Overall, these results indicate the importance of
@@
 rare habitats.
-<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
+
 The ordinal multilayer network generated indicated within-year time windows of
-increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
-Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
+increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
+15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
 windows of higher edge overlap, between approximately October and May, had
@@
 
-As one might expect, when the number of observations used to generate multilayer networks increased,
-individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
+As the number of observations used to generate multilayer networks increased,
+individuals became more connected and metrics generally appeared to stabilize.
 Graph strength across individuals in all three habitat layers was highly
@@
 <!-- Figure: metrics by social scale -->
-(ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+(ref:socres) Varying scale in spatial distance threshold.
+For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 Graph strength peaked in time window 9, with noticeable higher strength than the following year.
-
-<!-- JWT: edge overlap, graph strength, and multidegree are presented in different orders in the graphs.
-They should be presented in the same order each time even if the combination of what you show changes.
--->
 
@@
 resolution lead to a decrease in availability of patchy and rare habitats and,
-<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
-Could you just say 'less common' or even just 'patchy'?-->
 correspondingly, lower connectivity of individuals in these habitats. Temporal
 windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations led to a general stabilization in network
+Finally, increasing number of observations lead to a general stabilizing in network
 metrics. As such, scale is inherently tied to the generation  of multilayer
@@
 them up.
-<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
-You could focus on just talking about the importance of scale for behavioural and spatial ecology.
-Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
-Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
-above with what you already have-->
 
@@
 for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale to generate networks is an
+positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011]. Defining the social scale at which to generate networks is an
 essential consideration for social network analysis <!-- with direct impacts on
@@
 specifically a spatial distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat types with
-increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
+found increasing individual graph strength across three habitat layers with
+increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
 habitat layers differed in their response to spatial distance threshold, with
 open and forage with a larger increase in graph strength and greater variation
-across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
+across individuals. These results emphasize that multilayer network metrics are
 directly influenced by social scale, in this case the spatial distance
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*Rangifer tarandus*) social network graph strength differed between seasons, where 
-graph strength was stronger in winter and contrastingly low in summer when
+(*Rangifer tarandus*) sociality differed between seasons, where social
+associations were stronger in winter and contrastingly low in summer when
 resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
@@
 resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
+open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
@@
 habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Lichen and open
-layers had greater individual variation in graph strength, while lichen was the
-only layer to show large responses in graph strength to increasing spatial
+increasing spatial resolution and variation between individuals. Forage and open
+layers had greater individual variation in graph strength, while forage was the
+sole layer to show large responses in graph strength to increasing spatial
 resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
@@
 
-Selection of appropriate time windows is essential for capturing sociality in specific
+The selection of time windows is essential for capturing sociality in specific
 life stages of interest. Social phenotypes can change over ontogeny in ways that

### 2020-06-17 paper/supplement.Rmd
fix render line in knit

@@
    #   reference_docx: template.docx
-knit: (function(inputFile, encoding) {
-  rmarkdown::render(inputFile, encoding = encoding,
+knit: (function(inputFile) {
+  rmarkdown::render(inputFile,
   output_format = "all") })

### 2020-06-18 paper/manuscript.Rmd
rm source bc of self invalidation
fix smashed pars and sentences from comments

--- 2020-06-17 paper/manuscript.Rmd
@@
 output:
-   bookdown::github_document2: default
+   # bookdown::github_document2: default
    bookdown::word_document2:
@@
 rare habitats.
+
 <!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
@@
 habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments.<!--  <- long sentence with two coulds -->For example, social processes may be an 
+the social and spatial environments.<!--  <- long sentence with two coulds --> For example, social processes may be an 
 emergent property of the landscape because animals aggregate at resources, such
@@
 
+<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
+
 # Acknowledgements

### 2020-06-18 paper/manuscript.Rmd
fix encoding in rmd

--- 2020-06-17 paper/manuscript.Rmd
@@
    bookdown::github_document2: default
-   bookdown::word_document2:
-     reference_docx: template.docx
-knit: (function(inputFile) {
-  rmarkdown::render(inputFile, output_format = "all") })
+   # bookdown::word_document2:
+   #   reference_docx: template.docx
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
 bibliography: ../references/knitcite.bib
@@
 
-source('../scripts/00-variables.R')
+# source('../scripts/00-variables.R')
 

### 2020-06-18 paper/supplement.Rmd
rm source bc of self invalidation
fix encoding in rmd

@@
    #   reference_docx: template.docx
-knit: (function(inputFile) {
-  rmarkdown::render(inputFile,
-  output_format = "all") })
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
 bibliography: ../references/knitcite.bib

### 2020-06-18 paper/manuscript.Rmd
fst readd instead of include graphics

@@
     echo = FALSE,
-    # warning = FALSE,
-    # message = FALSE,
     eval = TRUE,
@@
 
-# source('../scripts/00-variables.R')
+library(data.table)
 
-library(data.table)
-DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
-nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
+drake::loadd(vars)
+
+drake::loadd(data)
+DT <- sub
+setalloccol(DT)
+
+drake::loadd(nobs)
+
 timedefs <- fread('../data/supp-data/timecut-defs.csv')
@@
 ```{r lcres, fig.cap='(ref:lcres)'}
-knitr::include_graphics('../graphics/figure-lc.png')
+# knitr::include_graphics('../graphics/figure-lc.png')
+drake::readd(lc_figure)
 ```

### 2020-06-18 scripts/figures/figure-fogo-ml.R
add figs as last line in figure scripts for drake

@@ -162,3 +162,6 @@ ggsave('graphics/figure-fogo-ml.png',
 
 # ggsave('graphics/supp-temp-nid.png',
 #        gnid, width = 5, height = 5)
+
+# For drake
+g

### 2020-06-18 scripts/figures/figure-lc.R

@@ -122,3 +122,7 @@ ggsave('graphics/figure-lc.png',
 
 ggsave('graphics/supp-count-lc.png',
        gcount, width = 5, height = 5)
+
+
+# For drake
+g

### 2020-06-18 scripts/figures/figure-ml.R

@@ -181,3 +181,6 @@ labels <- data.table(
 
 # Output ------------------------------------------------------------------
 ggsave('graphics/figure-ml.png', width = 8, height = 6)
+
+# For drake
+gnn

### 2020-06-18 scripts/figures/figure-nobs.R

@@ -89,3 +89,7 @@ ggsave('graphics/figure-nobs.png',
 
 # ggsave('graphics/supp-temp-nid.png',
 #        gnid, width = 5, height = 5)
+
+
+# For drake
+g

### 2020-06-18 scripts/figures/figure-temp.R

@@ -121,3 +121,7 @@ ggsave('graphics/figure-temp.png',
 
 ggsave('graphics/supp-temp-nid.png',
        gnid, width = 5, height = 5)
+
+
+# For drake
+g

### 2020-06-18 paper/manuscript.Rmd
revert to readRDS in manuscript
replace source variables for now
rm manuscript and supp from plan (for now)

@@
 
-drake::loadd(vars)
+source('../scripts/00-variables.R')
 
-drake::loadd(data)
-DT <- sub
-setalloccol(DT)
-
-drake::loadd(nobs)
-
+DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
+nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
 timedefs <- fread('../data/supp-data/timecut-defs.csv')
@@
 ```{r lcres, fig.cap='(ref:lcres)'}
-# knitr::include_graphics('../graphics/figure-lc.png')
-drake::readd(lc_figure)
+knitr::include_graphics('../graphics/figure-lc.png')
 ```

### 2020-06-18 scripts/plan.R

@@ -62,17 +62,17 @@ plan <- drake_plan(
   
   # Number of observations
   nobs = scale_nobs(data),
-  nobs_figure = fig_nobs(nobs),
+  nobs_figure = fig_nobs(nobs)
   
   # TODO: fogo car ml
   
   # Manuscript
-  manuscript = rmarkdown::render(
-    knitr_in('paper/manuscript.Rmd')
-  ),
-  
-  # Supplement
-  supplement = rmarkdown::render(
-    knitr_in('paper/supplement.Rmd')
-  )
+  # manuscript = rmarkdown::render(
+  #   knitr_in('paper/manuscript.Rmd')
+  # ),
+  # 
+  # # Supplement
+  # supplement = rmarkdown::render(
+  #   knitr_in('paper/supplement.Rmd')
+  # )
 )

### 2020-06-20 paper/manuscript.Rmd
small edits todo

--- 2020-06-18 paper/manuscript.Rmd
@@
 output:
-   bookdown::github_document2: default
-   # bookdown::word_document2:
-   #   reference_docx: template.docx
+   # bookdown::github_document2: default
+   bookdown::word_document2:
+     reference_docx: template.docx
 knit: (function(inputFile, encoding) {
-  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
+  rmarkdown::render(inputFile, encoding = encoding,
+  output_format = "all") })
 bibliography: ../references/knitcite.bib
@@
 
-# source('../scripts/00-variables.R')
+source('../scripts/00-variables.R')
 
@@
 are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales, through processes such as
-species-specific as trophic interactions and resource availability
-[@Legendre_1993; @Chave_2013] and global climate and productivity [@Field_2009].
+@Allen_2015]. Animals are influenced across scales, through ecological processes such as
+species-specific trophic interactions, resource availability
+[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
+<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
 Multiscale ecology has been integrated into species distribution modelling
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
-among others. Meanwhile, in the context of animal behaviour, certain behaviours
+among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
 are scale-dependent; for example, acoustic communication in birds varies with
@@
 used to describe multidimensional human social systems, complex transportation
-networks, and neural networks [@Silk_2018]. The role of scale within multilayer
+networks, and neural networks [@Silk_2018]. <!-- just "scale".. edit sent -->The role of scale within multilayer
 social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the social, spatial or temporal scales associated
+novel understanding of variation in the social, spatial, or temporal scales associated
 with social systems.
 
-Our examinations is motivated by behavioural, landscape, and spatial ecology to
+<!-- we examined-->Our examinations are motivated by behavioural, landscape, and spatial ecology to
 build a conceptual and analytical framework for scale-dependent multilayer
@@
 interpret complex social systems? Second, can variation in the social, spatial,
-and temporal scale improve predictions associated with biological differences in
+and temporal scale improve <!-- replace pred-->predictions associated with biological differences in
 seasonal resource availability and social association? We conclude with
@@
 We used a temporal multilayer network to assess the seasonality of caribou
-sociality. Multilayer networks consisted of the social association between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
+sociality. Multilayer networks consisted of the social associations between 
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
 days taken from the entire study period. Social associations were defined by
@@
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a
-decrease in rate after 100 m. These results suggest the optimal social scale at
-which groups should be assigned is likely somewhere between ~20 - 100 m based on
-the rate at which network metrics stabilized. For ungulates, groups are often
+sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
+the rate of increase after 100 m (<!--TODO: figure XX-->). 
+These results suggest the optimal social scale at
+which groups should be assigned is between ~20 - 100 m based on
+the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
 assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
@@
 an appropriate social scale for generating social networks in caribou and
-similar species.
+similar species. <!--QW: I'm not sure about this statement. Should it be more about 
+how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
+the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
+any Clutton-Brock red deer paper that uses group size data)-->
 
-Increasing land cover resolution resulted in decreased availability of forage,
+Increasing land cover resolution resulted in decreased availability of foraging habitat 
+<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
+refers to the thing an animal is eating-->,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
@@
 1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
-forage layers across land cover resolutions than open and forest (Figure
-\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
-increased with increasing spatial resolution, while decreasing in forage habitat
+foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
+\@ref(fig:lcres) D).
+<!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again.
+I think this should be reordered so it's easier to follow.
+-->
+The proportion of relocations in forest and open habitats
+increased with increasing spatial resolution, while decreasing in foraging habitat
 (Supplementary 1 Figure 1).  Overall, these results indicate the importance of
@@
 
+<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
 The ordinal multilayer network generated indicated within-year time windows of
-increased caribou sociality. Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). Time
+increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
+Edge overlap was higher in time windows 1, 6-11 and
+15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
 windows of higher edge overlap, between approximately October and May, had
@@
 resolution lead to a decrease in availability of patchy and rare habitats and, 
+<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
+Could you just say 'less common' or even just 'patchy'?-->
 correspondingly, lower connectivity of individuals in these habitats. Temporal
 windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations lead to a general stabilizing in network
+Finally, increasing number of observations led to a general stabilization in network
 metrics. As such, scale is inherently tied to the generation  of multilayer
@@
 for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale at which to generate networks is an
+positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011]. Defining the social scale to generate networks is an
 essential consideration for social network analysis <!-- with direct impacts on
@@
 specifically a spatial distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing spatial distance threshold (Figure \@ref(fig:socres)). In addition,
+found increasing individual graph strength across three habitat types with
+increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
 habitat layers differed in their response to spatial distance threshold, with
 open and forage with a larger increase in graph strength and greater variation
-across individuals. These results emphasize that multilayer network metrics are
+across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
 directly influenced by social scale, in this case the spatial distance
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*Rangifer tarandus*) sociality differed between seasons, where social
-associations were stronger in winter and contrastingly low in summer when
+(*R. tarandus*) social network graph strength differed between seasons, where 
+graph strength was stronger in winter and contrastingly low in summer when
 resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
-bison*) showed stronger habitat selection in larger groups and avoidance of
+bison*) showed stronger habitat selection in larger groups, and avoidance of
 predation risk was a main factor contributing to their habitat selection
@@
 resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage is a rare and
+open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
 of relocations in this habitat type with increasing spatial resolution (Supplementary 1
-Figure 1). Similar to increasing spatial distance threshold, the influence
+Figure 1). Similar to increasing social distance threshold, the influence
 of increasing spatial resolution on graph strength was notably different between
 habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Forage and open
-layers had greater individual variation in graph strength, while forage was the
-sole layer to show large responses in graph strength to increasing spatial
+increasing spatial resolution and variation between individuals. Lichen and open
+layers had greater individual variation in graph strength, while lichen was the
+only layer to show large responses in graph strength to increasing spatial
 resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
@@
 habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments. For example, social processes may be an
+the social and spatial environments.<!--  <- long sentence with two coulds --> For example, social processes may be an 
 emergent property of the landscape because animals aggregate at resources, such

### 2020-06-20 paper/manuscript.Rmd
social distance threshold

@@
 buffered GPS fixes at each time step. As such, individuals in a group are within
-the spatial distance threshold of at least one other though not necessarily all
+the social distance threshold of at least one other though not necessarily all
 other individuals [@Robitaille_2019]. Group assignment based on the chain rule
 has previously been applied to caribou using a temporal threshold of 5 minutes
-and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
+and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
 all networks, individual caribou were represented as nodes and associations between
@@
 simultaneous fixes from individuals A and B that were separated by more than the
-spatial distance threshold [@Farine_2015].
+social distance threshold [@Farine_2015].
 
@@
 
-We generated multilayer networks across a series of spatial distance thresholds 
+We generated multilayer networks across a series of social distance thresholds 
 that relate to behavioural interactions that could occur within those distances
 <!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
-for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
+for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
 500 m) represented a range of visual (short distance) to auditory (long
@@
 another were considered in the same group. We calculated graph strength and
-multidegree for each habitat layer and spatial distance threshold, and edge
+multidegree for each habitat layer and social distance threshold, and edge
 <!-- JWT: can we call spatial distance social distance? -->
@@
 
-As one might expect, when the number of observations used to generate multilayer networks increased,
+As the number of observations used to generate multilayer networks increased,
 individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
@@
 multilayer networks. For social scale, we found individuals became more
-connected with increasing spatial distance threshold. Increasing land cover
+connected with increasing social distance threshold. Increasing land cover
 resolution lead to a decrease in availability of patchy and rare habitats and, 
@@
 social networks generated using GPS location data require using a social scale,
-specifically a spatial distance threshold, to define social associations. We
+specifically a social distance threshold, to define social associations. We
 found increasing individual graph strength across three habitat types with
-increasing spatial distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
-habitat layers differed in their response to spatial distance threshold, with
+increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
+habitat layers differed in their response to social distance threshold, with
 open and forage with a larger increase in graph strength and greater variation

### 2020-06-20 paper/manuscript.Rmd
no rangifer

@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
 A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (*R.
-tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-(*R. tarandus*) social network graph strength differed between seasons, where 
+social network graph strength differed between seasons, where 
 graph strength was stronger in winter and contrastingly low in summer when
@@
 
-(ref:ml) Visualization of multilayer network representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+(ref:ml) Visualization of multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.

### 2020-06-20 paper/manuscript.Rmd
no lichen

@@
 types into three categories using the R package `raster` [@Hijmans_2019]:
-foraging, open, and forest habitats. Foraging habitat consisted of lichen, open
+foraging, open, and forest habitats. Foraging habitat consisted of foraging, open
 habitat consisted of wetland, rocky barrens, and anthropogenic, while forest
@@
 specifically a social distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat types with
+found increasing individual graph strength across three habitat layers with
 increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
@@
 resolution increased, edge overlap decreased in forage while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Forage <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
+open and forest habitats (Figure \@ref(fig:socres) D). Foraging <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
@@
 habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Lichen and open
-layers had greater individual variation in graph strength, while lichen was the
+increasing spatial resolution and variation between individuals. Foraging and open
+layers had greater individual variation in graph strength, while foraging was the
 only layer to show large responses in graph strength to increasing spatial

### 2020-06-20 paper/manuscript.Rmd

@@
 knit: (function(inputFile, encoding) {
-  rmarkdown::render(inputFile, encoding = encoding,
-  output_format = "all") })
+  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
 bibliography: ../references/knitcite.bib
@@
 
+library(data.table)
+
 source('../scripts/00-variables.R')
 
-library(data.table)
 DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')

### 2020-06-20 paper/manuscript.Rmd
foraging

@@
 elementary-layers (summer and winter) and three land cover elementary-layers
-(forage, forest, and open) combined for a total of six layers. Single layers were
+(foraging, forest, and open) combined for a total of six layers. Single layers were
 composed of individuals linked by social associations, for each season and land cover combination.-->
@@
 social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and forage) for the entire study period. At
+three habitat layers (open, forest and foraging) for the entire study period. At
 the finest scale, individuals within 5 m of one another were considered in the
@@
 `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
-forage) for the entire study period. Social associations of individuals were
+foraging) for the entire study period. Social associations of individuals were
 defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
@@
 edges observed in each combination of habitat layer and spatial scale.
-<!-- JWT: Your graphs present things in the order of Forage, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->
+<!-- JWT: Your graphs present things in the order of Foraging, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->
 
@@
 networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
-across three habitat layers (open, forest and forage) using $N$ randomly
+across three habitat layers (open, forest and foraging) using $N$ randomly
 selected observations. We first generated a maximum of 1000 timesteps and
@@
 Individuals in multilayer networks became more connected as the spatial distance
-<!-- JWT: I really think calling it spatial distance is misleading given we want to represent social scale.
-Even if we stick with calling it spatial distance (I see you call it social distance in the graph), we need to lead in calling it social scale so the reader knows that's what we're referencing.
--->
 threshold increased. Mean graph strength differed across habitat layers with
-similar and higher graph strength in open and forage layers, and lower strength
+similar and higher graph strength in open and foraging layers, and lower strength
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
@@
 
-Increasing land cover resolution resulted in decreased availability of foraging habitat 
-<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
-refers to the thing an animal is eating-->,
+Increasing land cover resolution resulted in decreased availability of foraging habitat,
 a rare and patchy habitat, and corresponding low connectivity of individuals in
@@
 forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
-sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
+sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
 1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
@@
 After 100 m, graph strength continued to increase at a slower rate.
-Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
+Open and foraging layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
 
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
 D) Edge overlap of habitat layers across spatial resolutions.
-Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m.
-Above 600 m, the forage layers are stable.
+Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m.
+Above 600 m, the foraging layers are stable.
 E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
-Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
+Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
 Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
 A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
 B) Edge overlap increased for all habitat layers with increasing number of observations.
-Open and forage layers had higher edge overlap than forest layers.
+Open and foraging layers had higher edge overlap than forest layers.
 C) Multidegree increased for all individuals with increasing number of observations.
@@
 habitat layers differed in their response to social distance threshold, with
-open and forage with a larger increase in graph strength and greater variation
+open and foraging with a larger increase in graph strength and greater variation
 across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
@@
 of increasing spatial resolution depending on the habitat layer. As spatial
-resolution increased, edge overlap decreased in forage while remaining stable in
+resolution increased, edge overlap decreased in foraging while remaining stable in
 open and forest habitats (Figure \@ref(fig:socres) D). Foraging <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
-Twelve layers represent combinations of four time windows and three habitat classes (open, forest and forage).
+Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging).
 Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).

### 2020-06-20 paper/manuscript.Rmd
render md

@@
 output:
-   # bookdown::github_document2: default
-   bookdown::word_document2:
-     reference_docx: template.docx
+   bookdown::github_document2: default
+   # bookdown::word_document2:
+   #   reference_docx: template.docx
 knit: (function(inputFile, encoding) {

### 2020-06-20 scripts/figures/figure-fogo-ml.R
temporal window bottom

@@ -134,27 +134,23 @@ nodesize <- 3
 
 
 # Patchwork ---------------------------------------------------------------
-layout <- 'A
-           A
-           B
-           C
-           C'
+# layout <- 'A
+#            A
+#            B
+#            C
+#            C'
 
 
-(g <- gprop / gnn / gstr + 
-   plot_layout(design = layout) 
-)
+# (g <- gprop / gnn / gstr + 
+#    plot_layout(design = layout) 
+# )
 
 
-g <- gnn
-# gsimm
+g <- gnn + 
+  plot_annotation(caption = 'Temporal Window') & 
+  theme(plot.caption = element_text(hjust = 0.5, 
+                                    size = rel(1.2)))
 
 # Output ------------------------------------------------------------------
 ggsave('graphics/figure-fogo-ml.png',
        g, width = 10, height = 9)
-
-# ggsave('graphics/supp-temp-nid.png',
-#        gnid, width = 5, height = 5)
-
-# For drake
-g

### 2020-06-20 paper/manuscript.Rmd
foraging is 13% of landscape

@@
 resolution increased, edge overlap decreased in foraging while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Foraging <!--Lichen? I think we need to call this lichen and not forage --> is a rare (<!--TODO--> XX % of the landscape) and
+open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (13% of the landscape) and
 patchy habitat on Fogo Island, as is indicated by a decrease in the proportion

### 2020-06-20 paper/manuscript.Rmd
fogo car ml cap

@@
 
-(ref:ml) Visualization of multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each individual is represented by a unique color.
+(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
 Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging).
-Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI).
+Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
 

### 2020-06-20 paper/supplement.Rmd
tidy
freq calc for lc

@@
 )
-
-# source('../scripts/00-variables.R')
 
@@
 ```
+
+```{r}
+data.table(freq(lc))[!is.na(value), count / sum(count)]
+
+```

### 2020-06-20 paper/manuscript.Rmd
last foraging

@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.

### 2020-06-21 scripts/figures/figure-fogo-ml.R
adjust xlab

@@ -117,9 +117,11 @@ nodesize <- 3
   scale_size_area(max_size = 1) + 
   scale_fill_manual(values = lccolors) + 
   theme_blank() +
-  theme(strip.background = element_rect(fill = NA, color = NA),
+  theme(axis.title.x = element_text(size = 14), 
+        strip.background = element_rect(fill = NA, color = NA),
         strip.text = element_text(size = 14),
-        panel.spacing = unit(0, "lines"))
+        panel.spacing = unit(0, "lines")) +
+    xlab('Temporal Window')
 )
 
 # Number of individuals

### 2020-06-21 paper/manuscript.Rmd
make timedefs dates idates

@@
 timedefs <- fread('../data/supp-data/timecut-defs.csv')
+timedefs[, c('mindate', 'maxdate') := .(as.IDate(mindate), as.IDate(maxdate))]
 ```

### 2020-06-21 scripts/figures/figure-fogo-ml.R
rm border

@@ -148,10 +148,7 @@ nodesize <- 3
 # )
 
 
-g <- gnn + 
-  plot_annotation(caption = 'Temporal Window') & 
-  theme(plot.caption = element_text(hjust = 0.5, 
-                                    size = rel(1.2)))
+g <- gnn
 
 # Output ------------------------------------------------------------------
 ggsave('graphics/figure-fogo-ml.png',

### 2020-06-21 paper/manuscript.Rmd
social distance

@@
 We generated multilayer networks across a series of social distance thresholds 
-that relate to behavioural interactions that could occur within those distances
-<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
 for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
@@
 same group, whereas at the coarsest scale, individuals within 500 m of one
-another were considered in the same group. We calculated graph strength and
+another were considered in the same group. Increasing social distance threshold 
+is a proxy for potential behavioural interactions that occur across these distances.
+We calculated graph strength and
 multidegree for each habitat layer and social distance threshold, and edge
-<!-- JWT: can we call spatial distance social distance? -->
 overlap across the entire series of networks to determine proportion of total
@@
 -->
+
+<!-- TODO: somewhere ref:ml -->
 

### 2020-06-21 paper/manuscript.Rmd
order foraging, forest, open

@@
 types into three categories using the R package `raster` [@Hijmans_2019]:
-foraging, open, and forest habitats. Foraging habitat consisted of foraging, open
-habitat consisted of wetland, rocky barrens, and anthropogenic, while forest
-habitat consisted of coniferous forest, conifer scrub, broad leaf forest, and
-mixed-wood forest. Water habitat was excluded from all subsequent analyses.
+foraging, forest, and open habitats. Foraging habitat consisted of foraging,
+forest habitat consisted of coniferous forest, conifer scrub, broad leaf forest,
+and mixed-wood forest, while open habitat consisted of wetland, rocky barrens,
+and anthropogenic. Water habitat was excluded from all subsequent analyses.
 
@@
 social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (open, forest and foraging) for the entire study period. At
+three habitat layers (foraging, forest and open) for the entire study period. At
 the finest scale, individuals within 5 m of one another were considered in the
@@
 multilayer network consisting of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
-foraging) for the entire study period. Social associations of individuals were
+`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, forest and
+open) for the entire study period. Social associations of individuals were
 defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
@@
 networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
-across three habitat layers (open, forest and foraging) using $N$ randomly
+across three habitat layers (foraging, forest and open) using $N$ randomly
 selected observations. We first generated a maximum of 1000 timesteps and
@@
 threshold increased. Mean graph strength differed across habitat layers with
-similar and higher graph strength in open and foraging layers, and lower strength
+similar and higher graph strength in foraging and open layers, and lower strength
 in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
@@
 Increasing land cover resolution resulted in decreased availability of foraging habitat,
-a rare and patchy habitat, and corresponding low connectivity of individuals in
+a rare habitat, and corresponding low connectivity of individuals in
 these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength

### 2020-06-21 paper/manuscript.Rmd
order edge overlap, str, etc

@@
 After 100 m, graph strength continued to increase at a slower rate.
-Open and foraging layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
+Foraging and open layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
 
@@
 For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
-A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
-D) Edge overlap of habitat layers across spatial resolutions.
+A) Edge overlap of habitat layers across spatial resolutions.
 Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m.
 Above 600 m, the foraging layers are stable.
-E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
+B) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
 Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
 Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
+C, D, E) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
 
@@
 Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
-A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
-B) Edge overlap increased for all habitat layers with increasing number of observations.
-Open and foraging layers had higher edge overlap than forest layers.
+A) Edge overlap increased for all habitat layers with increasing number of observations.
+Foraging and open layers had higher edge overlap than forest layers.
+B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
 C) Multidegree increased for all individuals with increasing number of observations.
@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (open, forest and foraging).
+Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open).
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

### 2020-06-21 scripts/figures/figure-temp.R
add vline for years

@@ -31,6 +31,9 @@ DT[, middate := mean(c(mindate, maxdate)), layer]
 
 DT[, meangraphstrength := mean(graphstrength), by = timecut]
 
+yrs <- data.table(date = as.IDate(paste0(DT[, unique(year(mindate))], 
+                                         '-01-01')))
+
 # Edge overlap
 gprop <- ggplot(DT) + 
   geom_segment(aes(x = mindate, xend = maxdate, 
@@ -41,7 +44,8 @@ gprop <- ggplot(DT) +
   base +
   labs(x = NULL, y = 'Edge Overlap', subtitle = 'A)') + 
   ylim(0, 1) +
-  scale_x_date(expand = c(0, 0), breaks = pretty_breaks(13))
+  geom_vline(aes(xintercept = date), data = yrs, alpha = 0.5, size = 0.3) +
+  scale_x_date(expand = c(0, 0), date_breaks = '1 month', date_labels = '%b')
 
 
 # Graph strength
@@ -56,7 +60,8 @@ gstr <- ggplot(DT) +
   guides(color = FALSE) +
   base +
   labs(x = xlab, y = 'Graph Strength', subtitle = 'C)') +
-  scale_x_date(expand = c(0, 0), breaks = pretty_breaks(n = 13))
+  geom_vline(aes(xintercept = date), data = yrs, alpha = 0.5, size = 0.3) +
+  scale_x_date(expand = c(0, 0), date_breaks = '1 month', date_labels = '%b')
 
 
 # Layer similarity
@@ -71,7 +76,7 @@ gstr <- ggplot(DT) +
 #   scale_x_date(expand = c(0, 0), breaks = pretty_breaks(n = 10))
 
 # Network
-netDT[, degree := paste0('N = ', uniqueN(name)), layer]
+netDT[, degree := paste0('N=', uniqueN(name)), layer]
 netDT[, c('capX', 'capY') := .(mean(x), min(y) - 0.2), layer]
 gnn <- ggplot(
   netDT,
@@ -113,7 +118,7 @@ layout <- 'A
 
 
 (g <- gprop / gnn / gstr + 
-   plot_layout(design = layout) 
+   plot_layout(design = layout)
 )
 
 

### 2020-06-21 paper/manuscript.Rmd
adjust soc results

@@
 sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
-the rate of increase after 100 m (<!--TODO: figure XX-->). 
+the rate of increase after 100 m (Figure \@ref(fig:socres)). 
 These results suggest the optimal social scale at
 which groups should be assigned is between ~20 - 100 m based on
-the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
+the rate at which graph strength stabilized. For ungulates, groups are often
 assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier

### 2020-06-21 paper/manuscript.Rmd
fin todo order

@@
 a rare habitat, and corresponding low connectivity of individuals in
-these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
-and edge overlap were relatively consistent across land cover resolutions for
+these habitats at higher resolution (Figure \@ref(fig:lcres)). Edge overlap were relatively consistent across land cover resolutions for
 forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
@@
 \@ref(fig:lcres) D). 
-<!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again.
-I think this should be reordered so it's easier to follow.
--->
 The proportion of relocations in forest and open habitats

### 2020-06-21 paper/manuscript.Rmd
add dates directly

@@
 <!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
-The ordinal multilayer network generated indicated within-year time windows of
-increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
-Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
-windows of higher edge overlap, between approximately October and May, had
-correspondingly higher graph strength compared to time windows of lower edge
-overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
-strength peaked across the time series in periods 9 and 10. These results
-suggest that ordinal multilayer networks can effectively capture discrete time
-windows of aggregation and dissaggregation related to resource availability, and
-highlight the importance of carefully selecting the temporal scale of analysis.
+The ordinal multilayer network indicated within-year time windows where social 
+network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,  
+`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
+and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`) 
+than in time windows 2-5 and 12-15 (between `r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]` 
+and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
+(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between approximately October and June, had correspondingly higher graph strength 
+compared to time windows of lower edge overlap, between approximately June 
+and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
+series between  `r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
+These results suggest that ordinal multilayer networks can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.
 
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and variance in metrics decreased. <!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" -->
-Graph strength across individuals in all three habitat layers was highly
+individuals became more connected and variance in metrics decreased.<!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" --> Graph strength across individuals in all three habitat layers was highly
 variable at low number of observations and stabilized after ~100 observations

### 2020-06-21 scripts/figures/figure-temp.R
add time windows over nets

@@ -93,10 +93,9 @@ gnn <- ggplot(
     geom_nodes() +
     geom_nodes(aes(xend, yend)) +
     theme_blank() + 
-    theme(strip.background = element_blank(),
-          strip.text = element_blank()) + 
+    theme(strip.background = element_blank(), text = element_text(size = 11)) + 
     labs(subtitle = 'B)') +
-  geom_text(aes(capX, capY, label = degree))
+  geom_text(aes(capX, capY, label = degree), size = (5/14) * 9)
 
 # Number of individuals
 (gnid <- ggplot(unique(DT[, .(middate, mindate, maxdate, nid)])) +
@@ -117,7 +116,7 @@ layout <- 'A
            C'
 
 
-(g <- gprop / gnn / gstr + 
+(g <- gprop + gnn + gstr + 
    plot_layout(design = layout)
 )
 

### 2020-06-21 paper/manuscript.Rmd
start cut down biolog

@@
 
+<!-- 
+TODO: cut down to this
+
+Given recent technological advancements in biologging and wildlife tracking technology 
+[@Borger_2020], remotely sensed data provides a unique opportunity to use
+multilayer social network analysis to answer complex questions about animal
+socioecology
+
+track the fine-scale movements of groups over large distances and time scales
+[@Torney_2018]
+-->
+
 Importantly, the key to incorporating movement in multilayer networks across

### 2020-06-21 paper/manuscript.Rmd
start box1

@@
 
-Monolayer network approaches have been increasingly used to link social network
-position with individual fitness, including in primates [@Brent_2017;
-@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
-for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale to generate networks is an
-essential consideration for social network analysis <!-- with direct impacts on
-outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
-social networks generated using GPS location data require using a social scale,
-specifically a social distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
-habitat layers differed in their response to social distance threshold, with
-open and foraging with a larger increase in graph strength and greater variation
-across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
-directly influenced by social scale, in this case the spatial distance
-threshold.
-
 Social structure and habitat selection are intimately related: individuals must
@@
 
+# Box 1
+Monolayer network approaches have been increasingly used to link social network
+position with individual fitness, including in primates [@Brent_2017;
+@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
+[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
+for understanding fitness consequences in the context of social network
+positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011]. Defining the social scale to generate networks is an
+essential consideration for social network analysis <!-- with direct impacts on
+outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
+social networks generated using GPS location data require using a social scale,
+specifically a social distance threshold, to define social associations. We
+found increasing individual graph strength across three habitat layers with
+increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
+habitat layers differed in their response to social distance threshold, with
+open and foraging with a larger increase in graph strength and greater variation
+across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
+directly influenced by social scale, in this case the spatial distance
+threshold.
+
 # Conclusion

### 2020-06-22 paper/manuscript.Rmd
rasters back on top

@@
 these habitats at higher resolution (Figure \@ref(fig:lcres)). Edge overlap were relatively consistent across land cover resolutions for
-forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
+forest and open layers (Figure \@ref(fig:lcres) D). Edge overlap decreased
 sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
@@
 foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
-\@ref(fig:lcres) D). 
+\@ref(fig:lcres) E). 
 The proportion of relocations in forest and open habitats
@@
 For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
-A) Edge overlap of habitat layers across spatial resolutions.
+A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
+D) Edge overlap of habitat layers across spatial resolutions.
 Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m.
 Above 600 m, the foraging layers are stable.
-B) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
+E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
 Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
 Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
-C, D, E) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
 

### 2020-06-22 scripts/figures/figure-lc.R

@@ -66,7 +66,7 @@ gprop <- ggplot(DT) +
   # guides(color = FALSE) +
   scale_color_manual(values = lccolors) +
   base +
-  labs(x = NULL, y = 'Edge Overlap', subtitle = 'A)')
+  labs(x = NULL, y = 'Edge Overlap', subtitle = 'D)')
   
 
 gstr <- ggplot(DT) +
@@ -78,41 +78,39 @@ gstr <- ggplot(DT) +
   guides(color = FALSE) +
   scale_color_manual(values = lccolors) +
   base +
-  labs(x = NULL, y = 'Graph Strength', subtitle = 'B)') + 
+  labs(x = NULL, y = 'Graph Strength', subtitle = 'E)') + 
   theme(panel.spacing = unit(1, "lines"))
 
 
 g30 <- gplot(lc30) + 
   geom_tile(aes(fill = factor(value))) + 
   scale_fill_manual(values = lcvalcolors) +
-  labs(subtitle = 'C) 30 m') +
+  labs(subtitle = 'A) 30 m') +
   themelc + 
   guides(fill = FALSE)
 
 g500 <- gplot(lc500) + 
   geom_tile(aes(fill = factor(value))) + 
   scale_fill_manual(values = lcvalcolors) +
-  labs(subtitle = 'D) 500 m') +
+  labs(subtitle = 'B) 500 m') +
   themelc + 
   guides(fill = FALSE)
 
 g1000 <- gplot(lc1000) + 
   geom_tile(aes(fill = factor(value))) + 
   scale_fill_manual(values = lcvalcolors) +
-  labs(subtitle = 'E) 1000 m') +
+  labs(subtitle = 'C) 1000 m') +
   themelc + 
   guides(fill = FALSE)
 
 
 
 # Patchwork ---------------------------------------------------------------
-layout <- 'AAAAAB
-           CCCCCC
-           DDEEFF'
+layout <- 'AABBCC
+           DDDDDE
+           FFFFFF'
 
-(g <- gprop + guide_area() + gstr +
-   g30 + g500 + g1000 + 
-   # plot_annotation(caption = xlab) +
+(g <- g30 + g500 + g1000 + gprop + guide_area() + gstr +
    plot_layout(design = layout,
                guides = 'collect') + 
    plot_annotation(caption = 'Land Cover Resolution') &

### 2020-06-22 paper/manuscript.Rmd
add box 2 for conclusion questiosn
rm conclusion
outline discussion
note intro

@@
 predictably with social interaction [@Castles_2014;
-@Farine_2015a]. We therefore define social scale as the type of social relationship
+@Farine_2015a]. <!-- careful with this definition of social scale ..
+social scale is the type of and specification/detail/definition of-->We therefore define social scale as the type of social relationship
 observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
@@
 
+<!-- 
+outline
+
+1. TODO intro
+
+2. social scale. our results. possible extensions with HMM. observational of dif behaviours
+
+3. habitat+social, implicit -> explicit, our results.
+
+4. movement, 1 sent biolog
+
+5. seasonality, time windows
+
+6. number obs
+
+7. from conclusions
+
+box1: fitness
+box2: extending qs
+
+-->
+
 Our results highlight the influence of social, spatial and temporal scale on
@@
 
-# Box 1
-Monolayer network approaches have been increasingly used to link social network
-position with individual fitness, including in primates [@Brent_2017;
-@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
-for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale to generate networks is an
-essential consideration for social network analysis <!-- with direct impacts on
-outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
-social networks generated using GPS location data require using a social scale,
-specifically a social distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
-habitat layers differed in their response to social distance threshold, with
-open and foraging with a larger increase in graph strength and greater variation
-across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
-directly influenced by social scale, in this case the spatial distance
-threshold.
-
-# Conclusion
+<!-- this was conclusion -->
 Multilayer networks remain a nascent but powerful tool in animal behavioural
@@
 linking spatial and social layer in multilayer networks.
+<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
+<!-- this was conclusion -->
 
+# Box 1
+Monolayer network approaches have been increasingly used to link social network
+position with individual fitness, including in primates [@Brent_2017;
+@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
+[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
+for understanding fitness consequences in the context of social network
+positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
+@Holekamp_2011]. Defining the social scale to generate networks is an
+essential consideration for social network analysis <!-- with direct impacts on
+outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
+social networks generated using GPS location data require using a social scale,
+specifically a social distance threshold, to define social associations. We
+found increasing individual graph strength across three habitat layers with
+increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
+habitat layers differed in their response to social distance threshold, with
+open and foraging with a larger increase in graph strength and greater variation
+across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
+directly influenced by social scale, in this case the spatial distance
+threshold.
+
+# Box 2 
 Silk et al. (2018) summarized some key multilayer questions in animal behaviour
@@
 environment and make decisions about where to move next?
-
-<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
 

### 2020-06-22 paper/manuscript.Rmd
work p1

@@
 
+<!-- intro -->
+Complex animal social systems are influenced by biological and observation scales.
+By parsing social systems into contexts using multilayer networks,
+we observed differences across social, spatial and temporal scales.
+Social scale
+Spatial and temporal contexts 
+including habitats, discrete patches and fragmented landscapes, as well as across 
+seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
+Sociality exists across scales characterized by different 
+types of behaviours as well as spatial and temporal thresholds defining these. 
+Our results highlight the influence of social, spatial and temporal scales
+on multilayer animal social networks, showing a requirement to consider biologically
+relevant scales when selecting observational scales for a given study. 
+<!-- intro -->
+
 Our results highlight the influence of social, spatial and temporal scale on

### 2020-06-22 paper/manuscript.Rmd
tidy

@@
 # Discussion
-<!-- 1)
-First, to what degree does the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influence our ability to
-interpret complex social systems? 
--->
-
-<!-- 2)
-Second, can variation in the social, spatial,
-and temporal scale improve predictions associated with biological differences in
-seasonal resource availability and social association?
-
-+
-We conclude with
-perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness,
-movement ecology and collective movement, and habitat selection
-and space use.
--->
-
-<!-- TODO: somewhere ref:ml -->
-
 <!-- 
@@
 
+TODO: somewhere ref:ml
+
 7. from conclusions
@@
 box2: extending qs
-
 -->
@@
 networks with an additional set of questions posed through the lens of spatial
-ecology that are relevant to the promise and problem of scale in multilayer
-networks:
+ecology that are relevant to scale in multilayer networks:
 

### 2020-06-22 paper/manuscript.Rmd
social p

@@
 
+<!-- social scale -->
+Defining the social scale to generate networks is an
+essential consideration for social network analysis <!-- with direct impacts on
+outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
+social networks generated using GPS location data require using a social scale,
+specifically a social distance threshold, to define social associations. We
+found increasing individual graph strength across three habitat layers with
+increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
+habitat layers differed in their response to social distance threshold, with
+open and foraging with a larger increase in graph strength and greater variation
+across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
+directly influenced by social scale, in this case the spatial distance
+threshold.
+<!-- social scale -->
+
+<!-- drop 
 Our results highlight the influence of social, spatial and temporal scale on
@@
 resolution lead to a decrease in availability of patchy and rare habitats and,
-<!--QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
-Could you just say 'less common' or even just 'patchy'?-->
+
+QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
+Could you just say 'less common' or even just 'patchy'?
+
 correspondingly, lower connectivity of individuals in these habitats. Temporal
@@
 them up.
-<!--QW: I will pre-empt Eric and say I think this paragraph could maybe not mention the results at all. 
-You could focus on just talking about the importance of scale for behavioural and spatial ecology.
-Why is it important and what are the more broadly applicable ideas that lead us to this paper? 
-Maybe keep this little summary paragraph for now - I think likely we could integrate what I describe 
-above with what you already have-->
+-->
 

### 2020-06-22 paper/manuscript.Rmd
more social p

@@
 <!-- intro -->
+<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology.
+Why is it important and what are the more broadly applicable ideas that lead us to this paper -->
+
 Complex animal social systems are influenced by biological and observation scales.
@@
 <!-- social scale -->
-Defining the social scale to generate networks is an
-essential consideration for social network analysis <!-- with direct impacts on
-outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
-social networks generated using GPS location data require using a social scale,
-specifically a social distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
-habitat layers differed in their response to social distance threshold, with
-open and foraging with a larger increase in graph strength and greater variation
-across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
-directly influenced by social scale, in this case the spatial distance
-threshold.
+Social scale is essential consideration for
+social network analysis [@Castles_2014; @Carter_2015; @Farine_2015a].
+Proximity-based social networks generated using GPS location data use a social
+distance threshold to define social associations. Increasing the social distance threshold
+resulted in an increase in graph strength 
+across all three habitat layers  (Figure
+\@ref(fig:socres)). <!-- This means blah blah for different types of
+interactions.--> However, habitat layers differed in their response to
+increasing social distance threshold, with open and foraging with a larger
+increase in graph strength and greater variation across individuals. 
+<!-- What could this mean biologically? --> These results emphasize that multilayer
+network metrics are directly influenced by social scale. In extension, 
+caribou relocations could be classified into behavioural states using hidden
+Markov models to explore the influence of behavioural states on social scale 
+in a multilayer network [see @Jones_2020]. 
 <!-- social scale -->
 
-<!-- drop 
-Our results highlight the influence of social, spatial and temporal scale on
-multilayer networks. For social scale, we found individuals became more
-connected with increasing social distance threshold. Increasing land cover
-resolution lead to a decrease in availability of patchy and rare habitats and,
-
-QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
-Could you just say 'less common' or even just 'patchy'?
-
-correspondingly, lower connectivity of individuals in these habitats. Temporal
-windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations led to a general stabilization in network
-metrics. As such, scale is inherently tied to the generation  of multilayer
-networks and metrics evaluating them, as well as the individual layers that make
-them up.
--->
-
+<!-- habitat+social -->
 Social structure and habitat selection are intimately related: individuals must
@@
 available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four orders of habitat selection: (1)
+is a scale-dependent process [@Mayor_2009]. 
+Johnson (1980) identified four orders of habitat selection: (1)
 the geographical range of a species, (2) the home range of an individual, the
 (3) habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+habitat patch. <!--Kie et al. [-@Kie_2002] found that, independently, third order of
 selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.-->
 Moving past this hierarchical perspective, Mayor (2007) emphasized the

### 2020-06-22 paper/manuscript.Rmd
hab p

@@
 range of spatial scales, we evaluated the influence of habitat spatial
-resolution on multilayer network metrics. The results indicate varied influence
-of increasing spatial resolution depending on the habitat layer. As spatial
-resolution increased, edge overlap decreased in foraging while remaining stable in
+resolution on multilayer network metrics. <!--The results indicate varied influence
+of increasing spatial resolution depending on the habitat layer.--> As spatial
+resolution increased, edge overlap decreased in foraging habitats while remaining stable in
 open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (13% of the landscape) and
-patchy habitat on Fogo Island, as is indicated by a decrease in the proportion
-of relocations in this habitat type with increasing spatial resolution (Supplementary 1
-Figure 1). Similar to increasing social distance threshold, the influence
+patchy habitat on Fogo Island and the proportion of relocations in foraging habitat
+type decreased as spatial resolution increased (~15% at 30 m - <2% at 1000 m). Similar to increasing social distance threshold, the influence
 of increasing spatial resolution on graph strength was notably different between

### 2020-06-22 paper/manuscript.Rmd
mv drop

@@
 
+<!-- habitat+social -->
+
+<!-- drop 
+Our results highlight the influence of social, spatial and temporal scale on
+multilayer networks. For social scale, we found individuals became more
+connected with increasing social distance threshold. Increasing land cover
+resolution lead to a decrease in availability of patchy and rare habitats and,
+
+QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
+Could you just say 'less common' or even just 'patchy'?
+
+correspondingly, lower connectivity of individuals in these habitats. Temporal
+windows highlighted clear periods of increased sociality among individuals.
+Finally, increasing number of observations led to a general stabilization in network
+metrics. As such, scale is inherently tied to the generation  of multilayer
+networks and metrics evaluating them, as well as the individual layers that make
+them up.
+-->
+
 Social processes, movement decisions, and space use are inextricably linked and

### 2020-06-22 paper/manuscript.Rmd
todo refill box 1

@@
 # Box 1
+<!-- TODO: retrieve from prev versions -->
 Monolayer network approaches have been increasingly used to link social network
@@
 positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011]. Defining the social scale to generate networks is an
-essential consideration for social network analysis <!-- with direct impacts on
-outcomes blah-->[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based
-social networks generated using GPS location data require using a social scale,
-specifically a social distance threshold, to define social associations. We
-found increasing individual graph strength across three habitat layers with
-increasing social distance threshold (Figure \@ref(fig:socres)). <!-- This means blah blah for different types of interactions.--> In addition, 
-habitat layers differed in their response to social distance threshold, with
-open and foraging with a larger increase in graph strength and greater variation
-across individuals. <!-- What could this mean biologically? --> These results emphasize that multilayer network metrics are
-directly influenced by social scale, in this case the spatial distance
-threshold.
+@Holekamp_2011].
 

### 2020-06-22 paper/manuscript.Rmd
adjust %

@@
 increased with increasing spatial resolution, while decreasing in foraging habitat
-(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
+(14.5% at 30 m - <2% at 1000 m).  Overall, these results indicate the importance of
 matching land cover resolution to scale of selection as well as ensuring the
@@
 resolution increased, edge overlap decreased in foraging habitats while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (13% of the landscape) and
+open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (14.5% of the landscape) and
 patchy habitat on Fogo Island and the proportion of relocations in foraging habitat
-type decreased as spatial resolution increased (~15% at 30 m - <2% at 1000 m). Similar to increasing social distance threshold, the influence
+type decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Similar to increasing social distance threshold, the influence
 of increasing spatial resolution on graph strength was notably different between

### 2020-06-22 paper/manuscript.Rmd
fin hab p

@@
 available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. 
-Johnson (1980) identified four orders of habitat selection: (1)
-the geographical range of a species, (2) the home range of an individual, the
-(3) habitat patches within the home range and (4) specific resources within a
-habitat patch. <!--Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.-->
-Moving past this hierarchical perspective, Mayor (2007) emphasized the
-importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours.
+is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four
+orders of habitat selection: (1) the geographical range of a species, (2) the
+home range of an individual, the (3) habitat patches within the home range and
+(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
+that, independently, third order of selection was insufficient for capturing
+landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
+scale larger than their home range size. Moving past this hierarchical
+perspective, Mayor (2007) emphasized the importance of considering a broad
+continuum of scales to reveal scale-dependent selection and avoid the bias of
+predefined scales assumed to be associated with certain behaviours.
 
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-social network graph strength differed between seasons, where 
-graph strength was stronger in winter and contrastingly low in summer when
-resource availability are more homogeneous [@Peignier_2019]. Bison (*Bison
+social network graph strength was higher in winter and contrastingly lower in summer when
+resource availability is more homogeneous [@Peignier_2019]. Bison (*Bison
 bison*) showed stronger habitat selection in larger groups, and avoidance of
@@
 [@Fortin_2009]. These examples, comparing sociality and habitat selection across
-temporal or spatial contexts, are implicitly multilayer analyses.
+spatial and temporal contexts, are implicitly multilayer analyses.
 
@@
 influence of habitat selection on sociality across scales. Animal social systems
-can be parsed by spatial contexts, for example as defined by habitat types as in
-Figure \@ref(fig:lcres). Given that habitat data are available across a wide
-range of spatial scales, we evaluated the influence of habitat spatial
-resolution on multilayer network metrics. <!--The results indicate varied influence
-of increasing spatial resolution depending on the habitat layer.--> As spatial
-resolution increased, edge overlap decreased in foraging habitats while remaining stable in
-open and forest habitats (Figure \@ref(fig:socres) D). Foraging is a rare (14.5% of the landscape) and
-patchy habitat on Fogo Island and the proportion of relocations in foraging habitat
-type decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Similar to increasing social distance threshold, the influence
-of increasing spatial resolution on graph strength was notably different between
-habitat layers. Forest layers showed little change in graph strength with
-increasing spatial resolution and variation between individuals. Foraging and open
-layers had greater individual variation in graph strength, while foraging was the
-only layer to show large responses in graph strength to increasing spatial
-resolution (Figure \@ref(fig:socres) E). As such, multilayer network measures
-related to habitat are explicitly dependent on spatial scale. Edge overlap can
-indicate if some associations between individuals are dependent on the
-habitat-context [@Battiston_2014]. If the spatial resolution of the habitat data
-are insufficient to capture rare habitats, context-specific relationships
-between individuals may not be captured by multilayer networks.
+can be parsed by spatial contexts, for example as defined by habitat type as in
+Figure \@ref(fig:lcres). Since habitat data are available across a range of
+spatial scales, we evaluated the influence of increasing spatial resolution on
+multilayer network metrics. As spatial resolution increased, edge overlap
+remained stable in open and forest layers but decreased in foraging layers
+(Figure \@ref(fig:socres) D). Graph strength did not change in
+forest layers with increasing spatial resolution (Figure \@ref(fig:socres) E).
+Foraging and open layer had greater individual variation in graph strength, and
+foraging layers showed an increase in graph strength with increasing spatial
+resolution (Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the
+landscape) on Fogo Island and the proportion of relocations in foraging habitat
+decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m).
+Despite this, at 30 m resolution the foraging layer had similar edge overlap as
+the open layer indicating its importance in caribou sociality. As such,
+multilayer network measures related to habitat are explicitly dependent on
+spatial scale.  If the spatial resolution of the habitat data are insufficient
+to capture rare habitats, for example, context-specific relationships between
+individuals may not be captured.
 

### 2020-06-22 paper/manuscript.Rmd
fin mov p

@@
 individuals may not be captured.
+<!-- habitat+social -->
 
-<!-- habitat+social -->
+<!-- mov -->
+Social processes, movement decisions, and space use are inextricably linked and
+multilayer networks represent a potential analytical framework for linking these
+processes [@Mourier_2019]. Collective movement can reduce per capita predation
+risk via detection-dilution trade-offs and improve information transfer about
+the quality or location of resources [@Jolles_2019]. Multilayer networks could
+be constructed from layers defined by movement parameters, given the existing
+framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
+edges could represent measures of collective movement based on dynamic
+interaction metrics [@Long_2014]. We generated multilayer networks based on
+habitat-specific layers of social association. Integrating habitat-specific
+movement layers could further illuminate the role of movement as a driver of the
+social and spatial environments an individual experiences [@Webber_2018]. For
+example, social processes may be an emergent property of the landscape because
+animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
+Movement to, from, or within habitat patches or territories can also contribute
+to the formation of the social environment [@Spiegel_2016]. For example, in
+sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
+edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
+movement ecology within a multilayer network framework is a logical next step
+for a burgeoning field. Importantly, the technological advancements in
+biologging and wildlife tracking technology [@Border_2020] have provided a
+unique opportunity to integrate movement and habitat in multilayer networks to
+answer complex questions about animal socioecology.
+<!-- mov -->
 
@@
 -->
-
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Movement as a collective group can reduce per capita
-predation risk via detection-dilution trade-offs and improve information
-transfer about the quality or location of resources to other group members
-[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
-behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
-quantify movement parameters could be integrated. For example, edges could
-represent measures of dyadic or collective movement based on dynamic interaction
-metrics [@Long_2014]. Integrating movement layers with habitat-specific social
-association layers could further illuminate the role of movement as a driver
-of the social and spatial environments an individual experiences [@Webber_2018].
-We generated multilayer networks based on habitat-specific layers of 
-social association. Coordinated movement of dyads, or groups, could vary based on
-habitat, and the approach we outline could be used to explore mechanisms linking
-the social and spatial environments.<!--  <- long sentence with two coulds --> For example, social processes may be an 
-emergent property of the landscape because animals aggregate at resources, such
-as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
-patches or territories can also contribute to the formation of the social
-environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
-males interacted primarily at home range edges, presumably driving territorial
-behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
-network framework is a logical next step for a burgeoning field. In particular,
-when association networks are habitat-specific, we suggest the integration of
-movement and space use in multilayer networks provides novel insights into the
-effects of habitat configuration on the formation of the social environment
-[@He_2019; @Webber_2018].
-
-<!-- 
-TODO: cut down to this
-
-Given recent technological advancements in biologging and wildlife tracking technology 
-[@Borger_2020], remotely sensed data provides a unique opportunity to use
-multilayer social network analysis to answer complex questions about animal
-socioecology
-
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]
--->
-
-Importantly, the key to incorporating movement in multilayer networks across
-scales is the technological advancements available to overcome previous
-limitations [@Hughey_2018]. Biologging and wildlife tracking technology has
-advanced to the point where relocations can be programmed to occur as frequently
-as each second [@B_rger_2016], a practice which has been applied to questions of
-collective movement [e.g @Strandburg_Peshkin_2015]. Meanwhile, remote sensing
-technology, including unmanned aerial vehicles and satellites, can be used to
-track the fine-scale movements of groups over large distances and time scales
-[@Torney_2018]. Using technology to infer behaviour has therefore become
-standard operating procedure for many species in many systems. Our ability to
-collect and process remotely sensed data and infer social processes based on
-animal movement provides an opportunity to use multilayer social network
-analysis to answer complex questions about animal socioecology.
 

### 2020-06-22 paper/manuscript.Rmd
mv up temp, nobs

@@
 
-<!-- drop 
-Our results highlight the influence of social, spatial and temporal scale on
-multilayer networks. For social scale, we found individuals became more
-connected with increasing social distance threshold. Increasing land cover
-resolution lead to a decrease in availability of patchy and rare habitats and,
-
-QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
-Could you just say 'less common' or even just 'patchy'?
-
-correspondingly, lower connectivity of individuals in these habitats. Temporal
-windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations led to a general stabilization in network
-metrics. As such, scale is inherently tied to the generation  of multilayer
-networks and metrics evaluating them, as well as the individual layers that make
-them up.
--->
-
+<!-- temp -->
 The effect of seasonality of resources on sociality can be directly measured by
@@
 position over multiple aggregated time periods.
+<!-- temp -->
 
+<!-- nobs -->
 Finally, it is crucial to consider sufficient data to construct robust networks
@@
 sensitivity analysis.
+<!-- temp -->
+
+<!-- drop 
+Our results highlight the influence of social, spatial and temporal scale on
+multilayer networks. For social scale, we found individuals became more
+connected with increasing social distance threshold. Increasing land cover
+resolution lead to a decrease in availability of patchy and rare habitats and,
+
+QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
+Could you just say 'less common' or even just 'patchy'?
+
+correspondingly, lower connectivity of individuals in these habitats. Temporal
+windows highlighted clear periods of increased sociality among individuals.
+Finally, increasing number of observations led to a general stabilization in network
+metrics. As such, scale is inherently tied to the generation  of multilayer
+networks and metrics evaluating them, as well as the individual layers that make
+them up.
+-->
 

### 2020-06-22 paper/manuscript.Rmd
work temp p

@@
 (time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
-overlap correspond to seasons of low resource availability [Peigner_2019].
+overlap correspond to seasons of heterogeneous resource availability [Peigner_2019].
 Similarly, individual graph strength was also highest in these periods (Figure
 \@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
-in separate layers, multilayer networks provide a detailed and dynamic perspective at
+in separate layers, multilayer networks provide a detailed and dynamic perspective of
 animal social networks.
 
+<!-- workworkworkworkworwkrowrk -->
 Selection of appropriate time windows is essential for capturing sociality in specific
-life stages of interest. Social phenotypes can change over ontogeny in ways that
-can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
+life stages of interest.
+
+<!-- fitness -->
+Social phenotypes can change over ontogeny in ways that
+can affect fitness [@Berger_2015; @Brent_2017]. 
+Further complicating the issue,
 individuals can vary in their rate of development [@Tarka_2018]. This variation
@@
 implications of an individual’s social phenotype over different stages of
-ontogeny difficult. However, considering fine temporal scales has been show to
+ontogeny difficult.
+
+However, considering fine temporal scales has been show to
 provide insight across developmental stages that may otherwise be missed
 [@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. -->
+
 Furthermore, given the non-independent nature of social

### 2020-06-22 paper/manuscript.Rmd
some conclusion

@@
 
+TODO: add t bonnell
+TODO: add autocorrelation
+
 <!-- workworkworkworkworwkrowrk -->
@@
 
-<!-- this was conclusion -->
+<!-- (this was the) conclusion -->
 Multilayer networks remain a nascent but powerful tool in animal behavioural
@@
 and temporal scale within a multilayer framework. We
-show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
+show that (1) multilayer social networks are scale-dependent, and (2) 
+the use of multilayer networks is useful for
 identifying habitat or season-specific social processes. Our analyses of social,
@@
 to an increased attention to the scale at which ecological processes are
-observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
+observed [@Schneider_2001; @Chave_2013]. <!-- rm tech-->In addition, recent technological
 advances have lead to increased data complexity and resolution. Remotely sensed
@@
 allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
-at a higher temporal resolution [@B_rger_2016]. Given this increased
+at a higher temporal resolution [@B_rger_2016]. <!-- rm tech-->Given<!-- the increased.. 
+complex + higher resolution + remotely sensed--> this increased
 availability of complex data, it is important to consider using a broad
@@
 <!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
-<!-- this was conclusion -->
+<!-- (this was the) conclusion -->
 

### 2020-06-23 paper/manuscript.Rmd
temp p

@@
 for a burgeoning field. Importantly, the technological advancements in
-biologging and wildlife tracking technology [@Border_2020] have provided a
+biologging and wildlife tracking technology [@Border_2020] have enabled this
 unique opportunity to integrate movement and habitat in multilayer networks to
@@
 <!-- temp -->
-The effect of seasonality of resources on sociality can be directly measured by
-differences across discrete time windows. Using an ordinal multilayer network
-consisting of 20 discrete time windows throughout the study period, we observed
-periods of increased sociality in caribou on Fogo Island (Figure \@ref(fig:temp)). 
-Edge overlap was higher between approximately October and May
-(time windows 1, 6-11, 15-20) compared to between approximately May and October
-(time windows 2-5, 12-15) (Figure \@ref(fig:temp) A). These periods of high edge
-overlap correspond to seasons of heterogeneous resource availability [Peigner_2019].
-Similarly, individual graph strength was also highest in these periods (Figure
-\@ref(fig:temp) B). By explicitly considering the temporal context of social interactions
-in separate layers, multilayer networks provide a detailed and dynamic perspective of
-animal social networks.
+Changes in network metrics through time can explain the influence of seasonality
+of resources on animal sociality. Using an ordinal multilayer network composed
+of 20 discrete time windows throughout the study period, we observed periods of
+increased sociality in caribou on Fogo Island. Edge overlap was higher during
+fall, winter and spring (approximately October - June) than in summer
+(approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
+individual graph strength was also highest in these periods (Figure
+\@ref(fig:temp) C). Periods of increased sociality correspond to seasons of
+heterogeneous resource availability [Peigner_2019]. By explicitly considering
+the temporal context of social interactions in separate layers, multilayer
+networks provide a detailed and dynamic perspective of animal social networks.
+In addition, this could be extended using time-aggregated networks and a moving-window
+approach to inform the temporal scale including time window size and sampling effort
+[@Farine_2017; @Bonnell_2020].
 
-TODO: add t bonnell
-TODO: add autocorrelation
+Due to the autocorrelated nature of biologging data that we recommend users ensure social association data are non-randomly distributed [@Farine_2017b].
 

### 2020-06-23 paper/manuscript.Rmd
nobs p

@@
 [@Farine_2017; @Bonnell_2020].
-
-Due to the autocorrelated nature of biologging data that we recommend users ensure social association data are non-randomly distributed [@Farine_2017b].
-
-<!-- workworkworkworkworwkrowrk -->
-Selection of appropriate time windows is essential for capturing sociality in specific
-life stages of interest.
-
-<!-- fitness -->
-Social phenotypes can change over ontogeny in ways that
-can affect fitness [@Berger_2015; @Brent_2017]. 
-Further complicating the issue,
-individuals can vary in their rate of development [@Tarka_2018]. This variation
-can make defining the appropriate temporal scale for testing the fitness
-implications of an individual’s social phenotype over different stages of
-ontogeny difficult.
-
-However, considering fine temporal scales has been show to
-provide insight across developmental stages that may otherwise be missed
-[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. -->
-
-Furthermore, given the non-independent nature of social
-interactions and associations, especially over time, it can be challenging to
-test hypotheses about social dynamics with a suitable null control
-[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
-ordinal layers of discrete time windows provide a way to make appropriate null
-models to test questions about the dynamics of an individual’s social network
-position over multiple aggregated time periods.
 <!-- temp -->
@@
 <!-- nobs -->
-Finally, it is crucial to consider sufficient data to construct robust networks
-when selecting time windows and study periods. Time windows should be long
-enough for each layer to have enough data for robust networks [@Farine_2017]. To
+It is crucial to include sufficient data within sampling periods or
+time windows to construct robust networks [@Farine_2017; Proskurnikov_2017]. To
 test the influence of data quantity on multilayer networks, we used a subset of
-observations to generate multilayer networks. All network metrics across all
-three habitat layers appeared to stabilize with increasing number of
+observations to generate multilayer networks. Variance decreased across
+all network metrics in all three habitat layers with increasing number of
 observations. Individual graph strength showed high variability at low number of
@@
 and graph strength remained relatively static, while edge overlap and
-multidegree continued to increase slowly. As more observations were added, more
-and rarer relationships were recorded revealing the value of this form of
-sensitivity analysis.
-<!-- temp -->
+multidegree continued to increase slowly. As more observations were added, rarer 
+relationships were recorded revealing the value of this form of
+sensitivity analysis. Finally, due to the autocorrelated nature of biologging 
+data it is essential to ensure social association data area non-randomly
+distributed [@Farine_2017b].
+<!-- nobs -->
 

### 2020-06-23 paper/manuscript.Rmd
mv to box 1

@@
 
+Selection of appropriate time windows is essential for capturing sociality in specific
+life stages of interest. Social phenotypes can change over ontogeny in ways that
+can affect fitness [@Berger_2015; @Brent_2017]. 
+Further complicating the issue,
+individuals can vary in their rate of development [@Tarka_2018]. This variation
+can make defining the appropriate temporal scale for testing the fitness
+implications of an individual’s social phenotype over different stages of
+ontogeny difficult.  However, considering fine temporal scales has been show to
+provide insight across developmental stages that may otherwise be missed
+[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. -->
+
 # Box 2 

### 2020-06-23 paper/manuscript.Rmd
rm

@@
 
-<!-- drop 
-Our results highlight the influence of social, spatial and temporal scale on
-multilayer networks. For social scale, we found individuals became more
-connected with increasing social distance threshold. Increasing land cover
-resolution lead to a decrease in availability of patchy and rare habitats and,
-
-QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
-Could you just say 'less common' or even just 'patchy'?
-
-correspondingly, lower connectivity of individuals in these habitats. Temporal
-windows highlighted clear periods of increased sociality among individuals.
-Finally, increasing number of observations led to a general stabilization in network
-metrics. As such, scale is inherently tied to the generation  of multilayer
-networks and metrics evaluating them, as well as the individual layers that make
-them up.
--->
-
-<!--
-Multilayer networks can be built with different types of interactions
-
-In contrast to multilayer networks formed by combining layers defined
-by different types of interactions, multilayer networks with GPS data are limited to 
-proximity based measures. An alternative which has been explored is using 
-hidden markov models behavioural states, within which individuals are associating. [@Jones_2020]
-
-Another potential application would be
-to generate social networks during times when animals are engaged in different
-behaviours, including travelling, interacting, or foraging [@Muller_2018;
-@Finn_2019] and construct a multilayer network based on behaviour-specific
-monolayer networks [e.g. @Smith_Aguilar_2019].
-
-netTS
-
-However, animals
-have certain interactions that do not require proximity such as long-distance
-vocalization and olfactory signals [@Carter_2015].
-
-With the advancement of
-biologging technology, we have the ability to record social interactions that do
-not require proximity, particularly long-distance communication networks with
-devices like microphone arrays [@Snijders_2017].
-
--->
-
 <!-- (this was the) conclusion -->

### 2020-06-23 paper/manuscript.Rmd
reflow, tidy
conclusion ps

@@
 <!--
-outline
-
-1. TODO intro
-
-2. social scale. our results. possible extensions with HMM. observational of dif behaviours
-
-3. habitat+social, implicit -> explicit, our results.
-
-4. movement, 1 sent biolog
-
-5. seasonality, time windows
-
-6. number obs
+1. intro
 
@@
 <!-- social scale -->
-Social scale is essential consideration for
-social network analysis [@Castles_2014; @Carter_2015; @Farine_2015a].
-Proximity-based social networks generated using GPS location data use a social
-distance threshold to define social associations. Increasing the social distance threshold
-resulted in an increase in graph strength 
-across all three habitat layers  (Figure
+Social scale is essential consideration for social network analysis
+[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based social networks
+generated using GPS location data use a social distance threshold to define
+social associations. Increasing the social distance threshold resulted in an
+increase in graph strength across all three habitat layers  (Figure
 \@ref(fig:socres)). <!-- This means blah blah for different types of
@@
 increasing social distance threshold, with open and foraging with a larger
-increase in graph strength and greater variation across individuals. 
-<!-- What could this mean biologically? --> These results emphasize that multilayer
-network metrics are directly influenced by social scale. In extension, 
-caribou relocations could be classified into behavioural states using hidden
-Markov models to explore the influence of behavioural states on social scale 
-in a multilayer network [see @Jones_2020]. 
+increase in graph strength and greater variation across individuals. <!-- What
+could this mean biologically? --> These results emphasize that multilayer
+network metrics are directly influenced by social scale. In extension, caribou
+relocations could be classified into behavioural states using hidden Markov
+models to explore the influence of behavioural states on social scale in a
+multilayer network [see @Jones_2020].
 <!-- social scale -->
@@
 high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-social network graph strength was higher in winter and contrastingly lower in summer when
-resource availability is more homogeneous [@Peignier_2019]. Bison (*Bison
-bison*) showed stronger habitat selection in larger groups, and avoidance of
-predation risk was a main factor contributing to their habitat selection
-[@Fortin_2009]. These examples, comparing sociality and habitat selection across
-spatial and temporal contexts, are implicitly multilayer analyses.
+social network graph strength was higher in winter and contrastingly lower in
+summer when resource availability is more homogeneous [@Peignier_2019]. Bison
+(*Bison bison*) showed stronger habitat selection in larger groups, and
+avoidance of predation risk was a main factor contributing to their habitat
+selection [@Fortin_2009]. These examples, comparing sociality and habitat
+selection across spatial and temporal contexts, are implicitly multilayer
+analyses.
 
@@
 remained stable in open and forest layers but decreased in foraging layers
-(Figure \@ref(fig:socres) D). Graph strength did not change in
-forest layers with increasing spatial resolution (Figure \@ref(fig:socres) E).
-Foraging and open layer had greater individual variation in graph strength, and
-foraging layers showed an increase in graph strength with increasing spatial
-resolution (Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the
-landscape) on Fogo Island and the proportion of relocations in foraging habitat
-decreased as spatial resolution increased (14.5% at 30 m - <2% at 1000 m).
-Despite this, at 30 m resolution the foraging layer had similar edge overlap as
-the open layer indicating its importance in caribou sociality. As such,
-multilayer network measures related to habitat are explicitly dependent on
-spatial scale.  If the spatial resolution of the habitat data are insufficient
-to capture rare habitats, for example, context-specific relationships between
-individuals may not be captured.
+(Figure \@ref(fig:socres) D). Graph strength did not change in forest layers
+with increasing spatial resolution (Figure \@ref(fig:socres) E). Foraging and
+open layer had greater individual variation in graph strength, and foraging
+layers showed an increase in graph strength with increasing spatial resolution
+(Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the landscape)
+on Fogo Island and the proportion of relocations in foraging habitat decreased
+as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
+at 30 m resolution the foraging layer had similar edge overlap as the open layer
+indicating its importance in caribou sociality. As such, multilayer network
+measures related to habitat are explicitly dependent on spatial scale.  If the
+spatial resolution of the habitat data are insufficient to capture rare
+habitats, for example, context-specific relationships between individuals may
+not be captured.
 <!-- habitat+social -->
@@
 <!-- temp --> 
-Changes in network metrics through time can explain the influence of seasonality
-of resources on animal sociality. Using an ordinal multilayer network composed
-of 20 discrete time windows throughout the study period, we observed periods of
-increased sociality in caribou on Fogo Island. Edge overlap was higher during
-fall, winter and spring (approximately October - June) than in summer
-(approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
+Changes in network metrics through time can explain the influence
+of seasonality of resources on animal sociality. Using an ordinal multilayer
+network composed of 20 discrete time windows throughout the study period, we
+observed periods of increased sociality in caribou on Fogo Island. Edge overlap
+was higher during fall, winter and spring (approximately October - June) than in
+summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
 individual graph strength was also highest in these periods (Figure
@@
 networks provide a detailed and dynamic perspective of animal social networks.
-In addition, this could be extended using time-aggregated networks and a moving-window
-approach to inform the temporal scale including time window size and sampling effort
-[@Farine_2017; @Bonnell_2020].
+In addition, this could be extended using time-aggregated networks and a
+moving-window approach to inform the temporal scale including time window size
+and sampling effort [@Farine_2017; @Bonnell_2020]. 
 <!-- temp -->
@@
 <!-- nobs -->
-It is crucial to include sufficient data within sampling periods or
-time windows to construct robust networks [@Farine_2017; Proskurnikov_2017]. To
-test the influence of data quantity on multilayer networks, we used a subset of
-observations to generate multilayer networks. Variance decreased across
-all network metrics in all three habitat layers with increasing number of
+It is crucial to include sufficient data within sampling periods or time windows
+to construct robust networks [@Farine_2017; Proskurnikov_2017]. To test the
+influence of data quantity on multilayer networks, we used a subset of
+observations to generate multilayer networks. Variance decreased across all
+network metrics in all three habitat layers with increasing number of
 observations. Individual graph strength showed high variability at low number of
@@
 multidegree continued to increase slowly. As more observations were added, rarer
-relationships were recorded revealing the value of this form of
-sensitivity analysis. Finally, due to the autocorrelated nature of biologging 
-data it is essential to ensure social association data area non-randomly
-distributed [@Farine_2017b].
+relationships were recorded revealing the value of this form of sensitivity
+analysis. Finally, due to the autocorrelated nature of biologging data it is
+essential to ensure social association data area non-randomly distributed
+[@Farine_2017b].
 <!-- nobs -->
@@
 <!-- (this was the) conclusion -->
-Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate the potential novel analyses that vary social, spatial,
-and temporal scale within a multilayer framework. We
-show that (1) multilayer social networks are scale-dependent, and (2) 
-the use of multilayer networks is useful for
-identifying habitat or season-specific social processes. Our analyses of social,
-spatial, and temporal scales in a multilayer network framework highlight the potential
-to identify scales at which different properties of layers within a multilayer
-network show the most variability.
-
-Furthermore, we discuss the potential
-integration of individual phenotypes and fitness, collective movement, and
-habitat selection for future analyses considering spatial ecology using
-multilayer networks.
 
@@
 to an increased attention to the scale at which ecological processes are
-observed [@Schneider_2001; @Chave_2013]. <!-- rm tech-->In addition, recent technological
-advances have lead to increased data complexity and resolution. Remotely sensed
-imagery collected by modern satellites provide, for example, 10 m spatial
-resolution optical imagery at a temporal revisit period of five days at the
-equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
-allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
-at a higher temporal resolution [@B_rger_2016]. <!-- rm tech-->Given<!-- the increased.. 
-complex + higher resolution + remotely sensed--> this increased
-availability of complex data, it is important to consider using a broad
-continuum of scales to fully capture ecological processes, carefully select and
-combine sources of data with different temporal and spatial scales, and
-establish a clear link between scales of observation and meaningful biology.
+observed [@Schneider_2001; @Chave_2013]. Recent technological advances in
+remotely sensed imagery [@Drusch_2012] and animal tracking devices
+[@B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
+resolution data. We highlight ways in which scale should be considered when
+building social networks from both observed and remotely-sensed data. It is
+important to consider a broad continuum of scales to fully capture ecological
+processes, carefully select and combine sources of data with different temporal
+and spatial scales, and establish a clear link between scales of observation and
+meaningful biology.
 
-Multilayer networks are complicated in that they can incorporate data as varied
-as social interactions, landscape features, and seasons, all of which exist at
-different scales and units of measurement. Our analysis of caribou multilayer
-networks which incorporated high resolution GPS telemetry data and spatial land cover
-data is grounded in the context of observed animal social networks, as the
-scales we chose to explore, e.g., number of observations, sociality across space
-and time, are ones that can be observed as has <!-- edit-->traditionally been done in
-ethology. We highlight ways in which scale ought to be considered for both
-observed and remotely-sensed data when building social networks. GPS telemetry 
-data provides a link between large scale landscape properties and
-fine scale social interactions as animal movement occurs across the landscape,
-and when taken into account with multiple individuals<!-- edit--> can indicate association
-patterns. Thus, a layer incorporating relocation data could be a great boon
-linking spatial and social layer in multilayer networks.
-<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
+Multilayer networks remain a nascent but powerful tool in animal behavioural
+ecology. We demonstrate the novel analyses in varying social, spatial,
+and temporal scale within a multilayer framework. We show that (1) multilayer
+social networks are scale-dependent, and (2) the use of multilayer networks is
+useful for identifying habitat or season-specific social processes. Our analysis
+of caribou multilayer networks incorporating high resolution GPS telemetry data
+and spatial land cover data is grounded in the context of observed animal social
+networks, as the scales we chose to explore, e.g., number of observations and
+sociality across space and time, are ones that have also traditionally been done
+in ethology.
+
+<!-- TODO: round it out -->
+
 <!-- (this was the) conclusion -->
@@
 We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
-Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J. Hogg, and L.
-Newediuk for their comments on previous versions of this manuscript as well as
-D. C. Schneider for inspiration and helpful discussions about scale. Funding for
-this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a
-NSERC Discovery Grant to EVW.
+Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J.
+Hogg, and L. Newediuk for their comments on previous versions of this manuscript
+as well as D. C. Schneider for inspiration and helpful discussions about scale.
+Funding for this study was provided by a Vanier Canada Graduate Scholarship to
+QMRW and a NSERC Discovery Grant to EVW.
 

### 2020-06-23 paper/manuscript.Rmd
box 1 work

@@
 # Box 1
+Social phenotype has been increasingly linked to individual fitness, including in
+primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011],
+and birds [@McDonald_2007; @Royle_2012]. Social and temporal scales have emerged
+as important variables for understanding the fitness consequences of social network
+position [@Almeling_2016; @Berger_2015; @Brent_2017; @Holekamp_2011].
+
+Varying social scales can have different fitness repercussions for individuals.
+Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
+but stronger and more stable social associates and grooming partners rather than
+simply more associates [@Ellis_2019]. Furthermore, it is a common trope that
+individuals must be associating to interact, and many studies assume that
+proximity is proxy for interacting [@Farine_2015a]. For instance, baboons need
+to be in proximity to groom each other. Certain animals use interactions that do
+not require proximity such as long-distance vocalization or olfactory signals
+[@Carter_2015]. It is possible to record social interactions that do not require
+proximity, for example using microphone arrays to construct long-distance
+communication networks [@Snijders_2017]. Our results indicate varying social
+patterns in different habitat types, potentially suggesting different types
+of interactions. Higher graph strength in forage and open habitats may 
+be an indication of caribou using visual cues not possible in forest habitats
+(Figure \@ref(fig:socres)).
+
+Changing social phenotypes over ontogeny can affect fitness [@Berger_2015; @Brent_2017].
+Temporal scale is important as individuals progress through development at 
+different rates [@Tarka_2018] and this variation can complicate the selection of 
+time windows. Considering fine temporal scales provide insight across
+developmental stages that may otherwise be missed [@Turner_2017].
+
+Thus, it is
+critical to carefully consider the temporal scale that is meaningful for the
+proposed hypotheses.
+
+Multilayer networks enable researchers to look at similarities and differences
+between explicit stages of ontogeny, seasons or other temporal windows
+
+Multilayer networks provide unique opportunities and challenges, linking these
+various scales, for understanding the social phenotypes and environments of
+individuals and their fitness outcomes.
+
+Multilayer network
+metrics could be used to assess the relationship between an individual’s social
+phenotype and fitness.
+
+It would also be a meaningful reduction of many
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks [@Castles_2014].
+
+Furthermore, multilayer networks provide a framework
+to test hypotheses linking social phenotypes and fitness across temporal scales.
+Because of the non-independent nature of social interactions and associations,
+especially over time, it is hard to test hypotheses about social dynamics with a
+suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
+multilayer networks, making layers of different temporal periods provides a way
+to make appropriate null models to test questions about the dynamics of an
+individual’s social network position over multiple aggregated time periods.
+
+In both mono- and multilayer networks, 
+the effect of
+scale on the relationship between an individual’s social network position and
+fitness need to be considered based on the hypotheses being tested and
+logistical constraints.
+<!-- previous version -->
+
 <!-- TODO: retrieve from prev versions -->

### 2020-06-23 paper/manuscript.Rmd
minor edits discussion

@@
 remained stable in open and forest layers but decreased in foraging layers
-(Figure \@ref(fig:socres) D). Graph strength did not change in forest layers
-with increasing spatial resolution (Figure \@ref(fig:socres) E). Foraging and
+(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
+with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
 open layer had greater individual variation in graph strength, and foraging
 layers showed an increase in graph strength with increasing spatial resolution
-(Figure \@ref(fig:socres) E). Foraging habitat is rare (14.5% of the landscape)
+(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
 on Fogo Island and the proportion of relocations in foraging habitat decreased
 as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
-at 30 m resolution the foraging layer had similar edge overlap as the open layer
+the foraging layer had similar edge overlap as the open layer at 30 m resolution 
 indicating its importance in caribou sociality. As such, multilayer network
@@
 summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
-individual graph strength was also highest in these periods (Figure
-\@ref(fig:temp) C). Periods of increased sociality correspond to seasons of
+individual graph strength was also higher in these periods (Figure
+\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
 heterogeneous resource availability [Peigner_2019]. By explicitly considering
@@
 to construct robust networks [@Farine_2017; Proskurnikov_2017]. To test the
-influence of data quantity on multilayer networks, we used a subset of
-observations to generate multilayer networks. Variance decreased across all
+influence of data quantity on multilayer networks, we generate multilayer networks
+using a subset of observations. Variance decreased across all
 network metrics in all three habitat layers with increasing number of
@@
 
-<!-- (this was the) conclusion -->
-
+<!-- conclusion -->
 Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
@@
 in ethology.
-
 <!-- TODO: round it out -->
 
-<!-- (this was the) conclusion -->
+<!-- conclusion -->
 

### 2020-06-23 paper/manuscript.Rmd
buffer size

@@
 threshold increased. Mean graph strength differed across habitat layers with
-similar and higher graph strength in foraging and open layers, and lower strength
-in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
-sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
-the rate of increase after 100 m (Figure \@ref(fig:socres)). 
-These results suggest the optimal social scale at
-which groups should be assigned is between ~20 - 100 m based on
-the rate at which graph strength stabilized. For ungulates, groups are often
-assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
-et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
-an appropriate social scale for generating social networks in caribou and
-similar species. <!--QW: I'm not sure about this statement. Should it be more about 
-how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
-the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
-any Clutton-Brock red deer paper that uses group size data)-->
+similar and higher graph strength in foraging and open layers, and lower
+strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
+increased sharply between 5 m and 100 m in all three habitat classes followed by
+a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
+results suggest the optimal social scale at which groups should be assigned is
+between ~20 - 100 m based on the rate at which graph strength stabilized. GPS
+data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
+confirm the use of 50 m buffer that has long been used for studies in the field
+[@Lingle_2003; @Clutton_1982]
 

### 2020-06-23 paper/manuscript.Rmd
prop locs

@@
 
-Increasing land cover resolution resulted in decreased availability of foraging habitat,
-a rare habitat, and corresponding low connectivity of individuals in
-these habitats at higher resolution (Figure \@ref(fig:lcres)). Edge overlap were relatively consistent across land cover resolutions for
-forest and open layers (Figure \@ref(fig:lcres) D). Edge overlap decreased
+Increasing land cover resolution resulted in decreased availability of foraging habitat and corresponding low connectivity of individuals at higher land cover resolutions. Edge overlap decreased
 sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
-1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
+1000 m (Figure \@ref(fig:lcres) D). In contrast, edge overlap was relatively consistent across land cover resolutions in
+forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more variable within
 foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
 \@ref(fig:lcres) E). 
-The proportion of relocations in forest and open habitats
+The proportion of relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m - 50.3% at 1000 m) habitats
 increased with increasing spatial resolution, while decreasing in foraging habitat

### 2020-06-23 paper/manuscript.Rmd
fig caps

@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
 After 100 m, graph strength continued to increase at a slower rate.
-Foraging and open layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
+Foraging and open layers showed higher variation in graph strength between individuals while forest layers had less variation and lower mean graph strength.
 
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m.
-Above 600 m, the foraging layers are stable.
+Above 600 m, edge overlap in foraging layers is stable.
 E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
 Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
-Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.
+Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.
 
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open).
+Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 A) Edge overlap increased for all habitat layers with increasing number of observations.
 Foraging and open layers had higher edge overlap than forest layers.
-B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations.
+B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations.
 C) Multidegree increased for all individuals with increasing number of observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines.
+Number of individuals in each time window is reported below each layer.
+C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines.
 Graph strength peaked in time window 9, with noticeable higher strength than the following year.

### 2020-06-23 paper/manuscript.Rmd
reflow

@@
 
-Increasing land cover resolution resulted in decreased availability of foraging habitat and corresponding low connectivity of individuals at higher land cover resolutions. Edge overlap decreased
-sharply between 30 m and 600 m in foraging layers, afterwards remaining stable to
-1000 m (Figure \@ref(fig:lcres) D). In contrast, edge overlap was relatively consistent across land cover resolutions in
-forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more variable within
-foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
-\@ref(fig:lcres) E). 
-The proportion of relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m - 50.3% at 1000 m) habitats
-increased with increasing spatial resolution, while decreasing in foraging habitat
-(14.5% at 30 m - <2% at 1000 m).  Overall, these results indicate the importance of
-matching land cover resolution to scale of selection as well as ensuring the
-land cover product used has a resolution fine enough to detect landscape
-features and habitats relevant to study species, such as important patchy and
-rare habitats.
+Increasing land cover resolution resulted in decreased availability of foraging
+habitat and corresponding low connectivity of individuals at higher land cover
+resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
+layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
+contrast, edge overlap was relatively consistent across land cover resolutions
+in forest and open layers (Figure \@ref(fig:lcres) D).  Graph strength was more
+variable within foraging habitat layers across land cover resolutions than open
+and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
+relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
+- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
+decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  Overall, these
+results indicate the importance of matching land cover resolution to scale of
+selection as well as ensuring the land cover product used has a resolution fine
+enough to detect landscape features and habitats relevant to study species, such
+as important patchy and rare habitats.
 
-<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
-The ordinal multilayer network indicated within-year time windows where social 
+The temporal multilayer network indicated within-year time windows where social 
 network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,  

### 2020-06-23 paper/manuscript.Rmd
no more stable

@@
 results suggest the optimal social scale at which groups should be assigned is
-between ~20 - 100 m based on the rate at which graph strength stabilized. GPS
-data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
+between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
+GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
 confirm the use of 50 m buffer that has long been used for studies in the field

### 2020-06-23 paper/manuscript.Rmd
temp edits

@@
 The temporal multilayer network indicated within-year time windows where social 
-network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,  
+network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
+15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,
 `r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
 and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`)
-than in time windows 2-5 and 12-15 (between `r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]` 
+than in time windows 2-5 and 12-15 (between 
+`r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]`
 and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
-(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between approximately October and June, had correspondingly higher graph strength 
+(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
+approximately October and June, also had higher graph strength 
 compared to time windows of lower edge overlap, between approximately June 
 and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
-series between  `r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
-These results suggest that ordinal multilayer networks can effectively capture discrete time windows of aggregation and dissaggregation related to resource availability, and highlight the importance of carefully selecting the temporal scale of analysis.
+series between  
+`r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
+These results suggest that ordinal multilayer networks can effectively 
+capture discrete time windows of aggregation and dissaggregation related 
+to resource availability, and highlight the importance of carefully 
+selecting the temporal scale of analysis.
 
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and variance in metrics decreased.<!--QW: I think throughout you want to say "variance decreased" instead of "stabilized" --> Graph strength across individuals in all three habitat layers was highly
-variable at low number of observations and stabilized after ~100 observations
+individuals became more connected and variance in metrics decreased.
+Graph strength across individuals in all three habitat layers was highly
+variable at low number of observations and variance decreased after ~100 observations
 (Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
@@
 \@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
-stabilizing after a certain number of observations are included, the results
+decreasing in variance after a certain number of observations are included, the results
 suggest this sensitivity method could be useful for determining the number of

### 2020-06-23 paper/manuscript.Rmd
fin order
tidy, reflow

@@
 ## Caribou socioecology
-Caribou are gregarious
-ungulates with fission-fusion dynamics [@Lesmerises_2018] that display temporal
-and spatial variation in social networks [@Peignier_2019]. In winter, caribou
-dig holes in the snow, termed craters, to access forage [@Bergerud_1974].
-Cratering is presumed to be a costly behaviour and as a result, caribou tend to
-occupy and re-use craters once they are established. <!-- and there is
-considerably less access to forage than when the landscape is snow-free.-->
+Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
+that display temporal and spatial variation in social networks [@Peignier_2019].
+In winter, caribou dig holes in the snow, termed craters, to access forage
+[@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
+result, caribou tend to occupy and re-use craters once they are established.
 Importantly, craters exist on the landscape at multiple scales: the crater scale
@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. 
+We used GPS location data collected from Fogo Island caribou between 
+`r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. 
 Adult female caribou were immobilized and fitted with global positioning
@@
 ### Network layer construction
-<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
-individual nodes and two aspects (season and land cover). Two season
-elementary-layers (summer and winter) and three land cover elementary-layers
-(foraging, forest, and open) combined for a total of six layers. Single layers were
-composed of individuals linked by social associations, for each season and land cover combination.-->
-
 We generated proximity-based social networks using the R package `spatsoc`
@@
 edges observed in each combination of habitat layer and spatial scale.
-<!-- JWT: Your graphs present things in the order of Foraging, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->
 

### 2020-06-23 paper/manuscript.Rmd
intro edits

@@
 [@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
-<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
-Multiscale ecology has been integrated into species distribution modelling
-[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
-among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
+Multiscale ecology has been integrated into, for example, species distribution modelling
+[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
+Meanwhile, in the context of animal behaviour, certain behaviours
 are scale-dependent; for example, acoustic communication in birds varies with
@@
 
-Sociality exists across both temporal and spatial scales (Whitehead 2008). For
+Sociality exists across both temporal and spatial scales [@Whitehead_2008]. For
 example, grooming requires close spatial proximity between conspecifics and
@@
 range overlap is an example of how animals share space over coarser spatial and
-temporal scales (e.g. Piza-Roca et al. 2018). Although the social environment
+temporal scales [e.g. @Piza_Roca_2018]. Although the social environment
 clearly scales spatially and temporally, it remains unclear whether coarser
@@
 predictably with social interaction [@Castles_2014;
-@Farine_2015a]. <!-- careful with this definition of social scale ..
-social scale is the type of and specification/detail/definition of-->We therefore define social scale as the type of social relationship
-observed that can be explicitly defined and measured [@Farine_2015a] and suggest the 
-potential for adaptive variance in social relationships is also scale-dependent. 
+@Farine_2015a]. We therefore define social scale as the explicit definition 
+and measurement of social relationships [@Farine_2015a]. 
+<!-- for QW:
+
+-->
+<!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
 <!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
@@
 
-Animal social network analysis is a well-developed tool used to measure the
+Social network analysis is a well-developed tool used to measure the
 relationships of individuals and organization of social systems [@Krause_2009;
-@Wey_2008; @Croft_2011]. Social network analysis provides insight into the
+@Wey_2008; @Croft_2011]. It provides insight into the
 structure of social communities and social network properties, which can
@@
 network analysis [@Webber_2019], it typically considers a single scale of
-sociality in a given network (monolayer), drastically simplifying the
+sociality in a monolayer network, drastically simplifying the
 complexity of animal social systems [@Finn_2019].
 
-Unlike traditional monolayer social networks, multilayer networks explicitly
+Extending traditional monolayer social networks, multilayer networks explicitly
 consider social systems across scale-dependent contexts
-[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
+[@Pilosof_2017]. Multilayer networks are composed of multiple layers, each
 representing (i) different classes of individuals, e.g. male or female, (ii)
@@
 used to describe multidimensional human social systems, complex transportation
-networks, and neural networks [@Silk_2018]. <!-- just "scale".. edit sent -->The role of scale within multilayer
+networks, and neural networks [@Silk_2018]. Scale within multilayer
 social networks remains unexplored but provides a unique opportunity to develop
@@
 
-<!-- we examined-->Our examinations are motivated by behavioural, landscape, and spatial ecology to
-build a conceptual and analytical framework for scale-dependent multilayer
-networks, and we apply this framework to a case study of caribou (*Rangifer
-tarandus*) in Newfoundland, Canada [@Peignier_2019]. We use this case study to
+We examined scale-dependent multilayer networks motivated by behavioural, landscape, 
+and spatial ecology to and applied this framework to caribou (*Rangifer
+tarandus*) on Fogo Island, Newfoundland, Canada. We use study to
 address two principal questions associated with scale-dependent multilayer
@@
 interpret complex social systems? Second, can variation in the social, spatial,
-and temporal scale improve <!-- replace pred-->predictions associated with biological differences in
-seasonal resource availability and social association? We conclude with
-perspectives for further development and application of scale in multilayer
-networks with respect to phenotypes and individual fitness,
-movement ecology and collective movement, and habitat selection
-and space use.
-<!-- JWT: This part may have to change depending on how we do the disc -->
+and temporal scale improve our understanding of the relationship between 
+social association and seasonal resource availability? We conclude with further 
+development and application of scale in multilayer
+networks with respect to habitat selection and space use, 
+movement ecology and collective movement, and phenotypes and individual fitness.
 

### 2020-06-23 paper/manuscript.Rmd
box 1 edits

@@
 but stronger and more stable social associates and grooming partners rather than
-simply more associates [@Ellis_2019]. Furthermore, it is a common trope that
+simply more associates [@Ellis_2019].  It is a common trope that
 individuals must be associating to interact, and many studies assume that
-proximity is proxy for interacting [@Farine_2015a]. For instance, baboons need
-to be in proximity to groom each other. Certain animals use interactions that do
+proximity is proxy for interacting [@Farine_2015a]. For instance, baboons must be 
+within proximity of each other for grooming yet other animals use interactions that do
 not require proximity such as long-distance vocalization or olfactory signals
 [@Carter_2015]. It is possible to record social interactions that do not require
-proximity, for example using microphone arrays to construct long-distance
+proximity using, for example, microphone arrays to construct long-distance
 communication networks [@Snijders_2017]. Our results indicate varying social
@@
 of interactions. Higher graph strength in forage and open habitats may 
-be an indication of caribou using visual cues not possible in forest habitats
+indicate that caribou use visual or other cues not relevant in forest habitats
 (Figure \@ref(fig:socres)).
 
+Multilayer networks enable researchers to look at similarities and differences
+between discrete temporal windows. 
 Changing social phenotypes over ontogeny can affect fitness [@Berger_2015; @Brent_2017].
-Temporal scale is important as individuals progress through development at 
+Individuals progress through development at 
 different rates [@Tarka_2018] and this variation can complicate the selection of 
-time windows. Considering fine temporal scales provide insight across
-developmental stages that may otherwise be missed [@Turner_2017].
+time windows. Considering fine temporal scales provides insight across
+developmental stages that may otherwise be missed [@Turner_2017]. Thus, it
+is critical to carefully consider the effect of
+scale on the relationship between an individual’s social network position and
+fitness using a temporal scale based on the hypotheses being tested and
+logistical constraints.
 
-Thus, it is
-critical to carefully consider the temporal scale that is meaningful for the
-proposed hypotheses.
-
-Multilayer networks enable researchers to look at similarities and differences
-between explicit stages of ontogeny, seasons or other temporal windows
-
-Multilayer networks provide unique opportunities and challenges, linking these
-various scales, for understanding the social phenotypes and environments of
-individuals and their fitness outcomes.
-
-Multilayer network
-metrics could be used to assess the relationship between an individual’s social
-phenotype and fitness.
-
-It would also be a meaningful reduction of many
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014].
-
-Furthermore, multilayer networks provide a framework
+Multilayer networks provide a framework
 to test hypotheses linking social phenotypes and fitness across temporal scales.
 Because of the non-independent nature of social interactions and associations,
-especially over time, it is hard to test hypotheses about social dynamics with a
+the selection of a suitable null model  to test hypotheses about social dynamics with a
 suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
@@
 
-In both mono- and multilayer networks, 
-the effect of
-scale on the relationship between an individual’s social network position and
-fitness need to be considered based on the hypotheses being tested and
-logistical constraints.
-<!-- previous version -->
-
-<!-- TODO: retrieve from prev versions -->
-Monolayer network approaches have been increasingly used to link social network
-position with individual fitness, including in primates [@Brent_2017;
-@Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011], and birds
-[@McDonald_2007; @Royle_2012]. Social scale has emerged as an important variable
-for understanding fitness consequences in the context of social network
-positions <!-- TODO JWT check-- JWT: these are right, and we could potentially replace the holekamp paper with our recent JAE one if it gets released in time --> [@Almeling_2016; @Berger_2015; @Brent_2017;
-@Holekamp_2011].
-
-Selection of appropriate time windows is essential for capturing sociality in specific
-life stages of interest. Social phenotypes can change over ontogeny in ways that
-can affect fitness [@Berger_2015; @Brent_2017]. 
-Further complicating the issue,
-individuals can vary in their rate of development [@Tarka_2018]. This variation
-can make defining the appropriate temporal scale for testing the fitness
-implications of an individual’s social phenotype over different stages of
-ontogeny difficult.  However, considering fine temporal scales has been show to
-provide insight across developmental stages that may otherwise be missed
-[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. -->
+network metrics that could help simplify statistical analyses and deal with the
+frequent correlations between social network metrics in different types of
+networks [@Castles_2014].
 

### 2020-06-23 paper/manuscript.Rmd
reflow

@@
 # Box 1
-Social phenotype has been increasingly linked to individual fitness, including in
-primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012; @Stanton_2011],
-and birds [@McDonald_2007; @Royle_2012]. Social and temporal scales have emerged
-as important variables for understanding the fitness consequences of social network
-position [@Almeling_2016; @Berger_2015; @Brent_2017; @Holekamp_2011].
+Social phenotype has been increasingly linked to individual fitness, including
+in primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
+@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Social and temporal
+scales have emerged as important variables for understanding the fitness
+consequences of social network position [@Almeling_2016; @Berger_2015;
+@Brent_2017; @Holekamp_2011].
 
@@
 but stronger and more stable social associates and grooming partners rather than
-simply more associates [@Ellis_2019].  It is a common trope that
-individuals must be associating to interact, and many studies assume that
-proximity is proxy for interacting [@Farine_2015a]. For instance, baboons must be 
-within proximity of each other for grooming yet other animals use interactions that do
-not require proximity such as long-distance vocalization or olfactory signals
+simply more associates [@Ellis_2019].  It is a common trope that individuals
+must be associating to interact, and many studies assume that proximity is proxy
+for interacting [@Farine_2015a]. For instance, baboons must be within proximity
+of each other for grooming yet other animals use interactions that do not
+require proximity such as long-distance vocalization or olfactory signals
 [@Carter_2015]. It is possible to record social interactions that do not require
@@
 communication networks [@Snijders_2017]. Our results indicate varying social
-patterns in different habitat types, potentially suggesting different types
-of interactions. Higher graph strength in forage and open habitats may 
-indicate that caribou use visual or other cues not relevant in forest habitats
-(Figure \@ref(fig:socres)).
+patterns in different habitat types, potentially suggesting different types of
+interactions. Higher graph strength in forage and open habitats may indicate
+that caribou use visual or other cues not relevant in forest habitats (Figure
+\@ref(fig:socres)).
 
 Multilayer networks enable researchers to look at similarities and differences
-between discrete temporal windows. 
-Changing social phenotypes over ontogeny can affect fitness [@Berger_2015; @Brent_2017].
-Individuals progress through development at 
-different rates [@Tarka_2018] and this variation can complicate the selection of 
-time windows. Considering fine temporal scales provides insight across
-developmental stages that may otherwise be missed [@Turner_2017]. Thus, it
-is critical to carefully consider the effect of
-scale on the relationship between an individual’s social network position and
-fitness using a temporal scale based on the hypotheses being tested and
-logistical constraints.
-
-Multilayer networks provide a framework
-to test hypotheses linking social phenotypes and fitness across temporal scales.
-Because of the non-independent nature of social interactions and associations,
-the selection of a suitable null model  to test hypotheses about social dynamics with a
-suitable null control [@Farine_2017; @Proskurnikov_2017]. Using the framework of
-multilayer networks, making layers of different temporal periods provides a way
-to make appropriate null models to test questions about the dynamics of an
-individual’s social network position over multiple aggregated time periods.
-
-network metrics that could help simplify statistical analyses and deal with the
-frequent correlations between social network metrics in different types of
-networks [@Castles_2014].
+between discrete temporal windows. Changing social phenotypes over ontogeny can
+affect fitness [@Berger_2015; @Brent_2017]. Individuals progress through
+development at different rates [@Tarka_2018] and this variation can complicate
+the selection of time windows. Considering fine temporal scales provides insight
+across developmental stages that may otherwise be missed [@Turner_2017]. Thus,
+it is critical to carefully consider the effect of scale on the relationship
+between an individual’s social network position and fitness using a temporal
+scale based on the hypotheses being tested and logistical constraints.
 

### 2020-06-23 paper/manuscript.Rmd
box 2 edits

@@
 research. While these questions are important for linking animal behaviour and
-multilayer networks, we summarize our perspectives on the future of multilayer
-networks with an additional set of questions posed through the lens of spatial
-ecology that are relevant to scale in multilayer networks:
+multilayer networks, we pose an additional set of questions on the future of multilayer
+networks through the lens of scale and behavioural, landscape, and spatial ecology:
 

### 2020-06-23 paper/manuscript.Rmd
car ml cap
intro p

@@
 1. intro
-
 TODO: somewhere ref:ml
-
-7. from conclusions
-
-box1: fitness
-box2: extending qs
 -->
@@
 Why is it important and what are the more broadly applicable ideas that lead us to this paper -->
-
-Complex animal social systems are influenced by biological and observation scales.
-By parsing social systems into contexts using multilayer networks,
-we observed differences across social, spatial and temporal scales.
-Social scale
-Spatial and temporal contexts 
-including habitats, discrete patches and fragmented landscapes, as well as across 
-seasonal differences in resource availability, or periods of migration, aggregation and disaggregation [@Kivela_2014; @Porter_2018; @Pilosof_2017]. 
-Sociality exists across scales characterized by different 
-types of behaviours as well as spatial and temporal thresholds defining these. 
-Our results highlight the influence of social, spatial and temporal scales
-on multilayer animal social networks, showing a requirement to consider biologically
-relevant scales when selecting observational scales for a given study. 
+Animal social systems are characterized and influenced by three types of scale. 
+Social scale defines the type and measurement of social relationships and directly
+impacts observed sociality between individuals. Spatial scale, in this study,
+reflects the resolution of the habitat within which social interactions occur. 
+Finally, temporal scale is related to both study design and network robustness
+as well as seasonal differences in resources, patch dynamics or
+landscape connectivity. By parsing social systems into discrete contexts 
+using multilayer networks, we highlight the influence of social, spatial and temporal scales
+on animal social systems, demonstrating the importance of considering biologically
+relevant and robust observational scales. 
 <!-- intro -->
@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open).
+Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open) informed by previous social, spatial and temporal scale analyses.
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

### 2020-06-23 paper/manuscript.Rmd
reflow

@@
 <!-- intro -->
-<!-- QW: could focus on just talking about the importance of scale for behavioural and spatial ecology.
-Why is it important and what are the more broadly applicable ideas that lead us to this paper -->
 Animal social systems are characterized and influenced by three types of scale.
-Social scale defines the type and measurement of social relationships and directly
-impacts observed sociality between individuals. Spatial scale, in this study,
-reflects the resolution of the habitat within which social interactions occur. 
-Finally, temporal scale is related to both study design and network robustness
-as well as seasonal differences in resources, patch dynamics or
-landscape connectivity. By parsing social systems into discrete contexts 
-using multilayer networks, we highlight the influence of social, spatial and temporal scales
-on animal social systems, demonstrating the importance of considering biologically
-relevant and robust observational scales. 
+Social scale defines the type and measurement of social relationships and
+directly impacts observed sociality between individuals. Spatial scale, in this
+study, reflects the resolution of the habitat within which social interactions
+occur. Finally, temporal scale is related to both study design and network
+robustness as well as seasonal differences in resources, patch dynamics or
+landscape connectivity. By parsing social systems into discrete contexts using
+multilayer networks, we highlight the influence of social, spatial and temporal
+scales on animal social systems, demonstrating the importance of considering
+biologically relevant and robust observational scales.
 <!-- intro -->

### 2020-06-23 paper/manuscript.Rmd
conclusion p

@@
 Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate the novel analyses in varying social, spatial,
-and temporal scale within a multilayer framework. We show that (1) multilayer
-social networks are scale-dependent, and (2) the use of multilayer networks is
-useful for identifying habitat or season-specific social processes. Our analysis
-of caribou multilayer networks incorporating high resolution GPS telemetry data
-and spatial land cover data is grounded in the context of observed animal social
-networks, as the scales we chose to explore, e.g., number of observations and
-sociality across space and time, are ones that have also traditionally been done
-in ethology.
+ecology. We demonstrate the novel analyses in varying social, spatial, and
+temporal scale within a multilayer framework. We show that (1) multilayer social
+networks are scale-dependent, and (2) the use of multilayer networks is useful
+for identifying habitat or season-specific social processes. Our multilayer
+network analysis of caribou sociality incorporating high resolution GPS
+telemetry data and spatial land cover data is grounded in the context of
+observed animal behaviour as the scales we chose to explore, e.g., number of
+observations and sociality across space and time, are ones that have also
+traditionally been done in ethology.
 <!-- TODO: round it out -->

### 2020-06-23 paper/manuscript.Rmd
restate multideg

@@
 Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. Extending degree centrality to multiple layers, we calculated multidegree,
-the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
+case SRI, in each layer. We calculated multidegree,
+the sum of degree centrality of individuals across layers, an extension
+of degree centrality to multiple layers [@Berlingerio_2012;
 @Kivela_2014]. Finally, we measured the similarity of layers by calculating edge

### 2020-06-23 paper/manuscript.Rmd
fix ref

@@
 used to describe multidimensional human social systems, complex transportation
-networks, and neural networks [@Silk_2018]. Scale within multilayer
+networks, and neural networks [@Kivela_2014]. Scale within multilayer
 social networks remains unexplored but provides a unique opportunity to develop

### 2020-06-23 paper/manuscript.Rmd
craters

@@
 that display temporal and spatial variation in social networks [@Peignier_2019].
-In winter, caribou dig holes in the snow, termed craters, to access forage
+In winter, caribou dig holes, termed craters, to access forage beneath the snow
 [@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
@@
 and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
-cover and, in winter, variable distribution of craters on the landscape.
+[@Mayor_2009]. Access to forage is therefore heterogeneous in winter 
+depending on snow cover and distribution of craters on the landscape.
 

### 2020-06-23 paper/manuscript.Rmd
com nets

@@
 for interacting [@Farine_2015a]. For instance, baboons must be within proximity
-of each other for grooming yet other animals use interactions that do not
-require proximity such as long-distance vocalization or olfactory signals
+of each other for grooming yet other animals interact using communication
+such as long-distance vocalization or olfactory signals 
 [@Carter_2015]. It is possible to record social interactions that do not require

### 2020-06-23 paper/manuscript.Rmd
work abstract

@@
 # Abstract
+<!-- Scale remains a foundational concept in ecology. Social processes range from 
+fine-scale interactions and co-occurrence to overlapping home ranges. Spatial 
+scale has become a central consideration in the way we understand landscape ecology
+and animal space use. Temporal variation in sociality and
+
+Multilayer networks promise the explicit integration of social, 
+spatial and temporal contexts of animal social networks.
+
+-->
+
 Scale remains a foundational concept in ecology. Spatial scale, for instance,
 has become a central consideration in the way we understand landscape ecology
-and animal space use. Meanwhile, social processes can also scale from fine-scale
-interactions to co-occurrence to overlapping home ranges and vary within and 
-across seasons. Multilayer networks promise the integration of monolayer
-animal social networks with the complexity and importance of animal space use
-and movement in heterogeneous landscapes. Despite the complex interplay between
-social networks and animal space use, there remains an important biological
-and methodological gap in our understanding of an animal’s perception of scale.
-Here we discuss the role of scale in the context of multilayer networks and
-provide a social ungulate case study to illustrate the role of social, spatial,
-and temporal scale on multilayer processes. <!--We also present perspectives on
+and animal space use. Meanwhile, social processes can range from fine-scale
+interactions to co-occurrence and overlapping home ranges. <!-- and vary within and 
+across seasons.--> Multilayer networks promise the explicit integration
+of the social, spatial and temporal contexts multilayer social networks. 
+Given the complex interplay of
+sociality and animal space use in heterogeneous landscapes, there remains 
+an important gap in our understanding of the influence of scale on animal
+social networks. Here we discuss social, spatial and temporal scale in the 
+context of multilayer caribou social networks. <!--We also present perspectives on
 future development and applications of scale in multilayer networks with respect

### 2020-06-23 paper/manuscript.Rmd
minor edits

@@
 are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales, through ecological processes such as
-species-specific trophic interactions, resource availability
+@Allen_2015]. Animals are influenced across scales through ecological processes such as
+trophic interactions, resource availability
 [@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
@@
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
-Meanwhile, in the context of animal behaviour, certain behaviours
+In the context of animal behaviour, certain behaviours
 are scale-dependent; for example, acoustic communication in birds varies with
@@
 
-Sociality exists across both temporal and spatial scales [@Whitehead_2008]. For
+Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
 example, grooming requires close spatial proximity between conspecifics and
-occurs over brief time periods [e.g. @Carter_2015], whereas social association
-represents shared space use by members of the same social group [Figure
+occurs over brief time periods [e.g. @Carter_2015], whereas social associations
+over long time periods 
+represent shared space use by members of the same social group [Figure
 \@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or

### 2020-06-25 paper/manuscript.Rmd
fix lc fig cap
abstract edits

@@
 across seasons.--> Multilayer networks promise the explicit integration
-of the social, spatial and temporal contexts multilayer social networks. 
+of the social, spatial and temporal contexts. 
 Given the complex interplay of
@@
 an important gap in our understanding of the influence of scale on animal
-social networks. Here we discuss social, spatial and temporal scale in the 
+social networks. We discuss ways of considering social, spatial and temporal scale in the 
 context of multilayer caribou social networks. <!--We also present perspectives on
@@
 processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research. Here, we
+animal social networks is an emerging area of research. We
 incorporate perspectives on how the social environment and spatial processes

### 2020-06-25 paper/manuscript.Rmd
intro edits

@@
 [@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
-Multiscale ecology has been integrated into, for example, species distribution modelling
+Multiscale ecology has been integrated into species distribution modelling
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
@@
 represent shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. Further, for social interactions or
-associations to occur individuals must share space, and thus have overlapping
-home ranges [@Vander_Wal_2013]. In the context of the social environment, home
+\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
+interact or associate and thus have overlapping
+home ranges [@Vander_2014]. Home
 range overlap is an example of how animals share space over coarser spatial and
-temporal scales [e.g. @Piza_Roca_2018]. Although the social environment
+temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
 clearly scales spatially and temporally, it remains unclear whether coarser
-scales of sociality, including social association and home range overlap, vary
-predictably with social interaction [@Castles_2014;
-@Farine_2015a]. We therefore define social scale as the explicit definition 
+scales of social interactions, such as social association and home range overlap, vary
+predictably [@Castles_2014; @Farine_2015a]. 
+We therefore define social scale as the explicit definition 
 and measurement of social relationships [@Farine_2015a]. 
@@
 and spatial ecology to and applied this framework to caribou (*Rangifer
-tarandus*) on Fogo Island, Newfoundland, Canada. We use study to
-address two principal questions associated with scale-dependent multilayer
-networks. First, to what degree does the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influence our ability to
-interpret complex social systems? Second, can variation in the social, spatial,
-and temporal scale improve our understanding of the relationship between 
-social association and seasonal resource availability? We conclude with further 
-development and application of scale in multilayer
-networks with respect to habitat selection and space use, 
-movement ecology and collective movement, and phenotypes and individual fitness.
+tarandus*) on Fogo Island, Newfoundland, Canada. First, we test to what degree 
+the social scale of relationships, spatial
+scale of landscapes, and temporal scale of analysis influences our ability to
+interpret complex social systems. Second, we address how variation in the social, spatial,
+and temporal scale improves our understanding of the relationship between 
+social association and seasonal resource availability. We conclude with potential
+future developments and applications of scale in multilayer
+networks.
 

### 2020-06-25 paper/manuscript.Rmd
methods edits

@@
 In winter, caribou dig holes, termed craters, to access forage beneath the snow
-[@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
+[@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
 result, caribou tend to occupy and re-use craters once they are established.
@@
 We used GPS location data collected from Fogo Island caribou between 
-`r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. 
+`r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. 
 Adult female caribou were immobilized and fitted with global positioning
@@
 We generated proximity-based social networks using the R package `spatsoc`
-[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
+[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. We assumed
 individuals were associating if simultaneous GPS fixes were within the spatial
@@
 the social distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. Group assignment based on the chain rule
+other individuals [@Robitaille_2019]. <!-- TODO: check jwt comment--> Group assignment based on the chain rule
 has previously been applied to caribou using a temporal threshold of 5 minutes
@@
 for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
-500 m) represented a range of visual (short distance) to auditory (long
-distance) sensory modalities of caribou. Multilayer networks consisted of the
+500 m) represented a range of visual (short distance) to olfactory and long 
+distance auditory sensory modalities of caribou. Multilayer networks consisted of the
 social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (foraging, forest and open) for the entire study period. At
+three habitat layers (foraging, forest, and open) for the entire study period. At
 the finest scale, individuals within 5 m of one another were considered in the
@@
 is a proxy for potential behavioural interactions that occur across these distances.
-We calculated graph strength and
-multidegree for each habitat layer and social distance threshold, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial distance
-threshold.
+For every social distance threshold, we calculated individual graph strength within each
+habitat layer, and edge overlap and multidegree across habitat layers.
 
@@
 represents the scale at which caribou tend to select and avoid habitat
-(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
-multilayer network consisting of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, forest and
-open) for the entire study period. Social associations of individuals were
-defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
-strength and multidegree for each habitat layer and spatial scale, and edge
-overlap across the entire series of networks to determine proportion of total
-edges observed in each combination of habitat layer and spatial scale.
+(Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social 
+associations between 
+`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers 
+(foraging, forest and
+open) for the entire study period. <!--TODO: check JWT / more clear to
+remove this redundance already mentioned in net lay construction? 
+Social associations of individuals were
+defined by spatiotemporal overlap within 5 minutes and 50 m.--> For each 
+land cover resolution, we calculated individual graph strength within each
+habitat layer, and edge overlap and multidegree across habitat layers.
 
@@
 days taken from the entire study period. Social associations were defined by
-spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
-window, we calculated individual graph strength and multidegree, and across the
-series of networks, we calculated edge overlap to determine proportion of total
-edges observed in each time window.
+spatiotemporal overlap of individuals within 5 minutes and 50 m. For each time
+window, we calculated individual graph strength within each
+time window, and edge overlap and multidegree across time windows.
 
@@
 Studies of social network analysis vary in the number and frequency of
-observations as well as the data collection technique used to generate networks
-[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
+observations as well as the data collection technique used to generate networks,
+ranging from directly observed to remotely sensed
+[@Davis_2018; @Webber_2019]. Remotely sensed GPS data is commonly collected at a
 fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
@@
 networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
-across three habitat layers (foraging, forest and open) using $N$ randomly
+across three habitat layers (foraging, forest, and open) using $N$ randomly
 selected observations. We first generated a maximum of 1000 timesteps and
@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest and open) informed by previous social, spatial and temporal scale analyses.
+Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses.
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

### 2020-06-25 paper/manuscript.Rmd
fix order of figures
oops
fix order

@@
 # Results
-Individuals in multilayer networks became more connected as the spatial distance
+Individuals in multilayer networks became more connected as the social distance
 threshold increased. Mean graph strength differed across habitat layers with
@@
 - 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
-decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  Overall, these
+decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  <!-- TODO: 
+break up -->Overall, these
 results indicate the importance of matching land cover resolution to scale of
-selection as well as ensuring the land cover product used has a resolution fine
+habitat selection as well as ensuring the land cover product used has a resolution fine
 enough to detect landscape features and habitats relevant to study species, such
@@
 to resource availability, and highlight the importance of carefully 
-selecting the temporal scale of analysis.
+selecting the temporal scale of analysis. <!-- TODO see comment-->
 
@@
 individuals became more connected and variance in metrics decreased.
-Graph strength across individuals in all three habitat layers was highly
-variable at low number of observations and variance decreased after ~100 observations
-(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
+Edge overlap increased across all three habitat
 layers with increasing number of observations (Figure \@ref(fig:nobs) B).
@@
 observations, and continued to increase until 1000 observations (Figure
-\@ref(fig:nobs) C). Given the observed trend of these multilayer metrics
+\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
+variable at low number of observations and variance decreased after ~100 observations
+(Figure \@ref(fig:nobs) A). Given the observed trend of these multilayer metrics
 decreasing in variance after a certain number of observations are included, the results
@@
 
+```{r socres, fig.cap='(ref:socres)'}
+knitr::include_graphics('../graphics/figure-soc.png')
+```
+
+\newpage
+
 ```{r lcres, fig.cap='(ref:lcres)'}
@@
 knitr::include_graphics('../graphics/figure-temp.png')
-```
-
-\newpage
-
-```{r socres, fig.cap='(ref:socres)'}
-knitr::include_graphics('../graphics/figure-soc.png')
 ```

### 2020-06-25 paper/manuscript.Rmd
N =

@@
 variable at low number of observations and variance decreased after ~100 observations
-(Figure \@ref(fig:nobs) A). Given the observed trend of these multilayer metrics
-decreasing in variance after a certain number of observations are included, the results
-suggest this sensitivity method could be useful for determining the number of
-observations necessary for sufficiently describing social dynamics across
-contexts.
+(Figure \@ref(fig:nobs) A). <!--TODO double check-->Since the variance in these 
+multilayer metrics decreases after a certain number
+of observations, this sensitivity method could be useful for determining the
+number of observations necessary for sufficiently describing social dynamics
+across contexts.
 
@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (N =               `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (N =               `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (N =              `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
 A) Edge overlap increased for all habitat layers with increasing number of observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (N =              `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 (ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
+Individual caribou (N =              `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
 Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses.

### 2020-06-26 paper/manuscript.Rmd
rm

@@
 sociality. Multilayer networks consisted of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
-days taken from the entire study period. Social associations were defined by
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods 
+from the entire study period. Social associations were defined by
 spatiotemporal overlap of individuals within 5 minutes and 50 m. For each time

### 2020-06-26 paper/manuscript.Rmd
todos

@@
 Multilayer networks represent a novel framework for explicitly testing the
-influence of habitat selection on sociality across scales. Animal social systems
+influence of habitat selection on sociality across scales <!-- TODO: add fig 6-->. Animal social systems
 can be parsed by spatial contexts, for example as defined by habitat type as in
@@
 for a burgeoning field. Importantly, the technological advancements in
-biologging and wildlife tracking technology [@Border_2020] have enabled this
+biologging and wildlife tracking technology <!-- TODO: fix-->[@Border_2020] have enabled this
 unique opportunity to integrate movement and habitat in multilayer networks to
@@
 It is crucial to include sufficient data within sampling periods or time windows
-to construct robust networks [@Farine_2017; Proskurnikov_2017]. To test the
+to construct robust networks <!--TODO check--> [@Farine_2017; Proskurnikov_2017]. To test the
 influence of data quantity on multilayer networks, we generate multilayer networks

### 2020-06-26 paper/manuscript.Rmd
intro p

@@
 <!-- intro -->
-Animal social systems are characterized and influenced by three types of scale.
+Animal social systems are characterized and influenced by scale.
+Three types of scale to consider are social, spatial, and temporal scale.
 Social scale defines the type and measurement of social relationships and
-directly impacts observed sociality between individuals. Spatial scale, in this
-study, reflects the resolution of the habitat within which social interactions
-occur. Finally, temporal scale is related to both study design and network
-robustness as well as seasonal differences in resources, patch dynamics or
-landscape connectivity. By parsing social systems into discrete contexts using
+directly impacts observed social connectivity between individuals. Spatial scale 
+can reflect the resolution of the habitat within which social interactions
+occur. Finally, temporal scale is related to both study design and seasonal 
+differences in social processes. By partitioning social associations into discrete contexts using
 multilayer networks, we highlight the influence of social, spatial and temporal
 scales on animal social systems, demonstrating the importance of considering
-biologically relevant and robust observational scales.
+biologically relevant and robust scales.
 <!-- intro -->

### 2020-06-28 paper/manuscript.Rmd
social p

@@
 Social scale is essential consideration for social network analysis
-[@Castles_2014; @Carter_2015; @Farine_2015a]. Proximity-based social networks
-generated using GPS location data use a social distance threshold to define
-social associations. Increasing the social distance threshold resulted in an
+[@Castles_2014; @Carter_2015; @Farine_2015a]. For example, networks can be
+constructed based on fine-scale social interactions (e.g. grooming or
+aggression), social associations (e.g. group membership or proximity), or
+spatial or home range overlap. Here, we define social associations in a series
+of proximity-based social networks based on a series of social distance
+thresholds. <!-- up to here-->Increasing the social distance threshold resulted in an
 increase in graph strength across all three habitat layers  (Figure

### 2020-06-28 paper/manuscript.Rmd
drop specific dates time results

@@
 network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
-15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,
-`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
-and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`)
-than in time windows 2-5 and 12-15 (between 
-`r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]`
-and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
+15-20 than in time windows 2-5 and 12-15 
 (Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
@@
 and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
-series between  
-`r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
+series between January 2018 and April 2018. 
 These results suggest that ordinal multilayer networks can effectively 

### 2020-06-28 paper/manuscript.Rmd
rm results from box1
add turner 2020

@@
 proximity using, for example, microphone arrays to construct long-distance
-communication networks [@Snijders_2017]. Our results indicate varying social
-patterns in different habitat types, potentially suggesting different types of
-interactions. Higher graph strength in forage and open habitats may indicate
-that caribou use visual or other cues not relevant in forest habitats (Figure
-\@ref(fig:socres)).
+communication networks [@Snijders_2017].
 
@@
 the selection of time windows. Considering fine temporal scales provides insight
-across developmental stages that may otherwise be missed [@Turner_2017]. Thus,
+across developmental stages that may otherwise be missed [@Turner_2020]. Thus,
 it is critical to carefully consider the effect of scale on the relationship

### 2020-06-28 paper/manuscript.Rmd
mv ref ml up

@@
 
+<!-- Figure: Fogo ML Net -->
+(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
+Individual caribou (n =              `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
+Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses.
+Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
+
 # Discussion
@@
 
-(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
-Individual caribou (n =              `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses.
-Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
-
 ```{r ml, fig.cap='(ref:ml)'}

### 2020-06-28 paper/manuscript.Rmd
social p

@@
 <!-- social scale -->
-Social scale is essential consideration for social network analysis
+Social scale is an essential consideration for social network analysis
 [@Castles_2014; @Carter_2015; @Farine_2015a]. For example, networks can be
@@
 aggression), social associations (e.g. group membership or proximity), or
-spatial or home range overlap. Here, we define social associations in a series
-of proximity-based social networks based on a series of social distance
-thresholds. <!-- up to here-->Increasing the social distance threshold resulted in an
-increase in graph strength across all three habitat layers  (Figure
-\@ref(fig:socres)). <!-- This means blah blah for different types of
-interactions.--> However, habitat layers differed in their response to
-increasing social distance threshold, with open and foraging with a larger
-increase in graph strength and greater variation across individuals. <!-- What
-could this mean biologically? --> These results emphasize that multilayer
-network metrics are directly influenced by social scale. In extension, caribou
-relocations could be classified into behavioural states using hidden Markov
-models to explore the influence of behavioural states on social scale in a
-multilayer network [see @Jones_2020].
+spatial or home range overlap. Here, we define social associations using a series
+of social distance thresholds to generate proximity-based social networks. 
+Across network layers, increasing the social distance threshold resulted in
+an increase in graph strength (Figure
+\@ref(fig:socres)). Specifically, the strength of social associations across 
+habitat layers, with open and foraging habitats demonstrating a more pronounced
+increase in graph strength as well as greater variation across individuals. 
+These results emphasize that multilayer network metrics are directly influenced
+by social scale. An extension of this analysis could be to incorporate 
+behavioural states to explore the influence of social scale on patterns of 
+association or interaction across habitat and behavioural layers [e.g. 
+using focal observations or hidden Markov Models see @Muller_2018; @Jones_2020].
 <!-- social scale -->
 
-<!-- habitat+social -->
+<!-- spatial -->
+Habitat selection, the use of
+available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
+is a scale-dependent process [@Mayor_2009].
+
 Social structure and habitat selection are intimately related: individuals must
@@
 resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007]. Habitat selection, the disproportionate use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Johnson (1980) identified four
+and fragmentation [@Banks_2007].  Johnson (1980) identified four
 orders of habitat selection: (1) the geographical range of a species, (2) the

### 2020-06-28 paper/manuscript.Rmd
fix borger

@@
 for a burgeoning field. Importantly, the technological advancements in
-biologging and wildlife tracking technology <!-- TODO: fix-->[@Border_2020] have enabled this
+biologging and wildlife tracking technology <!-- TODO: fix-->[@Borger_2020] have enabled this
 unique opportunity to integrate movement and habitat in multilayer networks to

### 2020-06-28 paper/manuscript.Rmd
spatial p

@@
 and measurement of social relationships [@Farine_2015a]. 
-<!-- for QW:
-
--->
+<!-- for QW:  -->
 <!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
@@
 # Results
+<!-- TODO intro + ml fig -->
+
 Individuals in multilayer networks became more connected as the social distance
@@
 available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009].
-
-Social structure and habitat selection are intimately related: individuals must
-share space to interact and the distribution of resources influences group
-dynamics and home range size [@Webber_2018]. Social structure is influenced by
-resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
-and fragmentation [@Banks_2007].  Johnson (1980) identified four
+is a scale-dependent process [@Mayor_2009]. Social structure and 
+habitat selection are intimately related and individuals must
+share space to interact [@Webber_2018]. Johnson (1980) identified four
 orders of habitat selection: (1) the geographical range of a species, (2) the
@@
 landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
-scale larger than their home range size. Moving past this hierarchical
+scale larger than their home range size. Scales of habitat selection could be 
+relevant for multilayer networks and our integration of habitat within a 
+multilayer context could be an important first step (see Figure \@ref(fig:lcres)). 
+Specifically, if individuals select habitats at the 
+home range scale, it may be relevant to assess social structure at 
+the home range overlap scale in a multilayer framework. By contrast,
+in cases where individuals select habitats at the patch-scale, 
+more fine-scale measures of sociality may be relevant. Moving past this hierarchical
 perspective, Mayor (2007) emphasized the importance of considering a broad
@@
 
+<!-- TODO: missing results -->
+
+<!-- spatial -->
+
+<!-- temp -->
 The emergent relationship between habitat and sociality has been explored by the
-distribution and phenology of resources and use of social information. For
+temporal distribution and phenology of resources and use of social information. 
+<!-- TODO: results -->
+
+For
 example, cougar (*Puma concolor*) home ranges overlapped more in regions with
-high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
-social network graph strength was higher in winter and contrastingly lower in
-summer when resource availability is more homogeneous [@Peignier_2019]. Bison
+high hunting opportunity, a proxy for resource richness [@Elbroch_2015].
+
+Bison
 (*Bison bison*) showed stronger habitat selection in larger groups, and
@@
 
+<!-- TODO repeat qs-->
+
 # Box 2 

### 2020-06-28 paper/manuscript.Rmd
to include

@@
 
-<!-- TODO: missing results -->
+<!-- TODO: missing results
+
+As spatial resolution increased, edge overlap
+remained stable in open and forest layers but decreased in foraging layers
+(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
+with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
+open layer had greater individual variation in graph strength, and foraging
+layers showed an increase in graph strength with increasing spatial resolution
+(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
+on Fogo Island and the proportion of relocations in foraging habitat decreased
+as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
+the foraging layer had similar edge overlap as the open layer at 30 m resolution 
+indicating its importance in caribou sociality. 
+-->
 
@@
 analyses.
-
-Multilayer networks represent a novel framework for explicitly testing the
-influence of habitat selection on sociality across scales <!-- TODO: add fig 6-->. Animal social systems
-can be parsed by spatial contexts, for example as defined by habitat type as in
-Figure \@ref(fig:lcres). Since habitat data are available across a range of
-spatial scales, we evaluated the influence of increasing spatial resolution on
-multilayer network metrics. As spatial resolution increased, edge overlap
-remained stable in open and forest layers but decreased in foraging layers
-(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
-with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
-open layer had greater individual variation in graph strength, and foraging
-layers showed an increase in graph strength with increasing spatial resolution
-(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
-on Fogo Island and the proportion of relocations in foraging habitat decreased
-as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
-the foraging layer had similar edge overlap as the open layer at 30 m resolution 
-indicating its importance in caribou sociality. As such, multilayer network
-measures related to habitat are explicitly dependent on spatial scale.  If the
-spatial resolution of the habitat data are insufficient to capture rare
-habitats, for example, context-specific relationships between individuals may
-not be captured.
-<!-- habitat+social -->
 

### 2020-06-28 paper/manuscript.Rmd
mov mov elsewhere

@@
 
-<!-- mov -->
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019]. Collective movement can reduce per capita predation
-risk via detection-dilution trade-offs and improve information transfer about
-the quality or location of resources [@Jolles_2019]. Multilayer networks could
-be constructed from layers defined by movement parameters, given the existing
-framework using behavioural layers [e.g. @Smith_Aguilar_2019]. For example,
-edges could represent measures of collective movement based on dynamic
-interaction metrics [@Long_2014]. We generated multilayer networks based on
-habitat-specific layers of social association. Integrating habitat-specific
-movement layers could further illuminate the role of movement as a driver of the
-social and spatial environments an individual experiences [@Webber_2018]. For
-example, social processes may be an emergent property of the landscape because
-animals aggregate at resources, such as waterholes [@Chamaill_Jammes_2008].
-Movement to, from, or within habitat patches or territories can also contribute
-to the formation of the social environment [@Spiegel_2016]. For example, in
-sleepy lizards (*Tiliqua rugosa*) males interacted primarily at home range
-edges, presumably driving territorial behaviour [@Spiegel_2018]. Incorporating
-movement ecology within a multilayer network framework is a logical next step
-for a burgeoning field. Importantly, the technological advancements in
-biologging and wildlife tracking technology <!-- TODO: fix-->[@Borger_2020] have enabled this
-unique opportunity to integrate movement and habitat in multilayer networks to
-answer complex questions about animal socioecology.
-<!-- mov -->
-
 <!-- temp --> 
@@
 <!-- conclusion -->
+
+<!-- TODO include mov elsewhere 
+Social processes, movement decisions, and space use are inextricably linked and
+multilayer networks represent a potential analytical framework for linking these
+processes [@Mourier_2019].
+
+Integrating habitat-specific
+movement layers could further illuminate the role of movement as a driver of the
+social and spatial environments an individual experiences [@Webber_2018].
+
+Incorporating
+movement ecology within a multilayer network framework is a logical next step
+for a burgeoning field. Importantly, the technological advancements in
+biologging and wildlife tracking technology [@Borger_2020] have enabled this
+unique opportunity to integrate movement and habitat in multilayer networks to
+answer complex questions about animal socioecology.
+-->
 

### 2020-06-28 paper/manuscript.Rmd
to include
fix mayor

@@
 more fine-scale measures of sociality may be relevant. Moving past this hierarchical
-perspective, Mayor (2007) emphasized the importance of considering a broad
+perspective, Mayor et al. [-@Mayor_2007] emphasized the importance of considering a broad
 continuum of scales to reveal scale-dependent selection and avoid the bias of
@@
 temporal distribution and phenology of resources and use of social information. 
-<!-- TODO: results -->
+<!-- TODO: results
+
+Edge overlap
+was higher during fall, winter and spring (approximately October - June) than in
+summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
+individual graph strength was also higher in these periods (Figure
+\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
+heterogeneous resource availability [Peigner_2019].
+
+By explicitly considering
+the temporal context of social interactions in separate layers, multilayer
+networks provide a detailed and dynamic perspective of animal social networks.
+In addition, this could be extended using time-aggregated networks and a
+moving-window approach to inform the temporal scale including time window size
+and sampling effort [@Farine_2017; @Bonnell_2020]. 
+-->
 
@@
 analyses.
-
-<!-- temp --> 
-Changes in network metrics through time can explain the influence
-of seasonality of resources on animal sociality. Using an ordinal multilayer
-network composed of 20 discrete time windows throughout the study period, we
-observed periods of increased sociality in caribou on Fogo Island. Edge overlap
-was higher during fall, winter and spring (approximately October - June) than in
-summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
-individual graph strength was also higher in these periods (Figure
-\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
-heterogeneous resource availability [Peigner_2019]. By explicitly considering
-the temporal context of social interactions in separate layers, multilayer
-networks provide a detailed and dynamic perspective of animal social networks.
-In addition, this could be extended using time-aggregated networks and a
-moving-window approach to inform the temporal scale including time window size
-and sampling effort [@Farine_2017; @Bonnell_2020]. 
-<!-- temp -->
 

### 2020-06-28 paper/manuscript.Rmd
temp p and include nobs in temp

@@
 <!-- temp -->
-The emergent relationship between habitat and sociality has been explored by the
-temporal distribution and phenology of resources and use of social information. 
 <!-- TODO: results
 
-Edge overlap
-was higher during fall, winter and spring (approximately October - June) than in
-summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
-individual graph strength was also higher in these periods (Figure
-\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
-heterogeneous resource availability [Peigner_2019].
-
-By explicitly considering
-the temporal context of social interactions in separate layers, multilayer
-networks provide a detailed and dynamic perspective of animal social networks.
 In addition, this could be extended using time-aggregated networks and a
@@
 -->
+The emergent relationship between habitat and sociality has been explored by the
+temporal distribution and phenology of resources and use of social information. 
+We found increased edge overlap in fall, winter and spring (approximately October - 
+June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A). 
+Similarly, individual graph strength was also higher in these periods 
+(Figure \@ref(fig:temp) C). These periods of increased sociality correspond 
+to seasons of heterogeneous resource availability [Peigner_2019]. By explicitly 
+considering the temporal context of social interactions in separate layers, multilayer
+networks provide a detailed and dynamic perspective of animal social networks.
+For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
+represented using temporal multilayer networks than aggregated networks 
+[@Pereira_2020]. Evans et al. [-@Evans_2020]
+observed seasonal differences in the social structure of mice 
+(*Mus musculus domesticus*) related to temperature and breeding activity. 
+Finally, it is crucial to include sufficient data within sampling periods or time windows
+to construct robust networks [@Farine_2017; Proskurnikov_2017]. We found
+variance decreased in edge overlap and multidegree across habitat layers as well
+as in graph strength within habitat layers with increasing number of 
+observations (Figure \@ref(fig:nobs)). As more observations were added, rarer
+relationships were recorded revealing the value of this form of sensitivity
+analysis.
 
-For
-example, cougar (*Puma concolor*) home ranges overlapped more in regions with
-high hunting opportunity, a proxy for resource richness [@Elbroch_2015].
-
-Bison
-(*Bison bison*) showed stronger habitat selection in larger groups, and
-avoidance of predation risk was a main factor contributing to their habitat
-selection [@Fortin_2009]. These examples, comparing sociality and habitat
-selection across spatial and temporal contexts, are implicitly multilayer
-analyses.
-
-<!-- nobs -->
-It is crucial to include sufficient data within sampling periods or time windows
-to construct robust networks <!--TODO check--> [@Farine_2017; Proskurnikov_2017]. To test the
-influence of data quantity on multilayer networks, we generate multilayer networks
-using a subset of observations. Variance decreased across all
-network metrics in all three habitat layers with increasing number of
-observations. Individual graph strength showed high variability at low number of
-observations, while edge overlap and multidegree increased sharply. After
-approximately 200 observations, the rate of change for all metrics decreased and
-and graph strength remained relatively static, while edge overlap and
-multidegree continued to increase slowly. As more observations were added, rarer
-relationships were recorded revealing the value of this form of sensitivity
-analysis. Finally, due to the autocorrelated nature of biologging data it is
-essential to ensure social association data area non-randomly distributed
-[@Farine_2017b].
-<!-- nobs -->
+<!-- Finally, due to the autocorrelated nature of biologging data it is -->
+<!-- essential to ensure social association data area non-randomly distributed -->
+<!-- [@Farine_2017b]. -->
 

### 2020-06-28 paper/manuscript.Rmd
rm box 2

@@
 
-# Box 2 
-Silk et al. (2018) summarized some key multilayer questions in animal behaviour
-research. While these questions are important for linking animal behaviour and
-multilayer networks, we pose an additional set of questions on the future of multilayer
-networks through the lens of scale and behavioural, landscape, and spatial ecology:
-
-1. How do social phenotypes vary across social, spatial, and temporal scales and
-at which scale might these influence fitness? Are some scales better predictors
-for different fitness metrics?
-
-2. Why do individuals associate more strongly with certain conspecifics in some
-habitats? What, if any, is the role of movement in the context of habitat
-networks?
-
-3. How, and why, does the spatial scale of perception influence, e.g. auditory,
-visual, or chemotaxis, influence the social environment? What is the role of
-memory, and by extension social and spatial cognition, as animals navigate their
-environment and make decisions about where to move next?
-
 # Acknowledgements

### 2020-06-28 paper/manuscript.Rmd
conclusion p

@@
 
-In addition, this could be extended using time-aggregated networks and a
-moving-window approach to inform the temporal scale including time window size
-and sampling effort [@Farine_2017; @Bonnell_2020]. 
 -->
@@
 temporal distribution and phenology of resources and use of social information. 
-We found increased edge overlap in fall, winter and spring (approximately October - 
-June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A). 
-Similarly, individual graph strength was also higher in these periods 
-(Figure \@ref(fig:temp) C). These periods of increased sociality correspond 
-to seasons of heterogeneous resource availability [Peigner_2019]. By explicitly 
+We found increased edge overlap and graph strength in fall, winter and spring (approximately October - 
+June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A, C). 
+These periods of increased sociality correspond 
+to seasons of heterogeneous resource availability [Peigner_2019]. This analysis 
+could be extended using time-aggregated networks and a
+moving-window approach to time window size
+and sampling effort [@Farine_2017; @Bonnell_2020]. By explicitly 
 considering the temporal context of social interactions in separate layers, multilayer
@@
 For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
-represented using temporal multilayer networks than aggregated networks 
+represented by temporal multilayer networks than aggregated networks 
 [@Pereira_2020]. Evans et al. [-@Evans_2020]
@@
 Finally, it is crucial to include sufficient data within sampling periods or time windows
-to construct robust networks [@Farine_2017; Proskurnikov_2017]. We found
+to construct robust networks [@Farine_2017; Proskurnikov_2017]. With increasing
+number of observations, we found
 variance decreased in edge overlap and multidegree across habitat layers as well
-as in graph strength within habitat layers with increasing number of 
-observations (Figure \@ref(fig:nobs)). As more observations were added, rarer
-relationships were recorded revealing the value of this form of sensitivity
+as in graph strength within habitat layers (Figure \@ref(fig:nobs)). 
+As more observations were added, rarer
+relationships were recorded demonstrating the value of this form of sensitivity
 analysis.

### 2020-06-28 paper/manuscript.Rmd
more conclusion p

@@
 remotely sensed imagery [@Drusch_2012] and animal tracking devices
-[@B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
+[@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
 resolution data. We highlight ways in which scale should be considered when
-building social networks from both observed and remotely-sensed data. It is
-important to consider a broad continuum of scales to fully capture ecological
-processes, carefully select and combine sources of data with different temporal
-and spatial scales, and establish a clear link between scales of observation and
-meaningful biology.
-
-Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology. We demonstrate the novel analyses in varying social, spatial, and
-temporal scale within a multilayer framework. We show that (1) multilayer social
-networks are scale-dependent, and (2) the use of multilayer networks is useful
-for identifying habitat or season-specific social processes. Our multilayer
+building social networks from both observed and remotely-sensed data. Our multilayer
 network analysis of caribou sociality incorporating high resolution GPS
@@
 traditionally been done in ethology.
+
+Multilayer networks remain a nascent but powerful tool in animal behavioural
+ecology and we introduce concepts of scale within the existing multilayer 
+framework. Silk et al. (2018) summarized some 
+key multilayer questions in animal behaviour
+research  and based on our case study of scale in the context of multilayer 
+networks, we conclude by posing an additional set of questions on the future 
+of multilayer networks through the lens of scale and behavioural, landscape, 
+and spatial ecology:
+
+1. How do social phenotypes vary across social, spatial, and temporal scales and
+at which scale might these influence fitness? Are some scales better predictors
+for different fitness metrics?
+
+2. Why do individuals associate more strongly with certain conspecifics in some
+habitats? What, if any, is the role of movement in the context of habitat
+networks?
+
+3. How, and why, does the spatial scale of perception influence, e.g. auditory,
+visual, or chemotaxis, influence the social environment? What is the role of
+memory, and by extension social and spatial cognition, as animals navigate their
+environment and make decisions about where to move next?
+
+We show that (1) multilayer social networks are scale-dependent, and (2) the use
+of multilayer networks is useful for identifying spatially or temporally
+specific social associations. It is important to consider a broad continuum of
+scales to fully capture ecological processes, carefully select and combine data
+with different temporal and spatial scales, and establish a clear link between
+biologically relevant scales of observation.
+
 <!-- TODO: round it out -->

### 2020-06-28 paper/manuscript.Rmd
ish fin conclusion p

@@
 remotely sensed imagery [@Drusch_2012] and animal tracking devices
-[@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
-resolution data. We highlight ways in which scale should be considered when
-building social networks from both observed and remotely-sensed data. Our multilayer
-network analysis of caribou sociality incorporating high resolution GPS
-telemetry data and spatial land cover data is grounded in the context of
-observed animal behaviour as the scales we chose to explore, e.g., number of
-observations and sociality across space and time, are ones that have also
-traditionally been done in ethology.
+[@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of
+complex, high resolution data. We highlight ways in which scale should be
+considered when building social networks from both observed and remotely-sensed
+data. Our multilayer network analysis of caribou sociality incorporating high
+resolution GPS telemetry data and spatial land cover data is grounded in the
+context of observed animal behaviour as the scales we chose to explore, e.g.,
+number of observations and sociality across space and time, are ones that have
+also traditionally been done in ethology.
 
@@
 ecology and we introduce concepts of scale within the existing multilayer
-framework. Silk et al. (2018) summarized some 
-key multilayer questions in animal behaviour
-research  and based on our case study of scale in the context of multilayer 
-networks, we conclude by posing an additional set of questions on the future 
-of multilayer networks through the lens of scale and behavioural, landscape, 
-and spatial ecology:
+framework. Silk et al. [-@Silk_2018] summarized some key multilayer questions in animal
+behaviour research  and based on our case study of scale in the context of
+multilayer networks, we conclude by posing an additional set of questions on the
+future of multilayer networks through the lens of scale and behavioural,
+landscape, and spatial ecology:
 
@@
 
-We show that (1) multilayer social networks are scale-dependent, and (2) the use
-of multilayer networks is useful for identifying spatially or temporally
-specific social associations. It is important to consider a broad continuum of
-scales to fully capture ecological processes, carefully select and combine data
-with different temporal and spatial scales, and establish a clear link between
-biologically relevant scales of observation.
-
-<!-- TODO: round it out -->
-
+We show that multilayer social networks are (1) scale-dependent, and (2) useful
+for identifying spatially or temporally specific social associations. When
+employing multilayer networks, it is important to consider a broad continuum of
+social, spatial and temporal scales to fully capture ecological processes and
+establish a clear link between biologically relevant scales of observation.
 <!-- conclusion -->

### 2020-06-28 paper/manuscript.Rmd
reflow, tidy

@@
 and animal space use. Meanwhile, social processes can range from fine-scale
-interactions to co-occurrence and overlapping home ranges. <!-- and vary within and 
-across seasons.--> Multilayer networks promise the explicit integration
-of the social, spatial and temporal contexts. 
-Given the complex interplay of
-sociality and animal space use in heterogeneous landscapes, there remains 
-an important gap in our understanding of the influence of scale on animal
-social networks. We discuss ways of considering social, spatial and temporal scale in the 
-context of multilayer caribou social networks. <!--We also present perspectives on
-future development and applications of scale in multilayer networks with respect
-to: phenotypes and individual fitness, movement ecology and collective movement,
-and habitat selection and space use.--> Effective integration of social and spatial
-processes, including biologically meaningful scales, within the context of
-animal social networks is an emerging area of research. We
-incorporate perspectives on how the social environment and spatial processes
-are linked across scales in a multilayer context.
+interactions to co-occurrence and overlapping home ranges. <!-- and vary within
+and across seasons.--> Multilayer networks promise the explicit integration of
+the social, spatial and temporal contexts. Given the complex interplay of
+sociality and animal space use in heterogeneous landscapes, there remains an
+important gap in our understanding of the influence of scale on animal social
+networks. We discuss ways of considering social, spatial and temporal scale in
+the context of multilayer caribou social networks. <!--We also present
+perspectives on future development and applications of scale in multilayer
+networks with respect to: phenotypes and individual fitness, movement ecology
+and collective movement, and habitat selection and space use.--> Effective
+integration of social and spatial processes, including biologically meaningful
+scales, within the context of animal social networks is an emerging area of
+research. We incorporate perspectives on how the social environment and spatial
+processes are linked across scales in a multilayer context.
 
@@
 and measurement of social relationships [@Farine_2015a].
-<!-- for QW:  -->
-<!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
-<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
-under the expectation that there is some scale at which variance is greatest, and presumably
-it is this scale that has the greatest effect on fitness or other traits-->
 
@@
 relationships of individuals and organization of social systems [@Krause_2009;
-@Wey_2008; @Croft_2011]. It provides insight into the
-structure of social communities and social network properties, which can
-influence population dynamics and evolutionary processes [@Pinter_Wollman_2013;
-@Kurvers_2014]. Despite the widespread use and innovation of traditional social
+@Wey_2008; @Croft_2011]. It provides insight into the structure of social
+communities and social network properties, which can influence population
+dynamics and evolutionary processes [@Pinter_Wollman_2013; @Kurvers_2014]. 
+Despite the widespread use and innovation of traditional social
 network analysis [@Webber_2019], it typically considers a single scale of
-sociality in a monolayer network, drastically simplifying the
-complexity of animal social systems [@Finn_2019].
+sociality in a monolayer network, drastically simplifying the complexity of
+animal social systems [@Finn_2019].
 
 Extending traditional monolayer social networks, multilayer networks explicitly
-consider social systems across scale-dependent contexts
-[@Pilosof_2017]. Multilayer networks are composed of multiple layers, each
-representing (i) different classes of individuals, e.g. male or female, (ii)
-types of behaviours, e.g. grooming, travelling, or foraging, (iii) spatial
-areas, e.g. local or regional, (iv) or temporal windows, e.g. daily or seasonal
-[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to
-studies of animal behaviour [@Silk_2018; @Finn_2019], although they have been
-used to describe multidimensional human social systems, complex transportation
-networks, and neural networks [@Kivela_2014]. Scale within multilayer
-social networks remains unexplored but provides a unique opportunity to develop
-novel understanding of variation in the social, spatial, or temporal scales associated
-with social systems.
+consider social systems across scale-dependent contexts [@Pilosof_2017].
+Multilayer networks are composed of multiple layers, each representing (i)
+different classes of individuals, e.g. male or female, (ii) types of behaviours,
+e.g. grooming, travelling, or foraging, (iii) spatial areas, e.g. local or
+regional, (iv) or temporal windows, e.g. daily or seasonal 
+[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
+behaviour [@Silk_2018; @Finn_2019], although they have been used to describe
+multidimensional human social systems, complex transportation networks, and
+neural networks [@Kivela_2014]. Scale within multilayer social networks remains
+unexplored but provides a unique opportunity to develop novel understanding of
+variation in the social, spatial, or temporal scales associated with social
+systems.
 
-We examined scale-dependent multilayer networks motivated by behavioural, landscape, 
-and spatial ecology to and applied this framework to caribou (*Rangifer
-tarandus*) on Fogo Island, Newfoundland, Canada. First, we test to what degree 
-the social scale of relationships, spatial
-scale of landscapes, and temporal scale of analysis influences our ability to
-interpret complex social systems. Second, we address how variation in the social, spatial,
-and temporal scale improves our understanding of the relationship between 
-social association and seasonal resource availability. We conclude with potential
-future developments and applications of scale in multilayer
-networks.
+We examined scale-dependent multilayer networks motivated by behavioural,
+landscape, and spatial ecology to and applied this framework to caribou
+(*Rangifer tarandus*) on Fogo Island, Newfoundland, Canada. First, we test to
+what degree the social scale of relationships, spatial scale of landscapes, and
+temporal scale of analysis influences our ability to interpret complex social
+systems. Second, we address how variation in the social, spatial, and temporal
+scale improves our understanding of the relationship between social association
+and seasonal resource availability. We conclude with potential future
+developments and applications of scale in multilayer networks.
 
@@
 and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. Access to forage is therefore heterogeneous in winter 
-depending on snow cover and distribution of craters on the landscape.
+[@Mayor_2009]. Access to forage is therefore heterogeneous in winter depending
+on snow cover and distribution of craters on the landscape.
 
@@
 500 m) represented a range of visual (short distance) to olfactory and long
-distance auditory sensory modalities of caribou. Multilayer networks consisted of the
-social association between `r DT[, uniqueN(get(idcol))]` individuals across
-three habitat layers (foraging, forest, and open) for the entire study period. At
-the finest scale, individuals within 5 m of one another were considered in the
-same group, whereas at the coarsest scale, individuals within 500 m of one
-another were considered in the same group. Increasing social distance threshold 
-is a proxy for potential behavioural interactions that occur across these distances.
-For every social distance threshold, we calculated individual graph strength within each
-habitat layer, and edge overlap and multidegree across habitat layers.
+distance auditory sensory modalities of caribou. Multilayer networks consisted
+of the social association between `r DT[, uniqueN(get(idcol))]` individuals
+across three habitat layers (foraging, forest, and open) for the entire study
+period. At the finest scale, individuals within 5 m of one another were
+considered in the same group, whereas at the coarsest scale, individuals within
+500 m of one another were considered in the same group. Increasing social
+distance threshold is a proxy for potential behavioural interactions that occur
+across these distances. For every social distance threshold, we calculated
+individual graph strength within each habitat layer, and edge overlap and
+multidegree across habitat layers.
 
@@
 (Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social
-associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers 
-(foraging, forest and
-open) for the entire study period. <!--TODO: check JWT / more clear to
-remove this redundance already mentioned in net lay construction? 
-Social associations of individuals were
-defined by spatiotemporal overlap within 5 minutes and 50 m.--> For each 
+associations between `r DT[, uniqueN(get(idcol))]` individuals across three
+habitat layers (foraging, forest and open) for the entire study period. For each
 land cover resolution, we calculated individual graph strength within each
@@
 sociality. Multilayer networks consisted of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods 
-from the entire study period. Social associations were defined by
-spatiotemporal overlap of individuals within 5 minutes and 50 m. For each time
-window, we calculated individual graph strength within each
-time window, and edge overlap and multidegree across time windows.
+`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods from the
+entire study period. Social associations were defined by spatiotemporal overlap
+of individuals within 5 minutes and 50 m. For each time window, we calculated
+individual graph strength within each time window, and edge overlap and
+multidegree across time windows.
 
@@
 observations as well as the data collection technique used to generate networks,
-ranging from directly observed to remotely sensed
-[@Davis_2018; @Webber_2019]. Remotely sensed GPS data is commonly collected at a
-fixed rate, e.g. every $x$ minutes or hours, continuously throughout the study
-period. Fix rate is a reflection of number of observations an individual would
-have been observed and recorded in traditional ethological studies. To
-investigate the influence of number of observations, we generated multilayer
-networks of social association between `r DT[, uniqueN(get(idcol))]` individuals
-across three habitat layers (foraging, forest, and open) using $N$ randomly
-selected observations. We first generated a maximum of 1000 timesteps and
-iteratively used $N$ of these ($N$ = 10 - 1000 observations by steps of 10), to
-ensure previously included timesteps, and resulting associations, were
-accumulated with subsequent observations to mimic collection of observational
-data. Within each multilayer network with $N$ observations, we calculated
-individual graph strength and multidegree. We calculated edge overlap across the
-entire series of networks to determine proportion of total edges as number of
-observations increased.
+ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
+Remotely sensed GPS data is commonly collected at a fixed rate, e.g. every $x$
+minutes or hours, continuously throughout the study period. Fix rate is a
+reflection of number of observations an individual would have been observed and
+recorded in traditional ethological studies. To investigate the influence of
+number of observations, we generated multilayer networks of social association
+between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
+(foraging, forest, and open) using $N$ randomly selected observations. We first
+generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ =
+10 - 1000 observations by steps of 10), to ensure previously included timesteps,
+and resulting associations, were accumulated with subsequent observations to
+mimic collection of observational data. Within each multilayer network with $N$
+observations, we calculated individual graph strength and multidegree. We
+calculated edge overlap across the entire series of networks to determine
+proportion of total edges as number of observations increased.
 
@@
 results suggest the optimal social scale at which groups should be assigned is
-between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
-GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
-confirm the use of 50 m buffer that has long been used for studies in the field
-[@Lingle_2003; @Clutton_1982]
+between ~20 - 100 m based on the rate at which variance in graph strength
+decreased. GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] 
+us to confirm the use of 50 m buffer that has long been used
+for studies in the field [@Lingle_2003; @Clutton_1982].
 
@@
 <!-- intro -->
-Animal social systems are characterized and influenced by scale.
-Three types of scale to consider are social, spatial, and temporal scale.
-Social scale defines the type and measurement of social relationships and
-directly impacts observed social connectivity between individuals. Spatial scale 
-can reflect the resolution of the habitat within which social interactions
-occur. Finally, temporal scale is related to both study design and seasonal 
-differences in social processes. By partitioning social associations into discrete contexts using
-multilayer networks, we highlight the influence of social, spatial and temporal
-scales on animal social systems, demonstrating the importance of considering
-biologically relevant and robust scales.
+Animal social systems are characterized and influenced by scale. Three types of
+scale to consider are social, spatial, and temporal scale. Social scale defines
+the type and measurement of social relationships and directly impacts observed
+social connectivity between individuals. Spatial scale can reflect the
+resolution of the habitat within which social interactions occur. Finally,
+temporal scale is related to both study design and seasonal differences in
+social processes. By partitioning social associations into discrete contexts
+using multilayer networks, we highlight the influence of social, spatial and
+temporal scales on animal social systems, demonstrating the importance of
+considering biologically relevant and robust scales.
 <!-- intro -->
@@
 aggression), social associations (e.g. group membership or proximity), or
-spatial or home range overlap. Here, we define social associations using a series
-of social distance thresholds to generate proximity-based social networks. 
-Across network layers, increasing the social distance threshold resulted in
-an increase in graph strength (Figure
-\@ref(fig:socres)). Specifically, the strength of social associations across 
-habitat layers, with open and foraging habitats demonstrating a more pronounced
-increase in graph strength as well as greater variation across individuals. 
-These results emphasize that multilayer network metrics are directly influenced
-by social scale. An extension of this analysis could be to incorporate 
-behavioural states to explore the influence of social scale on patterns of 
-association or interaction across habitat and behavioural layers [e.g. 
-using focal observations or hidden Markov Models see @Muller_2018; @Jones_2020].
+spatial or home range overlap. Here, we define social associations using a
+series of social distance thresholds to generate proximity-based social
+networks. Across network layers, increasing the social distance threshold
+resulted in an increase in graph strength (Figure \@ref(fig:socres)).
+Specifically, the strength of social associations across habitat layers, with
+open and foraging habitats demonstrating a more pronounced increase in graph
+strength as well as greater variation across individuals. These results
+emphasize that multilayer network metrics are directly influenced by social
+scale. An extension of this analysis could be to incorporate behavioural states
+to explore the influence of social scale on patterns of association or
+interaction across habitat and behavioural layers [e.g. using focal observations
+or hidden Markov Models see @Muller_2018; @Jones_2020].
 <!-- social scale -->
@@
 <!-- spatial -->
-Habitat selection, the use of
-available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
-is a scale-dependent process [@Mayor_2009]. Social structure and 
-habitat selection are intimately related and individuals must
-share space to interact [@Webber_2018]. Johnson (1980) identified four
+Habitat selection, the use of available resources or landscape features by
+animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
+Social structure and habitat selection are intimately related and individuals
+must share space to interact [@Webber_2018]. Johnson (1980) identified four
 orders of habitat selection: (1) the geographical range of a species, (2) the
@@
 relevant for multilayer networks and our integration of habitat within a
-multilayer context could be an important first step (see Figure \@ref(fig:lcres)). 
-Specifically, if individuals select habitats at the 
-home range scale, it may be relevant to assess social structure at 
-the home range overlap scale in a multilayer framework. By contrast,
-in cases where individuals select habitats at the patch-scale, 
-more fine-scale measures of sociality may be relevant. Moving past this hierarchical
-perspective, Mayor et al. [-@Mayor_2007] emphasized the importance of considering a broad
-continuum of scales to reveal scale-dependent selection and avoid the bias of
-predefined scales assumed to be associated with certain behaviours.
+multilayer context could be an important first step (see Figure
+\@ref(fig:lcres)). Specifically, if individuals select habitats at the home
+range scale, it may be relevant to assess social structure at the home range
+overlap scale in a multilayer framework. By contrast, in cases where individuals
+select habitats at the patch-scale, more fine-scale measures of sociality may be
+relevant. Moving past this hierarchical perspective, Mayor et al. [-@Mayor_2007]
+emphasized the importance of considering a broad continuum of scales to reveal
+scale-dependent selection and avoid the bias of predefined scales assumed to be
+associated with certain behaviours.
 
@@
 <!-- temp -->
-<!-- TODO: results
-
--->
 The emergent relationship between habitat and sociality has been explored by the
 temporal distribution and phenology of resources and use of social information.
-We found increased edge overlap and graph strength in fall, winter and spring (approximately October - 
-June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A, C). 
-These periods of increased sociality correspond 
+We found increased edge overlap and graph strength in fall, winter and spring
+(approximately October - June) than in summer (approximately June - October)
+(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
 to seasons of heterogeneous resource availability [Peigner_2019]. This analysis
-could be extended using time-aggregated networks and a
-moving-window approach to time window size
-and sampling effort [@Farine_2017; @Bonnell_2020]. By explicitly 
-considering the temporal context of social interactions in separate layers, multilayer
-networks provide a detailed and dynamic perspective of animal social networks.
-For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
-represented by temporal multilayer networks than aggregated networks 
-[@Pereira_2020]. Evans et al. [-@Evans_2020]
-observed seasonal differences in the social structure of mice 
-(*Mus musculus domesticus*) related to temperature and breeding activity. 
-Finally, it is crucial to include sufficient data within sampling periods or time windows
-to construct robust networks [@Farine_2017; Proskurnikov_2017]. With increasing
-number of observations, we found
-variance decreased in edge overlap and multidegree across habitat layers as well
-as in graph strength within habitat layers (Figure \@ref(fig:nobs)). 
-As more observations were added, rarer
-relationships were recorded demonstrating the value of this form of sensitivity
-analysis.
+could be extended using time-aggregated networks and a moving-window approach to
+time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
+explicitly considering the temporal context of social interactions in separate
+layers, multilayer networks provide a detailed and dynamic perspective of animal
+social networks. For example, female mandrill (*Mandrillus sphinx*) sociality is
+more completely represented by temporal multilayer networks than aggregated
+networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
+differences in the social structure of mice (*Mus musculus domesticus*) related
+to temperature and breeding activity. Finally, it is crucial to include
+sufficient data within sampling periods or time windows to construct robust
+networks [@Farine_2017; Proskurnikov_2017]. With increasing number of
+observations, we found variance decreased in edge overlap and multidegree across
+habitat layers as well as in graph strength within habitat layers (Figure
+\@ref(fig:nobs)). As more observations were added, rarer relationships were
+recorded demonstrating the value of this form of sensitivity analysis.
+<!-- temp -->
 
@@
 social and spatial environments an individual experiences [@Webber_2018]. 
-
-Incorporating
-movement ecology within a multilayer network framework is a logical next step
-for a burgeoning field. Importantly, the technological advancements in
-biologging and wildlife tracking technology [@Borger_2020] have enabled this
-unique opportunity to integrate movement and habitat in multilayer networks to
-answer complex questions about animal socioecology.
 -->
@@
 scale based on the hypotheses being tested and logistical constraints.
-
-<!-- TODO repeat qs-->
 

### 2020-06-28 paper/manuscript.Rmd
n not N

@@
 between `r DT[, uniqueN(get(idcol))]` individuals across three habitat layers
-(foraging, forest, and open) using $N$ randomly selected observations. We first
-generated a maximum of 1000 timesteps and iteratively used $N$ of these ($N$ =
+(foraging, forest, and open) using $n$ randomly selected observations. We first
+generated a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
 10 - 1000 observations by steps of 10), to ensure previously included timesteps,
 and resulting associations, were accumulated with subsequent observations to
-mimic collection of observational data. Within each multilayer network with $N$
+mimic collection of observational data. Within each multilayer network with $n$
 observations, we calculated individual graph strength and multidegree. We

### 2020-06-28 paper/manuscript.Rmd
add results to spat p

@@
 Social structure and habitat selection are intimately related and individuals
-must share space to interact [@Webber_2018]. Johnson (1980) identified four
+must share space to interact [@Webber_2018].
+
+We found edge overlap was stable in open and forest layers but decreasing in 
+foraging layers with increasing spatial scale (Figure \@ref(fig:lcres) D).
+Graph strength had greater individual variation in open and foraging layers than
+in forest layers (Figure \@ref(fig:lcres) E). We observed a decrease in 
+the proportion of relocations in foraging habitat with increasing spatial
+resolution (14.5% at 30 m - <2% at 1000 m). As the foraging layer  
+had similar edge overlap and graph strength as the open layer at 30 m spatial 
+resolution despite having lower abundance on the landscape (foraging: 12.8%, 
+open: 36.9%), this result highlights the importance of considering
+spatial scale when including habitat in multilayer networks. Johnson 
+[-@Johson_1980] identified four
 orders of habitat selection: (1) the geographical range of a species, (2) the
@@
 \@ref(fig:lcres)). Specifically, if individuals select habitats at the home
-range scale, it may be relevant to assess social structure at the home range
-overlap scale in a multilayer framework. By contrast, in cases where individuals
-select habitats at the patch-scale, more fine-scale measures of sociality may be
+range scale, it may be relevant to assess social structure using home
+range overlap. By contrast, in cases where individuals
+select habitats at the patch-scale, fine-scale measures of sociality may be more
 relevant. Moving past this hierarchical perspective, Mayor et al. [-@Mayor_2007]
@@
 associated with certain behaviours.
-
-<!-- TODO: missing results
-
-As spatial resolution increased, edge overlap
-remained stable in open and forest layers but decreased in foraging layers
-(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
-with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
-open layer had greater individual variation in graph strength, and foraging
-layers showed an increase in graph strength with increasing spatial resolution
-(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
-on Fogo Island and the proportion of relocations in foraging habitat decreased
-as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
-the foraging layer had similar edge overlap as the open layer at 30 m resolution 
-indicating its importance in caribou sociality. 
--->
-
 <!-- spatial -->
@@
 for identifying spatially or temporally specific social associations. When
-employing multilayer networks, it is important to consider a broad continuum of
-social, spatial and temporal scales to fully capture ecological processes and
+employing multilayer networks, it is critical to consider a broad continuum of
+social, spatial and temporal scales to fully capture ecological processes and to
 establish a clear link between biologically relevant scales of observation.

### 2020-06-28 paper/manuscript.Rmd
reflow

@@
 Social structure and habitat selection are intimately related and individuals
-must share space to interact [@Webber_2018].
-
-We found edge overlap was stable in open and forest layers but decreasing in 
-foraging layers with increasing spatial scale (Figure \@ref(fig:lcres) D).
-Graph strength had greater individual variation in open and foraging layers than
-in forest layers (Figure \@ref(fig:lcres) E). We observed a decrease in 
-the proportion of relocations in foraging habitat with increasing spatial
-resolution (14.5% at 30 m - <2% at 1000 m). As the foraging layer  
-had similar edge overlap and graph strength as the open layer at 30 m spatial 
-resolution despite having lower abundance on the landscape (foraging: 12.8%, 
-open: 36.9%), this result highlights the importance of considering
-spatial scale when including habitat in multilayer networks. Johnson 
-[-@Johson_1980] identified four
-orders of habitat selection: (1) the geographical range of a species, (2) the
-home range of an individual, the (3) habitat patches within the home range and
-(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
-that, independently, third order of selection was insufficient for capturing
-landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
-scale larger than their home range size. Scales of habitat selection could be
-relevant for multilayer networks and our integration of habitat within a
-multilayer context could be an important first step (see Figure
-\@ref(fig:lcres)). Specifically, if individuals select habitats at the home
-range scale, it may be relevant to assess social structure using home
-range overlap. By contrast, in cases where individuals
-select habitats at the patch-scale, fine-scale measures of sociality may be more
-relevant. Moving past this hierarchical perspective, Mayor et al. [-@Mayor_2007]
-emphasized the importance of considering a broad continuum of scales to reveal
-scale-dependent selection and avoid the bias of predefined scales assumed to be
-associated with certain behaviours.
+must share space to interact [@Webber_2018]. We found edge overlap was stable in
+open and forest layers but decreasing in foraging layers with increasing spatial
+scale (Figure \@ref(fig:lcres) D). Graph strength had greater individual
+variation in open and foraging layers than in forest layers (Figure
+\@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
+foraging habitat with increasing spatial resolution (14.5% at 30 m - <2% at 1000
+m). As the foraging layer had similar edge overlap and graph strength as the
+open layer at 30 m spatial resolution despite having lower abundance on the
+landscape (foraging: 12.8%, open: 36.9%), this result highlights the importance
+of considering spatial scale when including habitat in multilayer networks.
+Johnson [-@Johson_1980] identified four orders of habitat selection: (1) the
+geographical range of a species, (2) the home range of an individual, the (3)
+habitat patches within the home range and (4) specific resources within a
+habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
+selection was insufficient for capturing landscape attributes selected for by
+mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
+Scales of habitat selection could be relevant for multilayer networks and our
+integration of habitat within a multilayer context could be an important first
+step (see Figure \@ref(fig:lcres)). Specifically, if individuals select habitats
+at the home range scale, it may be relevant to assess social structure using
+home range overlap. By contrast, in cases where individuals select habitats at
+the patch-scale, fine-scale measures of sociality may be more relevant. Moving
+past this hierarchical perspective, Mayor et al. [-@Mayor_2007] emphasized the
+importance of considering a broad continuum of scales to reveal scale-dependent
+selection and avoid the bias of predefined scales assumed to be associated with
+certain behaviours.
 <!-- spatial -->

### 2020-06-28 paper/manuscript.Rmd
rm weird space

@@
 <!-- Figure: Fogo ML Net -->
-(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
+(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.

### 2020-06-28 paper/manuscript.Rmd
fix missing 30 m from count

@@
 - 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
-decreasing in foraging habitat (14.5% at 30 m - <2% at 1000 m).  <!-- TODO: 
+decreasing in foraging habitat (23.9% at 30 m - <2% at 1000 m).  <!-- TODO: 
 break up -->Overall, these
@@
 \@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
-foraging habitat with increasing spatial resolution (14.5% at 30 m - <2% at 1000
+foraging habitat with increasing spatial resolution (23.9% at 30 m - <2% at 1000
 m). As the foraging layer had similar edge overlap and graph strength as the
 open layer at 30 m spatial resolution despite having lower abundance on the
-landscape (foraging: 12.8%, open: 36.9%), this result highlights the importance
+landscape (foraging: 12.8%, open: 36.9%), this highlights the importance
 of considering spatial scale when including habitat in multilayer networks.

### 2020-06-28 scripts/02-landcover-scale.R

@@ -129,12 +129,12 @@ out <- rbindlist(nets)
 
 
 # Count locs in lc --------------------------------------------------------
-count <- rbindlist(lapply(grep('lc[0-9]', colnames(DT), value = TRUE), function(col) {
+count <- rbindlist(lapply(grep('lc|lc[0-9]', colnames(DT), value = TRUE), function(col) {
   DT[, .N, col][, 
     c('lc', 'res') := .(get(col), as.integer(gsub('lc', '', col)))][, 
       .(lc, res, N)]
 }))
-
+count[is.na(res), res := 30]
 
 
 

### 2020-06-28 paper/manuscript.Rmd
use count data directly

@@
 
+options(digits = 3)
+
 DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
 nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
+count <- readRDS('../data/derived-data/02-landcover-scale-count.Rds')
 timedefs <- fread('../data/supp-data/timecut-defs.csv')
@@
 \@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
-foraging habitat with increasing spatial resolution (23.9% at 30 m - <2% at 1000
+foraging habitat with increasing spatial resolution (`r count[res == 30 & lc == 3, percent]`% at 30 m - `r count[res == 1000 & lc == 3, percent]`% at 1000
 m). As the foraging layer had similar edge overlap and graph strength as the

### 2020-06-28 paper/manuscript.Rmd
use count data directly

@@
 and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
-relocations in forest (42.1% at 30 m - 48.2% at 1000 m) and open (43.3% at 30 m
-- 50.3% at 1000 m) habitats increased with increasing spatial resolution, while
-decreasing in foraging habitat (23.9% at 30 m - <2% at 1000 m).  <!-- TODO: 
-break up -->Overall, these
-results indicate the importance of matching land cover resolution to scale of
-habitat selection as well as ensuring the land cover product used has a resolution fine
-enough to detect landscape features and habitats relevant to study species, such
-as important patchy and rare habitats.
+relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
+`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
+(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
+`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
+with increasing spatial resolution, while decreasing in foraging habitat 
+(`r count[res == 30 & lc == 3, percent]`% at 30 m
+- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
+indicate the importance of matching land cover resolution to scale of
+habitat selection and choosing a land cover product with a resolution
+sufficient to detect less common habitats.
 

### 2020-06-28 paper/manuscript.Rmd
add ml mention

@@
 # Results
-<!-- TODO intro + ml fig -->
-
 Individuals in multilayer networks became more connected as the social distance
@@
 across contexts.
+
+An illustrative multilayer network was generated, informed by previous social, 
+spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
+distance threshold was 50 m. The spatial resolution of the land cover 
+raster was 30 m. -->Relocations were predominantly in open 
+(`r count[res == 30 & lc == 1, percent]`%) and forest 
+(`r count[res == 30 & lc == 2, percent]`%) habitats 
+compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
+Despite this, individuals were more strongly connected in foraging and open 
+habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
+forest: 0.11, open: 0.23). There was a seasonal difference in association, 
+individuals were more connected between approximately October - June 
+(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
+than between approximately June - October 
+(mean graph strength in time windows; 1: 0.04, 3: 0.03).
 

### 2020-06-28 paper/manuscript.Rmd
fix ml cap

@@
 <!-- Figure: Fogo ML Net -->
-(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
+(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut == 2, format(mindate, '%B %Y')]` and `r timedefs[timecut == 20, format(mindate, '%B %Y')]`.
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.

### 2020-06-28 scripts/figures/figure-fogo-ml.R
time not temporal window

@@ -121,7 +121,7 @@ nodesize <- 3
         strip.background = element_rect(fill = NA, color = NA),
         strip.text = element_text(size = 14),
         panel.spacing = unit(0, "lines")) +
-    xlab('Temporal Window')
+    xlab('Time Window')
 )
 
 # Number of individuals

### 2020-06-28 paper/manuscript.Rmd
fix johnson 1980

@@
 of considering spatial scale when including habitat in multilayer networks.
-Johnson [-@Johson_1980] identified four orders of habitat selection: (1) the
+Johnson [-@Johnson_1980] identified four orders of habitat selection: (1) the
 geographical range of a species, (2) the home range of an individual, the (3)

### 2020-06-28 paper/manuscript.Rmd
reflow, tidy

@@
 
-Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
-example, grooming requires close spatial proximity between conspecifics and
-occurs over brief time periods [e.g. @Carter_2015], whereas social associations
-over long time periods 
-represent shared space use by members of the same social group [Figure
-\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
-interact or associate and thus have overlapping
-home ranges [@Vander_2014]. Home
-range overlap is an example of how animals share space over coarser spatial and
-temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
-clearly scales spatially and temporally, it remains unclear whether coarser
-scales of social interactions, such as social association and home range overlap, vary
-predictably [@Castles_2014; @Farine_2015a]. 
-We therefore define social scale as the explicit definition 
-and measurement of social relationships [@Farine_2015a].
+Social interactions exists across both temporal and spatial scales
+[@Whitehead_2008]. For example, grooming requires close spatial proximity
+between conspecifics and occurs over brief time periods [e.g. @Carter_2015],
+whereas social associations over long time periods represent shared space use by
+members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
+Individuals must share space to interact or associate and thus have overlapping
+home ranges [@Vander_2014]. Home range overlap is an example of how animals
+share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
+Although the social environment clearly scales spatially and temporally, it
+remains unclear whether coarser scales of social interactions, such as social
+association and home range overlap, vary predictably [@Castles_2014;
+@Farine_2015a]. We therefore define social scale as the explicit definition and
+measurement of social relationships [@Farine_2015a].
 
@@
 e.g. grooming, travelling, or foraging, (iii) spatial areas, e.g. local or
-regional, (iv) or temporal windows, e.g. daily or seasonal 
-[@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
+regional, (iv) or temporal windows, e.g. daily or seasonal [@Kivela_2014;
+@Porter_2018]. Multilayer networks are relatively novel to studies of animal
 behaviour [@Silk_2018; @Finn_2019], although they have been used to describe
@@
 the social distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. <!-- TODO: check jwt comment--> Group assignment based on the chain rule
+other individuals [@Robitaille_2019]. Group assignment based on the chain rule
 has previously been applied to caribou using a temporal threshold of 5 minutes
@@
 between ~20 - 100 m based on the rate at which variance in graph strength
-decreased. GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] 
-us to confirm the use of 50 m buffer that has long been used
+decreased. GPS data allows [e.g. from this study and @Peignier_2019;
+@Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
 for studies in the field [@Lingle_2003; @Clutton_1982].
@@
 network metrics increased. Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15 
-(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
-approximately October and June, also had higher graph strength 
-compared to time windows of lower edge overlap, between approximately June 
-and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
-series between January 2018 and April 2018. 
-These results suggest that ordinal multilayer networks can effectively 
-capture discrete time windows of aggregation and dissaggregation related 
-to resource availability, and highlight the importance of carefully 
-selecting the temporal scale of analysis. <!-- TODO see comment-->
+15-20 than in time windows 2-5 and 12-15 (Figure \@ref(fig:temp) A). Time
+windows of higher edge overlap, between approximately October and June, also had
+higher graph strength compared to time windows of lower edge overlap, between
+approximately June and October (Figure \@ref(fig:temp) C). Graph strength peaked
+across the time series between January 2018 and April 2018. These results
+highlight the importance of carefully selecting the temporal scale of analysis
+to effectively capture within- and across-year variation in sociality.
 
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and variance in metrics decreased.
-Edge overlap increased across all three habitat
-layers with increasing number of observations (Figure \@ref(fig:nobs) B).
-Similarly, multidegree for all individuals increased quickly between 10 and 100
-observations, and continued to increase until 1000 observations (Figure
-\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
-variable at low number of observations and variance decreased after ~100 observations
-(Figure \@ref(fig:nobs) A). <!--TODO double check-->Since the variance in these 
-multilayer metrics decreases after a certain number
-of observations, this sensitivity method could be useful for determining the
-number of observations necessary for sufficiently describing social dynamics
-across contexts.
+individuals became more connected and variance in metrics decreased. Edge
+overlap increased across all three habitat layers with increasing number of
+observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
+individuals increased quickly between 10 and 100 observations, and continued to
+increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
+across individuals in all three habitat layers was highly variable at low number
+of observations and variance decreased after ~100 observations (Figure
+\@ref(fig:nobs) A). Since the variance in these multilayer metrics decreases
+after a certain number of observations, this sensitivity method could be useful
+for determining the number of observations necessary for sufficiently describing
+social dynamics across contexts.
 
@@
 # Discussion
-<!--
-1. intro
-TODO: somewhere ref:ml
--->
-
-<!-- intro -->
 Animal social systems are characterized and influenced by scale. Three types of
@@
 considering biologically relevant and robust scales.
-<!-- intro -->
 
-<!-- social scale -->
 Social scale is an essential consideration for social network analysis
@@
 or hidden Markov Models see @Muller_2018; @Jones_2020].
-<!-- social scale -->
 
-<!-- spatial -->
 Habitat selection, the use of available resources or landscape features by
@@
 certain behaviours.
-<!-- spatial -->
 
-<!-- temp -->
 The emergent relationship between habitat and sociality has been explored by the
@@
 recorded demonstrating the value of this form of sensitivity analysis.
-<!-- temp -->
 
-<!-- Finally, due to the autocorrelated nature of biologging data it is -->
-<!-- essential to ensure social association data area non-randomly distributed -->
-<!-- [@Farine_2017b]. -->
-
-<!-- conclusion -->
 Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
@@
 ecology and we introduce concepts of scale within the existing multilayer
-framework. Silk et al. [-@Silk_2018] summarized some key multilayer questions in animal
-behaviour research  and based on our case study of scale in the context of
-multilayer networks, we conclude by posing an additional set of questions on the
-future of multilayer networks through the lens of scale and behavioural,
+framework. Silk et al. [-@Silk_2018] summarized some key multilayer questions in
+animal behaviour research  and based on our case study of scale in the context
+of multilayer networks, we conclude by posing an additional set of questions on
+the future of multilayer networks through the lens of scale and behavioural,
 landscape, and spatial ecology:
@@
 establish a clear link between biologically relevant scales of observation.
-<!-- conclusion -->
+
+# Box 1
+<!-- Finally, due to the autocorrelated nature of biologging data it is -->
+<!-- essential to ensure social association data area non-randomly distributed -->
+<!-- [@Farine_2017b]. -->
 
@@
 
-# Box 1
 Social phenotype has been increasingly linked to individual fitness, including

### 2020-06-28 paper/manuscript.Rmd
fix bastille 2018

@@
 [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
-for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
-represents the scale at which caribou tend to select and avoid habitat
-(Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social
-associations between `r DT[, uniqueN(get(idcol))]` individuals across three
-habitat layers (foraging, forest and open) for the entire study period. For each
-land cover resolution, we calculated individual graph strength within each
-habitat layer, and edge overlap and multidegree across habitat layers.
+for caribou during foraging, while 500 - 1000 m represents the scale at which
+caribou tend to select and avoid habitat [@Bastille_2018].
+Multilayer networks consisted of the social associations between 
+`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, 
+forest and open) for the entire study period. For each land cover resolution, we
+calculated individual graph strength within each habitat layer, and edge overlap
+and multidegree across habitat layers.
 

### 2020-06-29 paper/manuscript.Rmd
fix digits and round
reflow
mention aggregated windows
fix count percent

@@
 
-options(digits = 3)
+options(digits = 2, round = 2)
 
@@
 count <- readRDS('../data/derived-data/02-landcover-scale-count.Rds')
+count[lc %in% c(1, 2, 3), percent := N / sum(N) * 100, by = res]
 timedefs <- fread('../data/supp-data/timecut-defs.csv')
@@
 ```
-
-\newpage
 
@@
 for caribou during foraging, while 500 - 1000 m represents the scale at which
-caribou tend to select and avoid habitat [@Bastille_2018].
-Multilayer networks consisted of the social associations between 
-`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, 
-forest and open) for the entire study period. For each land cover resolution, we
-calculated individual graph strength within each habitat layer, and edge overlap
-and multidegree across habitat layers.
+caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
+consisted of the social associations between `r DT[, uniqueN(get(idcol))]`
+individuals across three habitat layers (foraging, forest and open) for the
+entire study period. For each land cover resolution, we calculated individual
+graph strength within each habitat layer, and edge overlap and multidegree
+across habitat layers.
 
@@
 than between approximately June - October 
-(mean graph strength in time windows; 1: 0.04, 3: 0.03).
+(mean graph strength in time windows; 1: 0.04, 3: 0.03). The time windows
+were aggregated from the finer scale time windows presented above (time window 1:
+2-5, time window 2: 6-11, time window 3: 12-15, time window 4: 16-20).
 

### 2020-06-29 paper/manuscript.Rmd
morning edits

@@
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
-In the context of animal behaviour, certain behaviours
-are scale-dependent; for example, acoustic communication in birds varies with
-spatial scales [@Luther_2009]. We posit that it is important to consider that
-animal behaviour within the social environment will be scale-dependent. 
-<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->
+We posit that it is important to consider the scale-dependence of 
+animal behaviour within the social environment to effectively understand 
+complex social systems.
 
@@
 association and home range overlap, vary predictably [@Castles_2014;
-@Farine_2015a]. We therefore define social scale as the explicit definition and
+@Farine_2015a]. We define social scale as the explicit definition and
 measurement of social relationships [@Farine_2015a].
@@
 @Wey_2008; @Croft_2011]. It provides insight into the structure of social
-communities and social network properties, which can influence population
+communities, which can influence population
 dynamics and evolutionary processes [@Pinter_Wollman_2013; @Kurvers_2014]. 
 Despite the widespread use and innovation of traditional social
-network analysis [@Webber_2019], it typically considers a single scale of
-sociality in a monolayer network, drastically simplifying the complexity of
+network analysis [@Webber_2019], it typically considers
+sociality in a singular context, drastically simplifying the complexity of
 animal social systems [@Finn_2019].
@@
 @Porter_2018]. Multilayer networks are relatively novel to studies of animal
-behaviour [@Silk_2018; @Finn_2019], although they have been used to describe
-multidimensional human social systems, complex transportation networks, and
-neural networks [@Kivela_2014]. Scale within multilayer social networks remains
-unexplored but provides a unique opportunity to develop novel understanding of
-variation in the social, spatial, or temporal scales associated with social
-systems.
+behaviour [@Silk_2018; @Finn_2019] and integrating scale within these 
+remains an unexplored opportunity to develop novel understanding of
+animal social systems.
 
@@
 system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
-collars, 1,250 g) as described by [@Schaefer_2013]. Collars were programmed to
+collars, 1,250 g) as described by Schaefer and Mahoney [-@Schaefer_2013]. Collars were programmed to
 collect location fixes every 2 hours. Prior to analyses, we subset GPS fixes
@@
 types into three categories using the R package `raster` [@Hijmans_2019]:
-foraging, forest, and open habitats. Foraging habitat consisted of foraging,
+foraging, forest, and open habitats. Foraging habitat consisted of lichen,
 forest habitat consisted of coniferous forest, conifer scrub, broad leaf forest,
@@
 We generated proximity-based social networks using the R package `spatsoc`
-[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. We assumed
+[@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
+<!--We assumed
 individuals were associating if simultaneous GPS fixes were within the spatial
-distance threshold of one another. Typically for ungulates and other gregarious
+distance threshold of one another.--> Typically for ungulates and other gregarious
 mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
@@
 We used a series of metrics to characterize the multilayer networks, focusing on
-the role of individuals within and across layers, and the similarity of
-different layers. To measure the role of individuals within layers, we
-calculated degree centrality and graph strength. Degree centrality is the number
-of direct connections an individual has to other individuals in a network layer.
-Graph strength is the degree weighted by the strength of association, in this
-case SRI, in each layer. We calculated multidegree,
+the role of individuals within layers and the similarity of edges across layers.
+Within each layer, we calculated degree centrality, the number
+of direct connections an individual has, and graph strength, the degree weighted 
+by the strength of association. We calculated multidegree,
 the sum of degree centrality of individuals across layers, an extension
-of degree centrality to multiple layers [@Berlingerio_2012;
-@Kivela_2014]. Finally, we measured the similarity of layers by calculating edge
+of degree centrality to multiple layers [@Berlingerio_2012; @Kivela_2014]. 
+Finally, we measured the similarity of layers by calculating edge
 overlap. Edge overlap is defined as the proportion of edges present in each
@@
 for group assignment. Social distance thresholds (5, 25, 50, 75, 100, 250 and
-500 m) represented a range of visual (short distance) to olfactory and long
-distance auditory sensory modalities of caribou. Multilayer networks consisted
+500 m) represent a range of sensory modalities of caribou from visual 
+to olfactory and auditory. Multilayer networks consisted
 of the social association between `r DT[, uniqueN(get(idcol))]` individuals
@@
 [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
-for caribou during foraging, while 500 - 1000 m represents the scale at which
+for caribou, while 500 - 1000 m represents the scale at which
 caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks
@@
 `r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods from the
-entire study period. Social associations were defined by spatiotemporal overlap
-of individuals within 5 minutes and 50 m. For each time window, we calculated
+entire study period. For each time window, we calculated
 individual graph strength within each time window, and edge overlap and
@@
 Individuals in multilayer networks became more connected as the social distance
-threshold increased. Mean graph strength differed across habitat layers with
-similar and higher graph strength in foraging and open layers, and lower
-strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
+threshold increased. Mean graph strength was higher in foraging and open layers
+than in forest layers (Figure \@ref(fig:socres)). Individual graph strength
 increased sharply between 5 m and 100 m in all three habitat classes followed by
@@
 Increasing land cover resolution resulted in decreased availability of foraging
-habitat and corresponding low connectivity of individuals at higher land cover
+habitat and corresponding low connectivity of individuals in foraging layers
+at higher land cover
 resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
 layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
-contrast, edge overlap was relatively consistent across land cover resolutions
-in forest and open layers (Figure \@ref(fig:lcres) D). Graph strength was more
+contrast, edge overlap was relatively consistent in forest and open layers
+as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
 variable within foraging habitat layers across land cover resolutions than open
@@
 habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
-forest: 0.11, open: 0.23). There was a seasonal difference in association, 
-individuals were more connected between approximately October - June 
+forest: 0.11, open: 0.23). There was a seasonal difference in association with 
+individuals more connected between approximately October - June 
 (mean graph strength in time windows; 2: 0.37, 4: 0.18) 
@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open).
+Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A) Edge overlap increased for all habitat layers with increasing number of observations.
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`.
+Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
 A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
@@
 series of social distance thresholds to generate proximity-based social
-networks. Across network layers, increasing the social distance threshold
+networks. Across habitat layers, increasing the social distance threshold
 resulted in an increase in graph strength (Figure \@ref(fig:socres)).
-Specifically, the strength of social associations across habitat layers, with
-open and foraging habitats demonstrating a more pronounced increase in graph
-strength as well as greater variation across individuals. These results
+Specifically, open and foraging layers showed a larger increase in graph
+strength as well as greater variation across individuals with larger social
+distance thresholds. These results
 emphasize that multilayer network metrics are directly influenced by social
@@
 \@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
-foraging habitat with increasing spatial resolution (`r count[res == 30 & lc == 3, percent]`% at 30 m - `r count[res == 1000 & lc == 3, percent]`% at 1000
+foraging habitat with increasing spatial resolution 
+(`r count[res == 30 & lc == 3, percent]`% at 30 m - `r count[res == 1000 & lc == 3, percent]`% at 1000
 m). As the foraging layer had similar edge overlap and graph strength as the
-open layer at 30 m spatial resolution despite having lower abundance on the
-landscape (foraging: 12.8%, open: 36.9%), this highlights the importance
+open layer at 30 m spatial resolution, this highlights the importance
 of considering spatial scale when including habitat in multilayer networks.
@@
 habitat patches within the home range and (4) specific resources within a
-habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
-selection was insufficient for capturing landscape attributes selected for by
-mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
-Scales of habitat selection could be relevant for multilayer networks and our
+habitat patch. Scales of habitat selection could be relevant for multilayer networks and our
 integration of habitat within a multilayer context could be an important first
-step (see Figure \@ref(fig:lcres)). Specifically, if individuals select habitats
+step. Specifically, if individuals select habitats
 at the home range scale, it may be relevant to assess social structure using
@@
 (Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
-to seasons of heterogeneous resource availability [Peigner_2019]. This analysis
-could be extended using time-aggregated networks and a moving-window approach to
-time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
+to seasons of heterogeneous resource availability [Peignier_2019]. This analysis
+could be extended using time-aggregated networks and a moving-window approach for
+informing time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
 explicitly considering the temporal context of social interactions in separate
 layers, multilayer networks provide a detailed and dynamic perspective of animal
-social networks. For example, female mandrill (*Mandrillus sphinx*) sociality is
+social systems. For example, female mandrill (*Mandrillus sphinx*) sociality is
 more completely represented by temporal multilayer networks than aggregated
 networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
-differences in the social structure of mice (*Mus musculus domesticus*) related
+differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
 to temperature and breeding activity. Finally, it is crucial to include
 sufficient data within sampling periods or time windows to construct robust
-networks [@Farine_2017; Proskurnikov_2017]. With increasing number of
+networks [@Farine_2017; @Proskurnikov_2017]. With increasing number of
 observations, we found variance decreased in edge overlap and multidegree across
 habitat layers as well as in graph strength within habitat layers (Figure
-\@ref(fig:nobs)). As more observations were added, rarer relationships were
-recorded demonstrating the value of this form of sensitivity analysis.
+\@ref(fig:nobs)). In addition, less common relationships were recorded with
+increasing number of observations, demonstrating the value of this form of sensitivity analysis.
 
@@
 Multilayer networks remain a nascent but powerful tool in animal behavioural
-ecology and we introduce concepts of scale within the existing multilayer
-framework. Silk et al. [-@Silk_2018] summarized some key multilayer questions in
-animal behaviour research  and based on our case study of scale in the context
-of multilayer networks, we conclude by posing an additional set of questions on
+ecology. Silk et al. [-@Silk_2018] summarized some key multilayer questions in
+animal behaviour research and, based on our study of scale, 
+we conclude by posing an additional set of questions on
 the future of multilayer networks through the lens of scale and behavioural,
@@
 2. Why do individuals associate more strongly with certain conspecifics in some
-habitats? What, if any, is the role of movement in the context of habitat
+habitats? What is the role of movement in the context of habitat
 networks?

### 2020-06-29 paper/manuscript.Rmd
fix peignier
add temp to abs

@@
 output:
-   bookdown::github_document2: default
-   # bookdown::word_document2:
-   #   reference_docx: template.docx
+   # bookdown::github_document2: default
+   bookdown::word_document2:
+     reference_docx: template.docx
 knit: (function(inputFile, encoding) {
@@
 and animal space use. Meanwhile, social processes can range from fine-scale
-interactions to co-occurrence and overlapping home ranges. <!-- and vary within
+interactions to co-occurrence and overlapping home ranges. Lastly,
+sociality can vary within and across seasons. <!-- and vary within
 and across seasons.--> Multilayer networks promise the explicit integration of
@@
 (Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
-to seasons of heterogeneous resource availability [Peignier_2019]. This analysis
+to seasons of heterogeneous resource availability [@Peignier_2019]. This analysis
 could be extended using time-aggregated networks and a moving-window approach for

### 2020-06-29 paper/manuscript.Rmd
abstract edits

@@
 # Abstract
-<!-- Scale remains a foundational concept in ecology. Social processes range from 
-fine-scale interactions and co-occurrence to overlapping home ranges. Spatial 
-scale has become a central consideration in the way we understand landscape ecology
-and animal space use. Temporal variation in sociality and
-
-Multilayer networks promise the explicit integration of social, 
-spatial and temporal contexts of animal social networks.
-
--->
-
 Scale remains a foundational concept in ecology. Spatial scale, for instance,
 has become a central consideration in the way we understand landscape ecology
-and animal space use. Meanwhile, social processes can range from fine-scale
-interactions to co-occurrence and overlapping home ranges. Lastly,
-sociality can vary within and across seasons. <!-- and vary within
-and across seasons.--> Multilayer networks promise the explicit integration of
-the social, spatial and temporal contexts. Given the complex interplay of
+and animal space use. Meanwhile, scale-dependent social processes can range from fine-scale
+interactions to co-occurrence and overlapping home ranges. Furthermore,
+sociality can vary within and across seasons. Multilayer networks promise the 
+explicit integration of
+the social, spatial and, temporal contexts. Given the complex interplay of
 sociality and animal space use in heterogeneous landscapes, there remains an
 important gap in our understanding of the influence of scale on animal social
-networks. We discuss ways of considering social, spatial and temporal scale in
-the context of multilayer caribou social networks. <!--We also present
-perspectives on future development and applications of scale in multilayer
-networks with respect to: phenotypes and individual fitness, movement ecology
-and collective movement, and habitat selection and space use.--> Effective
+networks. Using an empirical example, we discuss ways of considering social, spatial and, temporal scale in
+the context of multilayer caribou social networks. Effective
 integration of social and spatial processes, including biologically meaningful
 scales, within the context of animal social networks is an emerging area of
-research. We incorporate perspectives on how the social environment and spatial
-processes are linked across scales in a multilayer context.
+research. We incorporate perspectives that link the social environment to spatial
+processes across scales in a multilayer context.
 
 ## Keywords
-Social network analysis, Landscape ecology, Movement ecology, Space use
+Rangifer, Social network analysis, Habitat selection, Landscape ecology, Space use
 

### 2020-06-29 paper/manuscript.Rmd
intro edits

@@
 [@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989].
-We posit that it is important to consider the scale-dependence of 
+We posit that it is important to consider the scale dependence of 
 animal behaviour within the social environment to effectively understand 
@@
 share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
-Although the social environment clearly scales spatially and temporally, it
+Although the social environment scales spatially and temporally, it
 remains unclear whether coarser scales of social interactions, such as social

### 2020-06-29 paper/manuscript.Rmd
methods edits

@@
 landscape, and spatial ecology to and applied this framework to caribou
-(*Rangifer tarandus*) on Fogo Island, Newfoundland, Canada. First, we test to
+(*Rangifer tarandus*). First, we test to
 what degree the social scale of relationships, spatial scale of landscapes, and
@@
 and the winter range scale (all craters within an individual’s range)
-[@Mayor_2009]. Access to forage is therefore heterogeneous in winter depending
+[@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
 on snow cover and distribution of craters on the landscape.
@@
 ## Caribou location data
-We used GPS location data collected from Fogo Island caribou between 
+We used GPS location data collected from caribou on Fogo Island, Newfoundland, Canada between 
 `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. 
@@
 [@Robitaille_2019] in `r substr(version$version.string, 1, 15)` [@R_Core_Team]. 
-<!--We assumed
-individuals were associating if simultaneous GPS fixes were within the spatial
-distance threshold of one another.--> Typically for ungulates and other gregarious
+Typically for ungulates and other gregarious
 mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
@@
 ranging from directly observed to remotely sensed [@Davis_2018; @Webber_2019].
-Remotely sensed GPS data is commonly collected at a fixed rate, e.g. every $x$
+Remotely sensed GPS data are commonly collected at a fixed rate, e.g. every $x$
 minutes or hours, continuously throughout the study period. Fix rate is a

### 2020-06-29 paper/manuscript.Rmd
results edits

@@
 threshold increased. Mean graph strength was higher in foraging and open layers
-than in forest layers (Figure \@ref(fig:socres)). Individual graph strength
-increased sharply between 5 m and 100 m in all three habitat classes followed by
+compared to forest layers (Figure \@ref(fig:socres)). Individual graph strength
+increased when the social distance threshold increased from 5 m and 100 m in 
+all three habitat layers followed by
 a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
@@
 between ~20 - 100 m based on the rate at which variance in graph strength
-decreased. GPS data allows [e.g. from this study and @Peignier_2019;
+decreased. GPS data allowed [e.g. from this study and @Peignier_2019;
 @Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
-for studies in the field [@Lingle_2003; @Clutton_1982].
+for studies of ungulate social behaviour in the field [@Lingle_2003; @Clutton_1982].
 
@@
 - `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
-indicate the importance of matching land cover resolution to scale of
+indicated the importance of matching land cover resolution to scale of
 habitat selection and choosing a land cover product with a resolution
@@
 network metrics increased. Edge overlap was higher in time windows 1, 6-11 and
-15-20 than in time windows 2-5 and 12-15 (Figure \@ref(fig:temp) A). Time
-windows of higher edge overlap, between approximately October and June, also had
+15-20 (between approximately October and June) than in time windows 2-5 and 12-15 
+(between approximately June and October) (Figure \@ref(fig:temp) A). Time
+windows of higher edge overlap also had
 higher graph strength compared to time windows of lower edge overlap, between
 approximately June and October (Figure \@ref(fig:temp) C). Graph strength peaked
-across the time series between January 2018 and April 2018. These results
+across the time series throughout winter 2018 (January to April). These results
 highlight the importance of carefully selecting the temporal scale of analysis
@@
 observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
-individuals increased quickly between 10 and 100 observations, and continued to
+individuals increased quickly between 10 and 100 observations and continued to
 increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
@@
 An illustrative multilayer network was generated, informed by previous social, 
-spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
-distance threshold was 50 m. The spatial resolution of the land cover 
-raster was 30 m. -->Relocations were predominantly in open 
+spatial, and temporal scale results (Figure \@ref(fig:ml)). Relocations were predominantly in open 
 (`r count[res == 30 & lc == 1, percent]`%) and forest 
@@
 compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
-Despite this, individuals were more strongly connected in foraging and open 
-habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
-forest: 0.11, open: 0.23). There was a seasonal difference in association with 
+Despite lower proportion of relocations in foraging habitat, 
+individuals were more strongly connected in foraging and open 
+habitats than in forest (mean graph strength in habitat layers (SD); foraging: 0.21 (0.23), 
+forest: 0.11 (0.13), open: 0.23 (0.24)). There was a seasonal difference in association with 
 individuals more connected between approximately October - June 
-(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
+(mean graph strength in time windows; 2: 0.37 (0.23), 4: 0.18 (0.11)) 
 than between approximately June - October 
-(mean graph strength in time windows; 1: 0.04, 3: 0.03). The time windows
+(mean graph strength in time windows; 1: 0.04 (0.04), 3: 0.03 (0.07)). The time windows
 were aggregated from the finer scale time windows presented above (time window 1:

### 2020-06-29 paper/manuscript.Rmd
discussion edits

@@
 Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses.
+Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses.
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
@@
 # Discussion
-Animal social systems are characterized and influenced by scale. Three types of
-scale to consider are social, spatial, and temporal scale. Social scale defines
+Animal social systems are characterized and influenced by scale (Figure \@ref(fig:ml)). Three types of
+scale particularly relevant to animals are social, spatial, and temporal. Social scale defines
 the type and measurement of social relationships and directly impacts observed
@@
 resolution of the habitat within which social interactions occur. Finally,
-temporal scale is related to both study design and seasonal differences in
+temporal scale relates to both study design and seasonal differences in
 social processes. By partitioning social associations into discrete contexts
-using multilayer networks, we highlight the influence of social, spatial and
+using multilayer networks, we highlight the influence of social, spatial, and
 temporal scales on animal social systems, demonstrating the importance of
@@
 resulted in an increase in graph strength (Figure \@ref(fig:socres)).
-Specifically, open and foraging layers showed a larger increase in graph
+Specifically, open and foraging layers had higher graph
 strength as well as greater variation across individuals with larger social
-distance thresholds. These results
-emphasize that multilayer network metrics are directly influenced by social
-scale. An extension of this analysis could be to incorporate behavioural states
+distance thresholds. While our understanding of patterns of ungulate grouping 
+across habitat types is relatively well-established [@Lingle_2003; @Kasozi_2020],
+the ability to generate habitat-specific social networks provides novel 
+inference given the ability to estimate inter- and intra-layer metrics. Furthermore,
+generating socially variable layers within a multilayer framework emphasizes
+that social scale directly influence multilayer network metrics. 
+An extension of this analysis could incorporate behavioural states
 to explore the influence of social scale on patterns of association or
-interaction across habitat and behavioural layers [e.g. using focal observations
-or hidden Markov Models see @Muller_2018; @Jones_2020].
+interaction across habitat and behavioural layers e.g. using focal observations
+or hidden Markov Models [see @Muller_2018; @Jones_2020].
 
 Habitat selection, the use of available resources or landscape features by
-animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
+animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009]
+that we can observe in multilayer networks.
 Social structure and habitat selection are intimately related and individuals
 must share space to interact [@Webber_2018]. We found edge overlap was stable in
-open and forest layers but decreasing in foraging layers with increasing spatial
-scale (Figure \@ref(fig:lcres) D). Graph strength had greater individual
+open and forest layers but decreased in foraging layers as spatial
+scale increased (Figure \@ref(fig:lcres) D). Graph strength had greater individual
 variation in open and foraging layers than in forest layers (Figure
-\@ref(fig:lcres) E). We observed a decrease in the proportion of relocations in
+\@ref(fig:lcres) E). Furthermore, we observed a decrease in the proportion of relocations in
 foraging habitat with increasing spatial resolution 
@@
 m). As the foraging layer had similar edge overlap and graph strength as the
-open layer at 30 m spatial resolution, this highlights the importance
-of considering spatial scale when including habitat in multilayer networks.
-Johnson [-@Johnson_1980] identified four orders of habitat selection: (1) the
+open layer at 30 m spatial resolution, spatial scale therefore played a
+key role in our multilayer social networks. 
+Johnson [-@Johnson_1980] identified four orders, or scales,  of habitat selection: (1) the
 geographical range of a species, (2) the home range of an individual, the (3)
@@
 step. Specifically, if individuals select habitats
-at the home range scale, it may be relevant to assess social structure using
+at the home range scale - e.g. at coarser resolution, it may be relevant to assess social structure using
 home range overlap. By contrast, in cases where individuals select habitats at
@@
 importance of considering a broad continuum of scales to reveal scale-dependent
-selection and avoid the bias of predefined scales assumed to be associated with
-certain behaviours.
+selection and avoid the bias of predefined scales assumed to associate with
+certain behaviours. We highlight the concept of scale of scale in multilayer 
+networks should be approached based on explicit and precise definitions
+to ensure robust measurements.
 
 The emergent relationship between habitat and sociality has been explored by the
-temporal distribution and phenology of resources and use of social information.
-We found increased edge overlap and graph strength in fall, winter and spring
-(approximately October - June) than in summer (approximately June - October)
+temporal distribution and phenology of resources and use of social information
+in multilayer networks [e.g. @Evans_2020].
+We observed seasonal variation in edge overlap. Specifically, we found 
+increased edge overlap and graph strength in autumn, winter and spring than in summer 
 (Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
-to seasons of heterogeneous resource availability [@Peignier_2019]. This analysis
+to seasons of heterogeneous resource availability for caribou [@Peignier_2019]. This analysis
 could be extended using time-aggregated networks and a moving-window approach for
@@
 observations, we found variance decreased in edge overlap and multidegree across
-habitat layers as well as in graph strength within habitat layers (Figure
-\@ref(fig:nobs)). In addition, less common relationships were recorded with
-increasing number of observations, demonstrating the value of this form of sensitivity analysis.
+habitat layers and in graph strength within habitat layers (Figure
+\@ref(fig:nobs)). As one might expect, dyads that only occasionally associated
+were more likely to be recorded with increasing number of observations, demonstrating 
+the value of this form of sensitivity analysis to social networks in general
+and multilayer networks in particular.
 
@@
 [@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of
-complex, high resolution data. We highlight ways in which scale should be
-considered when building social networks from both observed and remotely-sensed
+complex, high-resolution data. We highlight ways in which scale should be
+considered when building social networks from both observed and remotely sensed
 data. Our multilayer network analysis of caribou sociality incorporating high
@@
 context of observed animal behaviour as the scales we chose to explore, e.g.,
-number of observations and sociality across space and time, are ones that have
-also traditionally been done in ethology.
+social, spatial, and temporal, are scales that have
+also been investigated using traditional behavioural ethological methods.
 
@@
 
-1. How do social phenotypes vary across social, spatial, and temporal scales and
-at which scale might these influence fitness? Are some scales better predictors
-for different fitness metrics?
+1. How do multilayer social network metrics vary across social, spatial, and temporal scales and
+at which scale might these influence fitness (Box 1)? Are some scales better predictors
+for different fitness components, e.g. reproductive success or suvival?
 
@@
 employing multilayer networks, it is critical to consider a broad continuum of
-social, spatial and temporal scales to fully capture ecological processes and to
+social, spatial and, temporal scales to capture fully ecological processes and to
 establish a clear link between biologically relevant scales of observation.

### 2020-06-29 paper/manuscript.Rmd
box edits

@@
 # Box 1
-<!-- Finally, due to the autocorrelated nature of biologging data it is -->
-<!-- essential to ensure social association data area non-randomly distributed -->
-<!-- [@Farine_2017b]. -->
-
-<!-- TODO include mov elsewhere 
-Social processes, movement decisions, and space use are inextricably linked and
-multilayer networks represent a potential analytical framework for linking these
-processes [@Mourier_2019].
-
-Integrating habitat-specific
-movement layers could further illuminate the role of movement as a driver of the
-social and spatial environments an individual experiences [@Webber_2018]. 
--->
-
 Social phenotype has been increasingly linked to individual fitness, including
@@
 
-Varying social scales can have different fitness repercussions for individuals.
+Varying social scales can have different fitness outcomes for individuals.
 Rhesus macaques (*Macaca mulatta*) had higher survivorship when they had fewer
-but stronger and more stable social associates and grooming partners rather than
-simply more associates [@Ellis_2019].  It is a common trope that individuals
+stable social associates and grooming partners compared to many weak social 
+associates [@Ellis_2019]. Typically individuals
 must be associating to interact, and many studies assume that proximity is proxy
-for interacting [@Farine_2015a]. For instance, baboons must be within proximity
-of each other for grooming yet other animals interact using communication
-such as long-distance vocalization or olfactory signals 
-[@Carter_2015]. It is possible to record social interactions that do not require
+for interacting [@Farine_2015a]. For instance, baboons (*Papio* spp.) must be 
+within close proximity of each other for grooming yet, other forms
+of social interaction may occur over long-distances based on vocal or
+olfactory signals [@Carter_2015]. It is possible to record social interactions that do not require
 proximity using, for example, microphone arrays to construct long-distance
@@
 
-Multilayer networks enable researchers to look at similarities and differences
-between discrete temporal windows. Changing social phenotypes over ontogeny can
+Multilayer networks enable researchers to investigate similarities and differences
+in social processes between discrete temporal windows. Changing social phenotypes over ontogeny can
 affect fitness [@Berger_2015; @Brent_2017]. Individuals progress through
@@
 the selection of time windows. Considering fine temporal scales provides insight
-across developmental stages that may otherwise be missed [@Turner_2020]. Thus,
-it is critical to carefully consider the effect of scale on the relationship
+across developmental stages that may otherwise be missed [@Turner_2020]. It remains
+critical to carefully consider the effect of scale on the relationship
 between an individual’s social network position and fitness using a temporal

### 2020-08-14 paper/manuscript.Rmd

@@
 For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
-Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
+Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
 After 100 m, graph strength continued to increase at a slower rate.
@@
 Above 600 m, edge overlap in foraging layers is stable.
-E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution.
+E) Graph strength within habitat layers across spatial resolutions showing individuals as a separate line and the mean of individuals in bold.
 Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution.
 Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.
-
-<!-- Figure: metrics by number of observations -->
-(ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
-A) Edge overlap increased for all habitat layers with increasing number of observations.
-Foraging and open layers had higher edge overlap than forest layers.
-B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations.
-C) Multidegree increased for all individuals with increasing number of observations.
-Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
 
@@
 Graph strength peaked in time window 9, with noticeable higher strength than the following year.
+
+<!-- Figure: metrics by number of observations -->
+(ref:nobs) Varying scale in number of observations.
+Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+A) Edge overlap increased for all habitat layers with increasing number of observations.
+Foraging and open layers had higher edge overlap than forest layers.
+B) Graph strength within habitat layers with increasing number of observations showing individuals as a separate line and the mean of individuals in bold.
+Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations.
+C) Multidegree for all individuals increased with increasing number of observations.
+Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).
 

### 2020-08-17 paper/manuscript.Rmd
minor edits

@@
 # Introduction
-Our inference regarding the processes underlying ecological patterns
+Our inferences regarding the processes underlying ecological patterns
 are directly linked to the scale at which they are observed [@Levin_1992;
-@Allen_2015]. Animals are influenced across scales through ecological processes such as
+@Allen_2015]. Animals are influenced across scales by ecological processes such as
 trophic interactions, resource availability
@@
 
-We examined scale-dependent multilayer networks motivated by behavioural,
-landscape, and spatial ecology to and applied this framework to caribou
+We examined scale-dependent multilayer networks of behavioural,
+landscape, and spatial ecology and applied this framework to caribou
 (*Rangifer tarandus*). First, we test to
@@
 that display temporal and spatial variation in social networks [@Peignier_2019].
-In winter, caribou dig holes, termed craters, to access forage beneath the snow
+Caribou dig holes, termed craters, in winter to access forage beneath the snow
 [@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
@@
 and mixed-wood forest, while open habitat consisted of wetland, rocky barrens,
-and anthropogenic. Water habitat was excluded from all subsequent analyses.
+and anthropogenic areas. Water was excluded from all subsequent analyses.
 
@@
 500 m of one another were considered in the same group. Increasing social
-distance threshold is a proxy for potential behavioural interactions that occur
+distance threshold is a proxy for potential behavioural interactions (eg. vocal communication)
+that occur
 across these distances. For every social distance threshold, we calculated
@@
 selection and avoid the bias of predefined scales assumed to associate with
-certain behaviours. We highlight the concept of scale of scale in multilayer 
+certain behaviours. We highlight the concept of scale in multilayer 
 networks should be approached based on explicit and precise definitions
@@
 
+<!-- rm:
 Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
@@
 also been investigated using traditional behavioural ethological methods. 
+-->
 
@@
 animal behaviour research and, based on our study of scale, 
-we conclude by posing an additional set of questions on
-the future of multilayer networks through the lens of scale and behavioural,
-landscape, and spatial ecology:
+we conclude by posing an additional set of questions centered on scale in
+behavioural, landscape, and spatial ecology:
 

### 2020-08-17 paper/manuscript.Rmd
minor edits

@@
 all networks, individual caribou were represented as nodes and associations between
-individuals in a given network layer were represented as intralayer
-edges.
-
-We weighted edges of social networks by the strength of association between
-caribou using the simple ratio index [SRI, @Cairns_1987]:
+individuals were represented as edges. We weighted edges by the strength of 
+association between individuals using the simple ratio index [SRI, @Cairns_1987].
 
@@
 ### Spatial scale
-To assess the influence of spatial scale, we aggregated the land cover raster
-using the R package `grainchanger` [@Graham_2019] across a series of scales (100
-- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
-moving window method using a circular window corresponding to the above scales
-[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
+To assess the influence of land cover spatial scale, we aggregated the land cover raster
+using the R package `grainchanger` [@Graham_2019] across a series of scales 
+(100 - 1000 m by steps of 100 m) using a modal moving window method [@Graham_2019a]. 
+We assume 30 m and 100 m represents fine-scale decision making
 for caribou, while 500 - 1000 m represents the scale at which

### 2020-08-25 paper/manuscript.Rmd
adjust social scale p

@@
 
-Social interactions exists across both temporal and spatial scales
-[@Whitehead_2008]. For example, grooming requires close spatial proximity
-between conspecifics and occurs over brief time periods [e.g. @Carter_2015],
-whereas social associations over long time periods represent shared space use by
+Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
+For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas <!--Social
+associations occur over longer time periods and represent
+whereas social associations over longer time periods represent shared space use by
 members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
-Individuals must share space to interact or associate and thus have overlapping
-home ranges [@Vander_2014]. Home range overlap is an example of how animals
-share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
+<!--Individuals must share space to interact or associate and thus have overlapping
+home ranges [@Vander_2014].--> home range overlap and shared space use occur over
+coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
 Although the social environment scales spatially and temporally, it
@@
 association and home range overlap, vary predictably [@Castles_2014;
-@Farine_2015a]. We define social scale as the explicit definition and
-measurement of social relationships [@Farine_2015a].
+@Farine_2015a]. Social scale 
+is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].
 

### 2020-08-25 paper/manuscript.Rmd
specify fix rate again

@@
 Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
-data, the chain rule is applied by assigning a group identifier to the union of
-buffered GPS fixes at each time step. As such, individuals in a group are within
+mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. The chain rule is applied by assigning a group identifier to the union of
+buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
 the social distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. Group assignment based on the chain rule
-has previously been applied to caribou using a temporal threshold of 5 minutes
-and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. In
-all networks, individual caribou were represented as nodes and associations between
+other individuals [@Robitaille_2019]. Group assignment is defined using a 
+temporal threshold of 5 minutes
+and a social distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018]. 
+In all networks, individual caribou were represented as nodes and associations between
 individuals were represented as edges. We weighted edges by the strength of 

### 2020-08-25 paper/manuscript.Rmd
add evans 2019 to social scale p

@@
 Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
-For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas <!--Social
-associations occur over longer time periods and represent
-whereas social associations over longer time periods represent shared space use by
-members of the same social group [Figure \@ref(fig:spacetime), @Franks_2009].
-<!--Individuals must share space to interact or associate and thus have overlapping
-home ranges [@Vander_2014].--> home range overlap and shared space use occur over
+For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas social associations
+represent shared space use by members of the same social group over longer time periods [@Franks_2009], and home range overlap occurs over
 coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
@@
 association and home range overlap, vary predictably [@Castles_2014;
-@Farine_2015a]. Social scale 
+@Farine_2015a; @Evans_2019]. Social scale 
 is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].

### 2020-08-25 paper/manuscript.Rmd
nov - may, june - oct

@@
 The temporal multilayer network indicated within-year time windows where social
-network metrics increased. Edge overlap was higher in time windows 1, 6-11 and
-15-20 (between approximately October and June) than in time windows 2-5 and 12-15 
-(between approximately June and October) (Figure \@ref(fig:temp) A). Time
+network metrics increased. Edge overlap was higher in between approximately November and May (time windows 1, 6-11 and
+15-20) than between approximately June and October (time windows 2-5 and 12-15 
+ (Figure \@ref(fig:temp) A). Time
 windows of higher edge overlap also had
@@
 Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
-A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20).
+A) Edge overlap was high between approximately November and May (time windows 1, 6-11, 15-20) and low between approximately June and October (time windows 2-5 and 12-15).
 B) Ordinal network layers showing unweighted edges between individuals within time windows.
-Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15.
-Number of individuals in each time window is reported below each layer.
+Like edge overlap, individuals were more connected between November and May, compared to between June and October.
 C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines.

### 2020-08-26 paper/manuscript.Rmd
specifically which four time periods

@@
 (ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut == 2, format(mindate, '%B %Y')]` and `r timedefs[timecut == 20, format(mindate, '%B %Y')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses.
+Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant position across network layers they were observed in.
+Twelve layers represent combinations of four time windows (approximately June 2017 - October 2017, November 2017 - May 2018, June 2018 - October 2018, November 2017 - March 2019)  and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses.
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

### 2020-08-26 paper/manuscript.Rmd
reduce extraneous info in caps

--- 2020-08-25 paper/manuscript.Rmd
@@
 ## Caribou location data
-We used GPS location data collected from caribou on Fogo Island, Newfoundland, Canada between 
+We used GPS location data collected from `r DT[, uniqueN(get(idcol))]` adult female caribou on Fogo Island, Newfoundland, Canada between 
 `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`. 
-Adult female caribou were immobilized and fitted with global positioning
+Caribou were immobilized and fitted with global positioning
 system (GPS) collars (Lotek Wireless Inc., Newmarket, ON, Canada, GPS4400M
@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
+Multilayer networks were generated of caribou social associations within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
 A) Edge overlap was high between approximately November and May (time windows 1, 6-11, 15-20) and low between approximately June and October (time windows 2-5 and 12-15).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A) Edge overlap increased for all habitat layers with increasing number of observations.
@@
 <!-- Figure: Fogo ML Net -->
-(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut == 2, format(mindate, '%B %Y')]` and `r timedefs[timecut == 20, format(mindate, '%B %Y')]`.
-Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed.
-Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses.
+(ref:ml) Multilayer network representing social association of caribou across four time windows (approximately June 2017 - October 2017, November 2017 - May 2018, June 2018 - October 2018, November 2017 - March 2019)  and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses.
+Individual caribou are represented as nodes in a constant position across network layers they were observed in.
 Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

### 2020-08-26 paper/manuscript.Rmd
eg fine scale

@@
 We assume 30 m and 100 m represents fine-scale decision making
-for caribou, while 500 - 1000 m represents the scale at which
+for caribou [@Mayor_2007], while 500 - 1000 m represents the scale at which
 caribou tend to select and avoid habitat [@Bastille_2018]. Multilayer networks

### 2020-08-26 paper/manuscript.Rmd
add refs

@@
 animal behaviour within the social environment to effectively understand 
-complex social systems.
+complex social systems [@Whitehead_2008; @Webber_2018].
 

### 2020-08-26 paper/manuscript.Rmd
combine intro p
rm sri

@@
 @Wey_2008; @Croft_2011]. It provides insight into the structure of social
-communities, which can influence population
-dynamics and evolutionary processes [@Pinter_Wollman_2013; @Kurvers_2014]. 
-Despite the widespread use and innovation of traditional social
-network analysis [@Webber_2019], it typically considers
+communities, which can influence population dynamics and evolutionary processes
+[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use and innovation
+of traditional social network analysis [@Webber_2019], it typically considers
 sociality in a singular context, drastically simplifying the complexity of
-animal social systems [@Finn_2019].
+animal social systems [@Finn_2019]. Extending traditional monolayer social
+networks, multilayer networks explicitly consider social systems across
+scale-dependent contexts [@Pilosof_2017]. Multilayer networks are composed of
+multiple layers, each representing (i) different classes of individuals, e.g.
+male or female, (ii) types of behaviours, e.g. grooming, travelling, or
+foraging, (iii) spatial areas, e.g. local or regional, (iv) or temporal windows,
+e.g. daily or seasonal [@Kivela_2014; @Porter_2018]. Multilayer networks are 
+relatively novel to studies of animal behaviour [@Silk_2018; @Finn_2019] and 
+integrating scale within these remains an unexplored opportunity to develop 
+novel understanding of animal social systems.
 
-Extending traditional monolayer social networks, multilayer networks explicitly
-consider social systems across scale-dependent contexts [@Pilosof_2017].
-Multilayer networks are composed of multiple layers, each representing (i)
-different classes of individuals, e.g. male or female, (ii) types of behaviours,
-e.g. grooming, travelling, or foraging, (iii) spatial areas, e.g. local or
-regional, (iv) or temporal windows, e.g. daily or seasonal [@Kivela_2014;
-@Porter_2018]. Multilayer networks are relatively novel to studies of animal
-behaviour [@Silk_2018; @Finn_2019] and integrating scale within these 
-remains an unexplored opportunity to develop novel understanding of
-animal social systems.
-
-We examined scale-dependent multilayer networks of behavioural,
-landscape, and spatial ecology and applied this framework to caribou
-(*Rangifer tarandus*). First, we test to
-what degree the social scale of relationships, spatial scale of landscapes, and
-temporal scale of analysis influences our ability to interpret complex social
-systems. Second, we address how variation in the social, spatial, and temporal
-scale improves our understanding of the relationship between social association
-and seasonal resource availability. We conclude with potential future
-developments and applications of scale in multilayer networks.
+We examined scale-dependent multilayer networks of behavioural, landscape, and
+spatial ecology and applied this framework to caribou (*Rangifer tarandus*).
+First, we test to what degree the social scale of relationships, spatial scale
+of landscapes, and temporal scale of analysis influences our ability to
+interpret complex social systems. Second, we address how variation in the
+social, spatial, and temporal scale improves our understanding of the
+relationship between social association and seasonal resource availability. We
+conclude with potential future developments and applications of scale in
+multilayer networks.
 
@@
 association between individuals using the simple ratio index [SRI, @Cairns_1987].
-
-$$ SRI = \frac{x}{x + y_{AB} + y_{A} + y_{B}} $$
-
-where x is the number of fixes where individuals A and B were in the same group,
-$y_{A}$ is the number of fixes from individual A when individual B did not have
-a simultaneous fix, $y_{B}$ is the number of fixes from individual B when
-individual A did not have a simultaneous fix, and $y_{AB}$ is the number of
-simultaneous fixes from individuals A and B that were separated by more than the
-social distance threshold [@Farine_2015].
 

### 2020-08-26 paper/manuscript.Rmd
actually rm

@@
 
-<!-- rm:
-Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
-to an increased attention to the scale at which ecological processes are
-observed [@Schneider_2001; @Chave_2013]. Recent technological advances in
-remotely sensed imagery [@Drusch_2012] and animal tracking devices
-[@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of
-complex, high-resolution data. We highlight ways in which scale should be
-considered when building social networks from both observed and remotely sensed
-data. Our multilayer network analysis of caribou sociality incorporating high
-resolution GPS telemetry data and spatial land cover data is grounded in the
-context of observed animal behaviour as the scales we chose to explore, e.g.,
-social, spatial, and temporal, are scales that have
-also been investigated using traditional behavioural ethological methods. 
--->
-
 Multilayer networks remain a nascent but powerful tool in animal behavioural

### 2020-08-26 paper/manuscript.Rmd
add hr size
fix genetic structure

@@
 [@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
-on snow cover and distribution of craters on the landscape.
+on snow cover and distribution of craters on the landscape. Home range sizes for 
+caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
+summer [@Peignier_2019].
 
@@
 differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
-to temperature and breeding activity. Finally, it is crucial to include
+to genetic structure. Finally, it is crucial to include
 sufficient data within sampling periods or time windows to construct robust

### 2020-08-26 paper/manuscript.Rmd
how
fix cap m seq

@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each social distance threshold (5, 25, 50, 75, 100, 250, 500 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each land cover resolution (100 - 500 m by steps of 100 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
-differences in the multilayer social structure of mice (*Mus musculus domesticus*) related
+differences in how the multilayer social structure of mice (*Mus musculus domesticus*) related
 to genetic structure. Finally, it is crucial to include

### 2020-08-26 paper/manuscript.Rmd
portable affiliations in yaml
thanks to this SO question: https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown
and @tarleb

@@
 title: Considering scale in multilayer animal social networks
-author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
-date: |
-  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
-  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
-  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
+author:
+  - name: Alec L. Robitaille
+    email: robit.alec@gmail.com
+    institute: bio
+    correspondence: true
+  - name: Quinn M.R. Webber
+    institute: cabe
+  - name: Julie W. Turner
+    institute: bio
+  - name: Eric Vander Wal
+    institute: [bio, cabe]
+institute: 
+  - bio: Department of Biology, Memorial University of Newfoundland, Canada
+  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
 output:
-   # bookdown::github_document2: default
    bookdown::word_document2:
      reference_docx: template.docx
+     pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 knit: (function(inputFile, encoding) {

### 2020-08-26 paper/manuscript.Rmd
maybe add code availability?

@@
 
+# Code Availability
+
+Code for performing all multilayer social network analyses and generating the
+figures is available at 
+https://github.com/robitalec/scale-in-multilayer-networks [@Robitaille_2020] <!-- TODO: zenodo-->
+and released under the GNU General Public License 3.0. We depended on numerous R
+packages notably for the analysis: igraph, data.table, spatsoc, asnipe, and
+grainchanger, for the figures: ggplot2 and patchwork, and for reproducibility
+and workflow management drake, renv, and knitr.
+
 \newpage

### 2020-08-27 paper/manuscript.Rmd
revert title
example -> case study

@@
 ---
-title: Considering scale in multilayer animal social networks
+title: The problem and promise of scale in animal social multilayer networks
 author:
@@
 has become a central consideration in the way we understand landscape ecology
-and animal space use. Meanwhile, scale-dependent social processes can range from fine-scale
-interactions to co-occurrence and overlapping home ranges. Furthermore,
-sociality can vary within and across seasons. Multilayer networks promise the 
-explicit integration of
-the social, spatial and, temporal contexts. Given the complex interplay of
-sociality and animal space use in heterogeneous landscapes, there remains an
-important gap in our understanding of the influence of scale on animal social
-networks. Using an empirical example, we discuss ways of considering social, spatial and, temporal scale in
-the context of multilayer caribou social networks. Effective
-integration of social and spatial processes, including biologically meaningful
-scales, within the context of animal social networks is an emerging area of
-research. We incorporate perspectives that link the social environment to spatial
-processes across scales in a multilayer context.
+and animal space use. Meanwhile, scale-dependent social processes can range from
+fine-scale interactions to co-occurrence and overlapping home ranges.
+Furthermore, sociality can vary within and across seasons. Multilayer networks
+promise the explicit integration of the social, spatial and, temporal contexts.
+Given the complex interplay of sociality and animal space use in heterogeneous
+landscapes, there remains an important gap in our understanding of the influence
+of scale on animal social networks. Using an empirical case study, we discuss
+ways of considering social, spatial and, temporal scale in the context of
+multilayer caribou social networks. Effective integration of social and spatial
+processes, including biologically meaningful scales, within the context of
+animal social networks is an emerging area of research. We incorporate
+perspectives that link the social environment to spatial processes across scales
+in a multilayer context.
 

### 2020-08-27 paper/manuscript.Rmd
add caribou keyword
tidy intro p2

@@
 ## Keywords
-Rangifer, Social network analysis, Habitat selection, Landscape ecology, Space use
+Caribou, *Rangifer*, Social network analysis, Habitat selection, Landscape ecology, Space use
 
@@
 
-Social interactions exists across both temporal and spatial scales [Figure \@ref(fig:spacetime), @Whitehead_2008].
-For example, conspecific grooming requires close spatial proximity and occurs over brief time periods [e.g. @Carter_2015] whereas social associations
-represent shared space use by members of the same social group over longer time periods [@Franks_2009], and home range overlap occurs over
-coarser spatial and temporal scales [e.g. @Piza_Roca_2018].
-Although the social environment scales spatially and temporally, it
-remains unclear whether coarser scales of social interactions, such as social
-association and home range overlap, vary predictably [@Castles_2014;
-@Farine_2015a; @Evans_2019]. Social scale 
-is defined by the temporal and spatial scales across which different forms of sociality are measured  [@Farine_2015a].
+Social interactions exists across both temporal and spatial scales [Figure
+\@ref(fig:spacetime), @Whitehead_2008]. For example, conspecific grooming
+requires close spatial proximity and occurs over brief time periods 
+[e.g. @Carter_2015], social associations represent shared space use by members of the
+same social group over relatively longer time periods [@Franks_2009], and home
+range overlap occurs over coarser spatial and temporal scales [e.g.
+@Piza_Roca_2018]. Although the social environment scales spatially and
+temporally, it remains unclear whether coarser scales of social behaviour, such
+as social association and home range overlap, vary predictably 
+[@Castles_2014; @Farine_2015a; @Evans_2019]. Thus, social scale is defined by 
+the temporal and spatial scales across which different forms of sociality are measured
+[@Farine_2015a].
 

### 2020-08-27 paper/manuscript.Rmd
tidy intro p3, p4

@@
 scale-dependent contexts [@Pilosof_2017]. Multilayer networks are composed of
-multiple layers, each representing (i) different classes of individuals, e.g.
+multiple layers, that can represent (i) different classes of individuals, e.g.
 male or female, (ii) types of behaviours, e.g. grooming, travelling, or
@@
 relatively novel to studies of animal behaviour [@Silk_2018; @Finn_2019] and 
-integrating scale within these remains an unexplored opportunity to develop 
+integrating scale within multilayer networks remains an unexplored opportunity to develop 
 novel understanding of animal social systems.
@@
 of landscapes, and temporal scale of analysis influences our ability to
-interpret complex social systems. Second, we address how variation in the
-social, spatial, and temporal scale improves our understanding of the
-relationship between social association and seasonal resource availability. We
-conclude with potential future developments and applications of scale in
-multilayer networks.
+interpret complex social systems. Second, we address how variation in social,
+spatial, and temporal scales improves our understanding of the relationship
+between social association and seasonal resource availability. We conclude with
+potential future developments and applications of scale in multilayer networks.
 

### 2020-08-27 paper/manuscript.Rmd
add boertje 1985

@@
 Caribou dig holes, termed craters, in winter to access forage beneath the snow
-[@Bergerud_1974]. Cratering is presumed to be a costly behaviour, and as a
+[@Bergerud_1974]. Cratering is presumed to be a costly behaviour [@Boertje_1985], and as a
 result, caribou tend to occupy and re-use craters once they are established.
@@
 [@Mayor_2009]. Access to forage is therefore heterogeneous in winter and depends
-on snow cover and distribution of craters on the landscape. Home range sizes for 
-caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
-summer [@Peignier_2019].
+on snow cover and distribution of craters on the landscape.
 

### 2020-08-27 paper/manuscript.Rmd
mv hr size down
add kasozi 2020

@@
 individuals in the herd. We assumed these individuals were randomly distributed
-throughout the population.
+throughout the population. Home range sizes for 
+caribou on Fogo Island are on average 50.1 $km^2$ in winter and 17.5 $km^2$ in 
+summer [@Peignier_2019].
 
@@
 Land cover data were provided by the Newfoundland and Labrador Wildlife Division
-[@Integrated_2013]<!--TODO: check ref-->. Available land cover classification
+[@Integrated_2013]. Available land cover classification
 included nine habitat types at 30 m resolution. We reclassified the land cover
@@
 Typically for ungulates and other gregarious
-mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. The chain rule is applied by assigning a group identifier to the union of
+mammals, the ‘chain rule’ is used for group assignment [@Croft_2008; @Kasozi_2020]. 
+The chain rule is applied by assigning a group identifier to the union of
 buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within

### 2020-08-27 paper/manuscript.Rmd
minor edits

@@
 500 m of one another were considered in the same group. Increasing social
-distance threshold is a proxy for potential behavioural interactions (eg. vocal communication)
-that occur
-across these distances. For every social distance threshold, we calculated
-individual graph strength within each habitat layer, and edge overlap and
+distance threshold is a proxy for potential behavioural interactions 
+that occur across these distances (eg. grooming through vocal communication). 
+For every social distance threshold, we calculated
+individual graph strength within habitat layers, and edge overlap and
 multidegree across habitat layers.
@@
 individuals across three habitat layers (foraging, forest and open) for the
-entire study period. For each land cover resolution, we calculated individual
-graph strength within each habitat layer, and edge overlap and multidegree
+entire study period. For each land cover scale, we calculated individual
+graph strength within habitat layers, and edge overlap and multidegree
 across habitat layers.
@@
 entire study period. For each time window, we calculated
-individual graph strength within each time window, and edge overlap and
+individual graph strength within time windows, and edge overlap and
 multidegree across time windows.
@@
 (foraging, forest, and open) using $n$ randomly selected observations. We first
-generated a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
+selected a maximum of 1000 timesteps and iteratively used $n$ of these ($n$ =
 10 - 1000 observations by steps of 10), to ensure previously included timesteps,

### 2020-08-27 paper/manuscript.Rmd
minor edits

@@
 between ~20 - 100 m based on the rate at which variance in graph strength
-decreased. GPS data allowed [e.g. from this study and @Peignier_2019;
-@Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
-for studies of ungulate social behaviour in the field [@Lingle_2003; @Clutton_1982].
+decreased. GPS data allowed  us to confirm the use of 50 m buffer 
+[e.g. from this study and @Peignier_2019; @Lesmerises_2018] that has long been used
+for studies of ungulate social behaviour in the field 
+[@Lingle_2003; @Clutton_1982; @Kasozi_2020].
 
@@
 - `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
-indicated the importance of matching land cover resolution to scale of
+highlight the importance of matching land cover resolution to scale of
 habitat selection and choosing a land cover product with a resolution
@@
 The temporal multilayer network indicated within-year time windows where social
-network metrics increased. Edge overlap was higher in between approximately November and May (time windows 1, 6-11 and
+network metrics increased. Edge overlap was higher in between approximately 
+November and May (time windows 1, 6-11 and
 15-20) than between approximately June and October (time windows 2-5 and 12-15 
- (Figure \@ref(fig:temp) A). Time
-windows of higher edge overlap also had
+ (Figure \@ref(fig:temp) A). Time windows of higher edge overlap also had
 higher graph strength compared to time windows of lower edge overlap, between

### 2020-08-27 paper/manuscript.Rmd
minor edits

@@
 variation in open and foraging layers than in forest layers (Figure
-\@ref(fig:lcres) E). Furthermore, we observed a decrease in the proportion of relocations in
+\@ref(fig:lcres) E). On average, graph strength was highest in foraging habitat, 
+compared to forest and open habitat, despite the fact that foraging habitat was 
+the least common. Furthermore, we observed a decrease in the proportion of relocations in
 foraging habitat with increasing spatial resolution 
@@
 at which scale might these influence fitness (Box 1)? Are some scales better predictors
-for different fitness components, e.g. reproductive success or suvival?
+for different fitness components, e.g. reproductive success or survival?
 
 2. Why do individuals associate more strongly with certain conspecifics in some
-habitats? What is the role of movement in the context of habitat
+habitats? What is the role of movement in the context of habitat-specific social
 networks?

### 2020-08-27 paper/manuscript.Rmd
fill acknowledge

@@
 
-We thank all members of the Wildlife Evolutionary Ecology Lab, including J.
-Hendrix, K. Kingdon, S. Boyle, J. Balluffi-Fry, C. Prokopenko, I. Richmond, J.
-Hogg, and L. Newediuk for their comments on previous versions of this manuscript
-as well as D. C. Schneider for inspiration and helpful discussions about scale.
-Funding for this study was provided by a Vanier Canada Graduate Scholarship to
-QMRW and a NSERC Discovery Grant to EVW.
+We respectfully acknowledge the territory in which data were collected and
+analyzed as the ancestral homelands of the Beothuk and the Island of
+Newfoundland as the ancestral homelands of the Mi’kmaq and Beothuk. We thank
+members of the Newfoundland and Labrador Wildlife Division, including S. Moores,
+B. Adams, W. Barney, and J. Neville for facilitating animal captures and for
+logistical support in the field. We also thank all members of the Wildlife
+Evolutionary Ecology Lab, including J. Hendrix, K. Kingdon, S. Boyle, J.
+Balluffi-Fry, C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for their
+comments on previous versions of this manuscript as well as D. C. Schneider for
+inspiration and helpful discussions about scale. Funding for this study was
+provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery
+Grant to EVW.
 

### 2020-08-27 paper/manuscript.Rmd
add pkg citations

@@
 Code for performing all multilayer social network analyses and generating the
-figures is available at 
-https://github.com/robitalec/scale-in-multilayer-networks [@Robitaille_2020] <!-- TODO: zenodo-->
-and released under the GNU General Public License 3.0. We depended on numerous R
-packages notably for the analysis: igraph, data.table, spatsoc, asnipe, and
-grainchanger, for the figures: ggplot2 and patchwork, and for reproducibility
-and workflow management drake, renv, and knitr.
+figures is available at https://github.com/robitalec/scale-in-multilayer-networks 
+[@Robitaille_2020] and released under the GNU General Public License 3.0. 
+We depend on numerous R packages notably for the analysis: `igraph` [@Csardi_2006],
+`data.table` [@Dowle_2019], `spatsoc` [@Robitaille_2019], `asnipe` [@Farine_2019],
+and `grainchanger` [@Graham_2019], for the figures: `ggplot2` [@Wickham_2016] and
+`patchwork` [@Pedersen_2019], and for reproducibility and workflow management: 
+`drake` [@Landau_2018], `renv` [@Ushey_2020], and `knitr` [@Xie_2015].
 

### 2020-08-27 paper/manuscript.Rmd
caps based on

@@
 (ref:socres) Varying scale in social distance threshold.
-For each social distance threshold (5, 25, 50, 75, 100, 250, 500 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each social distance threshold (5, 25, 50, 75, 100, 250, 500 m), multilayer networks based on caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 Each line represents a single individual and graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes.
@@
 (ref:lcres) Varying spatial scale of land cover raster.
-For each land cover resolution (100 - 500 m by steps of 100 m), multilayer networks were constructed of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+For each land cover resolution (100 - 500 m by steps of 100 m), multilayer networks based on caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m).
@@
 (ref:temp) Varying temporal scale in multilayer networks.
-Multilayer networks were generated of caribou social associations within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
+Multilayer networks based on caribou social associations within time windows (20 ordinal sample periods) between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]`.
 A) Edge overlap was high between approximately November and May (time windows 1, 6-11, 15-20) and low between approximately June and October (time windows 2-5 and 12-15).
@@
 (ref:nobs) Varying scale in number of observations.
-Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
+Multilayer networks based on a subset of observations (10 - 1000 observations by steps of 10) of caribou social associations between `r DT[, format(min(datetime), '%B %Y')]` and `r DT[, format(max(datetime), '%B %Y')]` within three habitat layers (foraging, forest, and open).
 A) Edge overlap increased for all habitat layers with increasing number of observations.

### 2020-08-27 paper/manuscript.Rmd
digits
reorder a, b, c nobs

@@
 
-options(digits = 2, round = 2)
+options(digits = 1, round = 2)
 
@@
 As the number of observations used to generate multilayer networks increased,
-individuals became more connected and variance in metrics decreased. Edge
-overlap increased across all three habitat layers with increasing number of
-observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
-individuals increased quickly between 10 and 100 observations and continued to
-increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
-across individuals in all three habitat layers was highly variable at low number
-of observations and variance decreased after ~100 observations (Figure
-\@ref(fig:nobs) A). Since the variance in these multilayer metrics decreases
+individuals became more connected and variance in metrics decreased. Graph
+strength across individuals in all three habitat layers was highly variable at
+low number of observations and variance decreased after ~100 observations
+(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
+layers with increasing number of observations (Figure \@ref(fig:nobs) B).
+Similarly, multidegree for all individuals increased quickly between 10 and 100
+observations and continued to increase until 1000 observations (Figure
+\@ref(fig:nobs) C).  Since the variance in these multilayer metrics decreases
 after a certain number of observations, this sensitivity method could be useful

### 2020-08-27 paper/manuscript.Rmd
reorder lc

@@
 Increasing land cover resolution resulted in decreased availability of foraging
-habitat and corresponding low connectivity of individuals in foraging layers
-at higher land cover
-resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
-layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
-contrast, edge overlap was relatively consistent in forest and open layers
-as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
-variable within foraging habitat layers across land cover resolutions than open
-and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
-relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
-`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
-(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
-`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
-with increasing spatial resolution, while decreasing in foraging habitat 
-(`r count[res == 30 & lc == 3, percent]`% at 30 m
-- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
-highlight the importance of matching land cover resolution to scale of
-habitat selection and choosing a land cover product with a resolution
-sufficient to detect less common habitats.
+habitat and corresponding low connectivity of individuals in foraging layers at
+higher land cover resolutions. Edge overlap decreased sharply between 30 m and
+600 m in foraging layers, afterwards remaining stable to 1000 m (Figure
+\@ref(fig:lcres) D). In contrast, edge overlap was relatively consistent in
+forest and open layers as land cover resolution increased (Figure
+\@ref(fig:lcres) D). Graph strength was more variable within foraging habitat
+layers across land cover resolutions than open and forest habitat layers (Figure
+\@ref(fig:lcres) E). The proportion of relocations in forest 
+(`r count[res == 30 & lc == 2, percent]`% at 30 m - 
+`r count[res == 1000 & lc == 2, percent]`% at
+1000 m) and open (`r count[res == 30 & lc == 1, percent]`% at 30 m - 
+`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased with
+increasing spatial resolution, while decreasing in foraging habitat 
+(`r count[res == 30 & lc == 3, percent]`% at 30 m - 
+`r count[res == 1000 & lc == 3, percent]`% at 1000 m). 
+These results highlight the importance of matching land
+cover resolution to scale of habitat selection and choosing a land cover product
+with a resolution sufficient to detect less common habitats.
 

### 2020-08-28 paper/manuscript.Rmd

@@
 @Allen_2015]. Animals are influenced across scales by ecological processes such as
-trophic interactions, resource availability
-[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
+resource availability, trophic interactions, 
+[@Legendre_1993; @Chave_2013], and global climate [@Field_2009].
 Multiscale ecology has been integrated into species distribution modelling

### 2020-08-28 README.Rmd
add doi badge

@@
 ---
+
+[![DOI](https://zenodo.org/badge/291094231.svg)](https://zenodo.org/badge/latestdoi/291094231)
 
@@
 # The problem and promise of scale in multilayer networks
-Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal
 
-## TODO
-```{bash}
-grep -rni 'R/' -e 'TODO' || true;
-grep -rni 'scripts/' -e 'TODO' || true;
-grep -rni 'paper/manuscript.Rmd' -e 'TODO' || true;
-```
+* Authors:
+    + [Alec L. Robitaille](http://robitalec.ca)
+    + [Quinn M.R. Webber](https://qwebber.weebly.com/)
+    + [Julie W. Turner](https://www.julwturner.com/)
+    + [Eric Vander Wal](http://weel.gitlab.io)

### 2020-09-18 paper/manuscript.Rmd
fix title
minor edits

@@
 ---
-title: The problem and promise of scale in animal social multilayer networks
+title: The problem and promise of scale in multilayer animal social networks
 author:
@@
 
-(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyaena, passerine birds, sleepy lizards, and elephants.
+(ref:spacetime) Space-time diagram representing variation the relative spatial and temporal extent required for different types of social and communication processes for four species, including spotted hyenas, passerine birds, sleepy lizards, and elephants.
 Spatial and temporal extent for social interactions, e.g.
@@
 buffered GPS fixes collected at each two hour time step. As such, individuals in a group are within
-the social distance threshold of at least one other though not necessarily all
-other individuals [@Robitaille_2019]. Group assignment is defined using a 
+the social distance threshold of at least 1 other individual, though not 
+necessarily all other individuals [@Robitaille_2019]. Group assignment is defined using a 
 temporal threshold of 5 minutes

### 2020-09-18 paper/manuscript.Rmd
rm dup bib

@@
   rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
-bibliography: ../references/knitcite.bib
+bibliography: ../references/refs.bib
 csl: csl.csl

### 2020-09-18 paper/manuscript.Rmd
cap box1

@@
 
-# Box 1
+# Box 1: Phenotypes and Individual Fitness
 Social phenotype has been increasingly linked to individual fitness, including

### 2020-09-23 README.Rmd
fix title
update README

@@
 
-# The problem and promise of scale in multilayer networks
+# The problem and promise of scale in multilayer animal social networks
 
@@
     + [Eric Vander Wal](http://weel.gitlab.io)
+
+This repository contains the code accompanying the paper [“The problem and
+promise of scale in multilayer animal social networks”](https://doi.org/10.1093/cz/zoaa052). Scripts are under
+`scripts/` and reused functions are in `R/`. This project uses standard R
+package structure and can therefore be installed with `devtools`. This also
+helps declare external package dependencies required for the analysis. Please
+note that while functions are included here, they are not tested for use in
+other projects and may not be suitable (at least not in their current version).
+The project uses `drake` for workflow management and `renv` for explicitly
+declaring package dependencies and their versions.
+
+## Abstract
+Scale remains a foundational concept in ecology. Spatial scale, for instance,
+has become a central consideration in the way we understand landscape ecology
+and animal space use. Meanwhile, scale-dependent social processes can range from
+fine-scale interactions to co-occurrence and overlapping home ranges.
+Furthermore, sociality can vary within and across seasons. Multilayer networks
+promise the explicit integration of the social, spatial and, temporal contexts.
+Given the complex interplay of sociality and animal space use in heterogeneous
+landscapes, there remains an important gap in our understanding of the influence
+of scale on animal social networks. Using an empirical case study, we discuss
+ways of considering social, spatial and, temporal scale in the context of
+multilayer caribou social networks. Effective integration of social and spatial
+processes, including biologically meaningful scales, within the context of
+animal social networks is an emerging area of research. We incorporate
+perspectives that link the social environment to spatial processes across scales
+in a multilayer context.
